### 2018-06-27 papers/SiVL2018/objectnaming.tex
some files for the SiVL paper

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\title{How do we get from object recognition\\ to object naming?} % Replace with your title

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins.
\dots
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

Real-world objects are members of many categories. 
and speakers can typically between choose between different, more or less specific names when referring to a particular visual entity. 
For instance, the entity surrounded by the green box in Figure \ref{fig:example} is an instance of the categories \textit{female child, child, female, person, organism}, etc.\  and can be referred to with names such as e.g.\ \textit{girl, kid, cutie, daughter, person, human}.
But even though almost every task in language \& vision involves the prediction of object names (e.g. image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word/linguistic concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focussed on attributes, rather than object names.
Recently, however, \cite{graf2016animal} have shown that object naming preferences are subject to contextual constraints and pragmatic factors: in a typical reference game set-up with images of target objects surrounded by distractor objects, speakers have been found to flexibly adjust object names depending on the context. For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.

On the vision side, however, there is huge body of research on object recognition, i.e.\ labeling visual objects according to a set of categories, cf.\ \cite{simonyan2014very,deng2014large,googlenet}.

\begin{figure}
\centering
\includegraphics[height=3.5cm]{fig/flickr_1000268201_boxes}
\caption{INCLUDE MSCOCO examples}
\label{fig:example}
\end{figure}

\section{Background}

\section{Data}

\subsection{Corpora}

\paragraph{Referring Expressions}
We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
See \cite{Yu2016} for more details.

\paragraph{Image Captions}

TODO.

\subsection{Preprocessing}

We parse referring expressions and captions with the Stanford Dependency Parser.
We extract heads/object names as follows: TODO.

\section{Names: Levels of specificity}

In this Section, we investigate whether variability of reference level can be observed in existing data sets for language \& vision.

\subsection{Using WordNet}

\cite{graf2016animal} investigate object naming with respect to reference level. They distinguish and manually annotate 3 levels: (i) sub-level (\textit{dalmatian}), (ii) basic-level (\textit{dog}), (iii) super-level (\textit{animal}).

For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology. 
In this Section, we investigate whether WordNet is appropriate for defining reference level. We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.

\paragraph{Specifcity} We calculate this distance as follows: we lookup all synsets of a word and retrieve the respective paths to the root node in WordNet. 
For each word, we use the minimal path length as distance to the root node.

Table \ref{tab:specnames} shows the levels of specificity we observe for object names in the RefCoco data set.
We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels as the three-way classification adopted by \cite{graf2016animal}.

Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, here are some problematic examples from Table \ref{tab:specnames}:

\begin{itemize}
\item elephant (10) is more specific than panda (14)? horse is less specific than elephant (10)?
\end{itemize}

\begin{table}
\centering
\setlength{\tabcolsep}{4pt}
\begin{tabular}{rrl}
\toprule
 specificity &  rel.freq. &                          top 5 names \\
\midrule
          -1 &   0.071697 &      NONE,brocolli,zeb,broc,girafe \\
           2 &   0.003898 &                         thing,things \\
           3 &   0.001182 &   object,group,set,substance,objects \\
           4 &   0.140633 &           man,person,piece,head,part \\
           5 &   0.100739 &       player,glass,baby,front,corner \\
           6 &   0.208590 &              woman,girl,kid,boy,bowl \\
           7 &   0.238708 &            guy,right,chair,lady,bear \\
           8 &   0.110613 &           horse,bus,cow,pizza,batter \\
           9 &   0.097390 &         shirt,car,bike,donut,catcher \\
          10 &   0.048368 &   elephant,couch,truck,vase,suitcase \\
          11 &   0.008828 &    motorcycle,clock,mom,dad,scissors \\
          12 &   0.002822 &  oven,airplane,suv,taxi,refrigerator \\
          13 &   0.005253 &   laptop,fridge,canoe,orioles,pigeon \\
          14 &   0.000414 &  panda,freezer,penguin,rooster,rhino \\
          15 &   0.030870 &   zebra,giraffe,zebras,giraffes,deer \\
          16 &   0.000083 &       bison,mooses,orang,elks,sambar \\
          17 &   0.000143 &           ox,cattle,gnu,mustang,orca \\
\bottomrule
\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
\label{tab:specnames}
\end{table}

\clearpage

\bibliographystyle{splncs}
\bibliography{naming}
\end{document}

### 2018-06-28 utils/cmp_to_ilsvrc_synsets.py
add script for cmp_synsets(image_ds, ilsvrc)

@@ -1,0 +1,97 @@
+# coding: utf-8
+from collections import defaultdict
+import os
+import re
+import sys
+
+import json
+import matplotlib
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+
+import df_annotation
+from annotation_utils import get_synset_first, tag2pos, get_lch, get_ss_from_offset, get_path_similarity
+import annotation_utils as anno_utils
+
+
+dataset = "refcoco" #"flickr30k"
+data_dir = "../data/"
+cat_or_name = "names" #"region_cat" # "names"
+cat_map_refcoco = {"stop sign": "street sign", 
+                   "wine glass": "drinking glass",
+                   "sports ball": "ball", 
+                   "potted plant": "plant life"}
+
+#anno_infname = "%s_anno-dep-pos-wn-attr.json.gz" % (dataset)
+region_dfname = "%s_regions_distractors.json.gz" % (dataset)
+
+#annodf = pd.read_json(os.path.join(data_dir, anno_infname), compression='gzip', orient='split')
+regiondf = pd.read_json(os.path.join(data_dir, region_dfname), compression='gzip', orient='split')
+
+synsets_ilsvrc = [get_ss_from_offset(off.strip()) for off in open("../ilsvrc_synsets.txt")]
+
+
+# collect set of all possible synsets in image data
+
+if cat_or_name == "region_cat":
+    ssids1_imgdata = regiondf[cat_or_name].values.tolist()
+else:
+    ssids1_imgdata = [name for names in regiondf[cat_or_name] for name in names]
+    
+synsets_imgdata = []
+no_synset_available = set()
+for ssid1 in ssids1_imgdata:
+    if ssid1 != None:
+        if re.search("\.[nvra]\.[0-9]", ssid1):
+            ss1 = anno_utils.get_synset(ssid1)
+        else:
+            if ssid1.startswith("RAW:"):
+                ssid1 = re.sub("RAW: *", "", ssid1)
+                ssid1 = cat_map_refcoco.get(ssid1, ssid1).replace(" ", "_")
+            ss1 = get_synset_first(ssid1)
+        if not ss1:
+            no_synset_available.add(ssid1)
+            continue
+        synsets_imgdata.append(ss1)
+        
+synsets_imgdata = set(synsets_imgdata)
[…]

### 2018-06-28 utils/create_df_heads_distractors.py
[TBC?] adds script for creating data frame with heads_distractors information

@@ -1,0 +1,168 @@
+# coding: utf-8
+from collections import defaultdict
+import os
+import re
+import sys
+
+import json
+import matplotlib
+import numpy as np
+import matplotlib.pyplot as plt
+import pandas as pd
+
+import df_annotation
+from annotation_utils import get_synset_first, tag2pos, get_lch, get_path_similarity
+import annotation_utils as anno_utils
+
+
+dataset = "flickr30k"
+data_dir = "../data/"
+
+anno_infname = "%s_anno-dep-pos-wn-attr.json.gz" % (dataset)
+
+annodf = pd.read_json(os.path.join(data_dir, anno_infname), compression='gzip', orient='split')
+
+outfname_regiondf = "%s_regions_distractors.json.gz" % (dataset)
+
+
+if os.path.exists(os.path.join(data_dir, outfname_regiondf)):
+    regiondf = pd.read_json(os.path.join(data_dir, outfname_regiondf), compression='gzip', orient='split')
+else:
+    # Get head and its position in refexp (0 is "root")
+    heads = annodf["basicDependencies"].apply(lambda x:(x[0]['dependentGloss'], x[0]['dependent']-1))
+
+    # Get XXX
+    heads_wn = pd.DataFrame(heads).apply(axis=1, func=lambda x: annodf["wn_anno_parse"].iloc[x.name][heads.iloc[x.name][1]])
+
+
+    images = set(annodf.image_id)
+    image2region = {}
+    image2cats = {}
+    if "cat" in annodf:
+        for im in images:
+            image2region[im] = list(annodf[annodf['image_id'] == im].region_id)
+            image2cats[im] = list(annodf[annodf['image_id'] == im].cat)
+    else:
+        for im in images:
+            image2region[im] = list(annodf[annodf['image_id'] == im].region_id)
+            
+
+    # Get region to name mapping
+    region2names = defaultdict(list)
+    for region_id,head_wn in zip(list(annodf['region_id']),list(heads_wn)):
+        region2names[region_id].append(head_wn)
+
+
+    region2image = {reg:im for im in image2region for reg in image2region[im]}
+
+    region_dict = []
+    #for reg in region2image:
+    for reg in annodf.region_id:
+        regs_of_img = image2region.get(region2image.get(reg, 0), None)
+        if regs_of_img:
+
+            distractors = list(filter(lambda other: other!=reg, regs_of_img))
+
+        target_cat = [name_lex[1] for name_lex in region2names[reg]]
[…]

### 2018-06-28 papers/SiVL2018/objectnaming.tex

@@
 This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.
+
+Most research on computer vision and object recognition has somehow worked around the fact that objects can be instances of multiple, hierarchically embedded categories. 
+State-of-the-art recognition models are mostly trained as classifiers on a flat of 1000 categories in ImageNet, reducing the ImageNet ontology to an inherently flat annotation scheme and treating
+object labels as mutually exclusive.
 

### 2018-07-02 papers/SiVL2018/objectnaming.tex
Adds first draft of structure; splits sections into files

--- 2018-06-27 papers/SiVL2018/objectnaming.tex
@@
-% last updated in April 2002 by Antje Endemann
-% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016
+\cite{graf2016animal}
+\cite{Rosch1978}
+\subsection{Intro to Problem}
 
-\documentclass[runningheads]{llncs}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
-\usepackage{booktabs}
-\usepackage{color}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
-
-\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-
-\begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
-\pagestyle{headings}
-\mainmatter
-\def\ECCV18SubNumber{***}  % Insert your submission number here
-
-\title{How do we get from object recognition\\ to object naming?} % Replace with your title
-
-\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV18SubNumber}
-
-\maketitle
-
-\begin{abstract}
-The abstract should summarize the contents of the paper. LNCS guidelines
-indicate it should be at least 70 and at most 150 words. It should be set in 9-point
-font size and should be inset 1.0~cm from the right and left margins.
-\dots
-\keywords{We would like to encourage you to list your keywords within
-the abstract section}
-\end{abstract}
-
-\section{Introduction}
-
-Real-world objects are members of many categories. 
-and speakers can typically between choose between different, more or less specific names when referring to a particular visual entity. 
-For instance, the entity surrounded by the green box in Figure \ref{fig:example} is an instance of the categories \textit{female child, child, female, person, organism}, etc.\  and can be referred to with names such as e.g.\ \textit{girl, kid, cutie, daughter, person, human}.
-But even though almost every task in language \& vision involves the prediction of object names (e.g.
-image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word/linguistic concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
-Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focussed on attributes, rather than object names.
-Recently, however, \cite{graf2016animal} have shown that object naming preferences are subject to contextual constraints and pragmatic factors: in a typical reference game set-up with images of target objects surrounded by distractor objects, speakers have been found to flexibly adjust object names depending on the context.
-For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
-This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.
-
-On the vision side, however, there is huge body of research on object recognition, i.e.\ labeling visual objects according to a set of categories, cf.\ \cite{simonyan2014very,deng2014large,googlenet}.
-
-\begin{figure}
-\centering
-\includegraphics[height=3.5cm]{fig/flickr_1000268201_boxes}
-\caption{INCLUDE MSCOCO examples}
-\label{fig:example}
-\end{figure}
-
-\section{Background}
-
-\section{Data}
-
-\subsection{Corpora}
-
-\paragraph{Referring Expressions}
-We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
-These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
-RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
-The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
-See \cite{Yu2016} for more details.
-
-\paragraph{Image Captions}
-
-TODO.
-
-\subsection{Preprocessing}
-
-We parse referring expressions and captions with the Stanford Dependency Parser.
-We extract heads/object names as follows: TODO.
-
-\section{Names: Levels of specificity}
-
-In this Section, we investigate whether variability of reference level can be observed in existing data sets for language \& vision.
-
-\subsection{Using WordNet}
-
+\subsection{Definition Sub-, basic-, super-level Categories}
 \cite{graf2016animal} investigate object naming with respect to reference level.
@@
 
+\section{Requirements: What Do We Need? \cs{[Subsection of \ref{sec:object_naming}?]}}
 For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology.
-In this Section, we investigate whether WordNet is appropriate for defining reference level. We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.
-
-\paragraph{Specifcity} We calculate this distance as follows: we lookup all synsets of a word and retrieve the respective paths to the root node in WordNet. 
-For each word, we use the minimal path length as distance to the root node.
-
-Table \ref{tab:specnames} shows the levels of specificity we observe for object names in the RefCoco data set.
-We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels as the three-way classification adopted by \cite{graf2016animal}.
-
-Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, here are some problematic examples from Table \ref{tab:specnames}:
-
-\begin{itemize}
-\item elephant (10) is more specific than panda (14)? horse is less specific than elephant (10)?
-\end{itemize}
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{4pt}
-\begin{tabular}{rrl}
-\toprule
- specificity &  rel.freq. &                          top 5 names \\
-\midrule
-          -1 &   0.071697 &      NONE,brocolli,zeb,broc,girafe \\
-           2 &   0.003898 &                         thing,things \\
-           3 &   0.001182 &   object,group,set,substance,objects \\
-           4 &   0.140633 &           man,person,piece,head,part \\
-           5 &   0.100739 &       player,glass,baby,front,corner \\
-           6 &   0.208590 &              woman,girl,kid,boy,bowl \\
-           7 &   0.238708 &            guy,right,chair,lady,bear \\
-           8 &   0.110613 &           horse,bus,cow,pizza,batter \\
-           9 &   0.097390 &         shirt,car,bike,donut,catcher \\
-          10 &   0.048368 &   elephant,couch,truck,vase,suitcase \\
-          11 &   0.008828 &    motorcycle,clock,mom,dad,scissors \\
-          12 &   0.002822 &  oven,airplane,suv,taxi,refrigerator \\
-          13 &   0.005253 &   laptop,fridge,canoe,orioles,pigeon \\
-          14 &   0.000414 &  panda,freezer,penguin,rooster,rhino \\
-          15 &   0.030870 &   zebra,giraffe,zebras,giraffes,deer \\
-          16 &   0.000083 &       bison,mooses,orang,elks,sambar \\
-          17 &   0.000143 &           ox,cattle,gnu,mustang,orca \\
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{table}
-
-\clearpage
-
-\bibliographystyle{splncs}
-\bibliography{naming}
-\end{document}

### 2018-07-02 papers/SiVL2018/resources.tex
Adds first draft of structure; splits sections into files

\begin{table*}[t]
	\begin{tabular}{|l|l|llll|}
		\hline
		Resource & Purpose & \multicolumn{4}{c|}{Useful For}\\
				& 			& Basic-level Names & Specificity & Bla & Bli \\
		\hline \hline
		RefCOCO & XXX & 
	\end{tabular}
	\caption{\label{tab:summary_resources} Intended to provide an overview of resources, their purpose/use and shortcomings wrt object naming}
\end{table*}

\subsection{Computer Vision Resources}
\paragraph{Methods: Object Detectors, Image Classifiers}

\paragraph{ImageNet and ILSVRC}
\paragraph{MSCOCO} \cite{mscoco}

\subsection{V\ \&\ L Resources}
\paragraph{VisualGenome}
\paragraph{(ReferIt) RefCOCO and alike}
Based on MSCOCO; Other MSCOCO-based resources: Captions; Visual Genome in parts\\

We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
See \cite{Yu2016} for more details.

\paragraph{Flickr30k Entities}

\subsection{\cs{Language Resources? (WordNet)}}

\subsection{Analysis of Data wrt Our Requirements(?)}

\subsubsection{Pre-processing}
We parse referring expressions and captions with the Stanford Dependency Parser.
We extract heads/object names as follows: TODO.

\subsubsection{Level of Specificity} 
Variability of reference level in existing data sets for language \& vision?
Are resources appropriate for defining reference level?
\paragraph{WordNet?}

We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.
We estimate this distance as the minimal path length of all synsets of a word  to the root node.

Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the RefCoco data set.
We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification.

Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, here are some problematic examples from Table \ref{tab:specnames}:

\begin{itemize}
\item elephant (10) is more specific than panda (14)? horse is less specific than elephant (10)?
\end{itemize}

\begin{table}
\centering
\setlength{\tabcolsep}{4pt}
\begin{tabular}{rrl}
\toprule
 specificity &  rel.freq. &                          top 5 names \\
\midrule
          -1 &   0.071697 &      NONE,brocolli,zeb,broc,girafe \\
           2 &   0.003898 &                         thing,things \\
           3 &   0.001182 &   object,group,set,substance,objects \\
           4 &   0.140633 &           man,person,piece,head,part \\
           5 &   0.100739 &       player,glass,baby,front,corner \\
           6 &   0.208590 &              woman,girl,kid,boy,bowl \\
           7 &   0.238708 &            guy,right,chair,lady,bear \\
           8 &   0.110613 &           horse,bus,cow,pizza,batter \\
           9 &   0.097390 &         shirt,car,bike,donut,catcher \\
          10 &   0.048368 &   elephant,couch,truck,vase,suitcase \\
          11 &   0.008828 &    motorcycle,clock,mom,dad,scissors \\
          12 &   0.002822 &  oven,airplane,suv,taxi,refrigerator \\
          13 &   0.005253 &   laptop,fridge,canoe,orioles,pigeon \\
          14 &   0.000414 &  panda,freezer,penguin,rooster,rhino \\
          15 &   0.030870 &   zebra,giraffe,zebras,giraffes,deer \\
          16 &   0.000083 &       bison,mooses,orang,elks,sambar \\
          17 &   0.000143 &           ox,cattle,gnu,mustang,orca \\
\bottomrule
\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
\label{tab:specnames}
\end{table}

\paragraph{No. of images in ImageNet?}

### 2018-07-02 papers/SiVL2018/sivl_2018.tex
Adds first draft of structure; splits sections into files

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage[usenames, dvipsnames]{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\cs}[1]{\textcolor{PineGreen}{\emph{//cs: #1//}}}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\title{How do we get from object recognition\\ to object naming?} % Replace with your title

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins.
\dots
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

Real-world objects are members of many categories and speakers can typically choose between different, more or less specific names when referring to a particular visual entity. 
For instance, the entity surrounded by the green box in Figure \ref{fig:example} is an instance of the categories \textit{female child, child, female, person, organism}, etc.\  and can be referred to with names such as, e.g.,\ \textit{girl, kid, cutie, daughter, person, human}.
But even though almost every task in language \& vision involves the prediction of object names (e.g. image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word/linguistic concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
Recently, however, \cite{graf2016animal} have shown that object naming preferences are subject to contextual constraints and pragmatic factors: in a typical reference game set-up with images of target objects surrounded by distractor objects,\cs{of target objects, each  presented along with images of distractor objects} speakers have been found to flexibly adjust object names depending on the context. For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.

Most research on computer vision and object recognition has somehow worked around the fact that objects can be instances of multiple, hierarchically embedded categories. 
State-of-the-art recognition models are mostly trained as classifiers on a flat of 1000 categories in ImageNet, reducing the ImageNet ontology to an inherently flat annotation scheme and treating
object labels as mutually exclusive.

On the vision side, however, there is a huge body of research on object recognition, i.e.\ labeling visual objects according to a set of categories, cf.\ \cite{simonyan2014very,deng2014large,googlenet}.

\section{Naming Objects (in Context)}
\label{sec:object_naming}
\textbf{TODO@Laura}\\
\input{objectnaming}

\begin{figure}
	\centering
	\includegraphics[height=3.5cm]{fig/flickr_1000268201_boxes}
	\caption{INCLUDE MSCOCO examples}
	\label{fig:example}
\end{figure}

\section{Resources: What Do We Have?}
\label{sec:resources}
\textbf{TODO@Carina}\\
\input{resources}

\section{Proposal}
\label{sec:future_proposal}
\textbf{TODO@Sina (?)}\\
\input{proposal}

\clearpage
\bibliographystyle{splncs}
\bibliography{naming}
\end{document}

### 2018-07-02 utils/annotation_utils.py
cleans up code and files

@@ -73,7 +73,8 @@ def load_dep_parser():
     return StanfordNeuralDependencyParser(
         model_path=parser_modelpath,
         path_to_jar=parser_jarpath, path_to_models_jar=parser_modeljar, 
-        java_options='-Xmx4g')
+        java_options='-Xmx4g --add-modules java.se.ee',
+        corenlp_options='')
 
 def parse_refEpx(refExps, dep_parser=None):
     if not dep_parser:
@@ -131,9 +132,36 @@ def get_refanno(tagged_words):
     return ann_words
 
 def tag2pos(tag):
-    tag_map = {"JJ": "a", "JJS": "a", "NN": "n", "NNS": "n"} # TODO
+    tag_map = {"JJ": "a", "JJS": "a", "NN": "n", "NNS": "n", "None": None} # TODO
     return tag_map.get(tag, None)
 
+def _apply(ssid1, ssid2, func):
+    ss1 = ssid1
+    ss2 = ssid2
+    if isinstance(ssid1, str):
+        ss1 = get_synset(ssid1)
+    if isinstance(ssid2, str):
+        ss2 = get_synset(ssid2)
+    return func(ss1, ss2)
+
+def get_synset(ssid):
+    """
+    >>> get_synset('girl.n.01')
+    Synset('girl.n.01')
+    """
+    return wn.synset(ssid)
+
+def get_ss_from_offset(offset):
+    """
+    >>> get_synset_from_offset('02084071-n')
+    Synset('dog.n.01')
+    >>> get_synset_from_offset('n02084071')
+    Synset('dog.n.01')
+    """
+    if not offset[0].isdigit():
+        offset = offset[1:] + "-" + offset[0]
+    return wn.of2ss(offset)
+    
 def get_synset_first(word, pos=None):
     all_synsets = wn.synsets(word, pos)
     #if not all_synsets and pos != None:
@@ -141,6 +169,11 @@ def get_synset_first(word, pos=None):
     if all_synsets:
         return all_synsets[0]
     return None
+
+def get_ss_first_name_and_lexfile(word, pos=None):
+    synset = get_synset_first(word, pos=pos)
+    lexfile_info = get_ss_lexfile_info(synset)
+    return (get_synset_name(synset), lexfile_info)
 
 def get_synset_name(ss):
     if not ss:
@@ -157,6 +190,23 @@ def get_ss_lexfile_info(ss):
         return None
     return ss.lexname()
 
+def get_lch(ssid1, ssid2):
[…]

### 2018-07-02 utils/cmp_to_ilsvrc_synsets.py

@@ -14,84 +14,145 @@ import df_annotation
 from annotation_utils import get_synset_first, tag2pos, get_lch, get_ss_from_offset, get_path_similarity
 import annotation_utils as anno_utils
 
-
-dataset = "refcoco" #"flickr30k"
-data_dir = "../data/"
-cat_or_name = "names" #"region_cat" # "names"
-cat_map_refcoco = {"stop sign": "street sign", 
-                   "wine glass": "drinking glass",
-                   "sports ball": "ball", 
-                   "potted plant": "plant life"}
-
-#anno_infname = "%s_anno-dep-pos-wn-attr.json.gz" % (dataset)
-region_dfname = "%s_regions_distractors.json.gz" % (dataset)
-
-#annodf = pd.read_json(os.path.join(data_dir, anno_infname), compression='gzip', orient='split')
-regiondf = pd.read_json(os.path.join(data_dir, region_dfname), compression='gzip', orient='split')
-
-synsets_ilsvrc = [get_ss_from_offset(off.strip()) for off in open("../ilsvrc_synsets.txt")]
-
-
-# collect set of all possible synsets in image data
-
-if cat_or_name == "region_cat":
-    ssids1_imgdata = regiondf[cat_or_name].values.tolist()
-else:
-    ssids1_imgdata = [name for names in regiondf[cat_or_name] for name in names]
+def load_imagenet_data(imagenet_path="."):
+    synsets_ilsvrc = [get_ss_from_offset(off.strip()) for off in open(os.path.join(imagenet_path, 'ilsvrc_synsets.txt'))]
+    offsets_numImgs = json.load(open(os.path.join(imagenet_path, 'synsets_images_counts.json')))
     
-synsets_imgdata = []
-no_synset_available = set()
-for ssid1 in ssids1_imgdata:
-    if ssid1 != None:
-        if re.search("\.[nvra]\.[0-9]", ssid1):
-            ss1 = anno_utils.get_synset(ssid1)
-        else:
-            if ssid1.startswith("RAW:"):
-                ssid1 = re.sub("RAW: *", "", ssid1)
-                ssid1 = cat_map_refcoco.get(ssid1, ssid1).replace(" ", "_")
-            ss1 = get_synset_first(ssid1)
-        if not ss1:
-            no_synset_available.add(ssid1)
-            continue
-        synsets_imgdata.append(ss1)
[…]

### 2018-07-02 utils/create_df_heads_distractors.py

@@ -15,7 +15,7 @@ from annotation_utils import get_synset_first, tag2pos, get_lch, get_path_simila
 import annotation_utils as anno_utils
 
 
-dataset = "flickr30k"
+dataset = "refcoco" #"flickr30k"
 data_dir = "../data/"
 
 anno_infname = "%s_anno-dep-pos-wn-attr.json.gz" % (dataset)
@@ -23,7 +23,6 @@ anno_infname = "%s_anno-dep-pos-wn-attr.json.gz" % (dataset)
 annodf = pd.read_json(os.path.join(data_dir, anno_infname), compression='gzip', orient='split')
 
 outfname_regiondf = "%s_regions_distractors.json.gz" % (dataset)
-
 
 if os.path.exists(os.path.join(data_dir, outfname_regiondf)):
     regiondf = pd.read_json(os.path.join(data_dir, outfname_regiondf), compression='gzip', orient='split')
@@ -85,8 +84,9 @@ else:
 regiondf['ndistractors'] = regiondf.distractor_cats.apply(lambda x: len(x))
 #regiondf['ndistrs_unique'] = regiondf.distractor_cats.apply(lambda x: len(set(x)))
 
-#namings_distr_target = ["distractor_cats", "region_cat"]
 namings_distr_target = ["distractor_names", "names"]
+if dataset == "refcoco":
+    namings_distr_target = ["distractor_cats", "region_cat"]
 
 distances = []
 lch_distances = []
@@ -146,9 +146,9 @@ sorted_lch_counts = sorted(counts_lch.items(), key=lambda x: x[1], reverse=True)
 
 fout = open(os.path.join(data_dir, "lch_counts"+anno_infname.replace(".json", "").replace(".gz", "")+".txt"), "w")
 for lch, count in sorted_lch_counts:
-    fout.write("{0}\t{1:d}\t{2}\n".format(lch, count, " ".join(lch_objNames[lch])))
-    
+    fout.write("{0}\t{1:d}\t{2}\n".format(lch, count, " ".join([ss.name() for ss in lch_objNames[lch]])))
 fout.close()
+
 print("\nlch and counts written to ", os.path.join(data_dir, "lch_counts"+anno_infname.replace(".json", "").replace(".gz", "")+".txt"))
 
 

### 2018-07-02 utils/df_annotation.py

@@ -10,10 +10,19 @@ import pandas as pd
 
 import annotation_utils as anno_utils
 
-USRNAME ='u148188' # 'carina'
+USRNAME = 'u148188' #'carina' # 'u148188'
 
 def load_df(fpath):
     return pd.read_json(fpath, compression='gzip', orient='split')
+
+# PoS Tagging
+# From Stanford parses
+def add_pos_tags_from_parse(parsedf, out_fpath=None):
+    parsedf['tagged_parse'] = parsedf["parse"].apply(lambda x: re.findall("\(([^\)^\(]+?)\)", x))
+    parsedf['tagged_parse'] = parsedf["tagged_parse"].apply(lambda x: [[a.split()[1], a.split()[0]] for a in x])
+    if out_fpath:
+        parsedf.to_json(out_fpath, compression='gzip', orient='split')
+    return parsedf
 
 # Stanford PoS Tagger
 def add_pos_tags(refdf, out_fpath=None):
@@ -23,7 +32,11 @@ def add_pos_tags(refdf, out_fpath=None):
         refdf.to_json(out_fpath, compression='gzip', orient='split')
     return refdf
 
+
 # Stanford Neural Dependency Parser
+def load_dep_parses_from_json(json_fpath, out_fpath=None):
+    return pd.read_json("../data/%s_depdf.json.gz" % dataset, compression='gzip', orient='split')
+
 def add_dep_parses(refdf, out_fpath=None):
     dep_parser = anno_utils.load_dep_parser()    
     parses = anno_utils.parse_refEpx(
@@ -75,10 +88,16 @@ def add_root_from_dep_parse(json_fpath, out_fpath=None):
 
 # Attributes and Names
 def add_attrs_names(refdf, out_fpath=None):
-    if 'tagged' in refdf:
-        refdf['attr_name'] = refdf['tagged'].apply(lambda x: anno_utils.get_refanno(x))
-    if 'tagged_stnf' in refdf:
-        refdf['attr_name_stnf'] = refdf['tagged_stnf'].apply(lambda x: anno_utils.get_refanno(x))
+    level = 'tagged'
+    ext = ''
+    if 'tagged_parse' in refdf:
+        ext = '_parse'
+    elif 'tagged_stnf' in refdf:
+        ext = '_stnf'
+    level += ext
+    
+    if level in refdf:
+        refdf['attribute%s' % ext] = refdf[level].apply(lambda x: anno_utils.get_refanno(x))
[…]

### 2018-07-06 papers/SiVL2018/objectnaming.tex
adds first draft of Sec 2

@@
-\cite{graf2016animal}
-\cite{Rosch1978}
+%\cite{graf2016animal}
+%\cite{Rosch1978}
 \subsection{Intro to Problem}
+The act of naming an object amounts to that of picking out a nominal to be employed to refer to that particular object (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'') and can be seen as a subtask of generating a referring expression.
+The lexical choice involved in naming is a non-trivial one \cite{brown1958shall}\cite{olson1970language}.
+Since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative.
+Indeed, for all such names their denotation includes the target object.
+However, in communicative situations, a particular name is selected for an object considering conceptual information about the object and contextual requirements.
 
+To start with, lexical alternatives differ in their \textbf{level of specificity} (e.g., \textit{dog} is less specific than \textit{beagle})\cite{cruse1977pragmatics}.
+The categories and concepts they denote are organized in a hierarchical fashion according to class inclusion relations (e.g., a beagle is a dog, a dog is an animal etc.)  \cite{murphy2004big}.
+They can be seen as giving rise to a taxonomy, or ontology.
+%(note that, in principle, knowing the most specific category of an object in such a structure gives us inductive access to all its other categories) 
+It was shown that for each type of object, there is a preferred level of specificity which is employed in naming, called the \textbf{entry-level}.
+This typically corresponds to categories with an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \textit{dog}, \textit{car}) \cite{rosch1976basic}; however, for less prototypical members of such categories a more specific level is usually chosen (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}.
+This factor is typically referred to as \textbf{lexical availability}.
+Moreover, contextual factors also affect object naming.
+For example, scenarios where the target object is presented with other objects create a pressure for generating names which uniquely identify the target, thus excluding the competing alternatives (or \textit{distractors}).
+To do so, a speaker may be required to the use of more specific expressions than the entry-level, in spite of these being less default or generally more costly (e.g., long, infrequent).
+A series of study showed that speakers tend to balance the preferences for reducing the \textbf{cost} of a name, on one side, and \textbf{ambiguity}, on the other (for example, they may opt for an ambiguous expression if less costly) \cite{rohde2012communicating} \cite{graf2016animal}.
+Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or prominence \cite{}
+
+%\begin{itemize}
+%\item Naming (lexical choice of nominal reference) is not trivial: many names for an object \cite{brown1958shall}.
+If seen as the act of picking out an applicable level: each object simultaneously belong to multiple categories, which reflect different conceptualizations and may be more or less appropriate across contexts,
+
+% \cite{olson1970language}. Lexical alternatives: near-synonyms, hyponyms, hypernyms etc.\cite{edmonds2002near}
+
+%\item Typically, variation across levels of specificity \cite{cruse1977pragmatics} Concepts are organized in a hierarchical fashion according to class inclusion relations, giving rise to a taxonomy \cite{murphy2004big}.
+Note that if accessing the most specific category in such taxonomy we can inherit knowledge about all the other categories it is also part of, by backtracking the path up to the root in the ontology (inductive access to lexical alternatives\begin{center}
+
+%\item  Out-of-context preference for each object towards a certain specificity level, called \textbf{entry-level} category.
+Typically, this correspond to a intermediate level of specificity, called \textbf{basic level} \cite{rosch1976basic}, but for less typical members of the class may be more specific \cite{jolicoeur1984pictures}.
+
+%\item Context: distractors, competing alternatives, pressure for unique reference.
+Overriding the out-of-context preference and may require the use of other levels of specificity e.g.
+\cite{murphy1989categorizing}.
+%In context, balancing a preference for low-cost, on one side, and informative, on the other, expressions: reduce cost while keeping interpretability (an ambiguous expression may be chosen if less costly (more frequent and short)) \cite{rohde2012communicating, graf2016animal}.
+In interaction: coherence and alignment.
+
+%\end{itemize}
 \subsection{Definition Sub-, basic-, super-level Categories}

### 2018-07-07 papers/SiVL2018/objectnaming.tex
adds references and newcommands
refines sec 2

--- 2018-07-02 papers/SiVL2018/objectnaming.tex
@@
-\cite{graf2016animal}
-\cite{Rosch1978}
-\subsection{Intro to Problem}
+%\cite{graf2016animal}
+%\cite{Rosch1978}
+%\subsection{Intro to Problem}
+The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'') and can be seen as a subtask of generating a referring expression.
+The lexical choice involved in naming is a non-trivial one \cite{brown1958shall}.
+Indeed, since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative: in fact, their denotation includes the target object.
+The study of object naming targets those factors that lead to the choice of a particular name in communicative situations.
+These include properties of the object and candidate names, as well as contextual requirements.
 
-\subsection{Definition Sub-, basic-, super-level Categories}
-\cite{graf2016animal} investigate object naming with respect to reference level.
+Lexical alternatives in naming differ in their \textbf{level of specificity} (e.g., \textit{dog} is less specific than \textit{beagle})\cite{cruse1977pragmatics}: the categories and concepts they denote can indeed be organized in a hierarchical fashion according to class inclusion relations (e.g., a beagle is a dog, a dog is an animal etc.)  \cite{murphy2004big}.
+Such categories can be seen as giving rise to a taxonomy, or ontology, where locating an object at a certain category (e.g., beagle) allows to inductively access all its superordinate ones (e.g., dog, mammal, animal etc.).
+It was observed that each type of object exhibits a preferred level of specificity which it is more naturally named with, called the \textbf{entry-level}.
+This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \textit{bird}, \textit{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \textit{animal}, \textit{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \textit{sparrow}, \textit{convertible}).
+However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}.
+
+Contextual factors also affect object naming.
+Scenarios where multiple objects are available induce a pressure for generating names which uniquely identify the target, thus excluding the competing alternatives (or \textit{distractors})\cite{olson1970language}.
+For example, in presence of more than one dog, the name \textit{dog} is ambiguous in terms of the specific one is intended to refer to.
+In these contexts, a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative, though possibly less default or more costly (e.g., infrequent, long etc.).
+It was shown that in use speakers tend to choose a name given a trade-off between its \textbf{cost}, on one side, and its contextual \textbf{ambiguity}, on the other; for example, they may opt for a less informative expression if less costly \cite{rohde2012communicating} \cite{graf2016animal}.
+Note that reasoning about the contextual informativeness of a name require categorization of all the potential referents, and not only the target object (e.g., to know that \textit{dog} is ambiguous in a context require having recognized that there are multiple dogs in the scene).
+Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or prominence \cite{clark1983common}.
+
+%\begin{itemize}
+%\item Naming (lexical choice of nominal reference) is not trivial: many names for an object \cite{brown1958shall}.
+If seen as the act of picking out an applicable level: each object simultaneously belong to multiple categories, which reflect different conceptualizations and may be more or less appropriate across contexts,
+
+% \cite{olson1970language}. Lexical alternatives: near-synonyms, hyponyms, hypernyms etc.\cite{edmonds2002near}
+
+%\item Typically, variation across levels of specificity \cite{cruse1977pragmatics} Concepts are organized in a hierarchical fashion according to class inclusion relations, giving rise to a taxonomy \cite{murphy2004big}.
+Note that if accessing the most specific category in such taxonomy we can inherit knowledge about all the other categories it is also part of, by backtracking the path up to the root in the ontology (inductive access to lexical alternatives\begin{center}
+
+%\item  Out-of-context preference for each object towards a certain specificity level, called \textbf{entry-level} category.
+Typically, this correspond to a intermediate level of specificity, called \textbf{basic level} \cite{rosch1976basic}, but for less typical members of the class may be more specific \cite{jolicoeur1984pictures}.
+
+%\item Context: distractors, competing alternatives, pressure for unique reference.
+Overriding the out-of-context preference and may require the use of other levels of specificity e.g.
+\cite{murphy1989categorizing}.
+%In context, balancing a preference for low-cost, on one side, and informative, on the other, expressions: reduce cost while keeping interpretability (an ambiguous expression may be chosen if less costly (more frequent and short)) \cite{rohde2012communicating, graf2016animal}.
+In interaction: coherence and alignment.
+%\end{itemize}
+%\subsection{Definition Sub-, basic-, super-level Categories}
+%\cite{graf2016animal} investigate object naming with respect to reference level.
 They distinguish and manually annotate 3 levels: (i) sub-level (\textit{dalmatian}), (ii) basic-level (\textit{dog}), (iii) super-level (\textit{animal}).

### 2018-07-07 papers/SiVL2018/objectnaming.tex
adds requirements with respect to factors (Section 2)

@@
 For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology.
+
+\paragraph{Requirements regarding the factors}
+%Given an image which depicts an object~$o^t$, the target object of the naming task, along with $k$~distractor objects~\mbox{$d^i, i\in{1,...,k}$} (the perceptual context of~$o_t$, understood as the real-world situation in which a unique name for~$o_t$ is to be produced).
+\cs{Note: I am aware of the inconsistency caused by "leaf category". Needs to be replaced later.}
+
+\begin{itemize}
+	\item[---] Visual-Linguistic Factors
+	\begin{itemize}
+		\item[R1] Contextual informativeness\\
+		To reason about the contextual informativeness, the  repertory of categories of which an object can be an instance is required. \\
+		%What are the lexical alternatives of a target object which \textit{uniquely} refer to it?\\
+		%For each pair of target object and distractor, we need to know whether they are from the same most specific category. (I.e.,~are they of the same sub, basic or super-level?)\\
+		%Example pizza: is there another calzone? Is there another pizza? Is there another kind of food?)\\
+		$\Rightarrow$ The repertory of categories for an object can be queried from an existing taxonomy, such as WordNet \cite{fellbaum1998wordnet}, by its most specific name (the \textsl{leaf category} in the taxonomy).
+		Hence, for \textit{each} object in the image, its leaf category is required.
+		\item[R2] The preferred name of an object\\
+		The entry-level/basic-level name.\\
+		$\Rightarrow$ ?
+	\end{itemize}
+	\item[---] Linguistic (lexical) Factors
+	\begin{itemize}
+		\item[R3] Lexical cost\\
+		$\Rightarrow$ Can be estimated, e.g.,~by the length of an expression. Needs to be estimated for all lexical alternatives, i.e.,~requires R1.
+	\end{itemize}
+	\item[---] Perceptual Factors
+	\begin{itemize}
+		\item[R4] Perceptual salience\\
+		This can be estimated geometrically on the basis of the relative position and size of an object in the image.\\
+		$\Rightarrow$ The coordinates (e.g.,~bounding box) of the image region which shows object~$o$. 
+	\end{itemize}
+\end{itemize}

### 2018-07-08 papers/SiVL2018/objectnaming.tex

--- 2018-07-07 papers/SiVL2018/objectnaming.tex
@@
 Indeed, since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative: in fact, their denotation includes the target object.
-The study of object naming targets those factors that lead to the choice of a particular name in communicative situations.
-These include properties of the object and candidate names, as well as contextual requirements.
+The study of object naming focuses on those factors that lead to the choice of a particular name in communicative situations.
+%These include properties of the object and candidate names, as well as contextual requirements.
 
-Lexical alternatives in naming differ in their \textbf{level of specificity} (e.g., \textit{dog} is less specific than \textit{beagle})\cite{cruse1977pragmatics}: the categories and concepts they denote can indeed be organized in a hierarchical fashion according to class inclusion relations (e.g., a beagle is a dog, a dog is an animal etc.)  \cite{murphy2004big}.
-Such categories can be seen as giving rise to a taxonomy, or ontology, where locating an object at a certain category (e.g., beagle) allows to inductively access all its superordinate ones (e.g., dog, mammal, animal etc.).
-It was observed that each type of object exhibits a preferred level of specificity which it is more naturally named with, called the \textbf{entry-level}.
+Lexical alternatives in naming differ in their \textbf{level of specificity} (e.g., \textit{dog} is less specific than \textit{beagle})\cite{cruse1977pragmatics}: the categories they denote can indeed be organized in a hierarchical fashion according to class inclusion relations (e.g., a beagle is a dog, a dog is an animal etc.) \cite{murphy2004big}.
+Such a conceptual structure gives rise to a taxonomy, or ontology.
+%where locating an object at a certain category (e.g., beagle) allows to inductively access all its superordinate ones (e.g., dog, mammal, animal etc.).
+It was observed that each type of object exhibits a preferred level of specificity which it is more naturally named at, called the \textbf{entry-level}.
 This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \textit{bird}, \textit{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \textit{animal}, \textit{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \textit{sparrow}, \textit{convertible}).
 However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}.
+This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}.
 
@@
 Scenarios where multiple objects are available induce a pressure for generating names which uniquely identify the target, thus excluding the competing alternatives (or \textit{distractors})\cite{olson1970language}.
-For example, in presence of more than one dog, the name \textit{dog} is ambiguous in terms of the specific one is intended to refer to.
-In these contexts, a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative, though possibly less default or more costly (e.g., infrequent, long etc.).
-It was shown that in use speakers tend to choose a name given a trade-off between its \textbf{cost}, on one side, and its contextual \textbf{ambiguity}, on the other; for example, they may opt for a less informative expression if less costly \cite{rohde2012communicating} \cite{graf2016animal}.
-Note that reasoning about the contextual informativeness of a name require categorization of all the potential referents, and not only the target object (e.g., to know that \textit{dog} is ambiguous in a context require having recognized that there are multiple dogs in the scene).
-Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or prominence \cite{clark1983common}.
+For example, in presence of more than one dog, the name \textit{dog} is ambiguous in terms of the specific one it is intended to refer to.
+In these cases, a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative: it provides more specific information, though it is possibly more costly to produce (it may be a non-default, infrequent or long alternative).
+It was shown that in use speakers tend to choose a name given a trade-off between its \textbf{cost}, on one side, and its contextual \textbf{informativeness}, on the other; for example, they may still opt for an ambiguous expression if less costly for them to produce it \cite{rohde2012communicating} \cite{graf2016animal}.
+%Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene).
+Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or location \cite{clark1983common}.
 
@@
 
-\section{Requirements: What Do We Need? \cs{[Subsection of \ref{sec:object_naming}?]}}
-For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology.
+%\section{Requirements: What Do We Need? \cs{[Subsection of \ref{sec:object_naming}?]}}
+%For large-scale studies of object naming, we need to be able to automatically define the level of specificity of a name, given an ontology. 
+%
+%\paragraph{Requirements regarding the factors}
+%%Given an image which depicts an object~$o^t$, the target object of the naming task, along with $k$~distractor objects~\mbox{$d^i, i\in{1,...,k}$} (the perceptual context of~$o_t$, understood as the real-world situation in which a unique name for~$o_t$ is to be produced).
+%\cs{Note: I am aware of the inconsistency caused by "leaf category". Needs to be replaced later.}
+
+\section{Requirements}
+In order to study object naming as prompted by real-world images, not only do we need to collect names naturally generated by speakers, but also to quantify those factors whose interaction with naming we want to analyze.
+As we saw, phenomena that impacts on object naming are both perceptual and linguistic in nature: since we here focus on perception as vision, we distinguish between those that pertain language, vision or both.
+
+\la{Note that I swapped the order of contextual informativeness and lexical availability. What does R1 refer to? the requirement of sub-level info?}
+\begin{itemize}
+	\item[---] \textbf{Visual-Linguistic factors}
+	\begin{itemize}
+		\item[R1] \textbf{Lexical availability}: \\
+		In object naming, there is a preference for each object type towards a certain level of specificity.
+To detect this, we need to have access to a taxonomy, reflecting  hierarchical relations among the various categories, and map both names and target objects to their location in such a structure.
+For instance, if we want to check whether a convertible is more often referred to with a basic-level category, e.g., \textit{car}, or a more specific one, e.g., \textit{convertible}, we need to know that \textit{car} lexicalizes a category which is super-ordinate to that lexicalized by \textit{convertible}.
+Moreover, in the first place, we need to know which categories our target object belongs to (e.g., convertible, a car, a vehicle etc.) and hence which names could apply to it.
+Note that for due to class inclusion relations, it is sufficient to know the most specific category in the taxonomy, i.e., the sub-level, to deduce all the other others (e.g., convertibles $\subset$ cars $\subset$ vehicles ...
+).
+
+		For this purpose, one can use existing lexical resources as a taxonomy: for example, in WordNet \cite{fellbaum1998wordnet} words denoting the same category are grouped and linked to others by taxonomic relations.
+The repertory of categories, and hence candidate names, for a target object can be queried by taking the sub-level category, i.e., the \textsl{leaf category} in the taxonomy.
+
+		\item[R2] \textbf{Contextual informativeness}: \\
+		The same object may be named differently depending on the distractors it is combined with: a particular name may not be sufficiently specific to identify its referent if applicable to more than one object.
+In order to analyze this, we are required to know the repertory of categories that each of the potential referents is an instance of: for instance, we need to know that there are multiple cars, to judge whether \textit{car} is ambiguous.
+As before, we also need to map names to a taxonomy, in order to check which level of specificity is chosen.
+We then require similar resources as in R1, but extending information about the sub-level category to each object in the scene.
+
+	\end{itemize}
+	\item[---] \textbf{Linguistic factors}:
+	\begin{itemize}
+		\item[R3] \textbf{Cost}: \\
+		The cost of generation of a nominal may impact on its likelihood to be chosen in naming.
+Previous work \cite{graf2016animal} operationalized such cost in terms of length and frequency.
+These can readily be coded as functions of respectively the number of characters and the relative frequency (estimated from a text corpus) of a name.
+\la{Actually, they also include typicality in the cost but I would leave it out as we kind of put that phenomenon more under the umbrella of lexical availability.
+And in general, I am not sure what to say about that, actually ...
+Do we want typicality ratings?} However, reasoning about the cost of lexical alternatives requires having access to such alternatives, hence names applicable to the object.
+As before, these can be obtained by mapping the object to the taxonomy and derive the set of categories it is a member of.
+	\end{itemize}
+	\item[---] \textbf{Visual factors}
+	\begin{itemize}
+		\item[R4] \textbf{Perceptual salience}: \\
+		The prominence of an object in a scene may affect naming.	This can be estimated geometrically on the basis of the relative position and size of an object in the image.
+	\end{itemize}
+\end{itemize}
+%
+To summarize, to carry out an analyses of object naming in real-world images datasets we require:
+\begin{itemize}
+	\item Names naturally generated by speakers to refer to a target object in an image
+	\item Sub-level category of each object in the image (including the target object)
+	\item Set of categories mapped to their lexical realizations and organized according to taxonomic relations (e.g., WordNet)
+	\item Coordinates of the image region showing the target object.
+\end{itemize}
+%\begin{itemize}
+%	\item[---] Visual-Linguistic Factors
+%	\begin{itemize}
+%		\item[R1] Contextual informativeness\\
+%		To reason about the contextual informativeness, the  repertory of categories of which an object can be an instance is required. \\
+%		%What are the lexical alternatives of a target object which \textit{uniquely} refer to it?\\
+%		%For each pair of target object and distractor, we need to know whether they are from the same most specific category. (I.e.,~are they of the same sub, basic or super-level?)\\
+%		%Example pizza: is there another calzone? Is there another pizza? Is there another kind of food?)\\
+%		$\Rightarrow$ The repertory of categories for an object can be queried from an existing taxonomy, such as WordNet \cite{fellbaum1998wordnet}, by its most specific name (the \textsl{leaf category} in the taxonomy).
+%		Hence, for \textit{each} object in the image, its leaf category is required.
+%		\item[R2] The preferred name of an object\\
+%		The entry-level/basic-level name.\\
+%		$\Rightarrow$ ?
+%	\end{itemize}
+%	\item[---] Linguistic (lexical) Factors
+%	\begin{itemize}
+%		\item[R3] Lexical cost\\
+%		$\Rightarrow$ Can be estimated, e.g.,~by the length of an expression. Needs to be estimated for all lexical alternatives, i.e.,~requires R1.
+%	\end{itemize}
+%	\item[---] Perceptual Factors
+%	\begin{itemize}
+%		\item[R4] Perceptual salience\\
+%		This can be estimated geometrically on the basis of the relative position and size of an object in the image.\\
+%		$\Rightarrow$ The coordinates (e.g.,~bounding box) of the image region which shows object~$o$. 
+%	\end{itemize}
+%\end{itemize}

### 2018-07-09 papers/SiVL2018/sivl_2018.tex
test slack integration
adds newcommands
adds requirements with respect to factors (Section 2)
adds section 3
some changes in intro

@@
 \newcommand{\cs}[1]{\textcolor{PineGreen}{\emph{//cs: #1//}}}
+\newcommand{\la}[1]{\textcolor{cyan}{\emph{//la: #1//}}}
+
+\newcommand{\vgenome}{VisualGenome }
+\newcommand{\referit}{ReferIt }
+\newcommand{\refcoco}{RefCOCO }
+\newcommand{\refcocop}{RefCOCO+ }
+\newcommand{\flickr}{Flickr30k Entities }
+
+\newcommand{\refexp}[1]{\textsl{#1}}
+\newcommand{\cat}[1]{\textsc{#1}}
+
+\usepackage{pifont}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}
 
@@
 
-\title{How do we get from object recognition\\ to object naming?} % Replace with your title
+\title{Do we need object naming beyond entry-level categories?} % Replace with your title
 
@@
 
+While traditional approaches to computer vision have often focussed on categorizing and classifying visual content according to predefined annotation schemes (for e.g.\ object categories, attributes or actions), research on language \& vision typically aims at predicting or generating natural verbal descriptions of visual objects and scenes depicted in images or videos.
+In recent years, there has been an explosion of interest in language \& vision tasks in the NLP community, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
+All of these tasks require models that capture linguistic and visual knowledge at the same time, i.e.
+determining which combinations of words are appropriate for a given visual scene and, potentially, in a given discourse context, cf.\ \cite{vries2017guesswhat}.
+Moroever, in contrast to rigid classification often used in computer vision, the target output in language \& vision is usually more flexible and varies in terms of a range of factors:  different speakers might have different preferences when describing an object, and the same speaker might prefer different descriptions depending on the task or context.
+%next to knowledge about visual categories, require , thecomplex verbal utterances need to be produced, and in some cases, these utterances not only need to describe visual content, but also need to be appropriate in a relatively complex .
+
+In this paper, we take a look at a straightforward task in language \& vision that so far has found surprisingly little attention in the community: object naming, i.e.
+determining the nominal that speakers will use to refer to an object in a visual scene.
+With state-of-the-art computer vision systems being able to classify images into thousands of different categories \cite{googlenet}, it might even seem like this task is already solved.
+However, theoretically, the lexical choice involved in naming is a non-trivial one \cite{brown1958shall}.
 Real-world objects are members of many categories and speakers can typically choose between different, more or less specific names when referring to a particular visual entity. 
 For instance, the entity surrounded by the green box in Figure \ref{fig:example} is an instance of the categories \textit{female child, child, female, person, organism}, etc.\  and can be referred to with names such as, e.g.,\ \textit{girl, kid, cutie, daughter, person, human}.
-But even though almost every task in language \& vision involves the prediction of object names (e.g.
-image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word/linguistic concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
+Most research on computer vision and object recognition has somehow worked around the fact that objects can be instances of multiple, hierarchically embedded categories. 
+State-of-the-art recognition models are mostly trained as classifiers on a flat of 1000 categories in ImageNet, reducing the ImageNet ontology to an inherently flat annotation scheme.
+
+%But even though almost every task in language \& vision involves the prediction of object names (e.g.
+image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word or concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
 Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
-Recently, however, \cite{graf2016animal} have shown that object naming preferences are subject to contextual constraints and pragmatic factors: in a typical reference game set-up with images of target objects surrounded by distractor objects,\cs{of target objects, each  presented along with images of distractor objects} speakers have been found to flexibly adjust object names depending on the context.
+Recently, however, \cite{graf2016animal} have shown that object naming preferences \textit{are} subject to pragmatic factors: in a typical reference game set-up with images of target objects, each  presented along with images of distractor objects, speakers have been found to flexibly adjust object names depending on the context.
 For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
@@
 
-Most research on computer vision and object recognition has somehow worked around the fact that objects can be instances of multiple, hierarchically embedded categories. 
-State-of-the-art recognition models are mostly trained as classifiers on a flat of 1000 categories in ImageNet, reducing the ImageNet ontology to an inherently flat annotation scheme and treating
-object labels as mutually exclusive.
-
-On the vision side, however, there is a huge body of research on object recognition, i.e.\ labeling visual objects according to a set of categories, cf.\ \cite{simonyan2014very,deng2014large,googlenet}.
+The goal of this paper is to provide a systematic discussion of the object naming task and to show that existing, large-scale resources do not meet the requirements for a theoretically informed model of this very basic phenomenon in language \& vision.
 
@@
 
+yes, will try ...
+
 \clearpage

### 2018-07-09 papers/SiVL2018/objectnaming.tex
some changes in section 2

@@
 %\subsection{Intro to Problem}
+
+\subsection{Background}
+
 The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'') and can be seen as a subtask of generating a referring expression.
@@
 %\cs{Note: I am aware of the inconsistency caused by "leaf category". Needs to be replaced later.}
+
+\subsection{Previous Work}
+
+As mentioned above, there is hardly any work on language \& vision that has studied object naming explicitily, on large-scale data sets. 
+\cite{Ordonez:2016} investigate the problem of deriving appropriate object names, or so-called entry-level
+ categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via various translation procedures. 
+ Their performance is surprisingly low: around 35\% precision. We need to discuss this paper in more detail.
 

### 2018-07-09 papers/SiVL2018/objectnaming.tex
adds label

--- 2018-07-08 papers/SiVL2018/objectnaming.tex
@@
 \section{Requirements}
+\label{sec:requirements}
 In order to study object naming as prompted by real-world images, not only do we need to collect names naturally generated by speakers, but also to quantify those factors whose interaction with naming we want to analyze.

### 2018-07-09 papers/SiVL2018/resources.tex
adds resource discussion

@@
 \begin{table*}[t]
-	\begin{tabular}{|l|l|llll|}
+	\begin{tabular}{|l||l|c|c|c|c|}
 		\hline
-		Resource & Purpose & \multicolumn{4}{c|}{Useful For}\\
-				& 			& Basic-level Names & Specificity & Bla & Bli \\
+		Resource
+		& Purpose 	& \#Cat 	
+		& \multicolumn{2}{c|}{Constraints on} 
+		& WordNet  \\
+			&			
+		& 			
+		& language 	& images 
+		& IDs?\\
 		\hline \hline
-		RefCOCO & XXX & 
+		\refcoco 	& REG,REC& 80 		& -				
+					& $\geq$2 objects of same cat 
+					& \xmark \\
+		\refcocop 	& REG,REC
+					& 80		& + 			
+					& $\geq$2 objects of same cat 
+					& \xmark \\	
+		\flickr 	& Phrase localization
+					& ?				& -- 
+					& & \xmark \\
+					& Caption generation
+					& & & &  \\
+		\vgenome 	& Scene understanding 
+					& 80k 
+					& & & \cmark\\
+					& Phrase localization
+					& & & &  \\
+		\hline
 	\end{tabular}
-	\caption{\label{tab:summary_resources} Intended to provide an overview of resources, their purpose/use and shortcomings wrt object naming}
+	\caption{\label{tab:summary_resources} Intended to provide an overview of resources, their purpose/use and shortcomings wrt object naming.
+Cat: Categories; REG and REC: Referring expression generation and comprehension, respectively.}
 \end{table*}
 
-\subsection{Computer Vision Resources}
-\paragraph{Methods: Object Detectors, Image Classifiers}
+\begin{table*}[t]
+	\begin{center}
+	\begin{tabular}{|l|c|c|c|c|}
+		\hline
+		Resource & \multicolumn{3}{c|}{Provides (more or less directly)}\\
+		 		 & R1: Root-level & R2: Entry-level & R4: Coordinates  \\
+		\hline \hline
+		\refcoco 	& \xmark & \xmark & \cmark \\
+		\refcocop 	& \xmark & \xmark & \cmark \\
+		\flickr 	& \xmark & (\cmark) & \cmark \\
+		\vgenome 	& \xmark & \cmark 	& \cmark \\
+		\hline 		
+	\end{tabular}
+	\caption{\label{tab:summary_resources} BLABLA overview of resources and their shortcomings wrt object naming. REG and REC: Referring expression generation and comprehension, respectively.}
+	\end{center}
+\end{table*}
+
+\subsection{Linguistic Resources, Computer Vision Resources}
+\paragraph{WordNet}
+WordNet \cite{fellbaum1998wordnet} blabla.
+
+\paragraph{Methods: Object Detectors, Image Classifiers} \cs{Do we need that? I would say no.}
 
 \paragraph{ImageNet and ILSVRC}
-\paragraph{MSCOCO} \cite{mscoco}
 
+\paragraph{MS COCO} \cite{mscoco}
+MS COCO is an object recognition dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
+Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
+The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
+However, the COCO region-level (object) annotations are not linked to the captions.
 \subsection{V\ \&\ L Resources}
-\paragraph{VisualGenome}
-\paragraph{(ReferIt) RefCOCO and alike}
-Based on MSCOCO; Other MSCOCO-based resources: Captions; Visual Genome in parts\\
+
+\paragraph{\refcoco and \refcocop}~\\\cs{REF} 
+Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}.
+
+The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
+Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
+The matcher must click on the object he thinks the RE refers to. 
+If the matcher's prediction is correct, the RE is considered valid. 
+For more details on the datasets see \cite{Yu2016}.
+
+Finally, \referit is based on the SAIAPR image collection \cite{Grubinger2006} (20k images;99.5k image regions;120K REs), and captures not only REs for objects ("things") but also for scene categories (e.g.,{\refexp{grass, road}) (see also \cite{hu2015,mao2016generation}).
+The task of scene detection is beyond the focus of our study regarding object naming, we therefore will not discuss this dataset further.
+
+\paragraph{Flickr30k Entities}~\\
+The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
+Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
+The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}). 
+% 276k~manually annotated bounding boxes (i.e.,~entities are grounded in the image).
+%
+%
+% augments the 158k captions from Flickr30k with 244k coreference chains, linking mentions of the same entities across different captions for the same image, and associating them with 276k manually annotated bounding boxes.
+Such annotations are essential for continued progress in automatic image description and grounded language understanding.
+They enable us to define a new benchmark for localization of textual entity mentions in an image.
+
+\paragraph{VisualGenome}~\\
+VisualGenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
+
+\iffalse 
+5.4 Million Region Descriptions
+1.7 Million Visual Question Answers
+3.8 Million Object Instances
+2.8 Million Attributes
+2.3 Million Relationships
+Everything Mapped to Wordnet Synsets
+\fi
+
+\subsection{Discussion of Shortcomings}
+We discuss the shortcomings of the presented V\&L datasets with respect to their use for computational linguistic studies of reference in general, and in particular in how far they satisfy the requirements for the study of object naming which we put forward in  Section~\ref{sec:requirements}.
+
+\paragraph{\refcoco and \refcocop}
+The REs for both, \refcoco and \refcocop, were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
+\cs{Maybe people tended more to use REs expressing the function of the object?}
+%
+While these constraints ensured that the datasets are interesting from the computer vision perspective, they fall short in containing phenomena that are intriguing from the view of language research: 
+%
+The range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the experimental data in order to study the interaction of their underlying factors.
+This is not given in \refcoco(+) with respect to the study of reference. 
+First, how the choice of a RE for an object interacts with the categories of its distractors can only partially be observed in the data\footnote{For example, the preference of the entry-level category over a sufficiently unique more generic category can only be observed in images in which the target and the distractor objects are of different more generic categories.} due to~(i).
+And second, the study of how people \textit{naturally} refer to objects requires that speakers are not constraint in their choice of REs, which (ii)~does not fulfill.
+
+Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
+
+%(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose a basic-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).
+
+% the cost of a name and the contextual ambiguity it creates (see Section~\ref{sec:object_naming}), 
+% entry-level category
+
+With respect to the problem of object naming, \refcoco(+) does not fulfill requirement~R1. 
+As explained in Section~\ref{sec:requirements}, we can retrieve less specific categories from a taxonomy, but the most specific category of \textit{each} object depicted in an image needs to be provided by the data.
+This is not the case due to property~(iii), as well as due to the fact that the $80$~COCO categories tend to be entry-level categories. \cs{TODO: EX / ANALYSIS}
+%
+%However, the leaf category cannot be retrieved, disallowing us to determine whether target and distractors are of the same most specific category.
+
+The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the basic-level from the data \cs{TODO: Example or remove last part}.
+
+\paragraph{Solution to R2: Captions?}
+Additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
+Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+%
+In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
+such that natural language phrases first needed to be aligned with the image regions they refer to. 
+This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
+% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
+
+\paragraph{Solution to R1: Object detectors?}
+An alternative would be to apply object detectors trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained object detectors only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
+For the training of detectors using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.
+
+\paragraph{\flickr}
+By design, \flickr can be used to study the way people refer to individual entities in an image in dependence on the situation the speakers describe. 
+In contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
+We can therefore gather naturally produced object names from the data and may be able to infer their entry-level categories. 
+This is only the case for objects which are mentioned in the captions though, which is why \flickr does not fully satisfy requirement~R2.
+
+\flickr does not meet requirement R1 for similar reasons as \refcoco(+). 
+Object categories tend to be even less specific than those of COCO, they include, e.g.,~\cs{TODO; people...}.
+
+Note that \flickr is less suited for referring expression generation and interpretation\cs{use the term grounding, interpretation or understanding to refer to the process of linking language to an image region?}, though, in that the mentions in isolation of their linguistic context may not uniquely identify the referred object.
+
+\paragraph{Visual Genome}
+From a linguistic perspective, object categories (e.g.,~\cat{fawn}, \cat{industrial park}, \cat{opened bag}, \cat{carpet oriental}) are defined pragmatically, and the annotations are rather unstructured.
+For example, as illustrated in Figure~\ref{fig:ex_visualgenome}, the categorization of expressions into one of the three annotation types (region, attributes and relationships), is based on the verbs (\word{is} denotes attributes) and prepositions (\word{at} or \word{in} denotes relationships) \cs{double-check w/ paper}
+Note also the spelling mistakes (e.g.,~\word{dalmation}, \word{wating}). 
+Furthermore, regions and their annotations are highly redundant in that expressions referring to the same object may still be linked to different bounding boxes\cs{We would need to, e.g., merge boxes through IoU $\geq$ some threshold}.
+
+As far as object naming is concerned, requirement R1 is not met.    
+The annotators were free in their choice of a name for the objects, hence, the latter is usually the entry-level in many annotations. 
+For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, Visual Genome satisfies R2---we can infer the entry-level name of each object in the image.
+For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
+\\
+
+\begin{figure}[t]
+	\begin{center}
+	\begin{minipage}{.37\textwidth}
+		\includegraphics[scale=.25]{fig/visual_genome_dogs.png}
+	\end{minipage}
+	\begin{minipage}{.6\textwidth}
+		\begin{tabular}{l|l}
+			\hline
+			Annotation	& \\	
+			types		& 	\\
+			\hline \hline
+			Regions &  dalmatian's head; dalmatian dog\\
+					& wating at a dinner table; the dog is gray\\
+			Attributes & dog is gray; dalmation is eating\\
+			Relationships & dog at table; dalmation IN chair; \\
+							& heeler eating treat \\
+							\hline
+		\end{tabular}
+	\end{minipage}
+	\caption{Example of Visual Genome. \label{fig:ex_visualgenome}}
+	\end{center}
+\end{figure}
+
+\noindent
+Finally, requirement~R4 is met by all discussed datasets.
+
+\cs{XXXXX}\\\\
+\subsubsection{Analysis}
 
@@
 See \cite{Yu2016} for more details.
-
-\paragraph{Flickr30k Entities}
 

### 2018-07-09 papers/SiVL2018/resources.tex
adds resource discussion

@@
 \begin{table*}[t]
-	\begin{tabular}{|l||l|c|c|c|c|}
+	\begin{tabular}{|l||l|c|c|c|c|c|c|}
 		\hline
 		Resource
-		& Purpose 	& \#Cat 	
+		& Purpose 	& \#Cat & \#Ref/ & \#Refs
 		& \multicolumn{2}{c|}{Constraints on} 
 		& WordNet  \\
-			&			
+		& & & object			
 		& 			
@@
 		\hline \hline
-		\refcoco 	& REG,REC& 80 		& -				
-					& $\geq$2 objects of same cat 
+		\refcoco 	& REG,REC
+					& 80 & 3 & 50k
+					& -				
+					& $\geq$2 objs  
 					& \xmark \\
+					&
+					& & & 
+					& 
+					& of same cat
+					& \\
 		\refcocop 	& REG,REC
-					& 80		& + 			
-					& $\geq$2 objects of same cat 
+					& 80 & 3 & 50k
+					& + 			
+					& $\geq$2 objs  
 					& \xmark \\	
+					&
+					& & & 
+					& 
+					& of same cat
+					& \\
 		\flickr 	& Phrase localization
-					& ?				& -- 
+					& ?	& & 
+					& -- 
 					& & \xmark \\
@@
 		\vgenome 	& Scene understanding 
-					& 80k 
+					& 80k & & 
 					& & & \cmark\\
@@
 	\end{tabular}
-	\caption{\label{tab:summary_resources} Intended to provide an overview of resources, their purpose/use and shortcomings wrt object naming.
-Cat: Categories; REG and REC: Referring expression generation and comprehension, respectively.}
+	\caption{\label{tab:summary_resources} Overview of V\&L benchmarks for taks related to reference.
+Cat: Categories; Ref: Reference; REG and REC: Referring expression generation and comprehension, respectively.}
 \end{table*}
@@
 
-\paragraph{\refcoco and \refcocop}~\\\cs{REF} 
+\paragraph{\refcoco and \refcocop \cite{Yu2016}}~\\ 
 Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco}.
@@
 
-\paragraph{VisualGenome}~\\
-VisualGenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+\paragraph{\vgenome}~\\
+\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
 It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
@@
 \paragraph{Solution to R1: Object detectors?}
-An alternative would be to apply object detectors trained to predict the most specific category of the full inventory of objects which the dataset covers. 
-However, pre-trained object detectors only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
-For the training of detectors using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.
+An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.
 
@@
 We can therefore gather naturally produced object names from the data and may be able to infer their entry-level categories. 
-This is only the case for objects which are mentioned in the captions though, which is why \flickr does not fully satisfy requirement~R2.
+%
+This is only the case for objects which are mentioned in the captions, which is why \flickr does not fully satisfy requirement~R2 \cs{ADD EXAMPLE IMAGE}.
 
 \flickr does not meet requirement R1 for similar reasons as \refcoco(+). 
-Object categories tend to be even less specific than those of COCO, they include, e.g.,~\cs{TODO; people...}.
+Object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene}).
 
 Note that \flickr is less suited for referring expression generation and interpretation\cs{use the term grounding, interpretation or understanding to refer to the process of linking language to an image region?}, though, in that the mentions in isolation of their linguistic context may not uniquely identify the referred object.
+For example, the two men shown in the image in Figure~\ref{fig:ex_flickr} are  referred to by \refexp{a man} or \refexp{a guy}.
 
-\paragraph{Visual Genome}
+\begin{figure}[t]
+	\begin{center}
+		\begin{minipage}{.32\textwidth}
+			\includegraphics[width=4cm]{fig/flickr_1000523639_boxes.jpg}
+		\end{minipage}
+		\begin{minipage}{.67\textwidth}	
+				{
+			\begin{tabular}{l}
+				\hline
+				\green{[EN$_{39}$ Two people]} in {[EN$_{45}$ the photo]} are playing\\
+				\; \red{[EN$_{40}$ the guitar]} and {[EN$_{41}$ the other]} is poking at {[EN$_{0}$ him]} .\\
+
+			\blue{[EN$_{42}$ A man]} in \yellow{[EN$_{43}$ green]} holds \red{[EN$_{40}$ a guitar]} while \\
+			\;{[EN$_{41}$ the other man]} observes \yellow{[EN$_{43}$ his shirt]} .\\
+
+		{[EN$_{41}$ A man]} is fixing \yellow{[EN$_{43}$ the guitar players costume]} .\\
+
+	{[EN$_{41}$ a guy]} stitching up \yellow{[EN$_{43}$ another man 's coat]} .\\
+
+	\green{[EN$_{39}$ the two boys]} playing \red{[EN$_{40}$ guitar]} \\
+	\hline
+			\end{tabular}
+			}
+		\end{minipage}
+
+		\caption{Example of \flickr. \label{fig:ex_flickr}}
+	\end{center}
+\end{figure}
+
+\paragraph{\vgenome}
 From a linguistic perspective, object categories (e.g.,~\cat{fawn}, \cat{industrial park}, \cat{opened bag}, \cat{carpet oriental}) are defined pragmatically, and the annotations are rather unstructured.
@@
 The annotators were free in their choice of a name for the objects, hence, the latter is usually the entry-level in many annotations. 
-For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, Visual Genome satisfies R2---we can infer the entry-level name of each object in the image.
+For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, \vgenome satisfies R2---we can infer the entry-level name of each object in the image. 
 For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
@@
 	\begin{center}
-	\begin{minipage}{.37\textwidth}
-		\includegraphics[scale=.25]{fig/visual_genome_dogs.png}
+	\begin{minipage}{.33\textwidth}
+		\includegraphics[width=4cm]{fig/visual_genome_dogs.png}
 	\end{minipage}
-	\begin{minipage}{.6\textwidth}
+	\begin{minipage}{.65\textwidth}
 		\begin{tabular}{l|l}
@@
 	\end{minipage}
-	\caption{Example of Visual Genome. \label{fig:ex_visualgenome}}
+	\caption{Example of \vgenome. \label{fig:ex_visualgenome}}
 	\end{center}
@@
 \cs{XXXXX}\\\\
-\subsubsection{Analysis}
-
-We analyze the RefCOCO and RefCOCO+ datasets which contain referring expressions to objects in MSCOCO \cite{mscoco} images.
-These data collections were performed via crowdsourcing with the ReferIt Game \cite{Kazemzadeh2014}  where two players were paired and a director needed to refer to a predetermined object to a matcher, who then selected it.
-RefCOCO and RefCOCO+ contain 3 referring expressions on average per object, and overall 150K expressions for 50K objects. 
-The two datasets have been collected for an (almost) identical set of objects, but in RefCOCO+, players were asked not to use location words (\textit{on the left}, etc.).
-See \cite{Yu2016} for more details.
-
-\subsection{\cs{Language Resources? (WordNet)}}
 
 \subsection{Analysis of Data wrt Our Requirements(?)}
+
+\begin{table}[t]
+	\begin{tabular}{lccc}
+		\hline
+		Resource & \multicolumn{3}{c}{No. categories $cat$ for which $*(cat, \text{ILSVRC})$:} \\
+				& $\in$
+				& superset
+				& $\supset$\\
+		\hline \hline
+		\refcoco & 15 \\
+		\refcocop & \\
+		\flickr & \\
+		\vgenome & \\
+		\hline
+	\end{tabular}
+	\caption{Coverage of the categories by the $1,000$~synsets of the ILSVRC image classification challenge.  \label{tab:coverage_ilsvrc}}
+\end{table}
 

### 2018-07-09 papers/SiVL2018/proposal.tex

 vision people have focussed on learning very specific categories, and have not cared about learning actual concepts/names,

 language \& vision people have focussed on learning what speakers say in certain data sets, 
 we know that speakers will use object names at a medium level of specificity most of the time, 
 so it is difficult to learn the meaning of specific concepts from existing resources and to implement a model that can decide which level in the taxonomy is appropriate in context --- 
 we need a more systematic approach for collecting object naming data, 
 controlling the level of specificity (e.g. prompting speakers to come up with the most specific word they can think of)... this data might also give us insight into what basic-level and sub-level concepts are ..

### 2018-07-09 papers/SiVL2018/sivl_2018.tex
defines new commands
intermediate commit

@@
 
-\title{Do we need object naming beyond entry-level categories?} % Replace with your title
+\title{Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title
 
@@
 
-While traditional approaches to computer vision have often focussed on categorizing and classifying visual content according to predefined annotation schemes (for e.g.\ object categories, attributes or actions), research on language \& vision typically aims at predicting or generating natural verbal descriptions of visual objects and scenes depicted in images or videos.
-In recent years, there has been an explosion of interest in language \& vision tasks in the NLP community, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
-All of these tasks require models that capture linguistic and visual knowledge at the same time, i.e.
-determining which combinations of words are appropriate for a given visual scene and, potentially, in a given discourse context, cf.\ \cite{vries2017guesswhat}.
-Moroever, in contrast to rigid classification often used in computer vision, the target output in language \& vision is usually more flexible and varies in terms of a range of factors:  different speakers might have different preferences when describing an object, and the same speaker might prefer different descriptions depending on the task or context.
-%next to knowledge about visual categories, require , thecomplex verbal utterances need to be produced, and in some cases, these utterances not only need to describe visual content, but also need to be appropriate in a relatively complex .
+Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
+But, for a long time, computational research into language grounding, reference and situated interaction had to rely on ``block-worlds'' or very controlled, experimental environments \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref}, leading to models and corresponding findings at a rather restricted scale.
+This situation has radically changed with recent developments in the language \& vision community. 
+Pushed especially by developments in computer vision, there has been an explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
+
+Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems for very specific tasks and data sets.
 
@@
 image captioning, referring expression generation, visual dialogue), hardly any research has explicitly looked at object naming, i.e.\ determining the actual word or concept that speakers would use to refer to an object (in a particular context), but see \cite{Ordonez:2016,zarriess-schlangen:2017}.
-Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
-Recently, however, \cite{graf2016animal} have shown that object naming preferences \textit{are} subject to pragmatic factors: in a typical reference game set-up with images of target objects, each  presented along with images of distractor objects, speakers have been found to flexibly adjust object names depending on the context.
+%Even research in pragmatics, that traditionally deals with reference and referring expression production, has mostly focused on attributes, rather than object names.
+%Recently, however, \cite{graf2016animal} have shown that object naming preferences \textit{are} subject to pragmatic factors: in a typical reference game set-up with images of target objects, each  presented along with images of distractor objects, speakers have been found to flexibly adjust object names depending on the context.
 For instance, a \textit{dalmatian} would be called \textit{dalmatian} in the context of other dogs or simply \textit{dog} when none of the distractors is also a dog.
-This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.
+%This extends previous traditional work on concepts suggesting that the typicality of a referent determines its entry-level category (and consequently, its name) \cite{Rosch1978}.
 

### 2018-07-10 papers/SiVL2018/sivl_2018_6pages.tex
file for shortened version

% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{booktabs}
\usepackage[usenames, dvipsnames]{color}
\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\cs}[1]{\textcolor{PineGreen}{\emph{//cs: #1//}}}
\newcommand{\la}[1]{\textcolor{cyan}{\emph{//la: #1//}}}

\newcommand{\vgenome}{VisualGenome }
\newcommand{\referit}{ReferIt }
\newcommand{\refcoco}{RefCOCO }
\newcommand{\refcocop}{RefCOCO+ }
\newcommand{\flickr}{Flickr30k Entities }

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}

\newcommand{\green}[1]{\textcolor{PineGreen}{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\yellow}[1]{\textcolor{yellow}{#1}}

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV18SubNumber{***}  % Insert your submission number here

\title{Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title

\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}

\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}

\author{Anonymous ECCV submission}
\institute{Paper ID \ECCV18SubNumber}

\maketitle

\begin{abstract}
The abstract should summarize the contents of the paper. LNCS guidelines
indicate it should be at least 70 and at most 150 words. It should be set in 9-point
font size and should be inset 1.0~cm from the right and left margins.
\dots
\keywords{We would like to encourage you to list your keywords within
the abstract section}
\end{abstract}

\section{Introduction}

Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks -- they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf. \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.  
In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
However, so far, studies that have tested linguistic hypotheses on large-scale vision \& language resources have been relatively rare.

In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every language \& vision task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
Our starting point is a particular linguistic hypothesis related to object naming - namely that the choice of a name for an object is dependent on other objects in its visual context - which has been tested recently in a classical experimental setting \cite{graf2016animal}. 
We discuss how this hypothesis could be tested based on recent data sets that pair images and object descriptions, referring expressions or captions (all containing object names) and define a set of requirements for obtaining a theoretically informed model for object naming.
In sum, this discussion will show that specific requirements are met by particular resources, but none of the available corpora consistently satisfies all of the requirements.
We believe that this is a perfect showcase illustrating the challenges for linguistically motivated research in language and vision, and we derive a proposal for obtaining more consistently designed and annotated data collections for object naming.

\section{Naming Objects (in Context)}
\label{sec:object_naming}

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'').
Since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}. 
Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \textit{bird}, \textit{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \textit{animal}, \textit{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \textit{sparrow}, \textit{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}. This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}.

While the traditional notion of entry-level categories suggests that objects tend to be named by a \textit{single} preferred concept, research on pragmatics has found that speakers are flexible with respect to the chose level of specificity.
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating} \cite{graf2016animal}. For example, in presence of more than one dog, the name \textit{dog} is ambiguous and a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost (which is typically approximated by frequency) or saliency also come into play \cite{graf2016animal}  \cite{clark1983common}.
%Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene). 
%Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or location \cite{clark1983common}.

So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
 State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet (REF!!), though see work by Deng et al. on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
 concepts, adopting the traditional view that there is a single preferred name for a given object.
 Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.

\section{Requirements}
\label{sec:requirements}

\begin{figure}[t]
	\begin{center}
		\begin{minipage}{.52\textwidth}
			\includegraphics[width=\linewidth]{fig/graffig.pdf}
		\end{minipage}
		\begin{minipage}{.42\textwidth}
			\includegraphics[width=5cm]{fig/visual_genome_dogs.png}
		\end{minipage}
	\end{center}
	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
	\label{fig:graf_genome}
\end{figure}

In this Section we discuss requirements for scaling experimental studies on object names as in \cite{graf2016animal} to real-world images.
The difference between these two approaches is illustrated in Figure \ref{fig:graf_genome}, showing  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context.
Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, but we aim for studying object naming as prompted by real-world images. Therefore, we not only need access to names naturally generated by speakers, but also, we need to be able to quantify those factors whose interaction with naming we want to analyze.

Given a natural scene with multiple objects and a target object that a speaker referred to, we need to be able to answer the following questions:

\begin{itemize}
                 \item[R0] \textbf{Lexical choice}: \\
                 Which name did the speaker use to refer to the target object?
		\item[R1] \textbf{Lexical availability}: \\
		Which names are available for the target objects?  For instance, if we want to check whether a convertible is more often referred to with a basic-level category (\textit{car}) or a more specific one (\textit{convertible}) we need to know that a given object is a \textit{convertible}, and that \textit{convertible} is a sub-level concept of \textit{car} (and vehicle, etc.). Additionally, in \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). Thus, ideally, names would be grouped according to their taxonomic relations.
		\item[R2] \textbf{Contextual informativeness}: \\
		Which names are available for the other objects in the scene (i.e. distractors)?
		For instance, when the target is a convertible, we need to know that there are multiple convertible, cars, etc. to judge whether these concepts are ambiguous.

\end{itemize}

\section{Resources: What Do We Have?}
%\label{sec:resources}
%\textbf{TODO@Carina}\\
%\input{resources}

\section{Proposal}
%\label{sec:future_proposal}
%\textbf{TODO@Sina (?)}\\
%\input{proposal}

%yes, will try ...

\clearpage
\bibliographystyle{splncs}
\bibliography{naming}
\end{document}

### 2018-07-12 papers/SiVL2018/resources.tex
Adds practical requirements for datasets

@@
 
-%(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose a basic-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).
+%(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose the entry-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).
 
@@
 
-The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the basic-level from the data \cs{TODO: Example or remove last part}.
+The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the entry-level from the data \cs{TODO: Example or remove last part}.
 
@@
 \begin{table}[t]
-	\begin{tabular}{lccc}
+	\begin{tabular}{lrrrr}
 		\hline
-		Resource & \multicolumn{3}{c}{No. categories $cat$ for which $*(cat, \text{ILSVRC})$:} \\
-				& $\in$
-				& superset
-				& $\supset$\\
+			 			& \refcoco & \refcocop & \flickr & \vgenome \\
 		\hline \hline
-		\refcoco & 15 \\
-		\refcocop & \\
-		\flickr & \\
+		total \#synsets	&	2580\\
+		- match			&	112 \\
+		- hyponyms		&	36 \\
+		- hypernyms 	&	204 \\
+		\hline
+		%- not found		&	74 \\	
+		%\hline
+		\# 
+				& \multicolumn{3}{c}{No. object names $obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$:} \\
+				& (obj)
+				& in
+				& hypernym
+				& hyponym\\
+		\hline \hline
+		 	& 2580 & 112 & 204 & 36\\
+		 	& 15 & 30 & 1 \cs{??}\\
+		 	& \\
 		\vgenome 	& \\
@@
 	\end{tabular}
-	\caption{Coverage of the categories by the $1,000$~synsets of the ILSVRC image classification challenge.  \label{tab:coverage_ilsvrc}}
+	\caption{Coverage of the object names in the datasets by WordNet and by the $1,000$~synsets of the ILSVRC image classification challenge.
+\#synsets(obj): number of object names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
 \end{table}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

@@
 \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\usepackage{hyperref}
+
+\usepackage{xspace}
 
@@
 
-\newcommand{\vgenome}{VisualGenome }
-\newcommand{\referit}{ReferIt }
-\newcommand{\refcoco}{RefCOCO }
-\newcommand{\refcocop}{RefCOCO+ }
-\newcommand{\flickr}{Flickr30k Entities }
+\newcommand{\vgenome}{VisualGenome\xspace}
+\newcommand{\referit}{ReferIt\xspace}
+\newcommand{\refcoco}{RefCOCO\xspace}
+\newcommand{\refcocop}{RefCOCO+\xspace}
+\newcommand{\flickr}{Flickr30k Entities\xspace}
 
@@
 \end{abstract}
+
+@Carina TODO:
+\begin{itemize}
+	\item requirements: \\ 
+	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
+	add unconstraint object co-occurrences / unbiased as far as possible; \\
+	rename R1? (lexical alternatives? candidate names?)
+	\item title?
+\end{itemize}
 
@@
 \begin{itemize}
-                 \item[R0] \textbf{Lexical choice}: \\
+        \item[(1)] \textbf{Lexical choice}: \\
         Which name did the speaker use to refer to the target object?
-		\item[R1] \textbf{Lexical availability}: \\
+		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
+		%Which names are available for the target objects?  
 		Which names are available for the target objects? 
-For instance, if we want to check whether a convertible is more often referred to with a basic-level category (\textit{car}) or a more specific one (\textit{convertible}) we need to know that a given object is a \textit{convertible}, and that \textit{convertible} is a sub-level concept of \textit{car} (and vehicle, etc.).
-Additionally, in \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level).
-Thus, ideally, names would be grouped according to their taxonomic relations.
-		\item[R2] \textbf{Contextual informativeness}: \\
+		And how are they taxonomically related? 
+		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.).
+		%Additionally, in
+		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
+		Thus, ideally, %names 
+		lexical candidates 
+		would be grouped according to their taxonomic relations. 
+		\item[(3)] \textbf{Contextual informativeness}: \\
 		Which names are available for the other objects in the scene (i.e. distractors)?
-		For instance, when the target is a convertible, we need to know that there are multiple convertible, cars, etc. to judge whether these concepts are ambiguous.
-
+		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
 \end{itemize}
 
+In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
+A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
+Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.
+
+With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors.
+Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors.
+We summarize this requirement by the term \textbf{R3: unconstraint}. 
+Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
 \section{Resources: What Do We Have?}
-%\label{sec:resources}
-%\textbf{TODO@Carina}\\
-%\input{resources}
+\label{sec:resources}
+\input{resources}
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

@@
 
+\cs{Should the following be here or at the beginning of Sect. 4?}
+\cs{We could also call below requirements "Desiderata"}
 In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
@@
 Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
+
 \section{Resources: What Do We Have?}

### 2018-07-12 papers/SiVL2018/sivl_2018.tex
intermediate commit

@@
 \newcommand{\refexp}[1]{\textsl{#1}}
+\newcommand{\word}[1]{\textsl{#1}}
 \newcommand{\cat}[1]{\textsc{#1}}
+
+\newcommand{\green}[1]{\textcolor{PineGreen}{#1}}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand{\yellow}[1]{\textcolor{yellow}{#1}}
 
@@
 
-Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems for very specific tasks and data sets.
+Despite this dramatic progress in the field, however, a lot of research in language \& vision still centers around systems and applications for very specific tasks and data sets.
+Most of the influential papers have investigated which modeling architectures need to be adopted to re-generate human descriptions or utterances in a particular data set, whereas studies aimed at obtaining linguistic generalizations from existing data collections and models are relatively rare.
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

@@
         Which name did the speaker use to refer to the target object?
-		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
+		\item[(2)] \textbf{Lexical candidates}: \\
 		%Which names are available for the target objects?  
-		Which names are available for the target objects? 
+		Which names are applicable to the target objects? 
 		And how are they taxonomically related? 
@@
 		\item[(3)] \textbf{Contextual informativeness}: \\
-		Which names are available for the other objects in the scene (i.e. distractors)?
-		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
+		Which names are applicable for the other objects in the scene (i.e. distractors)?
+		For instance, when the target is a \cat{convertible}, we need to know if there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
+		%We are required to have this information in order to judge whether a certain name would be informative in a certain context, i.e., whether it would apply uniquely to the target object.
 \end{itemize}
@@
 Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
+Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
+For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
Adds practical requirements for datasets

@@
 Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
-For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
+For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once.
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
intermediate commit

--- 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
@@
 \label{sec:resources}
-\input{resources}
+%\input{resources}
+
+\paragraph{ImageNet and ILSVRC}
+
+%Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
+
+\subsection{\refcoco and \refcocop \cite{Yu2016}}~\\ 
+Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco},
+%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
+%However, the COCO region-level (object) annotations are not linked to the captions.
+a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
+The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
+Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
+The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
+If the matcher's prediction is correct, the RE is considered valid.
+
+\paragraph{Shortcomings}
+REs in \refcoco and \refcocop were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
+Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
+Finally, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy. \cs{TODO: EX / ANALYSIS}
+
+\begin{itemize}
+        \item[(R1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
+		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
+		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
+\end{itemize}
+
+\paragraph{Flickr30k Entities}~\\
+The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
+Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
+The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

@@
 Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
+Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
+For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once.
 

### 2018-07-12 papers/SiVL2018/resources.tex
intermediate commit
updates discussion to requirements

@@
 		& \multicolumn{2}{c|}{Constraints on} 
-		& WordNet  \\
+		& Coordinates  \\
 		& & & object			
@@
 		& language 	& images 
-		& IDs?\\
+		& \\
 		\hline \hline
@@
 					& $\geq$2 objs  
-					& \xmark \\
+					& \cmark \\
 					&
@@
 					& $\geq$2 objs  
-					& \xmark \\	
+					& \cmark \\	
 					&
@@
 					& -- 
-					& & \xmark \\
+					& & \cmark \\
 					& Caption generation
@@
 	\begin{center}
-	\begin{tabular}{|l|c|c|c|c|}
+	\begin{tabular}{|l|c|c|c|c|c|}
 		\hline
-		Resource & \multicolumn{3}{c|}{Provides (more or less directly)}\\
-		 		 & R1: Root-level & R2: Entry-level & R4: Coordinates  \\
+		Resource & \multicolumn{4}{c|}{Provides (Undirectly)}\\
+		 		 & R1: Most specific & R2: Entry-level 
+		 		 & R3: unconstraint & WordNet ID \\
 		\hline \hline
-		\refcoco 	& \xmark & \xmark & \cmark \\
-		\refcocop 	& \xmark & \xmark & \cmark \\
-		\flickr 	& \xmark & (\cmark) & \cmark \\
-		\vgenome 	& \xmark & \cmark 	& \cmark \\
+		\refcoco 	& \xmark & \xmark & \xmark & \xmark \\
+		\refcocop 	& \xmark & \xmark & \xmark & \xmark \\
+		\flickr 	& \xmark & (\cmark) & \cmark & \xmark \\
+		\vgenome 	& \xmark & \cmark 	& \cmark & \cmark \\
 		\hline 		
 	\end{tabular}
-	\caption{\label{tab:summary_resources} BLABLA overview of resources and their shortcomings wrt object naming. REG and REC: Referring expression generation and comprehension, respectively.}
+	\caption{\label{tab:resources_requirements} BLABLA overview of resources and their shortcomings wrt object naming. REG and REC: Referring expression generation and comprehension, respectively.}
 	\end{center}
@@
 \subsection{Linguistic Resources, Computer Vision Resources}
+
 \paragraph{WordNet}
@@
 \paragraph{MS COCO} \cite{mscoco}
-MS COCO is an object recognition dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
+MS COCO is an object recognition dataset of images of natural scenes. 
+As such it provides region-level object annotations for $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
 Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
 The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
-However, the COCO region-level (object) annotations are not linked to the captions.
+However, the COCO object annotations are not linked to the captions.
 \subsection{V\ \&\ L Resources}
+\cs{[If Table~\ref{tab:summary_resources} is kept (?):] \\
+Table~\ref{tab:summary_resources} gives an overview of the resources we discuss.}
 
@@
 
-The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
-Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
+The REs were collected via crowdsourcing in a two-player game that was designed to obtain REs which uniquely refer to the target objects in an image. 
+Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target in the image. 
 The matcher must click on the object he thinks the RE refers to. 
@@
 
-Finally, \referit is based on the SAIAPR image collection \cite{Grubinger2006} (20k images;99.5k image regions;120K REs), and captures not only REs for objects ("things") but also for scene categories (e.g.,{\refexp{grass, road}) (see also \cite{hu2015,mao2016generation}).
+Finally, \referit is based on the SAIAPR image collection \cite{Grubinger2006} %(20k images;99.5k image regions;120K REs), 
+ and captures not only REs for objects ("things") but also for scene categories (e.g.,{\refexp{grass, road}) (see also \cite{hu2015,mao2016generation}). 
 The task of scene detection is beyond the focus of our study regarding object naming, we therefore will not discuss this dataset further.
@@
 \subsection{Discussion of Shortcomings}
-We discuss the shortcomings of the presented V\&L datasets with respect to their use for computational linguistic studies of reference in general, and in particular in how far they satisfy the requirements for the study of object naming which we put forward in  Section~\ref{sec:requirements}.
+We discuss the shortcomings of the presented V\&L datasets with respect to their use for computational linguistic studies of reference in general, and in particular in how far they satisfy the Requirements R1--R3 for the study of object naming which we put forward in Section~\ref{sec:requirements}.
+\\
 
-\paragraph{\refcoco and \refcocop}
-The REs for both, \refcoco and \refcocop, were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-\cs{Maybe people tended more to use REs expressing the function of the object?}
+%\paragraph{\refcoco and \refcocop}
+The REs for both, \textit{\refcocop} and \textit{\refcoco} (henceforth, \refcoco/+), were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to, e.g.,~the appearance of objects.
+%\cs{Maybe people tended more to use REs expressing the function of the object?}
 %
-While these constraints ensured that the datasets are interesting from the computer vision perspective, they fall short in containing phenomena that are intriguing from the view of language research: 
+While these constraints ensured that the datasets are interesting from the computer vision perspective, they fall short in containing phenomena that are intriguing from the view of language research,
 %
-The range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the experimental data in order to study the interaction of their underlying factors.
-This is not given in \refcoco(+) with respect to the study of reference. 
+% Moved to requirements 
+% research:  The range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the experimental data in order to study the interaction of their underlying factors.
+%This is not given in \refcoco/+ with respect to the study of reference. 
+and are in contradiction to Requirement R3:  
 First, how the choice of a RE for an object interacts with the categories of its distractors can only partially be observed in the data\footnote{For example, the preference of the entry-level category over a sufficiently unique more generic category can only be observed in images in which the target and the distractor objects are of different more generic categories.} due to~(i).
@@
 
-Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
-
+Furthermore, (iii), not all objects in the images were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories. 
+For this reason and the fact that \refcoco/+ the $80$~COCO categories tend to be entry-level categories, it does thus not fulfill requirement~R1. 
+\cs{TODO: EX / ANALYSIS}
 %(i) violates (R0: The data contains only examples of case11, and excludes examples of case22, case23, case33 (case33:) do humans choose the entry-level category (e.g.,~\refexp{dog}) even though the super-level (e.g.,~\refexp{animal}) would suffice to uniquely refer to the object?).
-
+%
 % the cost of a name and the contextual ambiguity it creates (see Section~\ref{sec:object_naming}), 
 % entry-level category 
-
-With respect to the problem of object naming, \refcoco(+) does not fulfill requirement~R1. 
-As explained in Section~\ref{sec:requirements}, we can retrieve less specific categories from a taxonomy, but the most specific category of \textit{each} object depicted in an image needs to be provided by the data.
-This is not the case due to property~(iii), as well as due to the fact that the $80$~COCO categories tend to be entry-level categories. \cs{TODO: EX / ANALYSIS}
+%
+%With respect to the problem of object naming, \refcoco/+ does not fulfill requirement~R1. 
+%As explained in Section~\ref{sec:requirements}, we can retrieve less specific categories from a taxonomy, but the most specific category of \textit{each} object depicted in an image needs to be provided by the data.
+%This is not the case due to property~(iii), as well as due to the fact that the $80$~COCO categories tend to be entry-level categories. \cs{TODO: EX / ANALYSIS}
 %
@@
 
-The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraint~(i) to some extent---we may not be able to reliably infer the entry-level from the data \cs{TODO: Example or remove last part}.
+The dataset also falls short in fully meeting requirement~R2 due to property~(iii)---it only covers 80~object categories---and constraints~(i,ii) to some extent---we may not be able to reliably infer the entry-level from the data \cs{TODO: Example or remove last part}.
 
-\paragraph{Solution to R2: Captions?}
-Additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
-Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+\paragraph{}
+By design, \textit{\flickr} can be used to study the way people refer to individual entities in an image in dependence on the situation the speakers describe. 
+The annotators were not constraint by interfering external factors in their choice of entity mentions. \cs{double-check?} 
+We can therefore gather naturally produced object names from the data for objects which are mentioned in the captions and may be able to infer their entry-level categories (Requirement R2).
+\cs{ADD EXAMPLE IMAGE}
+
+%and may be able to infer their entry-level categories. 
 %
-In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
-such that natural language phrases first needed to be aligned with the image regions they refer to. 
-This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
-% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
+%This is only the case for objects which are mentioned in the captions, which is why \flickr does not fully satisfy requirement~R2 \cs{ADD EXAMPLE IMAGE}.
 
-\paragraph{Solution to R1: Object detectors?}
-An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
-However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of sub-level categories covered by the data need to be provided or collected from humans.
-
-\paragraph{\flickr}
-By design, \flickr can be used to study the way people refer to individual entities in an image in dependence on the situation the speakers describe. 
-In contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
-We can therefore gather naturally produced object names from the data and may be able to infer their entry-level categories. 
-%
-This is only the case for objects which are mentioned in the captions, which is why \flickr does not fully satisfy requirement~R2 \cs{ADD EXAMPLE IMAGE}.
-
-\flickr does not meet requirement R1 for similar reasons as \refcoco(+). 
+\flickr has similar issues in satisfying R1 as \refcoco/+. 
 Object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene}).
@@
 Note also the spelling mistakes (e.g.,~\word{dalmation}, \word{wating}). 
-Furthermore, regions and their annotations are highly redundant in that expressions referring to the same object may still be linked to different bounding boxes\cs{We would need to, e.g., merge boxes through IoU $\geq$ some threshold}.
+%Furthermore, regions and their annotations are highly redundant in that expressions referring to the same object may still be linked to different bounding boxes\cs{We would need to, e.g., merge boxes through IoU $\geq$ some threshold}.
 
@@
 For the same reason, on the other hand, and because of the dense image labeling and its exhaustive annotations, \vgenome satisfies R2---we can infer the entry-level name of each object in the image.
-For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is referred to by \refexp{heeler} once, and mostly by \refexp{dog} and its appearance or location.
-\\
+XX (Figure~\ref{fig:ex_visualgenome})\\
 
@@
 \noindent
-Finally, requirement~R4 is met by all discussed datasets.
+
+Table \ref{tab:resources_requirements} summarizes the shortcomings of the resources with respect to our requirements.
+
+\paragraph{Solution to R1: Object detectors?}
+An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
+
+\paragraph{Solution to R2: Captions?}
+Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
+Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+%
+In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
+such that natural language phrases first needed to be aligned with the image regions they refer to. 
+This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
+% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
intermediate commit

@@
 \begin{itemize}
-        \item[(R1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
+        \item[(1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
 		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
@@
 \paragraph{Flickr30k Entities}~\\
+The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
+Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
+The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
+
+\paragraph{Shortcomings}
+
+By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
+in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
+On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
+
+\begin{itemize}
+        \item[(1)] \textbf{Lexical choice}: is met, though object names might not be fully discriminative (as in referring expressions)
+		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
+		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
+\end{itemize}
+
+\subsection{Flickr30k Entities}~\\
 The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.

### 2018-07-12 papers/SiVL2018/resources.tex
modifies Table w/ ILVSRC/WordNet cmp

@@
 \begin{table}[t]
-	\begin{tabular}{lrrrr}
+	\begin{center}
+	\begin{tabular}{l|r|rrr}
 		\hline
-			 			& \refcoco & \refcocop & \flickr & \vgenome \\
-		\hline \hline
-		total \#synsets	&	2580\\
-		- match			&	112 \\
-		- hyponyms		&	36 \\
-		- hypernyms 	&	204 \\
-		\hline
-		%- not found		&	74 \\	
-		%\hline
-		\# 
-				& \multicolumn{3}{c}{No. object names $obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$:} \\
-				& (obj)
+				& \#synset($obj$) 
+				& \multicolumn{3}{c}{\#$obj$ for which $*(\text{synset}(obj), \text{ILSVRC})$} \\
+				&
 				& in
@@
 		\hline \hline
-		 	& 2580 & 112 & 204 & 36\\
-		 	& 15 & 30 & 1 \cs{??}\\
-		 	& \\
+		 \refcoco  (REs)		& 2,580 & 112 	& 204 	& 36\\
+		 \refcoco (categories)	& 78	& 15 	& 30 	& 1 (?) \\
 		\vgenome 	& \\
+		\flickr					& 6,139 & 238	& 338	& 95\\
 		\hline
 	\end{tabular}
-	\caption{Coverage of the object names in the datasets by WordNet and by the $1,000$~synsets of the ILSVRC image classification challenge.
-\#synsets(obj): number of object names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
+	\caption{Coverage of the unique object names (obtained from the categories or  from the REs) in the datasets by WordNet (first column) and by the $1,000$~synsets of the ILSVRC image classification challenge (columns~2--4).
+\#synsets($obj$): no.
+names for which synsets could be retrieved from WordNet;   \label{tab:coverage_ilsvrc}}
+	\end{center}
 \end{table}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

--- 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
@@
 
-@Carina TODO:
-\begin{itemize}
-	\item requirements: \\ 
-	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
-	add unconstraint object co-occurrences / unbiased as far as possible; \\
-	rename R1? (lexical alternatives? candidate names?)
-	\item title?
-\end{itemize}
+%@Carina TODO:
+%\begin{itemize}
+%	\item requirements: \\ 
+%	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
+%	add unconstraint object co-occurrences / unbiased as far as possible; \\
+%	rename R1? (lexical alternatives? candidate names?)
+%	\item title?
+%\end{itemize}
 
@@
 \cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
- concepts, adopting the traditional view that there is a single preferred name for a given object.
- Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.
+ concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independentl of the visual context.
+ %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.
 
@@
 
-In this Section we discuss requirements for scaling experimental studies on object names as in \cite{graf2016animal} to real-world images.
-The difference between these two approaches is illustrated in Figure \ref{fig:graf_genome}, showing  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context.
-Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, but we aim for studying object naming as prompted by real-world images.
-Therefore, we not only need access to names naturally generated by speakers, but also, we need to be able to quantify those factors whose interaction with naming we want to analyze.
-
-Given a natural scene with multiple objects and a target object that a speaker referred to, we need to be able to answer the following questions:
+In this Section we discuss the requirements for  being able to study the context dependence of object names to real-world images, inspired by \cite{graf2016animal}'s study.
+ Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
+Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus.
+Given a real-world scene with multiple objects and a target object that has to be named, we need access to:
 
 \begin{itemize}
-        \item[(1)] \textbf{Lexical choice}: \\
-        Which name did the speaker use to refer to the target object?
-		\item[(2)] \textbf{Lexical candidates}: \cs{"candidate" does not exclude the chosen name in contrast to "alternative"}\\
-		%Which names are available for the target objects?  
-		Which names are available for the target objects? 
-		And how are they taxonomically related? 
-		For instance, if we want to check whether a convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible}) we need to know that a given object is a \cat{convertible}, and that \cat{convertible} is a sub-level concept of \cat{car} (and \cat{vehicle}, etc.).
-		%Additionally, in
-		In \cite{graf2016animal}, the authors manually group object names used by speakers in terms of three levels (sub-level, basic-level, super-level). 
-		Thus, ideally, %names 
-		lexical candidates 
-		would be grouped according to their taxonomic relations. 
-		\item[(3)] \textbf{Contextual informativeness}: \\
-		Which names are available for the other objects in the scene (i.e. distractors)?
-		For instance, when the target is a \cat{convertible}, we need to know that there are multiple \cat{convertibles}, \cat{cars}, etc. to judge whether these concepts are ambiguous.
+
+		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
+		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
+		\item[(3)] the \textbf{natural name} chosen by a speaker for describing or referring to an object
+
 \end{itemize}
 
-\cs{Should the following be here or at the beginning of Sect. 4?}
-\cs{We could also call below requirements "Desiderata"}
-In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
-A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
-Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.
+For instance, if we want to check whether a specific object like convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible,limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or  a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible,car, etc}.
 
-With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors.
-Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors.
-We summarize this requirement by the term \textbf{R3: unconstraint}. 
-Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
+%\cs{Should the following be here or at the beginning of Sect. 4?}
+%\cs{We could also call below requirements "Desiderata"}
+%In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
+%A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
+%Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
+%Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
+%For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once.
+%
+%With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors.
+%Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors.
+%We summarize this requirement by the term \textbf{R3: unconstraint}. 
+%Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
+%
 
@@
 \label{sec:resources}
-%\input{resources}
 
-\paragraph{ImageNet and ILSVRC}
+\subsection{ImageNet and ILSVRC}
+
+ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases that follows a consistent taxonomy: its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
+Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
+Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
+However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset), such that no (or very few) distractors objects.
 
@@
 \begin{itemize}
-        \item[(R1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
-		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
-		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
+     		\item[(1)] \textbf{Specific categories}: are not available, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
+		\item[(2)] \textbf{Exhaustive annotations}: are not available, as not all objects were annotated with REs and corresponding categories
+		   \item[(3)] \textbf{Natural names}: are available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
+
 \end{itemize}
 
-\paragraph{Flickr30k Entities}~\\
+\subsection{Flickr30k Entities}
 The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
@@
 
-\section{Proposal}
+\paragraph{Shortcomings}
+
+By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
+in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
+On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
+
+\begin{itemize}
+     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
+		\item[(2)] \textbf{Exhaustive annotations}: are not available
+		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+
+\end{itemize}
+
+%\section{Carina}
+%input{resources}
+
+\subsection{Visual Genome}
+
+\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
+
+\paragraph{Shortcomings}
+
+\begin{itemize}
+     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
+				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
+		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+
+\end{itemize}
+
+\section{Possible Solutions}
+
+We now discuss solutions to the shortcomings discussed above.
+
+\subsection{Object detectors}
+As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
+An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
+
+\subsection{Post-annotating Captions}
+Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
+Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+%
+In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
+such that natural language phrases first needed to be aligned with the image regions they refer to. 
+This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
+% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
+
+\subsection{Collect naming data with controlled specificity}
+
 %\label{sec:future_proposal}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
intermediate commit

@@
 
-We now discuss solutions to the shortcomings discussed above.
+As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity.
+We now discuss tentative solutions to the shortcomings for this problem.
 
-\subsection{Object detectors}
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
-An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
-However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
-
-\subsection{Post-annotating Captions}
+\subsection{Post-annotating CoCo Captions}
 Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
@@
 
+\subsection{Exhaustive, automatic object labeling}
+
+One solution for obtaining objects labels at a consistent, specific level in a certain taxonomy would be to train and/or apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
+However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans. 
+Thus, it is unclear whether it is actually feasible to exhaustively label e.g. all objects in VisualGenome images with their corresponding leaf node in ImageNet, at a decent level of quality.
+
 \subsection{Collect naming data with controlled specificity}
+
+Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
+As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
+Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to gather
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
simple conclusion

@@
 
-\subsection{Collect naming data with controlled specificity}
+\subsection{Collect naming data with controlled level of specificity}
 
@@
 As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
-Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to gather
+Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to be able to systematically gather object names at the sub-level.
 
@@
 
+\section{Conclusion}
+
+In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
+The comparison between different data sets and available annotations for them reveals that consist procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to use of concepts) turns out to be difficult.
+
 \clearpage

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
some missing refs
small modifications

@@
 So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
- State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet (REF!!), though see work by Deng et al.
+ State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al.
 on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
 \cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
- concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independentl of the visual context.
+ concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independently of the visual context.
  %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.
@@
 
-In this Section we discuss the requirements for  being able to study the context dependence of object names to real-world images, inspired by \cite{graf2016animal}'s study.
+In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
  Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
@@
 
-ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases that follows a consistent taxonomy: its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
+ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories.
+ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
 Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
-Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset), such that no (or very few) distractors objects.
+However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) without any (or very few) distractors objects in context.
 
@@
 \bibliographystyle{splncs}
+\begin{footnotesize}
 \bibliography{naming}
+\end{footnotesize}
+
 \end{document}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
adds example regarding ISLVRC coverage

--- 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
@@
 	\begin{center}
-		\begin{minipage}{.52\textwidth}
-			\includegraphics[width=\linewidth]{fig/graffig.pdf}
+		\begin{minipage}{.35\textwidth}
+			\includegraphics[scale=.15]{fig/graffig.pdf}
 		\end{minipage}
-		\begin{minipage}{.42\textwidth}
-			\includegraphics[width=5cm]{fig/visual_genome_dogs.png}
+		\begin{minipage}{.2\textwidth}
+			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
+		\end{minipage}
+	\begin{minipage}{.2\textwidth}
+		\includegraphics[height=2.5cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes.jpg}
+	\end{minipage}
+	\begin{minipage}{.2\textwidth}
+		\includegraphics[height=3cm,width=2.5cm]{fig/refcoco_2400_dog_boxes.jpg}
+	\end{minipage}\vspace{-.7cm}\\
+\begin{minipage}{.35\textwidth}
+	...
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\tiny
+	{\textsl{dalmatian, dog, heeler}}
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\textsl{\tiny dog}
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\tiny \textsl{dog}
 \end{minipage}
@@
 
-\subsection{ImageNet and ILSVRC}
+\subsection{ImageNet}
 
@@
 Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset), such that no (or very few) distractors objects.
+However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.
 
@@
 
-\subsection{\refcoco and \refcocop \cite{Yu2016}}~\\ 
+\subsection{\refcoco and \refcocop \cite{Yu2016}}
 Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco},
@@
 
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity.
-We now discuss tentative solutions to the shortcomings for this problem.
+We now discuss solutions to the shortcomings discussed above.
 
-\subsection{Post-annotating CoCo Captions}
+\subsection{Object detectors}
+As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
+An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
+
+\subsection{Post-annotating Captions}
 Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
@@
 
-\subsection{Exhaustive, automatic object labeling}
-
-One solution for obtaining objects labels at a consistent, specific level in a certain taxonomy would be to train and/or apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
-However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans. 
-Thus, it is unclear whether it is actually feasible to exhaustively label e.g. all objects in VisualGenome images with their corresponding leaf node in ImageNet, at a decent level of quality.
-
 \subsection{Collect naming data with controlled specificity}
-
-Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
-As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
-Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to gather
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
adds images

@@
 		\begin{minipage}{.35\textwidth}
-			\includegraphics[scale=.15]{fig/graffig.pdf}
+			\includegraphics[scale=.15]{fig/graffig.jpg}
 		\end{minipage}
@@
 	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2.5cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes.jpg}
+		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
 	\end{minipage}
 	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=3cm,width=2.5cm]{fig/refcoco_2400_dog_boxes.jpg}
+		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
 	\end{minipage}\vspace{-.7cm}\\

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

--- 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
@@
 	\begin{center}
-		\begin{minipage}{.52\textwidth}
-			\includegraphics[width=\linewidth]{fig/graffig.pdf}
+		\begin{minipage}{.35\textwidth}
+			\includegraphics[width=4.2cm]{fig/graffig.jpg}
 		\end{minipage}
-		\begin{minipage}{.42\textwidth}
-			\includegraphics[width=5cm]{fig/visual_genome_dogs.png}
+		\begin{minipage}{.2\textwidth}
+			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
+		\end{minipage}
+	\begin{minipage}{.2\textwidth}
+		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
+	\end{minipage}
+	\begin{minipage}{.2\textwidth}
+		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
+	\end{minipage}\vspace{-0cm}\\
+\begin{minipage}{.35\textwidth}
+	---
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\tiny
+	{\textsl{dalmatian, dog, heeler}}
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\textsl{\tiny dog}
+\end{minipage}
+\begin{minipage}{.2\textwidth}
+	\tiny \textsl{dog}
 \end{minipage}
@@
 Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) without any (or very few) distractors objects in context.
+Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
+However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.
 
@@
 
-\subsection{Post-annotating CoCo Captions}
+\subsection{Object detectors}
+As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
+An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
+For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
+
+\subsection{Post-annotating COCO Captions}
 Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
adds abstract

@@
 
-\title{Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title
+\title{Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title
 
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper. LNCS guidelines
-indicate it should be at least 70 and at most 150 words. It should be set in 9-point
-font size and should be inset 1.0~cm from the right and left margins.
-\dots
+Massive data collections that are of interest for language \& vision tasks (from image captioning to visual dialogue) are nowadays available.
+In principle, these could constitute valuable resources also for research in Linguistics, besides application-oriented one.
+However, in practice very few studies have tested linguistic hypotheses using these large-scale datasets.
+In this paper, we illustrate the challenges of using this type of corpora for linguistic research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
+Our analysis of existing resources in language \& vision reveals that none of the available datasets consistently satisfies all of the requirements for a linguistically motivated study of this phenomenon.
+We conclude with a proposal for a more consistent annotation of language \& vision data which can aid the study of object naming.
+%The abstract should summarize the contents of the paper.
+LNCS guidelinesindicate it should be at least 70 and at most 150 words.
+It should be set in 9-point font size and should be inset 1.0~cm from the right and left margins.
 \keywords{We would like to encourage you to list your keywords within
@@
 	\begin{center}
-		\begin{minipage}{.35\textwidth}
-			\includegraphics[width=4.2cm]{fig/graffig.jpg}
+		\begin{minipage}{.52\textwidth}
+			\includegraphics[width=\linewidth]{fig/graffig.pdf}
 		\end{minipage}
-		\begin{minipage}{.2\textwidth}
-			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
-		\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
-	\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
-	\end{minipage}\vspace{-0cm}\\
-\begin{minipage}{.35\textwidth}
-	---
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny
-	{\textsl{dalmatian, dog, heeler}}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\textsl{\tiny dog}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny \textsl{dog}
+		\begin{minipage}{.42\textwidth}
+			\includegraphics[width=5cm]{fig/visual_genome_dogs.png}
 		\end{minipage}
@@
 
-\subsection{ImageNet}
+\subsection{ImageNet and ILSVRC}
 
@@
 Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
-Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.
+However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) without any (or very few) distractors objects in context.
 
@@
 
-\subsection{\refcoco and \refcocop \cite{Yu2016}}
+\subsection{\refcoco and \refcocop \cite{Yu2016}}~\\ 
 Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco},
@@
 
-\subsection{Object detectors}
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
-An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
-However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
-
-\subsection{Post-annotating COCO Captions}
+\subsection{Post-annotating CoCo Captions}
 Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
small modifications

@@
 \begin{abstract}
-Massive data collections that are of interest for language \& vision tasks (from image captioning to visual dialogue) are nowadays available.
-In principle, these could constitute valuable resources also for research in Linguistics, besides application-oriented one.
-However, in practice very few studies have tested linguistic hypotheses using these large-scale datasets.
+Massive data collections for applications in language \& vision are nowadays available.
+In principle, these could constitute valuable resources also for research in linguistics, besides task-specific modeling.
+However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
 In this paper, we illustrate the challenges of using this type of corpora for linguistic research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
@@
 It should be set in 9-point font size and should be inset 1.0~cm from the right and left margins.
-\keywords{We would like to encourage you to list your keywords within
-the abstract section}
+\keywords{Object naming, object categorization, concepts, entry-level categories}
 \end{abstract}
@@
 However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}.
-This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}.
-
+%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
 While the traditional notion of entry-level categories suggests that objects tend to be named by a \textit{single} preferred concept, research on pragmatics has found that speakers are flexible with respect to the chose level of specificity.
 Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating} \cite{graf2016animal}.
-For example, in presence of more than one dog, the name \textit{dog} is ambiguous and a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost (which is typically approximated by frequency) or saliency also come into play \cite{graf2016animal}  \cite{clark1983common}.
+For example, in presence of more than one dog, the name \textit{dog} is ambiguous and a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}  \cite{clark1983common}.
 %Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene).
@@
 
-So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
+So far, research in vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
  State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al.
@@
 \begin{itemize}   
-
 		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
@@
 \subsection{\refcoco and \refcocop \cite{Yu2016}}
-Both datasets are extensions of \referit\cite{Kazemzadeh2014}, a large-scale collection of referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO image collection \cite{mscoco},
+Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
 %The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
@@
 a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
-The REs were collected via crowdsourcing in a two-player game, which was designed to obtain REs uniquely referring to the target objects in an image. 
+The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
 Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
 The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-If the matcher's prediction is correct, the RE is considered valid.
-
-\paragraph{Shortcomings}
-REs in \refcoco and \refcocop were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
-Finally, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy. \cs{TODO: EX / ANALYSIS}
+REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
+%Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
 
 \begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
-		\item[(2)] \textbf{Exhaustive annotations}: are not available, as not all objects were annotated with REs and corresponding categories
-		   \item[(3)] \textbf{Natural names}: are available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
-
+     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy. \cs{TODO: EX / ANALYSIS}
+		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
+		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
 \end{itemize}
@@
 The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
-
-\paragraph{Shortcomings}
 
@@
 It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
-
-\paragraph{Shortcomings}
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
small modifications

@@
 Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
-With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,chen2015mind,vinyals:show,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016,schlazar:acl16}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
+With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
 In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks -- they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
@@
 	\end{center}
-	\caption{Experimental and real-world visual scenes showing dogs (GET MORE IMAGES OF DOGS FROM VG???)}
+		\vspace{-0.8cm}
+
+	\caption{Experimental and real-world visual scenes showing dogs from Visual Genome, RefCoco, and Flickr)}
 	\label{fig:graf_genome}
+		\vspace{-0.5cm}
+
 \end{figure}
@@
 		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
-		\item[(3)] the \textbf{natural name} chosen by a speaker for describing or referring to an object
+		\item[(3)] the \textbf{natural name} chosen by a speaker for referring to an object
 
@@
 \label{sec:resources}
+
+In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming.
+We focus on collections  that have been used for object recognition, referring expression generation, phrase localization in previous work, but do not discuss other collections for e.g.
+image captioning which typically do not link mentions of objects to corresponding image regions.
 
@@
 \begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy. \cs{TODO: EX / ANALYSIS}
+     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
 		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
@@
 As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity.
-We now discuss tentative solutions to the shortcomings for this problem.
+We now discuss tentative solutions.
 
@@
 % We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
-
-\subsection{Exhaustive, automatic object labeling}
-
-One solution for obtaining objects labels at a consistent, specific level in a certain taxonomy would be to train and/or apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
-However, pre-trained models only exist for a subset of the datasets' objects. \cs{TODO: ADD CMP WITH ILSVRC}
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans. 
-Thus, it is unclear whether it is actually feasible to exhaustively label e.g. all objects in VisualGenome images with their corresponding leaf node in ImageNet, at a decent level of quality.
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
added table

@@
 \begin{minipage}{.35\textwidth}
-	---
+	\tiny scene from  \cite{graf2016animal}
 \end{minipage}
@@
 In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
- Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
+ Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage (on left), and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
 Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus.
@@
 
+\begin{table}
+\centering
+\setlength{\tabcolsep}{2pt}
+\begin{tiny}
+\begin{tabular}{rrl|rrl}
+\toprule
+ spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
+\midrule
+           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
+           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
+           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
+           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
+           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
+           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
+           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
+           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
+\bottomrule
+\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
+\label{tab:specnames}
+\end{tiny}
+\vspace{-1cm}
+\label{tab:specnames}
+\end{table}
+\vspace{-0.6cm}
+
 %Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
@@
 \end{itemize}
+
+\paragraph{Analysis} We parse REs in RefCocowith the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
+We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.
+We estimate this distance as the minimal path length of all synsets of a word  to the root node.
+Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the RefCoco data set.
+We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
+Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
+At the same time, this overview clearly suggests that object names in RefCoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
 
@@
 
-\subsection{Post-annotating COCO Captions}
-Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
-Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+%\subsection{Post-annotating COCO Captions}
+%Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
+%Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
+%%
+%In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
+%such that natural language phrases first needed to be aligned with the image regions they refer to. 
+%This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
+%% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
 %
-In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
-such that natural language phrases first needed to be aligned with the image regions they refer to. 
-This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
-% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
+%
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
small mod

@@
 \bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level, relative frequency and 5 most frequent names are shown}
+\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
 \label{tab:specnames}

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
revising

--- 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
@@
 Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in linguistics, besides task-specific modeling.
+In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
 However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
-In this paper, we illustrate the challenges of using this type of corpora for linguistic research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
+In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
 Our analysis of existing resources in language \& vision reveals that none of the available datasets consistently satisfies all of the requirements for a linguistically motivated study of this phenomenon.
@@
 
-Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and linguistics.
-With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks -- they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
+Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and (computational) linguistics.
+With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision (L\&V) tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
+In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
 \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
 In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
-However, so far, studies that have tested linguistic hypotheses on large-scale vision \& language resources have been relatively rare.
+However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.
 
-In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every language \& vision task and is, at the same time, subject of ongoing research in language grounding and pragmatics.
-Our starting point is a particular linguistic hypothesis related to object naming - namely that the choice of a name for an object is dependent on other objects in its visual context - which has been tested recently in a classical experimental setting \cite{graf2016animal}.
+In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
+Our starting point is a particular linguistic hypothesis related to object naming---namely that the choice of a name for an object is dependent on other objects in its visual context---which has been tested recently in a classical experimental setting \cite{graf2016animal}.
 We discuss how this hypothesis could be tested based on recent data sets that pair images and object descriptions, referring expressions or captions (all containing object names) and define a set of requirements for obtaining a theoretically informed model for object naming.
-In sum, this discussion will show that specific requirements are met by particular resources, but none of the available corpora consistently satisfies all of the requirements.
-We believe that this is a perfect showcase illustrating the challenges for linguistically motivated research in language and vision, and we derive a proposal for obtaining more consistently designed and annotated data collections for object naming.
+In sum, this discussion will show that specific requirements are met by particular resources, but none of the available corpora consistently 
+satisfy 
+all of the requirements.
+We believe that this is a perfect showcase illustrating the challenges for linguistically motivated research in L\&V, and we derive a proposal for obtaining more consistently designed and annotated data collections for object naming.
 
@@
 
-The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \textit{dog}'', ``the white \textit{dog} to the left'').
-Since an object is simultaneously a member of multiple categories (e.g., a young beagle is at once a dog, a beagle, an animal, a puppy etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}.
+The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
+Since an object is simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}.
 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \textit{bird}, \textit{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \textit{animal}, \textit{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \textit{sparrow}, \textit{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called a \textit{penguin} and not a \textit{bird}) \cite{jolicoeur1984pictures}.
+This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
+However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \textit{single} preferred concept, research on pragmatics has found that speakers are flexible with respect to the chose level of specificity.
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating} \cite{graf2016animal}.
-For example, in presence of more than one dog, the name \textit{dog} is ambiguous and a sub-level category (e.g., \textit{rottweiler}, \textit{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}  \cite{clark1983common}.
+While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
+%with respect to the chose level of specificity. 
+their choice of the level of specificity. 
+Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
+\cite{rohde2012communicating}\cite{graf2016animal}.
+For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}\cite{clark1983common}.
 %Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene).
@@
 
-So far, research in vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
+So far, research in L\&V, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
  State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al.
@@
 In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
- Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
+ Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and real-world scenes where multiple objects occur in a natural context from \vgenome\cite{krishna2016visualgenome}, \refcoco\cite{Kazemzadeh2014}, and \flickr\cite{plummer2015flickr30kentities} (cf.
+Section~\ref{sec:resources}).
 Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus.
@@
 
-For instance, if we want to check whether a specific object like convertible is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible,limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or  a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible,car, etc}.
+For instance, if we want to check whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible, car, etc}.
 

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex

@@
 
+\begin{table}
+\centering
+\setlength{\tabcolsep}{2pt}
+\begin{tiny}
+\begin{tabular}{rrl|rrl}
+\toprule
+ spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
+\midrule
+           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
+           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
+           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
+           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
+           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
+           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
+           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
+           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
+\bottomrule
+\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
+\label{tab:specnames}
+\end{tiny}
+\vspace{-1cm}
+\label{tab:specnames}
+\end{table}
+\vspace{-0.6cm}
+
 %Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
revising

@@
 
-For instance, if we want to check whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know wether a speaker called the object that \refexp{convertible, car, etc}.
+%For instance, if we want to find out whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{convertible, car, etc}.
+
+For instance, if we want to find out whether a specific object like the left dog in  Fig.~\ref{fig:graf_genome}, second-left image, is more often referred to with a basic-level category (e.g.,~\refexp{dog}) or a more specific one (e.g.,~\refexp{dalmatian}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{dalmatian} or, e.g.,~an \cat{irish setter}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{dalmatian, dog, etc}.
 

### 2018-11-13 papers/SiVL2018/sivl_2018_6pages.tex

@@
 In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming.
-We focus on collections  that have been used for object recognition, referring expression generation, phrase localization in previous work, but do not discuss other collections for e.g.
+We focus on collections  that have been used for object recognition, referring expression generation, and phrase localization in previous work, but do not discuss other collections for e.g.
 image captioning which typically do not link mentions of objects to corresponding image regions.
@@
 
-ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories.
+ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories (e.g.,~the ILSVRC image classification challenge comprises 1k synsets \cite{ILSVRC15}).
 ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
@@
 
-\paragraph{Analysis} We parse REs in RefCocowith the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
-We hypothesize that the distance of a name's synset to the root node (entity) relates to its specificity.
+\paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
+We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
 We estimate this distance as the minimal path length of all synsets of a word  to the root node.
-Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the RefCoco data set.
+Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
 We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
 Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
-At the same time, this overview clearly suggests that object names in RefCoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
+At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
 
@@
 By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
-in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
-On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
+in contrast to \refcoco/+, the production of entity mentions did not underlie any constraints. 
+On the other hand, it is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
 
@@
 		\item[(2)] \textbf{Exhaustive annotations}: are not available
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})
 
@@
 \subsection{Object detectors}
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent annotations of object categories at a sufficient level of specificity.
-An alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers. 
+In order to obtain a sufficiently specific level for all objects in an image, an alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
 However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
@@
 In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
-The comparison between different data sets and available annotations for them reveals that consist procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to use of concepts) turns out to be difficult.
+The comparison between different data sets and available annotations for them reveals that consistent procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to the use of concepts) turns out to be difficult.
 

### 2018-12-20 papers/ACL2019/acl19_naming.tex
initial draft for acl 2019

\documentclass[11pt]{article}
%\usepackage[hyperref]{acl2017}
\usepackage[nohyperref]{acl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}  %%% for including graphics
\usepackage{rotating}
\usepackage{color}

%\aclfinalcopy % Uncomment this line for the final submission
\def\aclpaperid{489} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}

%\title{What do you need to know about a word when you\\ want to use it for naming objects?}
\title{An object deserves more than a single name}

\author{Sina Zarrie{\ss}  \and David Schlangen\\
  Dialogue Systems Group // CITEC // Faculty of Linguistics and Literary Studies \\
 Bielefeld University, Germany \\
  {\tt \{sina.zarriess,david.schlangen\}@uni-bielefeld.de} \\}

\date{}

\begin{document}

\maketitle

\begin{abstract}
\end{abstract}

\section{Introduction}

Categorizing and naming real-world objects is a fundamental ability of human cognition and communication. In NLP, object naming is a core phenomenon which is part of virtually every Language \& Vision task.
Since objects are often simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), the act of naming an object amounts to that of selecting a lexical concept  for it among the various potential alternatives.

Research on categorization and language production has used object naming as a basic paradigm for investigating the processes that underly formation, organization and retrieval of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}.
Research in computer vision has focused on automatic object recognition where, recently, powerful models have been developed that classify visual objects in real-world images into thousands of different categories \newcite{googlenet}.
In NLP (L\&V), however, research on object naming is relatively scarce.
While there has been an explosion of interest in various, sometimes complex, L\&V tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}, there has hardly been any work looking at linguistic questions involved in object naming.
As the starting point of this work, we argue that existing resources in L\&V constitute an excellent basis for empirical, large-scale investigations into object naming.
At the same time, we show that we need to systematically extend them and collect naming data in a more ??? way, so as to arrive at a solid empirical approach.

Shortcomings of existing resources:

\begin{itemize}
\item most corpora record a single label or a small set of descriptions for each object
\item no systematic inventory of object labels
\item existing taxonomies (WordNet) are not really useful
\end{itemize}

\section{Related Work}
\label{sec:related}

\paragraph{Cognition: Concepts and categorization}

 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating}\cite{graf2016animal}.

\paragraph{Vision: Object Recognition}

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.

\paragraph{Vision \& language: Naming and Referring}

\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
 categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g. involve corpus frequencies. 
 \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
 Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.

\section{Data Collection}
\label{sec:task}

describe the YouNameIt task here

\subsection{Materials} describe sampling of images, category selection

\subsection{Procedure} describe the crowdsourcing set-up and the task

\subsection{Data} give an overview of the collected data

\section{Analysis}

\subsection{Agreement, basic-level and entry-level names}

analyse data mainly from Phase 0

\begin{itemize}
\item  to what extent do people agree when their task is to give the most straightforward name they can think of to a visual object?
\item is the level of agreement the same for all categories?
\item how specific are the most familiar names? link names to WordNet, show that WordNet might not be ideal to assess specificity
\item how does agreement evolve in the later rounds of the game? (when people have to avoid taboo names), does agreement increase as the set of names becomes more narrow, or  does agreement decrease as people do creative, clever, unexpected things?
\end{itemize}

\subsection{Cases of disagreement}

when and why do people give different names to the same object? this will probably happen in phase 0, and even more so in the later round \sz{this is what I expect}

\begin{itemize}
\item  analyse naming disagreement using WordNet, how do names for the same object relate to each other according to WordNet?
\item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
\item we might need to do some manual annotation here and try to carefully describe the phenomena
\end{itemize}

\subsection{Taxonomic relations}

can we elicit natural sub-ordinate, super-ordinate concepts?

\section{Model}

\subsection{Model 1}
Train a simple naming model (classifiers) on original VisualGenome names. Test it on our data. How well does the model predict the most familiar name and the set of available names?

\subsection{Model 2}
Train a simple naming model (classifiers) on our data, maybe combined with VisualGenome data. How well does it work?

\subsection{Model 3}

can we model taxonomic/conceptual knowledge more directly? induce a taxonomy? or a multi-modal space for objects + names?

\section{Conclusion}

We have presented a systematic, large-scale study on object naming with real-world images and crowdsourced data.

\bibliography{ontowac}
\bibliographystyle{acl_natbib}

\end{document}

### 2018-12-20 papers/ACL2019/acl19_naming.tex
progress in intro

@@
 \newcommand{\cat}[1]{\textsc{#1}}
+\newcommand{\vgenome}{VisualGenome\xspace}
 
@@
 
-Categorizing and naming real-world objects is a fundamental ability of human cognition and communication.
-In NLP, object naming is a core phenomenon which is part of virtually every Language \& Vision task.
-Since objects are often simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), the act of naming an object amounts to that of selecting a lexical concept  for it among the various potential alternatives.
+The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of different categories.
+And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
+For instance, the object in Figure \ref{fig:cake} is at once a \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
 
-Research on categorization and language production has used object naming as a basic paradigm for investigating the processes that underly formation, organization and retrieval of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}.
-Research in computer vision has focused on automatic object recognition where, recently, powerful models have been developed that classify visual objects in real-world images into thousands of different categories \newcite{googlenet}.
-In NLP (L\&V), however, research on object naming is relatively scarce.
-While there has been an explosion of interest in various, sometimes complex, L\&V tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}, there has hardly been any work looking at linguistic questions involved in object naming.
-As the starting point of this work, we argue that existing resources in L\&V constitute an excellent basis for empirical, large-scale investigations into object naming.
-At the same time, we show that we need to systematically extend them and collect naming data in a more ??? way, so as to arrive at a solid empirical approach.
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[height=2cm,width=2.5cm]{Figures/cheescake.png}
+\caption{A real-world object in VisualGenome}
+\label{fig:cake}
+\end{center}
+\end{figure}
 
-Shortcomings of existing resources:
+Given the abundance of concepts available in language, the act of \textit{naming} a visual object is less trivial than it might seem intuitively: in order to describe or refer to an object, a name has to be selected from a complex network of concepts and from many competing lexical alternatives.
+Hence, research on cognition and language production has relied on object naming as a basic paradigm for investigating the processes that underly formation and organization of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}, though mostly using idealized, graphical objects from specific domains (plants, animals) as visual stimuli.
+Complementary to that, research in computer vision has (successfully) focused on automatically recognizing \textit{real-world} objects in images or videos, but using simplified categorization schemes where each object is assigned a single correct label or name, cf.\ \cite{googlenet}.
+%Here, powerful models have been developed recently that classify visual objects in real-world images into thousands of different (mutually exclusive) categories \newcite{googlenet}.
 
-\begin{itemize}
-\item most corpora record a single label or a small set of descriptions for each object
-\item no systematic inventory of object labels
-\item existing taxonomies (WordNet) are not really useful
-\end{itemize}
+In NLP, to date, research on object naming is relatively scarce despite the fact that
+ there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
+In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
+At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.
+
+The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming.
+Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
+Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object.
+Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
+object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
+These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
 
@@
  Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.
+
+\paragraph{Existing resources and their shortcomings} summarize SIVL paper here
 
@@
 
-\bibliography{ontowac}
+\bibliography{naming}
 \bibliographystyle{acl_natbib}

### 2018-12-20 papers/ACL2019/acl19_naming.tex
progress in intro

@@
 object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
-These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
+These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to assess (i) how representative nmaing choices are, (ii) how they related to the taxonomic properties of the object  ...
+get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
 

### 2018-12-20 papers/ACL2019/acl19_naming.tex
progress in intro

--- 2018-12-20 papers/ACL2019/acl19_naming.tex
@@
 %\title{What do you need to know about a word when you\\ want to use it for naming objects?}
-\title{An object deserves more than a single name}
+\title{How many times must an object be named (before we know what it is)?}
 
@@
 
-The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of different categories.
+The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories.
 And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
-For instance, the object in Figure \ref{fig:cake} is at once a \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
+For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
 
@@
 \begin{center}
-\includegraphics[height=2cm,width=2.5cm]{Figures/cheescake.png}
-\caption{A real-world object in VisualGenome}
+\includegraphics[height=3cm]{Figures/cheescake.png}
+\includegraphics[height=3cm]{Figures/cheesecak2.pdf}
+\caption{Two objects of the same type of cake, with different names in VisualGenome}
 \label{fig:cake}
@@
 
-Given the abundance of concepts available in language, the act of \textit{naming} a visual object is less trivial than it might seem intuitively: in order to describe or refer to an object, a name has to be selected from a complex network of concepts and from many competing lexical alternatives.
+Given the abundance of concepts available in language, the act of \textit{naming} a visual object is not just a labeling of visible properties, it amounts to selecting a name from a complex network of concepts and competing lexical alternatives.
 Hence, research on cognition and language production has relied on object naming as a basic paradigm for investigating the processes that underly formation and organization of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}, though mostly using idealized, graphical objects from specific domains (plants, animals) as visual stimuli.
@@
  there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
-At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.
+Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test beds for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
+%In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
+%At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.
 
-The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming.
-Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
-Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object.
-Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
-object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
-These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
+The goal of this paper is to extend Visual Genome  \cite{krishna2016visualgenome}, a well-known, large-scale resource in language \& vision research, in a way that it can serve as a broad empirical basis for systematic and linguistically motivated investigations into object naming.
+We argue that object naming is an interesting, core phenomenon in itself as it occurs in virtually every L\&V task, but our approach can also support more systematic analysis of broader tasks, such as e.g.\ modeling referring expressions.
+
+Even though VisualGenome is one of the most exhaustively annotated resources to date, providing dense object annotations and descriptions in real-world images, it suffers from two important shortcomings if one is interested in linguistic analysis of object naming:
+First, it only provides a single, manually annotated object description (including a single name) per object which makes it impossible to assess how representative the annotated naming choices are, e.g.\ whether speakers tend to generally prefer \refexp{cheesecake} for the highlighted object in Figure \ref{fig:cake}.
+Second, it does not provide consistent taxonomic information on objects and their categories, as names have been automatically linked to WordNet synsets. 
+This makes it difficult to assess how naming depends on the taxonomic properties of the object, e.g.\  that both objects in Figure \ref{fig:cake} are instances of \cat{cheesecake}, but one is named \refexp{cheesecake} and the other one is named \refexp{desert}.
+It is important to note here that this shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).
+
+In this work, we address these two shortcomings and present a crowdsourcing-based and light-weight experimental set-up for eliciting representative and taxonomically consistent (\sz{more complete?}) naming data.
+We compare our collected data against names annotated in Visual Genome, and calculate various measures assessing agreement, naming preferences etc.
+
+The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names.
+We show that this cheap, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.
 
@@
 
-\paragraph{Existing resources and their shortcomings} summarize SIVL paper here
+\paragraph{Existing resources and their shortcomings}
+Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
+object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
 
@@
 (when people have to avoid taboo names), does agreement increase as the set of names becomes more narrow, or  does agreement decrease as people do creative, clever, unexpected things?
+\item assess how representative name annotations in Visual Genome are, when compared to our names
 \end{itemize}

### 2019-01-03 papers/ACL2019/acl19_naming.tex
adds a few comments

@@
 \usepackage{rotating}
-\usepackage{color}
+\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
+\newcommand{\cs}[1]{\textcolor{Fuchsia}{\emph{//cs: #1//}}}
 \newcommand{\refexp}[1]{\textsl{#1}}
@@
  there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
-Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test beds for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
+Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test bed for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
 %In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
@@
 This makes it difficult to assess how naming depends on the taxonomic properties of the object, e.g.\  that both objects in Figure \ref{fig:cake} are instances of \cat{cheesecake}, but one is named \refexp{cheesecake} and the other one is named \refexp{desert}.
-It is important to note here that this shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).
+It is important to note here that these shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).
 
@@
 The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names.
-We show that this cheap, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.
+We show that this simple, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.
 
@@
 Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating}\cite{graf2016animal}.
+\cite{rohde2012communicating,graf2016animal}.
 
@@
 These object recognition systems are now widely used in vision \& language research.
-Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.
+Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.}
 
@@
 Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
-object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
+object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.
 
@@
 \item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
+\item \cs{Wrt points 1+2: Show that WordNet, again, is not ideal for retrieving all possible names of an object from a single synset.}
 \item we might need to do some manual annotation here and try to carefully describe the phenomena

### 2019-01-30 amt_pilot/amt_api/approveall.py
updated API, new pilot

@@ -23,6 +23,17 @@ def connect_mturk(config):
     print("Connected")
     return mturk
 
+def is_suspicious(answer_words):
+
+    suscount = 0
+    for a in answer_words:
+        if a not in WORDS:
+            suscount += 1
+            if suscount >= len(answer_words)/2:
+                return True
+    return False
+
+
 def get_assignments(mturk,hitid):
 
     aresponse = mturk.list_assignments_for_hit(
@@ -36,7 +47,7 @@ def get_assignments(mturk,hitid):
     while anext:
         nresponse = mturk.list_assignments_for_hit(
                     HITId=hitid,NextToken=anext,AssignmentStatuses=['Submitted'])
-        print(nresponse.keys())
+        #print(nresponse.keys())
         nextassign = nresponse['Assignments']
         assignments += nextassign
 
@@ -47,16 +58,6 @@ def get_assignments(mturk,hitid):
             
 
     return assignments
-
-def is_suspicious(answer_words):
-
-    suscount = 0
-    for a in answer_words:
-        if a not in WORDS:
-            suscount += 1
-            if suscount >= len(answer_words)/2:
-                return True
-    return False
 
 def review_results(mturk,path_published):
     '''ask AMT for results'''
@@ -71,8 +72,8 @@ def review_results(mturk,path_published):
         outapproved_name = filename[:-5]+"_approved.txt"
         outsuspicious_name = filename[:-5]+"_suspicious.txt"
 
-        appr_file = open(outapproved_name,'w')
-        susp_file = open(outsuspicious_name,'w')
+        appr_file = open(outapproved_name,'a')
+        susp_file = open(outsuspicious_name,'a')
 
         hit_results = []
 
@@ -87,40 +88,13 @@ def review_results(mturk,path_published):
                 
                 for assignment in assignments:
                     
-
-                    #print("assignment",assignment.keys())
-                    worker_id = assignment['WorkerId']
-                    answer_dict = xmltodict.parse(assignment['Answer'])
-                    #print(answer_dict['QuestionFormAnswers']['Answer'])
-                    #print("Worker,",worker_id)
-                    #print(answer_dict['QuestionFormAnswers'].keys())
-
-                    print("Assignment")
-                    answers = []
-                    for a in answer_dict['QuestionFormAnswers']['Answer']:
-                        param = a['QuestionIdentifier']
-                        if not 'objname-ex' in param:
-                            if 'objname' in param:
-                                if a['FreeText']:
[…]

### 2019-01-30 amt_pilot/amt_api/monitor.py

@@ -21,6 +21,34 @@ def connect_mturk(config):
     print("Connected")
     return mturk
 
+def get_assignments(mturk,hitid):
+
+    aresponse = mturk.list_assignments_for_hit(
+                    HITId=hitid)
+    anext = aresponse['NextToken']
+    assignments = aresponse['Assignments']
+
+    print("get Hit",hitid)
+
+    while anext:
+        nresponse = mturk.list_assignments_for_hit(
+                    HITId=hitid,NextToken=anext)
+        print(nresponse.keys())
+        nextassign = nresponse['Assignments']
+        assignments += nextassign
+
+        if 'NextToken' in nresponse:
+            anext = nresponse['NextToken']
+        else:
+            anext = None
+            
+
+    return assignments
+
+        
+
+
+
 
 def monitor_submission(mturk,path_published):
     '''ask AMT for results'''
@@ -37,9 +65,7 @@ def monitor_submission(mturk,path_published):
 
             if item['HIT']['HITId'] not in known_hits:
 
-                assignments_list = mturk.list_assignments_for_hit(
-                    HITId=item['HIT']['HITId']                )
-                assignments = assignments_list['Assignments']
+                assignments = get_assignments(mturk,item['HIT']['HITId'])
 
                 print("HIT/Assignments",item['HIT']['HITId'],len(assignments))
 

### 2019-01-30 amt_pilot/amt_api/publish.py

@@ -51,7 +51,55 @@ def make_new_hit(n_images,imgdf,img_index):
 
     return param_list,out_img_dict,img_index
 
-def publish_new_hit(mturk,config,hit_params):
+def get_qualifications(config):
+
+    if 'sandbox' in config['endpoint']['url']:
+        print("this is sandbox mode, no qualifications needed")
+        return [] ## no qualifications required in sandbox mode
+
+
+    qlist = [
+        {
+        'QualificationTypeId': '00000000000000000040',
+        'Comparator': 'GreaterThanOrEqualTo',
+        'IntegerValues': [
+            int(config['qualification']['approvedhits']),
+        ],
+        'ActionsGuarded':'PreviewAndAccept'
+        },
+        {
+        'QualificationTypeId': '000000000000000000L0',
+        'Comparator': 'GreaterThanOrEqualTo',
+        'IntegerValues': [
+            int(config['qualification']['approvalrate']),
+        ],
+        'ActionsGuarded':'PreviewAndAccept'
+        },
+        {
+                'QualificationTypeId' : '00000000000000000071',
+                'Comparator' : 'In',
+                'LocaleValues' : [
+                    {'Country':'GB'}, {'Country':'US'},
+                    {'Country':'AU'}, {'Country':'CA'},
+                    {'Country':'IE'}, {'Country':'NZ'} 
+                    ],
+                'ActionsGuarded': 'PreviewAndAccept'
+        },
+        {
+                'QualificationTypeId' : '00000000000000000071',
+                'Comparator' : 'In',
+                'LocaleValues' : [
+                    {'Country':'GB'}, {'Country':'US'},
+                    {'Country':'AU'}, {'Country':'CA'},
+                    {'Country':'IE'}, {'Country':'NZ'} 
+                    ],
+                'ActionsGuarded': 'PreviewAndAccept'
+        }
+    ]
+
+    return qlist
+
+def publish_new_hit(mturk,config,hit_params,hit_quals):
 
     new_hit = mturk.create_hit(
     HITLayoutId    = config['layout']['id'],
@@ -62,16 +110,7 @@ def publish_new_hit(mturk,config,hit_params):
     LifetimeInSeconds = int(config['hit']['lifetime']),
     AssignmentDurationInSeconds = int(config['hit']['assignmentduration']),
     MaxAssignments = int(config['hit']['maxassignments']),
[…]

### 2019-01-30 amt_pilot/amt_api/results.py

@@ -20,6 +20,31 @@ def connect_mturk(config):
     print("Connected")
     return mturk
 
+def get_assignments(mturk,hitid):
+
+    aresponse = mturk.list_assignments_for_hit(
+                    HITId=hitid,
+                    AssignmentStatuses=['Approved'])
+    anext = aresponse['NextToken']
+    assignments = aresponse['Assignments']
+
+    print("get Hit",hitid)
+
+    while anext:
+        nresponse = mturk.list_assignments_for_hit(
+                    HITId=hitid,NextToken=anext,AssignmentStatuses=['Approved'])
+        #print(nresponse.keys())
+        nextassign = nresponse['Assignments']
+        assignments += nextassign
+
+        if 'NextToken' in nresponse:
+            anext = nresponse['NextToken']
+        else:
+            anext = None
+            
+
+    return assignments
+
 
 def get_results(mturk,path_published,path_results):
     '''ask AMT for results'''
@@ -34,11 +59,8 @@ def get_results(mturk,path_published,path_results):
         for item in parsed:
             #print(item)
 
-            assignments_list = mturk.list_assignments_for_hit(
-                HITId=item['HIT']['HITId'],
-                AssignmentStatuses=['Approved']
-            )
-            assignments = assignments_list['Assignments']
+            assignments = get_assignments(mturk,item['HIT']['HITId'])
+
             print("HIT/Assignments",item['HIT']['HITId'],len(assignments))
 
             if len(assignments) > 0:

### 2019-02-02 papers/ACL2019/acl19_naming.tex
separated sections into files, some plans for analysis and reporting

--- 2018-12-20 papers/ACL2019/acl19_naming.tex
@@
 \newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
+\newcommand{\cs}[1]{\textcolor{Fuchsia}{\emph{//cs: #1//}}}
+\newcommand{\gbt}[1]{\textcolor{green}{\emph{//gb: #1//}}}
 \newcommand{\refexp}[1]{\textsl{#1}}
@@
 \newcommand{\vgenome}{VisualGenome\xspace}
+\newcommand{\ra}{$\rightarrow$}
 
 %\title{What do you need to know about a word when you\\ want to use it for naming objects?}
-\title{An object deserves more than a single name}
+%\title{How many times must an object be named (before we know what it is)?}
+
+\title{Object naming on steroids}
 
@@
 \begin{document}
-
 \maketitle
@@
 
-\section{Introduction}
-
-The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of different categories.
-And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
-For instance, the object in Figure \ref{fig:cake} is at once a \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[height=2cm,width=2.5cm]{Figures/cheescake.png}
-\caption{A real-world object in VisualGenome}
-\label{fig:cake}
-\end{center}
-\end{figure}
-
-Given the abundance of concepts available in language, the act of \textit{naming} a visual object is less trivial than it might seem intuitively: in order to describe or refer to an object, a name has to be selected from a complex network of concepts and from many competing lexical alternatives.
-Hence, research on cognition and language production has relied on object naming as a basic paradigm for investigating the processes that underly formation and organization of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}, though mostly using idealized, graphical objects from specific domains (plants, animals) as visual stimuli.
-Complementary to that, research in computer vision has (successfully) focused on automatically recognizing \textit{real-world} objects in images or videos, but using simplified categorization schemes where each object is assigned a single correct label or name, cf.\ \cite{googlenet}.
-%Here, powerful models have been developed recently that classify visual objects in real-world images into thousands of different (mutually exclusive) categories \newcite{googlenet}.
-
-In NLP, to date, research on object naming is relatively scarce despite the fact that
- there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
-At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.
-
-The goal of this paper is to extend some existing, large-scale resources available for language \& vision research in a way that they can serve as a solid and broad empirical basis for investigations into object naming.
-Thus, while large amounts images from different domains paired with verbal descriptions are generally available, none of the existing corpora records more than a few annotations per object.
-Even VisualGenome \cite{krishna2016visualgenome}, one of the most exhaustively annotated resources to date, only provides a single, manually annotated object description (including a single name) per object.
-Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
-object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).
-These two shortcomings - few names per object and inconsistent labeling of categories - make it difficult to assess (i) how representative nmaing choices are, (ii) how they related to the taxonomic properties of the object  ...
-get reliable and stable predictions as to how speakers will likely name a given object.\sz{need to make this point more clear}
-
-\section{Related Work}
-\label{sec:related}
-
-\paragraph{Cognition: Concepts and categorization}
-
- Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
-%with respect to the chose level of specificity. 
-their choice of the level of specificity. 
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating}\cite{graf2016animal}.
-
-\paragraph{Vision: Object Recognition}
-
-State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
-These object recognition systems are now widely used in vision \& language research.
-Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.
-
-\paragraph{Vision \& language: Naming and Referring}
-
-\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
- categories, from the output of an object recognizer.
-Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g.
-involve corpus frequencies.
- \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
- Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.
-
-\paragraph{Existing resources and their shortcomings} summarize SIVL paper here
-
-\section{Data Collection}
-\label{sec:task}
-
-describe the YouNameIt task here
-
-\subsection{Materials} describe sampling of images, category selection
-
-\subsection{Procedure} describe the crowdsourcing set-up and the task
-
-\subsection{Data} give an overview of the collected data
-
-\section{Analysis}
-
-\subsection{Agreement, basic-level and entry-level names}
-
-analyse data mainly from Phase 0
-
-\begin{itemize}
-\item  to what extent do people agree when their task is to give the most straightforward name they can think of to a visual object?
-\item is the level of agreement the same for all categories?
-\item how specific are the most familiar names? link names to WordNet, show that WordNet might not be ideal to assess specificity
-\item how does agreement evolve in the later rounds of the game?
-(when people have to avoid taboo names), does agreement increase as the set of names becomes more narrow, or  does agreement decrease as people do creative, clever, unexpected things?
-\end{itemize}
-
-\subsection{Cases of disagreement}
-
-when and why do people give different names to the same object? this will probably happen in phase 0, and even more so in the later round \sz{this is what I expect}
-
-\begin{itemize}
-\item  analyse naming disagreement using WordNet, how do names for the same object relate to each other according to WordNet?
-\item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
-\item we might need to do some manual annotation here and try to carefully describe the phenomena
-\end{itemize}
-
-\subsection{Taxonomic relations}
-
-can we elicit natural sub-ordinate, super-ordinate concepts?
-
-\section{Model}
-
-\subsection{Model 1}
-Train a simple naming model (classifiers) on original VisualGenome names. Test it on our data. How well does the model predict the most familiar name and the set of available names?
-
-\subsection{Model 2}
-Train a simple naming model (classifiers) on our data, maybe combined with VisualGenome data. How well does it work?
-
-\subsection{Model 3}
-
-can we model taxonomic/conceptual knowledge more directly? induce a taxonomy? or a multi-modal space for objects + names?
-
-\section{Conclusion}
-
-We have presented a systematic, large-scale study on object naming with real-world images and crowdsourced data.
+\input{intro}
+\input{relwork}
+\input{data-collection}
+\input{analysis}
+%\input{modeling}
+\input{conc}
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-02-02 papers/ACL2019/analysis.tex
separated sections into files, some plans for analysis and reporting

\section{Analysis}

\gbt{Note: the structure below is not supposed to be the one in the paper; it was the easiest way for me to plan the analysis a bit}

\subsection{Agreement, basic-level and entry-level names}

analyse data from Phase 0

Items:

\begin{itemize}
\item  to what extent do people agree when their task is to give the most straightforward name they can think of to a visual object? (see \ref{sec:snowgrad})
\item is the level of agreement the same for all categories? (see \ref{sec:snowgrad})
\item how specific are the most familiar names? link names to WordNet, show that WordNet might not be ideal to assess specificity
\item assess how representative name annotations in Visual Genome are, when compared to our names (see \ref{sec:vg})
% \item FOR LATER how does agreement evolve in the later rounds of the game? (when people have to avoid taboo names), does agreement increase as the set of names becomes more narrow, or  does agreement decrease as people do creative, clever, unexpected things?
\end{itemize}

\subsubsection{Agreement: Snowgrad's measure}
\label{sec:snowgrad}

Note: I (Gemma) will use three levels of analysis: ALL (all data lumped together), DOMAIN (Gemma's reorganization of Carina's ``supercategories''; see doc 0\_object\_naming\_taboo), COLLECTION NODE (Carina's ``synset / collection node'').

Plans for analysis (then we see what to put in the paper):

\begin{enumerate}
\item compute snowgrad measure and do a:
  \begin{itemize}
  \item histogram ALL
  \item boxplot by DOMAIN
  \item dataframe with mean and sd by COLLECTION NODE 
  \item[\ra] This will tell us how much agreement there is among subjects about how to name objects in general and within each domain/''subcategory''.
  \end{itemize}
\item can we find generalizations about tendencies in agreement? (open: how to go about it)
\end{enumerate}

\subsubsection{How representative are VG names?}
\label{sec:vg}

Compute the most frequent name for each image and see how often that name coincides with the one given by the VG annotator.

\subsection{Cases of disagreement}

when and why do people give different names to the same object? this will probably happen in phase 0, and even more so in the later round \sz{this is what I expect}

\gbt{Maybe we can fuse this analysis with the one in the next subsection (taxonomic relations). The way I would put it is, instead of disagreement and taxonomy, ``sources of variation''}

\begin{itemize}
\item analyse naming disagreement using WordNet, how do names for the same object relate to each other according to WordNet?Overarching question: 
\item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
\item \cs{Wrt points 1+2: Show that WordNet, again, is not ideal for retrieving all possible names of an object from a single synset.}
\item we might need to do some manual annotation here and try to carefully describe the phenomena
\end{itemize}

\subsection{Taxonomic relations}

can we elicit natural sub-ordinate, super-ordinate concepts?

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

### 2019-02-02 papers/ACL2019/data-collection.tex
separated sections into files, some plans for analysis and reporting

\section{Data Collection}
\label{sec:task}

%describe the YouNameIt task here

describe the task here

\subsection{Materials} describe sampling of images, category selection

Table with:

\begin{itemize}
\item rows: domains (if we go for long paper: then one row per collection node?)
\item columns:
  \begin{enumerate}
  \item \# collection nodes
  \item collection nodes (list)
  \item \# unique VG names
  \item example VG names
  \item \# unique objects
  \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
  \end{enumerate}
\end{itemize}

\subsection{Procedure} describe the crowdsourcing set-up and the task

\subsection{Data} give an overview of the collected data

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

### 2019-02-02 papers/ACL2019/intro.tex
separated sections into files, some plans for analysis and reporting

\section{Introduction}

The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.

\begin{figure}[htbp]
\begin{center}
\includegraphics[height=3cm]{Figures/cheescake.png}
\includegraphics[height=3cm]{Figures/cheesecak2.pdf}
\caption{Two objects of the same type of cake, with different names in VisualGenome}
\label{fig:cake}
\end{center}
\end{figure}

Given the abundance of concepts available in language, the act of \textit{naming} a visual object is not just a labeling of visible properties, it amounts to selecting a name from a complex network of concepts and competing lexical alternatives.
Hence, research on cognition and language production has relied on object naming as a basic paradigm for investigating the processes that underly formation and organization of concepts in the human mind  \cite{rosch1976basic} \sz{cite more here}, though mostly using idealized, graphical objects from specific domains (plants, animals) as visual stimuli.
Complementary to that, research in computer vision has (successfully) focused on automatically recognizing \textit{real-world} objects in images or videos, but using simplified categorization schemes where each object is assigned a single correct label or name, cf.\ \cite{googlenet}. %Here, powerful models have been developed recently that classify visual objects in real-world images into thousands of different (mutually exclusive) categories \newcite{googlenet}.

In NLP, to date, research on object naming is relatively scarce despite the fact that
 there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}. Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test bed for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
%In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
%At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.

The goal of this paper is to extend Visual Genome  \cite{krishna2016visualgenome}, a well-known, large-scale resource in language \& vision research, in a way that it can serve as a broad empirical basis for systematic and linguistically motivated investigations into object naming. 
We argue that object naming is an interesting, core phenomenon in itself as it occurs in virtually every L\&V task, but our approach can also support more systematic analysis of broader tasks, such as e.g.\ modeling referring expressions.

Even though VisualGenome is one of the most exhaustively annotated resources to date, providing dense object annotations and descriptions in real-world images, it suffers from two important shortcomings if one is interested in linguistic analysis of object naming:  
First, it only provides a single, manually annotated object description (including a single name) per object which makes it impossible to assess how representative the annotated naming choices are, e.g.\ whether speakers tend to generally prefer \refexp{cheesecake} for the highlighted object in Figure \ref{fig:cake}.
Second, it does not provide consistent taxonomic information on objects and their categories, as names have been automatically linked to WordNet synsets. 
This makes it difficult to assess how naming depends on the taxonomic properties of the object, e.g.\  that both objects in Figure \ref{fig:cake} are instances of \cat{cheesecake}, but one is named \refexp{cheesecake} and the other one is named \refexp{desert}. It is important to note here that these shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).

In this work, we address these two shortcomings and present a crowdsourcing-based and light-weight experimental set-up for eliciting representative and taxonomically consistent (\sz{more complete?}) naming data. We compare our collected data against names annotated in Visual Genome, and calculate various measures assessing agreement, naming preferences etc.

The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names. We show that this simple, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

### 2019-02-02 papers/ACL2019/modeling.tex
separated sections into files, some plans for analysis and reporting

\section{Model}

\subsection{Model 1}
Train a simple naming model (classifiers) on original VisualGenome names. Test it on our data. How well does the model predict the most familiar name and the set of available names?

\subsection{Model 2}
Train a simple naming model (classifiers) on our data, maybe combined with VisualGenome data. How well does it work?

\subsection{Model 3}

can we model taxonomic/conceptual knowledge more directly? induce a taxonomy? or a multi-modal space for objects + names?

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

### 2019-02-02 papers/ACL2019/relwork.tex
separated sections into files, some plans for analysis and reporting

\section{Related Work}
\label{sec:related}

\paragraph{Cognition: Concepts and categorization}

 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating,graf2016animal}.

\paragraph{Vision: Object Recognition}

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.}

\paragraph{Vision \& language: Naming and Referring}

\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
 categories, from the output of an object recognizer. Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g. involve corpus frequencies. 
 \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
 Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.

\paragraph{Existing resources and their shortcomings}
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl19_naming"
%%% End:

### 2019-02-24 analysis/gemmas-analysis.py
setting up Gemma's analysis scripts

@@ -1,0 +1,42 @@
+# -*- coding: utf-8 -*-
+
+# created gbt Sun Feb 24 2019
+
+import pandas as pd
+import numpy as np
+import os
+#from collections import Counter
+from utils_analysis import *
+
+df=pd.read_csv("../data_phase0/results-created_2019-Feb-20_13_36_05_final.csv",sep="\t")
+print(df.head())
+print(df.columns)
+
+#TO DO (from paper files)
+#
+#analyse data from Phase 0
+#
+#Items:
+#
+#\begin{itemize}
+#\item  to what extent do people agree when their task is to give the most straightforward name they can think of to a visual object? (see \ref{sec:snowgrad})
+#\item is the level of agreement the same for all categories? (see \ref{sec:snowgrad})
+#\item how specific are the most familiar names? link names to WordNet, show that WordNet might not be ideal to assess specificity
+#\item assess how representative name annotations in Visual Genome are, when compared to our names (see \ref{sec:vg})
+#\end{itemize}
+#
+#
+#Note: I (Gemma) will use three levels of analysis: ALL (all data lumped together), DOMAIN (Gemma's reorganization of Carina's ``supercategories''; see doc 0\_object\_naming\_taboo), COLLECTION NODE (Carina's ``synset / collection node'').
+# 
+#Plans for analysis (then we see what to put in the paper):
+#
+#\begin{enumerate}
+#\item compute snowgrad measure and do a:
+#  \begin{itemize}
+#  \item histogram ALL
+#  \item boxplot by DOMAIN
+#  \item dataframe with mean and sd by COLLECTION NODE 
+#  \item[\ra] This will tell us how much agreement there is among subjects about how to name objects in general and within each domain/''subcategory''.
+#  \end{itemize}
+#\item can we find generalizations about tendencies in agreement? (open: how to go about it)
+#\end{enumerate}

### 2019-02-25 analysis/load_results.py
updating load_results; adding 3 json result files.

@@ -9,7 +9,7 @@ import numpy as np
 #from spellchecker import SpellChecker
 #from nltk.stem.wordnet import WordNetLemmatizer
 
-def process_answers(resultfile,hit2images):
+def process_answers(resultfile, hit2images, with_opt_outs=False):
     
     with open(resultfile, 'r') as handle:
         resultlist = json.load(handle)
@@ -22,6 +22,7 @@ def process_answers(resultfile,hit2images):
         print(hitid)
         for a in assignm['Assignments']:
             #print(a)
+            workerId = a['WorkerId']
             answers = a['Answers']
             for ix in range(10):
                 object_id = hit2images[hitid][str(ix)][1]
@@ -33,6 +34,11 @@ def process_answers(resultfile,hit2images):
                 if name:
                     name = name.lower()
                     obj2answers[object_id][name] += 1
+                elif with_opt_outs:
+                    opt_out = "#"+answers[str(ix)]['optout-'+str(ix)]
+                    if answers[str(ix)]['other_reasons-'+str(ix)]:
+                        opt_out += "_" + answers[str(ix)]['other_reasons-'+str(ix)]
+                    obj2answers[object_id][opt_out] += 1
                     
                     
     ## optional: spell checking

### 2019-02-26 dataset_creation/scripts/annotation_utils.py
reorganises collected data folder (data_phase0)

@@ -12,7 +12,7 @@ folders = os.path.abspath(".").split(os.sep)
 if "\\" in os.sep:
     USRNAME = "C:\\Users\\Carina Silberer\\"
 elif "/" in os.sep:
-    USRNAME = folders[folders.index("media")+1] #"u148188"
+    USRNAME = "/home/u148188/"
 
 stanford_dir = '/home/%s/models/' % (USRNAME)
 '/home/carina/models/stanford-postagger-full-2018-02-27/'

### 2019-02-26 analysis/load_results.py
Add files via upload

@@ -9,8 +9,32 @@ import numpy as np
 #from spellchecker import SpellChecker
 #from nltk.stem.wordnet import WordNetLemmatizer
 
+def load_resultsdata_csv(datafile_csv):
+    fulldf = pd.read_csv(datafile_csv, sep="\t")
+    fulldf[["responses"]] = fulldf["responses"].apply(lambda a: eval(a))
+    return fulldf
+
+def _img2objname_map(imgdf):
+    # meta file used to publish the hits
+    img2names_map = dict()
+    for (idx, row) in imgdf.iterrows():
+        img2names_map[str(row.image_id)+"_"+str(row.object_id)] = (row.obj_names, row.category)
+    return img2names_map
+
+def add_objnames_categories(fulldf, img2names_map):
+    fulldf["sample_type"] = fulldf["cat"]
+    obj_names = []
+    obj_cats = []
+    for (idx, row) in fulldf.iterrows():
+        name_cat = img2names_map.get(str(row.vg_img_id)+"_"+str(row.vg_object_id), ["UNK", "UNK"])
+        obj_names.append(name_cat[0])
+        obj_cats.append(name_cat[1])
+    fulldf["obj_name"] = obj_names
+    fulldf["cat"] = obj_cats
+    return fulldf
+
+
 def process_answers(resultfile, hit2images, with_opt_outs=False):
-    
     with open(resultfile, 'r') as handle:
         resultlist = json.load(handle)
     
@@ -19,8 +43,9 @@ def process_answers(resultfile, hit2images, with_opt_outs=False):
     
     for assignm in resultlist:
         hitid = assignm['HITId']
-        print(hitid)
+        #print(hitid)
         for a in assignm['Assignments']:
+            skip_assignment = False
             #print(a)
             workerId = a['WorkerId']
             answers = a['Answers']
@@ -35,30 +60,40 @@ def process_answers(resultfile, hit2images, with_opt_outs=False):
                     name = name.lower()
                     obj2answers[object_id][name] += 1
                 elif with_opt_outs:
-                    opt_out = "#"+answers[str(ix)]['optout-'+str(ix)]
-                    if answers[str(ix)]['other_reasons-'+str(ix)]:
-                        opt_out += "_" + answers[str(ix)]['other_reasons-'+str(ix)]
-                    obj2answers[object_id][opt_out] += 1
-                    
+                    try:
+                        opt_out = "#"+answers[str(ix)]['optout-'+str(ix)]
[…]

### 2019-03-01 papers/ACL2019/data-collection.tex
change paper title, minor changes

@@
 
-\subsection{Materials} describe sampling of images, category selection
+\subsection{Visual Genome data}
+
+\gbt{to be refined -- taken from sivl submission as is}
+
+\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
+
+\begin{itemize}
+     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
+				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
+		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+
+\end{itemize}
+
+describe sampling of images, category selection
 
@@
 
-\begin{itemize}
-\item rows: domains (if we go for long paper: then one row per collection node?)
-\item columns:
-  \begin{enumerate}
-  \item \# collection nodes
-  \item collection nodes (list)
-  \item \# unique VG names
-  \item example VG names
-  \item \# unique objects
-  \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
-  \end{enumerate}
-\end{itemize}
+% \begin{itemize}
+% \item rows: domains (if we go for long paper: then one row per collection node?)
+% \item columns:
+%   \begin{enumerate}
+%   \item \# collection nodes
+%   \item collection nodes (list)
+%   \item \# unique VG names
+%   \item example VG names
+%   \item \# unique objects
+%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
+%   \end{enumerate}
+% \end{itemize}
 
@@
 %%% mode: latex
-%%% TeX-master: "acl19_naming"
+%%% TeX-master: "main"
 %%% End:

### 2019-03-04 analysis/load_results.py
adds function to load several csv result files from directory into one DF

@@ -1,18 +1,31 @@
-import pandas as pd
-import glob
-import os
-import json
-#import xmltodict
-import sys
 from collections import Counter
+import glob
+import json
+import os
+import re
+import sys
+
+#import xmltodict
+
 import numpy as np
+import pandas as pd
 #from spellchecker import SpellChecker
 #from nltk.stem.wordnet import WordNetLemmatizer
 
 def load_resultsdata_csv(datafile_csv):
+    if os.path.isdir(datafile_csv):
+        return load_all_results_csv(datafile_csv)
     fulldf = pd.read_csv(datafile_csv, sep="\t")
     fulldf[["responses"]] = fulldf["responses"].apply(lambda a: eval(a))
     return fulldf
+    
+def load_all_results_csv(data_dir):
+    res_patt =  re.compile("results-created.+?_final\.csv")
+    csv_files = [f for f in os.listdir(data_dir) if res_patt.match(f)]
+    all_dfs = []
+    for csv_file in csv_files:
+        all_dfs.append(load_resultsdata_csv(os.path.join(data_dir, csv_file)))
+    return pd.concat(all_dfs, ignore_index=True, sort=False)
 
 def _img2objname_map(imgdf):
     # meta file used to publish the hits

### 2019-05-03 analysis/prune_data_postcheckpoint_phase0.py
adds csv with collected data for all rounds 0-3

@@ -64,7 +64,7 @@ if __name__=="__main__":
     pruned_df.to_csv("results/pruned_df_%s.csv" % (param_str),
                     sep="\t", float_format='%.2f')
     
-    ## FAVOURITE: Option 2b (apply plural filter also to food)
+    ## SELECTED: Option 2b (apply plural filter also to food)
     MAX_OCCL = 0
     MAX_BBOX = 2
     MAX_PLURALS = 0.17

### 2019-05-03 dataset_creation/scripts/annotation_utils.py

@@ -172,6 +172,7 @@ def get_ss_from_offset(offset):
     >>> get_synset_from_offset('n02084071')
     Synset('dog.n.01')
     """
+    print(offset[1:], offset[0], offset)
     if not offset[0].isdigit():
         offset = offset[1:] + "-" + offset[0]
     return wn.of2ss(offset)
@@ -234,6 +235,12 @@ def get_subtree(synset):
 
 def get_all_hypernyms(synset):
     return synset.hypernym_paths()
+
+def get_hyponyms(synset):
+    return synset.hyponyms()
+
+def get_hypernyms(synset):
+    return synset.hypernyms()
 
 def get_all_hypernyms_ids(synset):
     all_hypers = synset.hypernym_paths()

### 2019-05-03 analysis/merge_rounds.py
script: merge data of rounds

@@ -1,0 +1,68 @@
+import os
+import re
+import sys
+from collections import Counter, defaultdict
+
+import numpy
+import pandas
+
+import matplotlib.pyplot as plt
+from matplotlib.pyplot import figure
+figure(num=None, figsize=(8, 6), dpi=80, facecolor='w', edgecolor='k')
+
+import load_results
+# TODO: improve mapping
+from  preprocess_results import get_name2domain_map, name2domain
+
+BASE_DIR = os.path.dirname(os.getcwd())
+
+
+if __name__=="__main__":
+    if len(sys.argv) < 2:
+        sys.stderr.write("Please provide results files to be merged.\n")
+        sys.exit()
+        
+    """
+    cols = ['vg_img_id', 'vg_object_id', 'cat', 'synset', 
+            'vg_obj_name', 'responses', 'opt-outs', 
+            'vg_domain', 'top_response_domain', 'responses_domains',                
+            'url', 'sample_type']
+    """
+    df_list = []
+    #"/home/u148188/object_naming/amt_phase0/result_files_rounds0-2/"
+    if os.path.isdir(sys.argv[1]):
+        result_files = []
+        for res_dir in sys.argv[1:]:
+            result_files.extend([os.path.join(res_dir, fname) for fname in os.listdir(res_dir) if (not os.path.isdir(os.path.join(res_dir, fname)) and "_final" in fname)])
+    else:
+        result_files = sys.argv[1:]
+
+    round_idx = 0
+    round_inds = []
+    for res_csvs in result_files:
+        print(res_csvs)
+        round_idx = int(re.search("_round([0-9]+)\.csv", res_csvs).group(1))
+        round_inds.append(round_idx)
+        df = load_results.load_preprocessed_results_csv(res_csvs)
+        
+        if "Unnamed: 0" in df.columns:
+            df.drop(columns=["Unnamed: 0"], axis=1, inplace=True)
+        for col_name in df.columns:
+            if "response" in col_name:
+                new_col_name = col_name + "_r%d" % round_idx
+                df.rename(columns={col_name: new_col_name}, inplace=True)
+                
+        df.set_index(["vg_object_id"], inplace=True)
+        df_list.append(df)
+
+    cols_to_use = []
+    merged_df = df_list[0]
+    for df in df_list[1:]:
+        cols_to_use = df.columns.difference(df_list[0].columns)
[…]

### 2019-05-06 analysis/agreement_table.py
scripts for spellchecking and calculating agreement

@@ -1,0 +1,95 @@
+import pandas as pd
+import glob
+import os
+import json
+import sys
+from collections import Counter
+import numpy as np
+
+def snodgrass_agreement(rdict,vocab,singletons=False):
+
+    # to decide: do we include singleton answers for calculating agreement?
+    if singletons:
+        vec = np.array([rdict[key] for key in rdict])
+    else:
+        vec = np.array([rdict[key] for key in rdict if vocab[key] > 1])
+    vec_rel = vec/(np.sum(vec))
+
+
+    agr = np.sum(vec_rel * np.log2(1/vec_rel)) ## check whether this is correct
+
+    return agr
+
+def percent_agreement(rdict):
+
+    # to decide: do we include singleton answers for calculating agreement?
+    topname = rdict.most_common(1)[0][0]
+    total = sum(rdict.values())
+    return rdict[topname]/total
+
+def make_df(filename):
+    resdf = pd.read_csv(filename,sep="\t")
+    resdf['spellchecked'] = resdf['spellchecked'].apply(lambda x: Counter(eval(x)))
+    resdf['clean'] = resdf['clean'].apply(lambda x: Counter(eval(x)))
+    resdf['canon'] = resdf['canon'].apply(lambda x: Counter(eval(x)))
+
+    vocab_counter = Counter()
+    vg_is_common = []
+
+    for ix,row in resdf.iterrows():
+
+        vocab_counter += row['spellchecked']
+        max_name = row['spellchecked'].most_common(1)[0][0]
+        vg_is_common.append(int(max_name == row['vg_obj_name']))
+
+    resdf['vg_is_max'] = vg_is_common
+
+    return resdf
+
+fn = 'all_responses_round0-3_cleaned.csv'
+resdf = make_df(fn)
+
+resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
+resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
+nobjects = len(resdf)
+
+tablerows = []
+tablerows.append(('all',\
+
+                 str("%.2f"%np.mean(resdf['percent_agree'])),\
+                 str("%.2f"%np.mean(resdf['snodgrass'])),\
+                 str("%.2f"%(np.sum(resdf['vg_is_max'])/nobjects))))
+
+for c in set(list(resdf['cat'])):
+    catdf = resdf[resdf['cat'] == c]
[…]

### 2019-05-06 papers/EMNLP2019/many_names.tex
EMNLP paper draft files

%
% File emnlp2019.tex
%
%% Based on the style files for ACL 2019, which were
%% Based on the style files for EMNLP 2018, which were
%% Based on the style files for ACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp-ijcnlp-2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}  %%% for including graphics
\usepackage{booktabs}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP-IJCNLP 2019}
\newcommand\conforg{SIGDAT}

\title{Instructions for \confname{} Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
\end{abstract}

\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}

\section{Introduction}

The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories. And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy. For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc. Hence, when speakers name objects, e.g.\ when referring, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.

\begin{figure}[htbp]
\begin{center}
\includegraphics[height=3cm]{Figures/cheescake.png}
\includegraphics[height=3cm]{Figures/cheesecak2.pdf}
\caption{Two objects of the same type of cake, with different names in VisualGenome}
\label{fig:cake}
\end{center}
\end{figure}

To date, research in NLP has surprisingly little to say about object naming, despite the fact that
 there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}. 
In contrast, closely related areas, such as computer vision and cognitive science, have investigated very related tasks in quite some depth: object recognition systems developed in the area of computer vision  are now able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
Furthermore, work on concepts, following the seminal work by Rosch, suggests that objects are typically conceptualized at a preferred level of specificity called the \textbf{entry-level}. Psycho-linguistic studies have been able to support this theory based on collections of so-called object naming norms.

This paper aims at addressing the genuinely linguistic questions revolving around the phenomenon of object naming by (i) presenting a collection of high-quality, large-scale naming data,  and (ii) analysis methods for this data and (iii) a first baseline model that accounts for the semantic flexibility of names for objects in real-world images. From computer vision, we borrow the idea of modeling realistic visual objects in realistic scenes (real-world images), but go beyond the simplistic assumption that object names correspond to unambiguous labels in a flat classification scheme (with no conceptual relations between the labels). From psycholinguistics, we borrow the idea of eliciting natural, representative naming data from many subjects, but go beyond using artificial, highly stylized objects.

\section{Related Work}

\section{Analysis}

\subsection{Agreement}

We compute the following agreement measures:

\begin{itemize}
\item \textbf{top \%}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
\item \textbf{SD \%}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects
\item \textbf{=VG}: the proportion of objects where the most frequent name coincides with the name annotated in VisualGenome
\end{itemize}

\begin{table*}
\small
\begin{tabular}{llll|llll|llll}
\toprule
    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
                         domain & \% top &    SD &   =VG &         id &     \% top &    SD &   =VG &             id &     \% top &    SD &   =VG \\
\midrule
                           person &  0.52 &  2.14 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.34 &  2.67 &  0.36 \\
                        tableware &  0.52 &  1.92 &  0.40 &      crockery.n.01 &  0.52 &  1.92 &  0.40 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
              clothing &  0.64 &  1.59 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
 instruments &  0.66 &  1.52 &  0.79 &    furnishing.n.02 &  0.67 &  1.50 &  0.80 &   kitchen\_utensil.n.01 &  0.60 &  1.85 &  0.56 \\
                solid food &  0.67 &  1.43 &  0.56 &   baked\_goods.n.01 &  0.67 &  1.43 &  0.56 &       baked\_goods.n.01 &  0.67 &  1.43 &  0.56 \\
          structure &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
       %                       all &  0.70 &  1.35 &  0.73 &               None &  None &  None &  None &                   None &  None &  None &  None \\
                          vehicle &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.43 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
                   food, nutrient &  0.72 &  1.27 &  0.68 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.52 &  1.99 &  0.15 \\
         plants &  0.79 &  0.86 &  0.73 &        flower.n.01 &  0.79 &  0.86 &  0.73 &            flower.n.01 &  0.79 &  0.86 &  0.73 \\
                             ware &  0.82 &  0.96 &  0.94 &       cutlery.n.02 &  0.82 &  0.96 &  0.94 &           cutlery.n.02 &  0.82 &  0.96 &  0.94 \\
                             tool &  0.86 &  0.73 &  0.94 &          tool.n.01 &  0.86 &  0.73 &  0.94 &              tool.n.01 &  0.86 &  0.73 &  0.94 \\
                           animal &  0.91 &  0.43 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
\bottomrule
 all &  0.70 &  1.35 &  0.73            \\

\bottomrule
\end{tabular}
\caption{Agreement in object names for objects of different domains, if applicable, synsets with maximal and minimal agreement (top \%) are shown }
\label{tab:agree}
\end{table*}

Table \ref{tab:agree} shows that, overall, our annotators achieve a fair amount of agreement in the object naming choices. The domain where annotators agree most is the animal domain, which, interestingly, happens to be the domain that has been mostly discussed in the object naming literature. \sz{... much more to say}

\subsection{Disagreement}

Why and when do speakers disagree in their object naming choices. We first propose a qualitative analysis here.

\begin{itemize}
\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
\item \textbf{taxonomic levels}: e.g.\ man vs. person
\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
\end{itemize}

Can we tease these types of disagreements apart automatically, using WordNet?

\end{document}

### 2019-05-06 papers/ACL2019/intro.tex
all recent changes

@@
 For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
+Hence, when speaker name objects, e.g.\ when referring to it, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.
 
@@
 
-The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names.
-We show that this simple, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.
+The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of,
 

### 2019-05-06 papers/EMNLP2019/many_names.tex
small change, text git integration
updates in spellchecking, new findings in analysis

@@
 
-\subsection{Disagreement}
+Why is naming more flexible in certain domains than in others?
 
-Why and when do speakers disagree in their object naming choices. We first propose a qualitative analysis here.
+\subsection{Lexical relations}
+
+In this section, we take a closer look at the lexical variation we observe in our data set.
+We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
+These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
+For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
+\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
+w_n$ constitute the less frequent alternatives of $w_{top}$.
+The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
+The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
+In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain. \sz{domains need to be updated}
+
+The naming variants can be grouped according to their lexical relation, as follows:
 
 \begin{itemize}
-\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
-\item \textbf{taxonomic levels}: e.g.\ man vs. person
-\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
-\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
+\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
+\item \textbf{hyponymy}: e.g.\ man vs. person
+\item \textbf{co-hyponymy}: e.g.\ chicken vs. dinner, swan vs. goose
+\item \textbf{no relation}: e.g.\  desk vs. apple
 \end{itemize}
+
+\begin{table}
+\small
+\begin{tabular}{llll}
+\toprule
+        relation & \% types & \% tokens & av. depth \\
+\midrule
+ co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
+    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
+        synonymy &  0.015 &  0.121 &       1.000 \\
+\bottomrule
+\end{tabular}
+\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?}}
+\label{tab:rel}
+\end{table}
+
+Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).
+
+We use WordNet to extract lexical relations between the naming variants in our data set.
+Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below).
+Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy.
+For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
+
+\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.}
+
+Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet, for types and tokens of naming variants respectively.
+\sz{Is it clear what types and tokens mean here?
+probably not...}
+
+\subsection{Issues with WordNet}
+
+%\begin{itemize}
+%\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
+%\item \textbf{taxonomic levels}: e.g.\ man vs. person
+%\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
+%\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
+%\end{itemize}
 
@@
 
+\begin{table*}
+\small
+\begin{tabular}{lp{12cm}}
+\toprule
+                         category &                                                                                                                                                                                                                    most frequent naming variants \\
+\midrule
+ food, solid food &  sandwich -- food (492), hotdog -- food (467), hotdog -- sandwich (318), cake -- food (265), bread -- sandwich (257), bread -- food (247), bread -- bun (206), donut -- food (188), hotdog -- bun (184), sandwich -- burger (163) \\
+ structure, construction &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
+ tool &  knife -- pizza (27), knife -- food (22), knife -- cake (17), knife -- banana (16), knife -- plate (15), knife -- apple (13), knife -- pocket knife (12), knife -- butter knife (12), knife -- table (10), knife -- carrot (8) \\
+ vehicle &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
+ plant, flora, plant life &  flower -- flowers (29), rose -- flower (25), flower -- rose (22), flower -- vase (18), flowers -- flower (14), flower -- dandelion (14), plant -- flower (12), flower -- sunflower (11), plant -- wheat (11), flower -- flower pot (10) \\
+ food, nutrient &  pizza -- food (1796), sandwich -- food (631), pizza -- cheese (447), pizza -- plate (423), salad -- food (402), sandwich -- burger (235), pizza -- toppings (217), pizza -- pizza slice (162), sandwich -- bread (156), food -- sandwich (147) \\
+ tableware &  cup -- mug (146), mug -- cup (104), cup -- coffee (93), cup -- drink (73), bowl -- food (60), cup -- glass (39), bowl -- cup (36), glass -- wine glass (35), glass -- cup (34), cup -- coffee cup (31) \\
+ article of clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
+ animal &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
+ ware &  fork -- spoon (71), fork -- plate (44), spoon -- food (32), fork -- food (31), fork -- cake (21), spoon -- fork (18), spoon -- wooden spoon (15), fork -- broccoli (15), fork -- silverware (10), spoon -- vegetables (8) \\
+ person &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
+ instrumentality, instrumentation &  couch -- sofa (4090), desk -- table (3435), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
+\bottomrule
+\end{tabular}\caption{Most frequent naming variants for each category}
+\label{tab:exvariants}
+\end{table*}
+
 \end{document}

### 2019-05-06 analysis/agreement_table.py

@@ -46,50 +46,53 @@ def make_df(filename):
 
     return resdf
 
+def make_agreement_table(resdf):
+    resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
+    resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
+    nobjects = len(resdf)
+
+    tablerows = []
+    tablerows.append(('all',\
+
+                     str("%.2f"%np.mean(resdf['percent_agree'])),\
+                     str("%.2f"%np.mean(resdf['snodgrass'])),\
+                     str("%.2f"%(np.sum(resdf['vg_is_max'])/nobjects))))
+
+    for c in set(list(resdf['cat'])):
+        catdf = resdf[resdf['cat'] == c]
+        ncat = len(catdf)
+
+        synagree = Counter()
+        for s in set(list(catdf['synset'])):
+            syndf = catdf[catdf['synset'] == s]
+            synagree[s] = np.mean(syndf['percent_agree'])
+        print(c)
+        print(synagree)
+        topsyn = synagree.most_common(1)[0][0]
+        botsyn = synagree.most_common()[:-1-1:-1][0][0]
+
+        topdf = catdf[catdf['synset'] == topsyn]
+        botdf = catdf[catdf['synset'] == botsyn]
+
+        tablerows.append((c,\
+
+                         str("%.2f"%np.mean(catdf['percent_agree'])),\
+                         str("%.2f"%np.mean(catdf['snodgrass'])),\
+                         str("%.2f"%(np.sum(catdf['vg_is_max'])/ncat)),\
+                         topsyn,
+                         str("%.2f"%np.mean(topdf['percent_agree'])),\
+                         str("%.2f"%np.mean(topdf['snodgrass'])),\
+                         str("%.2f"%(np.sum(topdf['vg_is_max'])/len(topdf))),\
+                         botsyn,
+                         str("%.2f"%np.mean(botdf['percent_agree'])),\
+                         str("%.2f"%np.mean(botdf['snodgrass'])),\
+                         str("%.2f"%(np.sum(botdf['vg_is_max'])/len(botdf)))\
+                         ))
+
[…]

### 2019-05-06 papers/EMNLP2019/many_names.tex
a really sketchy intro, not entirely happy yet

@@
 
-The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories.
-And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
-For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
-Hence, when speakers name objects, e.g.\ when referring, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.
+Expressions describing or referring to objects in visual scenes typically include a word naming the type of the object: e.g.,  \emph{cheesecake} or  \emph{dessert}  in Figure~\ref{fig:ex1}. 
+Determining these objects names is a core aspect of virtually every language \& vision task, ranging from e.g.\ referring expression generation to visual dialogue.
+Nevertheless, research in language \& vision has mostly  sidestepped questions about how speakers actually choose these names and how computational models should account for it.
+
+While state-of-the-art computer vision systems are able to accurately classify images into thousands of different categories (e.g.\  \newcite{googlenet}), they mostly adopt very simple assumptions with respect to the underlying lexicon, which is typically implemented as a simple, flat labeling scheme.
+Thus, a standard object recognition system would be trained to classify the objects in Figure~\ref{fig:cake} as either  \emph{dessert} or \emph{cake}.
+In contrast, humans seem to be more flexible as to the chosen level of generality and to the chosen part of the taxonomy (see objects in Figure \ref{fig:cake} that could be named \refexp{cake}, \refexp{cheesecake}, \refexp{dessert}, \refexp{sweet}, \refexp{pastry}, \refexp{food} etc.)
+Seminal work on prototypes suggests that the prototypicality of the object will determine the level of generality of the object name, i.e.\  a robin can be named \emph{bird}, but a penguin is better referred to as ``\emph{penguin}'' \cite{Rosch1978}.
+
+%To date, surprisingly little work has been done on testing such theoretical predictions on large-scale, language \& vision data sets and integrating them explicitly into modeling frameworks.
 
@@
 
-To date, research in NLP has surprisingly little to say about object naming, despite the fact that
- there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In contrast, closely related areas, such as computer vision and cognitive science, have investigated very related tasks in quite some depth: object recognition systems developed in the area of computer vision  are now able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
-Furthermore, work on concepts, following the seminal work by Rosch, suggests that objects are typically conceptualized at a preferred level of specificity called the \textbf{entry-level}.
+\sz{something is missing here .. explain why exactly we did what we did, why is it interesting to collect many names for the same object?}
+
+There are two main findings:
+
+\begin{itemize}
+\item the level of agreement in object naming is much higher in certain domains than in others, as it happens, the domains that have been traditionally used in object naming research (e.g.
+animals) seem to display the highest amount of agreement in our data set
+\item while previous work has mostly focussed on variation in the level of generality (\emph{penguin} vs.
+\emph{bird}), our datasets contains a lot of variability for names coming from different parts of the taxonomy (\emph{dessert} vs.
+\emph{cake}, \emph{bottle} vs.
+\emph{wine})
+\end{itemize}
+
+%The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories.
+And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
+For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
+Hence, when speakers name objects, e.g.\ when referring, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.
+
+%To date, research in NLP has surprisingly little to say about object naming, despite the fact that
+% there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
+%In contrast, closely related areas, such as computer vision and cognitive science, have investigated very related tasks in quite some depth: object recognition systems developed in the area of computer vision  are now able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
+%Furthermore, work on concepts, following the seminal work by Rosch, suggests that objects are typically conceptualized at a preferred level of specificity called the \textbf{entry-level}.
 Psycho-linguistic studies have been able to support this theory based on collections of so-called object naming norms.
-
-This paper aims at addressing the genuinely linguistic questions revolving around the phenomenon of object naming by (i) presenting a collection of high-quality, large-scale naming data,  and (ii) analysis methods for this data and (iii) a first baseline model that accounts for the semantic flexibility of names for objects in real-world images.
+%
+%This paper aims at addressing the genuinely linguistic questions revolving around the phenomenon of object naming by (i) presenting a collection of high-quality, large-scale naming data,  and (ii) analysis methods for this data and (iii) a first baseline model that accounts for the semantic flexibility of names for objects in real-world images.
 From computer vision, we borrow the idea of modeling realistic visual objects in realistic scenes (real-world images), but go beyond the simplistic assumption that object names correspond to unambiguous labels in a flat classification scheme (with no conceptual relations between the labels).
@@
 For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
+\sz{should we call this co-hyponymy or co-hierarchical relation?}
 
@@
 
-Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet, for types and tokens of naming variants respectively.
-\sz{Is it clear what types and tokens mean here?
-probably not...}
+Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
+Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
+\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
+This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
+Our data suggests that co-hierarchical variation is really important too.
 
@@
 
-%\begin{itemize}
-%\item \textbf{synonyms}: e.g.\ aircraft vs. airplane 
-%\item \textbf{taxonomic levels}: e.g.\ man vs. person
-%\item \textbf{cross-classification}: e.g.\ chicken vs. dinner
-%\item \textbf{conceptual disagreement}: e.g.\ swan vs. goose
-%\end{itemize}
+Some (interesting, somewhat cherry-picked) word pairs were WordNet does not find any relation (excluded in the above analysis):
 
-Can we tease these types of disagreements apart automatically, using WordNet?
+\begin{itemize}
+\item lettuce -- salad
+\item fruit -- food
+\item man -- catcher
+\item bowl --chili
+\item bowl -- diner
+\item burger -- meat
+\item statue -- animal (image shows statue of an animal)
+\item bottle -- alcohol
+\item donut --desert
+\item zebra -- stripes
+\item oven -- grill
+\end{itemize}
+
+\sz{discuss...}
+
+\subsection{Entry-level names and preference orders....}
+
+\sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}.
+For 50\% of these images, annotators still prefer \textit{bird} as the most common name.
+According to the theory of entry-level categories, this should not happen.
+People should always prefer \textit{penguin} over \textit{bird}.
+
+\sz{how can we analyze this quantitatively?}
 
@@
 
+\subsection{Co-hyponyms as names for objects}
+
+\sz{analyze and discuss why we find so many co-hyponyms in our data set}
+
+\section{Modeling}
+
+\sz{I think, the prevalence of co-hyponymy is the most interesting finding. Can we learn to predict whether to co-hyponyms can be used to name the same object?}
+
 \end{document}

### 2019-05-07 papers/EMNLP2019/many_names.tex
additional comment in the intro
update column for vg domain

@@
 
+Two main findings in the literature:
+
+\begin{itemize}
+\item very high agreement, most people use the same name for the same object
+\item prototypicality is a factor, context too, but research has only looked at generality/specificity of the name
+\end{itemize}
+
 \sz{something is missing here .. explain why exactly we did what we did, why is it interesting to collect many names for the same object?}
@@
 \midrule
-                           person &  0.52 &  2.14 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.34 &  2.67 &  0.36 \\
-                        tableware &  0.52 &  1.92 &  0.40 &      crockery.n.01 &  0.52 &  1.92 &  0.40 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
-              clothing &  0.64 &  1.59 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
- instruments &  0.66 &  1.52 &  0.79 &    furnishing.n.02 &  0.67 &  1.50 &  0.80 &   kitchen\_utensil.n.01 &  0.60 &  1.85 &  0.56 \\
-                solid food &  0.67 &  1.43 &  0.56 &   baked\_goods.n.01 &  0.67 &  1.43 &  0.56 &       baked\_goods.n.01 &  0.67 &  1.43 &  0.56 \\
-          structure &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
-       %                       all &  0.70 &  1.35 &  0.73 &               None &  None &  None &  None &                   None &  None &  None &  None \\
-                          vehicle &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.43 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
-                   food, nutrient &  0.72 &  1.27 &  0.68 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.52 &  1.99 &  0.15 \\
-         plants &  0.79 &  0.86 &  0.73 &        flower.n.01 &  0.79 &  0.86 &  0.73 &            flower.n.01 &  0.79 &  0.86 &  0.73 \\
-                             ware &  0.82 &  0.96 &  0.94 &       cutlery.n.02 &  0.82 &  0.96 &  0.94 &           cutlery.n.02 &  0.82 &  0.96 &  0.94 \\
-                             tool &  0.86 &  0.73 &  0.94 &          tool.n.01 &  0.86 &  0.73 &  0.94 &              tool.n.01 &  0.86 &  0.73 &  0.94 \\
-                           animal &  0.91 &  0.43 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
+         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
+       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
+           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
+      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
+           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
+       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
+ animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
 \bottomrule
- all &  0.70 &  1.35 &  0.73            \\
+ all &  0.70 &  1.34 &  0.73            \\
 
@@
 \small
-\begin{tabular}{lp{12cm}}
+\begin{tabular}{lp{13cm}}
 \toprule
                          category &                                                                                                                                                                                                                    most frequent naming variants \\
+
 \midrule
- food, solid food &  sandwich -- food (492), hotdog -- food (467), hotdog -- sandwich (318), cake -- food (265), bread -- sandwich (257), bread -- food (247), bread -- bun (206), donut -- food (188), hotdog -- bun (184), sandwich -- burger (163) \\
- structure, construction &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
- tool &  knife -- pizza (27), knife -- food (22), knife -- cake (17), knife -- banana (16), knife -- plate (15), knife -- apple (13), knife -- pocket knife (12), knife -- butter knife (12), knife -- table (10), knife -- carrot (8) \\
- vehicle &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
- plant, flora, plant life &  flower -- flowers (29), rose -- flower (25), flower -- rose (22), flower -- vase (18), flowers -- flower (14), flower -- dandelion (14), plant -- flower (12), flower -- sunflower (11), plant -- wheat (11), flower -- flower pot (10) \\
- food, nutrient &  pizza -- food (1796), sandwich -- food (631), pizza -- cheese (447), pizza -- plate (423), salad -- food (402), sandwich -- burger (235), pizza -- toppings (217), pizza -- pizza slice (162), sandwich -- bread (156), food -- sandwich (147) \\
- tableware &  cup -- mug (146), mug -- cup (104), cup -- coffee (93), cup -- drink (73), bowl -- food (60), cup -- glass (39), bowl -- cup (36), glass -- wine glass (35), glass -- cup (34), cup -- coffee cup (31) \\
- article of clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
- animal &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
- ware &  fork -- spoon (71), fork -- plate (44), spoon -- food (32), fork -- food (31), fork -- cake (21), spoon -- fork (18), spoon -- wooden spoon (15), fork -- broccoli (15), fork -- silverware (10), spoon -- vegetables (8) \\
- person &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
- instrumentality, instrumentation &  couch -- sofa (4090), desk -- table (3435), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
+ people &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
+ food &  pizza -- food (1883), sandwich -- food (1123), hotdog -- food (540), pizza -- cheese (457), pizza -- plate (430), salad -- food (402), sandwich -- burger (398), hotdog -- sandwich (351), sandwich -- bread (318), cake -- food (286) \\
+ home &  couch -- sofa (4090), desk -- table (3448), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
+ buildings &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
+ vehicles &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
+ clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
+ animals\_plants &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
 \bottomrule

### 2019-05-07 analysis/agreement_table.py

@@ -58,8 +58,8 @@ def make_agreement_table(resdf):
                      str("%.2f"%np.mean(resdf['snodgrass'])),\
                      str("%.2f"%(np.sum(resdf['vg_is_max'])/nobjects))))
 
-    for c in set(list(resdf['cat'])):
-        catdf = resdf[resdf['cat'] == c]
+    for c in set(list(resdf['vg_domain'])):
+        catdf = resdf[resdf['vg_domain'] == c]
         ncat = len(catdf)
 
         synagree = Counter()
@@ -89,7 +89,7 @@ def make_agreement_table(resdf):
                          str("%.2f"%(np.sum(botdf['vg_is_max'])/len(botdf)))\
                          ))
 
-    outdf = pd.DataFrame(tablerows,columns=['category','% top','SD','=VG','max synset','%','SD','=VG','min synset','%','SD','=VG' ])
+    outdf = pd.DataFrame(tablerows,columns=['domain','% top','SD','=VG','max synset','%','SD','=VG','min synset','%','SD','=VG' ])
     print(outdf.sort_values(by=['% top']).to_latex(index=False))
 
 

### 2019-05-07 analysis/wordnet_analysis.py
testing git

@@ -1,0 +1,674 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# In[7]:
+
+
+from nltk.corpus import wordnet as wn
+import pandas as pd
+from agreement_table import make_df
+
+
+# In[8]:
+
+
+import os
+import json
+import sys
+from collections import Counter
+import numpy as np
+
+
+# In[98]:
+
+
+fn = 'all_responses_round0-3_cleaned.csv'
+resdf = make_df(fn)
+
+
+# In[99]:
+
+
+resdf.head()
+
+
+# In[100]:
+
+
+def name_pairs(rdict):
+   
+    np_count = Counter()
+    if len(rdict.keys()) > 1:
+        topname = rdict.most_common(1)[0][0]
+        for oname in rdict:
+            if not oname == topname:
+                np_count[(topname,oname)] = rdict[oname]
+                
+    return np_count
+
+
+# In[101]:
+
+
+paircount = Counter()
+for ndict in resdf['spellchecked']:
+    #print(ndict)
+    x = name_pairs(ndict)
+    paircount.update(x)
+
+
+# In[102]:
+
+
+paircount.most_common(20)
+
+
+# In[103]:
+
+
+for ((top,other),freq) in paircount.most_common(20):
+    topsyn = wn.synsets(top)
+    othersyn = wn.synsets(other)
+    print(top,topsyn)
+    print(other,othersyn)
+    print("***")
+
+
+# In[104]:
+
+
+hyp = lambda s:s.hypernyms()
+list(sp.closure(hyp,depth=4))
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[ ]:
+
+
+
+
+
+# In[128]:
+
+
+hyp = lambda s:s.hypernyms()
+
+def is_hyponym(w1,w2,max_depth=5):
+    
+    for dpt in range(1,max_depth):
+        
+        syns1 = wn.synsets(w1,pos="n")
+        syns2 = wn.synsets(w2,pos="n")
+        
+        for syn1 in syns1:
+            hyp_closure = list(syn1.closure(hyp,depth=dpt))    
+            
[…]

### 2019-05-07 analysis/wordnet_analysis.py
testing git

@@ -1,17 +1,10 @@
 #!/usr/bin/env python
 # coding: utf-8
 
-# In[7]:
-
 
 from nltk.corpus import wordnet as wn
 import pandas as pd
 from agreement_table import make_df
-
-
-# In[8]:
-
-
 import os
 import json
 import sys
@@ -19,31 +12,24 @@ from collections import Counter
 import numpy as np
 
 
-# In[98]:
-
 
 fn = 'all_responses_round0-3_cleaned.csv'
 resdf = make_df(fn)
 
-
-# In[99]:
-
-
-resdf.head()
+hyp = lambda s:s.hypernyms()
 
 
-# In[100]:
 
 
 def name_pairs(rdict):
-   
+
     np_count = Counter()
     if len(rdict.keys()) > 1:
         topname = rdict.most_common(1)[0][0]
         for oname in rdict:
             if not oname == topname:
                 np_count[(topname,oname)] = rdict[oname]
-                
+
     return np_count
 
 
@@ -81,125 +67,70 @@ hyp = lambda s:s.hypernyms()
 list(sp.closure(hyp,depth=4))
 
 
-# In[ ]:
 
 
 
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[ ]:
-
-
-
-
-
-# In[128]:
-
-
-hyp = lambda s:s.hypernyms()
 
 def is_hyponym(w1,w2,max_depth=5):
-    
+
     for dpt in range(1,max_depth):
-        
+
         syns1 = wn.synsets(w1,pos="n")
         syns2 = wn.synsets(w2,pos="n")
-        
+
         for syn1 in syns1:
-            hyp_closure = list(syn1.closure(hyp,depth=dpt))    
-            
+            hyp_closure = list(syn1.closure(hyp,depth=dpt))
+
             for syn2 in syns2:
                 if syn2 in hyp_closure:
                     return dpt
     return 0
 
 def is_hypernym(w1,w2,max_depth=5):
-    
+
     for dpt in range(1,max_depth):
-        
+
         syns1 = wn.synsets(w1,pos="n")
         syns2 = wn.synsets(w2,pos="n")
-        
+
         for syn2 in syns2:
[…]

### 2019-05-07 analysis/wordnet_analysis.py
does it work?

@@ -43,13 +43,6 @@ for ndict in resdf['spellchecked']:
     paircount.update(x)
 
 
-# In[102]:
-
-
-paircount.most_common(20)
-
-
-# In[103]:
 
 
 for ((top,other),freq) in paircount.most_common(20):
@@ -58,16 +51,6 @@ for ((top,other),freq) in paircount.most_common(20):
     print(top,topsyn)
     print(other,othersyn)
     print("***")
-
-
-# In[104]:
-
-
-hyp = lambda s:s.hypernyms()
-list(sp.closure(hyp,depth=4))
-
-
-
 
 
 
@@ -138,19 +121,6 @@ def is_cohyponym(w1,w2,max_depth=5):
     return 0
 
 
-# In[106]:
-
-
-is_hyponym("person","man")
-
-
-# In[107]:
-
-
-is_hypernym("person","man")
-
-
-# In[129]:
 
 
 pair_depth = {}
@@ -168,14 +138,6 @@ for (top,other) in paircount:
         print(top,other,len(wn.synsets(top)),len(wn.synsets(other)))
 
 
-# In[130]:
-
-
-pair_depth
-
-
-# In[226]:
-
 
 pair_rel = {}
 no_rel = Counter()
@@ -191,26 +153,6 @@ for p in paircount:
     else:
         no_rel[p] = paircount[p]
 
-
-# In[168]:
-
-
-len(no_rel),len(have_rel)
-
-
-# In[169]:
-
-
-sum(no_rel.values())/sum(paircount.values())
-
-
-# In[170]:
-
-
-sum(have_rel.values())
-
-
-# In[193]:
 
 
 unordered_counts = Counter()

### 2019-05-07 analysis/wordnet_analysis.py
2nd version of extracting naming variants

@@ -29,6 +29,16 @@ def name_pairs(rdict):
 
     return np_count
 
+def vg_name_pairs(vg_name,rdict):
+
+    np_count = Counter()
+
+    for oname in rdict:
+        if not oname == vg_name:
+            np_count[(vg_name,oname)] = rdict[oname]
+
+    return np_count
+
 
 def is_hyponym(w1,w2,max_depth=5):
 
@@ -96,17 +106,18 @@ def is_cohyponym(w1,w2,max_depth=1):
 fn = 'all_responses_round0-3_cleaned.csv'
 resdf = make_df(fn)
 
-ordered_paircount = Counter()
+#ordered_paircount = Counter()
 paircount = Counter()
 wordcount = Counter()
 
-for ndict in resdf['spellchecked']:
+for x,row in resdf.iterrows():
     #print(ndict)
-    x = name_pairs(ndict)
-    ordered_paircount.update(x)
-    for pair in x:
-        paircount[tuple(sorted(pair))] += x[pair]
-    wordcount.update(ndict)
+    #x = name_pairs(ndict)
+    x = vg_name_pairs(row['vg_obj_name'],row['spellchecked'])
+    paircount.update(x)
+    #for pair in x:
+    #    paircount[tuple(sorted(pair))] += x[pair]
+    wordcount.update(row['spellchecked'])
 
 print("N name types:",len(wordcount))
 singletons = [w for w in wordcount if wordcount[w] == 1]
@@ -119,13 +130,13 @@ for w in wordcount:
         wn_wordcount[w] = wordcount[w]
         wn_map[w] = w
     elif len(wn.synsets('_'.join(w.split(' ')))) > 0:
-        wn_wordcount['_'.join(w.split(' '))] = wordcount[w]
+        wn_wordcount[w] = wordcount[w]
         wn_map[w] = '_'.join(w.split(' '))
     elif len(wn.synsets(''.join(w.split(' ')))) > 0:
-        wn_wordcount[''.join(w.split(' '))] = wordcount[w]
+        wn_wordcount[w] = wordcount[w]
         wn_map[w] = ''.join(w.split(' '))
     elif len(wn.synsets('-'.join(w.split(' ')))) > 0:
-        wn_wordcount['-'.join(w.split(' '))] = wordcount[w]
+        wn_wordcount[w] = wordcount[w]
         wn_map[w] = '-'.join(w.split(' '))
 
 wn_singletons = [w for w in wn_wordcount if wn_wordcount[w] == 1]
[…]

### 2019-05-07 papers/ACL2019/data-collection.tex
update

@@
 
-\gbt{to be refined -- taken from sivl submission as is}
+\gbt{START to be refined -- taken from sivl submission as is}
 
@@
 \end{itemize}
+\gbt{END to be refined -- taken from sivl submission as is}
 
-describe sampling of images, category selection
+\cs{START @ GBT}
+\subsection{Sampling of Instances (Images/Objects)}
+Since our work connects research on object naming in computer vision and in psycholinguistics/cognitive science, we aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict objects of frequent classes/names in visual genome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature.
+%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al.
+as basis.
+We chose the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of norming studies (REFS).
+In contrast to the latter, the McRae norms do not contain names of the \textsc{person} category, which we manually added.
 
-Table with:
+(As appropriate: We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).)
 
+\paragraph{Collection nodes}
+We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.
+
+We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ.
+of instances labeled with the synset of the object name is meant.}
+
+First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}.
+From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names.
+For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
+
+Goal of this procedure is the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
+The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
+We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
+We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} have an area of~$20-90\%$ of the whole image area.
+
+Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 
+Sampling proceeded in dependence on the overall size of the individual collection seeds: 
+up to~$800$ objects per seed: all instances, but at most 500, are collected; more than~$800$ objects per seed: all instances, but at most~$1,000$, are collected.  \textbf{double-check}
+
+\cs{END @ GBT}
+
+Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains.
+(\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
 % \begin{itemize}
@@
 
+Number of images/objects:        25,596\\
+Number of object names:  450\\
+Number of collection nodes (synsets):    52 \\
+
 \subsection{Procedure} describe the crowdsourcing set-up and the task
+TODO: Footnote: we ran pilot experiments to design our experiment and instructions.
+\paragraph{Collection Method}
+\begin{itemize}
+	\item instructions; put layout in appendix
+	\item each round: HIT of 10 instances, collect 9~annotations for each HIT
+	\item round 0 (with opt-outs) $\rightarrow$ pruning $\rightarrow$ rounds 1-3 (no opt-outs)\\
+	pruning: Based on given opt-outs: keep images with no OCCLUSION, at most BBOX is ambiguous twice, at most 17\% of names in plural form, most frequent names is of same domain as VG name (gives $25,596$, i.e., discard $5,497$ instances)
+	\item workers could only participate in one round, such as to avoid workers annotating an instance more than once. 
+\end{itemize}
+
+Overall $XX$~participants, each annotated between $XX$ and $XX$ instances.
 

### 2019-05-07 papers/EMNLP2019/data-collection.tex
adds messy dataset creation pre-AMT

--- 2019-05-07 papers/ACL2019/data-collection.tex
@@
 
-Goal of this procedure is the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
+\paragraph{Collection of instance candidates}
+Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
 The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
@@
 
+\paragraph{Sampling of instances}
 Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 

### 2019-05-07 papers/EMNLP2019/analysis.tex

--- 2019-05-07 papers/EMNLP2019/many_names.tex
@@
-%
-% File emnlp2019.tex
-%
-%% Based on the style files for ACL 2019, which were
-%% Based on the style files for EMNLP 2018, which were
-%% Based on the style files for ACL 2018, which were
-%% Based on the style files for ACL-2015, with some improvements
-%%  taken from the NAACL-2016 style
-%% Based on the style files for ACL-2014, which were, in turn,
-%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
-%% EACL-2009, IJCNLP-2008...
-%% Based on the style files for EACL 2006 by 
-%%e.agirre@ehu.es or Sergi.Balari@uab.es
-%% and that of ACL 08 by Joakim Nivre and Noah Smith
-
-\documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{emnlp-ijcnlp-2019}
-\usepackage{times}
-\usepackage{latexsym}
-\usepackage{graphicx}  %%% for including graphics
-\usepackage{booktabs}
-
-\usepackage{url}
-
-%\aclfinalcopy % Uncomment this line for the final submission
-
-%\setlength\titlebox{5cm}
-% You can expand the titlebox if you need extra space
-% to show all the authors. Please do not make the titlebox
-% smaller than 5cm (the original size); we will check this
-% in the camera-ready version and ask you to change it back.
-
-\newcommand\BibTeX{B{\sc ib}\TeX}
-\newcommand\confname{EMNLP-IJCNLP 2019}
-\newcommand\conforg{SIGDAT}
-
-\title{Instructions for \confname{} Proceedings}
-
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
-
-\date{}
-
-\begin{document}
-\maketitle
-\begin{abstract}
-\end{abstract}
-
-\newcommand{\refexp}[1]{\textsl{#1}}
-\newcommand{\word}[1]{\textsl{#1}}
-\newcommand{\cat}[1]{\textsc{#1}}
-\newcommand{\vgenome}{VisualGenome\xspace}
-\newcommand{\ra}{$\rightarrow$}
-
-\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-
-\section{Introduction}
-
-Expressions describing or referring to objects in visual scenes typically include a word naming the type of the object: e.g.,  \emph{cheesecake} or  \emph{dessert}  in Figure~\ref{fig:ex1}. 
-Determining these objects names is a core aspect of virtually every language \& vision task, ranging from e.g.\ referring expression generation to visual dialogue.
-Nevertheless, research in language \& vision has mostly  sidestepped questions about how speakers actually choose these names and how computational models should account for it.
-
-While state-of-the-art computer vision systems are able to accurately classify images into thousands of different categories (e.g.\  \newcite{googlenet}), they mostly adopt very simple assumptions with respect to the underlying lexicon, which is typically implemented as a simple, flat labeling scheme.
-Thus, a standard object recognition system would be trained to classify the objects in Figure~\ref{fig:cake} as either  \emph{dessert} or \emph{cake}.
-In contrast, humans seem to be more flexible as to the chosen level of generality and to the chosen part of the taxonomy (see objects in Figure \ref{fig:cake} that could be named \refexp{cake}, \refexp{cheesecake}, \refexp{dessert}, \refexp{sweet}, \refexp{pastry}, \refexp{food} etc.)
-Seminal work on prototypes suggests that the prototypicality of the object will determine the level of generality of the object name, i.e.\  a robin can be named \emph{bird}, but a penguin is better referred to as ``\emph{penguin}'' \cite{Rosch1978}.
-
-%To date, surprisingly little work has been done on testing such theoretical predictions on large-scale, language \& vision data sets and integrating them explicitly into modeling frameworks.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[height=3cm]{Figures/cheescake.png}
-\includegraphics[height=3cm]{Figures/cheesecak2.pdf}
-\caption{Two objects of the same type of cake, with different names in VisualGenome}
-\label{fig:cake}
-\end{center}
-\end{figure}
-
-Two main findings in the literature:
-
-\begin{itemize}
-\item very high agreement, most people use the same name for the same object
-\item prototypicality is a factor, context too, but research has only looked at generality/specificity of the name
-\end{itemize}
-
-\sz{something is missing here .. explain why exactly we did what we did, why is it interesting to collect many names for the same object?}
-
-There are two main findings:
-
-\begin{itemize}
-\item the level of agreement in object naming is much higher in certain domains than in others, as it happens, the domains that have been traditionally used in object naming research (e.g.
-animals) seem to display the highest amount of agreement in our data set
-\item while previous work has mostly focussed on variation in the level of generality (\emph{penguin} vs.
-\emph{bird}), our datasets contains a lot of variability for names coming from different parts of the taxonomy (\emph{dessert} vs.
-\emph{cake}, \emph{bottle} vs.
-\emph{wine})
-\end{itemize}
-
-%The real-world objects that we interact with in our every-day life can be categorized into many thousands and maybe millions of categories.
-And even a single object can be member of many categories, i.e.\ at different taxonomical levels or in different parts of a taxonomy.
-For instance, both objects in Figure \ref{fig:cake} are at once instances of \cat{cake}, \cat{cheesecake}, \cat{dessert}, \cat{sweet}, \cat{pastry}, \cat{food} etc.
-Hence, when speakers name objects, e.g.\ when referring, they have to select a lexical item from a complex network of concepts and competing lexical alternatives.
-
-%To date, research in NLP has surprisingly little to say about object naming, despite the fact that
-% there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}.
-%In contrast, closely related areas, such as computer vision and cognitive science, have investigated very related tasks in quite some depth: object recognition systems developed in the area of computer vision  are now able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
-%Furthermore, work on concepts, following the seminal work by Rosch, suggests that objects are typically conceptualized at a preferred level of specificity called the \textbf{entry-level}.
-Psycho-linguistic studies have been able to support this theory based on collections of so-called object naming norms.
-%
-%This paper aims at addressing the genuinely linguistic questions revolving around the phenomenon of object naming by (i) presenting a collection of high-quality, large-scale naming data,  and (ii) analysis methods for this data and (iii) a first baseline model that accounts for the semantic flexibility of names for objects in real-world images.
-From computer vision, we borrow the idea of modeling realistic visual objects in realistic scenes (real-world images), but go beyond the simplistic assumption that object names correspond to unambiguous labels in a flat classification scheme (with no conceptual relations between the labels).
-From psycholinguistics, we borrow the idea of eliciting natural, representative naming data from many subjects, but go beyond using artificial, highly stylized objects.
-
-\section{Related Work}
-
-\section{Analysis}
-
 \subsection{Agreement}
@@
 \begin{itemize}
-\item \textbf{top \%}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
-\item \textbf{SD \%}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects
+\item \textbf{\% top}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
+\item \textbf{SN}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects \gbt{Note: changing SD to SN cause SD is typically standard deviation}
 \item \textbf{=VG}: the proportion of objects where the most frequent name coincides with the name annotated in VisualGenome
@@
     & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
-                         domain & \% top &    SD &   =VG &         id &     \% top &    SD &   =VG &             id &     \% top &    SD &   =VG \\
+                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
 \midrule
@@
 
-Why is naming more flexible in certain domains than in others?
+Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
 
@@
 The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain. \sz{domains need to be updated}
+In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain.
 
@@
 \end{tabular}
-\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?}}
+\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please.
+Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens?
+And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes.
+This way we'll be able to see differences across domains.}}
 \label{tab:rel}
@@
 
-\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.}
+\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}
 
@@
 
-\subsection{Issues with WordNet}
+\subsection{Beyond synonymy and hypernymy: cross-classification}
+
+\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following:}
+
+  \begin{enumerate}
+  \item Dataframe for images: for each image,
+    \begin{itemize}
+    \item top -- top name
+    \item \% top
+    \item SN -- snodgrass agreement
+    \item =VG
+    \item dictionary or similar with names and counts
+    \end{itemize}
+  \item Dataframe for name variants: for each variant pair,
+    \begin{itemize}
+    \item top name
+    \item variant
+    \item frequency of the pair
+    \item domain of top
+    \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
+    \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
+    \end{itemize}
+  \end{enumerate}
 
@@
 \item bowl --chili
-\item bowl -- diner
+\item bowl -- diner \gbt{spelling mistake? should be dinner?} 
 \item burger -- meat
@@
 \item bottle -- alcohol
-\item donut --desert
+\item donut --desert \gbt{spelling mistake? should be dessert?} 
 \item zebra -- stripes
@@
 
-\subsection{Entry-level names and preference orders....}
+% \subsection{Entry-level names and preference orders....}
 
-\sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}.
+% \sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}.
 For 50\% of these images, annotators still prefer \textit{bird} as the most common name.
@@
 
-\sz{how can we analyze this quantitatively?}
+% \sz{how can we analyze this quantitatively?}
 
@@
 
-\subsection{Co-hyponyms as names for objects}
-
-\sz{analyze and discuss why we find so many co-hyponyms in our data set}
-
-\section{Modeling}
-
-\sz{I think, the prevalence of co-hyponymy is the most interesting finding. Can we learn to predict whether to co-hyponyms can be used to name the same object?}
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main"
+%%% End:

### 2019-05-07 papers/EMNLP2019/data-collection.tex

@@
 (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
+
+\begin{table*}
+\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
+	\toprule
+	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
+	\midrule
+	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
+	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
+	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
+	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
+	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
+	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
+	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
+	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
+	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
+	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
+	\bottomrule
+\end{tabular}
+	\caption{Overview of our dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
+\end{table*}
+
+\begin{table*}
+	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
+	\toprule
+	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
+	\midrule
+	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
+	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
+	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
+	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
+	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
+	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
+	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
+	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
+	  fish.n.01 (11) &   &   &   &   &   &   \\
+	\bottomrule
+\end{tabular}
+	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
+\end{table*}
+
 % \begin{itemize}
@@
 \begin{itemize}
-	\item instructions; put layout in appendix
+	\item instructions; \\
+	Appendix~\ref{app:instructions} gives the instructions as they were presented to the annotators. 
 	\item each round: HIT of 10 instances, collect 9~annotations for each HIT

### 2019-05-07 papers/EMNLP2019/analysis.tex
intro quite decent; minor fixes in other sections

@@
 \item \textbf{hyponymy}: e.g.\ man vs. person
-\item \textbf{co-hyponymy}: e.g.\ chicken vs. dinner, swan vs. goose
+\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
 \item \textbf{no relation}: e.g.\  desk vs. apple
@@
 \begin{table}
-\small
-\begin{tabular}{llll}
+
+\begin{tabular}{lll}
 \toprule
-        relation & \% types & \% tokens & av. depth \\
+       relation &  types & tokens \\
 \midrule
- co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
-    hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
-        synonymy &  0.015 &  0.121 &       1.000 \\
+synonymy &  0.01 &  0.09 \\
+co-hyponymy &  0.03 &  0.07 \\
+hypernymy &  0.06 &  0.35 \\
+not-covered &  0.19 &  0.04 \\
+crossclassified &  0.70 &  0.47 \\
 \bottomrule
 \end{tabular}
+% \small
+% \begin{tabular}{llll}
+% \toprule
+%         relation & \% types & \% tokens & av. depth \\
+% \midrule
+%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
+%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
+%         synonymy &  0.015 &  0.121 &       1.000 \\
+% \bottomrule
+% \end{tabular}
 \caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please.
@@
 \end{table}
+
+\begin{table*}
+\small
+\begin{tabular}{lp{13cm}}
+\toprule
+                         category &                                                                                                                                                                                                                    most frequent naming variants \\
+
+\midrule
+ people &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
+ food &  pizza -- food (1883), sandwich -- food (1123), hotdog -- food (540), pizza -- cheese (457), pizza -- plate (430), salad -- food (402), sandwich -- burger (398), hotdog -- sandwich (351), sandwich -- bread (318), cake -- food (286) \\
+ home &  couch -- sofa (4090), desk -- table (3448), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
+ buildings &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
+ vehicles &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
+ clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
+ animals\_plants &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
+\bottomrule
+\end{tabular}\caption{Most frequent naming variants for each category}
+\label{tab:exvariants}
+\end{table*}
 
@@
 
-\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following:}
+\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following (see commented text):}
 
-  \begin{enumerate}
-  \item Dataframe for images: for each image,
-    \begin{itemize}
-    \item top -- top name
-    \item \% top
-    \item SN -- snodgrass agreement
-    \item =VG
-    \item dictionary or similar with names and counts
-    \end{itemize}
-  \item Dataframe for name variants: for each variant pair,
-    \begin{itemize}
-    \item top name
-    \item variant
-    \item frequency of the pair
-    \item domain of top
-    \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
-    \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
-    \end{itemize}
-  \end{enumerate}
+  % \begin{enumerate}
+  % \item Dataframe for images: for each image,
+  %   \begin{itemize}
+  %   \item top -- top name
+  %   \item \% top
+  %   \item SN -- snodgrass agreement
+  %   \item =VG
+  %   \item dictionary or similar with names and counts
+  %   \end{itemize}
+  % \item Dataframe for name variants: for each variant pair,
+  %   \begin{itemize}
+  %   \item top name
+  %   \item variant
+  %   \item frequency of the pair
+  %   \item domain of top
+  %   \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
+  %   \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
+  %   \end{itemize}
+  % \end{enumerate}
 
@@
 
-\begin{table*}
-\small
-\begin{tabular}{lp{13cm}}
-\toprule
-                         category &                                                                                                                                                                                                                    most frequent naming variants \\
-
-\midrule
- people &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
- food &  pizza -- food (1883), sandwich -- food (1123), hotdog -- food (540), pizza -- cheese (457), pizza -- plate (430), salad -- food (402), sandwich -- burger (398), hotdog -- sandwich (351), sandwich -- bread (318), cake -- food (286) \\
- home &  couch -- sofa (4090), desk -- table (3448), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
- buildings &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
- vehicles &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
- clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
- animals\_plants &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
-\bottomrule
-\end{tabular}\caption{Most frequent naming variants for each category}
-\label{tab:exvariants}
-\end{table*}
-
 %%% Local Variables:

### 2019-05-07 papers/EMNLP2019/data-collection.tex
intro quite decent; minor fixes in other sections

@@
-\section{Data Collection}
-\label{sec:task}
-
-%describe the YouNameIt task here
-
-describe the task here
-
-\subsection{Visual Genome data}
-
-\gbt{START to be refined -- taken from sivl submission as is}
-
-\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+We take data from \vgenome \cite{krishna2016visualgenome}, which aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
 It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
 
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
-				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+% \gbt{START to be refined -- taken from sivl submission as is}
 
-\end{itemize}
-\gbt{END to be refined -- taken from sivl submission as is}
+% \vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+% It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
 
-\cs{START @ GBT}
+% \begin{itemize}
+%      		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
+% 				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
+% 		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
+
+% \end{itemize}
+% \gbt{END to be refined -- taken from sivl submission as is}
+
 \subsection{Sampling of Instances (Images/Objects)}
-Since our work connects research on object naming in computer vision and in psycholinguistics/cognitive science, we aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict objects of frequent classes/names in visual genome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature.
+
+We aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict common objects.
+ % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
 %Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al.
 as basis.
-We chose the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of norming studies (REFS).
-In contrast to the latter, the McRae norms do not contain names of the \textsc{person} category, which we manually added.
+We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
+We added the \textsc{person} category because it is very frequent category in \vgenome.
 
@@
 \paragraph{Collection nodes}
+% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
 We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.
@@
 We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
-We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} have an area of~$20-90\%$ of the whole image area.
+We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} had an area of~$20-90\%$ of the whole image area.
 
@@
 (\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
+\gbt{I would put only a table with the final dataset, not the intermediate one (round0). That is, include a table with the 25K imgs (the 30K imgs were just our initial pool).}
 
@@
 \begin{table*}
+\small
 	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
@@
 
-Overall $XX$~participants, each annotated between $XX$ and $XX$ instances.
+Overall $XX$~participants, each annotated between $XX$ and $XX$ instances. \gbt{Put mean or median instead of min-max}
 
-\subsection{Data} give an overview of the collected data
+\subsection{Data}
+
+give an overview of the collected data
 

### 2019-05-07 papers/EMNLP2019/relwork.tex
intro quite decent; minor fixes in other sections

--- 2019-02-02 papers/ACL2019/relwork.tex
@@
-\section{Related Work}
-\label{sec:related}
-
 \paragraph{Cognition: Concepts and categorization}
 
- Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
+ Seminal work on concepts by Rosch and colleagues suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}.
 This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
@@
 These object recognition systems are now widely used in vision \& language research.
-Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.}
+Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.} \gbt{ok}
 
@@
  \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
- Thus, object naming is an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.
+Object naming is also an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.
+\gbt{Should we put this as motivation also in the intro?}
 
-\paragraph{Existing resources and their shortcomings}
-Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
+% \paragraph{Existing resources and their shortcomings}
+% Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g.
 object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.

### 2019-05-07 analysis/agreement_table.py
extracting flat naming variants

@@ -92,7 +92,7 @@ def make_agreement_table(resdf):
     outdf = pd.DataFrame(tablerows,columns=['domain','% top','SD','=VG','max synset','%','SD','=VG','min synset','%','SD','=VG' ])
     print(outdf.sort_values(by=['% top']).to_latex(index=False))
 
-
-fn = 'all_responses_round0-3_cleaned.csv'
-resdf = make_df(fn)
-make_agreement_table(resdf)
+if __name__ == '__main__':
+    fn = 'all_responses_round0-3_cleaned.csv'
+    resdf = make_df(fn)
+    make_agreement_table(resdf)

### 2019-05-07 analysis/wordnet_analysis.py

@@ -29,6 +29,22 @@ def name_pairs(rdict):
 
     return np_count
 
+def flat_name_pairs(rdict):
+
+    np_count = Counter()
+    if len(rdict.keys()) > 1:
+        names = rdict.most_common()
+        for i,(n,fr) in enumerate(names):
+            if i < len(names):
+                alt_names = names[i+1:]
+                top_name = names[i][0]
+
+                for oname,fr in alt_names:
+                    if not oname == top_name:
+                        np_count[(top_name,oname)] = fr
+
+    return np_count
+
 def vg_name_pairs(vg_name,rdict):
 
     np_count = Counter()
@@ -106,17 +122,17 @@ def is_cohyponym(w1,w2,max_depth=1):
 fn = 'all_responses_round0-3_cleaned.csv'
 resdf = make_df(fn)
 
-#ordered_paircount = Counter()
+ordered_paircount = Counter()
 paircount = Counter()
 wordcount = Counter()
 
 for x,row in resdf.iterrows():
     #print(ndict)
-    #x = name_pairs(ndict)
-    x = vg_name_pairs(row['vg_obj_name'],row['spellchecked'])
-    paircount.update(x)
-    #for pair in x:
-    #    paircount[tuple(sorted(pair))] += x[pair]
+    x = flat_name_pairs(row['spellchecked'])
+    #x = vg_name_pairs(row['vg_obj_name'],row['spellchecked'])
+    ordered_paircount.update(x)
+    for pair in x:
+        paircount[tuple(sorted(pair))] += x[pair]
     wordcount.update(row['spellchecked'])
 
 print("N name types:",len(wordcount))
@@ -146,13 +162,13 @@ print("... singletons:",len(wn_singletons))
 
 wn_paircount = Counter({(w1,w2):paircount[(w1,w2)] for (w1,w2) in paircount if w1 in wn_wordcount \
                                                                                and w2 in wn_wordcount })
-#wn_ordered_paircount = Counter({(w1,w2):ordered_paircount[(w1,w2)] for (w1,w2) in ordered_paircount if w1 in wn_wordcount and w2 in wn_wordcount })
+wn_ordered_paircount = Counter({(w1,w2):ordered_paircount[(w1,w2)] for (w1,w2) in ordered_paircount if w1 in wn_wordcount and w2 in wn_wordcount })
 
-#print("N ordered name variants:",len(ordered_paircount))
-#print("N name variants :",len(paircount))
[…]

### 2019-05-08 analysis/wordnet_analysis.py
new csv files with relations, domains, synsets

@@ -35,13 +35,16 @@ def flat_name_pairs(rdict):
     if len(rdict.keys()) > 1:
         names = rdict.most_common()
         for i,(n,fr) in enumerate(names):
-            if i < len(names):
+            # Threshold
+            if i < len(names) and fr > 1:
                 alt_names = names[i+1:]
                 top_name = names[i][0]
 
                 for oname,fr in alt_names:
                     if not oname == top_name:
                         np_count[(top_name,oname)] = fr
+            else:
+                break
 
     return np_count
 
@@ -58,33 +61,30 @@ def vg_name_pairs(vg_name,rdict):
 
 def is_hyponym(w1,w2,max_depth=5):
 
-    for dpt in range(1,max_depth):
+    syns1 = wn.synsets(w1,pos="n")
+    syns2 = wn.synsets(w2,pos="n")
 
-        syns1 = wn.synsets(w1,pos="n")
-        syns2 = wn.synsets(w2,pos="n")
+    for syn1 in syns1:
+        hyp_closure = list(syn1.closure(hyp,depth=dpt))
 
-        for syn1 in syns1:
-            hyp_closure = list(syn1.closure(hyp,depth=dpt))
-
-            for syn2 in syns2:
-                if syn2 in hyp_closure:
-                    return dpt
-    return 0
+        for syn2 in syns2:
+            if syn2 in hyp_closure:
+                return (True,syn1,syn2)
+    return (False,0,0)
 
 def is_hypernym(w1,w2,max_depth=5):
 
-    for dpt in range(1,max_depth):
 
-        syns1 = wn.synsets(w1,pos="n")
-        syns2 = wn.synsets(w2,pos="n")
+    syns1 = wn.synsets(w1,pos="n")
+    syns2 = wn.synsets(w2,pos="n")
 
-        for syn2 in syns2:
-            hyp_closure = list(syn2.closure(hyp,depth=dpt))
+    for syn2 in syns2:
+        hyp_closure = list(syn2.closure(hyp,depth=max_depth))
 
-            for syn1 in syns1:
-                if syn1 in hyp_closure:
-                    return dpt
-    return 0
+        for syn1 in syns1:
+            if syn1 in hyp_closure:
+                return (True,syn1,syn2)
+    return (False,0,0)
 
 def is_synonym(w1,w2):
 
@@ -95,8 +95,8 @@ def is_synonym(w1,w2):
 
         for syn1 in syns1:
[…]

### 2019-05-08 papers/EMNLP2019/analysis.tex
new table in analysis with relation distr. shown for each domain

@@
 
-\begin{table}
+\begin{table*}
 
-\begin{tabular}{lll}
-\toprule
-       relation &  types & tokens \\
-\midrule
-synonymy &  0.01 &  0.09 \\
-co-hyponymy &  0.03 &  0.07 \\
-hypernymy &  0.06 &  0.35 \\
-not-covered &  0.19 &  0.04 \\
-crossclassified &  0.70 &  0.47 \\
-\bottomrule
-\end{tabular}
+%\begin{tabular}{lll}
+%\toprule
+%       relation &  types & tokens \\
+%\midrule
+%synonymy &  0.01 &  0.09 \\
+%co-hyponymy &  0.03 &  0.07 \\
+%hypernymy &  0.06 &  0.35 \\
+%not-covered &  0.19 &  0.04 \\
+%crossclassified &  0.70 &  0.47 \\
+%\bottomrule
+%\end{tabular}
 % \small
@@
 % \end{tabular}
+
+\begin{tabular}{l|ll|ll|ll|ll|ll}
+\toprule
+      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
+         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
+\midrule
+ people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
+ clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
+ animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
+ food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
+ vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
+ home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
+ buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
+ \hline
+ all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
+\bottomrule
+\end{tabular}
+
 \caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please.
@@
 \label{tab:rel}
-\end{table}
+\end{table*}
 

### 2019-05-08 analysis/wordnet_analysis.py

@@ -247,17 +247,51 @@ for p in pairrel:
         typecounts[rel] += 1
         tokencounts[rel] += paircount[p]
 
+domtypecounts = {}
+domtokencounts = {}
+for (domain,top,other) in domain_paircount:
+    if (top,other) in pairrel:
+        rel = pairrel[(top,other)][0]
+    else:
+        rel = pairrel[(other,top)][0]
+    if '.' in rel:
+        rel = rel[:-2]
+    if domain not in domtypecounts:
+        domtypecounts[domain] = Counter()
+        domtokencounts[domain] = Counter()
+    domtypecounts[domain][rel] += 1
+    domtokencounts[domain][rel] += domain_paircount[(domain,top,other)]
+
+
+
 
 outdf = []
 totaltypes = sum(typecounts.values())
 totaltokens = sum(tokencounts.values())
-for p in typecounts:
-    outdf.append((p,"%.3f"%(typecounts[p]/totaltypes),"%.3f"%(tokencounts[p]/totaltokens)))
+relations = typecounts.keys()
 
+for domain in domtypecounts:
+    row = [domain]
+    for p in relations:
+        row.append("%.3f"%(domtypecounts[domain][p]/sum(domtypecounts[domain].values())))
+        row.append("%.3f"%(domtokencounts[domain][p]/sum(domtokencounts[domain].values())))
+    outdf.append(row)
 
-outdff = pd.DataFrame(outdf,columns=['relation','types','tokens'])
+row = ['all']
+for p in relations:
+    row.append("%.3f"%(typecounts[p]/totaltypes))
+    row.append("%.3f"%(tokencounts[p]/totaltokens))
+outdf.append(row)
 
-print(outdff.sort_values(by=['types']).to_latex(index=False))
+print(outdf)
+
+colnames = ['domain']
+for p in relations:
+    colnames.append(p+"_typ")
+    colnames.append(p+"_tok")
+outdff = pd.DataFrame(outdf,columns=colnames)
+
+print(outdff.to_latex(index=False))
 
 
 pairdf = []

### 2019-05-08 analysis/gemmas-analysis.py
partial annotation

@@ -6,11 +6,11 @@ import pandas as pd
 import numpy as np
 import os
 #from collections import Counter
-from utils_analysis import *
+#from utils_analysis import *
 
-df=pd.read_csv("../data_phase0/results-created_2019-Feb-20_13_36_05_final.csv",sep="\t")
-print(df.head())
-print(df.columns)
+#df=pd.read_csv("../data_phase0/results-created_2019-Feb-20_13_36_05_final.csv",sep="\t")
+#print(df.head())
+#print(df.columns)
 
 #TO DO (from paper files)
 #
@@ -40,3 +40,13 @@ print(df.columns)
 #  \end{itemize}
 #\item can we find generalizations about tendencies in agreement? (open: how to go about it)
 #\end{enumerate}
+
+df = pd.read_csv('domains_names_pairs_relations_v2.csv',index_col=0)
+
+df.columns
+
+for i in ['home','people','clothing','vehicles','buildings','food','animals_plants']:
+    filename= i+'-to-annotate.csv'
+    d=df[(df.relation=="crossclassified") & (df.domain==i)].sort_values('totalfreq',ascending=False)
+    d=d.head(1000)
+    d.to_csv(filename)

### 2019-05-09 analysis/add_younameit_categories.py
commits scripts used for checkpoint

@@ -1,0 +1,18 @@
+import os
+
+import pandas
+
+BASE_DIR = os.path.dirname(os.getcwd())
+
+def _add_younameit_cats(df, category_mapping_fname="dataset_creation/categories/category_mapping.tsv"):
+    # load category mapping (WordNet --> YouNameIt)
+    cat2samplecats_map = pandas.read_csv(os.path.join(BASE_DIR, category_mapping_fname), sep="\t")
+    wncat2younameit = {wn_cat:yni_cat for (idx, (wn_cat, yni_cat)) in \
+        cat2samplecats_map[["wordnet_category","younameit_category"]]\
+            .drop_duplicates(subset="wordnet_category").iterrows()}
+    
+    df["domain"] = df["cat"].apply(lambda cat: wncat2younameit.get(cat, "UNK"))
+    return df
+
+    
+

### 2019-05-09 analysis/preprocess_results.py

@@ -1,0 +1,95 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Apr  4 17:27:28 2019
+
+@author: Carina Silberer
+"""
+import operator
+import os
+import re
+import sys
+from collections import defaultdict
+
+from matplotlib.pyplot import figure
+figure(num=None, figsize=(8, 6), dpi=80, facecolor='w', edgecolor='k')
+
+import load_results
+import add_younameit_categories as cat_mapper
+
+BASE_DIR = os.path.dirname(os.getcwd())
+
+def get_name2domain_map(df):
+    # get object name to category mapping, to augment collected names with categories (as far as available)
+    name_cat_map = df[["vg_domain", "vg_obj_name"]].to_dict()
+    name_cat_map = {name_cat_map["vg_obj_name"][idx]:name_cat_map["vg_domain"][idx] \
+                    for (idx, cat) in enumerate(name_cat_map["vg_domain"])}
+    return name_cat_map
+
+def name2domain(name, mapping):
+    return mapping.get(name, "$"+name)
+
+def _streamline_name(obj_name):
+    return re.sub("\s+", " ", obj_name)
+
+if __name__=="__main__":
+    if len(sys.argv) < 2:
+        sys.stderr.write("Please provide a results file or directory.\n")
+        sys.exit()
+        
+    results_path = os.path.dirname(sys.argv[1])
+    if os.path.isdir(results_path):
+        out_results_file = os.path.join(results_path, "all_results_files_preprocessed_%s.csv" % (os.path.basename(results_path)))
+    else:
+        out_results_file = re.sub("(.+?)(\.(csv|tsv))?$", r"\1_preprocessed.csv", sys.argv[1])
+        
+    df = load_results.load_resultsdata_csv(sys.argv[1])
+
+    # add category mapping (WordNet --> YouNameIt) ==> column "domain"
+    df = cat_mapper._add_younameit_cats(df)
+    df.rename(columns={"domain": "vg_domain"}, inplace=True)
+
+    df.rename(columns={"obj_name": "vg_obj_name"}, inplace=True)
+    analysis_cat = "vg_domain" # "cat"
+
+    name_domain_map = get_name2domain_map(df)
+    domains = set(name_domain_map.values())
+                  
+    ## Post-processing of df of collected data
+    # separate opt-outs and object names
+    df["opt-outs"] = df["responses"].apply(
[…]

### 2019-05-09 papers/EMNLP2019/analysis.tex
annotation for crossclassified finished
finalized annotation; intial analysis in the explore notebook

@@
 
-\sz{discuss...}
+Interesting name pairs:
+
+\begin{itemize}
+\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
+\item field - grass: same (reverse); how to distinguish?
+\item dog - pet (different conceptualizations; classified as ``overlapping''
+\item airplane - flight, plane - flight (classified as ``adjacent'' although it's an event relation...)
+\end{itemize}
 

### 2019-05-10 papers/EMNLP2019/analysis.tex
middle of analysis results

@@
 
-\subsection{Beyond synonymy and hypernymy: cross-classification}
+\subsection{Crossclassified}
 
-\gbt{@Sina, for this section/my analysis, I'd need csvs (or some code that builds dataframes) containing the following (see commented text):}
+Table
 
-  % \begin{enumerate}
-  % \item Dataframe for images: for each image,
-  %   \begin{itemize}
-  %   \item top -- top name
-  %   \item \% top
-  %   \item SN -- snodgrass agreement
-  %   \item =VG
-  %   \item dictionary or similar with names and counts
-  %   \end{itemize}
-  % \item Dataframe for name variants: for each variant pair,
-  %   \begin{itemize}
-  %   \item top name
-  %   \item variant
-  %   \item frequency of the pair
-  %   \item domain of top
-  %   \item domain of variant (one of ours or ``OTHER'' if not in any of them?)
-  %   \item relationship in wordnet, one of: synonymy, hyponymy, co-hyponymy, other, not in wordnet (agree? the latter means ``one of the elements not in wordnet'')
-  %   \end{itemize}
-  % \end{enumerate}
-
-Some (interesting, somewhat cherry-picked) word pairs were WordNet does not find any relation (excluded in the above analysis):
-
-\begin{itemize}
-\item lettuce -- salad
-\item fruit -- food
-\item man -- catcher
-\item bowl --chili
-\item bowl -- diner \gbt{spelling mistake? should be dinner?} 
-\item burger -- meat
-\item statue -- animal (image shows statue of an animal)
-\item bottle -- alcohol
-\item donut --desert \gbt{spelling mistake? should be dessert?} 
-\item zebra -- stripes
-\item oven -- grill
-\end{itemize}
+\begin{table*}
+  \label{tab:crossclass}
+\small
+\begin{tabular}{lrl|lrl}
+  \toprule
+    \multicolumn{3}{c}{same object (217; 31\%)} & \multicolumn{3}{c}{not same object (483; 69\%)}\\
+\midrule
+co-hyponyms &          104  & horse-donkey, truck-jeep, castle-church & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
+overlapping &           69  & skater-boy, cat-toy, horse-statue & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
+hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
+hypernym.2  &           16  & donut-pastry, train-vehicle, van-automobile & supports.2 &           64 & shirt-child, donut-plate, carpet-floor\\
+other       &            8  & sandwich-meal, plane-plain, umbrella-tent & part.1     &           20 & wheel-moped, sink-counter, bread-sub\\
+	    & 		    & & other      &           10 & plane-flight, horse-wood\\
+\bottomrule
+\end{tabular}
+\caption{Relations between words or objects when the variants refer to the same object (left) or not (right).}
+\end{table*}
 
@@
 
+% \begin{itemize}
+% \item lettuce -- salad
+% \item fruit -- food
+% \item man -- catcher
+% \item bowl --chili
+% \item bowl -- diner \gbt{spelling mistake? should be dinner?} 
+% \item burger -- meat
+% \item statue -- animal (image shows statue of an animal)
+% \item bottle -- alcohol
+% \item donut --desert \gbt{spelling mistake? should be dessert?} 
+% \item zebra -- stripes
+% \item oven -- grill
+% \end{itemize}
+
 %%% Local Variables:

### 2019-05-10 analysis/gemmas-analysis.py

@@ -8,6 +8,13 @@ import os
 #from collections import Counter
 #from utils_analysis import *
 
+
+df=pd.read_csv('pairs-annotation/annotated-crossclasssified-pairs-alldomains.csv',index_col=0)
+df.head()
+f_all=df[df.same_object=='f'].subrelation.value_counts()
+t_all=df[df.same_object=='t'].subrelation.value_counts()
+
+
 #df=pd.read_csv("../data_phase0/results-created_2019-Feb-20_13_36_05_final.csv",sep="\t")
 #print(df.head())
 #print(df.columns)
@@ -41,12 +48,12 @@ import os
 #\item can we find generalizations about tendencies in agreement? (open: how to go about it)
 #\end{enumerate}
 
-df = pd.read_csv('domains_names_pairs_relations_v2.csv',index_col=0)
+# df = pd.read_csv('domains_names_pairs_relations_v2.csv',index_col=0)
 
-df.columns
+# df.columns
 
-for i in ['home','people','clothing','vehicles','buildings','food','animals_plants']:
-    filename= i+'-to-annotate.csv'
-    d=df[(df.relation=="crossclassified") & (df.domain==i)].sort_values('totalfreq',ascending=False)
-    d=d.head(1000)
-    d.to_csv(filename)
+# for i in ['home','people','clothing','vehicles','buildings','food','animals_plants']:
+#     filename= i+'-to-annotate.csv'
+#     d=df[(df.relation=="crossclassified") & (df.domain==i)].sort_values('totalfreq',ascending=False)
+#     d=d.head(1000)
+#     d.to_csv(filename)

### 2019-05-10 papers/EMNLP2019/analysis.tex
done initial annotation pass

@@
 
-\subsection{Crossclassified}
+\subsection{The ``no relation'' case}
 
-Table
+We manually annotated the 100 most frequent name pairs in the ``no relation'' case.
+Table~\ref{tab:crossclass} shows that, in this category, one third of the pairs do refer to the same object, but the relationship is not captured in WordNet.
+Most of these cases are arguably coverage issues of WordNet, which doesn't capture the co-hyponymy of \textit{horse}-\textit{donkey} or the fact that \textit{vehicle} is hypernym of \textit{train}.\gbt{I find this really weird...
+also some other cases I annotated.
+It sounds like I should have listened more carefully to Carina when she suggested going down and up in the wordnet hierarchy (cf.\ the example of food-fruit).
+:/ Maybe we'd capture quite a bit of them if we did a more sophisticated querying of WordNet.
+To discuss.}
+% between \textit{hat}-\textit{beanie}.
+However, a substantial group is constituted by names whose denotations overlap even if they don't belong to the same category.
+These are typically alternative conceptualizations of objects: as a cat or a toy, as a kind of building or its function (\textit{building}-\textit{home}), or as a portion or a kind of food (\textit{pizza-slice}).
 
@@
   \toprule
-    \multicolumn{3}{c}{same object (217; 31\%)} & \multicolumn{3}{c}{not same object (483; 69\%)}\\
+    \multicolumn{3}{c}{same object (215; 31\%)} & \multicolumn{3}{c}{not same object (485; 69\%)}\\
 \midrule
-co-hyponyms &          104  & horse-donkey, truck-jeep, castle-church & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
-overlapping &           69  & skater-boy, cat-toy, horse-statue & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
+co-hyponyms &          148  & horse-donkey, truck-jeep, skier-woman & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
+overlapping &           22  & cat-toy, building-home, pizza-slice & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
 hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
@@
 
+Still, 69\% of the annotated pairs arguably do not denote the same object.
+Here we find problems HUMANS MAKE SAME ``ERRORS'' AS MACHINES -- REFERENTIAL UNCERTAINTY IN THE ABSENCE OF CONTEXT (discuss as planned with Carina).
+
 Interesting name pairs:
@@
 \item field - grass: same (reverse); how to distinguish?
-\item dog - pet (different conceptualizations; classified as ``overlapping''
-\item airplane - flight, plane - flight (classified as ``adjacent'' although it's an event relation...)
+\item dog - pet (different conceptualizations; classified as ``hypernym.2'')
+\item airplane - flight, plane - flight (classified as ``other'').
 \end{itemize}
+
+Most of the cases are co-hyponyms with categories that are easily confused, such as \textit{horse}-\textit{donkey}, \textit{truck}-\textit{jeep}.
+In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.
 

### 2019-05-11 papers/EMNLP2019/analysis.tex
attempt at an abstract (too long), updates in agreement table

--- 2019-05-10 papers/EMNLP2019/analysis.tex
@@
 \small
-\begin{tabular}{llll|llll|llll}
+\centering
+\begin{tabular}{llll|lll}
 \toprule
-    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
-                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
+& \multicolumn{3}{c}{non-canonicalized} & \multicolumn{3}{c}{annotated vs. non-canonicalized} \\
+         domain &  \% top &    SD &     N$_{types}$ & Max=VG & \% VG (Micro) & \% VG (Macro) \\
 \midrule
-         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
-       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
-           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
-      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
-           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
-       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
- animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
+         people &  51.88 &  2.13 &  8.60 &  49.77 &        32.25 &        32.25 \\
+       clothing &  63.93 &  1.58 &  6.44 &  70.16 &        52.58 &        52.63 \\
+           home &  66.35 &  1.50 &  6.31 &  78.48 &        58.82 &        58.92 \\
+      buildings &  66.87 &  1.55 &  6.89 &  72.60 &        55.46 &        55.59 \\
+           food &  71.27 &  1.30 &  5.49 &  62.89 &        52.11 &        52.25 \\
+       vehicles &  71.97 &  1.13 &  4.66 &  71.11 &        60.18 &        60.20 \\
+ animals\_plants &  91.26 &  0.44 &  2.68 &  93.84 &        88.01 &        88.01 \\
+ \midrule
+             all &  69.69 &  1.34 &  5.70 &  72.77 &        58.65 &        58.43 \\
 \bottomrule
- all &  0.70 &  1.34 &  0.73            \\
+\end{tabular}
+\caption{Agreement in non-canonicalized naming data, and between annotated (original VisualGenome) and non-canonicalized names for different object domains }
+\label{tab:agree}
+\end{table*}
 
+\begin{table*}
+\small
+%\begin{tabular}{llll|llll|llll}
+%\toprule
+%    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
+%                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
+%\midrule
+%         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
+%       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
+%           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
+%      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
+%           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
+%       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
+% animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
+%\bottomrule
+% all &  0.70 &  1.34 &  0.73            \\
+%
+%\bottomrule
+%\end{tabular}
+\begin{tabular}{lllllllllllllll}
+\toprule
+         domain &  \% top &    SD & Max=VG &   \% VG &         max synset &      \% &    SD & Max=VG &   \% VG &             min synset &      \% &    SD & Max=VG &   \% VG \\
+\midrule
+         people &  51.88 &  2.13 &  49.77 &  32.25 &  professional.n.01 &  60.67 &  2.02 &  20.00 &  11.67 &           athlete.n.01 &  35.59 &  2.62 &  36.87 &  24.76 \\
+       clothing &  63.93 &  1.58 &  70.16 &  52.58 &      neckwear.n.01 &  79.32 &  0.91 &  76.92 &  65.45 &          footwear.n.01 &  46.90 &  2.55 &  40.00 &  25.97 \\
+           home &  66.35 &  1.50 &  78.48 &  58.82 &          tool.n.01 &  86.44 &  0.73 &  94.44 &  82.34 &          crockery.n.01 &  51.69 &  1.92 &  40.22 &  29.37 \\
+      buildings &  66.87 &  1.55 &  72.60 &  55.46 &        bridge.n.01 &  75.48 &  1.21 &  86.87 &  69.58 &  place\_of\_worship.n.01 &  46.23 &  2.26 &   8.33 &   7.43 \\
+            all &  69.69 &  1.34 &  72.77 &  58.65 &               None &   None &  None &   None &   None &                   None &   None &  None &   None &   None \\
+           food &  71.27 &  1.30 &  62.89 &  52.11 &  edible\_fruit.n.01 &  79.67 &  0.89 &  78.57 &  69.78 &         vegetable.n.01 &  52.83 &  1.97 &  14.58 &  10.90 \\
+       vehicles &  71.97 &  1.13 &  71.11 &  60.18 &         train.n.01 &  92.74 &  0.42 &  99.16 &  92.14 &          aircraft.n.01 &  52.46 &  1.50 &  40.56 &  37.49 \\
+ animals\_plants &  91.26 &  0.44 &  93.84 &  88.01 &        feline.n.01 &  94.78 &  0.29 &  98.95 &  94.15 &              fish.n.01 &  38.97 &  2.53 &  54.55 &  32.50 \\
 \bottomrule

### 2019-05-13 analysis/agreement_table.py
function for boxplots

@@ -5,6 +5,8 @@ import json
 import sys
 from collections import Counter
 import numpy as np
+import matplotlib.pyplot as plt
+import numpy as np
 
 def snodgrass_agreement(rdict,vocab,singletons=False):
 
@@ -56,16 +58,18 @@ def make_df(filename):
     resdf['vg_overlap'] = vg_overlap
     resdf['n_anno'] = nanno
     resdf['n_types'] = ntypes
+    resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
+    resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
 
     return resdf
 
 def make_agreement_table(resdf):
-    resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
-    resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
+
     nobjects = len(resdf)
 
     tablerows = []
     tablerows2 = []
+
 
     tablerows.append(('all',\
 
@@ -75,7 +79,6 @@ def make_agreement_table(resdf):
                      str("%.2f"%((np.sum(resdf['vg_is_max'])/nobjects)*100)),\
                      str("%.2f"%((np.sum(resdf['vg_mean'])/nobjects)*100)),\
                      str("%.2f"%((np.sum(resdf['vg_overlap'])/np.sum(resdf['n_anno']))*100))
-
                      ))
 
     for c in set(list(resdf['vg_domain'])):
@@ -104,6 +107,9 @@ def make_agreement_table(resdf):
                          str("%.2f"%((np.sum(catdf['vg_overlap'])/np.sum(catdf['n_anno']))*100))
 
                     ))
+
+
+
         tablerows2.append((c,\
 
                          topsyn,
@@ -125,7 +131,38 @@ def make_agreement_table(resdf):
     outdf2 = pd.DataFrame(tablerows2,columns=['domain','max synset','% top1','SD','Max=VG','% VG','min synset','% top','SD','Max=VG','% VG' ])
     print(outdf2.sort_values(by=['% top1']).to_latex(index=False))
 
+def agreement_boxplot(resdf):
+    plotdata = []
+    cats = ['all']
+    plotdata.append(list(resdf['percent_agree']))
+
+    for c in set(list(resdf['vg_domain'])):
[…]

### 2019-05-13 analysis/agreement_table.py
intro?

@@ -146,18 +146,22 @@ def agreement_boxplot(resdf):
     #plt.xticks(range(1,len(cats)), cats)
     plt.savefig("agreebox.png")
 
-    fig, ax = plt.subplots(411)
+    fig, ax = plt.subplots()
     plotdata = []
     cats = []
+    rangec = []
 
-    for c in list(set(list(resdf['synset'])))[:10]:
+    for i,c in enumerate(list(set(list(resdf['synset'])))[:20]):
         cats.append(c)
+        rangec.append((i+1)*4)
         catdf = resdf[resdf['synset'] == c]
         plotdata.append(list(catdf['percent_agree']))
 
+    print(rangec)
     fig, ax = plt.subplots()
-    ax.boxplot(plotdata,labels=cats,vert=True)
-    #plt.xticks(range(1,len(cats)), cats)
+    ax.boxplot(plotdata)
+    plt.xticks(range(1,len(cats)+1), cats,fontsize = 6, rotation = 90)
+    plt.subplots_adjust(bottom=0.15)
     plt.savefig("agreebox_synset.png")
 
 

### 2019-05-13 papers/EMNLP2019/analysis.tex
separated analysis in 2 parts, + an astonishing new result

--- 2019-05-10 papers/EMNLP2019/analysis.tex
@@
-\subsection{Agreement}
+In this Section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
+Whereas traditional picture naming studies typically use a prototypical image per category and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
+Second, we will uses the existing annotation of names in VG to analyze agreement on the level of categories.
+
+\subsection{Measures}
 
@@
 \begin{itemize}
-\item \textbf{\% top}: for each object, we calculate the relative frequency of the most common name, and then average over all objects
-\item \textbf{SN}: for each object, we calculate the Snodgrass agreement measure, and then average over all objects \gbt{Note: changing SD to SN cause SD is typically standard deviation}
-\item \textbf{=VG}: the proportion of objects where the most frequent name coincides with the name annotated in VisualGenome
+\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
+\item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
+\item \textbf{N}: the average number of types in the response set of MN
+\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
+\item \textbf{top=VG}: the proportion of items where the top response in MN corresponds to the VG name
+\item \textbf{\% VG}: the average relative frequency of the VG name in the response set
+
 \end{itemize}
+
+For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets.
+Furthermore, we compute \textbf{category-level agreement} by merging the response sets for all objects that have the same VG name and compute the measures over these aggregated response sets.
+
+\subsection{Results}
+
+Table \ref{tab:agree} shows the analysis of the instance-level and category-level agreement.
+On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices.
+Thus, for roughly 70\% of our objects, the most frequent response in MN corresponds to the original VG name and, similarly, the average frequency of the top response is also 70\%.
+Generally, this seems to suggest that indeed many objects in our data set have a canonical name.
+At the same time, the average number of name types per object (5.7 and 2.9, when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that can be elicited for instances.
+Furthermore, the agreement varies quite considerably among domains:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement).
+The people domain, on the other hand, is subject to much more variation and agreement is dramatically lower here, and comes close to 50\% for \% top.
+
+Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VG name, we obtain on average 28 types (with $n > 1)$, i.e.
+27 variants of the original VG name.
+Surprisingly, here, only 29.4\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in MN, on average, prefer a different name.
+Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.
+What does this discrepancy between the instance-level and category-level agreement in VG and MN naming choices mean?
+First of all, it suggests that the same original VG name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
+Second, this clearly shows that annotators in VG do not generally annotate the most canonical name and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
+\sz{think more ...}
 
@@
 \small
-\begin{tabular}{llll|llll|llll}
+\begin{tabular}{p{1.3cm}ccccccc|ccccccc}
 \toprule
-    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
-                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
+ & \multicolumn{7}{c|}{Instance-level agreement} & \multicolumn{7}{c}{Category-level agreement}\\ 
+           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG &      \# Obj & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG &  \# Cat\\
 \midrule
-         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
-       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
-           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
-      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
-           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
-       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
- animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
-\bottomrule
- all &  0.70 &  1.34 &  0.73            \\
+         people &  51.9 &  2.1 &  8.6 &   4.3 &   49.8 &  32.3 &   4533 &  43.8 &  2.9 &  88.5 &  45.1 &   20.0 &  10.9 &   55 \\
+         clothing &  63.9 &  1.6 &  6.4 &   3.2 &   70.2 &  52.6 &   2192 &  50.6 &  2.5 &  68.3 &  32.5 &   38.5 &  24.6 &   39 \\
+           home &  66.4 &  1.5 &  6.3 &   3.1 &   78.5 &  58.8 &   6292 &  50.7 &  2.7 &  90.6 &  42.6 &   39.3 &  24.9 &   89 \\
+      buildings &  66.9 &  1.5 &  6.9 &   3.0 &   72.6 &  55.5 &    967 &  47.8 &  2.9 &  59.9 &  27.2 &   27.8 &  19.2 &   36 \\       
+                  food &  71.3 &  1.3 &  5.5 &   2.9 &   62.9 &  52.1 &   1975 &  47.0 &  2.5 &  31.5 &  15.0 &   29.3 &  19.3 &   92 \\
+              vehicles &  72.0 &  1.1 &  4.7 &   2.4 &   71.1 &  60.2 &   4552 &  56.5 &  2.0 &  63.3 &  30.0 &   18.4 &  17.9 &   49 \\
+        animals,plants &  91.3 &  0.4 &  2.7 &   1.5 &   93.8 &  88.0 &   4804 &  67.6 &  1.5 &  26.5 &  12.3 &   28.1 &  25.7 &   89 \\
+       \midrule
+       all &  69.7 &  1.3 &  5.7 &   2.9 &   72.8 &  58.7 &  25315 &  52.8 &  2.4 &  58.2 &  27.8 &   29.4 &  20.9 &  449 \\
 
 \bottomrule
-\end{tabular}
-\caption{Agreement in object names for objects of different domains, if applicable, synsets with maximal and minimal agreement (top \%) are shown }
+\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG categories (i.e.\ after grouping objects by their VG name) }
 \label{tab:agree}
@@
 
-Table \ref{tab:agree} shows that, overall, our annotators achieve a fair amount of agreement in the object naming choices.
-The domain where annotators agree most is the animal domain, which, interestingly, happens to be the domain that has been mostly discussed in the object naming literature.
-\sz{...
-much more to say}
+%Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
 
-Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
+\subsection{Qualitative Analysis}
 
-\subsection{Lexical relations}
-
-In this section, we take a closer look at the lexical variation we observe in our data set.
-We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
-These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
-For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
-\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
-w_n$ constitute the less frequent alternatives of $w_{top}$.
-The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
-The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain.
-
-The naming variants can be grouped according to their lexical relation, as follows:
-
-\begin{itemize}
-\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
-\item \textbf{hyponymy}: e.g.\ man vs. person
-\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
-\item \textbf{no relation}: e.g.\  desk vs. apple
-\end{itemize}
-
-\begin{table*}
-
-%\begin{tabular}{lll}
-%\toprule
-%       relation &  types & tokens \\
-%\midrule
-%synonymy &  0.01 &  0.09 \\
-%co-hyponymy &  0.03 &  0.07 \\
-%hypernymy &  0.06 &  0.35 \\
-%not-covered &  0.19 &  0.04 \\
-%crossclassified &  0.70 &  0.47 \\
-%\bottomrule
-%\end{tabular}
-% \small
-% \begin{tabular}{llll}
-% \toprule
-%         relation & \% types & \% tokens & av. depth \\
-% \midrule
-%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
-%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
-%         synonymy &  0.015 &  0.121 &       1.000 \\
-% \bottomrule
-% \end{tabular}
-
-\begin{tabular}{l|ll|ll|ll|ll|ll}
+\begin{table}
+\small
+\begin{tabular}{lp{4.8cm}r}
 \toprule
-      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
-         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
+VG name &  top5 MN names &  n$_{obj}$  \\
 \midrule
- people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
- clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
- animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
- food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
- vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
- home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
- buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
- \hline
- all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
+\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
+ giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
+ zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
+ cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
+\midrule
+\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
+ booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
+ cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
+ robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
+  \midrule
+  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
+ sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
+ pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
+ necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
+ \midrule
+   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
+ shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
+ bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
+ vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
 \bottomrule
 \end{tabular}
-
-\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please.
-Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens?
-And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes.
-This way we'll be able to see differences across domains.}}
-\label{tab:rel}
-\end{table*}
-
-\begin{table*}
-\small
-\begin{tabular}{lp{13cm}}
-\toprule
-                         category &                                                                                                                                                                                                                    most frequent naming variants \\
-
-\midrule
- people &  woman -- person (3594), man -- person (3546), boy -- child (3243), woman -- girl (2328), girl -- child (1985), woman -- tennis player (1277), man -- player (1273), man -- boy (1214), skateboarder -- skater (1194), man -- t-shirt (1143) \\
- food &  pizza -- food (1883), sandwich -- food (1123), hotdog -- food (540), pizza -- cheese (457), pizza -- plate (430), salad -- food (402), sandwich -- burger (398), hotdog -- sandwich (351), sandwich -- bread (318), cake -- food (286) \\
- home &  couch -- sofa (4090), desk -- table (3448), carpet -- floor (1697), bench -- chair (1401), desk -- keyboard (1380), counter -- table (1201), table -- desk (1135), counter -- countertop (1101), table -- counter (906), rug -- carpet (895) \\
- buildings &  house -- building (1160), building -- house (511), bridge -- train (326), bridge -- overpass (235), house -- window (161), house -- home (123), tent -- canopy (120), building -- castle (101), bridge -- building (98), bridge -- pole (85) \\
- vehicles &  airplane -- plane (11194), plane -- airplane (3829), motorcycle -- bike (2624), airplane -- jet (1319), boat -- ship (1301), truck -- car (1095), car -- vehicle (874), motorcycle -- wheel (861), truck -- vehicle (718), truck -- wheel (716) \\
- clothing &  shirt -- t-shirt (2914), jacket -- coat (2396), jacket -- shirt (1552), jacket -- suit (1168), suit -- jacket (1029), shirt -- jacket (813), shirt -- tie (723), shirt -- man (487), shirt -- dress (462), shirt -- sweater (450) \\
- animals\_plants &  cow -- bull (515), sheep -- goat (486), cow -- animal (445), giraffe -- animal (380), bird -- parrot (349), sheep -- animal (294), sheep -- lamb (282), horse -- animal (269), cat -- animal (237), bird -- seagull (231) \\
-\bottomrule
-\end{tabular}\caption{Most frequent naming variants for each category}
-\label{tab:exvariants}
-\end{table*}
-
-Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).
-
-We use WordNet to extract lexical relations between the naming variants in our data set.
-Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below).
-Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy.
-For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
-\sz{should we call this co-hyponymy or co-hierarchical relation?}
-
-\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}
-
-Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
-Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
-\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
-This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
-Our data suggests that co-hierarchical variation is really important too.
-
-\subsection{The ``no relation'' case}
-
-We manually annotated the 100 most frequent name pairs in the ``no relation'' case.
-Table~\ref{tab:crossclass} shows that, in this category, one third of the pairs do refer to the same object, but the relationship is not captured in WordNet.
-Most of these cases are arguably coverage issues of WordNet, which doesn't capture the co-hyponymy of \textit{horse}-\textit{donkey} or the fact that \textit{vehicle} is hypernym of \textit{train}.\gbt{I find this really weird...
-also some other cases I annotated.
-It sounds like I should have listened more carefully to Carina when she suggested going down and up in the wordnet hierarchy (cf.\ the example of food-fruit).
-:/ Maybe we'd capture quite a bit of them if we did a more sophisticated querying of WordNet.
-To discuss.}
-% between \textit{hat}-\textit{beanie}.
-However, a substantial group is constituted by names whose denotations overlap even if they don't belong to the same category.
-These are typically alternative conceptualizations of objects: as a cat or a toy, as a kind of building or its function (\textit{building}-\textit{home}), or as a portion or a kind of food (\textit{pizza-slice}).
-
-\begin{table*}
-  \label{tab:crossclass}
-\small
-\begin{tabular}{lrl|lrl}
-  \toprule
-    \multicolumn{3}{c}{same object (215; 31\%)} & \multicolumn{3}{c}{not same object (485; 69\%)}\\
-\midrule
-co-hyponyms &          148  & horse-donkey, truck-jeep, skier-woman & adjacent   &          167 & building-clock, cat-pole, bed-chair\\
-overlapping &           22  & cat-toy, building-home, pizza-slice & supports.1 &          122 & couch-pillow, bowl-fruit, person-dress\\
-hypernym.1  &           18  & hat-beanie, jacket-tuxedo, building-hut & part.2     &102& plane-wings, pizza-cheese\\
-hypernym.2  &           16  & donut-pastry, train-vehicle, van-automobile & supports.2 &           64 & shirt-child, donut-plate, carpet-floor\\
-other       &            8  & sandwich-meal, plane-plain, umbrella-tent & part.1     &           20 & wheel-moped, sink-counter, bread-sub\\
-	    & 		    & & other      &           10 & plane-flight, horse-wood\\
-\bottomrule
-\end{tabular}
-\caption{Relations between words or objects when the variants refer to the same object (left) or not (right).}
-\end{table*}
-
-Still, 69\% of the annotated pairs arguably do not denote the same object.
-Here we find problems HUMANS MAKE SAME ``ERRORS'' AS MACHINES -- REFERENTIAL UNCERTAINTY IN THE ABSENCE OF CONTEXT (discuss as planned with Carina).
-
-Interesting name pairs:
-
-\begin{itemize}
-\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
-\item field - grass: same (reverse); how to distinguish?
-\item dog - pet (different conceptualizations; classified as ``hypernym.2'')
-\item airplane - flight, plane - flight (classified as ``other'').
-\end{itemize}
-
-Most of the cases are co-hyponyms with categories that are easily confused, such as \textit{horse}-\textit{donkey}, \textit{truck}-\textit{jeep}.
-In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.
+\caption{Qualitative examples for VG names and their most frequent corresponding responses in the MN data set (percentages shown in brackets), canonical means that the VG name is the top name in MN, and non-canonical vice versa}
+\end{table}
 

### 2019-05-13 papers/EMNLP2019/analysis2.tex
separated analysis in 2 parts, + an astonishing new result

\subsection{Lexical relations}

In this section, we take a closer look at the lexical variation we observe in our data set. We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain.

The naming variants can be grouped according to their lexical relation, as follows:

\begin{itemize}
\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
\item \textbf{hyponymy}: e.g.\ man vs. person
\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
\item \textbf{no relation}: e.g.\  desk vs. apple
\end{itemize}

\begin{table*}

%\begin{tabular}{lll}
%\toprule
%       relation &  types & tokens \\
%\midrule
%synonymy &  0.01 &  0.09 \\
%co-hyponymy &  0.03 &  0.07 \\
%hypernymy &  0.06 &  0.35 \\
%not-covered &  0.19 &  0.04 \\
%crossclassified &  0.70 &  0.47 \\
%\bottomrule
%\end{tabular}
% \small
% \begin{tabular}{llll}
% \toprule
%         relation & \% types & \% tokens & av. depth \\
% \midrule
%  co-hyponymy (closure, max depth=10) &  0.889 &  0.551 &       3.479 \\
%     hyponymy (closure, max depth=10) &  0.097 &  0.328 &       2.204 \\
%         synonymy &  0.015 &  0.121 &       1.000 \\
% \bottomrule
% \end{tabular}

\begin{tabular}{l|ll|ll|ll|ll|ll}
\toprule
      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
\midrule
 people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
 clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
 animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
 food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
 vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
 home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
 buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
 \hline
 all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
\bottomrule
\end{tabular}

\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please. Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens? And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes. This way we'll be able to see differences across domains.}}
\label{tab:rel}
\end{table*}

Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).

We use WordNet to extract lexical relations between the naming variants in our data set.
Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below). Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy. 
For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
\sz{should we call this co-hyponymy or co-hierarchical relation?}

\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}

Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
Our data suggests that co-hierarchical variation is really important too.

\subsection{The ``no relation'' case}

We manually annotated the 100 most frequent name pairs in the ``no relation'' case. Table~\ref{tab:crossclass} shows that, in this category, one third of the pairs do refer to the same object, but the relationship is not captured in WordNet. 
Most of these cases are arguably coverage issues of WordNet, which doesn't capture the co-hyponymy of \textit{horse}-\textit{donkey} or the fact that \textit{vehicle} is hypernym of \textit{train}.\gbt{I find this really weird... also some other cases I annotated. It sounds like I should have listened more carefully to Carina when she suggested going down and up in the wordnet hierarchy (cf.\ the example of food-fruit). :/ Maybe we'd capture quite a bit of them if we did a more sophisticated querying of WordNet. To discuss.}
% between \textit{hat}-\textit{beanie}.
However, a substantial group is constituted by names whose denotations overlap even if they don't belong to the same category. These are typically alternative conceptualizations of objects: as a cat or a toy, as a kind of building or its function (\textit{building}-\textit{home}), or as a portion or a kind of food (\textit{pizza-slice}).

Still, 69\% of the annotated pairs arguably do not denote the same object. Here we find problems HUMANS MAKE SAME ``ERRORS'' AS MACHINES -- REFERENTIAL UNCERTAINTY IN THE ABSENCE OF CONTEXT (discuss as planned with Carina).

Interesting name pairs:

\begin{itemize}
\item storefront - store: strictly speaking it's part-whole, but how can one distinguish between the two? 
\item field - grass: same (reverse); how to distinguish?
\item dog - pet (different conceptualizations; classified as ``hypernym.2'')
\item airplane - flight, plane - flight (classified as ``other'').
\end{itemize}

Most of the cases are co-hyponyms with categories that are easily confused, such as \textit{horse}-\textit{donkey}, \textit{truck}-\textit{jeep}.
In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.

### 2019-05-13 analysis/agreement_table.py

@@ -41,6 +41,7 @@ def make_df(filename):
     vg_overlap = []
     nanno = []
     ntypes = []
+    ntypesmin1 = []
 
     for ix,row in resdf.iterrows():
 
@@ -52,12 +53,16 @@ def make_df(filename):
         vg_overlap.append(row['spellchecked'][row['vg_obj_name']])
         nanno.append(sum(row['spellchecked'].values()))
         ntypes.append(len(row['spellchecked'].keys()))
+        min1types = [k for k in row['spellchecked'].keys() if row['spellchecked'][k] > 1]
+        ntypesmin1.append(len(min1types))
+
 
     resdf['vg_is_max'] = vg_is_common
     resdf['vg_mean'] = vg_prop
     resdf['vg_overlap'] = vg_overlap
     resdf['n_anno'] = nanno
     resdf['n_types'] = ntypes
+    resdf['n_types_min1'] = ntypesmin1
     resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
     resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
 
@@ -73,13 +78,14 @@ def make_agreement_table(resdf):
 
     tablerows.append(('all',\
 
-                     str("%.2f"%(np.mean(resdf['percent_agree'])*100)),\
-                     str("%.2f"%np.mean(resdf['snodgrass'])),\
-                     str("%.2f"%np.mean(resdf['n_types'])),\
-                     str("%.2f"%((np.sum(resdf['vg_is_max'])/nobjects)*100)),\
-                     str("%.2f"%((np.sum(resdf['vg_mean'])/nobjects)*100)),\
-                     str("%.2f"%((np.sum(resdf['vg_overlap'])/np.sum(resdf['n_anno']))*100))
-                     ))
+                     str("%.1f"%(np.mean(resdf['percent_agree'])*100)),\
+                     str("%.1f"%np.mean(resdf['snodgrass'])),\
+                     str("%.1f"%np.mean(resdf['n_types'])),\
+                     str("%.1f"%np.mean(resdf['n_types_min1'])),\
+                     str("%.1f"%((np.sum(resdf['vg_is_max'])/nobjects)*100)),\
+                     str("%.1f"%((np.sum(resdf['vg_mean'])/nobjects)*100)),\
+                     str(len(resdf))
+                    ))
 
[…]

### 2019-05-13 analysis/load_results.py
--

@@ -134,32 +134,3 @@ def process_hits(hitfile):
     for hit in hitlist:
         hit2images[hit['HIT']['HITId']] = hit['Images']
     return hit2images
-
-
-def check_spelling(answers):
-    d = answers
-    misspelled = spell.unknown(d.keys())
-    ok = {w:d[w] for w in d.keys() if not w in misspelled}
-    #print(misspelled)
-    #print(ok)
-    
-    for mis in misspelled:
-        #print("Checking:",mis)
-        cands = spell.candidates(mis)
-        #print("Cand:",cands)
-        corrected = False
-        for c in ok:
-            if c in cands:
-                #print("YAY")
-                ok[c] += d[mis]
-                corrected = True
-                break
-        if not corrected:
-            ok[mis] = d[mis]
-            
-    clean_answers = Counter()
-    for w in ok:
-        lem_w = Lem.lemmatize(w)
-        clean_answers[lem_w] += ok[w]
-        
-    return clean_answers

### 2019-05-13 papers/EMNLP2019/analysis2.tex

@@
+Previous work on large-scale collections of labels or names of objects has (explicitly or implicitly) assumed that once naming data is canonical, linguistic alternatives of the canonical name can simply be retrieved from existing taxonomies like e.g.\ WordNet.
+If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
+Hence, in this Section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
+
 \subsection{Lexical relations}
@@
 
-\begin{table*}
+\begin{table}
+\small
+\begin{tabular}{lcc|cc}
+\toprule
+ & \multicolumn{2}{c}{all MN variants} &  \multicolumn{2}{c}{MN $n > 10$} \\
+        relation & \%token &    \%types & \%token &    \%types \\
+\midrule
+\multicolumn{2}{c}{\it easy to recover}\\
+ meronymy &  0.3 &  0.9 &  0.8 &  1.0 \\
+ synonymy &  1.8 &  6.4 &  2.5 &  7.2 \\
+ hypernymy &  8.8 &  28.2 &  11.0 &  31.3 \\
+\midrule
+\multicolumn{2}{c}{\it difficult to recover}\\
+holonymy.1 &  0.2 &  0.8 &  0.3 &  0.9 \\
+ co-hyponymy &  4.8 &  6.2 &  6.0 &  6.4 \\
+ hyponymy &  4.9 &  6.6 &  5.5 &  6.9 \\
+ \midrule
+ \multicolumn{2}{c}{\it not recoverable}\\
+ name not covered &  7.8 &  2.8 &  5.8 &  2.1 \\
+ rel not covered &  71.3 &  48.1 &  68.0 &  44.2 \\
+\bottomrule
 
+\end{tabular}
 %\begin{tabular}{lll}
@@
 
-\begin{tabular}{l|ll|ll|ll|ll|ll}
-\toprule
-      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
-         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
-\midrule
- people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
- clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
- animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
- food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
- vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
- home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
- buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
- \hline
- all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
-\bottomrule
-\end{tabular}
+%\begin{tabular}{l|ll|ll|ll|ll|ll}
+%\toprule
+%      & \multicolumn{2}{c}{crossclassified} & \multicolumn{2}{c}{co-hyponymy} & \multicolumn{2}{c}{hypernymy} & \multicolumn{2}{c}{not-covered} & \multicolumn{2}{c}{synonymy} \\
+%         domain & typ & tok & typ & tok & typ & tok & typ &  tok & typ & tok \\
+%\midrule
+% people &  0.725 &  0.618 &  0.019 &  0.032 &  0.051 &  0.293 &  0.200 &  0.038 &  0.005 &  0.019 \\
+% clothing &  0.709 &  0.661 &  0.020 &  0.046 &  0.045 &  0.195 &  0.219 &  0.085 &  0.008 &  0.012 \\
+% animals\_plants &  0.679 &  0.461 &  0.032 &  0.102 &  0.111 &  0.365 &  0.167 &  0.058 &  0.011 &  0.014 \\
+% food &  0.590 &  0.433 &  0.031 &  0.033 &  0.104 &  0.432 &  0.267 &  0.089 &  0.009 &  0.013 \\
+% vehicles &  0.635 &  0.329 &  0.026 &  0.083 &  0.059 &  0.239 &  0.271 &  0.089 &  0.008 &  0.260 \\
+% home &  0.672 &  0.644 &  0.026 &  0.072 &  0.040 &  0.130 &  0.254 &  0.097 &  0.009 &  0.057 \\
+% buildings &  0.780 &  0.725 &  0.026 &  0.038 &  0.045 &  0.156 &  0.138 &  0.058 &  0.011 &  0.022 \\
+% \hline
+% all &  0.731 &  0.574 &  0.033 &  0.057 &  0.076 &  0.256 &  0.147 &  0.050 &  0.013 &  0.064 \\
+%\bottomrule
+%\end{tabular}
 
-\caption{Lexical relations between naming variants according to WordNet, for the set of name pairs where both words can be found in WordNet and stand in a \sz{should we produce this table for the different domains?} \gbt{yes, please.
-Maybe do rows domains, columns lexical relations (synymymy, hyponymy, co-hyponymy, other, not in wordnet), with subcolumns for types and tokens?
-And do percentages over rows -- for each domain, how many of the variants we find fall into each of the classes.
-This way we'll be able to see differences across domains.}}
+\caption{Lexical relations between naming variants in WN and the VG name according to WordNet}
 \label{tab:rel}
-\end{table*}
+\end{table}
 

### 2019-05-14 papers/EMNLP2019/analysis.tex
changes to abstract; comments to analysis-agreement section

@@
-In this Section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
+In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
 Whereas traditional picture naming studies typically use a prototypical image per category and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
-Second, we will uses the existing annotation of names in VG to analyze agreement on the level of categories.
+Second, we will uses the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
 
@@
 \item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
-\item \textbf{N}: the average number of types in the response set of MN
+\item \textbf{N}: the average number of types in the response set of ManyNames
 \item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
-\item \textbf{top=VG}: the proportion of items where the top response in MN corresponds to the VG name
-\item \textbf{\% VG}: the average relative frequency of the VG name in the response set
+\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
+\item \textbf{\% VG}: the average relative frequency of the VisualGenome name in the response set
 
@@
 For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets.
-Furthermore, we compute \textbf{category-level agreement} by merging the response sets for all objects that have the same VG name and compute the measures over these aggregated response sets.
+Furthermore, we compute \textbf{category-level agreement} by merging the response sets for all objects that have the same VisualGenome name and compute the measures over these aggregated response sets.
+\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
 
@@
 On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices.
-Thus, for roughly 70\% of our objects, the most frequent response in MN corresponds to the original VG name and, similarly, the average frequency of the top response is also 70\%.
+Thus, for roughly 70\% of our objects, the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%.
 Generally, this seems to suggest that indeed many objects in our data set have a canonical name.
-At the same time, the average number of name types per object (5.7 and 2.9, when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that can be elicited for instances.
+At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
 Furthermore, the agreement varies quite considerably among domains:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement).
@@
 
-Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VG name, we obtain on average 28 types (with $n > 1)$, i.e.
+\gbt{Super-interesting results.}
+Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome name, we obtain on average 28 types (with $n > 1)$, i.e.
 27 variants of the original VG name.
-Surprisingly, here, only 29.4\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in MN, on average, prefer a different name.
+Surprisingly, here, only 29.4\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.
 Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.
-What does this discrepancy between the instance-level and category-level agreement in VG and MN naming choices mean?
-First of all, it suggests that the same original VG name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
+What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean?
+First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
 Second, this clearly shows that annotators in VG do not generally annotate the most canonical name and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
 \sz{think more ...}
+\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
+What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
+  That is, there are systematic properties of instances that make them have a single most salient name.
+  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
 
@@
 \subsection{Qualitative Analysis}
+
+\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.
 
@@
 \end{tabular}
-\caption{Qualitative examples for VG names and their most frequent corresponding responses in the MN data set (percentages shown in brackets), canonical means that the VG name is the top name in MN, and non-canonical vice versa}
+\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in the ManyNames data set (MN; percentages shown in brackets).
+``Canonical'' means that the VisualGenome name is the top name in ManyNames, and non-canonical vice versa.}
+\label{tab:qual}
 \end{table}
+
+\gbt{The non-canon.
+VG names suggest that people prefer more general names (``car $>$ sedan'', ``horse $>$ pony'', ``tie $>$ necktie'').
+Could be due to lexical availability (more general \ra more frequent \ra more available).
+This could be verified (using frequency).
+Hypothesis: In cases where top name != VG, the VG name is less general.
+Could be also a more general hypothesis: see if people prefer more frequent names in general.}
 

### 2019-05-14 papers/EMNLP2019/data-collection.tex
comments in intro on object naming in realistic scenes/context, needs to made a bit stronger maybe
pass over sect 2.1, sampling of images

@@
-We take data from \vgenome \cite{krishna2016visualgenome}, which aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
+We take data from \vgenome \cite{krishna2016visualgenome}, which
+% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+contains a dense region-based labeling of $108k$~images with object descriptions, attributes, and relationships, as well as question-answer pairs, all linked to WordNet synsets \cite{fellbaum1998wordnet}.
+\vgenome is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
+naturalistic images, as it has images of varying complexity, with close-ups as well as complex images with many objects.
+As common in Computer Vision, objects are identified via bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
+\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}
 
-% \gbt{START to be refined -- taken from sivl submission as is}
+\subsection{Sampling of Instances}
 
-% \vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-% It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
-
-% \begin{itemize}
-%      		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
-% 				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
-% 		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
-
-% \end{itemize}
-% \gbt{END to be refined -- taken from sivl submission as is}
-
-\subsection{Sampling of Instances (Images/Objects)}
-
-We aimed at collecting a relatively large amount of naturalistic images (\textit{instances}) that depict common objects.
  % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
@@
 as basis.
-We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
-We added the \textsc{person} category because it is very frequent category in \vgenome.
+We selected seven domains: six from McRae et al.'s feature norms (REF), a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is very frequent category in \vgenome.
+% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
+% We added the \textsc{person} category because it is very frequent category in \vgenome.
 
-(As appropriate: We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).)
+Within each domain, we aimed at collecting instances at different levels in a taxonomy to cover a wide range of phenomena, but it is not straightforward to do so because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
+% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
+Instead, we defined a set of synsets that we would use to collect our object instances from \vgenome, balancing variability.
+From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vgenome object instances of different names.
+For example, \vgenome instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vgenome, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
 
-\paragraph{Collection nodes}
-% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
-We defined a set of \textit{collection nodes} which we would then use to collect our object instances from VG.
-
-We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ.
+We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds}, and we had XXX\gbt{Carina?} of them.
+We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
+We further only considered objects whose bounding box covered an area of~$20-90\%$ of the image.
+% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ.
 of instances labeled with the synset of the object name is meant.}
 
-First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}.
-From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names.
+% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}.
+% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names.
 For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
 
-\paragraph{Collection of instance candidates}
-Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
-The collection of such instances using the nodes was then straightforward: We retrieved all VG images  depicting an object whose name matches or is subsumed by one of the collection nodes. 
-We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions/phrases (e.g.,~\textsl{pink bird}). 
-We further only considered objects whose bounding box\footnote{TODO: need to be clear from the general description of VG what is meant.} had an area of~$20-90\%$ of the whole image area.
+%\paragraph{Collection of instance candidates}
+% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
 
-\paragraph{Sampling of instances}
-Finally, from this set of instances we sampled our final dataset of $31,093$~instances. 
-Sampling proceeded in dependence on the overall size of the individual collection seeds: 
-up to~$800$ objects per seed: all instances, but at most 500, are collected; more than~$800$ objects per seed: all instances, but at most~$1,000$, are collected.  \textbf{double-check}
+% \paragraph{Sampling of instances}
 
-\cs{END @ GBT}
+Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to 500 instances for seeds with up to 800 objects, and up to 1000 instances for larger seeds.
+\textbf{double-check}
+This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see next subsection).
 
-Table~\ref{tab:XXX} gives an overview of the collection nodes, XXX, XXX, grouped into $7$~domains.
-(\textbf{Report only dataset after round0, with a note in caption/footnote referring to the checkpoint pruning.})
-\gbt{I would put only a table with the final dataset, not the intermediate one (round0). That is, include a table with the 25K imgs (the 30K imgs were just our initial pool).}
+\gbt{Checked up to here}.
+
+Table~\ref{tab:XXX} gives an overview of the collection synsets, XXX, XXX, grouped into $7$~domains.
+(\textbf{Report only final dataset, with a note in caption/footnote referring to the checkpoint pruning.})
 
@@
 	\midrule
-	  ungulate.n.01 (2037) &  aircraft.n.01 (1208) &  furnishing.n.02 (5355) &  shirt.n.01 (968) &  house.n.01 (364) &  dish.n.02 (812) &  woman.n.01 (1768) \\
-	 horse.n.01 (833) &  train.n.01 (957) &  vessel.n.03 (525) &  overgarment.n.01 (786) &  bridge.n.01 (297) &  baked\_goods.n.01 (770) &  man.n.01 (1167) \\
-	  feline.n.01 (763) &  car.n.01 (727) &  kitchen\_utensil.n.01 (132) &  dress.n.01 (199) &  shelter.n.01 (169) &  foodstuff.n.02 (280) &  male\_child.n.01 (853) \\
-	 dog.n.01 (688) &  motorcycle.n.01 (564) &  crockery.n.01 (92) &  headdress.n.01 (135) &  restaurant.n.01 (58) &  vegetable.n.01 (48) &  athlete.n.01 (396) \\
-	  bird.n.01 (389) &  truck.n.01 (559) &  cutlery.n.02 (82) &  neckwear.n.01 (65) &  outbuilding.n.01 (31) &  edible\_fruit.n.01 (42) &  child.n.01 (333) \\
-	  flower.n.01 (44) &  boat.n.01 (499) &  tool.n.01 (72) &  robe.n.01 (27) &  hotel.n.01 (19) &  beverage.n.01 (23) &  creator.n.02 (11) \\
-	  rodent.n.01 (27) &  ship.n.01 (38) &  lamp.n.01 (34) &  glove.n.02 (7) &  housing.n.01 (17) &   &  professional.n.01 (5) \\
-	 insect.n.01 (12) &   &   &  footwear.n.01 (5) &  place\_of\_worship.n.01 (12) &   &   \\
-	  fish.n.01 (11) &   &   &   &   &   &   \\
+	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
+	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
+	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
+	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
+	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
+	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
+	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
+	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
+	  fish$_1$ (11) &   &   &   &   &   &   \\
 	\bottomrule
 \end{tabular}
-	\caption{Overview of our dataset: Collection nodes for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
+	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
 \end{table*}

### 2019-05-15 papers/EMNLP2019/analysis.tex
adds example of picture naming pic of cake

@@
 In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
-Whereas traditional picture naming studies typically use a prototypical image per category and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
+Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
 Second, we will uses the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
+\begin{figure}[t]
+	\centering
+	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
+	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vandertwart \& Snodgrass) \label{fig:picture_naming}}}
+\end{figure}
 

### 2019-05-15 papers/EMNLP2019/analysis.tex
corrects tex bug; modifies 1 sentence in intro

@@
 	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
-	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vandertwart \& Snodgrass) \label{fig:picture_naming}}}
+	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vanderwart \& Snodgrass) \label{fig:picture_naming}}
 \end{figure}

### 2019-05-15 papers/EMNLP2019/analysis.tex
comments, questions, typo fixes

@@
 In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
-Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
-Second, we will uses the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
+Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
+Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
 \begin{figure}[t]
@@
 \item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
+\cs{How is this defined?}
 \item \textbf{N}: the average number of types in the response set of ManyNames
 \item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
+\cs{alternatively we could show a plot going from 1 to, let's say, $>10$}
 \item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
@@
 \gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
+\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}
 
@@
 On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices. 
-Thus, for roughly 70\% of our objects, the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%.
+Thus, for roughly 70\% of our objects (\textbf{std=?}), the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%.
 Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
 At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
-Furthermore, the agreement varies quite considerably among domains:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement).
+Furthermore, the agreement varies quite considerably among domains \cs{refer to std}:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement of over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement).
 The people domain, on the other hand, is subject to much more variation and agreement is dramatically lower here, and comes close to 50\% for \% top.
@@
 \gbt{Super-interesting results.}
-Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome name, we obtain on average 28 types (with $n > 1)$, i.e.
+Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome name, we obtain on average 28 types (with $N_{>1})$, i.e.
 27 variants of the original VG name.
@@
 Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
+\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
+%
+\subsection{Discussion (for now)}
 What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
 First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
-Second, this clearly shows that annotators in VG do not generally annotate the most canonical name and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
+Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
 \sz{think more ...}
@@
   However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
+\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}
+
+\cs{(?!?) With respect to implications for L+V  models on language *interpretation*: much lower agreement on object class-level than on instance-level speaks for using very fine-grained object annotations (as done in ILSVRC).
+	However, that naming variants are often not explained/recoverable by hierarchical relations questions in how far models can understand/interpret reference to objects using more general classes (i.e., names), despite being able to recognise an object's very specific class (e.g., ILSVRC synset).
+(Relevant?!?)}
 
@@
 \bottomrule
-\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG categories (i.e.\ after grouping objects by their VG name) }
+\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG categories (i.e.\ after grouping objects by their VG name) \cs{\textbf{std=?})}}
 \label{tab:agree}
@@
 \end{tabular}
-\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in the ManyNames data set (MN; percentages shown in brackets).
-``Canonical'' means that the VisualGenome name is the top name in ManyNames, and non-canonical vice versa.}
+\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets).
+``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
 \label{tab:qual}
@@
 Could be also a more general hypothesis: see if people prefer more frequent names in general.}
+\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}
+
+\cs{@Table~\ref{tab:agree} I still think that we could also have \%\ top with $N>1$ to give an idea as to how useful the data is for the people interested in using it for, e.g., model evaluation.
+For that, it is clear that crowdsourcing is noisy and before using it some outlier removal needs to be made.}
 

### 2019-05-15 papers/EMNLP2019/analysis2.tex
comments, questions, typo fixes

@@
 If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
-Hence, in this Section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
+Hence, in this section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
 
@@
 The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-In Table \ref{tab:exvariants}, we show the the naming variants with the highest raw token frequency for each domain.
+In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain.
 
@@
 
-We manually annotated the 100 most frequent name pairs in the ``no relation'' case.
+For each domain, we manually annotated the 100 most frequent name pairs in the ``no relation'' case.
 Table~\ref{tab:crossclass} shows that, in this category, one third of the pairs do refer to the same object, but the relationship is not captured in WordNet.

### 2019-05-15 analysis/agreement_table.py
changes in wordnet analysis

@@ -7,6 +7,7 @@ from collections import Counter
 import numpy as np
 import matplotlib.pyplot as plt
 import numpy as np
+from nltk.corpus import wordnet as wn
 
 def snodgrass_agreement(rdict,vocab,singletons=False):
 
@@ -142,10 +143,19 @@ def make_agreement_table(resdf):
 
 def make_synset_df(resdf):
 
+    objdf = pd.read_json('~/Downloads/objects.json.zip',compression='zip')
+    objdf = pd.DataFrame([obj for listobj in list(objdf['objects']) for obj in listobj])
+    objdf = objdf[objdf['synsets'].apply(lambda x: len(x) >0)]
+    objdf['synset'] = objdf['synsets'].apply(lambda x: x[0])
+    objdf['name'] = objdf['names'].apply(lambda x: x[0])
+    name2synset = dict(list(zip(objdf['name'],objdf['synset'])))
+    #name2lemmas = {n:[l._name for l in wn.synset(n).lemmas()] for n in name2synset}
+
     syn2resp = {}
     syn2synset = {}
     syn2domain = {}
     syncount = Counter()
+    syn2names = {}
 
     vg_is_common = []
     vg_prop = []
@@ -155,28 +165,34 @@ def make_synset_df(resdf):
     ntypesmin1 = []
 
     for ix,row in resdf.iterrows():
-        sn = row['vg_obj_name']
+        sn = name2synset[row['vg_obj_name']]
         if sn not in syn2resp:
             syn2resp[sn] = Counter()
             syn2domain[sn] = row['vg_domain']
             syn2synset[sn] = row['synset']
+        if sn not in syn2names:
+            syn2names[sn] = [l._name for l in wn.synset(sn).lemmas()]
+        if row['vg_obj_name'] not in syn2names[sn]:
+            syn2names[sn].append(row['vg_obj_name'])
         syn2resp[sn].update(row['spellchecked'])
         #syn2vg[sn][row['vg_obj_name']] += 1
         syncount[sn] += 1
 
     new_rows = []
     for sn in syn2resp:
-        new_rows.append((sn,syn2domain[sn],syn2synset[sn],syn2resp[sn],syncount[sn]))
+        new_rows.append((sn,syn2names[sn],syn2domain[sn],syn2synset[sn],syn2resp[sn],syncount[sn]))
 
-    syndf = pd.DataFrame(new_rows,columns=['vg_obj_name','vg_domain','synset','responses','n_images'])
[…]

### 2019-05-15 analysis/wordnet_analysis.py

@@ -5,6 +5,7 @@
 from nltk.corpus import wordnet as wn
 import pandas as pd
 from agreement_table import make_df
+from agreement_table import make_synset_df
 import os
 import json
 import sys
@@ -59,10 +60,10 @@ def vg_name_pairs(vg_name,rdict):
     return np_count
 
 
-def is_hyponym(w1,w2,max_depth=5):
+def is_hyponym(syns1,syns2,max_depth=5):
 
-    syns1 = wn.synsets(w1,pos="n")
-    syns2 = wn.synsets(w2,pos="n")
+    #syns1 = wn.synsets(w1,pos="n")
+    #syns2 = wn.synsets(w2,pos="n")
 
     for syn1 in syns1:
         hyp_closure = list(syn1.closure(hyp,depth=dpt))
@@ -72,11 +73,11 @@ def is_hyponym(w1,w2,max_depth=5):
                 return (True,syn1,syn2)
     return (False,0,0)
 
-def is_hypernym(w1,w2,max_depth=5):
+def is_hypernym(syns1,syns2,max_depth=5):
 
 
-    syns1 = wn.synsets(w1,pos="n")
-    syns2 = wn.synsets(w2,pos="n")
+    #syns1 = wn.synsets(w1,pos="n")
+    #syns2 = wn.synsets(w2,pos="n")
 
     for syn2 in syns2:
         hyp_closure = list(syn2.closure(hyp,depth=max_depth))
@@ -86,22 +87,23 @@ def is_hypernym(w1,w2,max_depth=5):
                 return (True,syn1,syn2)
     return (False,0,0)
 
-def is_synonym(w1,w2):
+def is_synonym(syns1,syns2):
 
-    syns1 = wn.synsets(w1,pos="n")
-    syns2 = wn.synsets(w2,pos="n")
+    #syns1 = wn.synsets(w1,pos="n")
+    #syns2 = wn.synsets(w2,pos="n")
 
     for syn2 in syns2:
 
         for syn1 in syns1:
-                if syn1 == syn2:
-                    return (True,syn1,syn2)
+            #print("synonym",syn1,syn2)
+            if syn1 == syn2:
+                return (True,syn1,syn2)
     return (False,0,0)
 
-def is_cohyponym(w1,w2,max_depth=1):
+def is_cohyponym(syns1,syns2,max_depth=1):
 
-    syns1 = wn.synsets(w1,pos="n")
[…]

### 2019-05-15 papers/EMNLP2019/analysis2.tex
big table with examples for no-rel-cases

@@
 \small
-\begin{tabular}{lcc|cc}
+\centering
+\begin{tabular}{llcc}
 \toprule
- & \multicolumn{2}{c}{all MN variants} &  \multicolumn{2}{c}{MN $n > 10$} \\
-        relation & \%token &    \%types & \%token &    \%types \\
+    &     relation & \% types & \% tok. \\
 \midrule
-\multicolumn{2}{c}{\it easy to recover}\\
- meronymy &  0.3 &  0.9 &  0.8 &  1.0 \\
- synonymy &  1.8 &  6.4 &  2.5 &  7.2 \\
- hypernymy &  8.8 &  28.2 &  11.0 &  31.3 \\
+\multirow{3}{*}{hierarchical} & meronym &  2.4 &  3.5 \\
+& synonym &  3.8 &  3.8 \\
+ & hypernym &  13.3 &  35.1 \\
  \midrule
-\multicolumn{2}{c}{\it difficult to recover}\\
-holonymy.1 &  0.2 &  0.8 &  0.3 &  0.9 \\
- co-hyponymy &  4.8 &  6.2 &  6.0 &  6.4 \\
- hyponymy &  4.9 &  6.6 &  5.5 &  6.9 \\
+ \multirow{3}{*}{less hierarchical} & holonym &  6.2 &  21.7 \\
+& co-hyponym &  7.4 &  13.7 \\
+ & hyponym &  8.6 &  14.7 \\
   \midrule
- \multicolumn{2}{c}{\it not recoverable}\\
- name not covered &  7.8 &  2.8 &  5.8 &  2.1 \\
- rel not covered &  71.3 &  48.1 &  68.0 &  44.2 \\
+ \multirow{2}{*}{non-hierarchical} & word-not-covered &  15.7 &  3.8 \\
+& complex relation &  73.1 &  59.0 \\
+
 \bottomrule
+\end{tabular}
 
-\end{tabular}
 %\begin{tabular}{lll}
@@
 
-\caption{Lexical relations between naming variants in WN and the VG name according to WordNet}
+\caption{Lexical relations of naming variants in MN to annotated VG synset, averaged over synsets}
 \label{tab:rel}
@@
 In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.
+
+\begin{figure*}
+\begin{minipage}[b]{0.5\linewidth}
+{\footnotesize
+\setlength{\tabcolsep}{1pt}
+\begin{tabular}{cp{4cm}p{4cm}p{4cm}}
+\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2343219_926143_supercat_unique.png}}  MN: desktop &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
+\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2350360_1042111_supercat_unique.png}} MN: table  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2389358_1261752_singleton_obj.png}}  MN: seat &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/1593011_2063521_singleton_obj.png}} MN: wood \\
+\textbf{sandwich} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2352086_856151_supercat_unique.png}} MN: burger  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2352833_1884120_supercat_unique.png}}  MN: plate &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2343230_2309969_supercat_unique.png}} MN: bun\\ 
+\textbf{girl} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2400735_406112_singleton_obj.png}} MN: t-shirt  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2329628_3363001_singleton_obj.png}}  MN: tennis player &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2315383_1055824_singleton_obj.png}} MN: kid\\ 
+\textbf{truck} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2317240_1022463_singleton_obj.png}} MN: wheel  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2410889_361670_singleton_obj.png}}  MN: bus &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2334129_965945_singleton_obj.png}} MN: trailer\\ 
+\textbf{bridge} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2349701_3192266_supercat_unique.png}} MN: train  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2322428_2930306_supercat_unique.png}}  MN: road &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2348679_2628081_supercat_unique.png}} MN: dock\\ 
+\textbf{bed} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2400919_1153609_singleton_obj.png}} MN: pillow  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2383991_529114_singleton_obj.png}}  MN: blanket &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{Figures/2343909_918810_singleton_obj.png}} MN: table\\
+
+\end{tabular}
+
+}
+\end{minipage}
+
+ \caption{\label{fig:ex}Examples from MN data set, where no relation between VG synset (in bold) and name annotation can be found}
+\end{figure*}

### 2019-05-15 analysis/wordnet_analysis.py

@@ -267,12 +267,14 @@ def add_rel_to_df(syndf,wn_vocab):
             if (not mname in row['vg_obj_names']):
             #mname in wn_vocab and \
                 rel,s1,s2 = get_syn_word_rel(vg_syn,mname,wn_vocab)
+                #if rel == 'hypernym':
+                #    print(rel,mname,s1,s2)
                 rel_typ_c[rel] += 1
                 rel_tok_c[rel] += row['responses'][mname]
 
                 if rel not in rel_synsets:
                     rel_synsets[rel] = []
-                rel_synsets[rel].append(s2)
+                rel_synsets[rel].append(mname)
 
         #print(rel_tok_c)
 
@@ -282,7 +284,7 @@ def add_rel_to_df(syndf,wn_vocab):
 
     syndf['rel_tokens'] = rel_token
     syndf['rel_types'] = rel_types
-    syndf['rel_synsets'] = rel_names
+    syndf['rel_names'] = rel_names
 
     return syndf
 
@@ -290,17 +292,16 @@ def add_rel_to_df(syndf,wn_vocab):
 def make_rel_table(syndf):
 
     outdf = []
-    rel2freq_types = {}
-    rel2freq_tokens = {}
+
+    relations = ['synonym','meronym','holonym','hypernym','hyponym','rel-not-covered','word-not-covered','co-hyponym']
+    rel2freq_types = {r:[] for r in relations}
+    rel2freq_tokens = {r:[] for r in relations}
     for ix,row in syndf.iterrows():
-        for rel in row['rel_tokens']:
-            if rel not in rel2freq_types:
-                rel2freq_types[rel] = []
-                rel2freq_tokens[rel] = []
-            total = sum(row['rel_tokens'].values())
+        total = sum(row['rel_tokens'].values())
+        totalt = sum(row['rel_types'].values())
+        for rel in rel2freq_types:
             rel2freq_tokens[rel].append(row['rel_tokens'][rel]/total)
-            total = sum(row['rel_types'].values())
-            rel2freq_types[rel].append(row['rel_types'][rel]/total)
+            rel2freq_types[rel].append(row['rel_types'][rel]/totalt)
 
     for p in rel2freq_types:
         row = [p]
@@ -313,10 +314,10 @@ def make_rel_table(syndf):
     print(outdf)
 
[…]

### 2019-05-15 papers/EMNLP2019/analysis2.tex
updated relation counts

@@
 \centering
-\begin{tabular}{llcc}
+\begin{tabular}{lcc}
 \toprule
-    &     relation & \% types & \% tok. \\
+         relation & \% types & \% token \\
 \midrule
-\multirow{3}{*}{hierarchical} & meronym &  2.4 &  3.5 \\
-& synonym &  3.8 &  3.8 \\
- & hypernym &  13.3 &  35.1 \\
- \midrule
- \multirow{3}{*}{less hierarchical} & holonym &  6.2 &  21.7 \\
-& co-hyponym &  7.4 &  13.7 \\
- & hyponym &  8.6 &  14.7 \\
-  \midrule
- \multirow{2}{*}{non-hierarchical} & word-not-covered &  15.7 &  3.8 \\
-& complex relation &  73.1 &  59.0 \\
-
+ meronym &  0.1 &  0.2 \\
+ holonym &  0.1 &  0.4 \\
+ synonym &  1.1 &  1.1 \\
+ hyponym &  2.2 &  3.8 \\
+ co-hyponym &  3.1 &  5.9 \\
+ hypernym &  10.5 &  27.7 \\
+ word-not-covered &  10.6 &  2.6 \\
+ rel-not-covered &  72.2 &  58.3 \\
 \bottomrule

### 2019-05-15 papers/EMNLP2019/analysis.tex
updated analysis table, + std, which is huge...

@@
 For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets.
-Furthermore, we compute \textbf{category-level agreement} by merging the response sets for all objects that have the same VisualGenome name and compute the measures over these aggregated response sets.
-\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
-\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}
+Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
+%\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
+%\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}
 
@@
 Thus, for roughly 70\% of our objects (\textbf{std=?}), the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%.
-Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
+%Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
+\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted).
+For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
 At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
@@
 \gbt{Super-interesting results.}
-Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome name, we obtain on average 28 types (with $N_{>1})$, i.e.
-27 variants of the original VG name.
-Surprisingly, here, only 29.4\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.
+Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e.
+variants of the original VG class.
+Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.
 Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
@@
 \begin{table*}
-\small
-\begin{tabular}{p{1.3cm}ccccccc|ccccccc}
+\footnotesize
+\begin{tabular}{p{1.3cm}cccccc|cccccc}
 \toprule
- & \multicolumn{7}{c|}{Instance-level agreement} & \multicolumn{7}{c}{Category-level agreement}\\ 
-           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG &      \# Obj & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG &  \# Cat\\
+ & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
+           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
 \midrule
-         people &  51.9 &  2.1 &  8.6 &   4.3 &   49.8 &  32.3 &   4533 &  43.8 &  2.9 &  88.5 &  45.1 &   20.0 &  10.9 &   55 \\
-         clothing &  63.9 &  1.6 &  6.4 &   3.2 &   70.2 &  52.6 &   2192 &  50.6 &  2.5 &  68.3 &  32.5 &   38.5 &  24.6 &   39 \\
-           home &  66.4 &  1.5 &  6.3 &   3.1 &   78.5 &  58.8 &   6292 &  50.7 &  2.7 &  90.6 &  42.6 &   39.3 &  24.9 &   89 \\
-      buildings &  66.9 &  1.5 &  6.9 &   3.0 &   72.6 &  55.5 &    967 &  47.8 &  2.9 &  59.9 &  27.2 &   27.8 &  19.2 &   36 \\       
-                  food &  71.3 &  1.3 &  5.5 &   2.9 &   62.9 &  52.1 &   1975 &  47.0 &  2.5 &  31.5 &  15.0 &   29.3 &  19.3 &   92 \\
-              vehicles &  72.0 &  1.1 &  4.7 &   2.4 &   71.1 &  60.2 &   4552 &  56.5 &  2.0 &  63.3 &  30.0 &   18.4 &  17.9 &   49 \\
-        animals,plants &  91.3 &  0.4 &  2.7 &   1.5 &   93.8 &  88.0 &   4804 &  67.6 &  1.5 &  26.5 &  12.3 &   28.1 &  25.7 &   89 \\
+            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
  \midrule
-       all &  69.7 &  1.3 &  5.7 &   2.9 &   72.8 &  58.7 &  25315 &  52.8 &  2.4 &  58.2 &  27.8 &   29.4 &  20.9 &  449 \\
-
+         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
+ animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
+       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
+       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
+      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
+           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
+           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
 \bottomrule
-\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG categories (i.e.\ after grouping objects by their VG name) \cs{\textbf{std=?})}}
+\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset) \cs{\textbf{std=?})}}
 \label{tab:agree}

### 2019-05-15 analysis/agreement_table.py

@@ -79,12 +79,15 @@ def make_agreement_table(resdf):
 
     tablerows.append(('all',\
 
-                     str("%.1f"%(np.mean(resdf['percent_agree'])*100)),\
+                     str("%.1f (%.1f)"%(np.mean(resdf['percent_agree'])*100,\
+                     np.std(resdf['percent_agree'])*100)),\
                      str("%.1f"%np.mean(resdf['snodgrass'])),\
                      str("%.1f"%np.mean(resdf['n_types'])),\
                      str("%.1f"%np.mean(resdf['n_types_min1'])),\
-                     str("%.1f"%((np.sum(resdf['vg_is_max'])/nobjects)*100)),\
-                     str("%.1f"%((np.sum(resdf['vg_mean'])/nobjects)*100)),\
+                     str("%.1f (%.1f)"%((np.sum(resdf['vg_is_max'])/nobjects)*100,
+                     np.std(resdf['vg_is_max'])*100)),\
+                     str("%.1f (%.1f)"%(((np.sum(resdf['vg_mean'])/nobjects)*100),
+                     np.std(resdf['vg_mean'])*100)),\
                      str(len(resdf))
                     ))
 
@@ -106,7 +109,8 @@ def make_agreement_table(resdf):
 
         tablerows.append((c,\
 
-                         str("%.1f"%(np.mean(catdf['percent_agree'])*100)),\
+                         str("%.1f (%.1f)"%(np.mean(catdf['percent_agree'])*100,
+                         np.std(catdf['percent_agree'])*100)),\
                          str("%.1f"%np.mean(catdf['snodgrass'])),\
                          str("%.1f"%np.mean(catdf['n_types'])),\
                          str("%.1f"%np.mean(catdf['n_types_min1'])),\

### 2019-05-16 papers/EMNLP2019/analysis.tex
comments on analysis, points to highlight

@@
+\gbt{Points to discuss in the paper, as discussed with Carina May 16:}
+
+\begin{itemize}
+\item Super high variance in the agreement.
+Higher agreement for instances, lower for classes.
+Suggests systematicities at the instance level that do not depend on the class.
+Hypothesis, supported by qualitative analysis (Figure 3): relevance of visual perceptual factors.
+E.g.: saliency, background/foreground (desk-keyboard; bridge-train); ``angle'' from which the object is shown (see girl-t-shirt example); \dots In addition, we also find aspects discussed by Psycholing, but at the level of the instance: Typicality (see truck-bus example, bridge-dock, bench-seat).
+\item Forget about WordNet.
+\item Implications for lang\&vision: 1) synset classification won't do (if the goal is to predict/label an object); 2) name classification won't do either; 3) ``mistakes'' done by models are also done by humans -- role of referential uncertainty.
+\end{itemize}
+
 In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
@@
 Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
-%\gbt{I'd call it ``name-level agreement'' -- it's not really category, is it?}
-%\cs{@Sina (referring to our discussion we've had) object class instead of category would imo be indeed clearer here}
+\gbt{@Sina, what are the synsets that you got here? Are they collection nodes, or the synset of the VG name as annotated in VG?}
 

### 2019-05-16 papers/EMNLP2019/data-collection.tex
complete draft section 2; puts supp material into separate file

@@
+% Number of images/objects:        25,596\\
+% Number of object names:  450\\
+% Number of collection nodes (synsets):    52 \\
+
 We take data from \vgenome \cite{krishna2016visualgenome}, which
@@
 as basis.
-We selected seven domains: six from McRae et al.'s feature norms (REF), a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is very frequent category in \vgenome.
+We selected images from seven domains: six based on McRae et al.'s feature norms (REF), a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is very frequent category in \vgenome.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 % Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
-Instead, we defined a set of synsets that we would use to collect our object instances from \vgenome, balancing variability.
+Instead, we defined a set of synsets (52 in total) that we would use to collect our object instances from \vgenome, balancing variability.
 From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vgenome object instances of different names.
@@
 
-We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds}, and we had XXX\gbt{Carina?} of them.
+We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds}, and we had 450 of them.
 We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
@@
 of instances labeled with the synset of the object name is meant.}
-
 % First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}.
@@
 For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
-
 %\paragraph{Collection of instance candidates}
 % Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
-
 % \paragraph{Sampling of instances}
-
 Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to 500 instances for seeds with up to 800 objects, and up to 1000 instances for larger seeds.
@@
 This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see next subsection).
-
-\gbt{Checked up to here}.
-
-Table~\ref{tab:XXX} gives an overview of the collection synsets, XXX, XXX, grouped into $7$~domains.
-(\textbf{Report only final dataset, with a note in caption/footnote referring to the checkpoint pruning.})
+Table~\ref{tab:overview_dataset1}shows the 7 domains together with the top 10 \vgenome names.
 
@@
 
-\begin{table*}
-\small
-	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
-	\toprule
-	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
-	\midrule
-	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
-	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
-	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
-	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
-	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
-	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
-	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
-	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
-	  fish$_1$ (11) &   &   &   &   &   &   \\
-	\bottomrule
-\end{tabular}
-	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
-\end{table*}
-
 % \begin{itemize}
@@
 
-Number of images/objects:        25,596\\
-Number of object names:  450\\
-Number of collection nodes (synsets):    52 \\
+\subsection{Elicitation Procedure}
 
-\subsection{Procedure} describe the crowdsourcing set-up and the task
-TODO: Footnote: we ran pilot experiments to design our experiment and instructions.
-\paragraph{Collection Method}
-\begin{itemize}
-	\item instructions; \\
-	Appendix~\ref{app:instructions} gives the instructions as they were presented to the annotators. 
-	\item each round: HIT of 10 instances, collect 9~annotations for each HIT
-	\item round 0 (with opt-outs) $\rightarrow$ pruning $\rightarrow$ rounds 1-3 (no opt-outs)\\
-	pruning: Based on given opt-outs: keep images with no OCCLUSION, at most BBOX is ambiguous twice, at most 17\% of names in plural form, most frequent names is of same domain as VG name (gives $25,596$, i.e., discard $5,497$ instances)
-	\item workers could only participate in one round, such as to avoid workers annotating an instance more than once. 
-\end{itemize}
-
-Overall $XX$~participants, each annotated between $XX$ and $XX$ instances. \gbt{Put mean or median instead of min-max}
-
-\subsection{Data}
-
-give an overview of the collected data
+To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk.
+In initial pilot studies, we found object identification via bounding boxes to be problematic.
+In some cases, the bounding box was not clear; in others, subjects named objects that were more salient than the one signaled by the bounding box (for instance, for a bounding box around a jacket, the man wearing it).
+We took special care of minimizing this issue, in two ways: Specifying the instructions such that subjects pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 names/object) in which we allowed subjects to indicate whether the objet was occluded or the bounding box unclear.
+The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
+We eliminated around 5.5K images based on pruning, obtaining the final dataset with 25,596 images.
+We then did 3 more collection rounds, obtaining a total of 36 names per image.
+Workers could only participate in one round, to avoid workers annotating an instance more than once.
+As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vgenome annotation and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language\&vision (see discussion in Sections~\ref{sec:analysis,??}).
+\gbt{TO DO: revise that this matches the narrative in the rest of the paper.}
+Overall $XX$ turkers took part in the data elicitation, each naming a median of XXX instances. \gbt{@Carina pls fill in.}
 

### 2019-05-16 papers/EMNLP2019/suppl_material.tex
complete draft section 2; puts supp material into separate file

%
% File emnlp2019.tex
%
%% Based on the style files for ACL 2019, which were
%% Based on the style files for EMNLP 2018, which were
%% Based on the style files for ACL 2018, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp-ijcnlp-2019}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}  %%% for including graphics
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}
\newcommand\confname{EMNLP-IJCNLP 2019}
\newcommand\conforg{SIGDAT}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//g: #1//}}}
\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}

\title{Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\section{Dataset: Supplementary Information}
\label{app:instructions}

Figures~\ref{fig:instructions1} and~\ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection). This yielded $25,596$ images, discarding $5,497$.

\begin{itemize}
\item they were not marked as occluded by any subject;
\item ``Bounding box is unclear'' was marked at most twice;
\item at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects);
\item the most frequent elicited name is of the same domain as the \vgenome name.
\end{itemize}

Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, XXX, XXX, grouped into the $7$~domains.
\gbt{@Carina, the table doesn't fit, maybe put one domain x row?}

\begin{table*}[htb]
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
	  fish$_1$ (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
      \end{table*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
  \caption{Instructions for AMT annotators for the first round.}
  \label{fig:instructions1}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$. They were accompanied by the FAQ in Figure~\ref{fig:faq}}
  \label{fig:instructions2}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round1+_p2.png}
  \caption{FAQ accompanying the instructions for AMT annotators for rounds~$2$ to~$4$.}
  \label{fig:faq}
\end{figure*}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-05-16 papers/EMNLP2019/analysis2.tex
starts to add some results in modeling

--- 2019-05-15 papers/EMNLP2019/analysis2.tex
@@
 \small
-\begin{tabular}{lcc|cc}
+\centering
+\begin{tabular}{lcc}
 \toprule
- & \multicolumn{2}{c}{all MN variants} &  \multicolumn{2}{c}{MN $n > 10$} \\
-        relation & \%token &    \%types & \%token &    \%types \\
+         relation & \% types & \% token \\
 \midrule
-\multicolumn{2}{c}{\it easy to recover}\\
- meronymy &  0.3 &  0.9 &  0.8 &  1.0 \\
- synonymy &  1.8 &  6.4 &  2.5 &  7.2 \\
- hypernymy &  8.8 &  28.2 &  11.0 &  31.3 \\
-\midrule
-\multicolumn{2}{c}{\it difficult to recover}\\
-holonymy.1 &  0.2 &  0.8 &  0.3 &  0.9 \\
- co-hyponymy &  4.8 &  6.2 &  6.0 &  6.4 \\
- hyponymy &  4.9 &  6.6 &  5.5 &  6.9 \\
- \midrule
- \multicolumn{2}{c}{\it not recoverable}\\
- name not covered &  7.8 &  2.8 &  5.8 &  2.1 \\
- rel not covered &  71.3 &  48.1 &  68.0 &  44.2 \\
+ meronym &  0.1 &  0.2 \\
+ holonym &  0.1 &  0.4 \\
+ synonym &  1.1 &  1.1 \\
+ hyponym &  2.2 &  3.8 \\
+ co-hyponym &  3.1 &  5.9 \\
+ hypernym &  10.5 &  27.7 \\
+ word-not-covered &  10.6 &  2.6 \\
+ rel-not-covered &  72.2 &  58.3 \\
 \bottomrule
+\end{tabular}
 
-\end{tabular}
 %\begin{tabular}{lll}
@@
 In some cases, the visual cues are not enough to distinguish between the categories, but the frequency of this phenomenon suggests that co-hyponyms can be used interchangeably.
+
+\begin{figure*}
+\begin{minipage}[b]{0.5\linewidth}
+{\footnotesize
+\setlength{\tabcolsep}{1pt}
+\begin{tabular}{cp{4cm}p{4cm}p{4cm}}
+\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
+\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
+\textbf{sandwich} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2352086_856151_supercat_unique.png}} MN: burger  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2352833_1884120_supercat_unique.png}}  MN: plate &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343230_2309969_supercat_unique.png}} MN: bun\\ 
+\textbf{girl} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2400735_406112_singleton_obj.png}} MN: t-shirt  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2329628_3363001_singleton_obj.png}}  MN: tennis player &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2315383_1055824_singleton_obj.png}} MN: kid\\ 
+\textbf{truck} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2317240_1022463_singleton_obj.png}} MN: wheel  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2410889_361670_singleton_obj.png}}  MN: bus &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334129_965945_singleton_obj.png}} MN: trailer\\ 
+\textbf{bridge} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2349701_3192266_supercat_unique.png}} MN: train  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2322428_2930306_supercat_unique.png}}  MN: road &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2348679_2628081_supercat_unique.png}} MN: dock\\ 
+\textbf{bed} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2400919_1153609_singleton_obj.png}} MN: pillow  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2383991_529114_singleton_obj.png}}  MN: blanket &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343909_918810_singleton_obj.png}} MN: table\\
+
+\end{tabular}
+
+}
+\end{minipage}
+
+ \caption{\label{fig:ex}Examples from MN data set, where no relation between VG synset (in bold) and name annotation can be found}
+\end{figure*}

### 2019-05-16 papers/EMNLP2019/modeling.tex
starts to add some results in modeling

\subsection{Experimental Setup}
\textbf{THIS IS VERY CRYPTIC}
\paragraph{Model}
We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}. 
It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
\iffalse
"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
Genome [21] data. To aid the learning of good feature
representations, we add an additional training output for
predicting attribute classes (in addition to object classes).
To predict attributes for region i, we concatenate the mean
pooled convolutional feature vi with a learned embedding
of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
attribute class plus a ‘no attributes’ class.
The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
bounding box regression outputs for both the RPN and the
final object class proposals respectively. We retain these
components and add an additional multi-class loss component to train the attribute predictor"
\fi

\paragraph{Data}
\begin{itemize}
	\item We use the softmax distribution for the VG object names, and ignore the distribution over attributes. 
	\item The authors manually cleaned the set of object names to remove those with poor detection performance.
	\item Set of classes: 1,600 object names
	Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes. (For those cases, we therefore would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy. )
	\item Image set and vocabulary: $XXX$~names are not in MN, i.e., our vocabulary (MN--VG) contains $XXX$~names. 
	We filtered out those images whose VG name was not found in MN--VG, which resulted in $24,585$~instances (note that of those $22,304$~images were also part of the training data of bottom-up)
\end{itemize}

\paragraph{Measures}
top: the model's top prediction
\begin{itemize}
	\item \textbf{top=VG} The average model accuracy on the VG names
	\item \textbf{top=MN-1} The average model accuracy on the top response in ManyNames
	\item \textbf{top$\in$MN} The average model accuracy to predict any name of the responses in ManyNames
	\item \textbf{KL} The average Kullback-Leibler divergence of the model's softmax output and the  distribution over ManyNames, estimated by normalizing the name counts per instance
\end{itemize}

We further compare the model on the set of instances where the VG names does not match the top response in MN.

Sets of instances: all images, not training, only those with VG != MN-1.

\paragraph{Results} 
\begin{table*}
	\small
	\begin{tabular}{l@{~}|rrrr|rrrr|rrrr}
				 &	\multicolumn{4}{c|}{All images ($24,585$)} 
				 & \multicolumn{4}{c|}{Images w/ VG != MN-1 ($6,280$)}
				 & \multicolumn{4}{c}{$\neg$Train images ($2,281$)} \\
		domain	 &  top=VG & top=MN-1 & top$\in$MN  &  KL
					&  top=VG & top=MN-1 & top$\in$MN  & KL
					&  top=VG & top=MN-1 & top$\in$MN  & KL\\
		\toprule
		all 	& 68.7 & 76.8 & 94.8 & 
				& 20.7 & 52.5 & 92.3 & 
				& 63.5	& 73.1	& 92.5 &\\
		\midrule
		... \\
		\bottomrule
	\end{tabular}
	\caption{Blabla	\label{tab:model}}
\end{table*}
\iffalse
Total sum of differences after score conversion to relevant classes: 156.810 (avg=0.006378)
Evaluation on VG (24585 instances):
Accuracy (top VG): 0.686678869229 (t: 16882, f: 7703, not found: 0)
Evaluation on YNI-1 (24585 instances):
Accuracy (top1 YNI): 0.768069961359 (t: 18883, f: 5702, not found: nan)
Evaluation on YNI-10 (24585 instances):
Accuracy (top10 YNI): 0.947813707545 (t: 23302, f: 1283, not found: nan)

Evaluation on VG -- only instances where topYNI != VG (6280):
Accuracy (top VG): 0.207006369427 (t: 1300, f: 4980, not found: 0)
Evaluation on YNI-1 -- only instances where topYNI != VG (6280):
Accuracy (top1 YNI): 0.525636942675 (t: 3301, f: 2979, not found: nan)
Evaluation on YNI-10 -- only instances where topYNI != VG (6280):
Accuracy (top10 YNI): 0.922929936306 (t: 5796, f: 484, not found: nan)

Evaluation VG on training images (22304)
Accuracy (top VG): 0.691983500717 (t: 15434, f: 6870, not found: 0)
Evaluation YNI-1 on training images (22304)
Accuracy (top1 YNI): 0.771879483501 (t: 17216, f: 5088, not found: nan)
Evaluation YNI-10 on training images (22304)
Accuracy (top10 YNI): 0.950098637016 (t: 21191, f: 1113, not found: nan)

Evaluation VG on NOT training images (2281)
Accuracy (top VG): 0.634809294169 (t: 1448, f: 833, not found: 0)
Evaluation YNI-1 on NOT training images (2281)
Accuracy (top1 YNI): 0.73081981587 (t: 1667, f: 614, not found: nan)
Evaluation YNI-10 on NOT training images (2281)
Accuracy (top10 YNI): 0.925471284524 (t: 2111, f: 170, not found: nan)

\fi

### 2019-05-17 papers/EMNLP2019/analysis.tex
looked at freq. thresholds, separated type counts (histograms) and agreement figures in analysis

--- 2019-05-15 papers/EMNLP2019/analysis.tex
@@
+%\gbt{Points to discuss in the paper, as discussed with Carina May 16:}
+%
+%\begin{itemize}
+%\item Super high variance in the agreement.
+Higher agreement for instances, lower for classes.
+Suggests systematicities at the instance level that do not depend on the class.
+Hypothesis, supported by qualitative analysis (Figure 3): relevance of visual perceptual factors.
+E.g.: saliency, background/foreground (desk-keyboard; bridge-train); ``angle'' from which the object is shown (see girl-t-shirt example); \dots In addition, we also find aspects discussed by Psycholing, but at the level of the instance: Typicality (see truck-bus example, bridge-dock, bench-seat).
+%\item Forget about WordNet.
+%\item Implications for lang\&vision: 1) synset classification won't do (if the goal is to predict/label an object); 2) name classification won't do either; 3) ``mistakes'' done by models are also done by humans -- role of referential uncertainty.
+%\end{itemize}
+
 In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
 Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
-Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
+Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of classes.
 \begin{figure}[t]
@@
 \end{figure}
+
+\subsection{Names, instances, classes}
+
+First of all, to see whether objects in ManyNames bear a canonical name, we simply count how many different names (i.e.\ types) are given to instances, and to all instances that have the same synset annotated in VisualGenome.
+As the data is collected via crowdsourcing and a certain amount of noise is to be expected, we apply different frequency thresholds on the response sets for instances and synsets.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, obtained with different thresholds (from 1 to 6).
+Without any frequency thresholding, the proportion of instances and classes that have a single name annotated is small, i.e.\ below 10\% in both cases.
+When raising the threshold up to a minimum of 4 occurences in the response set  for instances (meaning more than 10\% of the 36 annotations), the proportion of objects that really only have a single name annotated is considerably higher, but still below 50\%.
+Thus, as expected in a free annotation scenario, the MN data contains a certain number of low-frequency responses.
+The fact that even after applying a relatively strict frequency filter most objects have more than one name annotated indicates that there is a non-negligible  level of variation when different speakers name the same object.
+
+The amount of variation increases substantially when looking at the number of names we find for different synsets in Visual Genome, as is indicated by the histogram for type counts of synsets in Figure \ref{fig:ntypes}.
+Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency threshols.
+
+\begin{figure*}
+\begin{minipage}[b]{0.4\linewidth}
+\includegraphics[scale=.4]{Figures/types_instances.png}
+\end{minipage}
+\begin{minipage}[b]{0.6\linewidth}
+\includegraphics[scale=.4]{Figures/types_classes.png}
+\end{minipage}
+ \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, based on different frequency tresholds (applied on the level of instances and classes respectively)}
+\end{figure*}
 
@@
 \cs{How is this defined?}
-\item \textbf{N}: the average number of types in the response set of ManyNames
-\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
+%\item \textbf{N}: the average number of types in the response set of ManyNames
+%\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
 \cs{alternatively we could show a plot going from 1 to, let's say, $>10$}
@@
 \footnotesize
-\begin{tabular}{p{1.3cm}cccccc|cccccc}
+%\begin{tabular}{p{1.3cm}cccccc|cccccc}
+%\toprule
+% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
+%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
+%\midrule
+%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
+% \midrule
+%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
+% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
+%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
+%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
+%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
+%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
+%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
+%\bottomrule
+%\end{tabular}
+
+\begin{tabular}{lcccc|cccc}
 \toprule
- & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
-           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
+ & \multicolumn{4}{c|}{Instance-level agreement} & \multicolumn{4}{c}{Class-level agreement}\\ 
+         domain &         \%top &    H &       top=VG &          \%VG &         \%top &    H &       top=VG &          \%VG \\
 \midrule
-            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
- \midrule
-         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
- animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
-       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
-       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
-      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
-           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
-           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
+            all &  78.5 (21.5) &  0.7 &  72.8 (44.5) &  65.1 (36.1) &  58.9 (21.9) &  1.8 &  32.7 (46.9) &  23.2 (27.1) \\
+ animals\_plants &  95.8 (11.4) &  0.1 &         93.8 &         92.1 &  74.3 (22.5) &  1.0 &         29.5 &         25.8 \\
+      buildings &  79.0 (21.1) &  0.7 &         72.6 &         64.8 &  53.5 (19.4) &  2.2 &         32.3 &         22.1 \\
+           home &  76.3 (20.6) &  0.8 &         78.5 &         67.0 &  56.4 (20.3) &  2.1 &         45.9 &         29.9 \\
+           food &  79.8 (20.5) &  0.7 &         62.9 &         57.0 &  52.7 (21.1) &  1.9 &         31.1 &         20.8 \\
+       vehicles &  79.0 (19.9) &  0.6 &         71.1 &         65.6 &  58.6 (17.0) &  1.7 &         21.4 &         21.1 \\
+         people &  64.4 (21.8) &  1.2 &         49.8 &         39.3 &  51.1 (19.6) &  2.2 &         24.4 &         12.9 \\
+       clothing &  73.9 (18.5) &  0.9 &         70.2 &         60.2 &  56.2 (17.2) &  1.9 &         40.5 &         26.0 \\
 \bottomrule
-\end{tabular}\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset) \cs{\textbf{std=?})}}
+\end{tabular}
+
+\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 3)}
 \label{tab:agree}

### 2019-05-17 analysis/agreement_table.py

@@ -36,6 +36,8 @@ def make_df(filename):
     resdf['clean'] = resdf['clean'].apply(lambda x: Counter(eval(x)))
     resdf['canon'] = resdf['canon'].apply(lambda x: Counter(eval(x)))
 
+    resdf['spellchecked_min3'] = resdf['spellchecked'].apply(lambda x: Counter({k:x[k] for k in x if x[k] > 2}))
+
     vocab_counter = Counter()
     vg_is_common = []
     vg_prop = []
@@ -49,7 +51,7 @@ def make_df(filename):
         vocab_counter += row['spellchecked']
         max_name = row['spellchecked'].most_common(1)[0][0]
         vg_is_common.append(int(max_name == row['vg_obj_name']))
-        vg_weight = row['spellchecked'][row['vg_obj_name']]/sum(row['spellchecked'].values())
+        vg_weight = row['spellchecked_min3'][row['vg_obj_name']]/sum(row['spellchecked_min3'].values())
         vg_prop.append(vg_weight)
         vg_overlap.append(row['spellchecked'][row['vg_obj_name']])
         nanno.append(sum(row['spellchecked'].values()))
@@ -65,7 +67,9 @@ def make_df(filename):
     resdf['n_types'] = ntypes
     resdf['n_types_min1'] = ntypesmin1
     resdf['snodgrass'] = resdf['spellchecked'].apply(lambda x: snodgrass_agreement(x,{},True))
+    resdf['snodgrass_min3'] = resdf['spellchecked_min3'].apply(lambda x: snodgrass_agreement(x,{},True))
     resdf['percent_agree'] = resdf['spellchecked'].apply(lambda x: percent_agreement(x))
+    resdf['percent_agree_min3'] = resdf['spellchecked_min3'].apply(lambda x: percent_agreement(x))
 
     return resdf
 
@@ -79,16 +83,19 @@ def make_agreement_table(resdf):
 
     tablerows.append(('all',\
 
-                     str("%.1f (%.1f)"%(np.mean(resdf['percent_agree'])*100,\
-                     np.std(resdf['percent_agree'])*100)),\
-                     str("%.1f"%np.mean(resdf['snodgrass'])),\
-                     str("%.1f"%np.mean(resdf['n_types'])),\
-                     str("%.1f"%np.mean(resdf['n_types_min1'])),\
+                     #str("%.1f (%.1f)"%(np.mean(resdf['percent_agree'])*100,\
+                     #np.std(resdf['percent_agree'])*100)),\
[…]

### 2019-05-17 papers/EMNLP2019/analysis.tex
updated analysis table

@@
 
-\subsection{Measures}
+\subsection{Agreement}
 
@@
 \cs{How is this defined?}
-%\item \textbf{N}: the average number of types in the response set of ManyNames
+\begin{equation}
+H = \sum_{i=1}^k p_i\ log_2(1/p_i)
+\end{equation}
+
+\item \textbf{N}: the average number of types in the response set of ManyNames
 %\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
@@
 \gbt{@Sina, what are the synsets that you got here? Are they collection nodes, or the synset of the VG name as annotated in VG?}
-
-\subsection{Results}
 
@@
 %
-\subsection{Discussion (for now)}
-What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
-First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
-Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
-\sz{think more ...}
-\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
-What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
-  That is, there are systematic properties of instances that make them have a single most salient name.
-  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
-\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}
 
-\cs{(?!?) With respect to implications for L+V  models on language *interpretation*: much lower agreement on object class-level than on instance-level speaks for using very fine-grained object annotations (as done in ILSVRC).
-	However, that naming variants are often not explained/recoverable by hierarchical relations questions in how far models can understand/interpret reference to objects using more general classes (i.e., names), despite being able to recognise an object's very specific class (e.g., ILSVRC synset).
-(Relevant?!?)}
-
-\begin{table*}
-\footnotesize
-%\begin{tabular}{p{1.3cm}cccccc|cccccc}
-%\toprule
-% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
-%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
-%\midrule
-%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
-% \midrule
-%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
-% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
-%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
-%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
-%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
-%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
-%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
-%\bottomrule
-%\end{tabular}
-
-\begin{tabular}{lcccc|cccc}
-\toprule
- & \multicolumn{4}{c|}{Instance-level agreement} & \multicolumn{4}{c}{Class-level agreement}\\ 
-         domain &         \%top &    H &       top=VG &          \%VG &         \%top &    H &       top=VG &          \%VG \\
-\midrule
-            all &  78.5 (21.5) &  0.7 &  72.8 (44.5) &  65.1 (36.1) &  58.9 (21.9) &  1.8 &  32.7 (46.9) &  23.2 (27.1) \\
- animals\_plants &  95.8 (11.4) &  0.1 &         93.8 &         92.1 &  74.3 (22.5) &  1.0 &         29.5 &         25.8 \\
-      buildings &  79.0 (21.1) &  0.7 &         72.6 &         64.8 &  53.5 (19.4) &  2.2 &         32.3 &         22.1 \\
-           home &  76.3 (20.6) &  0.8 &         78.5 &         67.0 &  56.4 (20.3) &  2.1 &         45.9 &         29.9 \\
-           food &  79.8 (20.5) &  0.7 &         62.9 &         57.0 &  52.7 (21.1) &  1.9 &         31.1 &         20.8 \\
-       vehicles &  79.0 (19.9) &  0.6 &         71.1 &         65.6 &  58.6 (17.0) &  1.7 &         21.4 &         21.1 \\
-         people &  64.4 (21.8) &  1.2 &         49.8 &         39.3 &  51.1 (19.6) &  2.2 &         24.4 &         12.9 \\
-       clothing &  73.9 (18.5) &  0.9 &         70.2 &         60.2 &  56.2 (17.2) &  1.9 &         40.5 &         26.0 \\
-\bottomrule
-\end{tabular}
-
-\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 3)}
-\label{tab:agree}
-\end{table*}
-
-%Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
-
-\subsection{Qualitative Analysis}
+\paragraph{Qualitative Analysis}
 
@@
 
+\subsection{Discussion (for now)}
+What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
+First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
+Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
+\sz{think more ...}
+\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
+What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
+  That is, there are systematic properties of instances that make them have a single most salient name.
+  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
+\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}
+
+\cs{(?!?) With respect to implications for L+V  models on language *interpretation*: much lower agreement on object class-level than on instance-level speaks for using very fine-grained object annotations (as done in ILSVRC).
+	However, that naming variants are often not explained/recoverable by hierarchical relations questions in how far models can understand/interpret reference to objects using more general classes (i.e., names), despite being able to recognise an object's very specific class (e.g., ILSVRC synset).
+(Relevant?!?)}
+
+\begin{table*}
+\footnotesize
+%\begin{tabular}{p{1.3cm}cccccc|cccccc}
+%\toprule
+% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
+%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
+%\midrule
+%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
+% \midrule
+%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
+% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
+%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
+%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
+%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
+%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
+%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
+%\bottomrule
+%\end{tabular}
+
+\begin{tabular}{lccccc|ccccc}
+\toprule
+ & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
+          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
+\midrule
+            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
+       vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
+      buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
+       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
+           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
+         people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
+           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
+ animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
+\bottomrule
+\end{tabular}
+
+\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
+\label{tab:agree}
+\end{table*}
+
+%Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
+
 \cs{@Table~\ref{tab:agree} I still think that we could also have \%\ top with $N>1$ to give an idea as to how useful the data is for the people interested in using it for, e.g., model evaluation.

### 2019-05-17 analysis/agreement_table.py

@@ -36,7 +36,7 @@ def make_df(filename):
     resdf['clean'] = resdf['clean'].apply(lambda x: Counter(eval(x)))
     resdf['canon'] = resdf['canon'].apply(lambda x: Counter(eval(x)))
 
-    resdf['spellchecked_min3'] = resdf['spellchecked'].apply(lambda x: Counter({k:x[k] for k in x if x[k] > 2}))
+    resdf['spellchecked_min3'] = resdf['spellchecked'].apply(lambda x: Counter({k:x[k] for k in x if x[k] > 1}))
 
     vocab_counter = Counter()
     vg_is_common = []
@@ -85,16 +85,15 @@ def make_agreement_table(resdf):
 
                      #str("%.1f (%.1f)"%(np.mean(resdf['percent_agree'])*100,\
                      #np.std(resdf['percent_agree'])*100)),\
+                     str("%.1f"%np.mean(resdf['n_types_min1'])),\
                      str("%.1f (%.1f)"%(np.mean(resdf['percent_agree_min3'])*100,\
                      np.std(resdf['percent_agree_min3'])*100)),\
                      #str("%.1f"%np.mean(resdf['snodgrass'])),\
-                     str("%.1f"%np.mean(resdf['snodgrass_min3'])),\
+                     str("%.1f (%.1f)"%(np.mean(resdf['snodgrass_min3']),
+                     np.std(resdf['snodgrass_min3']))),\
                      #str("%.1f"%np.mean(resdf['n_types'])),\
-                     #str("%.1f"%np.mean(resdf['n_types_min1'])),\
-                     str("%.1f (%.1f)"%((np.sum(resdf['vg_is_max'])/nobjects)*100,
-                     np.std(resdf['vg_is_max'])*100)),\
-                     str("%.1f (%.1f)"%(((np.sum(resdf['vg_mean'])/nobjects)*100),
-                     np.std(resdf['vg_mean'])*100)),\
+                     str("%.1f"%((np.sum(resdf['vg_is_max'])/nobjects)*100)),\
+                     str("%.1f"%((np.sum(resdf['vg_mean'])/nobjects)*100)),\
                      #str(len(resdf))
                     ))
 
@@ -118,12 +117,13 @@ def make_agreement_table(resdf):
 
                          #str("%.1f (%.1f)"%(np.mean(catdf['percent_agree'])*100,
                          #np.std(catdf['percent_agree'])*100)),\
[…]

### 2019-05-17 papers/EMNLP2019/modeling.tex
Figures->figures; results in modeling

@@
 \paragraph{Measures}
-top: the model's top prediction
+\textsl{top}: the model's top prediction
 \begin{itemize}
-	\item \textbf{top=VG} The average model accuracy on the VG names
-	\item \textbf{top=MN-1} The average model accuracy on the top response in ManyNames
-	\item \textbf{top$\in$MN} The average model accuracy to predict any name of the responses in ManyNames
-	\item \textbf{KL} The average Kullback-Leibler divergence of the model's softmax output and the  distribution over ManyNames, estimated by normalizing the name counts per instance
+	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
+	\item \textbf{=MN-1} The average model accuracy of \textsl{top} on the top response in ManyNames
+	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
+	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
 \end{itemize}
 
-We further compare the model on the set of instances where the VG names does not match the top response in MN.
-
-Sets of instances: all images, not training, only those with VG != MN-1.
-
 \paragraph{Results} 
+We compare the model against a random baseline for the KL divergence, and against a most-frequent name baseline. 
+We further compare the model on the set of instances where the VG names does not match the top response in MN (block \mbox{VG$\neq$MN-1} in Table~\ref{tab:model}), and to those which were not part of the set of images used for training bottom-up ($\neg$Training).
+%
 \begin{table*}
+	\centering
 	\small
-	\begin{tabular}{l@{~}|rrrr|rrrr|rrrr}
-				 &	\multicolumn{4}{c|}{All images ($24,585$)} 
-				 & \multicolumn{4}{c|}{Images w/ VG != MN-1 ($6,280$)}
-				 & \multicolumn{4}{c}{$\neg$Train images ($2,281$)} \\
-		domain	 &  top=VG & top=MN-1 & top$\in$MN  &  KL
-					&  top=VG & top=MN-1 & top$\in$MN  & KL
-					&  top=VG & top=MN-1 & top$\in$MN  & KL\\
+\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
 	\toprule
-		all 	& 68.7 & 76.8 & 94.8 & 
-				& 20.7 & 52.5 & 92.3 & 
-				& 63.5	& 73.1	& 92.5 &\\
+	%{} &  All images-top=VG &  All images-top=MN-1 &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN-1 &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN-1 &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
+		& \multicolumn{12}{c}{Image subset} \\
+		&	\multicolumn{4}{c}{All ($24,585$)} 
+		& \multicolumn{4}{c}{VG$\neq$MN-1 ($6,280$)}
+		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
 	\midrule
-		... \\
+		Domain	 &  =VG & =MN-1 & $\in$MN  &  KL
+		&  =VG & =MN-1 & $\in$MN  & KL
+		&  =VG & =MN-1 & $\in$MN  & KL\\
+\midrule
+all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ \\
+home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
+food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
+buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
+vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
+animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
+clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
+people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
 \bottomrule
+%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
+Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
 \end{tabular}
-	\caption{Blabla	\label{tab:model}}
+\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN-1) and 6.9 ($\neg$Training)	\label{tab:model}}
 \end{table*}
-\iffalse
-Total sum of differences after score conversion to relevant classes: 156.810 (avg=0.006378)
-Evaluation on VG (24585 instances):
-Accuracy (top VG): 0.686678869229 (t: 16882, f: 7703, not found: 0)
-Evaluation on YNI-1 (24585 instances):
-Accuracy (top1 YNI): 0.768069961359 (t: 18883, f: 5702, not found: nan)
-Evaluation on YNI-10 (24585 instances):
-Accuracy (top10 YNI): 0.947813707545 (t: 23302, f: 1283, not found: nan)
-
-Evaluation on VG -- only instances where topYNI != VG (6280):
-Accuracy (top VG): 0.207006369427 (t: 1300, f: 4980, not found: 0)
-Evaluation on YNI-1 -- only instances where topYNI != VG (6280):
-Accuracy (top1 YNI): 0.525636942675 (t: 3301, f: 2979, not found: nan)
-Evaluation on YNI-10 -- only instances where topYNI != VG (6280):
-Accuracy (top10 YNI): 0.922929936306 (t: 5796, f: 484, not found: nan)
-
-Evaluation VG on training images (22304)
-Accuracy (top VG): 0.691983500717 (t: 15434, f: 6870, not found: 0)
-Evaluation YNI-1 on training images (22304)
-Accuracy (top1 YNI): 0.771879483501 (t: 17216, f: 5088, not found: nan)
-Evaluation YNI-10 on training images (22304)
-Accuracy (top10 YNI): 0.950098637016 (t: 21191, f: 1113, not found: nan)
-
-Evaluation VG on NOT training images (2281)
-Accuracy (top VG): 0.634809294169 (t: 1448, f: 833, not found: 0)
-Evaluation YNI-1 on NOT training images (2281)
-Accuracy (top1 YNI): 0.73081981587 (t: 1667, f: 614, not found: nan)
-Evaluation YNI-10 on NOT training images (2281)
-Accuracy (top10 YNI): 0.925471284524 (t: 2111, f: 170, not found: nan)
-
-\fi

### 2019-05-17 papers/EMNLP2019/analysis.tex
Figures->figures; results in modeling
new table with cool examples

@@
 
-\gbt{Super-interesting results.}
+%\gbt{Super-interesting results.}
 Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e.
@@
 Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
-\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
+%\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
 %
 
-\paragraph{Qualitative Analysis}
+\subsection{Variation and WordNet}
 
-\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.
+Previous work on large-scale collections of labels or names of objects has (explicitly or implicitly) assumed that once naming data is canonical, linguistic alternatives of the canonical name can simply be retrieved from existing taxonomies like e.g.\ WordNet.
+%If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
+Hence, in this section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
+%In this section, we take a closer look at the lexical variation we observe in our data set. 
+We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
+These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
+For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
+\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
+w_n$ constitute the less frequent alternatives of $w_{top}$.
+The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
+The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
+In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
+The naming variants can be grouped according to their lexical relation, as follows:
+
+\begin{itemize}
+\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
+\item \textbf{hyponymy}: e.g.\ man vs. person
+\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
+\item \textbf{no relation}: e.g.\  desk vs. apple
+\end{itemize}
 
@@
 \small
-\begin{tabular}{lp{4.8cm}r}
+\centering
+\begin{tabular}{lcc}
 \toprule
-VG name &  top5 MN names &  n$_{obj}$  \\
+         relation & \% types & \% token \\
 \midrule
-\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
- giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
- zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
- cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
-\midrule
-\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
- booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
- cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
- robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
-  \midrule
-  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
- sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
- pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
- necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
- \midrule
-   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
- shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
- bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
- vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
+% meronym &  0.1 &  0.2 \\
+% holonym &  0.1 &  0.4 \\
+ synonym &  1.1 &  1.1 \\
+ hyponym &  2.2 &  3.8 \\
+ co-hyponym &  3.1 &  5.9 \\
+ hypernym &  10.5 &  27.7 \\
+ word-not-covered &  10.6 &  2.6 \\
+ rel-not-covered &  72.2 &  58.3 \\
 \bottomrule
 \end{tabular}
-\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets).
-``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
-\label{tab:qual}
+\caption{Lexical relations of naming variants in MN to annotated VG synset, averaged over synsets}
+\label{tab:rel}
 \end{table}
 
-\gbt{The non-canon.
+Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).
+
+We use WordNet to extract lexical relations between the naming variants in our data set.
+Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below).
+Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy.
+For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
+\sz{should we call this co-hyponymy or co-hierarchical relation?}
+
+\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}
+
+Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
+Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
+\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
+This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
+Our data suggests that co-hierarchical variation is really important too.
+
+%\subsection{Qualitative Analysis}
+
+%\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.
+
+%\begin{table}
+%\small
+%\begin{tabular}{lp{4.8cm}r}
+%\toprule
+%VG name &  top5 MN names &  n$_{obj}$  \\
+%\midrule
+%\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
+% giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
+% zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
+% cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
+%\midrule
+%\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
+% booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
+% cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
+% robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
+%  \midrule
+%  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
+% sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
+% pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
+% necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
+% \midrule
+%   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
+% shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
+% bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
+% vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
+%\bottomrule
+%\end{tabular}
+%\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets).
+``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
+%\label{tab:qual}
+%\end{table}
+
+\begin{figure*}
+\begin{minipage}[b]{0.5\linewidth}
+{\footnotesize
+\setlength{\tabcolsep}{1pt}
+\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}
+%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
+%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
+%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
+%\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
+%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
+%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
+\multicolumn{4}{c}{\textbf{VG: sandwich}}\\
+ \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), food (5), burger (2), hamburger (2), meal (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} food (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), food (7), bun (4), sandwich (3), bread (2)\\ 
+\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20), building (11)  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\ 
+\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2321254_3438076_singleton_obj.png}} bed (36)  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2324306_3412337_singleton_obj.png}}  bed (16), bench (6), crib (5) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2342811_3485104_singleton_obj.png}}  bed (17), book (6), table (4), toy (3), bible (2), doll (2) & 
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
+\multicolumn{4}{c}{\textbf{VG: batter}}\\
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), person (3), baseball player (2) &
+  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), baseball player (7), batter (5), player (3), helmet (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\
+\multicolumn{4}{c}{\textbf{VG: robe}}\\
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &
+  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2)\\
+
+\end{tabular}
+
+}
+\end{minipage}
+
+ \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set}
+\end{figure*}
+
+%\gbt{The non-canon.
 VG names suggest that people prefer more general names (``car $>$ sedan'', ``horse $>$ pony'', ``tie $>$ necktie'').
@@
 Could be also a more general hypothesis: see if people prefer more frequent names in general.}
-\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}
+%\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}
 

### 2019-05-17 papers/EMNLP2019/analysis.tex

@@
 \begin{minipage}[b]{0.4\linewidth}
-\includegraphics[scale=.4]{Figures/types_instances.png}
+\includegraphics[scale=.4]{figures/types_instances.png}
 \end{minipage}
 \begin{minipage}[b]{0.6\linewidth}
-\includegraphics[scale=.4]{Figures/types_classes.png}
+\includegraphics[scale=.4]{figures/types_classes.png}
 \end{minipage}
@@
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), food (5), burger (2), hamburger (2), meal (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} food (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), food (7), bun (4), sandwich (3), bread (2)\\ 
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), \underline{food} (5), burger (2),  \underline{hamburger} (2),  \underline{meal} (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2)\\ 
 \multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
 \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20), building (11)  &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  \underline{building} (11)  &
 \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
@@
 \multicolumn{4}{c}{\textbf{VG: batter}}\\
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), person (3), baseball player (2) &
-  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), baseball player (7), batter (5), player (3), helmet (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
+  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
 \multicolumn{4}{c}{\textbf{VG: robe}}\\
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
   \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
 \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2)\\
+\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2)\\
 
@@
 
- \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set}
+ \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set, names that have a hierarchical relation to the VG synset in WordNet are underlined}
 \end{figure*}

### 2019-05-18 papers/EMNLP2019/analysis.tex
somewhat complete analysis section, discussion needs improvement

@@
 	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
-	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vanderwart \& Snodgrass) \label{fig:picture_naming}}
+	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies \cite{snodgrass} \label{fig:picture_naming}}
 \end{figure}
@@
 \subsection{Names, instances, classes}
+\label{subsec:counts}
 
-First of all, to see whether objects in ManyNames bear a canonical name, we simply count how many different names (i.e.\ types) are given to instances, and to all instances that have the same synset annotated in VisualGenome.
-As the data is collected via crowdsourcing and a certain amount of noise is to be expected, we apply different frequency thresholds on the response sets for instances and synsets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, obtained with different thresholds (from 1 to 6).
-Without any frequency thresholding, the proportion of instances and classes that have a single name annotated is small, i.e.\ below 10\% in both cases.
-When raising the threshold up to a minimum of 4 occurences in the response set  for instances (meaning more than 10\% of the 36 annotations), the proportion of objects that really only have a single name annotated is considerably higher, but still below 50\%.
-Thus, as expected in a free annotation scenario, the MN data contains a certain number of low-frequency responses.
-The fact that even after applying a relatively strict frequency filter most objects have more than one name annotated indicates that there is a non-negligible  level of variation when different speakers name the same object.
+Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the MN response set, i.e.
+a set of name types with annotation frequencies (max.
+36 annotations per object).
+See Figure \ref{fig:ex} for examples of object annotations.
+Based on the VisualGenome synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
 
-The amount of variation increases substantially when looking at the number of names we find for different synsets in Visual Genome, as is indicated by the histogram for type counts of synsets in Figure \ref{fig:ntypes}.
-Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency threshols.
+As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
+Since a certain amount of noise in the crowd-sourced MN data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e. how many objects or classes have at least $n$ names.
+Generally, without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, i.e.\ below 10\% in both cases.
+
+The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the MN data which, again, is expected in an annotation task where subjects are free to choose any response that would like to.
+Thus, when filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
+Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%, even when applying a strict frequency filter of 4.
+This indicates that there is non-negligible variation when different speakers name the same object, though the variation seems to be restricted to a manageable set of up to 5 names per object.
+
+However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure \ref{fig:ntypes} (right).
+Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency thresholds.
+This clearly indicates that different instances annotated with the same name and synset in VisualGenome trigger different naming variants.
+Examples illustrating this can be found in Figure \ref{fig:ex}, where e.g.
+the response sets for different instances of the class \textit{bridge} have no overlap except for the name \textit{bridge}.
+Implications of this finding will be discussed below in Section \ref{subsec:discuss}.
 
@@
 
+\begin{table*}
+\footnotesize
+%\begin{tabular}{p{1.3cm}cccccc|cccccc}
+%\toprule
+% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
+%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
+%\midrule
+%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
+% \midrule
+%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
+% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
+%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
+%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
+%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
+%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
+%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
+%\bottomrule
+%\end{tabular}
+
+\begin{tabular}{lccccc|ccccc}
+\toprule
+ & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
+          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
+\midrule
+            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
+            \midrule
+                     people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
+       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
+           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
+                 buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
+           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
+                  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
+ animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
+\bottomrule
+\end{tabular}
+
+\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
+\label{tab:agree}
+\end{table*}
+
 \subsection{Agreement}
 
-We compute the following agreement measures:
+As type counts give a rather rough indication for variation in object naming, we analyse the following agreement measures which account for the distribution of names in the response sets:
 
@@
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
-\item \textbf{$H$}: the $H$ agreement measure used previously in the psycholinguistic literature
-\cs{How is this defined?}
+\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, 0 is perfect agreement 
+%\cs{How is this defined?}
 \begin{equation}
@@
 \item \textbf{N}: the average number of types in the response set of ManyNames
-%\item \textbf{N$_{>1}$}: the average number of types, excluding types that have been annotated only once
-\cs{alternatively we could show a plot going from 1 to, let's say, $>10$}
 \item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
@@
 
-For measuring \textbf{instance-level agreement}, we consider all names annotated for an object as a response set and then average over these response sets.
-Furthermore, we compute \textbf{class-level agreement} by merging the response sets for all objects that have the same synset (given for the original VisualGenome name) and compute the measures over these aggregated response sets.
-\gbt{@Sina, what are the synsets that you got here? Are they collection nodes, or the synset of the VG name as annotated in VG?}
+Again, we measure instance-level and class-level agreement on response sets for objects and classes respectively.
+To account for potential noise, we filter the response sets for names with a frequency of 1 and use these to compute
+the various measures shown in Table \ref{tab:agree}.
+Generally, the agreement measures follow a similar pattern as the type counts discussed in \label{subsec:counts}:
+On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices, i.e.
+the dominant name is annotated by 75\% of the subjects and the original VisualGenome name has an average proportion of 62\% in the MN responses.
+On the class-level, however, the agreement is much lower, i.e.\ the average frequency of the dominant name drops to 56.4\% and the frequency of the VG name even more to 23.4\%.
+The $H$ measures indicates a fair amount of agreement for instances, which is a bit lower than the agreement found in picture norming studies on artificial images (e.g.
+\cite{snodgrass} report an average $H$ of 0.55).
+On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
 
-Table \ref{tab:agree} shows the analysis of the instance-level and category-level agreement.
-On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices. 
-Thus, for roughly 70\% of our objects (\textbf{std=?}), the most frequent response in ManyNames corresponds to the original VisualGenome name and, similarly, the average frequency of the top response is also 70\%.
 %Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
-\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted).
+%\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted).
 For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
-At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
-Furthermore, the agreement varies quite considerably among domains \cs{refer to std}:  in the animal domain, which is often discussed in the object naming literature, annotators achieve a very stable and robust agreement of over 90\% and an $H$ agreement which comes close to 0 (where 0 is perfect agreement).
-The people domain, on the other hand, is subject to much more variation and agreement is dramatically lower here, and comes close to 50\% for \% top.
+%At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
+Furthermore, Table \ref{tab:agree} reports the agreement measures compute separately for the different domains in the MN data.
+Two domains are particularly noteworthy: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particular low agreement.
+For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
+Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain.
+This indicates that the agreement measures are unstable for different instances and classes.
+The qualitative examples in Figure \ref{fig:ex} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
+The following Section will attempt to shed further light on the potential sources of this variation in object naming that we observe here.
 
-%\gbt{Super-interesting results.}
-Finally, the category-level agreement figures tell yet another story: when aggregating the responses for all objects with the same VisualGenome synset, we obtain on average 30 types (with $N_{>1})$, i.e.
-variants of the original VG class.
-Surprisingly, here, only 32.7\% of the aggregated response sets still have the VG name as the most frequent response, which means that for 70\% of the VG names, annotators in ManyNames, on average, prefer a different name.
-Likewise, the relative frequency of the top response drops considerably and $H$ increases from 1.3 for instance-level agreement to 2.4 on object-level agreement.  
-%\cs{Can we say more about what's going on in the people and vehicles domain, category-level, top=VG? E.g., put corresponding examples in Tab.\ref{tab:qual}}
-%
+\subsection{Specificity and other sources of variation}
 
-\subsection{Variation and WordNet}
-
-Previous work on large-scale collections of labels or names of objects has (explicitly or implicitly) assumed that once naming data is canonical, linguistic alternatives of the canonical name can simply be retrieved from existing taxonomies like e.g.\ WordNet.
-%If this was indeed the case, it would be feasible (and probably even desirable) to canonicalize object names during dataset collection, without loosing too much information about linguistic variations in natural object naming scenarios (like e.g.\ referring expression generation).
-Hence, in this section, we investigate to what extent the variation in object naming that we find in our MN data set (see previous Section) is covered by WordNet.
-%In this section, we take a closer look at the lexical variation we observe in our data set. 
-We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
+Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity.
+ We now investigate to what extent the naming variation in the MN data set (see previous Section) can be attributed and explained with specificity. 
+ Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional MN names, and check whether the MN name stand in a hierarchical taxonomic relation to 
+ the object name's synset in VisualGenome.
+%%In this section, we take a closer look at the lexical variation we observe in our data set. 
+%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
 These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
-For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
+%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
 \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
@@
 The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
-The naming variants can be grouped according to their lexical relation, as follows:
+%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
+%The naming variants can be grouped according to their lexical relation, as follows:
+%
+%\begin{itemize}
+%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
+%\item \textbf{hyponymy}: e.g.\ man vs. person
+%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
+%\item \textbf{no relation}: e.g.\  desk vs. apple
+%\end{itemize}
 
-\begin{itemize}
-\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
-\item \textbf{hyponymy}: e.g.\ man vs. person
-\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
-\item \textbf{no relation}: e.g.\  desk vs. apple
-\end{itemize}
+Table \ref{tab:rel} shows how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
+Luckily, the coverage of WordNet for our name data is satisfactory, i.e. we were able to analyze 90\% of the name types which account for 97\% of the annotation tokens.
+Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the VG annotators.
+But overall, the most frequent case by far is that no hierarchical relation between the name and the synset can be retrieved from WordNet.
+Thus, strikingly, most of the naming variation in MN is \textit{not} related to different preferences in levels of specificity, but to other sources.
 
@@
 % holonym &  0.1 &  0.4 \\
+ word-not-covered &  10.6 &  2.6 \\
+\midrule
  synonym &  1.1 &  1.1 \\
@@
  hypernym &  10.5 &  27.7 \\
- word-not-covered &  10.6 &  2.6 \\
  rel-not-covered &  72.2 &  58.3 \\
@@
 
-Research on object naming following the idea of entry-level categories has, essentially, exclusively looked at names that stand in a hierarchical relation (i.e.\ hyponymy/hypernymy).
+Based on the examples in Figure \ref{fig:ex}, we will now provide a qualitative discussion of other types of variation we found in the data.
 
-We use WordNet to extract lexical relations between the naming variants in our data set.
-Unfortunately, this means that we have to exclude a certain portion of the data as either (i) one of the name is not covered in WordNet, (ii) we cannot find a lexical relation between the two names (see below).
-Also, we had to be relatively permissive with respect to the definition of hyponymy/co-hyponymy.
-For instance, to analyze \textit{giraffe} as a hyponym of \textit{animal} we have to look at the closure of the hyponyms of \textit{animal} with a depth of 8 (in WordNet).
-\sz{should we call this co-hyponymy or co-hierarchical relation?}
+\begin{description}
+\item[referential uncertainty:] despite our various attempts to filter objects that are occluded or have unclear bounding boxes \sz{see Section REF}, we still find many examples where annotators were uncertain about the identity of the object indicated by the bounding box and named an adjacent or a supporting object (e.g.
+\textit{bed-book}) or a part of the target object (\textit{batter-helmet})
+\item[crossclassification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-sandwich})
+\item[conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (e.g. \textit{bed-bench},\textit{sandwich-hotdog})
+\item[metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (e.g.
+\textit{sandwich-basket}, \textit{bed-bed sheet})
+\item[issues with WordNet:] due to WordNet's fine-grained hierarchy, it can be difficult to retrieve certain loosely related synonyms or hypernyms (e.g. \textit{robe-dress})
+\end{description}
 
-\sz{include Table that reports counts of the naming variants, coverage in WordNet etc.} \gbt{I think it'd be best to put the out-of-wordnet info in the Lexical relations table -- this way we have everything in one place.}
-
-Table \ref{tab:rel} shows the distribution of lexical relations for those naming variants that we were able to analyze with WordNet.
-Both in terms of their types and token frequency, the naming variants that instantiate a (loose) co-hyponymy relation are by far the most frequent.
-\sz{discuss in more detail, discuss: to what extent is this an artefact of WordNet?}
-This is really interesting: most research on object naming, to date, has focussed on hyponymy/hypernymy, i.e. variation that relates to hierarchical relations between object names.
-Our data suggests that co-hierarchical variation is really important too.
+As it is non-trivial to separate this cases in an automatic or manual manner, we leave a precise quantitative analysis of these phenomena for future work.
 
@@
 \subsection{Discussion (for now)}
-What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
-First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
-Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
+\label{subsec:discuss}
+
+Summarizing our analysis, we find that the object naming variation attested in our MN corpus offers some new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (psycho-)linguistics.
+Whereas existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets, our data elicited from many speakers can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and can often not simply be retrieved from existing taxonomies like e.g.\ WordNet.
+For theoretical research, our data offers a lot of variation in object naming that cannot be explained by adopting a traditional taxonomy-driven and hierarchical view.
+
+So, \textit{do objects in real-world images have a canonical name?} As it turns out, this general question calls for a somewhat differentiated answer.
+When taking other, similarly subtle and similarly free annotation tasks in NLP as a benchmark (e.g. \sz{????})
+our analysis does indeed suggest that there are systematic properties of instances even in complex visual scenes that often make them have a dominant or strongly preferred name.
+  At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical, see e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
+Given that we find much lower agreement on object class-level than on instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
+However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).
+Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising crossclassification, metonymy and potentially other sources of variation.
+
+%What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
+%First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
+%Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
 \sz{think more ...}
-\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
+%\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
 What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
-  That is, there are systematic properties of instances that make them have a single most salient name.
-  However, I expect that this result will be very influenced by referential uncertainty (in single images, it will mostly be clear that it's a man, but in some it may be unclear \ra high instance agreement, low category agrement.}
-\cs{I don't think that 70\% is high. E.g., the ResNet has a top-1 error rate of 25\% on ILSVRC 2015.}
-
-\cs{(?!?) With respect to implications for L+V  models on language *interpretation*: much lower agreement on object class-level than on instance-level speaks for using very fine-grained object annotations (as done in ILSVRC).
-	However, that naming variants are often not explained/recoverable by hierarchical relations questions in how far models can understand/interpret reference to objects using more general classes (i.e., names), despite being able to recognise an object's very specific class (e.g., ILSVRC synset).
-(Relevant?!?)}
-
-\begin{table*}
-\footnotesize
-%\begin{tabular}{p{1.3cm}cccccc|cccccc}
-%\toprule
-% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
-%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
-%\midrule
-%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
-% \midrule
-%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
-% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
-%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
-%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
-%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
-%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
-%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
-%\bottomrule
-%\end{tabular}
-
-\begin{tabular}{lccccc|ccccc}
-\toprule
- & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
-          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
-\midrule
-            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
-       vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
-      buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
-       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
-           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
-         people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
-           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
- animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
-\bottomrule
-\end{tabular}
-
-\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
-\label{tab:agree}
-\end{table*}
 
@@
 
-\cs{@Table~\ref{tab:agree} I still think that we could also have \%\ top with $N>1$ to give an idea as to how useful the data is for the people interested in using it for, e.g., model evaluation.
+%\cs{@Table~\ref{tab:agree} I still think that we could also have \%\ top with $N>1$ to give an idea as to how useful the data is for the people interested in using it for, e.g., model evaluation.
 For that, it is clear that crowdsourcing is noisy and before using it some outlier removal needs to be made.}

### 2019-05-18 papers/EMNLP2019/modeling.tex

@@
+Our findings in Sections~\ref{sec:analysis} and~\ref{sec:taxo} are cause to question the appropriateness of the standard evaluation procedure of object naming or  detection methods, in which models are compared against a single symbol.
+%
+%Let us assume that we can define, for each instance, it's canonical name as the most frequently produced one. 
+Specifically, the assumption that there exists a canonical name for individual objects (instances), cannot be made in general.
+This was shown by the high standard deviation in terms of the relative frequency of an instance's top response (column \%top in Table~\ref{tab:agree}), as well as an average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG}).
+Further, as discussed in Section~\ref{sec:taxo}, many name alternatives are not hierarchically related to the VG name. 
+Hence, to distinguish automatically whether a predicted name is a true error (e.g.,\ XX) or actually a valid alternative to the given "ground truth" (e.g.,\ XX), simple methods, such as querying a taxonomic hierarchy, do not suffice.
+\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern}
+
+\cs{TODO: Say something about type disagreements on class-level, after having written the results discussion.}
+
+\cs{Ah, we still should have a comparison model with above argumentation :/.}
+
+\textbf{TBC, after results discussion done}
 \subsection{Experimental Setup}
 \textbf{THIS IS VERY CRYPTIC}
+
 \paragraph{Model}

### 2019-05-18 papers/EMNLP2019/modeling.tex
messy modeling motivation; a few comments on results

--- 2019-05-17 papers/EMNLP2019/modeling.tex
@@
+% mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)
+Our findings in Sections~\ref{sec:analysis} and~\ref{sec:taxo} are reason to question the appropriateness of the standard, single-label approach in visual object naming and categorization methods. 
+Even the assumption that there at least exists a canonical name, i.e., a  name on which the majority of people would agree, for individual visual objects (/or image regions(?)) (instances) is disputable.
+This was shown by the high standard deviation in terms of the relative frequency of an instance's top response (column \%top in Table~\ref{tab:agree}), as well as an average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG}).
+%
+The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
+It would be desirable to explicitly assess model towards their ability to account for naming variants of an instance/how different people would name the same object/image regions (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs.
+dog, animal, hat?).
+%
+
+The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
+previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}, and the references therein).
+
+% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
+% Wang et al.: ".
+The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
+[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy.
+\cs{remove or move to related work?
+also sentence to Ordonez}]
+\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF).
+\cs{maybe remove, since it is not that relevant?}}
+%
+% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
+%
+However, as discussed in Section~\ref{sec:taxo}, we found that many name alternatives are not hierarchically related to the VG name. 
+Hence, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically whether a predicted name is a true error (e.g.,\ XX) or actually a valid alternative to the given "ground truth" (e.g.,\ XX).
+\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
+%
+\cs{TODO: Say something about type disagreements on class-level, after having written the results discussion.}
+%
+\cs{Ah, we still should have a comparison model with above argumentation :/.}
+%
+Here, we will use ManyNames (MN) as evaluation data, and assess whether a SOTA model can account for the naming variants of individual objects in MN. 
+In contrast to above work where the models were trained on multiple labels, we use a classification model that was trained on single names--VG's object names (and attributes).
+%, i.e., it did not see multiple names for individual objects during training.
+By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
+And due to the nature of our collected data, the relations may not stand in a hierarchical relation.
+
+%We hypothesize that this is the case, see finding regarding the influence of visual cues. 
+%Get an intuition in how far models are able to identify an object by one of it's possible names (gt=dog, is system still able to identify the object if the name is puppy?).
+\cs{And with this argumentation, we ideally we compare to a model fine-tuned on our data...}
+
 \subsection{Experimental Setup}
@@
 We further compare the model on the set of instances where the VG names does not match the top response in MN (block \mbox{VG$\neq$MN-1} in Table~\ref{tab:model}), and to those which were not part of the set of images used for training bottom-up ($\neg$Training).
+Note that the latter two sets are disjoint. 
 %
@@
 	\midrule
+			 &  \multicolumn{2}{c}{single-label}
+			 &  \multicolumn{2}{c}{multi-label}
+			 &  \multicolumn{2}{c}{single-label}
+			 &  \multicolumn{2}{c}{multi-label}
+			 &  \multicolumn{2}{c}{single-label}
+			 &  \multicolumn{2}{c}{multi-label} \\
 		Domain	 &  =VG & =MN-1 & $\in$MN  &  KL
@@
 \end{table*}
+
+\begin{itemize}
+	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
+	\item VG!=MN-1 much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
+	\item for those more difficult images (VG!=MN-1), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
+	\item accuracy drops for notTrain (except for vehicles MN-1), but is still much better than VG!=MN-1  
+\end{itemize}

### 2019-05-19 papers/EMNLP2019/analysis.tex
pass over analysis section

@@
 
-In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
+In this section, we investigate to what extent names in VisualGenome and ManyNames can be considered canonical, i.e., to what extent speakers agree in their naming choices.
 Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
@@
 
-Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the MN response set, i.e.
+Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the ManyNames response set, i.e.
 a set of name types with annotation frequencies (max.
 36 annotations per object).
-See Figure \ref{fig:ex} for examples of object annotations.
+See Figure \ref{fig:ex-high-low-agreement} for examples of object annotations.
 Based on the VisualGenome synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
 
-As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
-Since a certain amount of noise in the crowd-sourced MN data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e. how many objects or classes have at least $n$ names.
-Generally, without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, i.e.\ below 10\% in both cases.
+% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
+%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.
+how many objects or classes have at least $n$ names, with different minimum frequency thresholds to account for possible noise in the crowdsourced data.
+Without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, below 10\% in both cases.
 
-The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the MN data which, again, is expected in an annotation task where subjects are free to choose any response that would like to.
-Thus, when filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
+The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the ManyNames data which, again, is expected in an annotation task where subjects are free to choose any response.
+When filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
 Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%, even when applying a strict frequency filter of 4.
-This indicates that there is non-negligible variation when different speakers name the same object, though the variation seems to be restricted to a manageable set of up to 5 names per object.
+This indicates that there is non-negligible variation when different speakers name the same object, and the variation seems to be restricted to a manageable set of up to 5 names per object.
 
@@
 This clearly indicates that different instances annotated with the same name and synset in VisualGenome trigger different naming variants.
-Examples illustrating this can be found in Figure \ref{fig:ex}, where e.g.
-the response sets for different instances of the class \textit{bridge} have no overlap except for the name \textit{bridge}.
+Examples illustrating this can be found in Figure \ref{fig:ex-high-low-agreement}.
 Implications of this finding will be discussed below in Section \ref{subsec:discuss}.
@@
 
-\caption{Agreement in naming measured on the level of instances and on the level of VG classes (i.e.\ after grouping objects by their VG synset), for filtered response sets (frequency threshold of 2)}
+\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vgenome synset), for filtered response sets (frequency threshold of 2)}
 \label{tab:agree}
@@
 
-As type counts give a rather rough indication for variation in object naming, we analyse the following agreement measures which account for the distribution of names in the response sets:
+%As type counts give a rather rough indication for variation in object naming, 
+We compute the following measures to check agreement on the object names:
 
@@
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
-\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, 0 is perfect agreement 
-%\cs{How is this defined?}
-\begin{equation}
-H = \sum_{i=1}^k p_i\ log_2(1/p_i)
-\end{equation}
+\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: $H = \sum_{i=1}^k p_i\ log_2(1/p_i)$
+
+% \begin{equation}
+% H = \sum_{i=1}^k p_i\ log_2(1/p_i)
+% \end{equation}
 
@@
 
-Again, we measure instance-level and class-level agreement on response sets for objects and classes respectively.
-To account for potential noise, we filter the response sets for names with a frequency of 1 and use these to compute
-the various measures shown in Table \ref{tab:agree}.
-Generally, the agreement measures follow a similar pattern as the type counts discussed in \label{subsec:counts}:
-On the instance-level, our annotators achieve a fair amount of overlap in their object naming choices, i.e.
-the dominant name is annotated by 75\% of the subjects and the original VisualGenome name has an average proportion of 62\% in the MN responses.
-On the class-level, however, the agreement is much lower, i.e.\ the average frequency of the dominant name drops to 56.4\% and the frequency of the VG name even more to 23.4\%.
-The $H$ measures indicates a fair amount of agreement for instances, which is a bit lower than the agreement found in picture norming studies on artificial images (e.g.
-\cite{snodgrass} report an average $H$ of 0.55).
+Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
+To account for potential noise, we filter out names with a frequency of 1 from the response sets.
+As shown in Table \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in the previous section:
+On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\% of the responses on average, and the original VisualGenome name having an average frequency of 62\% in the ManyNames responses.
+On the class level, however, the agreement is much lower: The average frequency of the top name drops to 56.4\% and the frequency of the \vgenome name even more, to 23.4\%.
+The $H$ measures indicates a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \cite{snodgrass} report an average $H$ of 0.55).
 On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
@@
 %At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
-Furthermore, Table \ref{tab:agree} reports the agreement measures compute separately for the different domains in the MN data.
-Two domains are particularly noteworthy: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particular low agreement.
-For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
+If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particularly low agreement.
+In the other domains values are around the average for the whole dataset.
+%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
 Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain.
-This indicates that the agreement measures are unstable for different instances and classes.
-The qualitative examples in Figure \ref{fig:ex} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
-The following Section will attempt to shed further light on the potential sources of this variation in object naming that we observe here.
+This indicates that the agreement varies a lot across instances, over and above the class or domain.
+The qualitative examples in Figure \ref{fig:ex-high-low-agreement} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
+These examples suggest that instances that are more prototypical of a category trigger higher agreeement.
+The following Section will examine other potential sources of variation in object naming.
 
@@
 
-Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity.
- We now investigate to what extent the naming variation in the MN data set (see previous Section) can be attributed and explained with specificity. 
- Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional MN names, and check whether the MN name stand in a hierarchical taxonomic relation to 
- the object name's synset in VisualGenome.
+Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity~\cite{+++}.
+This section shows that naming variation in ManyNames cannot be explained by this parameter.
+Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional ManyNames names, and check whether they stand in a taxonomic relation to the object synset given by VisualGenome.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 
@@
 
-Table \ref{tab:rel} shows how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
-Luckily, the coverage of WordNet for our name data is satisfactory, i.e. we were able to analyze 90\% of the name types which account for 97\% of the annotation tokens.
-Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the VG annotators.
-But overall, the most frequent case by far is that no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Thus, strikingly, most of the naming variation in MN is \textit{not} related to different preferences in levels of specificity, but to other sources.
+Table \ref{tab:rel} shows the distribution of the results. 
+how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
+\gbt{what do you mean, `` aggregated class-level response set''?}
+The coverage of WordNet for our name data is satisfactory (90\% of the name types, accounting for 97\% of the tokens).
+Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vgenome annotators.
+However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
+Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.
 
@@
 \end{tabular}
-\caption{Lexical relations of naming variants in MN to annotated VG synset, averaged over synsets}
+\caption{Lexical relations of naming variants in ManyNames to annotated \vgenome synset, averaged over synsets.}
 \label{tab:rel}
@@
 
-Based on the examples in Figure \ref{fig:ex}, we will now provide a qualitative discussion of other types of variation we found in the data.
+We provide a discussion of other types of variation we found in the data, based on qualitative analysis, and illustrating it with the examples in Figure \ref{fig:ex-high-low-agreement}:
 
 \begin{description}
-\item[referential uncertainty:] despite our various attempts to filter objects that are occluded or have unclear bounding boxes \sz{see Section REF}, we still find many examples where annotators were uncertain about the identity of the object indicated by the bounding box and named an adjacent or a supporting object (e.g.
-\textit{bed-book}) or a part of the target object (\textit{batter-helmet})
-\item[crossclassification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-sandwich})
-\item[conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (e.g. \textit{bed-bench},\textit{sandwich-hotdog})
-\item[metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (e.g.
-\textit{sandwich-basket}, \textit{bed-bed sheet})
-\item[issues with WordNet:] due to WordNet's fine-grained hierarchy, it can be difficult to retrieve certain loosely related synonyms or hypernyms (e.g. \textit{robe-dress})
+\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
+Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
+Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
+\item[Cross-classification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
+\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench},\textit{sandwich-hotdog})
+\item[Metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loosely related synonyms or hypernyms (\textit{robe-dress}).
 \end{description}
 
-As it is non-trivial to separate this cases in an automatic or manual manner, we leave a precise quantitative analysis of these phenomena for future work.
-
-%\subsection{Qualitative Analysis}
-
-%\sz{put qualititative discussion here} Table \ref{tab:qual} shows examples for canonical and non-canonical VG names in our data set, where canonical means that the name was the top response in the aggregated response set in ManyNames.
+As it is non-trivial to separate this cases, we leave a precise quantitative analysis of these phenomena for future work.
 
@@
 
- \caption{\label{fig:ex}Examples for different instances of VG synsets with low and high agreement in MN data set, names that have a hierarchical relation to the VG synset in WordNet are underlined}
+ \caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames data set, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined}
+\label{fig:ex-high-low-agreement}
 \end{figure*}
@@
 
-\subsection{Discussion (for now)}
+\subsection{Discussion}
 \label{subsec:discuss}
 
-Summarizing our analysis, we find that the object naming variation attested in our MN corpus offers some new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (psycho-)linguistics.
-Whereas existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets, our data elicited from many speakers can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and can often not simply be retrieved from existing taxonomies like e.g.\ WordNet.
-For theoretical research, our data offers a lot of variation in object naming that cannot be explained by adopting a traditional taxonomy-driven and hierarchical view.
+% gbt: I moved the following sentence to the Conclusion section. To determine: what parts of this discussion stay here, what go to the conclusion.
+% The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
 
-So, \textit{do objects in real-world images have a canonical name?} As it turns out, this general question calls for a somewhat differentiated answer.
-When taking other, similarly subtle and similarly free annotation tasks in NLP as a benchmark (e.g. \sz{????})
-our analysis does indeed suggest that there are systematic properties of instances even in complex visual scenes that often make them have a dominant or strongly preferred name.
-  At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical, see e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
-Given that we find much lower agreement on object class-level than on instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
+The answer to our question, \textit{do objects in real-world images have a canonical name?}, is nuanced.
+Our data suggests that there is indeed a tendency for particular instances marked by bounding boxes to elicit a single consistent name across subjects, but there is also consistent variation in naming.
+Moreover, there is high variability in agreement across instances within the same class or domain.
+The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
+
+Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
+When humans agree only around 70\% of the cases in how to name an object, it is not clear that the data can be taken as a gold standard in multi-label classification setting, as is commonly done in Computer Vision.
+  % At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
+See e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
+\gbt{It is not clear to me what this means: what kind of data is this?
+how does this result relate to our point?
+-- @Carina, expand?}
+Our data can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
+For theoretical research, we show that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.
+
+\gbt{I couldn't follow the discussion in the following pargraph. Do you think it's subsumed by the one above? Can we remove it?} 
+Given that we find much lower agreement on object class-level than on an instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
 However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).

### 2019-05-19 papers/EMNLP2019/modeling.tex
--

@@
 The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
-previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}, and the references therein).
+previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).
 

### 2019-05-19 papers/EMNLP2019/conclusion.tex

\subsection{Conclusion}
\label{sec:conclusion}

The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2019-05-19 papers/EMNLP2019/analysis.tex
adds model predictions to Fig4 (analysis)

@@
 %\end{table}
-
-\begin{figure*}
-\begin{minipage}[b]{0.5\linewidth}
-{\footnotesize
-\setlength{\tabcolsep}{1pt}
-\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}
-%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
-%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
-%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
-%\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
-%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
-%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
-\multicolumn{4}{c}{\textbf{VG: sandwich}}\\
- \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), \underline{food} (5), burger (2),  \underline{hamburger} (2),  \underline{meal} (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2)\\ 
-\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  \underline{building} (11)  &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\ 
-\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2321254_3438076_singleton_obj.png}} bed (36)  &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2324306_3412337_singleton_obj.png}}  bed (16), bench (6), crib (5) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2342811_3485104_singleton_obj.png}}  bed (17), book (6), table (4), toy (3), bible (2), doll (2) & 
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
-\multicolumn{4}{c}{\textbf{VG: batter}}\\
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
-  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
-\multicolumn{4}{c}{\textbf{VG: robe}}\\
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
-  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2)\\
-
-\end{tabular}
-
-}
-\end{minipage}
-
- \caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames data set, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined}
-\label{fig:ex-high-low-agreement}
-\end{figure*}
+\input{analysis_table_wModelpreds}
+%\input{analysis_table}
 

### 2019-05-19 papers/EMNLP2019/analysis_table.tex
adds model predictions to Fig4 (analysis)

\begin{figure*}
\begin{minipage}[b]{0.5\linewidth}
{\footnotesize
\setlength{\tabcolsep}{1pt}
\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}
%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2343219_926143_supercat_unique.png}}  MN: desktop &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2354847_1742687_seed_ambiguous.png}} MN: computer \\
%\textbf{bench} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2350360_1042111_supercat_unique.png}} MN: table  &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2389358_1261752_singleton_obj.png}}  MN: seat &
%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
\multicolumn{4}{c}{\textbf{VG: sandwich}}\\
 \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), \underline{food} (5), burger (2),  \underline{hamburger} (2),  \underline{meal} (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2)\\ 
\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  \underline{building} (11)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\ 
\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2321254_3438076_singleton_obj.png}} bed (36)  &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2324306_3412337_singleton_obj.png}}  bed (16), bench (6), crib (5) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2342811_3485104_singleton_obj.png}}  bed (17), book (6), table (4), toy (3), bible (2), doll (2) & 
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
\multicolumn{4}{c}{\textbf{VG: batter}}\\
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ 
\multicolumn{4}{c}{\textbf{VG: robe}}\\
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2)\\ 
\end{tabular}
}
\end{minipage}
 \caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames data set, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined}
\label{fig:ex-high-low-agreement}
\end{figure*}

### 2019-05-19 papers/EMNLP2019/analysis_table_wModelpreds.tex
adds model predictions to Fig4 (analysis)

--- 2019-05-19 papers/EMNLP2019/analysis_table.tex
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2)\\ 
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)]\\
+				%
+				 \textit{sandwich}, food, bread, sandwiches, plate, burger
+				 & plate, \textit{food}, \textit{basket}, hotdog, wrapper, paper
+				 & fish, chicken, meat, \textit{food}, \textit{sandwich}, bread
+				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table \\ 
+				%
+				%
 				\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\
+				\\ 
+				%
+				\textit{bridge}, arch, sky, structure, walkway
+				& \textit{building}, \textit{bridge}, sky, structure, church
+				& \textit{street}, \textit{road}, highway, intersection, pavement
+				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} \\ 
+				%
+				% 
 				\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
+				%
+				\textit{bed}, beds, sheets, frame, sheet
+				& \textit{bed}, table, bed frame, sofa, couch
+				& \textit{bed}, sheet, sheets, blanket, comforter, cover
+				& \textit{bed}, comforter, \textit{blanket}, cover, sheet \\ 
+				%
+				% 
 				\multicolumn{4}{c}{\textbf{VG: batter}}\\
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
-  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
+				%
+				\textit{man}, player, \textit{person}, shirt, guy
+				& \textit{player}, \textit{batter}, \textit{man}, \textit{baseball player}, uniform
+				& \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
+				& \textit{player}, batter, \textit{person}, man, uniform, boy, \textit{baseball player}, dirt \\ 
+				%
+				% 
 				\multicolumn{4}{c}{\textbf{VG: robe}}\\
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2)\\
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
+				%
+				woman, outfit, dress, girl, suit
+				& woman, outfit, \textit{dress}, girl, suit
+				& \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
+				& teddy bear, \textit{bear}, dog, \textit{toy}, stuffed animal, blanket, toys
+				%, stuffed animals \\ 
+				%
+				% 				
 			\end{tabular}
@@
 	\end{minipage}
- \caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames data set, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined}
+	\caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames. 
+		First row: responses in MN, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined.
+	Second row: top name prediction by bottom up, names which match a MN respose are in italics.}
 	\label{fig:ex-high-low-agreement}

### 2019-05-19 papers/EMNLP2019/data-collection.tex
small mods in intro and data-coll

@@
 
-We take data from \vgenome \cite{krishna2016visualgenome}, which
+We take data from \vgenome \cite[\vg henceforth]{krishna2016visualgenome}, which
 % aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-contains a dense region-based labeling of $108k$~images with object descriptions, attributes, and relationships, as well as question-answer pairs, all linked to WordNet synsets \cite{fellbaum1998wordnet}.
-\vgenome is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
+contains a dense region-based labeling of $108k$~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs,
+all linked to WordNet synsets \cite{fellbaum1998wordnet}.
+\vg is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
 naturalistic images, as it has images of varying complexity, with close-ups as well as complex images with many objects.
-As common in Computer Vision, objects are identified via bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
+As common in Computer Vision, objects are localized as 
+%identified via
+ bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
 \footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}
@@
 as basis.
-We selected images from seven domains: six based on McRae et al.'s feature norms (REF), a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is very frequent category in \vgenome.
+We selected images from seven domains: six based on \newcite{mcrae2005semantic}'s \citeyear{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 
-Within each domain, we aimed at collecting instances at different levels in a taxonomy to cover a wide range of phenomena, but it is not straightforward to do so because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
+Within each domain, we aimed at collecting instances at different levels in a taxonomy to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy %in the first place
+(e.g.\ \textsc{home}).
 % Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
-Instead, we defined a set of synsets (52 in total) that we would use to collect our object instances from \vgenome, balancing variability.
-From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vgenome object instances of different names.
-For example, \vgenome instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vgenome, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
+Instead, we defined a set of synsets ($52$\ in total) that we would use to collect our object instances from \vg, balancing variability.
+From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vg object instances of different names.
+For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
 
@@
 % \paragraph{Sampling of instances}
-Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to 500 instances for seeds with up to 800 objects, and up to 1000 instances for larger seeds.
+Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds.
 \textbf{double-check}
-This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see next subsection).
-Table~\ref{tab:overview_dataset1}shows the 7 domains together with the top 10 \vgenome names.
+This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see Section\ \ref{subsec:elicitation}). 
+Table~\ref{tab:overview_dataset1} shows the $7$\ domains together with the top $10$\ \vg names.
 
@@
 \subsection{Elicitation Procedure}
-
-To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk.
+\label{ssec:elicitation}
+To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
 In initial pilot studies, we found object identification via bounding boxes to be problematic.
-In some cases, the bounding box was not clear; in others, subjects named objects that were more salient than the one signaled by the bounding box (for instance, for a bounding box around a jacket, the man wearing it).
-We took special care of minimizing this issue, in two ways: Specifying the instructions such that subjects pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 names/object) in which we allowed subjects to indicate whether the objet was occluded or the bounding box unclear.
+In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the bounding box (for instance, for a box around a jacket, the man wearing it).
+We took special care of minimizing this issue, in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear.
 The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
-We eliminated around 5.5K images based on pruning, obtaining the final dataset with 25,596 images.
-We then did 3 more collection rounds, obtaining a total of 36 names per image.
+We eliminated around 5.5K images based on pruning, obtaining the final dataset with 25,596\ images.
+We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
 Workers could only participate in one round, to avoid workers annotating an instance more than once. 
-As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vgenome annotation and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language\&vision (see discussion in Sections~\ref{sec:analysis,??}).
+We obtained a total of 36 names per image (i.e.,\ objects).
+As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language \& vision (see discussion in Sections~\ref{sec:analysis,??}).
 \gbt{TO DO: revise that this matches the narrative in the rest of the paper.}

### 2019-05-20 papers/EMNLP2019/analysis.tex

@@
 
-In this section, we investigate to what extent names in VisualGenome and ManyNames can be considered canonical, i.e., to what extent speakers agree in their naming choices.
-Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and see to what extent names overlap for the same object.
-Second, we will use the existing annotation of names in VisualGenome to analyze agreement on the level of classes.
+We investigate to what extent names in \vg (\vg) and ManyNames can be considered canonical, i.e., to what extent speakers agree in their naming choices.
+Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on the concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and examine to what extent names overlap for the same object.
+Second, we will use the existing annotation of names in \vg to analyze agreement on the level of classes.
 \begin{figure}[t]
@@
 
-Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in VisualGenome, (ii) the object class or synset, annotated in VisualGenome and obtained via a semi-automatic linking of the object name to WordNet, (iii) the ManyNames response set, i.e.
+Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg and obtained via a semi-automatic linking of the object name to WordNet\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})}, (iii) the ManyNames response set, i.e.
 a set of name types with annotation frequencies (max.
 36 annotations per object).
-See Figure \ref{fig:ex-high-low-agreement} for examples of object annotations.
-Based on the VisualGenome synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
+See Figure \ref{fig:ex-high-low-agreement} for examples of object annotations \cs{(top rows below the respective images give the responses) [if model preds are kept]}.
+Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
 
@@
 %Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.
-how many objects or classes have at least $n$ names, with different minimum frequency thresholds to account for possible noise in the crowdsourced data.
-Without any frequency thresholding, the proportion of instances and classes that have a single name annotated is very small, below 10\% in both cases.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects (left) or classes (right) have at least $n$\ names, with different frequency thresholds~$n$ to account for possible noise in the crowdsourced data.
+Without any frequency thresholding~\mbox{($n$=1)}, the proportion of instances and classes that have a single name annotated is very small, below 10\%\ in both cases.
 
-The histogram for instances in Figure \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the ManyNames data which, again, is expected in an annotation task where subjects are free to choose any response.
-When filtering names with frequencies below 2, 3 or 4, the response sets for instances get more consistent such that the majority contains maximally 5 names.
-Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%, even when applying a strict frequency filter of 4.
-This indicates that there is non-negligible variation when different speakers name the same object, and the variation seems to be restricted to a manageable set of up to 5 names per object.
+The histogram for instances in Figure\ \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the ManyNames data, as is expected in an annotation task where subjects are free to choose any response.
+When discarding names with frequencies below\ \mbox{2, 3 or 4}, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
+majority of the response sets for instances become more consistent with at most 5\ names per set, 
+%Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%. %, even when applying a strict frequency filter of 4.
+but the sets with a single name still make up only $<$50\%\ of all sets. 
+In sum, this indicates that there is non-negligible variation when different speakers name the same object, and the variation seems to be restricted to a manageable set of up to 5\ names per object.
 
 However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure \ref{fig:ntypes} (right).
-Here, we observe that the rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10 or even 20 different name types, even after applying the frequency thresholds.
-This clearly indicates that different instances annotated with the same name and synset in VisualGenome trigger different naming variants.
-Examples illustrating this can be found in Figure \ref{fig:ex-high-low-agreement}.
+%Here, we observe that the 
+The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds.
+This clearly indicates that different instances annotated with the same
+%name and 
+\cs{(removed "name and") The synsets could have different names -- maybe say "or even same name"?}
+synset in \vg trigger different naming variants. Examples illustrating this can be found in Figure \ref{fig:ex-high-low-agreement}. 
 Implications of this finding will be discussed below in Section \ref{subsec:discuss}.
@@
 \end{figure*}
+\cs{Change yticks to 0-100, with label \%. Make font larger in Fig. with plots?}
 
@@
 \item \textbf{N}: the average number of types in the response set of ManyNames
-\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the VisualGenome name
-\item \textbf{\% VG}: the average relative frequency of the VisualGenome name in the response set
+\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the \vg name
+\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set
 
@@
 As shown in Table \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in the previous section:
-On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\% of the responses on average, and the original VisualGenome name having an average frequency of 62\% in the ManyNames responses.
+On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\% of the responses on average, and the original \vg name having an average frequency of 62\% in the ManyNames responses.
 On the class level, however, the agreement is much lower: The average frequency of the top name drops to 56.4\% and the frequency of the \vgenome name even more, to 23.4\%.
@@
 This section shows that naming variation in ManyNames cannot be explained by this parameter.
-Given that the VisualGenome names are already linked to WordNet, we compute the same linking for the additional ManyNames names, and check whether they stand in a taxonomic relation to the object synset given by VisualGenome.
+Given that the \vg names are already linked to WordNet, we compute the same linking for the additional ManyNames names, and check whether they stand in a taxonomic relation to the object synset given by \vg.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 

### 2019-05-20 papers/EMNLP2019/relwork.tex
(long) related work

@@
-\paragraph{Cognition: Concepts and categorization}
+Object naming is closely related to processes of visual object recognition investigated in Computer Vision or Cognitive Science.
+This Section will discuss how naming relates to questions addressed in these neighbouring areas and how it has been and should be studied as a linguistic phenomenon in Language \& Vision.
 
- Seminal work on concepts by Rosch and colleagues suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
+\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
+An important paradigm for experimental research here is picture naming, where human subjects are asked to say or write down the first name that comes to mind when looking at a given picture, typically a normed, black-and-white line drawing depicting a prototypical instance of a category on a white background \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
+Subjects have been shown to reach very high agreement on this task, e.g.\ \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Our annotation task is inspired by these picture naming studies, but uses real-world images with particular objects highlighted in them.
+Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}.
+Object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}.
+In L\&V,  deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
+For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for e.g.
+people are missing.
+
+\paragraph{Work on Hierarchical Object Categorization} is not only interested in visual object representations but also in principles underlying the organization of these object categories. 
+For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the hierarchical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy.
+%This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
+Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}.
+While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single correct or canonical category (that does have relations to other categories).
+This view has been criticized by more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple taxonomies at the same time \cite{ross1999food,SHAFTO20111}.
+A prominent example for this \textit{cross-classification} are food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
+To the best of our knowledge, this phenomenon has not received any attention in recent corpus-based work on L\&V.
+Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
+
+%Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.} \gbt{ok}
+
+%have  frameworks previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning};
+%Ristin et al., 2015 REF, and the references therein).
+
+% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
+% Wang et al.: ".
+The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
+%[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy.
+\cs{remove or move to related work?
+also sentence to Ordonez}
+
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
+%While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
 %with respect to the chose level of specificity. 
-their choice of the level of specificity. 
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating,graf2016animal}.
+%their choice of the level of specificity.
 
-\paragraph{Vision: Object Recognition}
+\paragraph{Work on Object Naming} that explicitly tries to model which \textit{word} (i.e. not a label or category) a speaker is going to use to name to an object is relatively scarce.
+Object names figure prominently in referring expressions that have been investigated a lot in natural language generation \cite{dale:1995,krahmer:2012}, but this area has, to date, focussed mostly on the selection of attributes rather than on determining the referent's name \cite{krahmer:2012,Kazemzadeh2014}.
+\newcite{Ordonez:2016} frame object naming as an extension of object recognition, taking up the notion of basic-level or entry-level categories from \cite{rosch1976basic}.
+Their model first classifies objects into very fine-grained categories and then decides which level in the taxonomy (i.e.\ WordNet) is appropriate for retrieving the actual name.
+This latter decision, however, is not based on natural referring expression data, but derived from frequencies in a text corpus. 
+ \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions for objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
+ Recent experimental work on reference found that the specificity of an object name is dependent on the taxonomic relatedness of other objects present in the visual context
+\cite{rohde2012communicating,graf2016animal}. Our work can be seen as a first step towards studying naming in real-world, natural reference.
+But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focusses on naming in isolation, rather than reference where naming interacts with other decisions like attribute selection.
 
-State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}).
-These object recognition systems are now widely used in vision \& language research.
-Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.} \gbt{ok}
-
-\paragraph{Vision \& language: Naming and Referring}
-
-\newcite{Ordonez:2016} have studied the problem of deriving appropriate object names, or so-called entry-level
- categories, from the output of an object recognizer.
-Their approach focusses on linking abstract object categories in ImageNet to actual words via translation procedures that e.g.
-involve corpus frequencies.
- \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions paired with objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
-Object naming is also an important task for referring expression generation, though most research in this area has focussed on content and attribute selection \cite{Kazemzadeh2014,gkatzia:2015,zarrieschlang:easy-pre,Maoetal:cocorefexp}.
-\gbt{Should we put this as motivation also in the intro?}
+%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language},
 

### 2019-05-20 papers/EMNLP2019/relwork.tex
small fixes in language in rel. work

@@
 An important paradigm for experimental research here is picture naming, where human subjects are asked to say or write down the first name that comes to mind when looking at a given picture, typically a normed, black-and-white line drawing depicting a prototypical instance of a category on a white background \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
-Subjects have been shown to reach very high agreement on this task, e.g.\ \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
-Our annotation task is inspired by these picture naming studies, but uses real-world images with particular objects highlighted in them.
-Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}.
-Object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}.
+Subjects have been shown to reach very high agreement on this task, \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Our annotation task is inspired by picture naming, but uses real-world images with particular objects highlighted in them.
+Recognition of instances (as opposed to prototypes or categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}.
+Current object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}.
 In L\&V,  deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
@@
 
-\paragraph{Work on Hierarchical Object Categorization} is not only interested in visual object representations but also in principles underlying the organization of these object categories. 
-For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the hierarchical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy.
+\paragraph{Work on Hierarchical Object Categorization} goes beyond visual representations of isolated categories but looks at the principles underlying the organization of object categories. 
+For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the taxonomical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy.
 %This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}.
-While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single correct or canonical category (that does have relations to other categories).
-This view has been criticized by more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple taxonomies at the same time \cite{ross1999food,SHAFTO20111}.
+Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich taxonomical structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}.
+While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single, canonical category (that does have relations to other categories).
+This view has been criticized in more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
 A prominent example for this \textit{cross-classification} are food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).

### 2019-05-20 papers/EMNLP2019/analysis.tex
explodes discussion in analysis

@@
 
-\subsection{Names, instances, classes}
+\subsection{Names, Instances, Classes}
 \label{subsec:counts}
@@
 
-However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure \ref{fig:ntypes} (right).
+However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
 %Here, we observe that the 
@@
 
-\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vgenome synset), for filtered response sets (frequency threshold of 2)}
+\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
 \label{tab:agree}
@@
 %As type counts give a rather rough indication for variation in object naming, 
-We compute the following measures to check agreement on the object names:
-
+We compute the following measures to assess agreement on the object names:
 \begin{itemize}
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
-\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: $H = \sum_{i=1}^k p_i\ log_2(1/p_i)$
+\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
+where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the response set. \cs{@Sina: right?}
 
@@
 \item \textbf{N}: the average number of types in the response set of ManyNames
-\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the \vg name
+\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the \vg name \cs{the numbers are percentages, aren't they?
+So we should either say "relative frequency", leaving open that we express it as percentage, or directly percentages.
+Proportion should be a value between 0 and 1, shouldn't it?!}
 \item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
+\end{itemize}
+\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
+Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
+To account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.
 
-\end{itemize}
-
-Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
-To account for potential noise, we filter out names with a frequency of 1 from the response sets.
-As shown in Table \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in the previous section:
-On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\% of the responses on average, and the original \vg name having an average frequency of 62\% in the ManyNames responses.
-On the class level, however, the agreement is much lower: The average frequency of the top name drops to 56.4\% and the frequency of the \vgenome name even more, to 23.4\%.
-The $H$ measures indicates a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \cite{snodgrass} report an average $H$ of 0.55).
+As shown in Table\ \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in Section\ \ref{subsec:counts}:
+On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\%\ of the responses on average, and the original \vg name having an average frequency of\ 63\% in the ManyNames responses.
+On the class level, however, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
+The $H$ measures indicate a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55).
 On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
@@
 %At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
-If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement (with an $H$ value of 0.2), and the \textsc{people} domain with a particularly low agreement.
-In the other domains values are around the average for the whole dataset.
+If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
+In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
 %For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
-Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain.
-This indicates that the agreement varies a lot across instances, over and above the class or domain.
-The qualitative examples in Figure \ref{fig:ex-high-low-agreement} further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
-These examples suggest that instances that are more prototypical of a category trigger higher agreeement.
-The following Section will examine other potential sources of variation in object naming.
 
-\subsection{Specificity and other sources of variation}
+Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}.
+This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
+The qualitative examples in Figure \ref{fig:ex-high-low-agreement} %further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
+illustrate this, showing visual instances with very high or low agreement. 
+These examples suggest that instances which are more prototypical of a category trigger higher agreement.
+The following section will examine other potential sources of variation in object naming.
 
+\subsection{Specificity and Other Sources of Variation}
 Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity~\cite{+++}.
-This section shows that naming variation in ManyNames cannot be explained by this parameter.
-Given that the \vg names are already linked to WordNet, we compute the same linking for the additional ManyNames names, and check whether they stand in a taxonomic relation to the object synset given by \vg.
+%This section shows that naming variation in ManyNames cannot be explained by this parameter.
+This parameter does not explain the naming variation in ManyNames, as we will show in the following. 
+Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.% given by \vg.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 
@@
 %\end{itemize}
-
+\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
 Table \ref{tab:rel} shows the distribution of the results. 
 how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
+\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
+and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
 \gbt{what do you mean, `` aggregated class-level response set''?}
-The coverage of WordNet for our name data is satisfactory (90\% of the name types, accounting for 97\% of the tokens).
-Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vgenome annotators.
+\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
+The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
+Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
 However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.
+Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
+ but to other sources.
 
@@
 \end{tabular}
-\caption{Lexical relations of naming variants in ManyNames to annotated \vgenome synset, averaged over synsets.}
+\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
 \label{tab:rel}
@@
 
-We provide a discussion of other types of variation we found in the data, based on qualitative analysis, and illustrating it with the examples in Figure \ref{fig:ex-high-low-agreement}:
+We discuss other types of variation we found in the data, based on qualitative analysis, and illustrate them with the examples in Figure\ \ref{fig:ex-high-low-agreement}:
 
 \begin{description}
-\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
 They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
@@
 \item[Cross-classification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench},\textit{sandwich-hotdog})
-\item[Metonymy:] similar to crossclassification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
+\item[Metonymy:] similar to cross-classification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
 \item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loosely related synonyms or hypernyms (\textit{robe-dress}).
@@
 
-The answer to our question, \textit{do objects in real-world images have a canonical name?}, is nuanced.
-Our data suggests that there is indeed a tendency for particular instances marked by bounding boxes to elicit a single consistent name across subjects, but there is also consistent variation in naming.
-Moreover, there is high variability in agreement across instances within the same class or domain.
+The answer to our question, \textit{do objects in real-world images have a canonical name?} is nuanced. 
+Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a single consistent name across subjects, which is in line with existing theoretical research on object naming and categorization \cs{ok??}.
+However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain. 
 The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
+\cs{With prototypical pictures (see Figure\ \ref{fig:picture_naming}), as done in traditional studies, this observation would not be possible.
+(??)}
+%For theoretical research, w
+We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.
 
+Our ManyNames dataset can be used for both, theoretical and practical research. 
+Specifically, it provides a means 
+(i) to study how different people would name the same object (image region) \cs{"visual awareness" would fit in here}, and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and
+%assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
+(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
+
+As far as research in L\&V and Computer Vision is concerned, our findings are reason to question the appropriateness of the standard, single-label approach in visual object naming and categorization methods.
+Even the assumption that there at least exists a canonical name
+%,\ i.e.,\ a  name on which the majority of people would agree 
+ for individual visual objects (localized by bounding boxes) is disputable (cf.\ the high standard deviation in terms of the relative frequency of an instance's top response (column \%top, Table~\ref{tab:agree}), and the average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG})\cs{a bit redundant now}).
+%
+The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
+It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs.
+dog, animal, hat?).
+%
+The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
+as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierachically related. 
+\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
+%
+% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
+% Wang et al.: ".
+The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
+% @related work
+%[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy.
+\cs{remove or move to related work?
+also sentence to Ordonez}]
+%\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF).
+\cs{maybe remove, since it is not that relevant?}}
+%
+%
+% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
+%
+However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
+For the same reason, even fine-grained recognition models (as those trained on ILSVRC REF) cannot be expected to be able to simply infer the recognition of more general classes.
+%since we found that many name alternatives are not hierarchically related to the VG name, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically a "truly" false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
+\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
+%
+
+\cs{?: Say something about type disagreements on class-level, after having written the results discussion.}
+%
+
+\cs{Ah, we still should have a comparison model with above argumentation :/.}
+%
+As a use-case study, in Section\ \ref{sec:modeling}, we will treat ManyNames as evaluation data and assess whether an existing SOTA model can account for the naming variants of individual objects.
+
+\iffalse
+*********
 Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
@@
 -- @Carina, expand?}
-Our data can be used to (i) assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to (ii) obtain available lexical alternatives of a preferred name, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
-For theoretical research, we show that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.
+\fi
 
@@
 However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).
-Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising crossclassification, metonymy and potentially other sources of variation.
+Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising cross-classification, metonymy and potentially other sources of variation.
 

### 2019-05-20 papers/EMNLP2019/data-collection.tex
explodes discussion in analysis

@@
 \subsection{Sampling of Instances}
-
+\label{ssec:sampling}
  % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
@@
 \begin{table*}
+	\small
+	\centering
 \begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
@@
 \end{tabular}
-	\caption{Overview of our dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
+	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
 \end{table*}
 
+\cs{@Carina ToDo: add some examples of synsets + names; maybe in suppl}
 % \begin{itemize}
@@
 Overall $XX$ turkers took part in the data elicitation, each naming a median of XXX instances. \gbt{@Carina pls fill in.}
-
+\cs{Maybe say something about the rejections, if space permits it.}
 %%% Local Variables:

### 2019-05-20 papers/EMNLP2019/analysis.tex
modeling, some stuff left for tomorrow

@@
 \subsection{Specificity and Other Sources of Variation}
+\label{ssec:variation}
 Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity~\cite{+++}.

### 2019-05-20 papers/EMNLP2019/modeling.tex
modeling, some stuff left for tomorrow

--- 2019-05-18 papers/EMNLP2019/modeling.tex
@@
-% mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)
-Our findings in Sections~\ref{sec:analysis} and~\ref{sec:taxo} are reason to question the appropriateness of the standard, single-label approach in visual object naming and categorization methods. 
-Even the assumption that there at least exists a canonical name, i.e., a  name on which the majority of people would agree, for individual visual objects (/or image regions(?)) (instances) is disputable.
-This was shown by the high standard deviation in terms of the relative frequency of an instance's top response (column \%top in Table~\ref{tab:agree}), as well as an average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG}).
-%
-The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
-It would be desirable to explicitly assess model towards their ability to account for naming variants of an instance/how different people would name the same object/image regions (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs.
-dog, animal, hat?).
-%
-
-The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
-previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}, and the references therein).
-
-% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
-% Wang et al.: ".
-The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
-[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy.
-\cs{remove or move to related work?
-also sentence to Ordonez}]
-\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF).
-\cs{maybe remove, since it is not that relevant?}}
-%
-% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
-%
-However, as discussed in Section~\ref{sec:taxo}, we found that many name alternatives are not hierarchically related to the VG name. 
-Hence, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically whether a predicted name is a true error (e.g.,\ XX) or actually a valid alternative to the given "ground truth" (e.g.,\ XX).
-\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
-%
-\cs{TODO: Say something about type disagreements on class-level, after having written the results discussion.}
-%
-\cs{Ah, we still should have a comparison model with above argumentation :/.}
-%
-Here, we will use ManyNames (MN) as evaluation data, and assess whether a SOTA model can account for the naming variants of individual objects in MN. 
-In contrast to above work where the models were trained on multiple labels, we use a classification model that was trained on single names--VG's object names (and attributes).
-%, i.e., it did not see multiple names for individual objects during training.
-By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
-And due to the nature of our collected data, the relations may not stand in a hierarchical relation.
-
-%We hypothesize that this is the case, see finding regarding the influence of visual cues. 
-%Get an intuition in how far models are able to identify an object by one of it's possible names (gt=dog, is system still able to identify the object if the name is puppy?).
-\cs{And with this argumentation, we ideally we compare to a model fine-tuned on our data...}
-
-\subsection{Experimental Setup}
-\textbf{THIS IS VERY CRYPTIC}
-\paragraph{Model}
-We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
-It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
-\iffalse
-"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
-Genome [21] data. To aid the learning of good feature
-representations, we add an additional training output for
-predicting attribute classes (in addition to object classes).
-To predict attributes for region i, we concatenate the mean
-pooled convolutional feature vi with a learned embedding
-of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
-attribute class plus a ‘no attributes’ class.
-The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
-bounding box regression outputs for both the RPN and the
-final object class proposals respectively. We retain these
-components and add an additional multi-class loss component to train the attribute predictor"
-\fi
-
-\paragraph{Data}
-\begin{itemize}
-	\item We use the softmax distribution for the VG object names, and ignore the distribution over attributes. 
-	\item The authors manually cleaned the set of object names to remove those with poor detection performance.
-	\item Set of classes: 1,600 object names
-	Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes.
-(For those cases, we therefore would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.
-)
-	\item Image set and vocabulary: $XXX$~names are not in MN, i.e., our vocabulary (MN--VG) contains $XXX$~names. 
-	We filtered out those images whose VG name was not found in MN--VG, which resulted in $24,585$~instances (note that of those $22,304$~images were also part of the training data of bottom-up)
-\end{itemize}
-
-\paragraph{Measures}
-\textsl{top}: the model's top prediction
-\begin{itemize}
-	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
-	\item \textbf{=MN-1} The average model accuracy of \textsl{top} on the top response in ManyNames
-	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
-	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
-\end{itemize}
-
-\paragraph{Results} 
-We compare the model against a random baseline for the KL divergence, and against a most-frequent name baseline. 
-We further compare the model on the set of instances where the VG names does not match the top response in MN (block \mbox{VG$\neq$MN-1} in Table~\ref{tab:model}), and to those which were not part of the set of images used for training bottom-up ($\neg$Training).
-Note that the latter two sets are disjoint. 
-%
 \begin{table*}
@@
 	\end{tabular}
-\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN-1) and 6.9 ($\neg$Training)	\label{tab:model}}
+	\caption{Baseline: The most frequent name.
+Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN-1) and 6.9 ($\neg$Training).
+The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
 \end{table*}
+%
+% mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)
+\cs{Ah, we still should have a comparison model with above argumentation :/.}
+%
+We use ManyNames\ (MN) as evaluation data, and assess whether a SOTA model can account for its naming variants provided for individual objects. 
+In contrast to existing work which uses multi-label data also during training (cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a classification model that was trained on single names---VG's object names (and attributes).
+%, i.e., it did not see multiple names for individual objects during training.
+By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
+And due to the nature of our collected data, the relations may not stand in a hierarchical relation.
 
+%We hypothesize that this is the case, see finding regarding the influence of visual cues. 
+%Get an intuition in how far models are able to identify an object by one of it's possible names (gt=dog, is system still able to identify the object if the name is puppy?).
+\cs{And with this argumentation, we'd ideally we compare to a model fine-tuned on our data ... so much future work}
+
+\subsection{Experimental Setup}
+\textbf{STILL TO BE DONE: Model, Data, formulation in Error Analysis}
+\paragraph{Classification model}
+We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
+It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
+\iffalse
+"To pretrain the bottom-up attention model, we first initialize Faster R-CNN with ResNet-101 pretrained for classification on ImageNet [35]. We then train on Visual
+Genome [21] data. To aid the learning of good feature
+representations, we add an additional training output for
+predicting attribute classes (in addition to object classes).
+To predict attributes for region i, we concatenate the mean
+pooled convolutional feature vi with a learned embedding
+of the ground-truth object class, and feed this into an additional output layer defining a softmax distribution over each
+attribute class plus a ‘no attributes’ class.
+The original Faster R-CNN multi-task loss function contains four components, defined over the classification and
+bounding box regression outputs for both the RPN and the
+final object class proposals respectively. We retain these
+components and add an additional multi-class loss component to train the attribute predictor"
+\fi
+
+\paragraph{Data}
+\begin{itemize}
+	\item We use the softmax distribution for the VG object names, and ignore the distribution over attributes. 
+	\item The authors manually cleaned the set of object names to remove those with poor detection performance.
+	\item Set of classes: 1,600 object names
+	Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes.
+(For those cases, we therefore would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.
+)
+	\item Image set and vocabulary: $346$~name types are not in MN, i.e., our vocabulary (MN--VG) contains $1,254$~names. 
+	We filtered out those images whose VG name was not found in MN--VG, which resulted in $24,585$~instances (note that of those $22,304$~images were also part of the training data of bottom-up)
+\end{itemize}
+
+\paragraph{Evaluation measures}
+Model effectiveness is assessed in both, the commonly used single-ground-truth setting and in a multi-label setting. 
+In the former, for each instance, we compare the model's top prediction to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
+In the multi-label setting, we report the average accuracy of the top prediction to match any of the responses in MN. 
+To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat the model's softmax output~$S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
+We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
+
+\iffalse
+\textsl{top}: the model's top prediction
+\begin{itemize}
+	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
+	\item \textbf{=MN-1} The average model accuracy of \textsl{top} on the top response in ManyNames
+	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
+	\item \textbf{KL} The average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ of the model's softmax output~$S$ and the  probability distribution~$M$ over ManyNames, estimated by normalizing the name counts per instance
+\end{itemize}
+\fi
+
+\paragraph{Results} 
+We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}. 
+Apart from the evaluation on the full set of instances (\textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN-1}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
+Note that the latter two sets are disjoint. 
+%
+
+The model performs worse on VG than on the top MN response (MN-1), even though the model saw the majority of the instances during training. 
+It achieves a higher accuracy of up to\ 55\% points on instances for which MN-1 and the VG name differ (\textsc{buildings}, VG$\neq$MN-1). 
+The reasons may be that MN-1 is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN-1 is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).
+Another reason could be that the model reproduces naming choices ("errors") caused by cases of visual uncertainty (cf.\ Section\ \ref{ssec:variation}; e.g.,\ (\textsl{bridge,street})).
+
+In the multi-label setting\ $\in$MN, the difference in accuracy between the objects in All and in the subset VG!=MN-1 is much lower compared to the MN-1 setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains).
+We thus believe that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, since a model's effectiveness is not measured by a single naming choice. 
+The data furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
+As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
+%For these more difficult instances (VG!=MN-1),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
+
+\cs{diffs btw. All, VGnotMN-1 and $\neg$Training  $\leftrightarrow$ overfitting?}
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
+\fi 
+\paragraph{Error Analysis}
+\begin{itemize}
+	\item Model does not make clear mistakes workers did, e.g. \textsl{boy-helmet} in Table\ \ref{fig:ex-high-low-agreement}; or spatial relationships (book-bed) ("referential uncertainty")
+	\item mirrors human "referential uncertainty" mistakes for clothing-person errors (man,shirt); and difficult.to.identify objects (bed,sheet)
+	\item visual perceptual errors: banana (human and model); but more than humans (...)
+	\item but makes clear, unreasonable mistakes (dirt, ...; bed,table; sky)
+	\item cross-classification: great (boy,batter; sandwich,food)
+	\item metonymy: (food,basket/plate)
+\end{itemize}

### 2019-05-21 papers/EMNLP2019/relwork.tex
intro + relwork fit into 2 pages

--- 2019-05-20 papers/EMNLP2019/relwork.tex
@@
 Object naming is closely related to processes of visual object recognition investigated in Computer Vision or Cognitive Science.
-This Section will discuss how naming relates to questions addressed in these neighbouring areas and how it has been and should be studied as a linguistic phenomenon in Language \& Vision.
+This Section discusses questions relates to these areas and naming as a linguistic phenomenon in Language \& Vision.
 
 \paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
-An important paradigm for experimental research here is picture naming, where human subjects are asked to say or write down the first name that comes to mind when looking at a given picture, typically a normed, black-and-white line drawing depicting a prototypical instance of a category on a white background \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
-Subjects have been shown to reach very high agreement on this task, e.g.\ \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
-Our annotation task is inspired by these picture naming studies, but uses real-world images with particular objects highlighted in them.
-Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}.
-Object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}.
+An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
+Subjects reach very high agreement in this task, \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
+Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to predict thousands of different categories, e.g.\  \newcite{googlenet}.
+Current object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}.
 In L\&V,  deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
@@
 
-\paragraph{Work on Hierarchical Object Categorization} is not only interested in visual object representations but also in principles underlying the organization of these object categories. 
-For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the hierarchical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy.
+\paragraph{Work on Hierarchical Object Categorization} 
+%goes beyond isolated object categories.
+% but looks at the principles underlying the organization of object categories.
+
+has emphasized the taxonomic organization of categories, e.g.\ seminal work on prototypes by Rosch \cite{rosch1976basic},  and found that humans tend to conceptualize objects at a basic or medium level of abstraction.
+% in this taxonomy. 
 %This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}.
-While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single correct or canonical category (that does have relations to other categories).
-This view has been criticized by more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple taxonomies at the same time \cite{ross1999food,SHAFTO20111}.
-A prominent example for this \textit{cross-classification} are food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
-To the best of our knowledge, this phenomenon has not received any attention in recent corpus-based work on L\&V.
+Granularity-aware approaches to object recognition have aimed at exploiting taxonomical structure underlying object labels \cite{deng2014large,wang2014poodle,peterson2018learning},  
+%While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, 
+but still aim to predict a single canonical category.% (that does have relations to other categories). 
+This view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
+To the best of our knowledge, this phenomenon has not received any attention in work on L\&V.
 Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
@@
 
-\paragraph{Work on Object Naming} that explicitly tries to model which \textit{word} (i.e. not a label or category) a speaker is going to use to name to an object is relatively scarce.
-Object names figure prominently in referring expressions that have been investigated a lot in natural language generation \cite{dale:1995,krahmer:2012}, but this area has, to date, focussed mostly on the selection of attributes rather than on determining the referent's name \cite{krahmer:2012,Kazemzadeh2014}.
-\newcite{Ordonez:2016} frame object naming as an extension of object recognition, taking up the notion of basic-level or entry-level categories from \cite{rosch1976basic}.
-Their model first classifies objects into very fine-grained categories and then decides which level in the taxonomy (i.e.\ WordNet) is appropriate for retrieving the actual name.
-This latter decision, however, is not based on natural referring expression data, but derived from frequencies in a text corpus. 
- \newcite{zarriess-schlangen:2017} learn a model of object naming on a corpus of referring expressions for objects in real-world images, but focus on combining visual and distributional information and on zero-shot learning.
- Recent experimental work on reference found that the specificity of an object name is dependent on the taxonomic relatedness of other objects present in the visual context
-\cite{rohde2012communicating,graf2016animal}. Our work can be seen as a first step towards studying naming in real-world, natural reference.
-But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focusses on naming in isolation, rather than reference where naming interacts with other decisions like attribute selection.
+\paragraph{Work on Object Naming} that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
+Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focussed mostly on the selection of attributes% rather than on determining the referent's name
+\cite{krahmer:2012}. 
+\newcite{Ordonez:2016} extend object recognition to naming as an extension, taking up the notion of entry-level categories \cite{rosch1976basic}.
+Their model classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name,
+based on frequencies in a text corpus. 
+ \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
+ Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
+\cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
+But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focusses on naming in isolation, rather than reference where naming interacts with attribute selection.
 

### 2019-05-21 papers/EMNLP2019/data-collection.tex
move data set table to suppl material, hope it's okay

@@
 
-\begin{table*}
-	\small
-	\centering
-\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
-	\toprule
-	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
-	\midrule
-	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
-	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
-	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
-	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
-	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
-	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
-	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
-	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
-	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
-	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
-	\bottomrule
-\end{tabular}
-	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
-\end{table*}
-
 \cs{@Carina ToDo: add some examples of synsets + names; maybe in suppl}

### 2019-05-21 papers/EMNLP2019/analysis.tex
moving the snodgrass cake to intro, need to change the caption still

@@
 
-We investigate to what extent names in \vg (\vg) and ManyNames can be considered canonical, i.e., to what extent speakers agree in their naming choices.
-Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on the concept or category-level, we carry out an analysis on two different levels: First, we will look at instances and examine to what extent names overlap for the same object.
-Second, we will use the existing annotation of names in \vg to analyze agreement on the level of classes.
-\begin{figure}[t]
-	\centering
-	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
-	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies \cite{snodgrass} \label{fig:picture_naming}}
-\end{figure}
+We investigate to what extent names in VisualGenome (\vg) and ManyNames can be considered canonical.%, i.e., to what extent speakers agree in their naming choices.
+Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
 
@@
 
-Our analysis is based on the following annotations associated with each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg and obtained via a semi-automatic linking of the object name to WordNet\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})}, (iii) the ManyNames response set, i.e.
+We analyse the following annotations associated with each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg and obtained via a semi-automatic linking of the object name to WordNet\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})}, (iii) the ManyNames response set, i.e.
 a set of name types with annotation frequencies (max.
 36 annotations per object).
-See Figure \ref{fig:ex-high-low-agreement} for examples of object annotations \cs{(top rows below the respective images give the responses) [if model preds are kept]}.
+See Figure \ref{fig:ex-high-low-agreement} for examples of objects and their response sets (top rows below the images).
+ %[if model preds are kept]}. 
  Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.

### 2019-05-21 papers/EMNLP2019/modeling.tex
modeling: finishes results+discussion; TODO: model+data formulation

@@
 %
-We use ManyNames\ (MN) as evaluation data, and assess whether a SOTA model can account for its naming variants provided for individual objects. 
-In contrast to existing work which uses multi-label data also during training (cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a classification model that was trained on single names---VG's object names (and attributes).
+We use ManyNames\ (MN) as evaluation data, and assess whether an object recognition model can account for MN's naming variants provided for individual objects. 
+In contrast to existing works on multi-label classification, which also train their models towards multi-label predictions 
+% multi-label data also during training 
+(cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a model that was trained on single names---VG's object names (and attributes, though).
 %, i.e., it did not see multiple names for individual objects during training.
-By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
+Through this case study we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
+We argue that this is a more natural setting, since people may not hear different names when referring to the same object, but rather across different objects of the same class \cs{any REF to paper where name choice for specific object stays consistent once done?}.
+%By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
 And due to the nature of our collected data, the relations may not stand in a hierarchical relation.
@@
 %Get an intuition in how far models are able to identify an object by one of it's possible names (gt=dog, is system still able to identify the object if the name is puppy?).
-\cs{And with this argumentation, we'd ideally we compare to a model fine-tuned on our data ... so much future work}
+\cs{And with this argumentation, we'd ideally compare to a model fine-tuned on our data ... and to a model trained on all our names with a response count$>$n ... so much future work}
 
 \subsection{Experimental Setup}
-\textbf{STILL TO BE DONE: Model, Data, formulation in Error Analysis}
+\textbf{STILL TO BE DONE: Model, Data}
 \paragraph{Classification model}
@@
 
-\paragraph{Results} 
+\paragraph{Results \& Discussion} 
 We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}. 
@@
 
-In the multi-label setting\ $\in$MN, the difference in accuracy between the objects in All and in the subset VG!=MN-1 is much lower compared to the MN-1 setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains).
-We thus believe that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, since a model's effectiveness is not measured by a single naming choice. 
-The data furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
+In the multi-label setting, $\in$MN, the difference in accuracy between the objects in All and in the subset VG!=MN-1 is much lower compared to the MN-1 setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains).
+Comparison to the results on unseen images demonstrates Bottom-up's generalization ability. 
+While the difference varies highly across the domains (All vs. \mbox{$\neg$\textit{Training}}), it is negligible on average (row \textit{all}), and the same on the \mbox{VG!=MN-1} images. 
+%Unsurprisingly, the effectiveness of Bottom-up drops on the images which it has not seen during training, and the difference in accuracy highly varies across the domains (All vs.
+\mbox{$\neg$\textit{Training}}).
+Taken together, we thus believe that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, since a model's effectiveness is not measured by a single naming choice.
+
+The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
 As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
+It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which tend to contain occluded or unclear bounding boxes \cs{can we say that?}.
 %For these more difficult instances (VG!=MN-1),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
 
-\cs{diffs btw. All, VGnotMN-1 and $\neg$Training  $\leftrightarrow$ overfitting?}
+Comparing the model output to MN on individual images gives an intuition for how much Bottom-up accounts for naming choices due to different sources of variation: 
+In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{(boy,helmet)},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror  cases of human "referential uncertainty"
+%(\textsc{clothing}-\textsc{person}: 
+(\textsl{(man,shirt)}, \textsl{(bed,sheet)}, but see \textsl{(book,bed})), as well as cross-classification (\textsl{(boy,batter)}, \textsl{(sandwich,food)}), and metonymy \textsl{(food,basket/plate)}.
+It reflects perceptual mistakes caused by unclear images (\textit{sandwich,banana}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{(bridge,sky)}, \textsl{(pants/player,dirt)}.
+
 \iffalse
@@
 \end{itemize}
-\fi 
+
 \paragraph{Error Analysis}
@@
 \end{itemize}
+\fi

### 2019-05-21 papers/EMNLP2019/suppl_material.tex

@@
 
+\begin{table*}
+	\small
+	\centering
+\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
+	\toprule
+	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
+	\midrule
+	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
+	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
+	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
+	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
+	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
+	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
+	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
+	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
+	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
+	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
+	\bottomrule
+\end{tabular}
+	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
+\end{table*}
+
 \end{document}

### 2019-05-21 papers/EMNLP2019/analysis.tex
analysis cut down to less than 3 pages

@@
 
-We investigate to what extent names in VisualGenome (\vg) and ManyNames can be considered canonical.%, i.e., to what extent speakers agree in their naming choices.
-Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
-
-\subsection{Names, Instances, Classes}
-\label{subsec:counts}
-
-We analyse the following annotations associated with each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg and obtained via a semi-automatic linking of the object name to WordNet\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})}, (iii) the ManyNames response set, i.e.
-a set of name types with annotation frequencies (max.
-36 annotations per object).
-See Figure \ref{fig:ex-high-low-agreement} for examples of objects and their response sets (top rows below the images).
- %[if model preds are kept]}. 
- Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
-
-% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
-%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects (left) or classes (right) have at least $n$\ names, with different frequency thresholds~$n$ to account for possible noise in the crowdsourced data.
-Without any frequency thresholding~\mbox{($n$=1)}, the proportion of instances and classes that have a single name annotated is very small, below 10\%\ in both cases.
-
-The histogram for instances in Figure\ \ref{fig:ntypes} suggests that there is a certain amount of low-frequency responses in the ManyNames data, as is expected in an annotation task where subjects are free to choose any response.
-When discarding names with frequencies below\ \mbox{2, 3 or 4}, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
-majority of the response sets for instances become more consistent with at most 5\ names per set, 
-%Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%. %, even when applying a strict frequency filter of 4.
-but the sets with a single name still make up only $<$50\%\ of all sets. 
-In sum, this indicates that there is non-negligible variation when different speakers name the same object, and the variation seems to be restricted to a manageable set of up to 5\ names per object.
-
-However, the number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
-%Here, we observe that the 
-The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds.
-This clearly indicates that different instances annotated with the same
-%name and 
-\cs{(removed "name and") The synsets could have different names -- maybe say "or even same name"?}
-synset in \vg trigger different naming variants. Examples illustrating this can be found in Figure \ref{fig:ex-high-low-agreement}. 
-Implications of this finding will be discussed below in Section \ref{subsec:discuss}.
+We investigate to what extent names in VisualGenome (\vg) and ManyNames can be considered canonical in terms of various agreement measures,
+%based on annotations in \vg and ManyNames, 
+and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
+%Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
 
@@
 \end{figure*}
-\cs{Change yticks to 0-100, with label \%. Make font larger in Fig. with plots?}
+
+\subsection{Names, Instances, Classes}
+\label{subsec:counts}
+
+We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
+%and obtained via a semi-automatic linking of the object name to WordNet
+ (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object),  see Figure \ref{fig:ex-high-low-agreement} for examples.
+ % of objects and their response sets (top rows below the images).
+ %[if model preds are kept]}. 
+ Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
+
+% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
+%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects (left) or classes (right) have at least $n$\ names, with different frequency thresholds~$t$ to account for possible noise in the crowdsourced data.
+Without any frequency thresholding~\mbox{($t$=1)}, the proportion of instances and classes that have a single name annotated is very small, below 10\%\ in both cases.
+
+The histogram for instances in Figure\ \ref{fig:ntypes} suggests that low-frequency responses are common in ManyNames, as is expected in a free annotation task.
+% where subjects are free to choose any response. 
+When discarding names these, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
+majority of the response sets become more consistent with at most 5\ names per set, 
+%Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%. %, even when applying a strict frequency filter of 4.
+but the sets with a single name still make up only $<$50\%\ of all sets. 
+This indicates that variation in naming instances is restricted to a manageable set of up to 5\ names per object, but is still non-neglibile.
+
+The number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
+%Here, we observe that the 
+The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds.
+This clearly indicates that different instances annotated with the same
+%name and 
+%\cs{(removed "name and") 
+%The synsets could have different names -- maybe say "or even same name"?}
+synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
+Implications of this will be discussed below in Section \ref{subsec:discuss}.
+
+%\cs{Change yticks to 0-100, with label \%. Make font larger in Fig. with plots?}
 
@@
 %As type counts give a rather rough indication for variation in object naming, 
-We compute the following measures to assess agreement on the object names:
+Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
+{\small
 \begin{itemize}
@@
 \item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
-where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the response set. \cs{@Sina: right?}
-
-% \begin{equation}
-% H = \sum_{i=1}^k p_i\ log_2(1/p_i)
-% \end{equation}
-
+where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
 \item \textbf{N}: the average number of types in the response set of ManyNames
-\item \textbf{top=VG}: the proportion of items where the top response in ManyNames corresponds to the \vg name \cs{the numbers are percentages, aren't they?
-So we should either say "relative frequency", leaving open that we express it as percentage, or directly percentages.
-Proportion should be a value between 0 and 1, shouldn't it?!}
+\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
 \item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
 \end{itemize}
-\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
-Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
-To account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.
+}
+%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
+%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
+%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.
 
 As shown in Table\ \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in Section\ \ref{subsec:counts}:
-On the instance level, our annotators achieve a fair amount of overlap in their object naming choices, with the most frequent name accounting for 75\%\ of the responses on average, and the original \vg name having an average frequency of\ 63\% in the ManyNames responses.
+On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
+the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
 On the class level, however, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
@@
 
-%Generally, this seems to suggest that indeed many objects in our data set have a canonical name. 
-%\sz{For NLP people, this looks like a good agreement (given that people were free to type what they wanted).
-For vision people who might think of it as an object labeling task, this would be pretty low/bad agreement.}
-%At the same time, the average number of name types per object (5.7, or 2.9 when excluding low-frequency types in each response set) suggests that there is a stable amount of naming variants that is elicited for instances.
 If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
-In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
+%In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
 %For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
-
-Another important aspect however is the large standard deviation values for both \%top and $H$, that we find both when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}.
+Across domains, however, we find a large standard deviation for both \%top and $H$.
+% when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}.
 This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
@@
 
-\subsection{Specificity and Other Sources of Variation}
+\subsection{Variation: Specificity and Other Sources}
 \label{ssec:variation}
-Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing objects names of different levels of specificity~\cite{+++}.
+Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
 %This section shows that naming variation in ManyNames cannot be explained by this parameter.
-This parameter does not explain the naming variation in ManyNames, as we will show in the following. 
-Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.% given by \vg.
+This parameter does not explain the variation in ManyNames, as we will show in the following. 
+Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
+For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
+% given by \vg.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 
@@
 %\end{itemize}
-\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
-Table \ref{tab:rel} shows the distribution of the results. 
-how frequently names with a certain relation to the synset occur in the aggregated class-level response set, in terms of their  type and token frequency. 
-\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
-and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
-\gbt{what do you mean, `` aggregated class-level response set''?}
-\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
+%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
+Table \ref{tab:rel} shows the distribution
+how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
+%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
+%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
+%\gbt{what do you mean, `` aggregated class-level response set''?}
+%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
 The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
@@
 \begin{description}
+\setlength{\itemsep}{0pt}
+\setlength{\parskip}{0pt}
 \item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
 They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
+%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
 Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
@@
 The answer to our question, \textit{do objects in real-world images have a canonical name?} is nuanced. 
-Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a single consistent name across subjects, which is in line with existing theoretical research on object naming and categorization \cs{ok??}.
+Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization.
 However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain. 
 The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
-\cs{With prototypical pictures (see Figure\ \ref{fig:picture_naming}), as done in traditional studies, this observation would not be possible.
-(??)}
+With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
 %For theoretical research, w
@@
 
-Our ManyNames dataset can be used for both, theoretical and practical research. 
-Specifically, it provides a means 
+Our ManyNames dataset provides a means 
 (i) to study how different people would name the same object (image region) \cs{"visual awareness" would fit in here}, and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and
@@
 
-As far as research in L\&V and Computer Vision is concerned, our findings are reason to question the appropriateness of the standard, single-label approach in visual object naming and categorization methods.
-Even the assumption that there at least exists a canonical name
+As far as research in L\&V and Computer Vision is concerned, our findings are reason to question 
+%the appropriateness of the standard, single-label approach in visual object naming and categorization methods. 
+ the common assumption that there at least exists a canonical name
 %,\ i.e.,\ a  name on which the majority of people would agree 
- for individual visual objects (localized by bounding boxes) is disputable (cf.\ the high standard deviation in terms of the relative frequency of an instance's top response (column \%top, Table~\ref{tab:agree}), and the average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG})\cs{a bit redundant now}).
+ for individual visual objects (localized by bounding boxes).
+ % cf.\ the high standard deviation in terms of the relative frequency of an instance's top response (column \%top, Table~\ref{tab:agree}), and the average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG})\cs{a bit redundant now}).
 %
@@
 It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs.
-dog, animal, hat?).
+dog, animal, hat).
 %
@@
 as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierachically related. 
-\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
+%\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
 %
@@
 However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-For the same reason, even fine-grained recognition models (as those trained on ILSVRC REF) cannot be expected to be able to simply infer the recognition of more general classes.
+For the same reason, even fine-grained recognition models (as those trained on ILSVRC \cite{ILSVRC15}) cannot be expected to be able to simply infer the recognition of more general classes.
 %since we found that many name alternatives are not hierarchically related to the VG name, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically a "truly" false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
+%\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
 %
 
-\cs{?: Say something about type disagreements on class-level, after having written the results discussion.}
+%\cs{?: Say something about type disagreements on class-level, after having written the results discussion.}
 %
 
-\cs{Ah, we still should have a comparison model with above argumentation :/.}
+%\cs{Ah, we still should have a comparison model with above argumentation :/.}
 %
-As a use-case study, in Section\ \ref{sec:modeling}, we will treat ManyNames as evaluation data and assess whether an existing SOTA model can account for the naming variants of individual objects.
+%As a use-case study, in Section\ \ref{sec:modeling}, we will treat ManyNames as evaluation data and assess whether an existing SOTA model can account for the naming variants of individual objects.
 
@@
 
-\gbt{I couldn't follow the discussion in the following pargraph. Do you think it's subsumed by the one above? Can we remove it?} 
-Given that we find much lower agreement on object class-level than on an instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
-However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).
+%\gbt{I couldn't follow the discussion in the following pargraph. Do you think it's subsumed by the one above? Can we remove it?} 
+%Given that we find much lower agreement on object class-level than on an instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
+%However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).
 Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising cross-classification, metonymy and potentially other sources of variation.

### 2019-05-21 papers/EMNLP2019/analysis.tex
analysis cut down a bit more

@@
 
-We investigate to what extent names in VisualGenome (\vg) and ManyNames can be considered canonical in terms of various agreement measures,
+We investigate to what extent names in our dataset can be considered canonical in terms of various agreement measures,
 %based on annotations in \vg and ManyNames, 
@@
 \begin{itemize}
+\setlength{\itemsep}{0pt}
+\setlength{\parskip}{0pt}
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
@@
 
-If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the object naming literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
+If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
 %In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
@@
 illustrate this, showing visual instances with very high or low agreement. 
-These examples suggest that instances which are more prototypical of a category trigger higher agreement.
+These suggest that instances which are more prototypical of a category trigger higher agreement.
 The following section will examine other potential sources of variation in object naming.
@@
 Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
- but to other sources.
+ but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:
 
@@
 \label{tab:rel}
+\vspace{-0.5cm}
 \end{table}
 
-We discuss other types of variation we found in the data, based on qualitative analysis, and illustrate them with the examples in Figure\ \ref{fig:ex-high-low-agreement}:
-
-\begin{description}
+\begin{description}[style=unboxed,leftmargin=0.2cm]
 \setlength{\itemsep}{0pt}
 \setlength{\parskip}{0pt}
+%\setlength{\leftmargin}{0pt}
 \item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
@@
 Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-\item[Cross-classification:] a substantial group is constituted by names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
+\item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
 \item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
-\item[Metonymy:] similar to cross-classification, we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loosely related synonyms or hypernyms (\textit{robe-dress}).
+\item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
 \end{description}
 
-As it is non-trivial to separate this cases, we leave a precise quantitative analysis of these phenomena for future work.
+As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
 

### 2019-05-21 papers/EMNLP2019/analysis.tex
updated plots

@@
 \end{minipage}
- \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, based on different frequency tresholds (applied on the level of instances and classes respectively)}
+\vspace{-0.8cm}
+ \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds}
 \end{figure*}
@@
 \end{tabular}
-
+\vspace{-0.3cm}
 \caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
@@
 
+%\vspace{-0.5cm}
 \begin{description}[style=unboxed,leftmargin=0.2cm]
@@
 \end{description}
+\vspace{-0.2cm}
 

### 2019-05-21 papers/EMNLP2019/analysis.tex
examples for relations in table

@@
 \centering
-\begin{tabular}{lcc}
+\setlength{\tabcolsep}{2pt}
+\begin{tabular}{lcc|p{2.5cm}}
 \toprule
-         relation & \% types & \% token \\
+         relation & \% types & \% token & \it ex: jacket \\
 \midrule
@@
 % holonym &  0.1 &  0.4 \\
- word-not-covered &  10.6 &  2.6 \\
+ word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
 \midrule
- synonym &  1.1 &  1.1 \\
- hyponym &  2.2 &  3.8 \\
- co-hyponym &  3.1 &  5.9 \\
- hypernym &  10.5 &  27.7 \\
- rel-not-covered &  72.2 &  58.3 \\
+ synonym &  1.1 &  1.1 & \it hoodie  \\
+ hyponym &  2.2 &  3.8 & \it parka, blazer \\
+ co-hyponym &  3.1 &  5.9 & \it raincoat\\
+ hypernym &  10.5 &  27.7 & \it clothing, coat\\
+ rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
 \bottomrule

### 2019-05-21 papers/EMNLP2019/modeling.tex
modeling section free for revision

@@
 		&  =VG & =MN-1 & $\in$MN  & KL\\ 
-		\midrule
-		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ \\
+		\midrule \vspace{.6ex}
+		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
 		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
@@
 \subsection{Experimental Setup}
-\textbf{STILL TO BE DONE: Model, Data}
 \paragraph{Classification model}
-We used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
-It uses Faster R-CNN in conjunction with the ResNet-101 CNN and was pretrained on object and attribute annotations from VisualGenome (after initialization with pretrained ImageNet model).
+To obtain object label predictions we used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
+It's feature vectors were used to train state-of-the-art image captioning and visual question answering models. 
+The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}, which the authors  initialized with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vgenome (\vg).\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
+%
 \iffalse
@@
 \paragraph{Data}
-\begin{itemize}
-	\item We use the softmax distribution for the VG object names, and ignore the distribution over attributes. 
-	\item The authors manually cleaned the set of object names to remove those with poor detection performance.
-	\item Set of classes: 1,600 object names
-	Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes.
-(For those cases, we therefore would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.
-)
-	\item Image set and vocabulary: $346$~name types are not in MN, i.e., our vocabulary (MN--VG) contains $1,254$~names. 
-	We filtered out those images whose VG name was not found in MN--VG, which resulted in $24,585$~instances (note that of those $22,304$~images were also part of the training data of bottom-up)
-\end{itemize}
+Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
+Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN. 
+%(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
+Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of $1,254$~names. 
+Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data).
 
-\paragraph{Evaluation measures}
+\paragraph{Evaluation Procedure}
+We apply Bottom-up to each image and extracted the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.
+
 Model effectiveness is assessed in both, the commonly used single-ground-truth setting and in a multi-label setting. 
-In the former, for each instance, we compare the model's top prediction to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
+In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
 In the multi-label setting, we report the average accuracy of the top prediction to match any of the responses in MN. 
-To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat the model's softmax output~$S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
+To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat\ $S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.

### 2019-05-21 papers/EMNLP2019/relwork.tex
fix broken ref

@@
 \paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
-An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
+An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure \ref{fig:cake}.
 Subjects reach very high agreement in this task, \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.

### 2019-05-21 papers/EMNLP2019/modeling.tex
pass over modeling section

@@
 		\toprule
-		%{} &  All images-top=VG &  All images-top=MN-1 &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN-1 &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN-1 &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
+		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
 		& \multicolumn{12}{c}{Image subset} \\
 		&	\multicolumn{4}{c}{All ($24,585$)} 
-		& \multicolumn{4}{c}{VG$\neq$MN-1 ($6,280$)}
+		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
 		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
@@
 		&  \multicolumn{2}{c}{multi-label} \\
-		Domain	 &  =VG & =MN-1 & $\in$MN  &  KL
-		&  =VG & =MN-1 & $\in$MN  & KL
-		&  =VG & =MN-1 & $\in$MN  & KL\\ 
+		Domain	 &  =VG & =MN & $\in$MN  &  KL
+		&  =VG & =MN & $\in$MN  & KL
+		&  =VG & =MN & $\in$MN  & KL\\ 
 		\midrule \vspace{.6ex}
@@
 	\caption{Baseline: The most frequent name.
-Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN-1) and 6.9 ($\neg$Training).
+Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
 The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
@@
 % mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)
-\cs{Ah, we still should have a comparison model with above argumentation :/.}
+
 %
@@
 % multi-label data also during training 
-(cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a model that was trained on single names---VG's object names (and attributes, though).
+(cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a model that was trained on single names---VG's object names.
 %, i.e., it did not see multiple names for individual objects during training.
@@
 %Get an intuition in how far models are able to identify an object by one of it's possible names (gt=dog, is system still able to identify the object if the name is puppy?).
-\cs{And with this argumentation, we'd ideally compare to a model fine-tuned on our data ... and to a model trained on all our names with a response count$>$n ... so much future work}
+% \cs{And with this argumentation, we'd ideally compare to a model fine-tuned on our data ... and to a model trained on all our names with a response count$>$n ... so much future work}
 
-\subsection{Experimental Setup}
-\paragraph{Classification model}
+%\subsection{Experimental Setup}
+\paragraph{Model and Data}
 To obtain object label predictions we used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
@@
 
-\paragraph{Data}
-Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
+%\paragraph{Data}
+We test on $24,585$~images from MN and $1,254$~names.
+From the original vocabulary of Bottom-up, consisting of $1,600$ object names, we removed the ones that are not found in MN, and we also filtered out the images of MN whose \vg name was not in the resulting vocabulary.
+Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set.
+%Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
+\gbt{Carina, I don't understand the following sentence}
 Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN.
 %(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
-Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of $1,254$~names. 
-Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data).
+% Despite the much larger vocabulary of MN ($XX$\ name types), $346$~types are not in MN, which we removed, resulting in a final vocabulary (\mbox{MN$\cap$VG}) of 
+% Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data).
 
 \paragraph{Evaluation Procedure}
-We apply Bottom-up to each image and extracted the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.
+We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.
 
-Model effectiveness is assessed in both, the commonly used single-ground-truth setting and in a multi-label setting. 
-In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN-1}, respectively).
-In the multi-label setting, we report the average accuracy of the top prediction to match any of the responses in MN. 
-To assess the model's ability to account for human naming variations of MN instances, including the likelihood of names being produced for an instance, we treat\ $S$ as a probability distribution and compare it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
+Model effectiveness is assessed in two settings, the commonly used single-label setting and a multi-label setting. 
+In the former, for each instance, we compare the model's top prediction (the object label with the highest score in\ $S$) to its VG name and to the top response in MN, respectively, and report the average accuracy across all instances (\textit{=VG} and \textit{=MN}, respectively).
+In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
+We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}).
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
+We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}.
+\gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0...
+with MN top.
+Not sure if this is too ``cheap'' -- is it a matter of course that it will be lower?
+Not if the distribution doesn't reflect the actual $M$?}
 
@@
 	\item \textbf{=VG} The average model accuracy of \textsl{top} on the VG names
-	\item \textbf{=MN-1} The average model accuracy of \textsl{top} on the top response in ManyNames
+	\item \textbf{=MN} The average model accuracy of \textsl{top} on the top response in ManyNames
 	\item \textbf{$\in$MN} The average model accuracy of \textsl{top} to match any name of the responses in ManyNames
@@
 
-\paragraph{Results \& Discussion} 
-We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}. 
-Apart from the evaluation on the full set of instances (\textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN-1}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
-Note that the latter two sets are disjoint. 
-%
+%\subsection{Results \& Discussion}
+\paragraph{Results and Discussion}
+Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax probabilities for the images in the figure.
+\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.
+All important points can be made at that level, and this way we gain space.}
+% Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
+% The latter two sets are disjoint. 
+Strikingly, the model performs worse on VG than on the top MN response, even though the model was trained on VG names and saw the majority of the instances during training: It has a general accuracy of 76.8 on MN, 68.7 on VG (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger, 52.6 vs.\ 20.7.
+We hypothesize two main reasons for this difference.
+First, the top MN name may be more reliable because it is collected from multiple subjects: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textit{sandwich}, but \textit{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three subjects still chose \textit{sandwich}).
+Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
+% It achieves a higher accuracy of up to\ 55\% points on instances for which MN and the VG name differ (\textsc{buildings}, VG$\neq$MN). 
+% The reasons may be that MN is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).
 
-The model performs worse on VG than on the top MN response (MN-1), even though the model saw the majority of the instances during training. 
-It achieves a higher accuracy of up to\ 55\% points on instances for which MN-1 and the VG name differ (\textsc{buildings}, VG$\neq$MN-1). 
-The reasons may be that MN-1 is more general than VG for many cases (e.g.,\ the examples for \textsl{batter} in Fig.\ \ref{fig:ex-high-low-agreement}), or that MN-1 is more reliable due to up to $36$~annotations per instance as well as to our elicitation procedure\footnote{Recall that we instructed the workers explicitly to produce object names, and did not obtain them by canonicalizing object descriptions as was done for VG.} (e.g.,\ (\textsl{sandwich,hotdog}), Fig.\ \ref{fig:ex-high-low-agreement}).
-Another reason could be that the model reproduces naming choices ("errors") caused by cases of visual uncertainty (cf.\ Section\ \ref{ssec:variation}; e.g.,\ (\textsl{bridge,street})).
-
-In the multi-label setting, $\in$MN, the difference in accuracy between the objects in All and in the subset VG!=MN-1 is much lower compared to the MN-1 setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains).
-Comparison to the results on unseen images demonstrates Bottom-up's generalization ability. 
-While the difference varies highly across the domains (All vs. \mbox{$\neg$\textit{Training}}), it is negligible on average (row \textit{all}), and the same on the \mbox{VG!=MN-1} images. 
-%Unsurprisingly, the effectiveness of Bottom-up drops on the images which it has not seen during training, and the difference in accuracy highly varies across the domains (All vs.
-\mbox{$\neg$\textit{Training}}).
-Taken together, we thus believe that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, since a model's effectiveness is not measured by a single naming choice.
+Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In 92-95\% of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object --even in the unseen images (\mbox{$\neg$\textit{Training}}).
+This is a very high result.
+% In the multi-label setting, $\in$MN, the difference in accuracy between the objects in the \textit{All} and in the subset VG$\neq$MN is much lower compared to the single-label setting ($-2.5$\% vs.\ $-24.2$\%\ points, all domains).
+%Comparison to the results on unseen images demonstrates Bottom-up's generalization ability. 
+% While the difference varies highly across the domains (All vs. \mbox{$\neg$\textit{Training}}), it is negligible on average (row \textit{all}), and the same on the \mbox{VG$\neq$MN} images. 
+Taken together, the results suggest that our ManyNames dataset provides a more robust evaluation framework than single-label datasets, allowing researchers to better differentiate between possible alternative names and true mistakes.
 
@@
 As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
+\gbt{The following is interesting but I would move it to supp. material (see above).}
 It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which tend to contain occluded or unclear bounding boxes \cs{can we say that?}.
-%For these more difficult instances (VG!=MN-1),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
+%For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
 
-Comparing the model output to MN on individual images gives an intuition for how much Bottom-up accounts for naming choices due to different sources of variation: 
-In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{(boy,helmet)},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror  cases of human "referential uncertainty"
-%(\textsc{clothing}-\textsc{person}: 
-(\textsl{(man,shirt)}, \textsl{(bed,sheet)}, but see \textsl{(book,bed})), as well as cross-classification (\textsl{(boy,batter)}, \textsl{(sandwich,food)}), and metonymy \textsl{(food,basket/plate)}.
-It reflects perceptual mistakes caused by unclear images (\textit{sandwich,banana}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{(bridge,sky)}, \textsl{(pants/player,dirt)}.
+Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
+In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty''
+(\textsl{man-shirt}, \textsl{bed-sheet}).
+We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
+It also reflects perceptual mistakes caused by unclear images (\textit{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}.
 
@@
 	\item VG worse than MN; considering that model was trained on VG - is it because MN has easier labels? Does this mean that generalisation ability is better evaluated on MN?
-	\item VG!=MN-1 much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
-	\item for those more difficult images (VG!=MN-1), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
-	\item accuracy drops for notTrain (except for vehicles MN-1), but is still much better than VG!=MN-1  
+	\item VG$\neq$MN much worse than All $\Rightarrow$ Former has more difficult/ambiguous images (for both? classifier and human?)
+	\item for those more difficult images (VG$\neq$MN), the difference for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
+	\item accuracy drops for notTrain (except for vehicles MN), but is still much better than VG$\neq$MN  
 \end{itemize}
@@
 \fi
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "main.tex"
+%%% End:

### 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
adds model predictions to Fig4 (analysis)

@@
 	\begin{minipage}[b]{0.5\linewidth}
-		{\footnotesize
+		{\scriptsize
 			\setlength{\tabcolsep}{1pt}
@@
 				%
+				\rowcolor{lightgray}
 				 \textit{sandwich}, food, bread, sandwiches, plate, burger
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\
-				\\ 
 				%
+				\rowcolor{lightgray}
 				\textit{bridge}, arch, sky, structure, walkway
@@
 				%
+				\rowcolor{lightgray}
 				\textit{bed}, beds, sheets, frame, sheet
@@
 				%
+				\rowcolor{lightgray}
 				\textit{man}, player, \textit{person}, shirt, guy
@@
 				%
+				\rowcolor{lightgray}
 				woman, outfit, dress, girl, suit
@@
 				& \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
-				& teddy bear, \textit{bear}, dog, \textit{toy}, stuffed animal, blanket, toys
+				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
 				%, stuffed animals \\ 
@@
 	\end{minipage}
-	\caption{Examples for different instances of \vgenome synsets with low and high agreement in ManyNames. 
+	\caption{Examples for instances of \vgenome synsets with low and high agreement in ManyNames. 
 		First row: responses in MN, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined.
-	Second row: top name prediction by bottom up, names which match a MN respose are in italics.}
+	Second row (gray): top name prediction by bottom up, names which match a MN response are in italics.}
 	\label{fig:ex-high-low-agreement}

### 2019-05-21 papers/EMNLP2019/modeling.tex
one more comment modeling section
small changes

@@
 %Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
-\gbt{Carina, I don't understand the following sentence}
-Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN.
+Semantically similar classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN.
 %(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
@@
 In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
-We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}).
+We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
+%; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
-We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}.
+We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense.
+TBD?
+MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}.
 \gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0...
@@
 \paragraph{Results and Discussion}
-Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax probabilities for the images in the figure.
+Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
 \gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.

### 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
magic! small table, more space

@@
 			\setlength{\tabcolsep}{1pt}
-			\begin{tabular}{p{4cm}|p{4cm}|p{4cm}|p{4cm}}
+			\begin{tabular}{p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}}
 				%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
@@
 				%\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1593011_2063521_singleton_obj.png}} MN: wood \\
-				\multicolumn{4}{c}{\textbf{VG: sandwich}}\\
+				\multicolumn{4}{c|}{\textbf{VG: sandwich}} & \multicolumn{2}{c}{\textbf{VG: robe}}\\
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)]\\
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)] &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2)\\ 
 				%
@@
 				 & fish, chicken, meat, \textit{food}, \textit{sandwich}, bread
-				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table \\ 
+				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table
+				 & woman, outfit, dress, girl, suit
+				& woman, outfit, \textit{dress}, girl, suit \\ 
 				%
 				%
-				\multicolumn{4}{c}{\textbf{VG: bridge} }\\ 
+				\multicolumn{4}{c|}{\textbf{VG: bridge} } & \multicolumn{2}{c}{\textbf{VG: robe}}\\ 
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3)\\
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2412972_3494120_singleton_obj.png}} pier (6), railing (5), dock (5), bridge (5), fence (4), rail (3), boardwalk (3) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
 				%
@@
 				& \textit{street}, \textit{road}, highway, intersection, pavement
-				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} \\ 
+				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} 
+			         & \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
+				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
+\\ 
 				%
 				% 
-				\multicolumn{4}{c}{\textbf{VG: bed}}\\ 
+				\multicolumn{4}{c|}{\textbf{VG: bed}} & \multicolumn{2}{c}{\textbf{VG: batter}}\\ 
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2321254_3438076_singleton_obj.png}} bed (36)  &
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2342811_3485104_singleton_obj.png}}  bed (17), book (6), table (4), toy (3), bible (2), doll (2) & 
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5)\\ 
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ \\
 				%
@@
 				& \textit{bed}, sheet, sheets, blanket, comforter, cover
-				& \textit{bed}, comforter, \textit{blanket}, cover, sheet \\ 
-				%
-				% 
-				\multicolumn{4}{c}{\textbf{VG: batter}}\\
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
-				%
-				\rowcolor{lightgray}
-				\textit{man}, player, \textit{person}, shirt, guy
-				& \textit{player}, \textit{batter}, \textit{man}, \textit{baseball player}, uniform
+				& \textit{bed}, comforter, \textit{blanket}, cover, sheet 
 				& \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
@@
 				% 
-				\multicolumn{4}{c}{\textbf{VG: robe}}\\
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
-				%
-				\rowcolor{lightgray}
-				woman, outfit, dress, girl, suit
-				& woman, outfit, \textit{dress}, girl, suit
-				& \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
-				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
-				%, stuffed animals \\ 
+%				\multicolumn{4}{c}{\textbf{VG: batter}}\\
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
+%				%
+%				\rowcolor{lightgray}
+%				\textit{man}, player, \textit{person}, shirt, guy
+%				& \textit{player}, \textit{batter}, \textit{man}, \textit{baseball player}, uniform
+%				& \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
+%				& \textit{player}, batter, \textit{person}, man, uniform, boy, \textit{baseball player}, dirt \\ 
 				%
 				% 
+%				\multicolumn{4}{c}{\textbf{VG: robe}}\\
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
+%				%
+%				\rowcolor{lightgray}
+%				woman, outfit, dress, girl, suit
+%				& woman, outfit, \textit{dress}, girl, suit
+%				& \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
+%				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
+%				%, stuffed animals \\ 
+%				%
+%				% 				
 			\end{tabular}
@@
 \end{figure*}
+
+\begin{table*}
+	\centering
+	\small
+	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
+		\toprule
+		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
+		& \multicolumn{12}{c}{Image subset} \\
+		&	\multicolumn{4}{c}{All ($24,585$)} 
+		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
+		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
+		\midrule
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label}
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label}
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label} \\
+		Domain	 &  =VG & =MN & $\in$MN  &  KL
+		&  =VG & =MN & $\in$MN  & KL
+		&  =VG & =MN & $\in$MN  & KL\\ 
+		\midrule \vspace{.6ex}
+		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
+		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
+		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
+		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
+		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
+		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
+		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
+		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
+		\bottomrule
+		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
+		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
+	\end{tabular}
+	\caption{Baseline: The most frequent name.
+Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
+The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
+\end{table*}

### 2019-05-21 papers/EMNLP2019/modeling.tex
magic! small table, more space

--- 2019-05-21 papers/EMNLP2019/modeling.tex
@@
-\begin{table*}
-	\centering
-	\small
-	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
-		\toprule
-		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
-		& \multicolumn{12}{c}{Image subset} \\
-		&	\multicolumn{4}{c}{All ($24,585$)} 
-		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
-		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
-		\midrule
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label} \\
-		Domain	 &  =VG & =MN & $\in$MN  &  KL
-		&  =VG & =MN & $\in$MN  & KL
-		&  =VG & =MN & $\in$MN  & KL\\ 
-		\midrule \vspace{.6ex}
-		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
-		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
-		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
-		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
-		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
-		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
-		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
-		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
-		\bottomrule
-		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
-		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
-	\end{tabular}
-	\caption{Baseline: The most frequent name.
-Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
-The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
-\end{table*}
 %
@@
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
-We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense. TBD?}.
+We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense.
+TBD?
+MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}.
 \gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0...

### 2019-05-21 papers/EMNLP2019/data-collection.tex

@@
 We obtained a total of 36 names per image (i.e.,\ objects).
-As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language \& vision (see discussion in Sections~\ref{sec:analysis,??}).
+As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language \& vision (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
 \gbt{TO DO: revise that this matches the narrative in the rest of the paper.}
-Overall $XX$ turkers took part in the data elicitation, each naming a median of XXX instances. \gbt{@Carina pls fill in.}
+Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
 \cs{Maybe say something about the rejections, if space permits it.}

### 2019-05-21 papers/EMNLP2019/modeling.tex
went over the modeling section (and changed its title)

@@
 %
-We use ManyNames\ (MN) as evaluation data, and assess whether an object recognition model can account for MN's naming variants provided for individual objects.
-In contrast to existing works on multi-label classification, which also train their models towards multi-label predictions 
+We use ManyNames\ (MN) to evaluate whether an object recognition model can account for naming variants for objects in MN.
+In contrast to existing works on training and predicting multiple labels
+% classification, which also train their models towards multi-label predictions 
 % multi-label data also during training 
-(cf.\ Section\ \ref{sec:relwork}\cs{check that this is said there}), we use a model that was trained on single names---VG's object names.
-%, i.e., it did not see multiple names for individual objects during training.
-Through this case study we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
-We argue that this is a more natural setting, since people may not hear different names when referring to the same object, but rather across different objects of the same class \cs{any REF to paper where name choice for specific object stays consistent once done?}.
+(cf.\ Section\ \ref{sec:relwork}), we use a model that was trained on single names---VG's object names. %, i.e., it did not see multiple names for individual objects during training.  
+%Through this case study 
+We examine whether this model implicitly learns representations of the relations between object names despite of not being trained towards this. 
+We argue that this is a more natural setting, since people may not hear different names when referring to the same object, but rather across different objects of the same class \cite{frank2009using}.
+%\cs{any REF to paper where name choice for specific object stays consistent once done?}. 
 %By this means, we examine whether classification models are able to implicitly learn representations of the relations between object names despite of not being trained towards this. 
@@
 To obtain object label predictions we used \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} bottom-up attention model (\textit{Bottom-up} henceforth)\footnote{The features code and data is available at \url{https://github.com/peteanderson80/bottom-up-attention}}.
-It's feature vectors were used to train state-of-the-art image captioning and visual question answering models. 
+%It's feature vectors were used to train state-of-the-art image captioning and visual question answering models. 
 The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}, which the authors  initialized with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vgenome (\vg).\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
@@
 We test on $24,585$~images from MN and $1,254$~names.
-From the original vocabulary of Bottom-up, consisting of $1,600$ object names, we removed the ones that are not found in MN, and we also filtered out the images of MN whose \vg name was not in the resulting vocabulary.
+From the original vocabulary of Bottom-up, consisting of $1,600$ object names, we removed the ones \sz{how many?} that are not found in MN, and filtered  images whose \vg name was not in the resulting vocabulary.
 Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set.
 %Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
-\gbt{Carina, I don't understand the following sentence}
+\gbt{Carina, I don't understand the following sentence} \sz{me neither}
 Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN.
@@
 \gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.
-All important points can be made at that level, and this way we gain space.}
+All important points can be made at that level, and this way we gain space.} \sz{I would not do that}
 % Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
@@
 \gbt{The following is interesting but I would move it to supp. material (see above).}
-It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which tend to contain occluded or unclear bounding boxes \cs{can we say that?}.
+It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}.
 %For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain

### 2019-05-21 papers/EMNLP2019/relwork.tex
revises rel work

@@
 Object naming is closely related to processes of visual object recognition investigated in Computer Vision or Cognitive Science.
-This Section discusses questions relates to these areas and naming as a linguistic phenomenon in Language \& Vision.
+We discuss questions related to these areas and naming as a linguistic phenomenon in L\&V.
 
-\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
-An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure \ref{fig:cake}.
-Subjects reach very high agreement in this task, \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
+\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
+An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure\ \ref{fig:cake}.
+Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
 Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
-Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to predict thousands of different categories, e.g.\  \newcite{googlenet}.
-Current object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}.
+Recognition of instances (as opposed to categories) in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories, (e.g.\ \newcite{googlenet}).
+Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach. 
+%, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}. 
+%\cs{do you mean multi-label classifiers in single ground-truth label settings?}
 In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
-For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for e.g.
-people are missing.
+For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.
 
@@
 % but looks at the principles underlying the organization of object categories. 
-
-has emphasized the taxonomic organization of categories, e.g.\ seminal work on prototypes by Rosch \cite{rosch1976basic},  and found that humans tend to conceptualize objects at a basic or medium level of abstraction.
+has emphasized the taxonomic organization of categories, e.g.\ seminal work on prototypes by \newcite{rosch1976basic},  and found that humans tend to conceptualize objects at a basic or medium level of abstraction.
 % in this taxonomy. 
 %This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-Granularity-aware approaches to object recognition have aimed at exploiting taxonomical structure underlying object labels \cite{deng2014large,wang2014poodle,peterson2018learning},  
+Granularity-aware object recognition methods have incorporated the taxonomic structure underlying object labels in multi-label settings \cite{deng2014large,wang2014poodle,peterson2018learning}, as an account to the criticism on the use of single-labels.
 %While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, 
-but still aim to predict a single canonical category.% (that does have relations to other categories). 
-This view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+%but still aim to predict a single canonical category. % (that does have relations to other categories). 
+The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
 This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
-To the best of our knowledge, this phenomenon has not received any attention in work on L\&V.
+To the best of our knowledge, this phenomenon has not received any attention in L\&V.
 Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
-
+%
 %Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.} \gbt{ok}
-
+%
 %have  frameworks previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning};
 %Ristin et al., 2015 REF, and the references therein). 
-
+%
 % \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
@@
 also sentence to Ordonez}
-
+%
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
@@
 \paragraph{Work on Object Naming} that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
-Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focussed mostly on the selection of attributes% rather than on determining the referent's name
+Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name
 \cite{krahmer:2012}. 
-\newcite{Ordonez:2016} extend object recognition to naming as an extension, taking up the notion of entry-level categories \cite{rosch1976basic}.
-Their model classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name,
-based on frequencies in a text corpus. 
+\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
+% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
+%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
  \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 

### 2019-05-21 papers/EMNLP2019/conclusion.tex
modeling: finishes results+discussion; TODO: model+data formulation
first go at conclusion

@@
-\subsection{Conclusion}
-\label{sec:conclusion}
+The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
+For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
+In future work, we want to use the ManyNames data to fine-tune existing models such that their behavior is more human-like, and check if models trained on the ManyNames data perform better than models trained on single labels.
+\gbt{@Carina, pls check if this is what you meant}
 
-The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
+For theoretical work, it provides name variation data with natural images and thus at the \textit{instance} level, as opposed to the category level that has been the focus up to now in theoretical work, due to the use of highly stylized drawings.
+This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as prototypicality of the instance itself, or the effect of the visual context.
+However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation.
+Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag} when the two overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
+This of course is not an issue when working with the kind of images that traditional studies in Psycholinguistics have used, and future work will need to address it.
+\gbt{Do you think this is too negative as a conclusion? I feel like it's the elephant in the room -- if we don't say it here, we should say it somewhere prominently.}
 

### 2019-05-21 papers/EMNLP2019/data-collection.tex
revises modeling revision
data coll -- 1 TODO left

@@
 as basis.
-We selected images from seven domains: six based on \newcite{mcrae2005semantic}'s \citeyear{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that consists of common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
+We selected images from seven domains: six based on McRae et al.'s  (\citeyear{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 
-Within each domain, we aimed at collecting instances at different levels in a taxonomy to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy %in the first place
+Within each domain, we aimed at collecting instances at different taxonomic levels  to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy %in the first place
 (e.g.\ \textsc{home}).
@@
 Instead, we defined a set of synsets ($52$\ in total) that we would use to collect our object instances from \vg, balancing variability.
-From the set of synsets that match or subsume the concepts in the McRae norms, we kept those that had a high number of \vg object instances of different names.
+From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
 For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
 
-We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds}, and we had 450 of them.
-We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{(REF to tagger)}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
-We further only considered objects whose bounding box covered an area of~$20-90\%$ of the image.
+We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
+We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}).
+We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
 % We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ.
@@
 Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds.
-\textbf{double-check}
-This yielded a dataset with $31,093$~instances, which was further pruned during annotation (see Section\ \ref{subsec:elicitation}). 
-Table~\ref{tab:overview_dataset1} shows the $7$\ domains together with the top $10$\ \vg names.
-
-\cs{@Carina ToDo: add some examples of synsets + names; maybe in suppl}
+%\textbf{double-check}
+This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation. 
+See Section\ \ref{ssec:elicitation} and the Supplemental Material for details on the pruning. 
 % \begin{itemize}
@@
 In initial pilot studies, we found object identification via bounding boxes to be problematic.
-In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the bounding box (for instance, for a box around a jacket, the man wearing it).
-We took special care of minimizing this issue, in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear.
-The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
-We eliminated around 5.5K images based on pruning, obtaining the final dataset with 25,596\ images.
+In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
+We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear.
+%The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
+We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images. 
+(We refer to the Supplemental Material for the task instructions and more details on the pruning and the dataset.) 
 We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
@@
 We obtained a total of 36 names per image (i.e.,\ objects).
-As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in language \& vision (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
+As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
 \gbt{TO DO: revise that this matches the narrative in the rest of the paper.}
 Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
-\cs{Maybe say something about the rejections, if space permits it.}
+%\cs{Maybe say something about the rejections, if space permits it.}
 %%% Local Variables:

### 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
fitting table
moves table with modeling results.

@@
-\begin{figure*}
+\begin{figure*}[t]
 	\begin{minipage}[b]{0.5\linewidth}
@@
 			\setlength{\tabcolsep}{1pt}
-			\begin{tabular}{p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}|p{2.8cm}}
+			\begin{tabular}{p{2.6cm}|p{2.6cm}|p{2.6cm}|p{2.6cm}|p{2.6cm}|p{2.6cm}}
 				%\textbf{desk} &  \raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2320949_1048853_singleton_obj.png}} MN: keyboard  &
@@
 \end{figure*}
-
-\begin{table*}
-	\centering
-	\small
-	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
-		\toprule
-		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
-		& \multicolumn{12}{c}{Image subset} \\
-		&	\multicolumn{4}{c}{All ($24,585$)} 
-		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
-		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
-		\midrule
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label} \\
-		Domain	 &  =VG & =MN & $\in$MN  &  KL
-		&  =VG & =MN & $\in$MN  & KL
-		&  =VG & =MN & $\in$MN  & KL\\ 
-		\midrule \vspace{.6ex}
-		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
-		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
-		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
-		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
-		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
-		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
-		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
-		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
-		\bottomrule
-		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
-		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
-	\end{tabular}
-	\caption{Baseline: The most frequent name.
-Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
-The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
-\end{table*}

### 2019-05-21 papers/EMNLP2019/modeling.tex
moves table with modeling results.

@@
 % mismatch between the visual awareness of the target object (man) and that of the competitor object (shirt)
-
 %
@@
 %\paragraph{Data}
-We test on $24,585$~images from MN and $1,254$~names.
-From the original vocabulary of Bottom-up, consisting of $1,600$ object names, we removed the ones \sz{how many?} that are not found in MN, and filtered  images whose \vg name was not in the resulting vocabulary.
+Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
+They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. \gbt{Carina, I don't understand the following sentence}
+
+From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
 Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set. 
-%Bottom-up was trained on a set of $1,600$\ object names (the authors manually removed names with poor a detection performance from the original set). 
-\gbt{Carina, I don't understand the following sentence} \sz{me neither}
-Overlapping classes, such as \textsl{person} and \textsl{guy}, were not merged to single classes which is in line with the data structure of MN.
+%
 %(For those cases, we would expect that evaluating the model output on our set of names per instance to yield higher detection accuracy.)
@@
 % Similarly, we filtered out the images of MN whose \vg name was not in \mbox{MN$\cap$VG}, which resulted in $24,585$~instances (note that of those, $22,304$~images were also part of Bottom-up's training data).
-
 \paragraph{Evaluation Procedure}
-We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.
+We apply Bottom-up to each image and extract the distribution~$S$ over object labels from the final softmax layer output for the ground-truth bounding box of the target object.\footnote{We converted the scores to our vocabulary size.}
 
@@
 In the multi-label setting, we report the average accuracy of the top prediction matching any of the responses in MN.
-We also test the model's ability to mimick the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}).
+We also test the model's ability to mimic the distribution of names provided by humans, by treating $S$ as a probability distribution and comparing it to the probability distribution~$M$ over the MN responses (estimated by normalizing the name counts).
+%; as in the analysis above, we remove names with frequency 1 to account for possible noise\gbt{@Carina, pls revise}). 
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
@@
 \paragraph{Results and Discussion}
-Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax probabilities for the images in the figure.
+Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
 \gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.
-All important points can be made at that level, and this way we gain space.} \sz{I would not do that}
+All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
 % Apart from the evaluation on the full set of instances (column \textit{\mbox{All}} in Table~\ref{tab:model}), we further assess model effectiveness on the instances whose  \vg names do not match the top response in MN (\mbox{\textit{VG}$\neq$\textit{MN}}), and on those which were not part of the set of images used for training bottom-up (\mbox{$\neg$\textit{Training}}).
 % The latter two sets are disjoint. 
-Strikingly, the model performs worse on VG than on the top MN response, even though the model was trained on VG names and saw the majority of the instances during training: It has a general accuracy of 76.8 on MN, 68.7 on VG (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger, 52.6 vs.\ 20.7.
+Strikingly, the model performs worse on \vg than on the top MN response, even though the model was trained on \vg names and saw the majority of the instances during training: It has a general accuracy of $76.8$\ on MN, $68.7$\ on \vg (see condition \textit{All}), and in the subset where the top names differ (VG$\neq$MN) the difference is even bigger,\ $52.6$ vs.\ $20.7$.
 We hypothesize two main reasons for this difference.
@@
 
-Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In 92-95\% of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object --even in the unseen images (\mbox{$\neg$\textit{Training}}).
+Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In \mbox{$92-95\%$}\ of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object--even in the unseen images (\mbox{$\neg$\textit{Training}}).
 This is a very high result.
@@
 It also reflects perceptual mistakes caused by unclear images (\textit{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}.
-
+%
 \iffalse

### 2019-05-21 papers/EMNLP2019/modeling.tex
--

@@
 Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
-They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. \gbt{Carina, I don't understand the following sentence}
-
+They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. %\gbt{Carina, I don't understand the following sentence}
+%
 From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
@@
 We hypothesize two main reasons for this difference.
-First, the top MN name may be more reliable because it is collected from multiple subjects: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textit{sandwich}, but \textit{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three subjects still chose \textit{sandwich}).
+First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
 Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.

### 2019-05-21 papers/EMNLP2019/analysis.tex
moves table with modeling results.

@@
  but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:
-
-\begin{table}
+%
+\begin{table}[t]
 \small
@@
 Our ManyNames dataset provides a means 
-(i) to study how different people would name the same object (image region) \cs{"visual awareness" would fit in here}, and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and
+(i) to study how different people would name the same object (image region),  
+%\cs{"visual awareness" would fit in here}, 
+and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
 %assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
@@
 % peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
+%
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
+		\toprule
+		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
+		& \multicolumn{12}{c}{Image subset} \\
+		&	\multicolumn{4}{c}{All ($24,585$)} 
+		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
+		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
+		\midrule
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label}
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label}
+		&  \multicolumn{2}{c}{single-label}
+		&  \multicolumn{2}{c}{multi-label} \\
+		Domain	 &  =VG & =MN & $\in$MN  &  KL
+		&  =VG & =MN & $\in$MN  & KL
+		&  =VG & =MN & $\in$MN  & KL\\ 
+		\midrule \vspace{.6ex}
+		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
+		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
+		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
+		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
+		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
+		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
+		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
+		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
+		\bottomrule
+		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
+		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
+	\end{tabular}
+	\caption{Baseline: The most frequent name.
+Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
+The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
+\end{table*}
 %

### 2019-05-21 papers/EMNLP2019/conclusion.tex

@@
 For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
-In future work, we want to use the ManyNames data to fine-tune existing models such that their behavior is more human-like, and check if models trained on the ManyNames data perform better than models trained on single labels.
+%In future work, we want to use the ManyNames data to fine-tune  existing models tsuch that their behavior is more human-like, and check if models trained on the ManyNames data perform better than models trained on single labels.
 \gbt{@Carina, pls check if this is what you meant}
+In future work, we want to use ManyNames to fine-tune and examine  existing models in a multi-label setting towards a behavior that is more human-like. 
+%, and check if models trained on the ManyNames data perform better than models trained on single labels. \gbt{@Carina, pls check if this is what you meant}
 
@@
 This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as prototypicality of the instance itself, or the effect of the visual context.
-However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation.
+
+%However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation. 
+The use of naturalistic images in place of stylized drawings also comes with new challenges, which interfere with the study of naming variation: the factors inherently underlying variations cannot be easily separated from those introduced by issues such as object identification.
 Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag} when the two overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
-This of course is not an issue when working with the kind of images that traditional studies in Psycholinguistics have used, and future work will need to address it.
+%This of course is not an issue when working with the kind of images that traditional studies in Psycholinguistics have used, and future work will need to address this.
+Future work will need to address these challenges. 
 \gbt{Do you think this is too negative as a conclusion? I feel like it's the elephant in the room -- if we don't say it here, we should say it somewhere prominently.}

### 2019-05-21 papers/EMNLP2019/suppl_material.tex

@@
 Figures~\ref{fig:instructions1} and~\ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
-After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection).
-This yielded $25,596$ images, discarding $5,497$.
-
+After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection):
 \begin{itemize}
@@
 \end{itemize}
+This yielded $25,596$ images, discarding $5,497$.
+Table~\ref{tab:overview_dataset1} shows the $7$\ domains together with the top $10$\ VG names.
 
-Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, XXX, XXX, grouped into the $7$~domains.
+Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, grouped into the $7$~domains.
 \gbt{@Carina, the table doesn't fit, maybe put one domain x row?}
@@
 \end{tabular}
-	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
+	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). %\textbf{double-check}
+		 \label{tab:overview_dataset2}}
       \end{table*}
@@
 \end{tabular}
-	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
+	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
+		 \label{tab:overview_dataset1}}
 \end{table*}

### 2019-05-21 papers/EMNLP2019/analysis.tex
better refs on variation in image captioning

@@
 Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
-{\small
 \begin{itemize}
@@
 \end{itemize}
-}
+
 %\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
@@
 
-As shown in Table\ \ref{tab:agree}, generally, the agreement measures follow a similar pattern as the type counts discussed in Section\ \ref{subsec:counts}:
+Table\ \ref{tab:agree} shows, generally, that the agreement measures follow a similar pattern as the type counts in Section\ \ref{subsec:counts}:
 On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
 the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
-On the class level, however, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
-The $H$ measures indicate a fair amount of agreement for instances, a bit lower than the agreement found in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55).
+On the class level, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
+The $H$ measures indicate a fair amount of agreement for instances, which is a bit lower than in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55).
 On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.

### 2019-05-21 papers/EMNLP2019/analysis.tex
small fixes

--- 2019-05-21 papers/EMNLP2019/analysis.tex
@@
 Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
-{\small
+
 \begin{itemize}
-\setlength{\itemsep}{0pt}
+\setlength{\itemsep}{1pt}
 \setlength{\parskip}{0pt}
-\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent)
+\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
 \item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
-where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses.% \cs{@Sina: right?}
-\item \textbf{N}: the average number of types in the response set of ManyNames
-\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name 
-\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set 
+where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
+\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name.
+\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
 \end{itemize}
-}
+
 %\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
@@
 However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
- but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:
+Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.
+
+We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}.
+\textbf{Referential uncertainty}: despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
+%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
+Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
+\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
+\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
+As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
 %
@@
 
+%GBT: I changed this cause I'm afraid to be left out for formal reasons. 
 %\vspace{-0.5cm}
-\begin{description}[style=unboxed,leftmargin=0.2cm]
-\setlength{\itemsep}{0pt}
-\setlength{\parskip}{0pt}
-%\setlength{\leftmargin}{0pt}
-\item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+% \begin{description}[style=unboxed,leftmargin=0.2cm]
+% \setlength{\itemsep}{1pt}
+% \setlength{\parskip}{0pt}
+% %\setlength{\leftmargin}{0pt}
+% \item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
 They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
+% %Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
 Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-\item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-\item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
-\item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-\item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
-\end{description}
-\vspace{-0.2cm}
-
-As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
+% \item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
+% \item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
+% \item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+% \item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
+% \end{description}
+% \vspace{-0.2cm}
 

### 2019-05-21 papers/EMNLP2019/data-collection.tex
small fixes

@@
 As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
-\gbt{TO DO: revise that this matches the narrative in the rest of the paper.}
 Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

### 2019-05-21 papers/EMNLP2019/analysis.tex

@@
 Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
-
 \begin{itemize}

### 2019-05-21 papers/EMNLP2019/analysis.tex
small things here and there

@@
 % where subjects are free to choose any response. 
-When discarding names these, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
+When discarding these names, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
 majority of the response sets become more consistent with at most 5\ names per set, 
@@
 but the sets with a single name still make up only $<$50\%\ of all sets. 
-This indicates that variation in naming instances is restricted to a manageable set of up to 5\ names per object, but is still non-neglibile.
+This indicates that variation in naming instances is more or less restricted, but is still non-negligible. 
+%to a manageable set of up to 5\ names per object.
 
@@
 \begin{itemize}
-\setlength{\itemsep}{1pt}
-\setlength{\parskip}{0pt}
+\setlength{\itemsep}{2pt}
+\setlength{\parskip}{1pt}
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
@@
 This parameter does not explain the variation in ManyNames, as we will show in the following.
+
 Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.

### 2019-05-21 papers/EMNLP2019/modeling.tex
small things here and there

@@
 %It's feature vectors were used to train state-of-the-art image captioning and visual question answering models. 
-The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}, which the authors  initialized with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vgenome (\vg).\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
+The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
+The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
 %

### 2019-05-21 papers/EMNLP2019/modeling.tex
--

--- 2019-05-21 papers/EMNLP2019/modeling.tex
@@
 Table~\ref{tab:model} shows the results, and Figure~\ref{fig:ex-high-low-agreement} the names with highest softmax scores for the images in the figure.
-\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.
+%\gbt{Proposal: in Table~\ref{tab:model} we only put the general results (not by domain), and move the by-domain part to the supp.\ material.
 All important points can be made at that level, and this way we gain space.}\sz{I would not do that}
@@
 \gbt{The following is interesting but I would move it to supp. material (see above).}
-It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}.
+It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}.
+%, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
 %For these more difficult instances (VG$\neq$MN),for multi-label is much lower to All (columns inMN) $\Rightarrow$ MN provides a more robust evaluation framework; highest drop in food domain
@@
 We also find cross-classification (\textsl{boy-batter}) and metonymy (\textsl{food-plate}). 
-It also reflects perceptual mistakes caused by unclear images (\textit{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}.
+Finally, it reflects perceptual mistakes caused by unclear images (\textsl{street-bridge}), but makes also quite a few predictions which are unreasonable or inconsistent from a human perspective (and not contained in MN), such as \textsl{bridge-sky}, \textsl{player-dirt}.
 %

### 2019-05-21 papers/EMNLP2019/conclusion.tex

--- 2019-05-19 papers/EMNLP2019/conclusion.tex
@@
-\subsection{Conclusion}
-\label{sec:conclusion}
+The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
+For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
+In future work, we want to use ManyNames to fine-tune and examine  existing models in a multi-label setting towards a behavior that is more human-like.
 
-The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
+For theoretical work, it provides name variation data with natural images and thus at the \textit{instance} level, as opposed to the category level that has been the focus up to now in theoretical work, due to the use of highly stylized drawings.
+This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as the prototypicality of the instance itself, or the effect of the visual context.
+
+%However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation. 
+The use of naturalistic images in place of stylized drawings also comes with new challenges, which interfere with the study of naming variation: the factors inherently underlying variation cannot be easily separated from those introduced by issues such as object identification.
+Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
+Future work will need to address these challenges.
 

### 2019-05-21 papers/EMNLP2019/data-collection.tex

@@
 
-We take data from \vgenome \cite[\vg henceforth]{krishna2016visualgenome}, which
+We take data from \vg~\cite{krishna2016visualgenome}, which
 % aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
@@
 all linked to WordNet synsets \cite{fellbaum1998wordnet}.
-\vg is suitable for our purpose of collecting names for a relatively large amount of instances of common objects in
-naturalistic images, as it has images of varying complexity, with close-ups as well as complex images with many objects.
-As common in Computer Vision, objects are localized as 
+\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
+%As common in Computer Vision, O
+Objects are localized as 
 %identified via
- bounding boxes (see red boxes in Figure~\ref{fig:cake}).% 
+ bounding boxes, as in Figure~\ref{fig:cake}.% 
 \footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

### 2019-05-21 papers/EMNLP2019/analysis.tex
small fixes

@@
 synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
-Implications of this will be discussed below in Section \ref{subsec:discuss}.
+Implications of this will be discussed in Section \ref{subsec:discuss}.
 
@@
 %As type counts give a rather rough indication for variation in object naming, 
-Next, we look at the following agreement measures, computed with $t=1$: % to assess agreement on the object names:
+Next, we look at the following agreement measures, computed with $t>1$: 
+%$t=1$: % to assess agreement on the object names:
 \begin{itemize}
-\setlength{\itemsep}{2pt}
-\setlength{\parskip}{1pt}
+% \setlength{\itemsep}{2pt}
+% \setlength{\parskip}{1pt}
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
@@
 The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
-It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, dog, animal, pet vs.
-dog, animal, hat).
+It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, \textsl{dog, animal, pet} vs.
+\textsl{dog, animal, hat}).
 %
 The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
-as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierachically related. 
+as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierarchically related. 
 %\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
@@
 However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-For the same reason, even fine-grained recognition models (as those trained on ILSVRC \cite{ILSVRC15}) cannot be expected to be able to simply infer the recognition of more general classes.
+For the same reason, even fine-grained recognition models (as those trained on ILSVRC) cannot be expected to be able to simply infer the recognition of more general classes.
 %since we found that many name alternatives are not hierarchically related to the VG name, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically a "truly" false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).

### 2019-05-21 papers/EMNLP2019/data-collection.tex
small fixes

@@
 % aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-contains a dense region-based labeling of $108k$~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs,
+contains a dense region-based labeling of $108$K~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs,
 all linked to WordNet synsets \cite{fellbaum1998wordnet}.
@@
 Workers could only participate in one round, to avoid workers annotating an instance more than once. 
-We obtained a total of 36 names per image (i.e.,\ objects).
+We obtained a total of 36 names per image (i.e.,\ object).
 As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).

### 2019-05-21 papers/EMNLP2019/modeling.tex
small fixes

@@
 %\paragraph{Data}
-Bottom-up was trained on a $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
+Bottom-up was trained on a set of $1,600$\ object names, manually curated by the authors. % (the authors manually removed names with poor a detection performance from the original set). 
 They did not merge semantically similar classes, such as \textsl{person} and \textsl{guy}, which is in line with the data structure of MN. %\gbt{Carina, I don't understand the following sentence}
@@
 From this set, we test on $1,254$~names (we removed the $346$\ names which are not in MN), and on $24,585$~images from MN, after filtering those whose \vg name was not in the vocabulary. 
-Note that $22,304$~of the images were also part of Bottom-up's training data; below we report separate results for data in and out of the training set. 
+Note that $22,304$~of the images were also part of Bottom-up's training data; we report separate results for data in and out of the training set. 
 %
@@
 We report the average Kullback-Leibler divergence~$\mathrm{D_{KL}}(M||S)$ \cite{kullback1951information}.
-We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline \cs{not sure whether the latter, at least in its current form, makes sense.
-TBD?
-MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}.
-\gbt{Random baseline values missing; I'm not sure if it makes sense; we could maybe compare it to the single-label distribution: Compare $S$ to $M$, like we do, and then to a distribution to vectors with 1, 0, 0, 0...
-with MN top.
-Not sure if this is too ``cheap'' -- is it a matter of course that it will be lower?
-Not if the distribution doesn't reflect the actual $M$?}
-
+We compare Bottom-up against a random baseline for the KL divergence, and against a most-frequent name baseline. 
+% \cs{not sure whether the latter, at least in its current form, makes sense. TBD? MF name baseline: I would say it's not relevant for this paper (we mainly compare different settings).}. 
+%
 \iffalse
@@
 We hypothesize two main reasons for this difference.
-First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the rightmost example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
+First, the top MN name may be more reliable because it is collected from multiple workers: For instance, in the fourth example of the first row of Figure~\ref{fig:ex-high-low-agreement}, the VG annotator chose \textsl{sandwich}, but \textsl{hotdog} is more appropriate and accordingly it was chosen by most subjects in MN (note however that three workers still chose \textsl{sandwich}).
 Second, the model can in some cases be subject to similar kinds of visual uncertainty as humans (cf.\ Section\ \ref{ssec:variation}), like mistaking a bridge for a street in the third image in the second row of Figure~\ref{fig:ex-high-low-agreement}.
@@
 
-Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In \mbox{$92-95\%$}\ of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object--even in the unseen images (\mbox{$\neg$\textit{Training}}).
+Results in the multi-label setting, $\in$MN, suggest that the current single-label evaluation dominant in the field may be too stringent: In \mbox{$92-95\%$}\ of the cases across conditions, the model's top choice corresponds to a name actually produced by human subjects for that object---even in the unseen images (\mbox{$\neg$\textit{Training}}).
 This is a very high result.
@@
 The dataset furthermore allows for comparing models on weighted naming alternatives, as illustrated by measuring the KL divergence. 
-As shown in the table, the model outperforms the random baseline on all image sets. \cs{we could also (better?) use the average responses over all instances in MN -- TBD}
-\gbt{The following is interesting but I would move it to supp. material (see above).}
-It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Tab.\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}.
+As shown in the table, the model outperforms the random baseline on all image sets (with a KL between \mbox{$6.5$ and $6.9\%$}, see caption). 
+%\cs{we could also (better?) use the average responses over all instances in MN -- TBD} 
+%\gbt{The following is interesting but I would move it to supp. material (see above).}
+It best accounts for human naming choices on the \textsc{animals\_plants} and \textsc{vehicles} domains (for which we found workers to give more general names, have the least number of types per object, and the highest agreement\ $H$, Table\ \ref{tab:agree}), and worst on \textsc{food} and \textsc{buildings}.
+%, which tend to contain occluded or unclear bounding boxes.
 %, which might \sz{?} contain occluded or unclear bounding boxes.% \cs{can we say that?}. 
@@
 Qualitative analysis suggests that Bottom-up presents many of the phenomena related to naming variation that we find in humans.
-In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Fig.\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty''
+In some cases, the model does not make clear referential mistakes made by workers (e.g.,\ \textsl{boy-helmet},\ Figure\ \ref{fig:ex-high-low-agreement}), but overall tends to mirror cases of human ``referential uncertainty''
 (\textsl{man-shirt}, \textsl{bed-sheet}).

### 2019-05-21 papers/EMNLP2019/relwork.tex
small fixes

@@
 In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
-For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.
+For instance, many labels in the ILSVRC  challenge \cite{ILSVRC15} correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.
 
@@
 \cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
-But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focusses on naming in isolation, rather than reference where naming interacts with attribute selection.
+But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
 

### 2019-05-21 papers/EMNLP2019/suppl_material.tex
small fixes

--- 2019-05-16 papers/EMNLP2019/suppl_material.tex
@@
 
-Figures~\ref{fig:instructions1} and~\ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
-After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection).
-This yielded $25,596$ images, discarding $5,497$.
-
+Figures~\ref{fig:instructions1} and \ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
+After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection):
 \begin{itemize}
@@
 \end{itemize}
-
-Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, XXX, XXX, grouped into the $7$~domains.
-\gbt{@Carina, the table doesn't fit, maybe put one domain x row?}
-
-\begin{table*}[htb]
+This yielded $25,596$ images, discarding $5,497$.
+Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, grouped into the $7$~domains, and Table~\ref{tab:overview_dataset1} shows the $7$\ domains together with the top $10$\ VG names.
+\iffalse
+\begin{table*}[t]
 	\small
+	\centering
+ \begin{tabular}{ll@{~}l@{~}l@{~}l@{~}l@{~}l@{~}}
+ 	\toprule
+ 	{} &              &                  \\
+ 	\midrule
+ 	home           &  bed (888) &  bench (714) &  table (687) &  desk (672) &  counter (516) \\
+ 	&  couch (366) &  chair (365) &  carpet (307) &  bowl (219) &  curtain (182) \\
+ 	buildings      &  house (340) &  bridge (274) &  dugout (91) &  tent (53) &  restaurant (33)\\
+ 	 &  overpass (23) 	&  grill (22) &  garage (18) &  hotel (16) &  castle (14) \\
+ 	vehicles       &  train (954) &  car (642) &  plane (485) &  airplane (479) &  motorcycle (466) \\
+ 	 &  truck (465) 	&  boat (450) &  jet (106) &  aircraft (85) &  van (76) \\
+ 	people         &  boy (853) &  man (806) &  woman (766) &  girl (650) &  lady (342)\\
+ 	 &  guy (330) &  child (230) &  batter (110) &  kid (85) &  skateboarder (80) \\
+ 	animals\_plants &  giraffe (915) &  horse (822) &  cat (754) &  dog (654) &  zebra (461) \\
+ 	&  cow (324) &  bird (295) &  sheep (216) &  bull (48) &  flower (40) \\
+ 	food           &  pizza (518) &  cake (261) &  bread (186) &  sandwich (153) &  bun (143)\\
+ 	 &  cheese (110)  	&  donut (78) &  salad (70) &  sauce (68) &  apple (33) \\
+ 	clothing       &  shirt (904) &  jacket (451) &  coat (267) &  dress (190) &  hat (77) \\
+ 	 	&  t-shirt (62) &  tie (51) &  blazer (43) &  hood (26) &  cap (20) \\
+ 	\bottomrule
+ \end{tabular}
+	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). %\textbf{double-check}
+	\label{tab:overview_dataset1transpose}}
+\end{table*}
+\fi
+\begin{table*}[htp]
+	\small
+	\centering
+	\begin{tabular}{lllll}
+			\toprule
+			Domain & \multicolumn{4}{c}{Synsets}\\
+			\midrule			
+			buildings      &  house$_1$ (364) &  bridge$_1$ (297) &  shelter$_1$ (169) &  restaurant$_1$ (58)\\
+			&  outbuilding$_1$ (31) &  hotel$_1$ (19) &  housing$_1$ (17) &  place\_of\_worship$_1$ (12)     \\
+			people         &  woman$_1$ (1768) &  man$_1$ (1167) &  male\_child$_1$ (853) &  athlete$_1$ (396) \\
+			&  child$_1$ (333) &  creator$_2$ (11) &  professional$_1$ (5)    \\
+			home           &  furnishing$_2$ (5355) &  vessel$_3$ (525) &  kitchen\_utensil$_1$ (132) &  crockery$_1$ (92) \\
+			&  cutlery$_2$ (82) &  tool$_1$ (72) &  lamp$_1$ (34)    \\
+			clothing       &  shirt$_1$ (968) &  overgarment$_1$ (786) &  dress$_1$ (199) &  headdress$_1$ (135)\\
+			 &  neckwear$_1$ (65) 		&  robe$_1$ (27) &  glove$_2$ (7) &  footwear$_1$ (5)    \\
+			vehicles       &  aircraft$_1$ (1208) &  train$_1$ (957) &  car$_1$ (727) &  motorcycle$_1$ (564) \\
+			&  truck$_1$ (559) &  boat$_1$ (499) &  ship$_1$ (38)    \\
+			food           &  dish$_2$ (812) &  baked\_goods$_1$ (770) &  foodstuff$_2$ (280) &  vegetable$_1$ (48) \\
+			&  edible\_fruit$_1$ (42) 	&  beverage$_1$ (23)   \\
+			animals\_plants &  ungulate$_1$ (2037) &  horse$_1$ (833) &  feline$_1$ (763) &  dog$_1$ (688) \\
+			&  bird$_1$ (389) &  flower$_1$ (44) &  rodent$_1$ (27) &  insect$_1$ (12) \\ 
+			&  fish$_1$ (11) &   \\
+			\bottomrule
+		\end{tabular}
+		\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). %\textbf{double-check}
+			\label{tab:overview_dataset2}}
+	\end{table*}
+%
+%
+\begin{table*}[htp]
+	\small
+	\centering
 	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
 		\toprule
-	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
+		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
 		\midrule
-	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
-	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
-	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
-	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
-	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
-	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
-	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
-	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
-	  fish$_1$ (11) &   &   &   &   &   &   \\
+		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
+		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
+		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
+		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
+		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
+		truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
+		boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
+		jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
+		aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
+		van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
 		\bottomrule
 	\end{tabular}
-	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
+	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
+		\label{tab:overview_dataset1}}
 \end{table*}
 
-\begin{figure*}[htb]
+\begin{figure*}[htp]
   \centering
@@
 
-\begin{figure*}[htb]
+\begin{figure*}[htp]
   \centering
@@
 \end{figure*}
-
-\begin{figure*}[htb]
+%
+\begin{figure*}[htp]
   \centering

### 2019-07-12 papers/EMNLP2019/reviews_author_response.txt
Draft response to reviews (+ reviews)

General Response to Reviewers:
- Thank you so much for all the comments which will help us to revise the paper and make unclear parts, in particular with respect to the difference to referring expression tasks (/datasets) and the prediction experiment more comprehensible.

- We will make the ManyNames dataset publicly available upon acceptance of the paper. 
[XXX probably better to not mention:] We are also planning to perform a verification phase to identify noisy labels.

Dataset questions:

- VisualGenome has been used especially in Language+Vision research (REFS).

Experimental questions:

The experiment shows the following: 
With our experiment in Section 5 and its results we hope to spur discussion and reconsideration of the current standard in Language & Vision research which works on modeling the human way of naming and referring to real-world objects. 
In particular:
- The evaluation against a single label may be ill-defined, since this label may not be the one a majority of humans would agree on for the given instance (=> we need many more annotations for a single instance to obtain a canonical name) 
- To assess the ability to "recognize" an object (against other models), it may not be conclusive to do this based on a single label, but instead on what labels it predicts as most probable.

Regarding the experiment specifically: 
Please recall that we only compared on the shared set of 1,254 name types which is a fraction of those in ManyNames. We hope that testing and comparing fine-tuned models on ManyNames would be useful to evaluate their ability to mimic human naming variation, and further to compare models against their ability to distinguish variants from for humans unreasonable/inconstistent mistakes.

Fine-tuning on ManyNames for the described experiment would allow for covering all name types, but disallows a direct comparison of ManyNames against VG object names in the single label setting.
We will fine-tune models on ManyNames in the future as a means to analyse the underlying (visual) factors causing naming variation, which is beyond the scope of the present paper.

> What is the loss of training? Ground-truth targets are the actual distribution of names or top-1 names?
We did not retrain or fine-tune Bottom-up, but used the publicly available model (see Anderson et al. 2018). 
For evaluation we used both, and four different ground truth targets in total, see L680-691. Thank you for pointing out that this was unclear.

Review #3:
---
Thank you very much for your review. We will revise the presentation of the tables as you suggested.

Response to Reviewer #1:
---
In contrast to the works you list, our dataset and its analysis is not on referring expressions for objects, but on object names---i.e., words (nouns or compound nouns) which you would naturally use to name an object ("entry-level category" or "canonical name"), irrespective of whether you would use the same name for other objects in the same image (e.g., an image showing several giraffes, chairs or boys). 
It is a phenomenon underlying referring expressions. To understand how the choice of the name interacts with choosing attributes (modifiers, prepositional phrases), one needs to know which name variants exist and how they are related. 
See also the last paragraph on page 791 (page 5) in the first paper you point out (Kazemzadeh et al., 2014) for the difference of referring expressions and canonical names (entry-level categories). It also that the paper adopts two standard assumptions:
- naming variants are related hierarchically, which, as we show, is not the only relation in real-world images
- there exists an entry-level (canonical name), we know which ones they are, and they are instance-invariant

Unfortunately we found existing datasets (ReferIt, those based on MSCOCO, VisualGenome descriptions) to not provide the information necessary for linguistically studying object naming (and ultimately referring expressions): 
* Regarding the ReferIt paper (Kazemzadeh et al., 2014) in particular: 
- Only 10.7% of all object instances have 2 or more referring expressions, while almost 90% has only one expression. Hence, most of the instances have one name, at most 2, i.e., provide neither name variants on the instance-level, nor is recoverable whether the chosen noun is the name one would naturally use for the instance. 
- The latter also applies to the option to use the VisualGenome object *descriptions* (as opposed to the single object *name*). 
- Among ReferIt's most frequently objects are, e.g., corner, background, head, pic, sky, foreground.

* The situation is similar with respect to the datasets based on MSCOCO (https://arxiv.org/abs/1608.00272): 
- On average, they also only have between 1.5 and 2.8 referring expressions per instance. 
- They only cover the 80 MSCOCO categories, and these are of different levels of specificity (person, dog, tie, donut, ...).

L237: Balancing was conducted to avoid bias: Larger seeds subsumed more different VG object classes than smaller seeds.

Object segmentations instead of bounding boxes would make object identification clearer in many cases, but not in those where there is a very high overlap of two objects (e.g., bed example Fig.3). 
We exploited the meta-annotation for filtering after round 0.

L206 gives the reference to the dataset: McRae et al. (2005)

Please find the answers on the experiment in Section 5 in the general answers.

===
Response to Reviewer #2:

We perfectly agree that reporting results on the training data (in addition to results on unseen images) is nonstandard. It was striking, though (and this is why we chose to include these results) that Bottom-up even obtains a higher accuracy on ManyNames than on its own training signals, as you noted in your review.

We refrain from judging over the label noise in VG, but leave this to the readers of the corresponding paper where they describe the undertaken measures to obtain and verify object name labels.

We were considering using directly the MSCOCO labels for the MSCOCO images (recall that Visual Genome was built on top of MSCOCO), but decided against it for the following reasons: MSCOCO only contains 80, well (easy to) separated categories of an arbitrary level of specificity (person, dog, tie, donut, ...).  This does result in little noise, but also in  images not as densely labeled as in VG. 
In sum, linguistically analysing object naming variations across many different domains and classes, and allowing researchers to analyse the influence of the context (objects and their domain or category) would not be possible with MSCOCO annotations.

Please see the answers to your remaining questions on the experiment in Section 5 amongst the general answers to all reviewers.

### REVIEWS ###

Review #1
What is this paper about, what contributions does it make, and what are the main strengths and weaknesses?
This paper focuses on the variation of "how to name an object in an image", called "object naming" in the VisualGeneome dataset. While it is confirmed (e.g., by work in referring expression) that people can call/name an object by various names rather than a unique name, datasets and analysis are limited. This paper newly constructs a dataset ManyNames from the VisualGenome, which has 25K object instances and app. 36 name suggestions by different annotators per instance. It enables us to analyze the variation statistically and actually provided some findings in this paper, e.g., names of animals/plants are less varied than those of people. But, public availability of the dataset is not mentioned in the paper.

Reasons to accept
New VisualGenome-based dataset of object name variation with many annotations per instance, which has 25K objects and app. 36 names for each

Statistical analysis on name variation based on seven domains

Reasons to reject
Fewer novel findings and unclear contribution while some simple analyses are performed

The dataset seems not publicly available (guessed from the current version)

The dataset construction could have an issue leasing low-quality noisy annotations for confused referential objects

The dataset can possibly be substituted by existing datasets to some extent, while the paper misses

Questions for the Author(s)
First of all, I am wondering about novelty, especially compared with existing papers on referring expression. The paper args in Section 2's "Object Naming", but it is not convincing enough. For example, this paper ignores some large (e.g. >50K objects) datasets of referring expression on real-world images. Even the VisualGenome dataset, which is used in this work, has open-vocabulary region descriptions similarly.
https://www.aclweb.org/anthology/D14-1086

https://arxiv.org/abs/1511.02283

https://arxiv.org/abs/1608.00272

Especially, the top paper did similar analyses on its dataset. The core difference is that it performed only global "entry-level (class-level)" analyses while this work does local "object-level" analyses and focuses on expressions without "attribute", right? 
Furthermore, the datasets often have more than one annotation for each object, which could indicate we can do "object-level" analyses on them. Could you refine and clarify the novelty of this paper again? And, why is the new dataset required and valuable?

As mentioned in the above, through prior work, it is neither surprising nor missed that a (contextualized) object can be called by many names. Thus, the core question of this paper, "Do Objects in Real-World Images Have a Canonical Name?", will not impactful (at least, in the NLP community). I feel that people already know "no". Similarly, I feel "the common assumption ..." at L546- sounds overclaiming. Labeling a single (exclusive) label for each object does not mean it has such an assumption of canonical names. Most studies do not mix up defined "labels" and "names".

The ManyNames dataset will not be publicly released? If not, the contribution will be limited.

L185: what does "robust" mean specifically?

L237: The description of the balancing procedure ("Because of the ... large seeds") is confusing for me. Could you rephrase it? And, did the balancing cause some bias in the dataset, which could side-effect analysis about "natural" distribution?

(L441-) 
I think referential uncertainty is just an error of dataset construction rather than a valuable nature or issue of name variation. This makes analyses and application difficult. If it used datasets with segmentation (e.g. COCO, openimages) rather than VisualGenome, this error would not happen. Otherwise, by verification, it seems preferred to remove such errors or add "ambiguous"-label to such objects. And, Fig. 1 in the appendix shows the forms of "Object occluded/not recognizable" and "Bounding box is unclear". Did the authors exploit the meta-annotation?

If the ManyNames dataset will be publicly released, including information of annotators could be useful, e.g. for analyzing speaker-level variation.

The target of the experience in Section 5 is unclear. What question do its results answer in summary?

(L635-) The experimental setting is less organized well.

Please rephrase the settings of the dataset and used labels. Currently, it's difficult to understand.

What is the loss of training? Ground-truth targets are the actual distribution of names or top-1 names?

L725-: These lines suggest it could improve "unreasonably hard top-1 evaluation" to "reasonably soft distributional evaluation". But, typical classification tasks (e.g. ImageNet) are based on their own exclusive class sets. How can we introduce ManyNames dataset for their evaluation?

L206: "a dataset widely used in Psycholinguistics" Please add a reference to this. What is the dataset?

Typos, Grammar, Style, and Presentation Improvements
The paper often says that the ManyNames has "36" names for each object. But, it removed annotations partially and thus many objects have little less than 36 names. Please reconsider to modify expressions appropriately.
L293-4: (i)'s "original name" and (ii)'s "object class" are the same one? If so, I feel it a little confusing due to the different expressions.

L161: "To the best of ..." 
One of the largest reasons why cross-classification is not often occurred/attended so far seems that the class set of typical datasets (e.g. ImageNet) are already well designed to eliminate such non-exclusive labels (to prevent the cross-classification phenomenon). They might consider the phenomenon behind the successful design of label sets. So, "received any attention" sounds a little overclaiming for me.

Review #2
What is this paper about, what contributions does it make, and what are the main strengths and weaknesses?
PAPER SUMMARY The paper addresses the question of object naming in real-world images. The authors introduce the ManyNames dataset of object names in real-world images, collected using Mechanical Turk to elicit 36 names for ~25K object instances from Visual Genome (VG).
The authors analyze their collected data, and compare their annotations to those in VG. They show that an object’s most common name in ManyNames is often not the same as its VG label, and moreover that an object’s most common ManyNames name and its VG label often share no nontrivial taxonomic relationship in the WordNet hierarchy.

The authors also extract predictions from a vision model trained on VG (Bottom-up attention), and compare them with the VG annotations and the ManyNames annotations. Interestingly, the model’s predictions show greater agreement with ManyNames even though the model was trained on VG.

STRENGTHS I agree with the authors’ central idea that real-world object naming has not been studied much to date in computer vision, and that this is an important direction for study if computer vision models are to communicate naturally with people.

The ManyNames dataset is well-designed, and can be useful for future work in this direction.

Overall the paper is well-written and easy to follow.

WEAKNESSES My main criticism of the paper is that even if I accept the paper’s central claim that single object labels for visual objects is problematic, it’s not clear what the immediate takeaways or action items should be language+vision researchers. Since models trained on VG achieve very high absolute performance on ManyWords even without finetuning (92.5% on test images in the multi-label case), I do not think that ManyWords will be very useful for benchmarking progress on this task. Furthermore the authors do not propose any new models or techniques for predicting object names in the multi-name setting. As someone who has worked in language+vision, I feel that I didn’t learn much from this paper.

Some of the more interesting results of the paper are that ManyWords object names are often different from VG, and that models trained on VG make predictions that are better-aligned with ManyWords annotations than with VG. I feel that these observations mainly reflect the high level of label noise in VG, rather than fundamental flaws with computer vision datasets more generally. For example, it would have been interesting to use the ManyWords data collection pipeline to re-annotate COCO object instances rather than VG object instances; compared to VG, COCO has very little label noise so I wonder whether the same findings would hold.

I also have some concerns about the experiments in Section 5. First, I don’t like that the All and VG=/=MN splits in Table 1 contain both VG training images and VG test images; it is very nonstandard to report the results of any machine learning model on a mix of training and testing data, so I am hesitant to draw any strong conclusions from these results. It is much more standard to evaluate machine learning models only on novel test images; to the authors’ credit the \not Training split does exactly this, but I feel that this should be the main (and perhaps only?) evaluation split. Second, the authors only report results from a model trained on VG; how does the performance change if the model is further finetuned on ManyWords?

Reasons to accept
The ManyWords dataset can be useful for studying object naming in real-world images.
Reasons to reject
It’s not clear what the concrete takeaways or next steps should be for practitioners The conclusions may be too specific to VG and less relevant to vision datasets more generally

Review #3
What is this paper about, what contributions does it make, and what are the main strengths and weaknesses?
The paper addresses the issues of discrepancy in naming objects. A new datasets was collected, with each instance (image) carefully selected from the VisualGenome dataset and labelled (named) by multiple tuckers. The name distribution represents the object better.
Overall, the authors propose a very interesting and also important issue in the field of visual&language, that previous image recognition efforts did not cover, which is innovative and inspiring.

Reasons to accept
The proposed issue is important and visionary. The dataset is well collected and may support future research.
Reasons to reject
The work is rather technically simple.
Questions for the Author(s)
The authors should polish the tables, such as using "bold" to indicate improvement over baselines/other methods, to achieve better interpretation.

### 2019-07-12 papers/EMNLP2019/reviews_author_response.txt
Two small modifications

@@
 - naming variants are related hierarchically, which, as we show, is not the only relation in real-world images
-- there exists an entry-level (canonical name), we know which ones they are, and they are instance-invariant
+- there exists an entry-level (canonical name) and we know which ones they are, they are instance-invariant
 
@@
 - They only cover the 80 MSCOCO categories, and these are of different levels of specificity (person, dog, tie, donut, ...).
+
+> Thus, the core question of this paper, "Do Objects in Real-World Images Have a Canonical Name?", will not impactful (at least, in the NLP community). I feel that people already know "no".
+Could you please provide the corresponding references which have analyzed and shown that real-world object instances do not have a preferred name most people would agree on, such that we can refer to this in our paper?
 

### 2019-09-12 papers/LREC2020/lrec2020naming.tex
initial LREC draft

--- 2018-11-13 papers/SiVL2018/sivl_2018_6pages.tex
@@
-% last updated in April 2002 by Antje Endemann
-% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016
+\documentclass[10pt, a4paper]{article}
+\usepackage{lrec}
+%\usepackage{multibib}
+%\newcites{languageresource}{Language Resources}
+\usepackage{graphicx}
+\usepackage{tabularx}
+\usepackage{soul}
+% for eps graphics
 
-\documentclass[runningheads]{llncs}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
+\usepackage{epstopdf}
+\usepackage[latin1]{inputenc}
+\usepackage{xspace}
 \usepackage{booktabs}
-\usepackage[usenames, dvipsnames]{color}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 \usepackage{hyperref}
+\usepackage{xstring}
 
-\usepackage{xspace}
+\newcommand{\secref}[1]{\StrSubstitute{\getrefnumber{#1}}{.}{ }}
 
-\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-\newcommand{\cs}[1]{\textcolor{PineGreen}{\emph{//cs: #1//}}}
-\newcommand{\la}[1]{\textcolor{cyan}{\emph{//la: #1//}}}
-
+\newcommand{\refexp}[1]{\textsl{#1}}
+\newcommand{\word}[1]{\textsl{#1}}
+\newcommand{\cat}[1]{\textsc{#1}}
 \newcommand{\vgenome}{VisualGenome\xspace}
+\newcommand{\vg}{VG\xspace}
+\newcommand{\ra}{$\rightarrow$}
 \newcommand{\referit}{ReferIt\xspace}
@@
 
-\newcommand{\refexp}[1]{\textsl{#1}}
-\newcommand{\word}[1]{\textsl{#1}}
-\newcommand{\cat}[1]{\textsc{#1}}
+\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
+\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//g: #1//}}}
+\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
 
-\newcommand{\green}[1]{\textcolor{PineGreen}{#1}}
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
-\newcommand{\yellow}[1]{\textcolor{yellow}{#1}}
+\title{Do resources in Language \& Vision favour the study of linguistic variation? \\ \vspace*{.5\baselineskip} A survey and a new collection of Object Naming data}
 
-\usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}
+\name{Author1, Author2, Author3}
+
+\address{Affiliation1, Affiliation2, Affiliation3 \\
+         Address1, Address2, Address3 \\
+         author1@xxx.yy, author2@zzz.edu, author3@hhh.com\\
+         \{author1, author5, author9\}@abc.org\\}
+
+\abstract{
+blabla \\ \newline \Keywords{keyword1, keyword2,
+keyword3} }
 
 \begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
-\pagestyle{headings}
-\mainmatter
-\def\ECCV18SubNumber{***}  % Insert your submission number here
 
-\title{Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title
-
-\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV18SubNumber}
-
-\maketitle
-
-\begin{abstract}
-Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
-However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
-In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
-Our analysis of existing resources in language \& vision reveals that none of the available datasets consistently satisfies all of the requirements for a linguistically motivated study of this phenomenon.
-We conclude with a proposal for a more consistent annotation of language \& vision data which can aid the study of object naming.
-%The abstract should summarize the contents of the paper.
-LNCS guidelinesindicate it should be at least 70 and at most 150 words.
-It should be set in 9-point font size and should be inset 1.0~cm from the right and left margins.
-\keywords{Object naming, object categorization, concepts, entry-level categories}
-\end{abstract}
-
-%@Carina TODO:
-%\begin{itemize}
-%	\item requirements: \\ 
-%	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
-%	add unconstraint object co-occurrences / unbiased as far as possible; \\
-%	rename R1? (lexical alternatives? candidate names?)
-%	\item title?
-%\end{itemize}
+\maketitleabstract
 
@@
 
-Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and (computational) linguistics.
-With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision (L\&V) tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
+Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision.
+This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
+An indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
+
+In principle, the massive data collections now available in L\&V should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
 \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
@@
 In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
-Our starting point is a particular linguistic hypothesis related to object naming---namely that the choice of a name for an object is dependent on other objects in its visual context---which has been tested recently in a classical experimental setting \cite{graf2016animal}.
-We discuss how this hypothesis could be tested based on recent data sets that pair images and object descriptions, referring expressions or captions (all containing object names) and define a set of requirements for obtaining a theoretically informed model for object naming.
-In sum, this discussion will show that specific requirements are met by particular resources, but none of the available corpora consistently 
-satisfy 
-all of the requirements.
-We believe that this is a perfect showcase illustrating the challenges for linguistically motivated research in L\&V, and we derive a proposal for obtaining more consistently designed and annotated data collections for object naming.
+We take stock of existing data sets that provide names for objects in real-world images. We contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
 
-\section{Naming Objects (in Context)}
-\label{sec:object_naming}
+\section{Background}
+
+\subsection{Object Naming as a Linguistic Phenomenon}
 
@@
 For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}\cite{clark1983common}.
-%Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene).
-%Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or location \cite{clark1983common}.
 
-So far, research in L\&V, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
- State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al.
-on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
-\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
- concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independently of the visual context.
- %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.
+\subsection{Modeling Object Naming}
 
-\section{Requirements}
-\label{sec:requirements}
+Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name
+\cite{krahmer:2012}. 
+\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
+% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
+%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
+ \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
+ Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
 
-\begin{figure}[t]
+\subsection{Relevant Resources}
+
+justify the following selection of resources....
+
+\begin{table*}
+\centering
+\begin{tabular}{lrrrrr}
+\toprule
+                         &   RefCoco &  Flickr30k &           VG &      VGmn &        MN \\
+\midrule
+                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
+                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
+     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
+ \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
+           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
+\bottomrule
+\end{tabular}
+\caption{Overview statistics for different data sets containing object naming data}
+\end{table*}
+
+\section{Survey: Object Naming in L\&V resources}
+
+\subsection{Visual Genome}
+
+\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V.
+In the following, we will focus on describing aspects immediately relevant to object naming only, while many other annotations are available as well (e.g.
+questions, paragraphs, etc.)
+
+\paragraph{Collection and annotation procedure}
+
+\vg aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+The data collection followed a complex procedure, involving many different rounds of annotation.
+The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image.
+In this stage, workers were encouraged to annotate
+In a second independent round (involving new workers), annotators were then asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
+As different region descriptions would potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
+
+\begin{figure}
 \begin{center}
-		\begin{minipage}{.35\textwidth}
-			\includegraphics[width=4.2cm]{fig/graffig.jpg}
-		\end{minipage}
-		\begin{minipage}{.2\textwidth}
-			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
-		\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
-	\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
-	\end{minipage}\vspace{-0cm}\\
-\begin{minipage}{.35\textwidth}
-	\tiny scene from  \cite{graf2016animal}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny
-	{\textsl{dalmatian, dog, heeler}}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\textsl{\tiny dog}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny \textsl{dog}
-\end{minipage}
+%\fbox{\parbox{6cm}{
+%This is a figure with a caption.}}
+\includegraphics[scale=0.4]{figures/vulture.png} 
+\begin{tabular}{lp{6cm}}
+object id & linked region descriptions\\
+\hline
+3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
+2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
+2385747 & small white beak of \textbf{bird}\\
+2681429 & a semi \textbf{long beak}\\  
+2346210 & a black and gray \textbf{vulture}\\
+ \end{tabular}
+\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
+\label{fig:bird}
 \end{center}
-		\vspace{-0.8cm}
-
-	\caption{Experimental and real-world visual scenes showing dogs from Visual Genome, RefCoco, and Flickr)}
-	\label{fig:graf_genome}
-		\vspace{-0.5cm}
-
 \end{figure}
 
-In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
- Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and real-world scenes where multiple objects occur in a natural context from \vgenome\cite{krishna2016visualgenome}, \refcoco\cite{Kazemzadeh2014}, and \flickr\cite{plummer2015flickr30kentities} (cf.
-Section~\ref{sec:resources}).
-Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus.
-Given a real-world scene with multiple objects and a target object that has to be named, we need access to:
+\paragraph{Example}
 
+Figure \ref{fig:bird} shows an example image from VisualGenome, and some of its object annotations.
+This illustrates that there is only a partial linking of objects that are mentioned across different region descriptions, i.e.\ the identity of objects cannot be established based on the annotation.
+for a given object and its bounding box, there might be different region descriptions and names associated with it.
+
+\paragraph{Discussion}
 \begin{itemize}
-		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
-		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
-		\item[(3)] the \textbf{natural name} chosen by a speaker for referring to an object
-
+\item advantages: exhaustive annotations of all/most objects in the image, variable region descriptions and possibly object names
+\item disadvantages: object linking is partial due to bottom-up annotation procedure
 \end{itemize}
 
-%For instance, if we want to find out whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{convertible, car, etc}.
-
-For instance, if we want to find out whether a specific object like the left dog in  Fig.~\ref{fig:graf_genome}, second-left image, is more often referred to with a basic-level category (e.g.,~\refexp{dog}) or a more specific one (e.g.,~\refexp{dalmatian}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{dalmatian} or, e.g.,~an \cat{irish setter}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{dalmatian, dog, etc}.
-
-%\cs{Should the following be here or at the beginning of Sect. 4?}
-%\cs{We could also call below requirements "Desiderata"}
-%In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
-%A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
-%Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
-%Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
-%For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once.
-%
-%With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors.
-%Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors.
-%We summarize this requirement by the term \textbf{R3: unconstraint}. 
-%Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
-%
-
-\section{Resources: What Do We Have?}
-\label{sec:resources}
-
-In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming.
-We focus on collections  that have been used for object recognition, referring expression generation, and phrase localization in previous work, but do not discuss other collections for e.g.
-image captioning which typically do not link mentions of objects to corresponding image regions.
-
-\subsection{ImageNet}
-
-ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories (e.g.,~the ILSVRC image classification challenge comprises 1k synsets \cite{ILSVRC15}).
-ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
-Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
-Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tiny}
-\begin{tabular}{rrl|rrl}
-\toprule
- spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
-\midrule
-           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
-           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
-           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
-           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
-           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
-           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
-           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
-           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{tiny}
-\vspace{-1cm}
-\label{tab:specnames}
-\end{table}
-\vspace{-0.6cm}
-
-%Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
-
-\subsection{\refcoco and \refcocop \cite{Yu2016}}
+\subsection{\refcoco and \refcocop}
 Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
@@
 
+\begin{table*}
+\centering
+\setlength{\tabcolsep}{2pt}
+\begin{small}
+\begin{tabular}{rrl|rrl}
+\toprule
+ spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
+\midrule
+           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
+           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
+           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
+           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
+           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
+           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
+           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
+           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
+\bottomrule
+\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
+\label{tab:specnames}
+\end{small}
+\label{tab:specnames}
+\end{table*}
+
 \subsection{Flickr30k Entities}
@@
 
-%\section{Carina}
-%input{resources}
-
-\subsection{Visual Genome}
-
-\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
-				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
-
-\end{itemize}
-
-\section{Possible Solutions}
-
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity.
-We now discuss tentative solutions.
-
-\subsection{Object detectors}
-In order to obtain a sufficiently specific level for all objects in an image, an alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
-However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
-
-%\subsection{Post-annotating COCO Captions}
-%Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
-%Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
-%%
-%In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
-%such that natural language phrases first needed to be aligned with the image regions they refer to. 
-%This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
-%% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
-%
-%
-
-\subsection{Collect naming data with controlled level of specificity}
-
-Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
-As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
-Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to be able to systematically gather object names at the sub-level.
-
-%\label{sec:future_proposal}
-%\textbf{TODO@Sina (?)}\\
-%\input{proposal}
-
-%yes, will try ...
-
 \section{Conclusion}
 
-In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
-The comparison between different data sets and available annotations for them reveals that consistent procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to the use of concepts) turns out to be difficult.
+Your submission of a finalised contribution for inclusion in the LREC
+proceedings automatically assigns the above-mentioned copyright to ELRA.
 
-\clearpage
-\bibliographystyle{splncs}
-\begin{footnotesize}
+\section{Acknowledgements}
+
+Place all acknowledgements (including those concerning research grants and
+funding) in a separate section at the end of the article.
+
+\section{Bibliographical References}
+\label{main:ref}
+
+\bibliographystyle{lrec}
 \bibliography{naming}
-\end{footnotesize}
+
+%\section{Language Resource References}
+%\label{lr:ref}
+%\bibliographystylelanguageresource{lrec}
+%\bibliographylanguageresource{lrec2020W-xample}
 

### 2019-09-12 analysis/analyse_verification_pilot.py
Add files via upload
note about todo (change paths)

@@ -66,6 +66,7 @@ def preprocess_annos(verif_df, outfname=None):
 
 
 if __name__=="__main__":
+    # paths to be adapted to new structure in github repo
     data_dir = sys.argv[1] if len(sys.argv) > 1 else "../data_phase0/"
     res_df = load_cleaned_results(os.path.join(data_dir, "all_responses_round0-3_cleaned.csv"))
     

### 2019-11-04 verification_phase0/create_amt_csv_for_verification.py
add uniqueturkerid as param to mturk

@@ -17,13 +17,15 @@ import json
 from nltk.corpus import wordnet as wn
 
 
-PHASE = "round0" # "pre-pilot" # "pilot", "phase0", "phase1", None
+PHASE = "pre-pilot" # "pilot", # "round0", "round1", None
 IMAGES_PER_HIT = 6
 
 MAX_IMAGE_PARAMS_PER_HIT = 11
 MAX_NAME_PARAMS_PER_IMAGE = 16
 
 REMOVE_SYNONYMS = False
+
+UNIQUE_TURKER_ID = "deed6e28db27a09e2acd09dcee3383a9"
 
 
 def main():
@@ -299,7 +301,7 @@ def main():
 
     # Now turn bins into rows of the AMT csv:
     header = [["image_url_{}".format(i)] + ["name_{}_{}".format(i,n) for n in range(MAX_NAME_PARAMS_PER_IMAGE)] + ["quality_control_{}".format(i)] for i in range(MAX_IMAGE_PARAMS_PER_HIT)]
-    header = [e for l in header for e in l]
+    header = ["unique_turker_id"] + [e for l in header for e in l]
     rows = []
     n_controls = []
     n_controls_pos = []
@@ -332,7 +334,7 @@ def main():
                     df.at[idx, 'quality_control_dict'][key] = "bold" + df.at[idx, 'quality_control_dict'][key][3:]
             # Obfuscate further with hex encoding
             row[i][-1] = str(df.at[idx, 'quality_control_dict']).replace("'", '"').encode('utf-8').hex()
-        row = [e for l in row for e in l]
+        row = [UNIQUE_TURKER_ID] + [e for l in row for e in l]
         rows.append(row)
         n_controls.append(controls/n_names)
         n_controls_pos.append(controls_pos/n_names)

### 2019-11-04 verification_phase0/amt_api/publish.py
allow specifying unique_turker_id in config

@@ -149,6 +149,9 @@ if __name__ == '__main__':
         logging.info("Batch {}, HIT {}".format(batch_idx, row_idx))
 
         param_list = [{'Name': key, 'Value': str(value)} for key, value in row.to_dict().items()]
+        if "unique_turker_id" in config["qualification"]:
+            param_list = [{'Name': 'unique_turker_id', 'Value': config["qualification"]["unique_turker_id"]}] + param_list
+
         logging.info(param_list)
 
         hit_data = create_new_hit(mturk, config, param_list, qualifications, config['data']['csvfile'] + '_' + str(row_idx))

### 2019-11-04 verification_phase0/create_amt_csv_for_verification.py

@@ -25,7 +25,7 @@ MAX_NAME_PARAMS_PER_IMAGE = 16
 
 REMOVE_SYNONYMS = False
 
-UNIQUE_TURKER_ID = "deed6e28db27a09e2acd09dcee3383a9"
+UNIQUE_TURKER_ID = False # "deed6e28db27a09e2acd09dcee3383a9" # or False, when generating from config
 
 
 def main():
@@ -301,7 +301,9 @@ def main():
 
     # Now turn bins into rows of the AMT csv:
     header = [["image_url_{}".format(i)] + ["name_{}_{}".format(i,n) for n in range(MAX_NAME_PARAMS_PER_IMAGE)] + ["quality_control_{}".format(i)] for i in range(MAX_IMAGE_PARAMS_PER_HIT)]
-    header = ["unique_turker_id"] + [e for l in header for e in l]
+    header = [e for l in header for e in l]
+    if UNIQUE_TURKER_ID:
+        header = ['unique_turker_id'] + header
     rows = []
     n_controls = []
     n_controls_pos = []
@@ -334,7 +336,9 @@ def main():
                     df.at[idx, 'quality_control_dict'][key] = "bold" + df.at[idx, 'quality_control_dict'][key][3:]
             # Obfuscate further with hex encoding
             row[i][-1] = str(df.at[idx, 'quality_control_dict']).replace("'", '"').encode('utf-8').hex()
-        row = [UNIQUE_TURKER_ID] + [e for l in row for e in l]
+        row = [e for l in row for e in l]
+        if UNIQUE_TURKER_ID:
+            row = [UNIQUE_TURKER_ID] + row
         rows.append(row)
         n_controls.append(controls/n_names)
         n_controls_pos.append(controls_pos/n_names)

### 2019-11-04 verification_phase0/amt_api/publish.py
bug fix in iteration over rows;  add unique turker variable if specified in config

@@ -145,13 +145,14 @@ if __name__ == '__main__':
     batch_idx = initial_row / batch_size
 
     ## Loop through all data rows from starting index, creating HITs, sleep after every batch size
-    for row_idx, row in data[initial_row:total_rows].iterrows():
+    for row_idx, row in data[initial_row:initial_row+total_rows].iterrows():
         logging.info("Batch {}, HIT {}".format(batch_idx, row_idx))
 
         param_list = [{'Name': key, 'Value': str(value)} for key, value in row.to_dict().items()]
-        if "unique_turker_id" in config["qualification"]:
-            param_list = [{'Name': 'unique_turker_id', 'Value': config["qualification"]["unique_turker_id"]}] + param_list
 
+        # Add unique turker id, or else empty string
+        unique_turker_id = config["qualification"]["unique_turker_id"] if "unique_turker_id" in config["qualification"] else ""
+        param_list = [{'Name': 'unique_turker_id', 'Value': unique_turker_id}] + param_list
         logging.info(param_list)
 
         hit_data = create_new_hit(mturk, config, param_list, qualifications, config['data']['csvfile'] + '_' + str(row_idx))

### 2019-11-04 verification_phase0/amt_api/publish.py
small bug fix in sleep

@@ -162,7 +162,7 @@ if __name__ == '__main__':
         logging.info("New hit groupId: " + hit_data['HIT']['HITGroupId'])
 
         # Sleepy time, now and then:.
-        if row_idx != total_rows-1 and ((row_idx + 1) % batch_size) == 0:
+        if row_idx != initial_row + total_rows-1 and ((row_idx + 1) % batch_size) == 0:
             outname = os.path.join(out_path, 'created_%s_uptobatch%d.json' % (moment, batch_idx))
             with open(outname, 'w') as outfile:
                 json.dump(all_resulting_HITs, outfile)

### 2019-11-04 verification_phase0/amt_api/publish.py
fix qual id key not found

@@ -15,7 +15,7 @@ def get_qualifications(config):
     if 'entry_id' in config['qualification']:
         print("create hit with data protection qualification")
 
-        qlist.append({'QualificationTypeId': config['qualification']['protectionid'],
+        qlist.append({'QualificationTypeId': config['qualification']['entry_id'],
                       'Comparator': 'GreaterThanOrEqualTo',
                       'IntegerValues': [100],
                       'ActionsGuarded': 'Accept'})

### 2019-11-04 verification_phase0/amt_api/create_qual.py
bug fix

@@ -12,7 +12,6 @@ import amt_api
 def make_qualification(mturk, question, answer, name, outpath):
 
     response = mturk.create_qualification_type(
-        Name=name,
         Keywords='data protection',
         Description='Please read our data protection policy and accept it',
         QualificationTypeStatus='Active',
@@ -29,7 +28,7 @@ def make_qualification(mturk, question, answer, name, outpath):
         
     return True
 
-def update_qualification(mturk, qualtypeID, question, answer):
+def update_qualification(mturk, qualtypeID, question, answer, name, outpath):
         
     response = mturk.update_qualification_type(
         QualificationTypeId=qualtypeID,
@@ -43,7 +42,7 @@ def update_qualification(mturk, qualtypeID, question, answer):
     print(response)
     del response['QualificationType']['CreationTime']
     
-    with open("protectionqual.json", 'w') as outfile:
+    with open(os.path.join(outpath, "{}.json".format(name)), 'w') as outfile:
         json.dump(response, outfile)
         
     return True

### 2019-11-05 verification_phase0/amt_api/create_single_hit.py
add code, config and xml for creating single-worker HIT for special payments

@@ -1,0 +1,119 @@
+import pandas as pd
+import time
+import json
+import configparser
+import logging
+import os
+import sys
+
+import amt_api
+
+
+def create_new_hit(mturk, config, hit_quals):
+    new_hit = mturk.create_hit(
+        Title=config['hit']['title'],
+        Reward=config['hit']['reward'],
+        Description=config['hit']['description'],
+        LifetimeInSeconds=eval(config['hit']['lifetime']),
+        Keywords=config['hit']['keywords'],
+        AssignmentDurationInSeconds=eval(config['hit']['assignmentduration']),
+        MaxAssignments=int(config['hit']['maxassignments']),
+        QualificationRequirements=hit_quals,
+        RequesterAnnotation=config['hit']['worker'],
+        Question=open(config['hit']['question']).read(),
+        AutoApprovalDelayInSeconds=eval(config['hit']['autoapprovaldelay']),
+    )
+
+    print("A new HIT has been created. You can preview it here:")
+    if 'sandbox' in config['endpoint']['url']:
+        print("https://workersandbox.mturk.com/mturk/preview?groupId=" + new_hit['HIT']['HITGroupId'])
+    else:
+        print("https://worker.mturk.com/mturk/preview?groupId=" + new_hit['HIT']['HITGroupId'])
+    print("HITID = " + new_hit['HIT']['HITId'] + " (Use to Get Results)")
+    del new_hit['HIT']['Question']
+    del new_hit['HIT']['CreationTime']
+    del new_hit['HIT']['Expiration']
+
+
+    return new_hit
+
+
+if __name__ == '__main__':
+
+    if len(sys.argv) < 2:
+        print("Please give a me a config file as argument")
+        sys.exit()
+    else:
+        configfile = sys.argv[1]
+
+    logging.info("config file: " + configfile)
+
+    config = configparser.ConfigParser()
+    config.read(configfile)
+
+
+    input("This will publish HITs based on {}. Press any key to continue.".format(os.path.basename(configfile)))    # TODO Compute how many HITs and money.
+    if not 'sandbox' in config['endpoint']['url']:
+        input("WARNING: This is not a drill! Will cost actual money!")
+
+    # Path structure
+    basepath = os.path.dirname(configfile)
+    out_path = os.path.join(basepath,config['data']['admindir'])
+    if not os.path.exists(out_path):
+        os.makedirs(out_path)
+
+    # Special-purpose stuff removed from config:
[…]

### 2019-11-06 verification_phase0/results_to_csv--complex.py
fox bug with synonym quality control

@@ -9,10 +9,10 @@ import os
 
 
 ANONYMIZE = False
-CONTROL_RELIABILITY_THRESHOLD = .5
+CONTROL_RELIABILITY_THRESHOLD = .7
 APPROVAL_TRESHOLD = .7  # TODO Can be higher once I have more annotations?
 BONUS_THRESHOLD = 1.0
-BLOCK_THRESHOLD = .8
+BLOCK_THRESHOLD = .7
 
 # TODO Generalize; get paths from a config argument?
 resultsdir = '1_pre-pilot/results/complex'
@@ -144,7 +144,7 @@ annotations['quality_control'] = annotations['quality_control'].apply(lambda x: 
 annotations['control_type'] = ""
 for i, row in annotations.iterrows():
     if row['name'] in row['quality_control']:
-        item = row['quality_control'][row['name']].replace("sans-", "typo-")
+        item = row['quality_control'][row['name']].replace("sans-", "typo-").replace("bold-", "syn-")
         if item == "arial":
             item = "vg_majority"
         elif item == "serif":
@@ -192,7 +192,7 @@ for i, row in annotations.iterrows():
 
     elif row['control_type'].startswith('syn'):
         synonyms = row['control_type'][4:].split(',')
-        same_rating = annotations.loc[(annotations['assignmentid'] == row['assignmentid']) & (annotations['image'] == row['image']) & (annotations['object'] == row['object']) & (annotations['rating'] == row['rating'])]['name'].unique().to_list()
+        same_rating = annotations.loc[(annotations['assignmentid'] == row['assignmentid']) & (annotations['image'] == row['image']) & (annotations['object'] == row['object']) & (annotations['rating'] == row['rating'])]['name'].unique().tolist()
         annotations.at[i, 'correct1'] = float(not any([syn not in same_rating for syn in synonyms]))
         annotations.at[i, 'correct2'] = float(not any([syn not in row['same_color'] for syn in synonyms]))
 

### 2019-11-06 papers/LREC2020/analysis.tex
LREC draft, copied together from EMNLP2019 and SiVL2018 rejections

--- 2019-05-21 papers/EMNLP2019/analysis.tex
@@
  \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds}
+
 \end{figure*}
+
+\begin{table*}
+\centering
+\begin{tabular}{lrrrrr}
+\toprule
+                         &   RefCoco &  Flickr30k &           VG &      VGmn &        MN \\
+\midrule
+                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
+                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
+     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
+ \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
+           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
+\bottomrule
+\end{tabular}
+\label{tab:compare}
+\caption{Overview statistics for different data sets containing object naming data}
+\end{table*}
+
+\subsection{Comparison with other datasets}
+\label{subsec:compare}
+
+See Table \ref{tabe:compare}
 
@@
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
-\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
+\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
 where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
@@
 %
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
-		\toprule
-		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
-		& \multicolumn{12}{c}{Image subset} \\
-		&	\multicolumn{4}{c}{All ($24,585$)} 
-		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
-		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
-		\midrule
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label}
-		&  \multicolumn{2}{c}{single-label}
-		&  \multicolumn{2}{c}{multi-label} \\
-		Domain	 &  =VG & =MN & $\in$MN  &  KL
-		&  =VG & =MN & $\in$MN  & KL
-		&  =VG & =MN & $\in$MN  & KL\\ 
-		\midrule \vspace{.6ex}
-		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\
-		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
-		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
-		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
-		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
-		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
-		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
-		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
-		\bottomrule
-		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
-		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
-	\end{tabular}
-	\caption{Baseline: The most frequent name.
-Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training).
-The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
-\end{table*}
 %

### 2019-11-06 papers/LREC2020/data-collection.tex
LREC draft, copied together from EMNLP2019 and SiVL2018 rejections

--- 2019-05-21 papers/EMNLP2019/data-collection.tex
@@
 as basis.
-We selected images from seven domains: six based on McRae et al.'s  (\citeyear{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
+We selected images from seven domains: six based on McRae et al.'s  (\cite{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
+
+\begin{table*}[htp]
+	\small
+	\centering
+	\begin{tabular}{lllll}
+			\toprule
+			Domain & \multicolumn{4}{c}{Synsets}\\
+			\midrule			
+			buildings      &  house$_1$ (364) &  bridge$_1$ (297) &  shelter$_1$ (169) &  restaurant$_1$ (58)\\
+			&  outbuilding$_1$ (31) &  hotel$_1$ (19) &  housing$_1$ (17) &  place\_of\_worship$_1$ (12)     \\
+			people         &  woman$_1$ (1768) &  man$_1$ (1167) &  male\_child$_1$ (853) &  athlete$_1$ (396) \\
+			&  child$_1$ (333) &  creator$_2$ (11) &  professional$_1$ (5)    \\
+			home           &  furnishing$_2$ (5355) &  vessel$_3$ (525) &  kitchen\_utensil$_1$ (132) &  crockery$_1$ (92) \\
+			&  cutlery$_2$ (82) &  tool$_1$ (72) &  lamp$_1$ (34)    \\
+			clothing       &  shirt$_1$ (968) &  overgarment$_1$ (786) &  dress$_1$ (199) &  headdress$_1$ (135)\\
+			 &  neckwear$_1$ (65) 		&  robe$_1$ (27) &  glove$_2$ (7) &  footwear$_1$ (5)    \\
+			vehicles       &  aircraft$_1$ (1208) &  train$_1$ (957) &  car$_1$ (727) &  motorcycle$_1$ (564) \\
+			&  truck$_1$ (559) &  boat$_1$ (499) &  ship$_1$ (38)    \\
+			food           &  dish$_2$ (812) &  baked\_goods$_1$ (770) &  foodstuff$_2$ (280) &  vegetable$_1$ (48) \\
+			&  edible\_fruit$_1$ (42) 	&  beverage$_1$ (23)   \\
+			animals\_plants &  ungulate$_1$ (2037) &  horse$_1$ (833) &  feline$_1$ (763) &  dog$_1$ (688) \\
+			&  bird$_1$ (389) &  flower$_1$ (44) &  rodent$_1$ (27) &  insect$_1$ (12) \\ 
+			&  fish$_1$ (11) &   \\
+			\bottomrule
+		\end{tabular}
+		\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). %\textbf{double-check}
+			\label{tab:overview_dataset2}}
+	\end{table*}
+%
+%
+\begin{table*}[htp]
+	\small
+	\centering
+	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
+		\toprule
+		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
+		\midrule
+		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
+		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
+		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
+		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
+		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
+		truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
+		boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
+		jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
+		aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
+		van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
+		\bottomrule
+	\end{tabular}
+	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
+		\label{tab:overview_dataset1}}
+\end{table*}
+
 %\cs{Maybe say something about the rejections, if space permits it.}

### 2019-11-06 papers/LREC2020/lrec2020naming.tex
LREC draft, copied together from EMNLP2019 and SiVL2018 rejections

@@
 % for eps graphics
+\usepackage[usenames, dvipsnames]{color}
 
@@
 \usepackage{xstring}
+\usepackage{xspace}
+\usepackage{multirow}
+\usepackage{colortbl}
 
@@
 
-\title{Do resources in Language \& Vision favour the study of linguistic variation? \\ \vspace*{.5\baselineskip} A survey and a new collection of Object Naming data}
+\definecolor{lightgray}{gray}{0.85}
+
+\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
 
@@
 \abstract{
-blabla \\ \newline \Keywords{keyword1, keyword2,
-keyword3} }
+Massive data collections for applications in language \& vision are nowadays available.
+In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
+However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
+In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images.
+Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon.
+We contribute a new dataset on top of Visual Genome that  \sz{...
+continue}
+ \\ \newline \Keywords{keyword1, keyword2, keyword3} }
 
@@
 Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision.
-This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
-An indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
+With the recent explosion of interest in this area, a number of (massive) data collections for various language \& vision (L\&V) tasks have become available: these range from image captioning data \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, and referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, to image paragraphs \sz{cite}, multi-modal summaries or visual dialogues \cite{das2017visual,vries2017guesswhat}.
+%This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
+%And indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
 
@@
 
-In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
-We take stock of existing data sets that provide names for objects in real-world images. We contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
+In this paper, we take a look at object naming, a basic phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics.
+\sz{explain picture naming here?} \sz{briefly say which linguistic questions/hypothesis could be investigated with respect o object naming} But despite the fact that object naming is relatively basic as a phenomenon, we observe that even corpora with massive annotation like VisualGenome~\cite[\vg henceforth]{krishna2016visualgenome} do not provide sufficient information for being able to study object names from a more linguistic perspective ...
+
+\begin{figure}[tbp]
+\scriptsize
+\begin{tabular}{p{4.3cm}p{2cm}}
+%VisualGenome+ManyNames & \cite{snodgrass}\\
+\centering
+\includegraphics[scale=0.15]{figures/2390077_1254219_supercat_unique.png} &
+\includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\
+ cake\ (53),  food\ (19), bread\ (8), burger\ (6), dessert\ (6), snacks\ (3), muffin\ (3),  pastry\ (3) & \hspace{.9cm} cake (83)
+\end{tabular}
+\caption{Names for a cake object in ManyNames (left) and in cite{snodgrass} (right), percentages of responses in parentheses.}
+\label{fig:cake}
+\end{figure}
+
+We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
+Thus, our images show objects in complex visual contexts,
+unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that has been previously used to train object classifiers \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
+
+As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{rosch1976basic,Ordonez:2016,graf2016animal}.
 
@@
 
-\subsection{Modeling Object Naming}
+\subsection{Visual Object Recognition}
 
+This line of research studies and models object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
+An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure\ \ref{fig:cake}.
+Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
+Recognition of instances (as opposed to categories) in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories, (e.g.\ \newcite{googlenet}).
+Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach. 
+%, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}. 
+%\cs{do you mean multi-label classifiers in single ground-truth label settings?}
+In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
+For instance, many labels in the ILSVRC  challenge \cite{ILSVRC15} correspond to very specific breeds of animals, whereas other common categories  for,\ e.g.,\ people are missing.
+
+\subsection{Hierarchical Object Categorization} 
+%goes beyond isolated object categories.
+% but looks at the principles underlying the organization of object categories. 
+...
+This line of research has emphasized the taxonomic organization of categories, e.g.\ seminal work on prototypes by \newcite{rosch1976basic},  and found that humans tend to conceptualize objects at a basic or medium level of abstraction.
+Granularity-aware object recognition methods have incorporated the taxonomic structure underlying object labels in multi-label settings \cite{deng2014large,wang2014poodle,peterson2018learning}, as an account to the criticism on the use of single-labels.
+%While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, 
+%but still aim to predict a single canonical category. % (that does have relations to other categories). 
+The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
+To the best of our knowledge, this phenomenon has not received any attention in L\&V.
+Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
+
+\subsection{Object Naming in L\&V}
+
+... work that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
 Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name
@@
  Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
+\cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
+But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
 
-\subsection{Relevant Resources}
-
-justify the following selection of resources....
-
-\begin{table*}
-\centering
-\begin{tabular}{lrrrrr}
-\toprule
-                         &   RefCoco &  Flickr30k &           VG &      VGmn &        MN \\
-\midrule
-                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
-                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
-     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
- \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
-           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
-\bottomrule
-\end{tabular}
-\caption{Overview statistics for different data sets containing object naming data}
-\end{table*}
-
-\section{Survey: Object Naming in L\&V resources}
+\section{Object Names in Existing L\&V resources}
 
@@
 
+\section{A New Dataset: Many Names}
+	\label{sec:data}
+	\input{data-collection}
+
+	\section{Analysis}
+	\label{sec:analysis}
+	\input{analysis}
+
 \section{Conclusion}

### 2019-11-06 verification_phase0/results_to_csv--complex.py
some cleanup; allow inspection of unreliable controls

@@ -14,6 +14,11 @@ APPROVAL_TRESHOLD = .7  # TODO Can be higher once I have more annotations?
 BONUS_THRESHOLD = 1.0
 BLOCK_THRESHOLD = .7
 
+INSPECT_FAILED_CONTROLS = False
+NO_REJECTION = True
+
+print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
+
 # TODO Generalize; get paths from a config argument?
 resultsdir = '1_pre-pilot/results/complex'
 
@@ -79,7 +84,6 @@ for i in range(MAX_N_IMAGES):
 print(assignments_from_mturk[:5].to_string())
 
 
-
 # Split by image
 meta = ['assignmentid', 'hitid', 'workerid']
 dfs_per_image = []
@@ -104,32 +108,32 @@ per_image['object'] = per_image['image_url'].apply(lambda x: x.split('//')[-1].s
 
 print("Per image:", len(per_image))
 
-print(per_image[:200].to_string())
 # print(per_image.groupby(['image', 'object']).agg({'workerid': lambda x: len(x.unique())}))
 
 
 
-# split by name
-dfs_per_name = []
+# Compile a dataframe with one row per annotation
+annotations = []
 for n in reversed(range(MAX_N_NAMES)):
     if 'name{}-rating'.format(n) in per_image:
         columns = ['assignmentid', 'hitid', 'workerid', 'image', 'object', 'name_{}'.format(n), 'name{}-rating'.format(n), 'name{}-type'.format(n), 'name{}-color'.format(n), 'image_url', 'quality_control']
         df = per_image[columns]
         df.columns = [col.replace('name_{}'.format(n), 'name').replace('name{}-'.format(n), '') for col in df.columns]
         df = df.loc[df['name'] != '']
-        dfs_per_name.append(df)
+        annotations.append(df)
 
-annotations = pd.concat(dfs_per_name)
+annotations = pd.concat(annotations)
+
+# Cleanup, typing, sorting
 annotations.reset_index(inplace=True)
-
 annotations = annotations[['hitid', 'assignmentid', 'workerid', 'image', 'object', 'name', 'rating', 'type', 'color', 'image_url', 'quality_control']]
-
 annotations['rating'] = annotations['rating'].astype(int)
 annotations['type'] = annotations['type'].replace({0: 'linguistic', 1: 'bounding box', 2: 'visual', 3: 'other'})
 annotations['color'] = annotations['color'].astype(int)
[…]

### 2019-11-06 verification_phase0/amt_api/approve_and_reject.py
bug fix; now include bonus amount in feedback message

@@ -21,9 +21,8 @@ MTURK_URL = 'https://mturk-requester.us-east-1.amazonaws.com'
 
 REJECT_FEEDBACK = 'HIT is rejected because too many control items were answered incorrectly.'
 APPROVE_FEEDBACK = 'Thank you for working for us!'
-BONUS_FEEDBACK = 'We have awarded a bonus of ${} because you did all control items perfectly.'
-
-BONUS_AMOUNT = '0.05'
+BONUS_AMOUNT = '0.10'
+BONUS_FEEDBACK = 'We have awarded a bonus of ${} because you did all control items perfectly.'.format(BONUS_AMOUNT)
 
 ###############################
 

### 2019-11-07 verification_phase0/create_amt_csv_for_verification.py
change to create csv for AMT with only single 'items' column

@@ -17,16 +17,11 @@ import json
 from nltk.corpus import wordnet as wn
 
 
-PHASE = "pre-pilot" # "pilot", # "round0", "round1", None
+PHASE = "pilot" # "pre-pilot" # "round0" "round1" None
 IMAGES_PER_HIT = 6
 
-MAX_IMAGE_PARAMS_PER_HIT = 11
-MAX_NAME_PARAMS_PER_IMAGE = 16
-
 REMOVE_SYNONYMS = False
-
-UNIQUE_TURKER_ID = False # "deed6e28db27a09e2acd09dcee3383a9" # or False, when generating from config
-
+MIN_CONTROL_PERCENTAGE = .1
 
 def main():
 
@@ -39,205 +34,218 @@ def main():
     manual_annotations = '../raw_data_phase0/verification_pilot/verif_annos_pilot.csv'
     many_names = "../proc_data_phase0/spellchecking/all_responses_round0-3_cleaned.csv"
 
-    df = preprocess_responses(many_names, relevant_cols)
+    auxpath = "aux/1_pre-pilot/items_with_qualitycontrol.csv"
 
-    # Collect all names in a list
-    df['names_list'] = df['spellchecked_min2'].apply(lambda x: [n for c,n in sorted([(x[n], n) for n in x], reverse=True)])
-    # And always incude vg name:
-    for i, row in df.iterrows():
-        if row['vg_obj_name'] not in row['names_list']: # add vg name to the back
-            df.at[i,'names_list'] += [row['vg_obj_name']]
-        elif row['vg_is_max']:  # bring vg name to the front
-            df.at[i, 'names_list'].insert(0, row['names_list'].pop(row['names_list'].index(row['vg_obj_name'])))
-    df['n_names'] = df['names_list'].apply(len)
+    if not os.path.exists(auxpath) or input("Create data with quality controls anew? N/y").lower().startswith('y'):
+        os.makedirs('aux/1_pre-pilot', exist_ok=True)
 
-    # Restrict to multiple names:
-    df = df.loc[df['n_names'] > 1]
+        df = preprocess_responses(many_names, relevant_cols)
 
-    print(df[:5].to_string())
+        # Collect all names in a list
+        df['names_list'] = df['spellchecked_min2'].apply(lambda x: [n for c,n in sorted([(x[n], n) for n in x], reverse=True)])
+        # And always incude vg name:
+        for i, row in df.iterrows():
[…]

### 2019-11-08 verification_phase0/results_to_csv--complex.py
enhance accept/reject criteria

@@ -9,18 +9,25 @@ import os
 
 
 ANONYMIZE = False
-CONTROL_RELIABILITY_THRESHOLD = .7
-APPROVAL_TRESHOLD = .7  # TODO Can be higher once I have more annotations?
+CONTROL_RELIABILITY_THRESHOLD = .49  # Delete control if not more than this did it correctly
+
+ASSIGNMENT_APPROVAL_TRESHOLD = .7   # will approve any assignment with score higher than this
+WORKER_APPROVAL_TRESHOLD = .8   # will approve all assignments even if a single assignment is crap
+
+WORKER_BLOCK_THRESHOLD = .8     # will block worker based on mean below this
+ASSIGNMENT_BLOCK_THRESHOLD = .7   # will block worker based on single assignment below .7
+
 BONUS_THRESHOLD = 1.0
-BLOCK_THRESHOLD = .7
 
-INSPECT_FAILED_CONTROLS = False
-NO_REJECTION = True
+INSPECT_FAILED_CONTROLS = True
+INSPECT_REJECTED_ASSIGNMENTS = True
+NO_REJECTION = False
 
-print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
+if NO_REJECTION:
+    print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
 
 # TODO Generalize; get paths from a config argument?
-resultsdir = '1_pre-pilot/results/complex'
+resultsdir = '1_pre-pilot/results'
 
 # TODO check overwrite
 
@@ -33,7 +40,9 @@ for filename in glob.glob(os.path.join(resultsdir, '*.json')):
 
             for assignment in hit['Assignments']:
                 assignment['HITId'] = hit['HITId']
+                assignment['RequesterAnnotation'] = hit['RequesterAnnotation']
                 assignment.update(hit['Params'])
+                assignment['items'] = eval(assignment['items'])
                 answers = {}
                 for key in assignment['Answers']:
                     answers.update(assignment['Answers'][key])
@@ -41,14 +50,13 @@ for filename in glob.glob(os.path.join(resultsdir, '*.json')):
                 del assignment['Answers']
                 assignments_from_mturk.append(assignment)
 
-                # TODO Get RequesterAnnotation
 
 assignments_from_mturk = pd.DataFrame(assignments_from_mturk)
 assignments_from_mturk.columns = [x.lower() for x in assignments_from_mturk.columns]
[…]

### 2019-11-08 papers/LREC2020/background.tex
divide LREC draft sections into separate tex files

--- 2019-11-06 papers/LREC2020/lrec2020naming.tex
@@
-\documentclass[10pt, a4paper]{article}
-\usepackage{lrec}
-%\usepackage{multibib}
-%\newcites{languageresource}{Language Resources}
-\usepackage{graphicx}
-\usepackage{tabularx}
-\usepackage{soul}
-% for eps graphics
-\usepackage[usenames, dvipsnames]{color}
-
-\usepackage{epstopdf}
-\usepackage[latin1]{inputenc}
-\usepackage{xspace}
-\usepackage{booktabs}
-\usepackage{hyperref}
-\usepackage{xstring}
-\usepackage{xspace}
-\usepackage{multirow}
-\usepackage{colortbl}
-
-\newcommand{\secref}[1]{\StrSubstitute{\getrefnumber{#1}}{.}{ }}
-
-\newcommand{\refexp}[1]{\textsl{#1}}
-\newcommand{\word}[1]{\textsl{#1}}
-\newcommand{\cat}[1]{\textsc{#1}}
-\newcommand{\vgenome}{VisualGenome\xspace}
-\newcommand{\vg}{VG\xspace}
-\newcommand{\ra}{$\rightarrow$}
-\newcommand{\referit}{ReferIt\xspace}
-\newcommand{\refcoco}{RefCOCO\xspace}
-\newcommand{\refcocop}{RefCOCO+\xspace}
-\newcommand{\flickr}{Flickr30k Entities\xspace}
-
-\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//g: #1//}}}
-\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
-
-\definecolor{lightgray}{gray}{0.85}
-
-\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
-
-\name{Author1, Author2, Author3}
-
-\address{Affiliation1, Affiliation2, Affiliation3 \\
-         Address1, Address2, Address3 \\
-         author1@xxx.yy, author2@zzz.edu, author3@hhh.com\\
-         \{author1, author5, author9\}@abc.org\\}
-
-\abstract{
-Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
-However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
-In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images.
-Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon.
-We contribute a new dataset on top of Visual Genome that  \sz{...
-continue}
- \\ \newline \Keywords{keyword1, keyword2, keyword3} }
-
-\begin{document}
-
-\maketitleabstract
-
-\section{Introduction}
-
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision.
-With the recent explosion of interest in this area, a number of (massive) data collections for various language \& vision (L\&V) tasks have become available: these range from image captioning data \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, and referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, to image paragraphs \sz{cite}, multi-modal summaries or visual dialogues \cite{das2017visual,vries2017guesswhat}.
-%This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
-%And indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
-
-In principle, the massive data collections now available in L\&V should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
-\cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
-In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
-However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.
-
-In this paper, we take a look at object naming, a basic phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics.
-\sz{explain picture naming here?} \sz{briefly say which linguistic questions/hypothesis could be investigated with respect o object naming} But despite the fact that object naming is relatively basic as a phenomenon, we observe that even corpora with massive annotation like VisualGenome~\cite[\vg henceforth]{krishna2016visualgenome} do not provide sufficient information for being able to study object names from a more linguistic perspective ...
-
-\begin{figure}[tbp]
-\scriptsize
-\begin{tabular}{p{4.3cm}p{2cm}}
-%VisualGenome+ManyNames & \cite{snodgrass}\\
-\centering
-\includegraphics[scale=0.15]{figures/2390077_1254219_supercat_unique.png} &
-\includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\
- cake\ (53),  food\ (19), bread\ (8), burger\ (6), dessert\ (6), snacks\ (3), muffin\ (3),  pastry\ (3) & \hspace{.9cm} cake (83)
-\end{tabular}
-\caption{Names for a cake object in ManyNames (left) and in cite{snodgrass} (right), percentages of responses in parentheses.}
-\label{fig:cake}
-\end{figure}
-
-We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
-Thus, our images show objects in complex visual contexts,
-unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that has been previously used to train object classifiers \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
-
-As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{rosch1976basic,Ordonez:2016,graf2016animal}.
-
-\section{Background}
-
 \subsection{Object Naming as a Linguistic Phenomenon}
@@
 
-\section{Object Names in Existing L\&V resources}
-
-\subsection{Visual Genome}
-
-\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V.
-In the following, we will focus on describing aspects immediately relevant to object naming only, while many other annotations are available as well (e.g.
-questions, paragraphs, etc.)
-
-\paragraph{Collection and annotation procedure}
-
-\vg aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-The data collection followed a complex procedure, involving many different rounds of annotation.
-The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image.
-In this stage, workers were encouraged to annotate
-In a second independent round (involving new workers), annotators were then asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
-As different region descriptions would potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
-
-\begin{figure}
-\begin{center}
-%\fbox{\parbox{6cm}{
-%This is a figure with a caption.}}
-\includegraphics[scale=0.4]{figures/vulture.png} 
-\begin{tabular}{lp{6cm}}
-object id & linked region descriptions\\
-\hline
-3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
-2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
-2385747 & small white beak of \textbf{bird}\\
-2681429 & a semi \textbf{long beak}\\  
-2346210 & a black and gray \textbf{vulture}\\
- \end{tabular}
-\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
-\label{fig:bird}
-\end{center}
-\end{figure}
-
-\paragraph{Example}
-
-Figure \ref{fig:bird} shows an example image from VisualGenome, and some of its object annotations.
-This illustrates that there is only a partial linking of objects that are mentioned across different region descriptions, i.e.\ the identity of objects cannot be established based on the annotation.
-for a given object and its bounding box, there might be different region descriptions and names associated with it.
-
-\paragraph{Discussion}
-\begin{itemize}
-\item advantages: exhaustive annotations of all/most objects in the image, variable region descriptions and possibly object names
-\item disadvantages: object linking is partial due to bottom-up annotation procedure
-\end{itemize}
-
-\subsection{\refcoco and \refcocop}
-Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
-%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
-%However, the COCO region-level (object) annotations are not linked to the captions.
-a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
-The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
-Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
-The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-%Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
-		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
-		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
-\end{itemize}
-
-\paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
-We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
-We estimate this distance as the minimal path length of all synsets of a word  to the root node.
-Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
-We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
-Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
-At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
-
-\begin{table*}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{small}
-\begin{tabular}{rrl|rrl}
-\toprule
- spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
-\midrule
-           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
-           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
-           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
-           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
-           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
-           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
-           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
-           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{small}
-\label{tab:specnames}
-\end{table*}
-
-\subsection{Flickr30k Entities}
-The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
-Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
-The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
-
-By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
-in contrast to \refcoco/+, the production of entity mentions did not underlie any constraints. 
-On the other hand, it is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
-		\item[(2)] \textbf{Exhaustive annotations}: are not available
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})
-
-\end{itemize}
-
-\section{A New Dataset: Many Names}
-	\label{sec:data}
-	\input{data-collection}
-
-	\section{Analysis}
-	\label{sec:analysis}
-	\input{analysis}
-
-\section{Conclusion}
-
-Your submission of a finalised contribution for inclusion in the LREC
-proceedings automatically assigns the above-mentioned copyright to ELRA.
-
-\section{Acknowledgements}
-
-Place all acknowledgements (including those concerning research grants and
-funding) in a separate section at the end of the article.
-
-\section{Bibliographical References}
-\label{main:ref}
-
-\bibliographystyle{lrec}
-\bibliography{naming}
-
-%\section{Language Resource References}
-%\label{lr:ref}
-%\bibliographystylelanguageresource{lrec}
-%\bibliographylanguageresource{lrec2020W-xample}
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "lrec2020naming"
+%%% End:

### 2019-11-08 papers/LREC2020/data-collection.tex
divide LREC draft sections into separate tex files

@@
 
+Figures~\ref{fig:instructions1} and \ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
+After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection):
+\begin{itemize}
+\item they were not marked as occluded by any subject;
+\item ``Bounding box is unclear'' was marked at most twice;
+\item at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects);
+\item the most frequent elicited name is of the same domain as the \vgenome name.
+\end{itemize}
+This yielded $25,596$ images, discarding $5,497$.
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
+  \caption{Instructions for AMT annotators for the first round.}
+  \label{fig:instructions1}
+\end{figure*}
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
+  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$. They were accompanied by the FAQ in Figure~\ref{fig:faq}}
+  \label{fig:instructions2}
+\end{figure*}
+%
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round1+_p2.png}
+  \caption{FAQ accompanying the instructions for AMT annotators for rounds~$2$ to~$4$.}
+  \label{fig:faq}
+\end{figure*}
+
 %\cs{Maybe say something about the rejections, if space permits it.}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "main"
+%%% TeX-master: "lrec2020naming"
 %%% End:

### 2019-11-08 papers/LREC2020/lrec2020naming.tex
divide LREC draft sections into separate tex files

--- 2019-09-12 papers/LREC2020/lrec2020naming.tex
@@
 \section{Introduction}
-
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision.
-This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
-An indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
-
-In principle, the massive data collections now available in L\&V should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
-\cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
-In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
-However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.
-
-In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
-We take stock of existing data sets that provide names for objects in real-world images. We contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
+\input{intro}
 
 \section{Background}
+\input{background}
 
-\subsection{Object Naming as a Linguistic Phenomenon}
+\section{Object Names in Existing L\&V resources}
+\input{survey}
 
-The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
-Since an object is simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}.
-Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
-%with respect to the chose level of specificity. 
-their choice of the level of specificity. 
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating}\cite{graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}\cite{clark1983common}.
+\section{A New Dataset: Many Names}
+\label{sec:data}
+\input{data-collection}
 
-\subsection{Modeling Object Naming}
-
-Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name
-\cite{krahmer:2012}. 
-\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
-% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
-%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
- \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
- Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
-
-\subsection{Relevant Resources}
-
-justify the following selection of resources....
-
-\begin{table*}
-\centering
-\begin{tabular}{lrrrrr}
-\toprule
-                         &   RefCoco &  Flickr30k &           VG &      VGmn &        MN \\
-\midrule
-                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
-                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
-     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
- \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
-           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
-\bottomrule
-\end{tabular}
-\caption{Overview statistics for different data sets containing object naming data}
-\end{table*}
-
-\section{Survey: Object Naming in L\&V resources}
-
-\subsection{Visual Genome}
-
-\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V.
-In the following, we will focus on describing aspects immediately relevant to object naming only, while many other annotations are available as well (e.g.
-questions, paragraphs, etc.)
-
-\paragraph{Collection and annotation procedure}
-
-\vg aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-The data collection followed a complex procedure, involving many different rounds of annotation.
-The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image.
-In this stage, workers were encouraged to annotate
-In a second independent round (involving new workers), annotators were then asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
-As different region descriptions would potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
-
-\begin{figure}
-\begin{center}
-%\fbox{\parbox{6cm}{
-%This is a figure with a caption.}}
-\includegraphics[scale=0.4]{figures/vulture.png} 
-\begin{tabular}{lp{6cm}}
-object id & linked region descriptions\\
-\hline
-3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
-2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
-2385747 & small white beak of \textbf{bird}\\
-2681429 & a semi \textbf{long beak}\\  
-2346210 & a black and gray \textbf{vulture}\\
- \end{tabular}
-\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
-\label{fig:bird}
-\end{center}
-\end{figure}
-
-\paragraph{Example}
-
-Figure \ref{fig:bird} shows an example image from VisualGenome, and some of its object annotations.
-This illustrates that there is only a partial linking of objects that are mentioned across different region descriptions, i.e.\ the identity of objects cannot be established based on the annotation.
-for a given object and its bounding box, there might be different region descriptions and names associated with it.
-
-\paragraph{Discussion}
-\begin{itemize}
-\item advantages: exhaustive annotations of all/most objects in the image, variable region descriptions and possibly object names
-\item disadvantages: object linking is partial due to bottom-up annotation procedure
-\end{itemize}
-
-\subsection{\refcoco and \refcocop}
-Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
-%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
-%However, the COCO region-level (object) annotations are not linked to the captions.
-a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
-The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
-Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
-The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-%Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
-		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
-		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
-\end{itemize}
-
-\paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
-We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
-We estimate this distance as the minimal path length of all synsets of a word  to the root node.
-Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
-We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
-Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
-At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
-
-\begin{table*}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{small}
-\begin{tabular}{rrl|rrl}
-\toprule
- spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
-\midrule
-           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
-           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
-           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
-           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
-           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
-           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
-           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
-           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{small}
-\label{tab:specnames}
-\end{table*}
-
-\subsection{Flickr30k Entities}
-The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
-Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
-The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
-
-By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
-in contrast to \refcoco/+, the production of entity mentions did not underlie any constraints. 
-On the other hand, it is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
-		\item[(2)] \textbf{Exhaustive annotations}: are not available
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})
-
-\end{itemize}
+\section{Analysis}
+\label{sec:analysis}
+\input{analysis}
 

### 2019-11-08 papers/LREC2020/survey.tex
divide LREC draft sections into separate tex files

--- 2018-11-13 papers/SiVL2018/sivl_2018_6pages.tex
@@
-% last updated in April 2002 by Antje Endemann
-% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016
+\subsection{Visual Genome}
 
-\documentclass[runningheads]{llncs}
-\usepackage{graphicx}
-\usepackage{amsmath,amssymb} % define this before the line numbering.
-\usepackage{ruler}
-\usepackage{booktabs}
-\usepackage[usenames, dvipsnames]{color}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
-\usepackage{hyperref}
+\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V.
+In the following, we will focus on describing aspects immediately relevant to object naming only, while many other annotations are available as well (e.g.
+questions, paragraphs, etc.)
 
-\usepackage{xspace}
+\paragraph{Collection and annotation procedure}
 
-\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
-\newcommand{\cs}[1]{\textcolor{PineGreen}{\emph{//cs: #1//}}}
-\newcommand{\la}[1]{\textcolor{cyan}{\emph{//la: #1//}}}
+\vg aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+The data collection followed a complex procedure, involving many different rounds of annotation.
+The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image.
+In this stage, workers were encouraged to annotate
+In a second independent round (involving new workers), annotators were then asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
+As different region descriptions would potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
 
-\newcommand{\vgenome}{VisualGenome\xspace}
-\newcommand{\referit}{ReferIt\xspace}
-\newcommand{\refcoco}{RefCOCO\xspace}
-\newcommand{\refcocop}{RefCOCO+\xspace}
-\newcommand{\flickr}{Flickr30k Entities\xspace}
-
-\newcommand{\refexp}[1]{\textsl{#1}}
-\newcommand{\word}[1]{\textsl{#1}}
-\newcommand{\cat}[1]{\textsc{#1}}
-
-\newcommand{\green}[1]{\textcolor{PineGreen}{#1}}
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
-\newcommand{\yellow}[1]{\textcolor{yellow}{#1}}
-
-\usepackage{pifont}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}
-
-\begin{document}
-% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
-% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
-% \linenumbers
-\pagestyle{headings}
-\mainmatter
-\def\ECCV18SubNumber{***}  % Insert your submission number here
-
-\title{Object naming is context-dependent - A case study on testing linguistic hypotheses on real-world image corpora} % Replace with your title
-
-\titlerunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\authorrunning{ECCV-18 submission ID \ECCV18SubNumber}
-
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCV18SubNumber}
-
-\maketitle
-
-\begin{abstract}
-Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
-However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
-In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely the context-dependence of object naming in real-world images.
-Our analysis of existing resources in language \& vision reveals that none of the available datasets consistently satisfies all of the requirements for a linguistically motivated study of this phenomenon.
-We conclude with a proposal for a more consistent annotation of language \& vision data which can aid the study of object naming.
-%The abstract should summarize the contents of the paper.
-LNCS guidelinesindicate it should be at least 70 and at most 150 words.
-It should be set in 9-point font size and should be inset 1.0~cm from the right and left margins.
-\keywords{Object naming, object categorization, concepts, entry-level categories}
-\end{abstract}
-
-%@Carina TODO:
-%\begin{itemize}
-%	\item requirements: \\ 
-%	add most specific name; (possible ways to obtain information: taxonomy, object detectors) \\
-%	add unconstraint object co-occurrences / unbiased as far as possible; \\
-%	rename R1? (lexical alternatives? candidate names?)
-%	\item title?
-%\end{itemize}
-
-\section{Introduction}
-
-Understanding and modeling the way humans converse about their environment using natural language has been a long-standing goal of research in various fields related to artificial intelligence and (computational) linguistics.
-With recent  developments in computer vision and a range of massive data collections in particular, there has been a veritable explosion of interest in language \& vision (L\&V) tasks, ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expression resolution and generation \cite{Kazemzadeh2014,mao15,Yu2016}, to multi-modal summarization or visual dialogue \cite{das2017visual,vries2017guesswhat}.
-In principle, the underlying data collections here should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
-\cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
-In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
-However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.
-
-In this paper, we take a look at object naming, a core phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. 
-Our starting point is a particular linguistic hypothesis related to object naming---namely that the choice of a name for an object is dependent on other objects in its visual context---which has been tested recently in a classical experimental setting \cite{graf2016animal}.
-We discuss how this hypothesis could be tested based on recent data sets that pair images and object descriptions, referring expressions or captions (all containing object names) and define a set of requirements for obtaining a theoretically informed model for object naming.
-In sum, this discussion will show that specific requirements are met by particular resources, but none of the available corpora consistently 
-satisfy 
-all of the requirements.
-We believe that this is a perfect showcase illustrating the challenges for linguistically motivated research in L\&V, and we derive a proposal for obtaining more consistently designed and annotated data collections for object naming.
-
-\section{Naming Objects (in Context)}
-\label{sec:object_naming}
-
-The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
-Since an object is simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}.
-Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
-%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
-%with respect to the chose level of specificity. 
-their choice of the level of specificity. 
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating}\cite{graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}\cite{clark1983common}.
-%Note that reasoning about the informativeness of a name require categorization of all the potential referents in that context (e.g., to know that \textit{dog} is ambiguous require having recognized that there are multiple dogs in the scene).
-%Other contextual factors affecting lexical choice include the \textbf{perceptual salience} of the object, such as its size or location \cite{clark1983common}.
-
-So far, research in L\&V, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
- State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al.
-on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
-\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
- concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independently of the visual context.
- %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.
-
-\section{Requirements}
-\label{sec:requirements}
-
-\begin{figure}[t]
+\begin{figure}
 \begin{center}
-		\begin{minipage}{.35\textwidth}
-			\includegraphics[width=4.2cm]{fig/graffig.jpg}
-		\end{minipage}
-		\begin{minipage}{.2\textwidth}
-			\includegraphics[height=2cm,width=2.5cm]{fig/visual_genome_dogs.png}
-		\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/flickr_1003163366_dog_boxes_crop.jpg}
-	\end{minipage}
-	\begin{minipage}{.2\textwidth}
-		\includegraphics[height=2cm,width=2.5cm]{fig/refcoco_2400_dog_boxes_crop.jpg}
-	\end{minipage}\vspace{-0cm}\\
-\begin{minipage}{.35\textwidth}
-	\tiny scene from  \cite{graf2016animal}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny
-	{\textsl{dalmatian, dog, heeler}}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\textsl{\tiny dog}
-\end{minipage}
-\begin{minipage}{.2\textwidth}
-	\tiny \textsl{dog}
-\end{minipage}
+%\fbox{\parbox{6cm}{
+%This is a figure with a caption.}}
+\includegraphics[scale=0.4]{figures/vulture.png} 
+\begin{tabular}{lp{6cm}}
+object id & linked region descriptions\\
+\hline
+3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
+2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
+2385747 & small white beak of \textbf{bird}\\
+2681429 & a semi \textbf{long beak}\\  
+2346210 & a black and gray \textbf{vulture}\\
+ \end{tabular}
+\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
+\label{fig:bird}
 \end{center}
-		\vspace{-0.8cm}
-
-	\caption{Experimental and real-world visual scenes showing dogs from Visual Genome, RefCoco, and Flickr)}
-	\label{fig:graf_genome}
-		\vspace{-0.5cm}
-
 \end{figure}
 
-In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
- Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and real-world scenes where multiple objects occur in a natural context from \vgenome\cite{krishna2016visualgenome}, \refcoco\cite{Kazemzadeh2014}, and \flickr\cite{plummer2015flickr30kentities} (cf.
-Section~\ref{sec:resources}).
-Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus.
-Given a real-world scene with multiple objects and a target object that has to be named, we need access to:
+\paragraph{Example}
 
+Figure \ref{fig:bird} shows an example image from VisualGenome, and some of its object annotations.
+This illustrates that there is only a partial linking of objects that are mentioned across different region descriptions, i.e.\ the identity of objects cannot be established based on the annotation.
+for a given object and its bounding box, there might be different region descriptions and names associated with it.
+
+\paragraph{Discussion}
 \begin{itemize}
-		\item[(1)] the \textbf{specific category} of the object that the speaker referred to 
-		\item[(2)] \textbf{exhaustive annotations} for all the other objects in the scene (i.e. distractors)
-		\item[(3)] the \textbf{natural name} chosen by a speaker for referring to an object
-
+\item advantages: exhaustive annotations of all/most objects in the image, variable region descriptions and possibly object names
+\item disadvantages: object linking is partial due to bottom-up annotation procedure
 \end{itemize}
 
-%For instance, if we want to find out whether a specific object like \cat{convertible} is more often referred to with a basic-level category (e.g.,~\refexp{car}) or a more specific one (e.g.,~\refexp{convertible, limousine}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{convertible} or a \cat{limousine}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{convertible, car, etc}.
-
-For instance, if we want to find out whether a specific object like the left dog in  Fig.~\ref{fig:graf_genome}, second-left image, is more often referred to with a basic-level category (e.g.,~\refexp{dog}) or a more specific one (e.g.,~\refexp{dalmatian}), all three requirements need to be fulfilled: we need to know whether the object is a \cat{dalmatian} or, e.g.,~an \cat{irish setter}, and likewise for its distractors, and we need to know whether a speaker called the object \refexp{dalmatian, dog, etc}.
-
-%\cs{Should the following be here or at the beginning of Sect. 4?}
-%\cs{We could also call below requirements "Desiderata"}
-%In practical terms, the prerequisite for Requirements~(2) and~(3) is, given an image, the information on \textbf{R1: the most specific category} of \textbf{each object} which is depicted in the image.
-%A taxonomy, such as WordNet \cite{fellbaum1998wordnet}, could then be queried with these categories to retrieve their individual lexical candidates arranged by their taxonomic relations. \\
-%Furthermore, the information on the \textbf{R2: entry-level category} of an object could be used as a pivot to taxonomically group its lexical candidates.  
-%Under the assumption that the entry-level, as the preferred level of specificity, is produced most often for an individual concept, may be inferrable from the data itself through maximum likelihood estimation.
-%For example, based on frequency estimates, the entry-level for the object on the left is \refexp{dalmatian} (Figure~\ref{fig:ex_visualgenome}), whereas the object on the right is named mostly \refexp{dog}, but \refexp{heeler} only once.
-%
-%With respect to linguistic data-driven experiments, the range of linguistic phenomena under study (see, e.g.,~Section~\ref{sec:object_naming} for phenomena in object naming) need to be observable in the data in order to study the interaction of their underlying factors.
-%Hence, a further practical requirement is that the data, first, captures ideally all possible combinations of the factor values across all factors\footnote{For example, data that contains only images where target and distractor objects do not share any lexical candidates would not be appropriate}, and second, that it has been naturally produced in that speakers were not constraint in their choice of a name by external factors.
-%We summarize this requirement by the term \textbf{R3: unconstraint}. 
-%Note that this requirement XXX \cs{@Sina ref to bias and paper you mentioned?}.
-%
-
-\section{Resources: What Do We Have?}
-\label{sec:resources}
-
-In the following, we will discuss datasets that provide descriptions or referring expressions for objects in real-world images and could, in principle,  be suitable for studying object naming.
-We focus on collections  that have been used for object recognition, referring expression generation, and phrase localization in previous work, but do not discuss other collections for e.g.
-image captioning which typically do not link mentions of objects to corresponding image regions.
-
-\subsection{ImageNet}
-
-ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories (e.g.,~the ILSVRC image classification challenge comprises 1k synsets \cite{ILSVRC15}).
-ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
-Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
-Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
-However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) and no (or very few) distractor objects.
-
-\begin{table}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tiny}
-\begin{tabular}{rrl|rrl}
-\toprule
- spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
-\midrule
-           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
-           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
-           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
-           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
-           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
-           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
-           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
-           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{tiny}
-\vspace{-1cm}
-\label{tab:specnames}
-\end{table}
-\vspace{-0.6cm}
-
-%Multiple datasets for vision \& language tasks have been built on top of COCO, such as the referring expressions datasets \refcoco and \refcocop which we will discuss below, and \textsl{COCO Captions} \cite{chen2015cococaptions}.
-
-\subsection{\refcoco and \refcocop \cite{Yu2016}}
+\subsection{\refcoco and \refcocop}
 Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
@@
 
-%\section{Carina}
-%input{resources}
-
-\subsection{Visual Genome}
-
-\vgenome \cite{krishna2016visualgenome} aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-It contains a dense region-based labeling of $108k$~images with textual expression of the attributes and references of objects, their relationships as well as question answer pairs, all linked to WordNet synsets \cite[see below]{fellbaum1998wordnet}.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, as object categories and names are not consistently annotated (and even conflated)
-				\item[(2)] \textbf{Exhaustive annotations}: are available, which is a huge advantage of this data sets
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in referring expressions)
-
-\end{itemize}
-
-\section{Possible Solutions}
-
-As discussed in Section \ref{sec:resources}, none of the corpora that contain natural naming data for objects in context provide consistent and dense annotations of object categories at a sufficient level of specificity.
-We now discuss tentative solutions.
-
-\subsection{Object detectors}
-In order to obtain a sufficiently specific level for all objects in an image, an alternative would be to apply object detectors or image classifiers trained to predict the most specific category of the full inventory of objects which the dataset covers.
-However, pre-trained models only exist for a subset of the datasets' objects  (For example, we could find $6,139$~synsets for the unique object names of Flick30k, of which $238$~synsets (ss) are in the synset set of the ILSVRC image classification challenge ($1$K in total), and $338$ and $95$~ss are super-level and sub-level categories of ILSVRC, respectively.)
-For the training of a model using, e.g., ImageNet \cite{imagenet_cvpr09}, on the other hand, the  set of most-specific categories covered by the data needs to be provided or collected from humans.
-
-%\subsection{Post-annotating COCO Captions}
-%Regarding \refcoco/+, additional REs could be collected from the COCO Captions dataset. %, which provides 5 natural language descriptions for each image in MS COCO. 
-%Since annotators could naturally refer to depicted objects in their descriptions (i.e.,~choose the entry-level as the most preferred reference whenever possible), we may infer the entry-level of the objects from them through maximum likelihood estimation.
-%%
-%In contrast to \flickr, though, the data does not contain region-phrase associations,  % (i.e.,~object mentions are not linked to the corresponding image regions). 
-%such that natural language phrases first needed to be aligned with the image regions they refer to. 
-%This task of \textit{language grounding}, which has been an active research topic in vision \& language (e.g.,~\cite{kong2014what,karpathy2015deep,rohrbach2016grounding}), is beyond the focus of our object naming study.
-%% We could also examine the bias shift of speakers (e.g.,~sparrow vs. bird may depend on the person)
-%
-%
-
-\subsection{Collect naming data with controlled level of specificity}
-
-Given that the quality of exhaustive automatic object detection for arbitrary objects in our naming data is hard to estimate, further human annotation on some of the existing data sets seems to be required.
-As annotation of arbitrary objects according to the ImageNet hierarchy is probably challenging for naive subjects, we plan to collect controlled, specific object names from humans as an approximate of specific categories.
-Thus, by prompting annotators to label an object with the most specific name they can think of, we hope to be able to systematically gather object names at the sub-level.
-
-%\label{sec:future_proposal}
-%\textbf{TODO@Sina (?)}\\
-%\input{proposal}
-
-%yes, will try ...
-
-\section{Conclusion}
-
-In this paper we have discussed some existing resources in vision \& language from the perspective of linguistically motivated studies on object naming.  
-The comparison between different data sets and available annotations for them reveals that consistent procedures for annotating object categories and eliciting object names are lacking to an extent that testing of  basic linguistic hypotheses (related to the use of concepts) turns out to be difficult.
-
-\clearpage
-\bibliographystyle{splncs}
-\begin{footnotesize}
-\bibliography{naming}
-\end{footnotesize}
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "lrec2020naming"
+%%% End:

### 2019-11-08 verification_phase0/amt_api/publish.py
return empty qlist if sandbox

@@ -12,6 +12,10 @@ import amt_api
 def get_qualifications(config):
     qlist = []
 
+    if 'sandbox' in config['endpoint']['url']:
+        print("this is sandbox mode, no qualifications needed")
+        return qlist
+
     if 'entry_id' in config['qualification']:
         print("create hit with data protection qualification")
 
@@ -22,14 +26,9 @@ def get_qualifications(config):
 
         # do not allow turkers who have a qualification that blocks them from participating
         if 'block_id' in config['qualification']:
-            print("WARNING: Creating block_id qualification has not been tested yet. Attempting now!")
             qlist.append({'QualificationTypeId': config['qualification']['block_id'],
                 'Comparator': 'DoesNotExist',
                 'ActionsGuarded':'DiscoverPreviewAndAccept'})
-
-    if 'sandbox' in config['endpoint']['url']:
-        print("this is sandbox mode, no qualifications needed")
-        return qlist
 
     # qlist.extend([
     #     {'QualificationTypeId': '00000000000000000040',

### 2019-11-08 verification_phase0/amt_api/results.py
handle requesterannotation

@@ -33,6 +33,7 @@ def get_results(mturk, path_published, path_results, ass_statuses):
 
             if len(assignments) > 0:
                 hit_out_dict = {'HITId': item['HIT']['HITId'],
+                                'RequesterAnnotation': item['HIT']['RequesterAnnotation'],
                                 'Assignments': [],
                                 'Params': {d['Name']: d['Value'] for d in item['HIT']['params']}}
 

### 2019-11-08 papers/LREC2020/intro.tex

Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision. With the recent explosion of interest in this area, a number of (massive) data collections for various language \& vision (L\&V) tasks have become available: these range from image captioning data \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, and referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, to image paragraphs \sz{cite}, multi-modal summaries or visual dialogues \cite{das2017visual,vries2017guesswhat}.
%This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities. 
%And indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.

In principle, the massive data collections now available in L\&V should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf. \cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.  
In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.

In this paper, we take a look at object naming, a basic phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics. \sz{explain picture naming here?} \sz{briefly say which linguistic questions/hypothesis could be investigated with respect o object naming} But despite the fact that object naming is relatively basic as a phenomenon, we observe that even corpora with massive annotation like VisualGenome~\cite[\vg henceforth]{krishna2016visualgenome} do not provide sufficient information for being able to study object names from a more linguistic perspective ...

\begin{figure}[tbp]
\scriptsize
\begin{tabular}{p{4.3cm}p{2cm}}
%VisualGenome+ManyNames & \cite{snodgrass}\\
\centering
\includegraphics[scale=0.15]{figures/2390077_1254219_supercat_unique.png} &
\includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\
 cake\ (53),  food\ (19), bread\ (8), burger\ (6), dessert\ (6), snacks\ (3), muffin\ (3),  pastry\ (3) & \hspace{.9cm} cake (83)
\end{tabular}
\caption{Names for a cake object in ManyNames (left) and in cite{snodgrass} (right), percentages of responses in parentheses.}
\label{fig:cake}
\end{figure}

We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
Thus, our images show objects in complex visual contexts,
unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that has been previously used to train object classifiers \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).

As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{rosch1976basic,Ordonez:2016,graf2016animal}.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "lrec2020naming"
%%% End:

### 2019-11-08 papers/LREC2020/survey.tex

@@
+We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.
+Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{+++}).
+As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to examine naming variation.
+This motivates our data collection, in which we collect 36 names per object.
+Still, because these datasets can be useful to examine other aspects of object naming, and we summarize their characteristics below.
+
+\begin{table*}
+\centering
+\begin{tabular}{lrrrrr}
+\toprule
+  &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
+\midrule
+                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
+                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
+     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
+ \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
+           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
+\bottomrule
+\end{tabular}
+\label{tab:compare}
+\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column? Is it necessary?}}
+\end{table*}
+
+\subsection{\refcoco and \refcocop}
+
+Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
+%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
+%However, the COCO region-level (object) annotations are not linked to the captions.
+a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
+The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
+Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
+The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
+REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
+\gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
+How did you compute these numbers, are they for names, or whole REs?}
+% Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
+
+We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors.
+Multiple annotations (2.84 on average) allow for some minimal analysis of naming variation in this setup. 
+However, note that not all objects are annotated with REs and corresponding categories, so it may be difficult to analyze the data with automatic processing.
+Names elicited in \refcoco should be natural, but it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
+Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
+To sum up, we would recommend \RefCOCO to study effect of distractors on object naming in a restricted set of categories.
+
+% \begin{itemize}
+% \item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
+% \item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
+% \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
+% \end{itemize}
+
+% gbt: I'm commenting out this analysis because it is not really relevant for assessing how useful RefCOCO is to study object naming: what it shows is that names appear at many different levels of a taxonomy, although they tend to be concentrated in middle levels (especially 6-7; in agreement with basic level hypothesis).
+To me, this is a data result, not a dataset result (clear?).
+% \paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
+% We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
+% We estimate this distance as the minimal path length of all synsets of a word  to the root node.
+% Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
+% We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
+% Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
+% At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
+
+% \begin{table*}
+% \centering
+% \setlength{\tabcolsep}{2pt}
+% \begin{small}
+% \begin{tabular}{rrl|rrl}
+% \toprule
+%  spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
+% \midrule
+%            2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
+%            3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
+%            4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
+%            5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
+%            6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
+%            7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
+%            8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
+%            9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
+% \bottomrule
+% \end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
+% \label{tab:specnames}
+% \end{small}
+% \label{tab:specnames}
+% \end{table*}
+
+\subsection{\flickr}
+
+The \flickr dataset \cite{plummer2015flickr30kentities}
+% \footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}
+augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level descriptions extracted from the captions.
+Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to.
+% The dataset was designed to advance image description generation and phrase localization in particular \cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}.
+
+This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were no subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size).
+\gbt{Any idea what kind of categories are covered in \flickr?}
+Moreover, although no exhaustive annotations of the image is available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
+The number of annotations per object, 2.3 annotations, is comparable to \refcoco.
+
+% \begin{itemize}
+% \item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
+% \item[(2)] \textbf{Exhaustive annotations}: are not available
+% \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})
+% \end{itemize}
+
 \subsection{Visual Genome}
-
-\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V.
-In the following, we will focus on describing aspects immediately relevant to object naming only, while many other annotations are available as well (e.g.
-questions, paragraphs, etc.)
-
-\paragraph{Collection and annotation procedure}
-
-\vg aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-The data collection followed a complex procedure, involving many different rounds of annotation.
-The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image.
-In this stage, workers were encouraged to annotate
-In a second independent round (involving new workers), annotators were then asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
-As different region descriptions would potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
 
@@
 
-\paragraph{Example}
+\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V; below, we focus on aspects immediately relevant to object naming.
+%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
+%\paragraph{Collection and annotation procedure}
+\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+The data collection followed a complex procedure, involving many different rounds of annotation.
+The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).
 
-Figure \ref{fig:bird} shows an example image from VisualGenome, and some of its object annotations.
-This illustrates that there is only a partial linking of objects that are mentioned across different region descriptions, i.e.\ the identity of objects cannot be established based on the annotation.
-for a given object and its bounding box, there might be different region descriptions and names associated with it.
+In a second, independent round (involving new workers), annotators were asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
+As different region descriptions can potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
 
-\paragraph{Discussion}
-\begin{itemize}
-\item advantages: exhaustive annotations of all/most objects in the image, variable region descriptions and possibly object names
-\item disadvantages: object linking is partial due to bottom-up annotation procedure
-\end{itemize}
+\gbt{@Sina, pls check that I got this right:}
+One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
+Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+This should make it easier to identify factors intervening in naming choices.
+However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
+Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
+This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the annotations.
 
-\subsection{\refcoco and \refcocop}
-Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
-%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
-%However, the COCO region-level (object) annotations are not linked to the captions.
-a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
-The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
-Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
-The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-%Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
+\subsection{Discussion}
 
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: not available, the $80$~COCO categories tend to be entry-level categories and are not linked to the ImageNet taxonomy (e.g.,~\cat{bird, person, car, bus})
-		\item[(2)] \textbf{Exhaustive annotations}: not available, as not all objects were annotated with REs and corresponding categories
-		   \item[(3)] \textbf{Natural names}: available, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
-\end{itemize}
-
-\paragraph{Analysis} We parse REs in \refcoco with the Stanford Dependency Parser and extract the nominal heads. We map these names to their most frequent sense/synset in WordNet.
-We hypothesize that the distance of a name's synset to the root node (\cat{entity}) relates to its specificity.
-We estimate this distance as the minimal path length of all synsets of a word  to the root node.
-Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
-We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
-Unfortunately, the levels of specificity predicted by WordNet do not seem to reflect linguistic intuitions, e.g.\ \refexp{elephant} is predicted to be more specific than \refexp{panda}.
-At the same time, this overview clearly suggests that object names in \refcoco do not only comprise entry-level categories, but also very general (\refexp{thing}) and very specific names (\refexp{ox}).
-
-\begin{table*}
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{small}
-\begin{tabular}{rrl|rrl}
-\toprule
- spec. &  rel.freq. &                          top 5 names & spec. &  rel.freq. &                          top 5 names \\
-\midrule
-           2 &   $<$ 0.01 &       \tiny                  thing,things & 10 &   0.05 &   elephant,couch,truck,vase,suitcase \\
-           3 &   $<$ 0.01 &    object,group,set,substance,objects & 11 &   $<$ 0.01 &    motorcycle,clock,mom,dad,scissors \\
-           4 &   0.14 &           man,person,piece,head,part & 12 &   $<$ 0.01 &  oven,airplane,suv,taxi,refrigerator  \\
-           5 &   0.10 &       player,glass,baby,front,corner & 13 &   $<$ 0.01 &    laptop,fridge,canoe,orioles,pigeon \\
-           6 &   0.21 &              woman,girl,kid,boy,bowl & 14 &   $<$ 0.01 &   panda,freezer,penguin,rooster,rhino \\
-           7 &   0.25 &            guy,right,chair,lady,bear & 15 &   0.03 &    zebra,giraffe,zebras,giraffes,deer \\
-           8 &   0.11 &           horse,bus,cow,pizza,batter & 16 &  $ <$ 0.01 &       bison,mooses,orang,elks,sambar \\
-           9 &   0.09 &         shirt,car,bike,donut,catcher & 17 &   $<$ 0.01 &           ox,cattle,gnu,mustang,orca \\          
-\bottomrule
-\end{tabular}\caption{Levels of specificity for naming choices in RefCOCO: for each level (distance between name and WordNet root), relative frequency and 5 most frequent names are shown}
-\label{tab:specnames}
-\end{small}
-\label{tab:specnames}
-\end{table*}
-
-\subsection{Flickr30k Entities}
-The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations.
-Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
-The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
-
-By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
-in contrast to \refcoco/+, the production of entity mentions did not underlie any constraints. 
-On the other hand, it is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.
-
-\begin{itemize}
-     		\item[(1)] \textbf{Specific categories}: are not available, object categories tend to be even less specific than those of COCO (e.g.,~\cat{people, animals, bodyparts, clothing}), or are abstract (\cat{other, scene})
-		\item[(2)] \textbf{Exhaustive annotations}: are not available
-		   \item[(3)] \textbf{Natural names}: are available, though object names might not be fully discriminative (as in REs; e.g.,~both animals in the right-most image in Fig.~\ref{fig:graf_genome} are named \refexp{dog})
-
-\end{itemize}
+\gbt{Do we need a discussion section wrapping up what we've said in this survey section and motivating MN?}
 

### 2019-11-09 papers/EMNLP2019/reviews_author_response.txt
revised data collection

--- 2019-07-12 papers/EMNLP2019/reviews_author_response.txt
@@
+Response to Review #1:
+
+The main contribution of our dataset is that it systematically collects names for objects; we have 25K objects with 33-36 annotations.
+There is, to our knowledge, no other dataset with similar characteristics:
+
+- Previous datasets, including those in the references provided in the review, contain one or few expressions per object (e.g., only 10.7% of ReferIt provides 2 or more expressions; the datasets based on COCO have between *** and *** expressions on average).
+
+- Previous datasets provide either referring expressions or object descriptions; we collect object names.
+This is a phenomenon underlying referring expressions, so to speak; to properly understand how the choice of the object name interacts with the choice of attributes (modifiers, prepositional phrases), one needs to know which name variants exist and how they are related.
+This is why we study object naming as a separate phenomenon.
+
+***THIS PARAGRAPH IS A CANDIDATE TO BE LEFT OUT IF WE ARE SHORT ON SPACE*** The first paper you point out (Kazemzadeh et al., 2014, page 791) distinguishes also between difference of referring expressions and canonical names (entry-level categories); however, it adopts two assumptions standard in Psycholinguistics that we show not to hold (that naming variants are related hierarchically, and that there is a largely instance-invariant entry-level or canonical name).
+VisualGenome contains region descriptions (often containing modifiers) instead of names, and only one or very few per region.
+
+> Thus, the core question of this paper, "Do Objects in Real-World Images Have a Canonical Name?", will not impactful (at least, in the NLP community). I feel that people already know "no".
+
+First, the answer according to our data is nuanced (on average, the most frequent name covers 75% of the responses, which is quite a large agreement; we also find quite a bit of variation); second, to the best of our knowledge there is no study that empirically addresses this question on a large scale; third, we provide evidence that the main source of naming variation studied so far, variation along a taxonomical hierarchy, accounts for very little of the data.
+
+L237: Balancing was conducted precisely to avoid bias: Larger seeds subsumed more different VG object classes than smaller seeds.
+Any dataset of course has some bias; we chose categories that are fairly common in visual data.
+
+We exploited the meta-annotation for filtering after round 0: we excluded around 6K objects that had no clear bounding boxes or were occluded.
+After that, for the rest of the annotations of the remaining 25K objects, we did not gather meta-annotations.
+
+L206 gives the reference to the dataset: McRae et al. (2005)
+
+Please find the answers on the experiment in Section 5 in the general answers to reviews below.
+
+Response to Review #2:
+
+We chose VG over COCO because we wanted to cover a wider range of categories.
+It is a well-accepted dataset in the community and in our own analyses of the VG data in our sample we did not identify much noise.
+
+We were considering using directly the MSCOCO labels for the MSCOCO images (recall that Visual Genome was built on top of MSCOCO), but decided against it for the following reasons: MSCOCO only contains 80, easy to separated categories of an arbitrary level of specificity (person, dog, tie, donut, ...).
+This does result in little noise, but also in images not as densely labeled as in VG.
+In sum, linguistically analysing object naming variations across many different domains and classes, and allowing researchers to analyse the influence of the context (objects and their domain or category) would not be possible with MSCOCO annotations.
+
+Indeed, reporting results on the training data (in addition to results on unseen images) is nonstandard.
+We included these results because we obtain a higher accuracy on ManyNames than on the original training data, as noted in your review, which is a striking result.
+We will rephrase to clarify, and reorganize the table such that it is clear that the results on the test partition are the main results.
+
+Please see the answers to your remaining questions on the experiment in Section 5 amongst the general answers to all reviewers.
+
+Response to Review #3:
+
+Thank you, we will revise the presentation of the tables as you suggested.
+
 General Response to Reviewers:
-- Thank you so much for all the comments which will help us to revise the paper and make unclear parts, in particular with respect to the difference to referring expression tasks (/datasets) and the prediction experiment more comprehensible.
+
+- Thank you for the constructive feedback.
 
 - We will make the ManyNames dataset publicly available upon acceptance of the paper.
-[XXX probably better to not mention:] We are also planning to perform a verification phase to identify noisy labels.
+
+Response to Chairs
 
@@
 Regarding the experiment specifically: 
-Please recall that we only compared on the shared set of 1,254 name types which is a fraction of those in ManyNames.
+Please recall that we only compared on the shared set of 1,254 name types, which is a fraction of those in ManyNames.
 We hope that testing and comparing fine-tuned models on ManyNames would be useful to evaluate their ability to mimic human naming variation, and further to compare models against their ability to distinguish variants from for humans unreasonable/inconstistent mistakes.
@@
 For evaluation we used both, and four different ground truth targets in total, see L680-691. Thank you for pointing out that this was unclear.
-
-Review #3:
----
-Thank you very much for your review. We will revise the presentation of the tables as you suggested.
-
-Response to Reviewer #1:
----
-In contrast to the works you list, our dataset and its analysis is not on referring expressions for objects, but on object names---i.e., words (nouns or compound nouns) which you would naturally use to name an object ("entry-level category" or "canonical name"), irrespective of whether you would use the same name for other objects in the same image (e.g., an image showing several giraffes, chairs or boys).
-It is a phenomenon underlying referring expressions.
-To understand how the choice of the name interacts with choosing attributes (modifiers, prepositional phrases), one needs to know which name variants exist and how they are related.
-See also the last paragraph on page 791 (page 5) in the first paper you point out (Kazemzadeh et al., 2014) for the difference of referring expressions and canonical names (entry-level categories).
-It also that the paper adopts two standard assumptions:
-- naming variants are related hierarchically, which, as we show, is not the only relation in real-world images
-- there exists an entry-level (canonical name), we know which ones they are, and they are instance-invariant
-
-Unfortunately we found existing datasets (ReferIt, those based on MSCOCO, VisualGenome descriptions) to not provide the information necessary for linguistically studying object naming (and ultimately referring expressions):
-* Regarding the ReferIt paper (Kazemzadeh et al., 2014) in particular: 
-- Only 10.7% of all object instances have 2 or more referring expressions, while almost 90% has only one expression.
-Hence, most of the instances have one name, at most 2, i.e., provide neither name variants on the instance-level, nor is recoverable whether the chosen noun is the name one would naturally use for the instance.
-- The latter also applies to the option to use the VisualGenome object *descriptions* (as opposed to the single object *name*). 
-- Among ReferIt's most frequently objects are, e.g., corner, background, head, pic, sky, foreground.
-
-* The situation is similar with respect to the datasets based on MSCOCO (https://arxiv.org/abs/1608.00272): 
-- On average, they also only have between 1.5 and 2.8 referring expressions per instance. 
-- They only cover the 80 MSCOCO categories, and these are of different levels of specificity (person, dog, tie, donut, ...).
-
-L237: Balancing was conducted to avoid bias: Larger seeds subsumed more different VG object classes than smaller seeds.
-
-Object segmentations instead of bounding boxes would make object identification clearer in many cases, but not in those where there is a very high overlap of two objects (e.g., bed example Fig.3). 
-We exploited the meta-annotation for filtering after round 0.
-
-L206 gives the reference to the dataset: McRae et al. (2005)
-
-Please find the answers on the experiment in Section 5 in the general answers.
-
-===
-Response to Reviewer #2:
-
-We perfectly agree that reporting results on the training data (in addition to results on unseen images) is nonstandard.
-It was striking, though (and this is why we chose to include these results) that Bottom-up even obtains a higher accuracy on ManyNames than on its own training signals, as you noted in your review.
-
-We refrain from judging over the label noise in VG, but leave this to the readers of the corresponding paper where they describe the undertaken measures to obtain and verify object name labels.
-
-We were considering using directly the MSCOCO labels for the MSCOCO images (recall that Visual Genome was built on top of MSCOCO), but decided against it for the following reasons: MSCOCO only contains 80, well (easy to) separated categories of an arbitrary level of specificity (person, dog, tie, donut, ...).
-This does result in little noise, but also in  images not as densely labeled as in VG.
-In sum, linguistically analysing object naming variations across many different domains and classes, and allowing researchers to analyse the influence of the context (objects and their domain or category) would not be possible with MSCOCO annotations.
-
-Please see the answers to your remaining questions on the experiment in Section 5 amongst the general answers to all reviewers.
 

### 2019-11-09 papers/LREC2020/data-collection.tex
revised data collection

--- 2019-05-21 papers/EMNLP2019/data-collection.tex
@@
 
-We take data from \vg~\cite{krishna2016visualgenome}, which
-% aims to provide a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-contains a dense region-based labeling of $108$K~images with, inter alia, objects, attributes and relationships,  %object descriptions, attributes, and relationships, as well as question-answer pairs,
+\begin{table*}[htp]
+	\small
+	\centering
+	\begin{tabular}{lp{14cm}}
+			\toprule
+			Domain & \multicolumn{1}{c}{Synsets}\\
+			\midrule			
+			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
+                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
+			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
+			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
+			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
+			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
+			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
+                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
+			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
+                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
+			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
+                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
+			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
+			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
+			\bottomrule
+		\end{tabular}
+		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
+                  \label{tab:overview_dataset2}}
+	\end{table*}
+
+\begin{table*}[htp]
+	\small
+	\centering
+	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
+		\toprule
+		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
+		\midrule
+		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
+		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
+		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
+		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
+		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
+		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
+		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
+		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
+		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
+		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
+		\bottomrule
+	\end{tabular}
+	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
+		\label{tab:overview_dataset1}}
+\end{table*}
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
+  \caption{Instructions for AMT annotators for the first round.}
+  \label{fig:instructions1}
+\end{figure*}
+
+We take data from \vgenome~\cite{krishna2016visualgenome}, which
+contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
 all linked to WordNet synsets \cite{fellbaum1998wordnet}.
 \vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
-%As common in Computer Vision, O
-Objects are localized as 
-%identified via
- bounding boxes, as in Figure~\ref{fig:cake}.% 
+As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
 \footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}
@@
 \label{ssec:sampling}
- % of frequent classes/names in  \vgenome, which, at the same time, have been frequently/commonly studied in the psycholinguistic literature. 
+
 %Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al.
 as basis.
-We selected images from seven domains: six based on McRae et al.'s  (\citeyear{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
+We selected images from seven domains: six based on McRae et al.'s  (\cite{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 
-Within each domain, we aimed at collecting instances at different taxonomic levels  to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy %in the first place
-(e.g.\ \textsc{home}).
-% Standard taxonomies do not align well with name variability; for instance, people use more varied names for types of dogs than for types of cows, while both dogs and cows are mammals.
-Instead, we defined a set of synsets ($52$\ in total) that we would use to collect our object instances from \vg, balancing variability.
+Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
+Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect our object instances from \vg.
+
 From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
 For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
+\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
 
@@
 Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds.
-%\textbf{double-check}
-This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation. 
-See Section\ \ref{ssec:elicitation} and the Supplemental Material for details on the pruning. 
+This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as follows.
+Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.
 % \begin{itemize}
@@
 \label{ssec:elicitation}
+
 To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
@@
 In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
-We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear.
-%The Appendix~\ref{app:instructions} contains the task instructions and details about the pruning and data procedure.
-We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images. 
-(We refer to the Supplemental Material for the task instructions and more details on the pruning and the dataset.) 
-We then did 3 more collection rounds, and shuffled the set of images per task between each round. 
+We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear (see Figure~\ref{fig:instructions1} for the instructions).
+
+%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
+After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
+This yielded $25,596$ images (we discarded $5,497$).
+We then did 3 more collection rounds, shuffling the set of images per task between each round.
+Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
 Workers could only participate in one round, to avoid workers annotating an instance more than once. 
-We obtained a total of 36 names per image (i.e.,\ object).
-As will become clear in the analysis, while object identification remains an issue despite these precautions, most mismatches between \vg annotations  and our data cannot be considered mistakes, and the annotation results have significant implications for the study of object naming in L\&V (see discussion in Sections~\ref{sec:analysis} and \ref{sec:modeling}).
+We obtained a total of 36 names per object.
 Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
+  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
+  \label{fig:instructions2}
+\end{figure*}
+
+% \begin{figure*}[htp]
+%   \centering
+%   \includegraphics[width=1.5\columnwidth]{figures/round1+_p2.png}
+%   \caption{FAQ accompanying the instructions for AMT annotators for rounds~$2$ to~$4$.}
+%   \label{fig:faq}
+% \end{figure*}
+
 %\cs{Maybe say something about the rejections, if space permits it.}
+
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "main"
+%%% TeX-master: "lrec2020naming"
 %%% End:

### 2019-11-09 papers/LREC2020/analysis.tex
divide LREC draft sections into separate tex files
revised data collection
revision section 5 (analysis); separate file for conclusions

@@
 
-We investigate to what extent names in our dataset can be considered canonical in terms of various agreement measures,
-%based on annotations in \vg and ManyNames, 
-and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
-%Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
+% We investigate to what extent names in our dataset can be considered canonical in terms of various agreement measures,
+% %based on annotations in \vg and ManyNames, 
+% and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
+% %Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
+
+\input{analysis_table_wModelpreds}
+%\input{analysis_table}
 
@@
  \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds} 
-
 \end{figure*}
 
-\begin{table*}
-\centering
-\begin{tabular}{lrrrrr}
-\toprule
-                         &   RefCoco &  Flickr30k &           VG &      VGmn &        MN \\
-\midrule
-                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
-                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
-     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
- \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
-           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
-\bottomrule
-\end{tabular}
-\label{tab:compare}
-\caption{Overview statistics for different data sets containing object naming data}
-\end{table*}
+Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames.
+% with higher and lower agreement
+As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous dataset: 35.3 on average, compared to 1-3 \gbt{to revise if we keep the VGmn column.} 
+It also contains the most variability, since objects have on average 5.7 names (compared to 1-1.9).
+This makes it in principle suitable to study how much inter-subject naming variation there is, and what factors influence such variation.
+However, data analysis shows that object identification is still an issue in our data: despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+They typically named an adjacent object or one supported by the target object (e.g.\ \textit{jacket-toy} in Fig.~\ref{fig:ex-high-low-agreement}) or a part of the target object.
+While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated (\textit{pants-player} or \textit{bed-sleeping bag} in Fig.~\ref{fig:ex-high-low-agreement}).
+Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
+Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
+In future work, we plan to filter out cases.
 
-\subsection{Comparison with other datasets}
-\label{subsec:compare}
-
-See Table \ref{tabe:compare}
-
-\subsection{Names, Instances, Classes}
+\subsection{Naming variation and agreement}
 \label{subsec:counts}
 
+\gbt{I think that we will need to remove the class-based analysis, for lack of space (plus, I think that the instance-level analysis is enough to get an idea of the data).
+For the moment I'm not doing it because I'd like to have your ok first.
+If we don't, we need to give an example and also say how many classes we have.
+Also, maybe rename ``\vg synsets'' instead of ``class''?}
+\gbt{BEGIN PART NOT EDITED}
 We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
@@
 
-\subsection{Agreement}
+\gbt{END PART NOT EDITED}
 
-%As type counts give a rather rough indication for variation in object naming, 
-Next, we look at the following agreement measures, computed with $t>1$: 
-%$t=1$: % to assess agreement on the object names:
+To assess agreement on the object names, we check the following measures, computed with $t>1$: 
+%$t=1$: % 
 \begin{itemize}
@@
 
-%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
-%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
-%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.
-
 Table\ \ref{tab:agree} shows, generally, that the agreement measures follow a similar pattern as the type counts in Section\ \ref{subsec:counts}:
-On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
-the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
+On the instance level, the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
 On the class level, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
@@
 These suggest that instances which are more prototypical of a category trigger higher agreement.
-The following section will examine other potential sources of variation in object naming.
+The following section will examine other sources of variation in object naming.
 
-\subsection{Variation: Specificity and Other Sources}
-\label{ssec:variation}
-Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
-%This section shows that naming variation in ManyNames cannot be explained by this parameter.
-This parameter does not explain the variation in ManyNames, as we will show in the following.
-
-Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
-For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
-% given by \vg.
-%%In this section, we take a closer look at the lexical variation we observe in our data set. 
-%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
-These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
-%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
-\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
-w_n$ constitute the less frequent alternatives of $w_{top}$.
-The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
-The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
-%The naming variants can be grouped according to their lexical relation, as follows:
-%
-%\begin{itemize}
-%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
-%\item \textbf{hyponymy}: e.g.\ man vs. person
-%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
-%\item \textbf{no relation}: e.g.\  desk vs. apple
-%\end{itemize}
-%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
-Table \ref{tab:rel} shows the distribution
-how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
-%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
-%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
-%\gbt{what do you mean, `` aggregated class-level response set''?}
-%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
-The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
-Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
-However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.
-
-We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}.
-\textbf{Referential uncertainty}: despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
-They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
-Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
-\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
-As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
-%
-\begin{table}[t]
-\small
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{lcc|p{2.5cm}}
-\toprule
-         relation & \% types & \% token & \it ex: jacket \\
-\midrule
-% meronym &  0.1 &  0.2 \\
-% holonym &  0.1 &  0.4 \\
- word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
-\midrule
- synonym &  1.1 &  1.1 & \it hoodie  \\
- hyponym &  2.2 &  3.8 & \it parka, blazer \\
- co-hyponym &  3.1 &  5.9 & \it raincoat\\
- hypernym &  10.5 &  27.7 & \it clothing, coat\\
- rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
-\bottomrule
-\end{tabular}
-\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
-\label{tab:rel}
-\vspace{-0.5cm}
-\end{table}
-
-%GBT: I changed this cause I'm afraid to be left out for formal reasons. 
-%\vspace{-0.5cm}
-% \begin{description}[style=unboxed,leftmargin=0.2cm]
-% \setlength{\itemsep}{1pt}
-% \setlength{\parskip}{0pt}
-% %\setlength{\leftmargin}{0pt}
-% \item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
-They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-% %Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
-Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-% \item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-% \item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
-% \item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-% \item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
-% \end{description}
-% \vspace{-0.2cm}
+To sum up, we find both substantial consistency in naming (the most frequent name accounts for 75\% of object names, on average) and substantial naming variation (the remaining 25\%).
+Moreover, there is a very large standard variation in how much agreement there is for objects in images, that only partially depend on the domain.
+We next turn to the sources of variation.
+%and our results suggest that a large part of the factors are instance-dependent.
 
@@
 %\end{table}
-\input{analysis_table_wModelpreds}
-%\input{analysis_table}
 
@@
 
-\subsection{Discussion}
-\label{subsec:discuss}
+\subsection{Sources of variation}
+\label{subsec:sources}
 
-% gbt: I moved the following sentence to the Conclusion section. To determine: what parts of this discussion stay here, what go to the conclusion.
-% The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
+Previous work on object naming has assumed that variation is mostly taxonomical (see Section \ref{sec:relwork}).
+This parameter does not explain the variation in ManyNames. 
+Table \ref{tab:rel} shows the distribution of synset relations in the ManyNames responses, in terms of their type and token frequency.
+To obtain it, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names to see if they stand in a taxonomic relation to the objects' \vg  synsets.%
+\footnote{For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10; the other relations are straightforward.
+The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).}
+As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
+Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of specificity.
+Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
+%%In this section, we take a closer look at the lexical variation we observe in our data set. 
+%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
+These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
+%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
+\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
+w_n$ constitute the less frequent alternatives of $w_{top}$.
+The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
+The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
+%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
+%The naming variants can be grouped according to their lexical relation, as follows:
+%
+%\begin{itemize}
+%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
+%\item \textbf{hyponymy}: e.g.\ man vs. person
+%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
+%\item \textbf{no relation}: e.g.\  desk vs. apple
+%\end{itemize}
+%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
 
-The answer to our question, \textit{do objects in real-world images have a canonical name?} is nuanced. 
-Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization.
-However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain. 
-The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
-With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
-%For theoretical research, w
-We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.
+%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
+%\gbt{what do you mean, `` aggregated class-level response set''?}
+%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
 
-Our ManyNames dataset provides a means 
-(i) to study how different people would name the same object (image region),  
-%\cs{"visual awareness" would fit in here}, 
-and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
-%assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
-(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
-
-As far as research in L\&V and Computer Vision is concerned, our findings are reason to question 
-%the appropriateness of the standard, single-label approach in visual object naming and categorization methods. 
- the common assumption that there at least exists a canonical name
-%,\ i.e.,\ a  name on which the majority of people would agree 
- for individual visual objects (localized by bounding boxes).
- % cf.\ the high standard deviation in terms of the relative frequency of an instance's top response (column \%top, Table~\ref{tab:agree}), and the average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG})\cs{a bit redundant now}).
+We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
+\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
+\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
+\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe-dress}).
+%As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
 %
-The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
-It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, \textsl{dog, animal, pet} vs.
-\textsl{dog, animal, hat}).
-%
-The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
-as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierarchically related. 
-%\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
-%
-% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
-% Wang et al.: ".
-The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
-% @related work
-%[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy.
-\cs{remove or move to related work?
-also sentence to Ordonez}]
-%\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF).
-\cs{maybe remove, since it is not that relevant?}}
-%
-%
-% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
-%
-%
-However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-For the same reason, even fine-grained recognition models (as those trained on ILSVRC) cannot be expected to be able to simply infer the recognition of more general classes.
-%since we found that many name alternatives are not hierarchically related to the VG name, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically a "truly" false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-%\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
-%
-
-%\cs{?: Say something about type disagreements on class-level, after having written the results discussion.}
-%
-
-%\cs{Ah, we still should have a comparison model with above argumentation :/.}
-%
-%As a use-case study, in Section\ \ref{sec:modeling}, we will treat ManyNames as evaluation data and assess whether an existing SOTA model can account for the naming variants of individual objects.
+\begin{table}[t]
+\small
+\centering
+\setlength{\tabcolsep}{2pt}
+\begin{tabular}{lcc|p{2.5cm}}
+\toprule
+         relation & \% types & \% token & \it ex: jacket \\
+\midrule
+% meronym &  0.1 &  0.2 \\
+% holonym &  0.1 &  0.4 \\
+ word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
+\midrule
+ synonym &  1.1 &  1.1 & \it hoodie  \\
+ hyponym &  2.2 &  3.8 & \it parka, blazer \\
+ co-hyponym &  3.1 &  5.9 & \it raincoat\\
+ hypernym &  10.5 &  27.7 & \it clothing, coat\\
+ rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
+\bottomrule
+\end{tabular}
+\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.
+\gbt{TO DO (IMPORTANT): change the rel-not-covered example to something that is true naming variation.
+I moved referential uncertainty out of the analysis of sources of variation.}}
+\label{tab:rel}
+\vspace{-0.5cm}
+\end{table}
 
@@
 %%% mode: latex
-%%% TeX-master: "main"
+%%% TeX-master: "lrec2020naming"
 %%% End:

### 2019-11-09 papers/LREC2020/conclusion.tex
revision section 5 (analysis); separate file for conclusions

--- 2019-05-21 papers/EMNLP2019/analysis.tex
@@
-%\gbt{Points to discuss in the paper, as discussed with Carina May 16:}
-%
-%\begin{itemize}
-%\item Super high variance in the agreement.
-Higher agreement for instances, lower for classes.
-Suggests systematicities at the instance level that do not depend on the class.
-Hypothesis, supported by qualitative analysis (Figure 3): relevance of visual perceptual factors.
-E.g.: saliency, background/foreground (desk-keyboard; bridge-train); ``angle'' from which the object is shown (see girl-t-shirt example); \dots In addition, we also find aspects discussed by Psycholing, but at the level of the instance: Typicality (see truck-bus example, bridge-dock, bench-seat).
-%\item Forget about WordNet.
-%\item Implications for lang\&vision: 1) synset classification won't do (if the goal is to predict/label an object); 2) name classification won't do either; 3) ``mistakes'' done by models are also done by humans -- role of referential uncertainty.
-%\end{itemize}
-
-We investigate to what extent names in our dataset can be considered canonical in terms of various agreement measures,
-%based on annotations in \vg and ManyNames, 
-and we look at sources of variation based on WordNet. %, i.e., to what extent speakers agree in their naming choices.
-%Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, look at concept-level agreement, we examine to what extent names overlap (i) for the same object and (ii) for different instances of the same class, based on the canonicalized names in \vg.
-
-\begin{figure*}
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[scale=.4]{figures/types_instances.png}
-\end{minipage}
-\begin{minipage}[b]{0.6\linewidth}
-\includegraphics[scale=.4]{figures/types_classes.png}
-\end{minipage}
-\vspace{-0.8cm}
- \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds}
-\end{figure*}
-
-\subsection{Names, Instances, Classes}
-\label{subsec:counts}
-
-We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
-%and obtained via a semi-automatic linking of the object name to WordNet
- (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object),  see Figure \ref{fig:ex-high-low-agreement} for examples.
- % of objects and their response sets (top rows below the images).
- %[if model preds are kept]}. 
- Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
-
-% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
-%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects (left) or classes (right) have at least $n$\ names, with different frequency thresholds~$t$ to account for possible noise in the crowdsourced data.
-Without any frequency thresholding~\mbox{($t$=1)}, the proportion of instances and classes that have a single name annotated is very small, below 10\%\ in both cases.
-
-The histogram for instances in Figure\ \ref{fig:ntypes} suggests that low-frequency responses are common in ManyNames, as is expected in a free annotation task.
-% where subjects are free to choose any response. 
-When discarding these names, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
-majority of the response sets become more consistent with at most 5\ names per set, 
-%Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%. %, even when applying a strict frequency filter of 4.
-but the sets with a single name still make up only $<$50\%\ of all sets. 
-This indicates that variation in naming instances is more or less restricted, but is still non-negligible. 
-%to a manageable set of up to 5\ names per object.
-
-The number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
-%Here, we observe that the 
-The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds.
-This clearly indicates that different instances annotated with the same
-%name and 
-%\cs{(removed "name and") 
-%The synsets could have different names -- maybe say "or even same name"?}
-synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
-Implications of this will be discussed in Section \ref{subsec:discuss}.
-
-%\cs{Change yticks to 0-100, with label \%. Make font larger in Fig. with plots?}
-
-\begin{table*}
-\footnotesize
-%\begin{tabular}{p{1.3cm}cccccc|cccccc}
-%\toprule
-% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
-%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
-%\midrule
-%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
-% \midrule
-%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
-% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
-%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
-%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
-%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
-%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
-%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
-%\bottomrule
-%\end{tabular}
-
-\begin{tabular}{lccccc|ccccc}
-\toprule
- & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
-          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
-\midrule
-            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
-            \midrule
-                     people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
-       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
-           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
-                 buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
-           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
-                  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
- animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
-\bottomrule
-\end{tabular}
-\vspace{-0.3cm}
-\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
-\label{tab:agree}
-\end{table*}
-
-\subsection{Agreement}
-
-%As type counts give a rather rough indication for variation in object naming, 
-Next, we look at the following agreement measures, computed with $t>1$: 
-%$t=1$: % to assess agreement on the object names:
-\begin{itemize}
-% \setlength{\itemsep}{2pt}
-% \setlength{\parskip}{1pt}
-\item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
-\item \textbf{$H$}: the $H$ agreement measure from \citet{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
-where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
-\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name.
-\item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
-\end{itemize}
-
-%\cs{Maybe it would be good to give an example for the class-level, to make it easier to follow the results discussion}
-%Again, we measure instance-level and class-level agreement on response sets for objects and synset classes, respectively.
-%o account for potential noise\cs{redundant}, we filter out names with a frequency of\ 1 from the response sets.
-
-Table\ \ref{tab:agree} shows, generally, that the agreement measures follow a similar pattern as the type counts in Section\ \ref{subsec:counts}:
-On the instance level, %our annotators achieve a fair amount of overlap in their object naming choices, with 
-the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
-On the class level, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
-The $H$ measures indicate a fair amount of agreement for instances, which is a bit lower than in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55).
-On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
-
-If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
-%In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
-%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
-Across domains, however, we find a large standard deviation for both \%top and $H$.
-% when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}.
-This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
-The qualitative examples in Figure \ref{fig:ex-high-low-agreement} %further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
-illustrate this, showing visual instances with very high or low agreement. 
-These suggest that instances which are more prototypical of a category trigger higher agreement.
-The following section will examine other potential sources of variation in object naming.
-
-\subsection{Variation: Specificity and Other Sources}
-\label{ssec:variation}
-Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
-%This section shows that naming variation in ManyNames cannot be explained by this parameter.
-This parameter does not explain the variation in ManyNames, as we will show in the following.
-
-Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
-For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
-% given by \vg.
-%%In this section, we take a closer look at the lexical variation we observe in our data set. 
-%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}.
-These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
-%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),...
-\}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ...
-w_n$ constitute the less frequent alternatives of $w_{top}$.
-The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs.
-The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
-%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
-%The naming variants can be grouped according to their lexical relation, as follows:
-%
-%\begin{itemize}
-%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
-%\item \textbf{hyponymy}: e.g.\ man vs. person
-%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
-%\item \textbf{no relation}: e.g.\  desk vs. apple
-%\end{itemize}
-%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
-Table \ref{tab:rel} shows the distribution
-how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
-%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
-%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."}
-%\gbt{what do you mean, `` aggregated class-level response set''?}
-%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
-The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
-Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
-However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, but to other sources.
-
-We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}.
-\textbf{Referential uncertainty}: despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
-They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-%Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
-Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
-\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
-As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
-%
-\begin{table}[t]
-\small
-\centering
-\setlength{\tabcolsep}{2pt}
-\begin{tabular}{lcc|p{2.5cm}}
-\toprule
-         relation & \% types & \% token & \it ex: jacket \\
-\midrule
-% meronym &  0.1 &  0.2 \\
-% holonym &  0.1 &  0.4 \\
- word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
-\midrule
- synonym &  1.1 &  1.1 & \it hoodie  \\
- hyponym &  2.2 &  3.8 & \it parka, blazer \\
- co-hyponym &  3.1 &  5.9 & \it raincoat\\
- hypernym &  10.5 &  27.7 & \it clothing, coat\\
- rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
-\bottomrule
-\end{tabular}
-\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
-\label{tab:rel}
-\vspace{-0.5cm}
-\end{table}
-
-%GBT: I changed this cause I'm afraid to be left out for formal reasons. 
-%\vspace{-0.5cm}
-% \begin{description}[style=unboxed,leftmargin=0.2cm]
-% \setlength{\itemsep}{1pt}
-% \setlength{\parskip}{0pt}
-% %\setlength{\leftmargin}{0pt}
-% \item[Referential uncertainty:] despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
-They typically named an adjacent object or one supported by the target object (e.g.\ \textit{book-bed}) or a part of the target object (\textit{pants-player}).
-% %Note that, while some of these cases are arguably annotation errors (\textit{boy-helmet}), in many cases it is not possible to distinguish which object is being indicated (\textit{bed-sleeping bag}).
-Pointing gestures in natural communication are as referentially uncertain as bounding boxes; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-% \item[Cross-classification:] a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-% \item[Conceptual disagreement:] as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog})
-% \item[Metonymy:] we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-% \item[Issues with WordNet:] due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose  synonyms or hypernyms (\textit{robe-dress}).
-% \end{description}
-% \vspace{-0.2cm}
-
-%\begin{table}
-%\small
-%\begin{tabular}{lp{4.8cm}r}
-%\toprule
-%VG name &  top5 MN names &  n$_{obj}$  \\
-%\midrule
-%\multicolumn{3}{c}{\it Canonical VG names with max agreement in MN}\\
-% giraffe &  giraffe (96.8), animal (1.2), zebra (0.4), camel (0.3), pole (0.1) &  915 \\
-% zebra &  zebra (96.3), animal (1.0), giraffe (0.9), horse (0.2), microwave (0.2) &  461  \\
-% cat &  cat (94.8), animal (0.9), kitten (0.8), dog (0.4), laptop (0.2) &  754\\
-%\midrule
-%\multicolumn{3}{c}{\it Canonical VG names with min agreement in MN}\\
-% booth &  booth (19.3), table (12.3), phone booth (9.8), bench (6.7), building (4.4) &  11 \\
-% cabbage &  cabbage (21.4), lettuce (17.0), hotdog (11.9), food (10.7), salad (10.4) &  9 \\
-% robe &  robe (22.1), shirt (16.8), jacket (13.3), dress (5.7), clothing (3.2) &  19 \\
-%  \midrule
-%  \multicolumn{3}{c}{\it Non-canon. VG names with max agreement in MN}\\
-% sedan &  car (88.4), wheel (3.1), vehicle (2.3), automobile (1.3), dog (0.8) &  11 \\
-% pony &  horse (83.9), pony (9.1), animal (2.9), donkey (1.1), cow (1.1) &  8 \\
-% necktie &  tie (81.4), necktie (10.2), shirt (4.6), ties (1.5), jacket (0.5) &  11 \\
-% \midrule
-%   \multicolumn{3}{c}{\it Non-canon. VG names with min agreement in MN}\\
-% shelter &  umbrella (9.7), shelter (8.8), roof (8.0), tent (7.1), building (6.8) &  10 \\
-% bath &  shower (13.3), elephant (9.9), birdbath (8.1), water (7.2), trough (7.2) &  10 \\
-% vegetable &  food (15.7), broccoli (13.1), sandwich (10.6), salad (9.3), pizza (7.8) &  25 \\
-%\bottomrule
-%\end{tabular}
-%\caption{Examples for VisualGenome (VG) names and their most frequent corresponding responses in ManyNames (MN; percentages shown in brackets).
-``Canonical'' means that the VG name is the top name in MN, and non-canonical vice versa.}
-%\label{tab:qual}
-%\end{table}
-\input{analysis_table_wModelpreds}
-%\input{analysis_table}
-
-%\gbt{The non-canon.
-VG names suggest that people prefer more general names (``car $>$ sedan'', ``horse $>$ pony'', ``tie $>$ necktie'').
-Could be due to lexical availability (more general \ra more frequent \ra more available).
-This could be verified (using frequency).
-Hypothesis: In cases where top name != VG, the VG name is less general.
-Could be also a more general hypothesis: see if people prefer more frequent names in general.}
-%\cs{@Table~\ref{tab:qual} (just wrt presentation) The most interesting blocks are 2 and 3 (canonical VG with min agr.; non-canonical with max agr.)}
-
-\subsection{Discussion}
-\label{subsec:discuss}
-
-% gbt: I moved the following sentence to the Conclusion section. To determine: what parts of this discussion stay here, what go to the conclusion.
 % The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
@@
 
-\iffalse
-*********
-Existing large-scale collections of labels or names of objects in L\&V provide simple annotations of individual objects with canonicalized name sets.
-When humans agree only around 70\% of the cases in how to name an object, it is not clear that the data can be taken as a gold standard in multi-label classification setting, as is commonly done in Computer Vision.
-% At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
-See e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
-\gbt{It is not clear to me what this means: what kind of data is this?
-how does this result relate to our point?
--- @Carina, expand?}
-\fi
-
-%\gbt{I couldn't follow the discussion in the following pargraph. Do you think it's subsumed by the one above? Can we remove it?} 
-%Given that we find much lower agreement on object class-level than on an instance-level, one might argue for using very fine-grained object annotations to remedy this problem. 
-%However, the fact that naming variants are often not recoverable by hierarchical relations suggest that even fine-grained recognition models cannot be expected to be able to simply infer recognition of more general classes (e.g., ILSVRC synset).
-Thus, neither simple multi-label classification nor more advance hierarchical approaches to object recognition seem to be well designed for capturing natural naming phenomena comprising cross-classification, metonymy and potentially other sources of variation.
-
-%What does this discrepancy between the instance-level and category-level agreement in VisualGenome and ManyNames naming choices mean? 
-%First of all, it suggests that the same original VisualGenome name can trigger very different variants depending on the visual instance, leading to a drastic increase of variants elicited for categories as compared to instances.
-%Second, this clearly shows that annotators in VG do not generally annotate the most canonical name \cs{but they don't annotate the name, but the description} and that many names annotated for objects in VG do not correspond to the overall most preferred variant.
-\sz{think more ...}
-%\gbt{I don't think we can conclude this second part -- we do have the 70\% top=VG figure that says that VG annotators annotate the most canonical name.
-What this suggests to me is that instance-level properties are more important than category-level properties, somehow.
-
-%Why is naming more flexible in certain domains than in others? \gbt{Hypothesis: expectation: little variation - hypernymy at most, more variation <-> more affordances <-> more varied relationships.}
-
-%\cs{@Table~\ref{tab:agree} I still think that we could also have \%\ top with $N>1$ to give an idea as to how useful the data is for the people interested in using it for, e.g., model evaluation.
-For that, it is clear that crowdsourcing is noisy and before using it some outlier removal needs to be made.}
-
-% \subsection{Entry-level names and preference orders....}
-
-% \sz{an interesting example:} In our data set, there are 24 images where \textit{penguin} has been used, so we know that the object is a \textit{penguin}.
-For 50\% of these images, annotators still prefer \textit{bird} as the most common name.
-According to the theory of entry-level categories, this should not happen.
-People should always prefer \textit{penguin} over \textit{bird}.
-
-% \sz{how can we analyze this quantitatively?}
-
-% \begin{itemize}
-% \item lettuce -- salad
-% \item fruit -- food
-% \item man -- catcher
-% \item bowl --chili
-% \item bowl -- diner \gbt{spelling mistake? should be dinner?} 
-% \item burger -- meat
-% \item statue -- animal (image shows statue of an animal)
-% \item bottle -- alcohol
-% \item donut --desert \gbt{spelling mistake? should be dessert?} 
-% \item zebra -- stripes
-% \item oven -- grill
-% \end{itemize}
-
 %%% Local Variables:
 %%% mode: latex
-%%% TeX-master: "main"
+%%% TeX-master: "lrec2020naming"
 %%% End:

### 2019-11-10 verification_phase0/results_to_csv--complex.py
lot of refractoring; towards computing agreement

@@ -4,17 +4,21 @@ import json
 import glob
 
 import numpy as np
-
+from collections import Counter
 import os
+from sklearn.metrics import cohen_kappa_score
 
 
 ANONYMIZE = False
-CONTROL_RELIABILITY_THRESHOLD = .49  # Delete control if not more than this did it correctly
+CONTROL_RELIABILITY_THRESHOLD = .5  # Delete control if fewer than this did it correctly
+
+WORKER_RELIABILITY_THRESHOLD = .85   # ignore worker if score (after filtering) lower than this # TODO implement this
+ASSIGNMENT_RELIABILITY_THRESHOLD = 1  # only total agreement makes an item reliable   # TODO implement this
 
 ASSIGNMENT_APPROVAL_TRESHOLD = .7   # will approve any assignment with score higher than this
-WORKER_APPROVAL_TRESHOLD = .8   # will approve all assignments even if a single assignment is crap
+WORKER_APPROVAL_TRESHOLD = .85   # will approve all assignments even if a few assignments are crap
 
-WORKER_BLOCK_THRESHOLD = .8     # will block worker based on mean below this
+WORKER_BLOCK_THRESHOLD = .85     # will block worker based on mean below this
 ASSIGNMENT_BLOCK_THRESHOLD = .7   # will block worker based on single assignment below .7
 
 BONUS_THRESHOLD = 1.0
@@ -22,6 +26,9 @@ BONUS_THRESHOLD = 1.0
 INSPECT_FAILED_CONTROLS = True
 INSPECT_REJECTED_ASSIGNMENTS = True
 NO_REJECTION = False
+
+RESTRICT_TO_N_WORKERS_PER_NAME = False  # TODO implement this
+COULANCE = 1 # TODO implement this
 
 if NO_REJECTION:
     print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
@@ -91,156 +98,167 @@ for i in range(MAX_N_IMAGES):
 
 # Split by image
 meta = ['hitid', 'requesterannotation', 'assignmentid', 'workerid']
-dfs_per_image = []
+image_annotations = []
 for i in reversed(range(MAX_N_IMAGES)): # reversed in order for names with 10 and 1 to not interfere.
     # columns = meta + ['image_url_{}'.format(i), 'quality_control_{}'.format(i)]
     columns = meta + ['items'] + [col for col in assignments_from_mturk.columns if col.startswith('img{}'.format(i))]
[…]

### 2019-11-10 verification_phase0/results_to_csv--complex.py
commit version used for accept/reject

@@ -10,25 +10,33 @@ from sklearn.metrics import cohen_kappa_score
 
 
 ANONYMIZE = False
+
+# Remove unreliable controls
 CONTROL_RELIABILITY_THRESHOLD = .5  # Delete control if fewer than this did it correctly
 
-WORKER_RELIABILITY_THRESHOLD = .85   # ignore worker if score (after filtering) lower than this # TODO implement this
-ASSIGNMENT_RELIABILITY_THRESHOLD = 1  # only total agreement makes an item reliable   # TODO implement this
-
+# Approve/bonus assignments/workers
 ASSIGNMENT_APPROVAL_TRESHOLD = .7   # will approve any assignment with score higher than this
 WORKER_APPROVAL_TRESHOLD = .85   # will approve all assignments even if a few assignments are crap
-
-WORKER_BLOCK_THRESHOLD = .85     # will block worker based on mean below this
-ASSIGNMENT_BLOCK_THRESHOLD = .7   # will block worker based on single assignment below .7
-
 BONUS_THRESHOLD = 1.0
+
+# Block based on assignments/workers
+ASSIGNMENT_BLOCK_THRESHOLD = .6   # will block worker based on single assignment below .7
+WORKER_BLOCK_THRESHOLD = .85     # will block worker based on mean below this
+
+# Some more absolute params
+NO_REJECTION = False
+COULANCE = 1
+
+# Delete annotations based on worker/assignment
+WORKER_RELIABILITY_THRESHOLD = .85   # ignore worker if control score (after filtering) lower than this # TODO implement this
+ASSIGNMENT_RELIABILITY_THRESHOLD = .75  # only total agreement makes an item reliable   # TODO implement this
+
 
 INSPECT_FAILED_CONTROLS = True
 INSPECT_REJECTED_ASSIGNMENTS = True
-NO_REJECTION = False
+
 
 RESTRICT_TO_N_WORKERS_PER_NAME = False  # TODO implement this
-COULANCE = 1 # TODO implement this
 
 if NO_REJECTION:
     print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
@@ -272,15 +280,30 @@ if INSPECT_FAILED_CONTROLS:
               control['same_color']))
     print('---------------------')
 
-# Inspect low-agreement items (lowest-agreement first)
-
-
-# Create assignments dataframe with some basic stats: # TODO Oh my this is ugly code...
 name_annotations['correct1-filtered'] = name_annotations['correct1'].copy()
[…]

### 2019-11-10 verification_phase0/amt_api/approve_and_reject.py
update (version as used post-pilot part 1)

@@ -15,8 +15,6 @@ import pandas as pd
 
 ###############################
 
-DO_ACCEPTANCE = False  # TODO
-DO_REJECTION = False
 MTURK_URL = 'https://mturk-requester.us-east-1.amazonaws.com'
 
 REJECT_FEEDBACK = 'HIT is rejected because too many control items were answered incorrectly.'
@@ -40,7 +38,7 @@ def main():
     basepath = os.path.dirname(configfile)
     adminpath = os.path.join(basepath, config['data']['admindir'])
     resultspath = os.path.join(basepath, config['data']['resultdir'])
-    assignmentspath = os.path.join(resultspath, 'assignments.csv')
+    assignmentspath = os.path.join(resultspath, 'per_assignment.csv')
 
     mturk = amt_api.connect_mturk(config)
 

### 2019-11-11 verification_phase0/amt_api/publish.py
specify unique turker limit in config

@@ -151,7 +151,8 @@ if __name__ == '__main__':
 
         # Add unique turker id, or else empty string
         unique_turker_id = config["qualification"]["unique_turker_id"] if "unique_turker_id" in config["qualification"] else ""
-        param_list = [{'Name': 'unique_turker_id', 'Value': unique_turker_id}] + param_list
+        unique_turker_limit = config["qualification"]["unique_turker_limit"] if "unique_turker_limit" in config["qualification"] else "99999"
+        param_list = [{'Name': 'unique_turker_id', 'Value': unique_turker_id}, {'Name': 'unique_turker_limit', 'Value': unique_turker_limit}] + param_list
         logging.info(param_list)
 
         hit_data = create_new_hit(mturk, config, param_list, qualifications, config['data']['csvfile'] + '_' + str(row_idx))

### 2019-11-11 papers/LREC2020/analysis_table_wModelpreds.tex

--- 2019-05-21 papers/EMNLP2019/analysis_table_wModelpreds.tex
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2339876_3928476_supercat_unique.png}} sandwich (34) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), \underline{food} (5), burger (2),  \underline{hamburger} (2),  \underline{meal} (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} \underline{food} (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), \underline{food} (7), bun (4), sandwich (3),  \underline{bread} (2) [banana (1)] &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2)\\ 
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2379889_1353176_supercat_unique.png}}  sandwich (15), basket (6), food (5), burger (2),  hamburger (2),  meal (2) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394266_465678_singleton_obj.png}} food (10), sandwich (8), toast (5), french toast (4), dessert (2), breakfast (2) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2386509_681763_supercat_unique.png}} hotdog (14), food (7), bun (4), sandwich (3),  bread (2) [banana (1)] &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2)\\ \\
 				%
-				\rowcolor{lightgray}
-				 \textit{sandwich}, food, bread, sandwiches, plate, burger
-				 & plate, \textit{food}, \textit{basket}, hotdog, wrapper, paper
-				 & fish, chicken, meat, \textit{food}, \textit{sandwich}, bread
-				 & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table
-				 & woman, outfit, dress, girl, suit
-				& woman, outfit, \textit{dress}, girl, suit \\ 
+				% \rowcolor{lightgray}
+				%  \textit{sandwich}, food, bread, sandwiches, plate, burger
+				%  & plate, \textit{food}, \textit{basket}, hotdog, wrapper, paper
+				%  & fish, chicken, meat, \textit{food}, \textit{sandwich}, bread
+				%  & \textit{hotdog}, \textit{bun}, \textit{banana}, \textit{bread}, table
+				%  & woman, outfit, dress, girl, suit
+				% & woman, outfit, \textit{dress}, girl, suit \\ 
 				%
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2341667_2006329_singleton_obj.png}} bridge (35)  &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  \underline{building} (11)  &
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/1592509_1610006_singleton_obj.png}} bridge (20),  building (11)  &
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2384683_1306430_singleton_obj.png}} street (16), road (15), bridge (3) &
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2) [stuffed animal (1)]\\\\
 				%
-				\rowcolor{lightgray}
-				\textit{bridge}, arch, sky, structure, walkway
-				& \textit{building}, \textit{bridge}, sky, structure, church
-				& \textit{street}, \textit{road}, highway, intersection, pavement
-				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} 
-			         & \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
-				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
-\\ 
+% 				\rowcolor{lightgray}
+% 				\textit{bridge}, arch, sky, structure, walkway
+% 				& \textit{building}, \textit{bridge}, sky, structure, church
+% 				& \textit{street}, \textit{road}, highway, intersection, pavement
+% 				& \textit{railing}, water, \textit{pier}, ocean, \textit{fence}, deck, \textit{dock} 
+% 			         & \textit{man}, shirt, person, \textit{robe}, coat, \textit{jacket}%, woman, outfit, clothes, clothing
+% 				& teddy bear, \textit{bear}, dog, \textit{toy}, \textit{stuffed animal}, blanket, toys
+% \\ 
 				%
@@
 				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/498222_3135415_singleton_obj.png}} bed (12), sleeping bag (9), blanket (7), bed sheet (5) &
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
-				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\ \\
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
+				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\
 				%
-				\rowcolor{lightgray}
-				\textit{bed}, beds, sheets, frame, sheet
-				& \textit{bed}, table, bed frame, sofa, couch
-				& \textit{bed}, sheet, sheets, blanket, comforter, cover
-				& \textit{bed}, comforter, \textit{blanket}, cover, sheet 
-				& \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
-				& \textit{player}, batter, \textit{person}, man, uniform, boy, \textit{baseball player}, dirt \\  
+				% \rowcolor{lightgray}
+				% \textit{bed}, beds, sheets, frame, sheet
+				% & \textit{bed}, table, bed frame, sofa, couch
+				% & \textit{bed}, sheet, sheets, blanket, comforter, cover
+				% & \textit{bed}, comforter, \textit{blanket}, cover, sheet 
+				% & \textit{boy}, \textit{player}, \textit{batter}, \textit{kid}, girl, \textit{child}, \textit{baseball player}, person, uniform
+				% & \textit{player}, batter, \textit{person}, man, uniform, boy, \textit{baseball player}, dirt \\  
 				%
@@
 %				\multicolumn{4}{c}{\textbf{VG: batter}}\\
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), \underline{person} (3), \underline{baseball player} (2) &
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), \underline{baseball player} (7), batter (5), \underline{player} (3), helmet (2) [player (1)]&
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), \underline{baseball player} (4), \underline{player} (4), man (3), child (3), batter (3), dress (2), kid (2)&
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), \underline{player} (5), shoe (4), bat (4), \underline{person} (4), legs (4), \underline{baseball player} (3), hitter (2)\\
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2372219_2683892_supercat_unique.png}} man (24), cap (5), person (3), baseball player (2) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2394377_464684_singleton_obj.png}} man (13), baseball player (7), batter (5), player (3), helmet (2) [player (1)]&
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2398907_2901496_singleton_obj.png}}  boy (7), helmet (5), baseball player (4), player (4), man (3), child (3), batter (3), dress (2), kid (2)&
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2337552_957263_singleton_obj.png}} pants (6), player (5), shoe (4), bat (4), person (4), legs (4), baseball player (3), hitter (2)\\
 %				%
@@
 %				\multicolumn{4}{c}{\textbf{VG: robe}}\\
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), \underline{bathrobe} (5) &
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2373180_2333161_singleton_obj.png}} robe (27), bathrobe (5) &
 %				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/160_1058761_supercat_unique.png}} dress (30), uniform (2) &
 %				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2334612_2838713_supercat_unique.png}}  robe (11), jacket (7), clothes (6), bag (3), dress (2), man (2) &
-%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), \underline{sweater} (9), coat (3), doll (3), toy (3), \underline{shirt} (2), bear (2), robe (2) [stuffed animal (1)]\\
+%				\raisebox{-\totalheight}{\includegraphics[width=0.9\linewidth]{figures/2340041_2137546_supercat_ambiguous.png}} jacket (10), sweater (9), coat (3), doll (3), toy (3), shirt (2), bear (2), robe (2) [stuffed animal (1)]\\
 %				%
@@
 		First row: responses in MN, names that have a hierarchical relation to the \vgenome synset in WordNet are underlined.
-	Second row (gray): top name prediction by bottom up, names which match a MN response are in italics.}
+	Second row (gray): top name prediction by Bottom-up, names which match a MN response are in italics.}
 	\label{fig:ex-high-low-agreement}

### 2019-11-11 papers/LREC2020/conclusion.tex

@@
+The question of how people choose names for objects presented visually is relevant for Computational Linguistics (especially Language \& Vision), Computer Vision, Cognitive Science, and Linguistics.
 % The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
-
-The answer to our question, \textit{do objects in real-world images have a canonical name?} is nuanced. 
-Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization.
-However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain. 
-The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
-With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
-%For theoretical research, w
-We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature.
-
-Our ManyNames dataset provides a means 
-(i) to study how different people would name the same object (image region),  
-%\cs{"visual awareness" would fit in here}, 
-and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
-%assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
+We have surveyed datasets that can be useful to address this question, and proposed a new dataset, ManyNames, that affords new possibilities, both for analysis and modeling, providing a means
+(i) to study how different people would name the same object (image region), and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and
 (ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
 
-As far as research in L\&V and Computer Vision is concerned, our findings are reason to question 
-%the appropriateness of the standard, single-label approach in visual object naming and categorization methods. 
- the common assumption that there at least exists a canonical name
-%,\ i.e.,\ a  name on which the majority of people would agree 
- for individual visual objects (localized by bounding boxes).
- % cf.\ the high standard deviation in terms of the relative frequency of an instance's top response (column \%top, Table~\ref{tab:agree}), and the average mismatch of $27\%$~between the instances' top response and their VG name (\mbox{top=VG})\cs{a bit redundant now}).
-%
-The ability to distinguish incorrect object names from name alternatives is essential for visual object understanding, though. 
-It would be desirable to explicitly assess models towards their ability to account for naming variants of an instance (e.g.,~in how far are the top N predicted names valid alternatives, such as, \textsl{dog, animal, pet} vs.
-\textsl{dog, animal, hat}).
-%
-The criticism on the use of single "ground truth" labels is not new, but %to our knowledge 
-as we outlined in Section\ \ref{sec:relwork}, previous work has focused on the determination of canonical names, or on "granularity-aware" models, where naming variants are hierarchically related. 
-%\cs{check that this is in related work: previous work has focused on the determination of canonical names (e.g.,~\newcite{Ordonez:2016}; Mathews et al REF), or on "granularity-aware" models, where naming variants are hierachically related (e.g.,~\newcite{wang2014poodle, peterson2018learning}; Ristin et al., 2015 REF, and the references therein).}
-%
-% \textit{training} of classifiers with multiple labels to improve image classification model depicting multiple objects (e.g.,~Wang et al., 2016 REF)
+\gbt{The following needs to be made more coherent}
+For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which affects model performance on object categorization and naming.
+Crucially, evaluations in these task assume that object identification is possible based on the bounding box, and evaluates only the categories or names of objects assuming they are unique.
+The naming variation we have found also challenge the common assumption that there exists a single canonical name for individual visual objects (also see \cite{deng2014large,wang2014poodle,peterson2018learning}).
+At the same time, the ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
+Our data allows models to be tested wrt their ability to account for naming variants of an instance: For instance, to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet} vs.
+\textsl{dog, hat, grass}).
+\gbt{We have to be careful; without the correction round this is not strictly speaking true. How can we phrase this?}
 % Wang et al.: ".
@@
 \cs{maybe remove, since it is not that relevant?}}
-%
-%
 % peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").
-%
-%
-However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-For the same reason, even fine-grained recognition models (as those trained on ILSVRC) cannot be expected to be able to simply infer the recognition of more general classes.
+
+% However, given the fact that naming variants are often not recoverable by hierarchical relations, a taxonomic hierarchy is only limited in its use to distinguish automatically a truly false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
+% For the same reason, even fine-grained recognition models (as those trained on ILSVRC) cannot be expected to be able to simply infer the recognition of more general classes.
 %since we found that many name alternatives are not hierarchically related to the VG name, there is only limited use of, e.g., a taxonomic hierarchy, to distinguish automatically a "truly" false prediction (e.g.,\ \textsl{plate}) from a (possibly context-specific) valid alternative (e.g.,\ \textsl{basket}) to the single "ground truth" in a dataset (e.g.,\ \textsl{sandwich}).
-%\cs{also distributional similarity? Remember that we looked into this for the checkpoint and did not find a clear similarity threshold/pattern} 
-%
 
-%\cs{?: Say something about type disagreements on class-level, after having written the results discussion.}
-%
-
-%\cs{Ah, we still should have a comparison model with above argumentation :/.}
-%
-%As a use-case study, in Section\ \ref{sec:modeling}, we will treat ManyNames as evaluation data and assess whether an existing SOTA model can account for the naming variants of individual objects.
+\gbt{Make the following coherent with the previous paragraph}
+Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization.
+However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain.
+The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
+With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
+We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches.
 

### 2019-11-11 papers/LREC2020/intro.tex

@@
 
-We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
+We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.%
+\footnote{The dataset will be available upon publication.}
 Thus, our images show objects in complex visual contexts,

### 2019-11-11 papers/LREC2020/lrec2020naming.tex
first revision Section 3 (dataset survey)
revised data collection
revision section 5 (analysis); separate file for conclusions

@@
 \usepackage{colortbl}
+\usepackage{xcolor}
 
@@
 
-\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
+%\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
+\title{Object Naming: A Survey and a New Dataset}
 
@@
 \section{Background}
+\label{sec:rel-work}
 \input{background}
@@
 
-\section{A New Dataset: Many Names}
+\section{A New Dataset: ManyNames}
 \label{sec:data}
@@
 \section{Conclusion}
+\label{sec:conc}
+\input{conclusion}
 
-Your submission of a finalised contribution for inclusion in the LREC
-proceedings automatically assigns the above-mentioned copyright to ELRA.
+% \section{Acknowledgements}
 
-\section{Acknowledgements}
-
-Place all acknowledgements (including those concerning research grants and
-funding) in a separate section at the end of the article.
+% Place all acknowledgements (including those concerning research grants and
+% funding) in a separate section at the end of the article.
 

### 2019-11-11 papers/LREC2020/survey.tex

@@
 Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
-To sum up, we would recommend \RefCOCO to study effect of distractors on object naming in a restricted set of categories.
+To sum up, we would recommend \refcoco to study effect of distractors on object naming in a restricted set of categories.
 
@@
 
+As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess \textbf{naming variation}, which requires having data from many subjects.
+This is the motivation for our dataset, ManyNames, an augmentation of \vg.
+
 %%% Local Variables:

### 2019-11-11 verification_phase0/results_to_csv--complex.py
add subsampling data, removing unreliable workers, & aligning with manual annotations: TODO cleanup

@@ -3,13 +3,15 @@ pd.options.display.max_colwidth = 100
 import json
 import glob
 
+import random
+
 import numpy as np
 from collections import Counter
 import os
 from sklearn.metrics import cohen_kappa_score
 
+from scipy.stats import pearsonr
 
-ANONYMIZE = False
 
 # Remove unreliable controls
 CONTROL_RELIABILITY_THRESHOLD = .5  # Delete control if fewer than this did it correctly
@@ -20,23 +22,16 @@ WORKER_APPROVAL_TRESHOLD = .85   # will approve all assignments even if a few as
 BONUS_THRESHOLD = 1.0
 
 # Block based on assignments/workers
-ASSIGNMENT_BLOCK_THRESHOLD = .6   # will block worker based on single assignment below .7
+ASSIGNMENT_BLOCK_THRESHOLD = .6   # will block worker based on single assignment below this
 WORKER_BLOCK_THRESHOLD = .85     # will block worker based on mean below this
 
 # Some more absolute params
 NO_REJECTION = False
 COULANCE = 1
 
-# Delete annotations based on worker/assignment
-WORKER_RELIABILITY_THRESHOLD = .85   # ignore worker if control score (after filtering) lower than this # TODO implement this
-ASSIGNMENT_RELIABILITY_THRESHOLD = .75  # only total agreement makes an item reliable   # TODO implement this
+INSPECT_FAILED_CONTROLS = False
+INSPECT_REJECTED_ASSIGNMENTS = False
 
-
-INSPECT_FAILED_CONTROLS = True
-INSPECT_REJECTED_ASSIGNMENTS = True
-
-
-RESTRICT_TO_N_WORKERS_PER_NAME = False  # TODO implement this
 
 if NO_REJECTION:
     print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
@@ -286,22 +281,6 @@ name_annotations['correct3-filtered'] = name_annotations['correct3'].copy()
 name_annotations.at[~name_annotations['reliable1'], 'correct1-filtered'] = np.nan
 name_annotations.at[~name_annotations['reliable2'], 'correct2-filtered'] = np.nan
 
-# To compute agreement, compile dataframe of one row per name
[…]

### 2019-11-11 verification_phase0/amt_api/approve_and_reject.py
update bonus amount

@@ -19,7 +19,7 @@ MTURK_URL = 'https://mturk-requester.us-east-1.amazonaws.com'
 
 REJECT_FEEDBACK = 'HIT is rejected because too many control items were answered incorrectly.'
 APPROVE_FEEDBACK = 'Thank you for working for us!'
-BONUS_AMOUNT = '0.10'
+BONUS_AMOUNT = '0.15'
 BONUS_FEEDBACK = 'We have awarded a bonus of ${} because you did all control items perfectly.'.format(BONUS_AMOUNT)
 
 ###############################

### 2019-11-11 verification_phase0/amt_api/publish.py
fix sleeping bug

@@ -144,6 +144,7 @@ if __name__ == '__main__':
     batch_idx = initial_row / batch_size
 
     ## Loop through all data rows from starting index, creating HITs, sleep after every batch size
+    n_hits_published = 0
     for row_idx, row in data[initial_row:initial_row+total_rows].iterrows():
         logging.info("Batch {}, HIT {}".format(batch_idx, row_idx))
 
@@ -156,13 +157,14 @@ if __name__ == '__main__':
         logging.info(param_list)
 
         hit_data = create_new_hit(mturk, config, param_list, qualifications, config['data']['csvfile'] + '_' + str(row_idx))
+        n_hits_published += 1
         all_resulting_HITs.append(hit_data)
 
         logging.info("New hit: " + str(hit_data['HIT']['HITId']))
         logging.info("New hit groupId: " + hit_data['HIT']['HITGroupId'])
 
         # Sleepy time, now and then:.
-        if row_idx != initial_row + total_rows-1 and ((row_idx + 1) % batch_size) == 0:
+        if n_hits_published != total_rows-1 and ((n_hits_published + 1) % batch_size) == 0:
             outname = os.path.join(out_path, 'created_%s_uptobatch%d.json' % (moment, batch_idx))
             with open(outname, 'w') as outfile:
                 json.dump(all_resulting_HITs, outfile)

### 2019-11-11 verification_phase0/align_with_manual_annotations.py
move correlation with manual annotations to separate file

@@ -1,0 +1,94 @@
+import pandas as pd
+from scipy.stats import pearsonr
+
+ROUNDS = {
+    'pilot1': '1_pre-pilot/processed_results/pilot1/name_annotations_ANON.csv',
+    # 'pilot2': '1_pre-pilot/processed_results/pilot2/name_annotations_ANON.csv',
+}
+
+name_annotations = None
+for round in ROUNDS:
+    print("Reading", ROUNDS[round])
+    df = pd.read_csv(ROUNDS[round], index_col=0, converters={'colors': eval, 'names': eval, 'same_color': eval})
+    df['round'] = round
+    if name_annotations is None:
+        name_annotations = df
+    else:
+        name_annotations = pd.concat([name_annotations, df])
+name_annotations.reset_index(inplace=True, drop=True)
+name_annotations['object'] = name_annotations['object'].astype(str)
+name_annotations['image'] = name_annotations['image'].astype(str)
+
+print('\n-------------------')
+print("name_annotations:", len(name_annotations))
+print(name_annotations[:5].to_string())
+
+# Turn name_annotations into name_pairs (one pair of names per row)
+name_pairs = []
+columns = ['round', 'image', 'object', 'url', 'workerid', 'name1', 'name2', 'correct_name', 'same_object']
+for i, row in name_annotations.iterrows():
+    for name in row['colors']:
+        name_pairs.append([row['round'], row['image'], row['object'], row['image_url'], row['workerid'], row['name'], name, row['rating'], row['colors'][name]])
+name_pairs = pd.DataFrame(name_pairs, columns=columns).groupby(['round', 'image', 'object', 'url', 'name1', 'name2']).mean()
+name_pairs.reset_index(level=0, inplace=True)
+
+print('\n-------------------')
+print("name_pairs:", len(name_pairs), name_pairs.index)
+print(name_pairs[:5].to_string())
+
+
+# Load manual annotations, make representations comparable/compatible
+manual_annotations = '../raw_data_phase0/verification_pilot/verif_annos_pilot.csv'
+name_pairs_amore = pd.read_csv(manual_annotations, sep="\t")
+name_pairs_amore['image'] = name_pairs_amore['url'].apply(lambda x: x.split('//')[2].split('_')[0])
[…]

### 2019-11-11 verification_phase0/results_to_csv--complex.py

@@ -8,9 +8,6 @@ import random
 import numpy as np
 from collections import Counter
 import os
-from sklearn.metrics import cohen_kappa_score
-
-from scipy.stats import pearsonr
 
 
 # Remove unreliable controls
@@ -443,50 +440,3 @@ if False:
 # print('names:', len(names))
 # print(names[:10].to_string())
 # print('---------------------')
-
-
-# Turn name_annotations into name_pairs (one pair of names per row)
-name_pairs = []
-columns = ['image', 'object', 'url', 'workerid', 'name1', 'name2', 'correct_name', 'same_object']
-for i, row in name_annotations.iterrows():
-    for name in row['colors']:
-        name_pairs.append([row['image'], row['object'], row['image_url'], row['workerid'], row['name'], name, row['rating'], row['colors'][name]])
-name_pairs = pd.DataFrame(name_pairs, columns=columns).groupby(['image', 'object', 'url', 'name1', 'name2']).mean()
-
-# Load manual annotations, make representations comparable/compatible
-manual_annotations = '../raw_data_phase0/verification_pilot/verif_annos_pilot.csv'
-name_pairs_amore = pd.read_csv(manual_annotations, sep="\t")
-name_pairs_amore['image'] = name_pairs_amore['url'].apply(lambda x: x.split('//')[2].split('_')[0])
-name_pairs_amore['object'] = name_pairs_amore['url'].apply(lambda x: x.split('//')[2].split('_')[1])
-name_pairs_amore['same_object'] = name_pairs_amore['same_object'].replace({'Yes': 1, 'Not sure': .5, 'No': 0})
-name_pairs_amore['correct_name'] = (3 - name_pairs_amore['correct_name']) / 3   # scale from [3,-3] to [0,2]
-name_pairs_amore.rename(columns={'mn_obj_name': 'name1', 'vg_obj_name': 'name2'}, inplace=True)
-name_pairs_amore = name_pairs_amore.groupby(['image', 'object', 'url', 'name1', 'name2']).agg({'correct_name': 'mean', 'same_object': 'mean'})
-
-# Join amore annotations and crowdsourced annotations, and compute pearson correlations
-amore_vs_crowd = name_pairs_amore.join(name_pairs, lsuffix='_amore', rsuffix='_crowd').dropna()
-print('\n---------------')
[…]

### 2019-11-11 verification_phase0/align_with_manual_annotations.py
remove debugging printout

@@ -33,7 +33,7 @@ name_pairs = pd.DataFrame(name_pairs, columns=columns).groupby(['round', 'image'
 name_pairs.reset_index(level=0, inplace=True)
 
 print('\n-------------------')
-print("name_pairs:", len(name_pairs), name_pairs.index)
+print("name_pairs:", len(name_pairs))
 print(name_pairs[:5].to_string())
 
 
@@ -48,7 +48,7 @@ name_pairs_amore.rename(columns={'mn_obj_name': 'name1', 'vg_obj_name': 'name2'}
 name_pairs_amore = name_pairs_amore.groupby(['image', 'object', 'url', 'name1', 'name2']).agg({'correct_name': 'mean', 'same_object': 'mean'})
 
 print('\n-------------------')
-print("name_pairs_amore:", len(name_pairs_amore), name_pairs_amore.index)
+print("name_pairs_amore:", len(name_pairs_amore))
 print(name_pairs_amore[:5].to_string())
 
 

### 2019-11-11 verification_phase0/align_with_manual_annotations.py
add TODO

@@ -23,7 +23,7 @@ print('\n-------------------')
 print("name_annotations:", len(name_annotations))
 print(name_annotations[:5].to_string())
 
-# Turn name_annotations into name_pairs (one pair of names per row)
+# Turn name_annotations into name_pairs (one pair of names per row) # TODO Actually make this a main output format?
 name_pairs = []
 columns = ['round', 'image', 'object', 'url', 'workerid', 'name1', 'name2', 'correct_name', 'same_object']
 for i, row in name_annotations.iterrows():
@@ -35,7 +35,6 @@ name_pairs.reset_index(level=0, inplace=True)
 print('\n-------------------')
 print("name_pairs:", len(name_pairs))
 print(name_pairs[:5].to_string())
-
 
 # Load manual annotations, make representations comparable/compatible
 manual_annotations = '../raw_data_phase0/verification_pilot/verif_annos_pilot.csv'

### 2019-11-11 verification_phase0/align_with_manual_annotations.py
add TODO

@@ -32,6 +32,8 @@ for i, row in name_annotations.iterrows():
 name_pairs = pd.DataFrame(name_pairs, columns=columns).groupby(['round', 'image', 'object', 'url', 'name1', 'name2']).mean()
 name_pairs.reset_index(level=0, inplace=True)
 
+# TODO inter-annotator agreement; name_pairs also more convenient for this
+
 print('\n-------------------')
 print("name_pairs:", len(name_pairs))
 print(name_pairs[:5].to_string())

### 2019-11-12 verification_phase0/align_with_manual_annotations.py
include data for pilot2 ; minor refractoring

@@ -3,7 +3,7 @@ from scipy.stats import pearsonr
 
 ROUNDS = {
     'pilot1': '1_pre-pilot/processed_results/pilot1/name_annotations_ANON.csv',
-    # 'pilot2': '1_pre-pilot/processed_results/pilot2/name_annotations_ANON.csv',
+    'pilot2': '1_pre-pilot/processed_results/pilot2/name_annotations_ANON.csv',
 }
 
 name_annotations = None
@@ -23,7 +23,7 @@ print('\n-------------------')
 print("name_annotations:", len(name_annotations))
 print(name_annotations[:5].to_string())
 
-# Turn name_annotations into name_pairs (one pair of names per row) # TODO Actually make this a main output format?
+# Turn name_annotations into name_pairs (one pair of names per row)
 name_pairs = []
 columns = ['round', 'image', 'object', 'url', 'workerid', 'name1', 'name2', 'correct_name', 'same_object']
 for i, row in name_annotations.iterrows():
@@ -32,21 +32,19 @@ for i, row in name_annotations.iterrows():
 name_pairs = pd.DataFrame(name_pairs, columns=columns).groupby(['round', 'image', 'object', 'url', 'name1', 'name2']).mean()
 name_pairs.reset_index(level=0, inplace=True)
 
-# TODO inter-annotator agreement; name_pairs also more convenient for this
-
 print('\n-------------------')
 print("name_pairs:", len(name_pairs))
 print(name_pairs[:5].to_string())
 
 # Load manual annotations, make representations comparable/compatible
 manual_annotations = '../raw_data_phase0/verification_pilot/verif_annos_pilot.csv'
-name_pairs_amore = pd.read_csv(manual_annotations, sep="\t")
-name_pairs_amore['image'] = name_pairs_amore['url'].apply(lambda x: x.split('//')[2].split('_')[0])
-name_pairs_amore['object'] = name_pairs_amore['url'].apply(lambda x: x.split('//')[2].split('_')[1])
-name_pairs_amore['same_object'] = name_pairs_amore['same_object'].replace({'Yes': 1, 'Not sure': .5, 'No': 0})
-name_pairs_amore['correct_name'] = (3 - name_pairs_amore['correct_name']) / 3   # scale from [3,-3] to [0,2]
-name_pairs_amore.rename(columns={'mn_obj_name': 'name1', 'vg_obj_name': 'name2'}, inplace=True)
[…]

### 2019-11-12 verification_phase0/results_to_csv--complex.py
update threshold for pilot2

@@ -14,7 +14,7 @@ import os
 CONTROL_RELIABILITY_THRESHOLD = .5  # Delete control if fewer than this did it correctly
 
 # Approve/bonus assignments/workers
-ASSIGNMENT_APPROVAL_TRESHOLD = .7   # will approve any assignment with score higher than this
+ASSIGNMENT_APPROVAL_TRESHOLD = .8   # will approve any assignment with score higher than this (pilot1: 0.7)
 WORKER_APPROVAL_TRESHOLD = .85   # will approve all assignments even if a few assignments are crap
 BONUS_THRESHOLD = 1.0
 
@@ -26,8 +26,8 @@ WORKER_BLOCK_THRESHOLD = .85     # will block worker based on mean below this
 NO_REJECTION = False
 COULANCE = 1
 
-INSPECT_FAILED_CONTROLS = False
-INSPECT_REJECTED_ASSIGNMENTS = False
+INSPECT_FAILED_CONTROLS = True
+INSPECT_REJECTED_ASSIGNMENTS = True
 
 
 if NO_REJECTION:

### 2019-11-12 verification_phase0/amt_api/approve_and_reject.py
addition to reject feedback

@@ -17,7 +17,7 @@ import pandas as pd
 
 MTURK_URL = 'https://mturk-requester.us-east-1.amazonaws.com'
 
-REJECT_FEEDBACK = 'HIT is rejected because too many control items were answered incorrectly.'
+REJECT_FEEDBACK = 'HIT is rejected because too many control items were answered incorrectly, on too many HITs.'
 APPROVE_FEEDBACK = 'Thank you for working for us!'
 BONUS_AMOUNT = '0.15'
 BONUS_FEEDBACK = 'We have awarded a bonus of ${} because you did all control items perfectly.'.format(BONUS_AMOUNT)

### 2019-11-12 verification_phase0/create_amt_csv_for_verification.py
add sorted() to fix reproducibility bug

@@ -17,7 +17,7 @@ import json
 from nltk.corpus import wordnet as wn
 
 
-PHASE = "pilot" # "pre-pilot" # "round0" "round1" None
+PHASE = "round0" # "pre-pilot" # "round0" "round1" None
 IMAGES_PER_HIT = 6
 
 REMOVE_SYNONYMS = False
@@ -115,7 +115,7 @@ def main():
             vg_data = json.load(file)
         vg_dict = {img['image_id']: img for img in vg_data}
 
-        vg_names = list(set([name for img in vg_data for object in img['objects'] for name in object['names']]))
+        vg_names = sorted(list(set([name for img in vg_data for object in img['objects'] for name in object['names']])))
 
         df['quality_control_dict'] = [{} for _ in range(len(df))]
         df['n_fillers'] = [0 for _ in range(len(df))]
@@ -235,6 +235,10 @@ def main():
 
 
     df = pd.read_csv(auxpath)
+    # Set again for reproducibility, just in case the first part is skipped
+    random.seed(481727)
+    np.random.seed(567912)
+
     df['quality_control_dict'] = df['quality_control_dict'].apply(eval)
     df['names_list'] = df['names_list'].apply(eval)
     print("Auxiliary file loaded from", auxpath)
@@ -307,12 +311,13 @@ def main():
 
 
     # Now turn bins into rows of the AMT csv:
-    header = ["items"]
+    header = ["items", "quality_control"]
     rows = []
     n_controls = []
     n_controls_pos = []
     for bin in bins:
         items = []
+        quality_controls = []
         controls = 0
         controls_pos = 0
         n_names = 0
@@ -324,6 +329,7 @@ def main():
             random.shuffle(names_list)
             item.append(names_list)
             n_names += len(names_list)
+            items.append(item)
             # Obfuscate with font labels: TODO Move the obfuscation down; do more globally, separately.
             for key in df.at[idx, 'quality_control_dict']:
                 controls += 1
@@ -339,9 +345,8 @@ def main():
                 elif df.at[idx, 'quality_control_dict'][key].startswith("syn"):
                     df.at[idx, 'quality_control_dict'][key] = "bold" + df.at[idx, 'quality_control_dict'][key][3:]
             # Obfuscate further with hex encoding
-            item.append(str(df.at[idx, 'quality_control_dict']).replace("'", '"').encode('utf-8').hex())
-            items.append(item)
-        row = [items]
[…]

### 2019-11-12 verification_phase0/results_to_csv--complex.py
*sigh* MAX_IMAGES and MAX_NAMES set too low; was not showing all data

@@ -62,8 +62,8 @@ assignments_from_mturk = pd.DataFrame(assignments_from_mturk)
 assignments_from_mturk.columns = [x.lower() for x in assignments_from_mturk.columns]
 assignments_from_mturk.rename(columns={"stored_font_size": 'control_score_mturk'}, inplace=True)
 
-MAX_N_IMAGES = max([int(col.split('-')[0][3:]) for col in assignments_from_mturk.columns if col.startswith('img')])
-MAX_N_NAMES = max([int(col.split('-')[1][4:]) for col in assignments_from_mturk.columns if col.startswith('img') and col.split('-')[1].startswith('name')])
+MAX_N_IMAGES = max([int(col.split('-')[0][3:]) for col in assignments_from_mturk.columns if col.startswith('img')]) + 1
+MAX_N_NAMES = max([int(col.split('-')[1][4:]) for col in assignments_from_mturk.columns if col.startswith('img') and col.split('-')[1].startswith('name')]) + 1
 
 # Merge boolean radiobutton columns into integer-valued rating columns
 for i in range(MAX_N_IMAGES):
@@ -104,9 +104,9 @@ for i in reversed(range(MAX_N_IMAGES)): # reversed in order for names with 10 an
     columns = meta + ['items'] + [col for col in assignments_from_mturk.columns if col.startswith('img{}'.format(i))]
     df = assignments_from_mturk[columns].copy()
     df.columns = [col.replace('img{}-'.format(i), '').lower() for col in df.columns]
-    df['names'] = df['items'].apply(lambda x: x[i][1] if len(x) > i else np.nan)
+    df['names'] = df['items'].apply(lambda x: x[i][1] if len(x) > i else [])
     df['n_names'] = df['names'].apply(len)
-    df['image_url'] = df['items'].apply(lambda x: x[i][0] if len(x) > i else np.nan)
+    df['image_url'] = df['items'].apply(lambda x: x[i][0] if len(x) > i else '')
     # unobfuscate quality control
     df['quality_control'] = df['items'].apply(lambda x: json.loads(bytes.fromhex(x[i][2]).decode('utf-8')) if len(x) > i else {})
     del df['items']
@@ -185,10 +185,10 @@ name_annotations['correct2'] = np.nan
 name_annotations['correct3'] = np.nan
 name_annotations['correct3_explanation'] = ""
 for i, row in name_annotations.iterrows():
-    if row['control_type'] == 'vg_majority':
[…]

### 2019-11-12 verification_phase0/amt_api/publish.py
tiny bug fix in sleep

@@ -164,7 +164,7 @@ if __name__ == '__main__':
         logging.info("New hit groupId: " + hit_data['HIT']['HITGroupId'])
 
         # Sleepy time, now and then:.
-        if n_hits_published != total_rows-1 and ((n_hits_published + 1) % batch_size) == 0:
+        if n_hits_published != total_rows and (n_hits_published % batch_size) == 0:
             outname = os.path.join(out_path, 'created_%s_uptobatch%d.json' % (moment, batch_idx))
             with open(outname, 'w') as outfile:
                 json.dump(all_resulting_HITs, outfile)

### 2019-11-12 verification_phase0/results_to_csv--complex.py
update to deal with obfuscated quality control

@@ -34,7 +34,7 @@ if NO_REJECTION:
     print("Warning: NO_REJECTION is set to true; all assignments will be accepted.")
 
 # TODO Generalize; get paths from a config argument?
-resultsdir = '1_pre-pilot/results'
+resultsdir = '1_pre-pilot/results/round0'
 
 # TODO check overwrite
 
@@ -50,6 +50,7 @@ for filename in glob.glob(os.path.join(resultsdir, '*.json')):
                 assignment['RequesterAnnotation'] = hit['RequesterAnnotation']
                 assignment.update(hit['Params'])
                 assignment['items'] = eval(assignment['items'])
+                assignment['quality_control'] = eval(assignment['quality_control'])
                 answers = {}
                 for key in assignment['Answers']:
                     answers.update(assignment['Answers'][key])
@@ -101,14 +102,14 @@ meta = ['hitid', 'requesterannotation', 'assignmentid', 'workerid']
 image_annotations = []
 for i in reversed(range(MAX_N_IMAGES)): # reversed in order for names with 10 and 1 to not interfere.
     # columns = meta + ['image_url_{}'.format(i), 'quality_control_{}'.format(i)]
-    columns = meta + ['items'] + [col for col in assignments_from_mturk.columns if col.startswith('img{}'.format(i))]
+    columns = meta + ['items', 'quality_control'] + [col for col in assignments_from_mturk.columns if col.startswith('img{}'.format(i))]
     df = assignments_from_mturk[columns].copy()
     df.columns = [col.replace('img{}-'.format(i), '').lower() for col in df.columns]
     df['names'] = df['items'].apply(lambda x: x[i][1] if len(x) > i else [])
     df['n_names'] = df['names'].apply(len)
     df['image_url'] = df['items'].apply(lambda x: x[i][0] if len(x) > i else '')
     # unobfuscate quality control
-    df['quality_control'] = df['items'].apply(lambda x: json.loads(bytes.fromhex(x[i][2]).decode('utf-8')) if len(x) > i else {})
+    df['quality_control'] = df['quality_control'].apply(lambda x: json.loads(bytes.fromhex(x[i]).decode('utf-8')) if len(x) > i else {})
     del df['items']
     image_annotations.append(df)
 

### 2019-11-13 verification_phase0/amt_api/publish.py
uncomment qual stuff

@@ -30,27 +30,27 @@ def get_qualifications(config):
                 'Comparator': 'DoesNotExist',
                 'ActionsGuarded':'DiscoverPreviewAndAccept'})
 
-    # qlist.extend([
-    #     {'QualificationTypeId': '00000000000000000040',
-    #     'Comparator': 'GreaterThanOrEqualTo',
-    #     'IntegerValues': [
-    #         int(config['qualification']['approvedhits']),
-    #         ],
-    #     'ActionsGuarded':'PreviewAndAccept'},
-    #     {'QualificationTypeId': '000000000000000000L0',
-    #     'Comparator': 'GreaterThanOrEqualTo',
-    #     'IntegerValues': [
-    #         int(config['qualification']['approvalrate']),
-    #         ],'ActionsGuarded':'PreviewAndAccept'},
-    #     {'QualificationTypeId' : '00000000000000000071',
-    #             'Comparator' : 'In',
-    #             'LocaleValues' : [
-    #                 {'Country':'GB'}, {'Country':'US'},
-    #                 {'Country':'AU'}, {'Country':'CA'},
-    #                 {'Country':'IE'}, {'Country':'NZ'}
-    #                 ],
-    #             'ActionsGuarded': 'PreviewAndAccept'}
-    #     ])
+        qlist.extend([
+            {'QualificationTypeId': '00000000000000000040',
+            'Comparator': 'GreaterThanOrEqualTo',
+            'IntegerValues': [
+                int(config['qualification']['approvedhits']),
+                ],
+            'ActionsGuarded':'PreviewAndAccept'},
+            {'QualificationTypeId': '000000000000000000L0',
+            'Comparator': 'GreaterThanOrEqualTo',
+            'IntegerValues': [
+                int(config['qualification']['approvalrate']),
+                ],'ActionsGuarded':'PreviewAndAccept'},
+            {'QualificationTypeId' : '00000000000000000071',
+                    'Comparator' : 'In',
+                    'LocaleValues' : [
+                        {'Country':'GB'}, {'Country':'US'},
+                        {'Country':'AU'}, {'Country':'CA'},
+                        {'Country':'IE'}, {'Country':'NZ'}
+                        ],
+                    'ActionsGuarded': 'PreviewAndAccept'}
+            ])
 
     return qlist
 

### 2019-11-25 papers/EMNLP2019/relwork.tex
some changes towards the LREC submission

@@
 %but still aim to predict a single canonical category. % (that does have relations to other categories). 
-The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food, where }.
 This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).

### 2019-11-25 papers/LREC2020/analysis.tex
some changes towards the LREC submission
Section 4 - data collection polished

@@
 If we don't, we need to give an example and also say how many classes we have.
-Also, maybe rename ``\vg synsets'' instead of ``class''?}
+Also, maybe rename ``\vg synsets'' instead of ``class''?} \sz{yes, please remove the class-based analysis.
+it's probably rather confusing}
 \gbt{BEGIN PART NOT EDITED}
@@
  synonym &  1.1 &  1.1 & \it hoodie  \\
- hyponym &  2.2 &  3.8 & \it parka, blazer \\
+ hyponym &  2.2 &  3.8 & \it parka\\ %, blazer \\
  co-hyponym &  3.1 &  5.9 & \it raincoat\\
- hypernym &  10.5 &  27.7 & \it clothing, coat\\
- rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
+ hypernym &  10.5 &  27.7 & \it clothing \\%, coat\\
+ rel-not-covered &  72.2 &  58.3 & \it sweatshirt\\%, man\\
 \bottomrule
 \end{tabular}
-\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.
-\gbt{TO DO (IMPORTANT): change the rel-not-covered example to something that is true naming variation.
-I moved referential uncertainty out of the analysis of sources of variation.}}
+\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples.}
 \label{tab:rel}

### 2019-11-25 papers/LREC2020/data-collection.tex
Section 4 - data collection polished

@@
 			\toprule
-			Domain & \multicolumn{1}{c}{Synsets}\\
+			Domain & \multicolumn{1}{c}{Collection synsets}\\
 			\midrule			
+			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
+			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
 			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
                                          outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
+			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
+                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
+			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
+                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
+			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
+			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
 			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
 			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
-			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
-			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
-			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
-                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
 			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
                                          truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
-			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
-                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
-			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
-			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
 			\bottomrule
@@
 all linked to WordNet synsets \cite{fellbaum1998wordnet}.
-\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
+\vgenome (VG) suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
 As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
@@
 as basis.
-We selected images from seven domains: six based on McRae et al.'s  (\cite{mcrae2005semantic}) feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}), and \textsc{person}, because it is a very frequent category in \vg.
-% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\textsc{animals}, \textsc{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
-% We added the \textsc{person} category because it is very frequent category in \vgenome.
+We selected images from seven domains: \domain{animals\_plants}, \domain{buildings}, \domain{clothing}, \domain{food}, \domain{home}, \domain{people}, \domain{vehicles}. 
+They are all based on McRae et al.'s  \cite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
+% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\domain{animals}, \domain{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
+% We added the \domain{person} category because it is very frequent category in \vgenome.
 
-Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \textsc{home}).
-Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect our object instances from \vg.
+Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \domain{home}).
+Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.
 
@@
 For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
-\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
+%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
 
 We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
+%\gbt{from the dataframe it's 449. Also, there are some mistakes ('dugout.', 'man's').+++
 We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}).
@@
 Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds.
-This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as follows.
+This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
 Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.
-% \begin{itemize}
-% \item rows: domains (if we go for long paper: then one row per collection node?)
-% \item columns:
-%   \begin{enumerate}
-%   \item \# collection nodes
-%   \item collection nodes (list)
-%   \item \# unique VG names
-%   \item example VG names
-%   \item \# unique objects
-%   \item \# unique images (? not sure if necessary; maybe only one of unique {objects, images})
-%   \end{enumerate}
-% \end{itemize}
 
@@
 In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
-We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning the set of images via an initial collection round (9 workers per task, i.e.,\ 9 names/object) in which we allowed workers to indicate whether the object was occluded or the box unclear (see Figure~\ref{fig:instructions1} for the instructions).
+We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning images with unclear boxes or occluded objects via an initial collection round in which we allowed workers to mark such cases.
+Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which 9 workers annotated each image.
 
 %We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
-After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
+After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
 This yielded $25,596$ images (we discarded $5,497$).
-We then did 3 more collection rounds, shuffling the set of images per task between each round.
+We then did 3 more collection rounds, obtaining a total of 36 images per object.
 Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
-Workers could only participate in one round, to avoid workers annotating an instance more than once. 
-We obtained a total of 36 names per object.
+We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
 Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

### 2019-11-25 papers/LREC2020/lrec2020naming.tex
some changes towards the LREC submission
Section 4 - data collection polished

@@
 \newcommand{\cat}[1]{\textsc{#1}}
+\newcommand{\domain}[1]{\textsc{#1}}
 \newcommand{\vgenome}{VisualGenome\xspace}
@@
 
-%\title{Naming Objects in Real-world Images: A survey and A new \sz{linguistically motivated????} collection}
-\title{Object Naming: A Survey and a New Dataset}
+\title{Object Naming in Language and Vision: A Survey and a New Dataset}
 
@@
 \abstract{
-Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in computational linguistics (CL), besides task-specific modeling.
+People choose particular names for objects, such as \word{dog} or \word{puppy} for a given particular dog.
+Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics (CL).
+We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
+Our dataset, ManyNames, provides 36 name annotations for each of 25K images from VisualGenome.
+We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, at least in our setup.
+% , contrary to expectation, hierarchical variation is not the main source of 
+% Massive data collections for applications in language \& vision are nowadays available.
+In principle, these could constitute valuable resources also for research in computational linguistics (CL).
 However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
@@
 continue}
- \\ \newline \Keywords{keyword1, keyword2, keyword3} }
+ \\ \newline \Keywords{object naming, language and vision, computer vision} }
 
@@
 \section{Object Names in Existing L\&V resources}
+\label{sec:survey}
 \input{survey}
@@
 
-% \section{Acknowledgements}
+ \section{Acknowledgements}
 

### 2019-11-25 papers/LREC2020/survey.tex
Section 4 - data collection polished

@@
 We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.
-Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{+++}).
+Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
 As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to examine naming variation.
@@
 \label{tab:compare}
-\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column? Is it necessary?}}
+\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column?
+Is it necessary?} \sz{VGmn refers to the subset of images in VG that appear in MN.
+This shows that the images we selected for ManyNames also have more annotations in VG.
+I think this is useful to know.}}
 \end{table*}
@@
 \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
-How did you compute these numbers, are they for names, or whole REs?}
+How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ...
+and it nicely shows that natural names are much more variable than strict categories}
 % Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.

### 2019-11-25 papers/LREC2020/analysis.tex
Figure with MN examples modified
Analysis section polished

@@
 
-\input{analysis_table_wModelpreds}
-%\input{analysis_table}
+\input{analysis_table_lrec2020}
 
-\begin{figure*}
-\begin{minipage}[b]{0.4\linewidth}
-\includegraphics[scale=.4]{figures/types_instances.png}
-\end{minipage}
-\begin{minipage}[b]{0.6\linewidth}
-\includegraphics[scale=.4]{figures/types_classes.png}
-\end{minipage}
-\vspace{-0.8cm}
- \caption{\label{fig:ntypes} Cumulative histograms for number of types found for instances and classes, with frequency thresholds} 
-\end{figure*}
+\begin{figure}
+\includegraphics[width=\columnwidth]{figures/types_instances.png}
+ \caption{\label{fig:ntypes} Cumulative histograms for number of types in ManyNames, with frequency thresholds} 
+\end{figure}
 
-Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames.
-% with higher and lower agreement
-As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous dataset: 35.3 on average, compared to 1-3 \gbt{to revise if we keep the VGmn column.} 
+As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous dataset: 35.3 on average, compared to 1-7.
 It also contains the most variability, since objects have on average 5.7 names (compared to 1-1.9).
-This makes it in principle suitable to study how much inter-subject naming variation there is, and what factors influence such variation.
-However, data analysis shows that object identification is still an issue in our data: despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
-They typically named an adjacent object or one supported by the target object (e.g.\ \textit{jacket-toy} in Fig.~\ref{fig:ex-high-low-agreement}) or a part of the target object.
-While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated (\textit{pants-player} or \textit{bed-sleeping bag} in Fig.~\ref{fig:ex-high-low-agreement}).
+Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low agreement.
+ManyNames is in principle suitable to study how much inter-subject naming variation there is, and what factors influence such variation.
+However, data analysis shows that object identification is still an issue in our data: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+Typically, workers named an adjacent object or one supported by the target object (such as \word{toy/book} instead of \word{bed} in Fig.~\ref{fig:ex-high-low-agreement}, image K), or a part of the target object.
+While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the bounding box, as in the \word{bed/sleeping bag} case of in Fig.~\ref{fig:ex-high-low-agreement} (image L).
 Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
 Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
-In future work, we plan to filter out cases.
+In future work, we plan to filter out these cases.
 
@@
 
-\gbt{I think that we will need to remove the class-based analysis, for lack of space (plus, I think that the instance-level analysis is enough to get an idea of the data).
-For the moment I'm not doing it because I'd like to have your ok first.
-If we don't, we need to give an example and also say how many classes we have.
-Also, maybe rename ``\vg synsets'' instead of ``class''?} \sz{yes, please remove the class-based analysis.
-it's probably rather confusing}
-\gbt{BEGIN PART NOT EDITED}
-We use the following annotations for each object: (i) the original name, annotated in \vg, (ii) the object class or synset, annotated in \vg\footnote{Recall that we used these VG synsets for collecting our images (Section~\ref{ssec:sampling})},
-%and obtained via a semi-automatic linking of the object name to WordNet
- (iii) the ManyNames response set, i.e. a set of name types with annotation frequencies (max. 36 annotations per object),  see Figure \ref{fig:ex-high-low-agreement} for examples.
- % of objects and their response sets (top rows below the images).
- %[if model preds are kept]}. 
- Based on the \vg synsets, we aggregate the annotations for instances of the same class and obtain a class-level response set that contains all names and their frequencies annotated for all objects of a class.
-
-% As a first simple measure of variation in object naming, we simply count how many different names (i.e.\ types) are given to instances and to classes.
-%Since a certain amount of noise in the crowd-sourced ManyNames data can be expected, we explore different frequency thresholds (from 1 to 6) to filter the response sets.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects (left) or classes (right) have at least $n$\ names, with different frequency thresholds~$t$ to account for possible noise in the crowdsourced data.
-Without any frequency thresholding~\mbox{($t$=1)}, the proportion of instances and classes that have a single name annotated is very small, below 10\%\ in both cases.
-
-The histogram for instances in Figure\ \ref{fig:ntypes} suggests that low-frequency responses are common in ManyNames, as is expected in a free annotation task.
-% where subjects are free to choose any response. 
-When discarding these names, the %response sets for instances get more consistent such that the majority contains at most 5\ names.
-majority of the response sets become more consistent with at most 5\ names per set, 
-%Nevertheless, the proportion of objects that really only have a single name annotated is still below 50\%. %, even when applying a strict frequency filter of 4.
-but the sets with a single name still make up only $<$50\%\ of all sets. 
-This indicates that variation in naming instances is more or less restricted, but is still non-negligible. 
-%to a manageable set of up to 5\ names per object.
-
-The number of types increases substantially when aggregating responses over classes, as shown in the cumulative histogram for type counts of synsets in Figure\ \ref{fig:ntypes}\ (right).
-%Here, we observe that the 
-The rise of the curve is much less steep than for instances and, generally, there are many synsets with more than 10\ or even 20\ different name types, even after applying the frequency thresholds.
-This clearly indicates that different instances annotated with the same
-%name and 
-%\cs{(removed "name and") 
-%The synsets could have different names -- maybe say "or even same name"?}
-synset in \vg trigger different naming variants (also see examples in Figure \ref{fig:ex-high-low-agreement}). 
-Implications of this will be discussed in Section \ref{subsec:discuss}.
-
-%\cs{Change yticks to 0-100, with label \%. Make font larger in Fig. with plots?}
+Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$ to account for possible noise in the crowdsourced data.
+Without any frequency thresholding~\mbox{($t$=1)}, the proportion of instances that have a single name annotated is very small, below 10\%, and there is a long tail of datapoints with many names, up to 19.
+With a reasonable (based on data inspection) threshold of $t$=2, a bit over 20\% of the objects have one name, almost 50\% up to 3 names, and 100\% up to 8 names.
+The average number of names is 2.9, and the most frequent name accounts on average for 75\% of the responses for a given object (Table~\ref{tab:agree}, and see below).
+Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.
 
 \begin{table*}
-\footnotesize
-%\begin{tabular}{p{1.3cm}cccccc|cccccc}
-%\toprule
-% & \multicolumn{6}{c|}{Instance-level agreement} & \multicolumn{6}{c}{Class-level agreement}\\ 
-%           domain & \% top &    $H$ &    N & N$_{>1}$ & top=VG &  \% VG & \% top &    $H$ &     N & N$_{>1}$ & top=VG &  \% VG \\
-%\midrule
-%            all &  69.7 (22.2) &  1.3 &  5.7 &   2.9 &  72.8  &  58.7  &   52.6 (21.1) &  2.4 &   62.2 &  29.7 &  32.7 (46.9) &  23.5 (27.0)  \\
-% \midrule
-%         people &  51.9 (18.1) &  2.1 &  8.6 &   4.3 &         49.8 &         32.3 &     43.1 (14.9) &  2.9 &  104.4 &  53.4 &         24.4 &         13.2  \\
-% animals\_plants &  91.3 (12.9) &  0.4 &  2.7 &   1.5 &         93.8 &         88.0 &     67.9 (23.5) &  1.5 &   26.7 &  12.4 &         29.5 &         26.2  \\
-%       clothing &  63.9 (17.9) &  1.6 &  6.4 &   3.2 &         70.2 &         52.6 &     49.3 (16.6) &  2.6 &   71.7 &  34.1 &         40.5 &         26.1  \\
-%       vehicles &  72.0 (19.5) &  1.1 &  4.7 &   2.4 &         71.1 &         60.2 &    54.4 (17.4) &  2.1 &   70.4 &  33.2 &         21.4 &         21.3  \\
-%      buildings &  66.9 (20.5) &  1.5 &  6.9 &   3.0 &         72.6 &         55.5 &      46.7 (18.2) &  3.0 &   68.5 &  31.3 &         32.3 &         22.3  \\
-%           home &  66.4 (20.5) &  1.5 &  6.3 &   3.1 &         78.5 &         58.8 &     49.6 (18.7) &  2.8 &  103.2 &  48.8 &         45.9 &         30.1  \\
-%           food &  71.3 (21.1) &  1.3 &  5.5 &   2.9 &         62.9 &         52.1 &     47.3 (19.5) &  2.5 &   32.1 &  15.2 &         31.1 &         20.8  \\
-%\bottomrule
-%\end{tabular}
-
-\begin{tabular}{lccccc|ccccc}
+\centering
+%\footnotesize
+\begin{tabular}{lccccc}
   \toprule
- & \multicolumn{5}{c|}{Instance-level agreement} & \multicolumn{5}{c}{Class-level agreement}\\ 
-          domain &    N &         \%top (std) &          H (std) & top=VG &   \%VG &     N &         \%top (std) &          H (std) & top=VG &   \%VG \\
+% & \multicolumn{5}{c}{Instance-level agreement} \\
+  domain &    N &         \%top (std) &          H (std) & t=VG &   \%VG \\
   \midrule
-            all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 &  29.7 &  56.4 (21.5) &  2.0 (1.0) &   32.7 &  23.4 \\
+  all &  2.9 &  75.2 (21.9) &  0.9 (0.7) &   72.8 &  62.8 \\
   \midrule
-                     people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 &  53.4 &  47.5 (17.2) &  2.5 (0.9) &   24.4 &  13.0 \\
-       clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4 &  34.1 &  53.4 (16.6) &  2.1 (0.8) &   40.5 &  26.1 \\
-           home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 &  48.8 &  54.0 (19.4) &  2.3 (1.0) &   45.9 &  29.9 \\
-                 buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6 &  31.3 &  51.0 (18.8) &  2.4 (0.9) &   32.3 &  22.2 \\
-           food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 &  15.2 &  50.8 (20.3) &  2.0 (0.8) &   31.1 &  20.8 \\
-                  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 &  33.2 &  57.4 (17.3) &  1.8 (0.6) &   21.4 &  21.2 \\
- animals\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0 &  12.4 &  71.3 (23.3) &  1.2 (0.9) &   29.5 &  26.1 \\
+  people &  4.3 &  59.0 (20.4) &  1.5 (0.7) &   49.8 &  36.3 \\
+  clothing &  3.2 &  70.1 (18.5) &  1.1 (0.6) &   70.2 &  57.4\\
+  home &  3.1 &  72.6 (20.7) &  1.0 (0.7) &   78.5 &  64.1 \\
+  buildings &  3.0 &  74.7 (20.7) &  1.0 (0.7) &   72.6 &  61.6\\
+  food &  2.9 &  76.4 (20.7) &  0.9 (0.7) &   62.9 &  55.2 \\
+  vehicles &  2.4 &  76.6 (19.8) &  0.8 (0.6) &   71.1 &  63.9 \\
+  animal\_plants &  1.5 &  94.5 (12.1) &  0.2 (0.4) &   93.8 &  91.0\\
 \bottomrule
@@
 \vspace{-0.3cm}
-\caption{Agreement in naming measured on the level of instances and on the level of \vgenome classes (i.e.\ after grouping objects by their \vg synset), for filtered response sets (frequency threshold of 2)}
+\caption{Agreement in object naming, with a frequency threshold of 2.}
+% Domain `an\_pl' is animal\_plants.}
 \label{tab:agree}
@@
 
-\gbt{END PART NOT EDITED}
-
-To assess agreement on the object names, we check the following measures, computed with $t>1$: 
-%$t=1$: % 
+To further assess agreement on the object names, we check the following measures, computed with $t=2$, with results in Table~\ref{tab:agree}:
 \begin{itemize}
-% \setlength{\itemsep}{2pt}
-% \setlength{\parskip}{1pt}
+\item \textbf{N}: the average number of types in the response set of ManyNames.
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
 \item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
-where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. \item \textbf{N}: the average number of types in the response set of ManyNames.
-\item \textbf{top=VG}: the percentage of items where the top response in ManyNames is the \vg name.
+where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. 
+\item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
 \item \textbf{\% VG}: the average relative frequency of the \vg name in the response set.
@@
 
-Table\ \ref{tab:agree} shows, generally, that the agreement measures follow a similar pattern as the type counts in Section\ \ref{subsec:counts}:
-On the instance level, the most frequent name accounts for 75\%\  and the \vg name for 63\% of the responses on average.
-On the class level, the agreement is much lower: The average frequency of the top name drops to\ 56\% and that of the \vg name even to\ 23\%.
-The $H$ measures indicate a fair amount of agreement for instances, which is a bit lower than in picture norming studies on artificial images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55).
-On the class-level, again, an average $H$ value of 2 points to a much more even distribution of name frequencies.
+Apart from the trends mentioned above, it is remarkable that only in 73\% of the cases the most frequent response coincides with the \vg name, and the \vg name accounts for 63\% of the responses on average.
+Our dataset can be expected to yield a more robust estimate for so-called entry-point names \cite{jolicoeur1984pictures}, that is, the name that most naturally comes to mind for a given object.
+The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55), which can be expected when using real images.
 
-If we check agreement by domain, two domains stand out: the \textsc{animals,plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \textsc{people} domain with a particularly low agreement.
-%In the other domains values are around the average for the whole dataset\cs{remove because redundant?}.
-%For the other domains the $H$ value ranges around 1, and \%top is between 70\% and 80\%.
-Across domains, however, we find a large standard deviation for both \%top and $H$.
-% when averaging over all objects and within objects of the same domain \cs{redundant--it is true for each case}.
-This indicates that the agreement varies a lot across instances\cs{", which shows that there is a high variance in agreement"(?)}, over and above the class or domain\cs{??}.
-The qualitative examples in Figure \ref{fig:ex-high-low-agreement} %further corroborate this evidence: depending on the visual instance, the agreement can be very high or very low.
-illustrate this, showing visual instances with very high or low agreement. 
-These suggest that instances which are more prototypical of a category trigger higher agreement.
+If we check agreement by domain, two domains stand out: the \domain{animals\_plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \domain{people} domain with a particularly low agreement.
+Across domains, however, we find a large standard deviation for both \%top and $H$, of around 20\% for all domains except \domain{people}.
+This indicates that agreement varies quite a bit across instances, with factors that cannot be attributed to domain only.
+The qualitative examples in Figure \ref{fig:ex-high-low-agreement} illustrate this, showing visual instances with very high or low agreement.
+These suggest that instances which are more prototypical of a category trigger higher agreement, although further research is necessary to examine the relevant factors.
 The following section will examine other sources of variation in object naming.
-
-To sum up, we find both substantial consistency in naming (the most frequent name accounts for 75\% of object names, on average) and substantial naming variation (the remaining 25\%).
-Moreover, there is a very large standard variation in how much agreement there is for objects in images, that only partially depend on the domain.
-We next turn to the sources of variation.
-%and our results suggest that a large part of the factors are instance-dependent.
 
@@
 
-Previous work on object naming has assumed that variation is mostly taxonomical (see Section \ref{sec:relwork}).
-This parameter does not explain the variation in ManyNames. 
-Table \ref{tab:rel} shows the distribution of synset relations in the ManyNames responses, in terms of their type and token frequency.
-To obtain it, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names to see if they stand in a taxonomic relation to the objects' \vg  synsets.%
-\footnote{For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10; the other relations are straightforward.
+Previous work on object naming has assumed that variation is mostly taxonomical (see Section~\ref{sec:rel-work}).
+This parameter does not seem to explain the variation in ManyNames. 
+Table \ref{tab:rel} shows the distribution of the lexical relations between ManyNames responses and the original \vg annotation, estimated from WordNet.
+To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
+\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of 10; the other relations are straightforward.
 The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).}
@@
 
-We did qualitative analysis and found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
-\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{boy-batter}, \textit{dessert-toast}).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed-bench}, \textit{sandwich-hotdog}).
-\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich-basket}, \textit{bed-bed sheet}).
-\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe-dress}).
+In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
+\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{toast/dessert/breakfast}, image C).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed/bench}, \textit{sandwich/hotdog}, images J and D).
+\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich/basket}, image B).
+\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe/dress}, image not shown).
 %As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
@@
 \begin{table}[t]
-\small
+%\small
 \centering
@@
 \toprule
-         relation & \% types & \% token & \it ex: jacket \\
+         relation & \% types & \% tokens & \it ex: jacket \\
 \midrule
@@
 \end{tabular}
-\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples.}
+\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets, with examples of variants for \word{jacket}.}
 \label{tab:rel}

### 2019-11-25 papers/LREC2020/lrec2020naming.tex
intro polished

@@
 \abstract{
-People choose particular names for objects, such as \word{dog} or \word{puppy} for a given particular dog.
+People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
 Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics (CL).
 We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
-Our dataset, ManyNames, provides 36 name annotations for each of 25K images from VisualGenome.
+Our dataset, ManyNames, provides 36 name annotations for each of 25K images selected from VisualGenome.
 We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, at least in our setup.

### 2019-11-25 papers/ACL2020/acl2020_main.tex
ACL2020: first commit with rough skeleton

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{color, colortbl}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xspace}

\renewcommand{\UrlFont}{\ttfamily\small}

%\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//gbt: #1//}}}
\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
\newcommand{\mw}[1]{\textcolor{orange!60!black}{\emph{//mw: #1//}}}

% To streamline frequently used terms:
\newcommand{\mn}{ManyNames\xspace}

\title{Something with Objects and Names}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}
%\input{introduction}

\begin{itemize}
	\item Real-world objects, being members of many categories, can be called by many names. Nonetheless, humans have a preferred name which they use to call an object (CITE) (\textsl{entry-level name}). 
	\item ...
	\item ...
	\item ...
	\item We adopt an empirical view on the notion of entry-level name, and define it  as the most frequently given name by humans who were asked to name an object depicted in an image. 
	\item ...
	\item ...
	\item This paper:
	\item We address the problem of (entry-level) object naming, and use the \mn dataset that provides many name annotations per object to obtain entry-level names and their alternatives for each object instance. 
	\item Contributions are XXX:
	\item[(1)] We obtain verified name responses for each object in \mn, along with name sets of originally wrongly identified objects. 
	\item We provide an analysis of naming variation: Agreement, number of alternatives, ...
	\item[(2)] ...
\end{itemize}

\section{Related Work}
\label{sec:related}
%\input{related}

[Sectioning to be revised]

\paragraph{(Entry-Level) Object Names}
Cognitive Science/psycholinguistics:\\
- levels of specificity\\
- basic-level vs. entry-level\\
- object naming studies
Language + Vision:\\
Ordonez et al., Zarriess \& Schlangen, ... \\
- Our work: empirical notion of entry-level

\paragraph{Visual Object Recognition in Computer Vision}
- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

\section{ManyNames: Entry-Level Names and their Alternatives}
\label{sec:manynames}
\input{manynames}

\section{Experiments}
\label{sec:experiments}
%\input{experiments}
\iffalse
\cs{under construction}
\begin{itemize}
	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
	\item ... 
	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data. 
\end{itemize}
\fi

We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}

\subsection{Predicting Entry-Level Names}
\label{sect:exp_entry}
Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?

Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.  
\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model--Vocab	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & MRR & HL 
		&  =VG & =MN & $\in$MN  & KL & MRR & HL\\ 
		\midrule
		FRCNN--VG2500 & VG \\
		FRCNN--VG1600 & VG \\
		FRCNN--MN442 & VG \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features--Vocab & GTtrain  \\
		\midrule 
		FRCNN--VG1600--XX1600 & MN \\
		FRCNN--VG1600--MN442 &  MN \\
		ResNet101--VG1600 & VG \\
		ResNet101--VG1600 & MN \\
		ResNet101--MN442 & VG \\
		ResNet101--MN442 & MN \\
		\bottomrule
	\end{tabular}
	\caption{Target vocabulary in test data: MN442. Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary). GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}. MRR is mean reciprocal rank; HL is Hamming loss.\label{tab:entrylevels}. }
\end{table*}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l@{~}|rrrr}
		\toprule
		... \\
		\midrule
		Domain	 & ... \\ 
		\midrule
		All           \\
		home           \\
		food           \\
		buildings      \\
		vehicles       \\
		animals\_plants \\
		clothing       \\
		people         \\
		\bottomrule
	\end{tabular}
	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
\end{table*}

\subsection{Humans vs. Models: Which Mistakes do they Make?}
\label{sect:exp_analysis}

\paragraph{Categorisation of Errors}
see Figure\ ref{fig:mistakes}
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.\ plane vs. airplane
	\item Semantically related\\
	e.g.\  motorcycle vs. scooter
\end{enumerate}

\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
\end{figure}

\subsection{Generalization Ability: OpenImages}
\label{sect:exp_openimages}
Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\

Models compared: FRCNN--VG1600 vs. FRCNN--MN442 vs. ResNet101--XX (best Vanilla).

\section{Conclusions}
\label{sec:conclusions}

%\bibliography{BLA}
%\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

\end{document}

### 2019-11-25 papers/LREC2020/intro.tex

--- 2019-11-08 papers/LREC2020/intro.tex
@@
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} name, refer to or talk about visual objects and scenes, in contrast to predicting abstract object labels as e.g.\ in Computer Vision.
-With the recent explosion of interest in this area, a number of (massive) data collections for various language \& vision (L\&V) tasks have become available: these range from image captioning data \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, and referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, to image paragraphs \sz{cite}, multi-modal summaries or visual dialogues \cite{das2017visual,vries2017guesswhat}.
-%This typically entails that data collections and models need to account for linguistic variation, as there can hardly ever be a single ground-truth utterance when describing or referring to visual entities.
-%And indeed, variation has been accounted for in the modeling and evaluation of certain L\&V tasks like image captioning \cite{vedantam2015cider,Bernardietal:automatic,dai2017towards}.
+\sz{what do we say about the availability of the dataset?}
+Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to fixed image labeling schemes used in Computer Vision.
+Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
+For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
 
-In principle, the massive data collections now available in L\&V should not only spur computational, application-oriented research aimed at implementing systems for very specific tasks---they should also constitute extremely valuable resources for research aimed at deriving linguistic generalizations about various phenomena related to language grounding, reference and situated interaction which, for a long time, have been investigated mostly in very controlled and small-domain experimental settings, cf.
-\cite{anderson1991hcrc,fernangen:sigd07,krahmer:2012,takenobu2012rex,zarriess2016pentoref} for some examples of traditional data collections related to reference and grounding.
-In turn, these linguistic generalizations could inform computational modeling, architecture design and future data collections.
-However, so far, studies that have tested linguistic hypotheses on large-scale L\&V resources have been relatively rare.
+As compared to work on perception and language grounding in linguistics or cognitive science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
+For instance, so-called picture naming norms used in psycholinguistics typically record ``annotations'' for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+Consequently, a reliable assessment of inter-annotator agreement, speaker preferences and a deeper linguistic analysis of the observed variation is mostly out of scope with available data collections in  L\&V.
+At the same time, these data sets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories whereas picture naming norms have been collected for idealized graphical objects, as shown in Figure \ref{fig:cake}.
 
-In this paper, we take a look at object naming, a basic phenomenon that occurs in virtually every L\&V task and is, at the same time, subject of ongoing research in language grounding and pragmatics.
-\sz{explain picture naming here?} \sz{briefly say which linguistic questions/hypothesis could be investigated with respect o object naming} But despite the fact that object naming is relatively basic as a phenomenon, we observe that even corpora with massive annotation like VisualGenome~\cite[\vg henceforth]{krishna2016visualgenome} do not provide sufficient information for being able to study object names from a more linguistic perspective ...
+In this paper, we take a first step at studying natural naming of objects in real-world images.
+We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, but also the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+As a starting point, we compare three popular datasets in  L\&V: RefCOCO, a collection of referring expressions, Flickr30k, a collection of captions, and VisualGenome, which features extensive region-level annotations.
+We observe that the object name annotations in these corpora suggests that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.
 
@@
 \end{tabular}
-\caption{Names for a cake object in ManyNames (left) and in cite{snodgrass} (right), percentages of responses in parentheses.}
+\caption{Names for a cake object in ManyNames (left) and in Snodgrass's Naming Norms (right), percentages of responses in parentheses.}
 \label{fig:cake}
@@
 
-We take a first step at studying natural naming of objects in real-world images and contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
-Thus, our images show objects in complex visual contexts,
-unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that has been previously used to train object classifiers \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
+Therefore, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
+Thus, the number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V and can be used to compute agreement and related measures reliably.
+Moreover, our images show objects in complex visual contexts,
+unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} which is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
+%
 
-As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{rosch1976basic,Ordonez:2016,graf2016animal}.
+As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
 

### 2019-11-25 papers/LREC2020/background.tex
pass over related work; needs some more work (pun not intended, it's just late)

@@
 The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
-Since an object is simultaneously a member of multiple categories (e.g., a young \refexp{beagle} is at once a \cat{dog}, a \cat{beagle}, an \cat{animal}, a \cat{puppy} etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with more or less \textbf{specific names} \cite{brown1958shall,murphy2004big}.
-Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}.
-This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}.
+Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with different names \cite{brown1958shall,murphy2004big}.
+
+Seminal work on concepts by Rosch inspired a taxonomic view of object naming, in which object names typically exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
+This typically corresponds to an intermediate level of specificity, i.e., basic level (e.g., \refexp{bird}, \refexp{car}; \newcite{rosch1976basic}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).
+However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}) \cite{jolicoeur1984pictures}.
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
-%with respect to the chose level of specificity. 
-their choice of the level of specificity. 
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}.
-\cite{rohde2012communicating}\cite{graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal}\cite{clark1983common}.
+While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity.
+Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
+For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
+
+The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
+We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.
 
@@
 
-This line of research studies and models object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
-An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass}, see Figure\ \ref{fig:cake}.
+Visual object recognition studies object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
+An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category (\newcite{snodgrass}, see Figure\ \ref{fig:cake}).
 Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
 Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
-Recognition of instances (as opposed to categories) in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories, (e.g.\ \newcite{googlenet}).
-Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach. 
-%, but typically implement multi-label classifiers where relations between labels are not considered \cite{ILSVRC15}. 
-%\cs{do you mean multi-label classifiers in single ground-truth label settings?}
+
+Recognition of objects in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories (e.g.\ \newcite{googlenet}). 
+Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, and typically assume a single ground-truth label.
+% (e.g., for the young beagle case above, it would be the category \domain{beagle}).
 In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
@@
 \subsection{Hierarchical Object Categorization}
-%goes beyond isolated object categories.
-% but looks at the principles underlying the organization of object categories. 
-...
-This line of research has emphasized the taxonomic organization of categories, e.g.\ seminal work on prototypes by \newcite{rosch1976basic},  and found that humans tend to conceptualize objects at a basic or medium level of abstraction.
-Granularity-aware object recognition methods have incorporated the taxonomic structure underlying object labels in multi-label settings \cite{deng2014large,wang2014poodle,peterson2018learning}, as an account to the criticism on the use of single-labels.
-%While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, 
-%but still aim to predict a single canonical category. % (that does have relations to other categories). 
-The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
-This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
-To the best of our knowledge, this phenomenon has not received any attention in L\&V.
-Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
+
+Some work in L\&V \cite{deng2014large,wang2014poodle,peterson2018learning} criticizes the use of single labels for object naming and categorization.
+This line of research has emphasized the taxonomic organization of categories, following the seminal work on prototypes by \newcite{rosch1976basic} mentioned above.
+These works propose granularity-aware object recognition methods, that incorporate the taxonomic structure underlying object labels in multi-label settings; for the ``young beagle'' example, labels \word{beagle}, \word{dog}, \word{animal} would all be considered valid.
+Instead, other sources of variation like cross-classification have not received attention in L\&V.
+As mentioned above, our results suggest that cross-classification occurs very frequently when naming objects in real-world images.
 
@@
 
-... work that models which \textit{word} (i.e.\ not label) a speaker will use to name an object is relatively scarce.
-Though names are prominent in referring expressions, investigated a lot in natural language generation \cite{dale:1995}, this area has focused mostly on the selection of attributes % rather than on determining the referent's name
-\cite{krahmer:2012}. 
-\newcite{Ordonez:2016} takes up the notion of entry-level categories \cite{rosch1976basic} and transfers an object's predicted fine-grained label to its name using text corpus statistics.
-% extend object recognition to naming, taking up the notion of entry-level categories \cite{rosch1976basic}.
-%Their model predicts classifies objects into fine-grained categories and then predicts a WordNet synset for retrieving the name, based on frequencies in a text corpus. 
+Work that models which \textbf{word} (as opposed to a category label) a speaker will use to name an object is relatively scarce.
+Natural language generation has intensively investigated referring expressions~\cite{dale:1995,krahmer:2012}; however, this area has focused mostly on the selection of attributes, typically assuming that the name is given.
+\gbt{Add example}
+\newcite{Ordonez:2016} takes up the notion of entry-level categories and transfers an object's predicted label to its name.
+Their model classifies objects into fine-grained categories (\gbt{e.g., ++++++ }), and then predicts a WordNet synset to retrieve the name (e.g., \word{swan}), based on frequencies in a text corpus.
+This work assumes that \gbt{+++++complete please, stating what's different to ours}
  \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
+\gbt{I don't understand how this differs from other research and our own.}
 Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
-\cite{rohde2012communicating,graf2016animal}. Our work is a first step towards studying naming in real-world, natural reference.
-But as there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
+\cite{rohde2012communicating,graf2016animal}. 
+However, this work studies a very limited set of images \gbt{+++++complete please, stating what's different to ours}
+Our work is a first step towards studying naming in real-world, natural reference.
+As there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
 

### 2019-11-25 papers/LREC2020/background.tex
survey section polished except for a few remaining questions

@@
 
+\begin{table*}[htb]
+  \centering
+  \begin{tabular}{lrrrrr}
+    \toprule
+    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
+    \midrule
+    \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
+    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
+    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
+    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.1 &      0.9 \\
+    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
+    \bottomrule
+  \end{tabular}
+  \label{tab:compare}
+  \caption{Overview statistics for different data sets containing object naming data.
+VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.
+\gbt{What is the VGmn column?
+Is it necessary?} \sz{VGmn refers to the subset of images in VG that appear in MN.
+This shows that the images we selected for ManyNames also have more annotations in VG.
+I think this is useful to know.} \gbt{ok!
+We'll need to explain why the number of objects not identical.}}
+\end{table*}
+
 \subsection{Hierarchical Object Categorization}

### 2019-11-25 papers/LREC2020/survey.tex
Analysis section polished
survey section polished except for a few remaining questions

--- 2019-11-08 papers/LREC2020/survey.tex
@@
-We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.
-Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{+++}).
-As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to examine naming variation.
-This motivates our data collection, in which we collect 36 names per object.
-Still, because these datasets can be useful to examine other aspects of object naming, and we summarize their characteristics below.
-
-\begin{table*}
-\centering
-\begin{tabular}{lrrrrr}
-\toprule
-  &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
-\midrule
-                  \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
-                naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
-     av. annotations/object &      2.84 &       2.30 &         1.69 &      7.24 &     35.30 \\
- \% objects with n types $>$ 1 &      0.68 &       0.29 &         0.02 &      0.05 &      0.93 \\
-           av. types/object &      1.88 &       1.38 &         1.02 &      1.08 &      5.70 \\
-\bottomrule
-\end{tabular}
-\label{tab:compare}
-\caption{Overview statistics for different data sets containing object naming data \gbt{What is the VGmn column? Is it necessary?}}
-\end{table*}
+We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.%
+\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
+Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
+As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual instances.
+This motivates our data collection. %, in which we collect 36 names per object.
+However, because these datasets can be useful to examine other aspects of object naming, we summarize their characteristics below.
 
@@
 REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
-\gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
-How did you compute these numbers, are they for names, or whole REs?}
+ % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
+How did you compute these numbers, are they for names, or whole REs?} \sz{well, 80 categories doesn't mean much as the categories can be very general (like "human") ...
+and it nicely shows that natural names are much more variable than strict categories}
 % Another critical property of the data is that, (iii), not all objects in an image were annotated with REs, may it due to the frequency constraint~(i), or due to the object not being part of the 80 COCO categories.
@@
 We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors.
-Multiple annotations (2.84 on average) allow for some minimal analysis of naming variation in this setup. 
-However, note that not all objects are annotated with REs and corresponding categories, so it may be difficult to analyze the data with automatic processing.
+Moreover, multiple annotations (2.84 on average) allow for some minimal analysis of naming variation.
+However, note that not all objects are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
 Names elicited in \refcoco should be natural, but it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
 Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
-To sum up, we would recommend \RefCOCO to study effect of distractors on object naming in a restricted set of categories.
+To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.
 
@@
 
-This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were no subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size).
-\gbt{Any idea what kind of categories are covered in \flickr?}
-Moreover, although no exhaustive annotations of the image is available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
+This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size).
+%\gbt{Any idea what kind of categories are covered in \flickr?}
+Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
 The number of annotations per object, 2.3 annotations, is comparable to \refcoco.
@@
 \subsection{Visual Genome}
+
+\vgenome \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
+%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
+%\paragraph{Collection and annotation procedure}
+\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
+The data collection followed a complex procedure, involving many different rounds of annotation.
+The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).
+
+In a second, independent round (involving new workers), annotators were asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
+As different region descriptions can potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select an existing object rather than annotating a new one.
+
+\gbt{@Sina, pls check that I got this right:}
+One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
+Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+This should make it easier to identify factors intervening in naming choices.
+However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
+Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
+This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.
+
+\subsection{Discussion}
+
+As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object?
+How much variation is there, for specific instances?
+What factors affect this variation?
+How does that impact modeling in L\&V?
+To answer these sorts of questions, we need naming data from many subjects for the same instances.
+This is the motivation for our dataset, ManyNames, an augmentation of \vg.
 
@@
 
-\vg \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V; below, we focus on aspects immediately relevant to object naming.
-%In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
-%\paragraph{Collection and annotation procedure}
-\vg aims at providing a full set of descriptions of the scenes which images depict in order to spur complete scene understanding. 
-The data collection followed a complex procedure, involving many different rounds of annotation.
-The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).
-
-In a second, independent round (involving new workers), annotators were asked to process the region descriptions by (i) marking the object names contained in the region description, and (ii) drawing a tight box around the corresponding region.
-As different region descriptions can potentially mention the same objects, each worker was shown a list of previously marked objects and encouraged to select on existing object rather than annotating a new one.
-
-\gbt{@Sina, pls check that I got this right:}
-One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
-Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
-This should make it easier to identify factors intervening in naming choices.
-However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
-Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
-This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the annotations.
-
-\subsection{Discussion}
-
-\gbt{Do we need a discussion section wrapping up what we've said in this survey section and motivating MN?}
-
 %%% Local Variables:

### 2019-11-26 papers/LREC2020/background.tex
cleaned up the background section (LREC paper), more focus on data sets, less stuff on modeling

@@
 
-Seminal work on concepts by Rosch inspired a taxonomic view of object naming, in which object names typically exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
-This typically corresponds to an intermediate level of specificity, i.e., basic level (e.g., \refexp{bird}, \refexp{car}; \newcite{rosch1976basic}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).
+Seminal work on concepts by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
+This typically corresponds to an intermediate level of specificity, i.e., basic level (e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).
 However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}) \cite{jolicoeur1984pictures}.
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity.
-Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is more informative and potentially preferred by speakers, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
-
+While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
+%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
+For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
+%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
 The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
@@
 
-\subsection{Visual Object Recognition}
+\subsection{Picture Naming in Cognitive Science}
 
-Visual object recognition studies object representations in the human visual system, (cf.\ \newcite{regan2000human,rossion2004revisiting}). 
-An important experimental paradigm here is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category (\newcite{snodgrass}, see Figure\ \ref{fig:cake}).
+An important experimental paradigm in work on human vision and categorization is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass,rossion2004revisiting}, see Figure\ \ref{fig:cake}.
 Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
@@
 
-Recognition of objects in images has also been the focus of Computer Vision, where state-of-the-art systems are now able to predict thousands of different categories (e.g.\ \newcite{googlenet}). 
-Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, and typically assume a single ground-truth label.
-% (e.g., for the young beagle case above, it would be the category \domain{beagle}).
-In L\&V, deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly.
-For instance, many labels in the ILSVRC  challenge \cite{ILSVRC15} correspond to very specific breeds of animals, whereas other common categories for,\ e.g.,\ people are missing.
+\subsection{Object Recognition in Computer Vision}
+
+In Computer Vision, object recognition is typically modelled as a classification task where objects need to be categorized according to a given labeling scheme that can comprise thousands of different categories in state-of-the-art systems \cite{googlenet,ILSVRC15}.
+Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} taxonomy, and typically assume a single ground-truth label. 
+The construction of ImageNet was set up as a two-stage procedure: (i) images for given nodes in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
+Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
+Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
+Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.
+
+\subsection{Object Naming in L\&V}
+
+In contrast to work on object recognition, work in L\&V typically collects and uses data sets where annotators produce free and natural utterances for a given image. 
+Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}.
+While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions.
+The overview in the following Section \ref{sec:survey} will focus on corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
+
+Our new collection, ManyNames, presented in Section \ref{sec:data} focusses on object names in in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in in L\&V.
+This controlled collection procedure, however, allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.
 
@@
 
-\subsection{Hierarchical Object Categorization}
-
-Some work in L\&V \cite{deng2014large,wang2014poodle,peterson2018learning} criticizes the use of single labels for object naming and categorization.
-This line of research has emphasized the taxonomic organization of categories, following the seminal work on prototypes by \newcite{rosch1976basic} mentioned above.
-These works propose granularity-aware object recognition methods, that incorporate the taxonomic structure underlying object labels in multi-label settings; for the ``young beagle'' example, labels \word{beagle}, \word{dog}, \word{animal} would all be considered valid.
-Instead, other sources of variation like cross-classification have not received attention in L\&V.
-As mentioned above, our results suggest that cross-classification occurs very frequently when naming objects in real-world images.
-
-\subsection{Object Naming in L\&V}
-
-Work that models which \textbf{word} (as opposed to a category label) a speaker will use to name an object is relatively scarce.
-Natural language generation has intensively investigated referring expressions~\cite{dale:1995,krahmer:2012}; however, this area has focused mostly on the selection of attributes, typically assuming that the name is given.
-\gbt{Add example}
-\newcite{Ordonez:2016} takes up the notion of entry-level categories and transfers an object's predicted label to its name.
-Their model classifies objects into fine-grained categories (\gbt{e.g., ++++++ }), and then predicts a WordNet synset to retrieve the name (e.g., \word{swan}), based on frequencies in a text corpus.
-This work assumes that \gbt{+++++complete please, stating what's different to ours}
- \newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
-\gbt{I don't understand how this differs from other research and our own.}
-Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
-\cite{rohde2012communicating,graf2016animal}. 
-However, this work studies a very limited set of images \gbt{+++++complete please, stating what's different to ours}
-Our work is a first step towards studying naming in real-world, natural reference.
-As there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
+%Work that models which \textbf{word} (as opposed to a category label) a speaker will use to name an object is relatively scarce.
+%Natural language generation has intensively investigated referring expressions~\cite{dale:1995,krahmer:2012}; however, this area has focused mostly on the selection of attributes, typically assuming that the name is given.
+%\gbt{Add example}
+%\newcite{Ordonez:2016} takes up the notion of entry-level categories and transfers an object's predicted label to its name.
+%Their model classifies objects into fine-grained categories (\gbt{e.g., ++++++ }), and then predicts a WordNet synset to retrieve the name (e.g., \word{swan}), based on frequencies in a text corpus.
+%This work assumes that \gbt{+++++complete please, stating what's different to ours}
+ %\newcite{zarriess-schlangen:2017} learn a naming model on referring expressions and real-world images, but focus on combining visual and distributional information. 
+%\gbt{I don't understand how this differs from other research and our own.}
+%Recent experimental work on reference found that the specificity of a name is dependent on the taxonomic relatedness of other objects in context
+%\cite{rohde2012communicating,graf2016animal}. 
+%However, this work studies a very limited set of images \gbt{+++++complete please, stating what's different to ours}
+%Our work is a first step towards studying naming in real-world, natural reference.
+%As there is virtually no existing large-scale resource that provides robust naming data elicited from multiple subjects \textit{and} for instances in real-world images, this paper focuses on naming in isolation, rather than reference where naming interacts with attribute selection.
+%
+%
+%
+%This line of research has emphasized the taxonomic organization of categories, following the seminal work on prototypes by \newcite{rosch1976basic} mentioned above.
+%These works propose granularity-aware object recognition methods, that incorporate the taxonomic structure underlying object labels in multi-label settings; for the ``young beagle'' example, labels \word{beagle}, \word{dog}, \word{animal} would all be considered valid.
+%Instead, other sources of variation like cross-classification have not received attention in L\&V.
+%As mentioned above, our results suggest that cross-classification occurs very frequently when naming objects in real-world images.
 

### 2019-11-26 papers/LREC2020/survey.tex
cleaned up the background section (LREC paper), more focus on data sets, less stuff on modeling

@@
 We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.%
-\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
+%\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
+% footnote not necessary! this is explained in the background section
 Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).

### 2019-11-26 papers/ACL2020/manynames.tex

\cs{@gbt @mw}
\subsection{Overview of ManyNames}
\label{sect:mn_overview}

\subsection{Verification of Annotations}
\label{sect:mn_verification}

\subsection{Analysis}
\label{sect:mn_analysis}
\paragraph{Of ManyNames:} 
\cs{+ @sz?}\\
\cs{Here goes what has not been discussed in LREC paper, because it focusses on entry-level names. }
\cs{Results aimed to show that we need \underline{multiple} annotations per object \underline{instance} to get the entry-level name}
\begin{itemize}
	\item Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)
	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs. 1 vs. 2 vs. 3). (i.e.,\ entry-level names cannot be derived from a few annotators)
	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz}
	\item ...
\end{itemize}

\paragraph{Of Verification Annotations}
\cs{@gbt @mw}
\begin{itemize}
	\item ...
	\item ...
	\item For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering).
\end{itemize}

### 2019-11-26 papers/LREC2020/lrec2020naming.tex
added authors to LREC paper

@@
 
-\name{Author1, Author2, Author3}
+\name{Carina Silberer, Sina Zarrie\ss, Gemma Boleda}
 
-\address{Affiliation1, Affiliation2, Affiliation3 \\
-         Address1, Address2, Address3 \\
-         author1@xxx.yy, author2@zzz.edu, author3@hhh.com\\
-         \{author1, author5, author9\}@abc.org\\}
+\address{Universitat Pompeu Fabra, University of Jena, Universitat Pompeu Fabra \\
+         Barcelona (Spain), Jena (Germany), Barcelona (Spain) \\
+         sina.zarriess@uni-jena.de\\
+         \{carina.silberer, gemma.boleda\}@upf.edu\\}
 

### 2019-11-26 verification_phase0/merge_and_clean_csv.py
add reliability filter; inspection of single worker's errors

@@ -89,6 +89,23 @@ if os.path.exists(out_path) and input("Recompute & overwrite merged csv files? y
 
 
 annotations_all = pd.read_csv(os.path.join(out_path, 'name_annotations_ANON.csv'), converters={'name_cluster-nofillers': eval, 'name_cluster': eval, 'same_object': eval})
+
+UNRELIABLE_WORKER_THRESHOLD = 0.9
+UNRELIABLE_ASSIGNMENT_TRESHOLD = 0.7
+
+assignments = pd.read_csv(os.path.join(out_path, 'per_assignment_ANON.csv'), converters={'mistakes': eval})
+
+per_worker = assignments.groupby('workerid').agg({'control_score-filtered': 'mean'}).reset_index()
+unreliable_workers = per_worker.loc[per_worker['control_score-filtered'] < UNRELIABLE_WORKER_THRESHOLD]['workerid']
+
+unreliable_assignments = assignments.loc[(assignments['control_score-filtered'] < UNRELIABLE_ASSIGNMENT_TRESHOLD) | (assignments['workerid'].isin(unreliable_workers))]['assignmentid']
+
+print("Workers: {}; unreliable: {}".format(len(per_worker), len(unreliable_workers)))
+print("Assignments: {}; unreliable: {}".format(len(assignments), len(unreliable_assignments)))
+
+if True:
+    annotations_all = annotations_all.loc[~annotations_all['assignmentid'].isin(unreliable_assignments)]
+
 annotations_targets = annotations_all.loc[annotations_all['control_type'].isna() | (annotations_all['control_type'] == 'vg_majority') | (annotations_all['control_type'].apply(lambda x: isinstance(x, str) and x.startswith('syn')))]
 
 print("\n-------------")
@@ -111,10 +128,29 @@ print("-------------")
 # Compute how many names are adequate that are NOT in the same cluster
 
 
+if False:
+    # Inspect workers who requester feedback:
+    print()
+    print("Workers to pay attention to:")
+    PAY_ATTENTION_TO_WORKERS = ['AO33H4GL9KZX9']
+    by_selected_workers = assignments.loc[assignments['workerid'].isin(PAY_ATTENTION_TO_WORKERS)].sort_values(by='workerid')
+    prev_worker = ""
+    for i, row in by_selected_workers.iterrows():
+        if row['workerid'] != prev_worker:
+            print("== {} ==".format(row['workerid']))
+            prev_worker = row['workerid']
[…]

### 2019-11-28 verification_phase0/amt_api/publish.py
allow specifying max assignments for publishing in data csv

@@ -63,7 +63,7 @@ def get_qualifications(config):
     return qlist
 
 
-def create_new_hit(mturk, config, hit_params, hit_quals, annotation):
+def create_new_hit(mturk, config, hit_params, max_assignments, hit_quals, annotation):
     new_hit = mturk.create_hit(
         HITLayoutId=config['layout']['id'],
         HITLayoutParameters=hit_params,
@@ -73,7 +73,7 @@ def create_new_hit(mturk, config, hit_params, hit_quals, annotation):
         LifetimeInSeconds=eval(config['hit']['lifetime']),
         Keywords=config['hit']['keywords'],
         AssignmentDurationInSeconds=eval(config['hit']['assignmentduration']),
-        MaxAssignments=int(config['hit']['maxassignments']),
+        MaxAssignments=max_assignments,
         QualificationRequirements=hit_quals,
         RequesterAnnotation=annotation,
     )
@@ -154,12 +154,16 @@ if __name__ == '__main__':
 
     batch_idx = initial_row / batch_size    # TODO Not quite right.
 
+    max_assignments = int(config['hit']['maxassignments'])  # Potentially overriden by data csv
+    if 'source' in data.columns:
+        input("Warning: max_assignments from config will be overriden by assignments column from data csv (enter to continue)")
+
     ## Loop through all data rows from starting index, creating HITs, sleep after every batch size
     n_hits_published = 0
     for row_idx, row in data[initial_row:initial_row+total_rows].iterrows():
         logging.info("Batch {}, HIT {}".format(batch_idx, row_idx))
 
-        param_list = [{'Name': key, 'Value': str(value)} for key, value in row.to_dict().items()]
+        param_list = [{'Name': key, 'Value': str(value)} for key, value in row.to_dict().items() if key not in ['source', 'assignments']]
 
         # Add unique turker id, or else empty string
         unique_turker_id = config["qualification"]["unique_turker_id"] if "unique_turker_id" in config["qualification"] else ""
@@ -167,7 +171,14 @@ if __name__ == '__main__':
         param_list = [{'Name': 'unique_turker_id', 'Value': unique_turker_id}, {'Name': 'unique_turker_limit', 'Value': unique_turker_limit}] + param_list
         logging.info(param_list)
 
-        hit_data = create_new_hit(mturk, config, param_list, qualifications, config['data']['csvfile'] + '_' + str(row_idx))
+        if 'assignments' in data.columns:
+            max_assignments = row['assignments']
[…]

### 2019-11-28 verification_phase0/merge_and_clean_csv.py
output HITs-to-be-redone to a csv

@@ -98,13 +98,49 @@ assignments = pd.read_csv(os.path.join(out_path, 'per_assignment_ANON.csv'), con
 per_worker = assignments.groupby('workerid').agg({'control_score-filtered': 'mean'}).reset_index()
 unreliable_workers = per_worker.loc[per_worker['control_score-filtered'] < UNRELIABLE_WORKER_THRESHOLD]['workerid']
 
-unreliable_assignments = assignments.loc[(assignments['control_score-filtered'] < UNRELIABLE_ASSIGNMENT_TRESHOLD) | (assignments['workerid'].isin(unreliable_workers))]['assignmentid']
+assignments['reliable'] = (assignments['control_score-filtered'] >= UNRELIABLE_ASSIGNMENT_TRESHOLD) & ~(assignments['workerid'].isin(unreliable_workers))
 
 print("Workers: {}; unreliable: {}".format(len(per_worker), len(unreliable_workers)))
-print("Assignments: {}; unreliable: {}".format(len(assignments), len(unreliable_assignments)))
+print("Assignments: {}; unreliable: {}".format(len(assignments), len(assignments.loc[~assignments['reliable']])))
 
-if True:
-    annotations_all = annotations_all.loc[~annotations_all['assignmentid'].isin(unreliable_assignments)]
+if False:
+    annotations_all = annotations_all.loc[assignments['reliable']]
+
+coverage = assignments.loc[assignments['reliable']].groupby('source').agg({'assignmentid': 'count'})
+for i in range(1047):
+    src = '../1_pre-pilot/verification_round0_amt.csv_{}'.format(i)
+    if src not in coverage.index:
+        coverage[src]['assignmentid'] = 0
+for i in range(292):
+    src = '../1_pre-pilot/verification_round1_amt.csv_{}'.format(i)
+    if src not in coverage.index:
+        coverage[src]['assignmentid'] = 0
+for i in range(1713):
+    src = '../1_pre-pilot/verification_round2_amt.csv_{}'.format(i)
+    if src not in coverage.index:
+        coverage[src]['assignmentid'] = 0
+coverage['missing'] = coverage['assignmentid'].apply(lambda x: 0 if x >= 3 else 3-x)
+print("MISSING:", coverage['missing'].sum())
+
+round0_amt = pd.read_csv('1_crowdsourced/verification_round0_amt.csv', sep=",", keep_default_na=False)
[…]

### 2019-11-28 papers/LREC2020/background.tex

@@
     \midrule
-    \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
+    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
     naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
     av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
-    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.1 &      0.9 \\
+    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
     av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
@@
   \label{tab:compare}
-  \caption{Overview statistics for different data sets containing object naming data.
-VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.
-\gbt{What is the VGmn column?
-Is it necessary?} \sz{VGmn refers to the subset of images in VG that appear in MN.
-This shows that the images we selected for ManyNames also have more annotations in VG.
-I think this is useful to know.} \gbt{ok!
-We'll need to explain why the number of objects not identical.}}
+  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.}
 \end{table*}

### 2019-11-28 papers/LREC2020/conclusion.tex
Analysis section polished

@@
-The question of how people choose names for objects presented visually is relevant for Computational Linguistics (especially Language \& Vision), Computer Vision, Cognitive Science, and Linguistics.
-% The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
-We have surveyed datasets that can be useful to address this question, and proposed a new dataset, ManyNames, that affords new possibilities, both for analysis and modeling, providing a means
-(i) to study how different people would name the same object (image region), and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and
-(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
+% To sum up, we find both substantial consistency in naming (the most frequent name accounts for 75\% of object names, on average) and substantial naming variation (the remaining 25\%).
+Moreover, there is a very large standard variation in how much agreement there is for objects in images, that only partially depend on the domain.
 
-\gbt{The following needs to be made more coherent}
-For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which affects model performance on object categorization and naming.
-Crucially, evaluations in these task assume that object identification is possible based on the bounding box, and evaluates only the categories or names of objects assuming they are unique.
-The naming variation we have found also challenge the common assumption that there exists a single canonical name for individual visual objects (also see \cite{deng2014large,wang2014poodle,peterson2018learning}).
-At the same time, the ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
-Our data allows models to be tested wrt their ability to account for naming variants of an instance: For instance, to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet} vs.
-\textsl{dog, hat, grass}).
-\gbt{We have to be careful; without the correction round this is not strictly speaking true. How can we phrase this?}
+The question of how people choose names for objects presented visually is relevant for Language and Vision, Computational Linguistics, Computer Vision, Cognitive Science, and Linguistics.
+We have surveyed datasets that can be useful to address this question, and proposed a new dataset, ManyNames, that affords new possibilities both for analysis and modeling of object naming.
+% gbt: commenting the following out cause it's a bit dangerous to say this without the verification phase.
+% , providing a means
+% (i) to study how different people would name the same object (image region), and, given a specific name, estimate how likely people are to use it for a given object, which might vary substantially across different instances of a given category, and
+% (ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.
+
+For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
+Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
+Our data suggests that this is not always the case and provides empirical data to for instance asses whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
+% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).
+
+Moreover, standard evaluations assume that object names (or categories) are unique.
+% The naming variation we have found also challenge the common assumption that there exists a single canonical name for individual visual objects (also see \cite{deng2014large,wang2014poodle,peterson2018learning}).
+The ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
+Our data provides a first step towards enabling model evaluation on naming variants of an instance, checking for instance to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet}) or not (\textsl{dog, hat, grass}).
+However, to fully enable this sort of analysis, a further annotation step is needed, to account for the referential uncertainty of bounding boxes and annotation noise.
+We plan to take this step in future work, which will also enable more robust conclusions with respect to naming variation.
+
 % Wang et al.: ".
@@
 
-\gbt{Make the following coherent with the previous paragraph}
-Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization.
-However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain.
+Our current data clearly supports the prediction in theoretical research on object naming and categorization that there will in general be a preferred name for a given visually presented object.
+It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches; (c) there is high variability in agreement across instances within the same domain.
 The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.
-With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
-We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches.
+With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.
+
+We hope that ManyNames triggers more empirical research on object naming, a topic that has been understudied in both computational and theoretical approaches to language.
 

### 2019-11-28 papers/LREC2020/data-collection.tex
Figure with MN examples modified
Analysis section polished

@@
 	\end{tabular}
-	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
-		\label{tab:overview_dataset1}}
+	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses).\label{tab:overview_dataset1}}
 \end{table*}
@@
   \centering
-  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
-  \caption{Instructions for AMT annotators for the first round.}
+  \includegraphics[width=1.5\columnwidth]{figures/round0_cropped.png}
+  \caption{Instructions for AMT annotators for the first round (whole instructions showed more examples, see Figure~\ref{fig:instructions2}).}
   \label{fig:instructions1}
@@
 We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
-%\gbt{from the dataframe it's 449. Also, there are some mistakes ('dugout.', 'man's').+++
+\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
 We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}).

### 2019-11-28 papers/LREC2020/intro.tex

@@
-\sz{what do we say about the availability of the dataset?}
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to fixed image labeling schemes used in Computer Vision.
+Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
 Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
@@
 
-As compared to work on perception and language grounding in linguistics or cognitive science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
-For instance, so-called picture naming norms used in psycholinguistics typically record ``annotations'' for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+As compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
+For instance, so-called picture naming norms used in Psycholinguistics typically record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
 Consequently, a reliable assessment of inter-annotator agreement, speaker preferences and a deeper linguistic analysis of the observed variation is mostly out of scope with available data collections in  L\&V.
-At the same time, these data sets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories whereas picture naming norms have been collected for idealized graphical objects, as shown in Figure \ref{fig:cake}.
+At the same time, these datasets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories, compared to the idealized drawings used in picture naming norms, as shown in Figure \ref{fig:cake}.
 
-In this paper, we take a first step at studying natural naming of objects in real-world images.
-We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, but also the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
-As a starting point, we compare three popular datasets in  L\&V: RefCOCO, a collection of referring expressions, Flickr30k, a collection of captions, and VisualGenome, which features extensive region-level annotations.
-We observe that the object name annotations in these corpora suggests that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.
+In this paper, we take a first step towards building a dataset with object naming data for real-world images.
+We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+As a starting point, we compare three popular datasets in L\&V: \refcoco, a collection of referring expressions, \flickr, a collection of captions, and \vgenome, which features extensive region-level annotations.
+We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.
 
@@
 
-Therefore, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg.
-Thus, the number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V and can be used to compute agreement and related measures reliably.
+To address this shortcoming, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vgenome.%
+\footnote{The dataset will be available upon publication.}
+The number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V.
 Moreover, our images show objects in complex visual contexts,
-unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} which is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
-%
+unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
 
-As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
 

### 2019-11-29 verification_phase0/merge_and_clean_csv.py
ugly insert for adding redone batch, removing unreliable rows from older batches

@@ -6,13 +6,29 @@ from collections import Counter
 
 
 BATCHES = [1,2,3,4,5,6,7,8]
+REDONE = ['redone']
 out_path = '1_crowdsourced/results/merged_{}'.format('-'.join([str(x) for x in BATCHES]))
+if len(REDONE) > 0:
+    out_path += '_{}'.format('-'.join(REDONE))
+
+write_csv = not os.path.exists(out_path) or input("Recompute & overwrite merged csv files? y/N").lower().startswith('y')
+
 os.makedirs(out_path, exist_ok=True)
+BATCHES = ['batch{}'.format(i) for i in BATCHES] + REDONE
 
-if os.path.exists(out_path) and input("Recompute & overwrite merged csv files? y/N").lower().startswith('y'):
+# For computing which assignments to redo:
+if len(REDONE) == 0:
+    UNRELIABLE_WORKER_THRESHOLD = 0.9
+    UNRELIABLE_ASSIGNMENT_TRESHOLD = 0.7
+# For actually deleting rows (less strict):
+else:
+    UNRELIABLE_WORKER_THRESHOLD = 0.5
+    UNRELIABLE_ASSIGNMENT_TRESHOLD = 0.6
 
-    name_annotations_paths = [(i, '1_crowdsourced/results/batch{}/name_annotations.csv'.format(i)) for i in BATCHES]
-    assignments_paths = [(i, '1_crowdsourced/results/batch{}/per_assignment.csv'.format(i)) for i in BATCHES]
+if write_csv:
+
+    name_annotations_paths = [(i, '1_crowdsourced/results/{}/name_annotations.csv'.format(i)) for i in BATCHES]
+    assignments_paths = [(i, '1_crowdsourced/results/{}/per_assignment.csv'.format(i)) for i in BATCHES]
 
     print("Merging dataframes...")
 
@@ -89,10 +105,6 @@ if os.path.exists(out_path) and input("Recompute & overwrite merged csv files? y
 
 
 annotations_all = pd.read_csv(os.path.join(out_path, 'name_annotations_ANON.csv'), converters={'name_cluster-nofillers': eval, 'name_cluster': eval, 'same_object': eval})
-
-UNRELIABLE_WORKER_THRESHOLD = 0.9
-UNRELIABLE_ASSIGNMENT_TRESHOLD = 0.7
-
[…]

### 2019-11-29 papers/LREC2020/intro.tex
LREC2020: adds comments Sect.1-3

@@
 Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
-Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
+Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily \cs{necessarily???
+\ra inherently?
+naturally?} results in linguistic variation.
 For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
@@
 We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
-As a starting point, we compare three popular datasets in L\&V: \refcoco, a collection of referring expressions, \flickr, a collection of captions, and \vgenome, which features extensive region-level annotations.
-We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.
+As a starting point, we compare three popular datasets in L\&V: \refcoco \cs{CITE}, a collection of referring expressions, \flickr \cs{CITE}, a collection of captions\cs{no, Flickr30K is a collection of captions, F Entities \ra of region-to-phrase linkings for image captions}, and \vgenome \cs{CITE -- at least VisualGenome should be cited}, which features extensive region-level annotations.
+We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or linguistic analysis.
 
@@
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \cs{explain basic-level, and if only with a reference or in a footnote} \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic (i.e.,\ hierarchical) relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
 

### 2019-11-29 papers/LREC2020/lrec2020naming.tex
LREC2020: adds comments Sect.1-3

@@
 \usepackage{xcolor}
+
+\usepackage{microtype}
 
@@
 People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
-Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics (CL).
+Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
 We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
-Our dataset, ManyNames, provides 36 name annotations for each of 25K images selected from VisualGenome.
-We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, at least in our setup.
+Our dataset, ManyNames, provides 36 name annotations for each of 25K images\cs{objects} selected from VisualGenome.
+We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
 % , contrary to expectation, hierarchical variation is not the main source of 
@@
 
+\cs{maybe streamline use of (i),(ii),... and (1),(2),...}
 \section{Introduction}

### 2019-11-29 proc_data_phase0/verification/insert_verification_column.py
and all_responses_round0-3_verified.csv and script that created it

@@ -1,0 +1,94 @@
+from analysis import load_results
+import os
+import pandas as pd
+from collections import Counter
+from tqdm import tqdm
+import numpy as np
+
+verification_data_path = '../../verification_phase0/1_crowdsourced/results/merged_1-2-3-4-5-6-7-8_redone/name_annotations_filtered_ANON.csv'
+many_names_path = "../spellchecking/all_responses_round0-3_cleaned.csv"
+out_path = "all_responses_round0-3_verified.csv"
+
+os.makedirs('../proc_data_phase0/verified/', exist_ok=True)
+
+manynames = load_results.load_cleaned_results(many_names_path, index_col='vg_img_id')
+manynames['spellchecked_min2'] = manynames['spellchecked'].apply(lambda x: Counter({k: x[k] for k in x if x[k] > 1}))
+
+verifications = pd.read_csv(verification_data_path, converters={'name_cluster-nofillers': eval, 'same_object': eval})
+del verifications['batch']
+del verifications['source']
+del verifications['hitid']
+del verifications['assignmentid']
+del verifications['workerid']
+del verifications['name_cluster']
+
+# Remove all manipulated control items
+# ad hoc fix for weird bug: elizabethville is not in fact a control item
+verifications = verifications.loc[(verifications['name'] == 'elizabethville') |
+                                  verifications['control_type'].isna() |
+                                  (verifications['control_type'] == 'vg_majority') |
+                                  (verifications['control_type'].apply(lambda x: isinstance(x, str) and x.startswith('syn')))]
+verifications.rename(columns={'name_cluster-nofillers': 'name_cluster'}, inplace=True)
+
+
+print("ManyNames:", len(manynames))
+print(manynames[:10].to_string())
+
+
+print("\nVerifications:", len(verifications))
+print(verifications[:10].to_string())
+
+# aggregate per image+name
+scores_per_name = verifications.groupby(['image', 'name']).agg({'adequacy': lambda x: x.tolist(), 'inadequacy_type': lambda x: x.tolist(), 'name_cluster': lambda x: x.tolist(), 'same_object': lambda x: x.tolist()})
+# Remove points with <=1 annotator to avoid division by zero
+scores_per_name = scores_per_name.loc[scores_per_name['adequacy'].apply(lambda x: len(x) > 1)]
+# Are these stats biased towards images with more names? They are counted more times... Then again, there are more names there to agree or not agree on.
[…]

### 2019-11-29 analysis/load_results.py
tweak load_cleaned_results to be applicable to the verified results

@@ -40,11 +40,22 @@ def load_preprocessed_results_csv(datafile_csv):
             df[[dict_col]] = df[dict_col].apply(lambda a: eval(a))
     return df
 
-def load_cleaned_results(filename, sep="\t"):
-    resdf = pd.read_csv(filename, sep=sep)
+def load_cleaned_results(filename, sep="\t", index_col=None):
+    resdf = pd.read_csv(filename, sep=sep, index_col=index_col)
     resdf['spellchecked'] = resdf['spellchecked'].apply(lambda x: Counter(eval(x)))
     resdf['clean'] = resdf['clean'].apply(lambda x: Counter(eval(x)))
     resdf['canon'] = resdf['canon'].apply(lambda x: Counter(eval(x)))
+
+    # remove any old index columns
+    columns = [col for col in resdf.columns if not col.startswith("Unnamed")]
+    resdf = resdf[columns]
+
+    # eval verified column if present
+    if 'verified' in resdf:
+        resdf['verified'] = resdf['verified'].apply(eval)
+    if 'spellchecked_min2' in resdf:
+        resdf['spellchecked_min2'] = resdf['spellchecked_min2'].apply(lambda x: Counter(eval(x)))
+
     return resdf
 
 def _img2objname_map(imgdf):

### 2019-11-29 papers/LREC2020/background.tex

@@
 The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
-Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be named with different names \cite{brown1958shall,murphy2004big}.
+Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.
 
-Seminal work on concepts by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
-This typically corresponds to an intermediate level of specificity, i.e., basic level (e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}) \cite{jolicoeur1984pictures}.
+Seminal work on objects\cs{only use object, not concept, otherwise we would unnecessarily need to explain it} by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
+This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
+\cs{Rosch uses the term 'level of abstraction'}
+However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
@@
 %Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-level category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
+For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
 %, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
-The purely taxonomic view has been criticized in more recent work on concept organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+The purely taxonomic view has been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
 This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
@@
 An important experimental paradigm in work on human vision and categorization is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass,rossion2004revisiting}, see Figure\ \ref{fig:cake}.
-Subjects reach very high agreement in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Subjects reach very high agreement\cs{what does agreement mean?
+\ra e.g., their is a clear tendency towards a certain name across all speakers?} in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
 Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
@@
 
-In Computer Vision, object recognition is typically modelled as a classification task where objects need to be categorized according to a given labeling scheme that can comprise thousands of different categories in state-of-the-art systems \cite{googlenet,ILSVRC15}.
-Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} taxonomy, and typically assume a single ground-truth label. 
-The construction of ImageNet was set up as a two-stage procedure: (i) images for given nodes in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
+In Computer Vision, object recognition is typically modeled as a classification task where objects need to be localized and categorized according to a given labeling scheme, which can comprise thousands of different categories, in \cs{?
+by?with?} state-of-the-art systems \cite{googlenet,ILSVRC15}.
+Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
+The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
 Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
@@
 While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions.
-The overview in the following Section \ref{sec:survey} will focus on corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
+The overview in Section \ref{sec:survey}\cs{why is there a dot behind the section number?} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
 
-Our new collection, ManyNames, presented in Section \ref{sec:data} focusses on object names in in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in in L\&V.
-This controlled collection procedure, however, allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.
+Our new collection, ManyNames, presented in Section \ref{sec:data} focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V.
+This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.
 
@@
   \end{tabular}
-  \label{tab:compare}
-  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.}
+  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
 \end{table*}

### 2019-11-29 papers/LREC2020/survey.tex

@@
-We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome.%
+\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
+
+We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
 %\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
@@
 This motivates our data collection. %, in which we collect 36 names per object.
-However, because these datasets can be useful to examine other aspects of object naming, we summarize their characteristics below.
+Since these datasets can, however, be useful to examine other aspects of object naming, we summarize their characteristics below.
 
@@
 
-Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of the MS COCO \cite{mscoco}, 
+Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
 %The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
@@
 We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors.
-Moreover, multiple annotations (2.84 on average) allow for some minimal analysis of naming variation.
-However, note that not all objects are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
-Names elicited in \refcoco should be natural, but it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
+\cs{what does this mean, maybe give example?, e.g., from above with dog and dalmatian or so; otherwise the issue with the following part may not be understood}
+Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
+However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
+While in \refcoco, the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
 Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
@@
 
-This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size).
+This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}).
 %\gbt{Any idea what kind of categories are covered in \flickr?}
 Moreover, although no exhaustive annotations of the images are available, the dataset does contain information for the most salient objects in the image, as they are typically mentioned in the captions.
-The number of annotations per object, 2.3 annotations, is comparable to \refcoco.
+The number of annotations per object, $2.3$\ annotations, is comparable to \refcoco.
 
@@
 
-\vgenome \cite{krishna2016visualgenome} is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
+\vgenome (VG, \newcite{krishna2016visualgenome}) is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
 %In the following, we will focus on describing aspects immediately relevant to object naming only, but many other annotations are available as well (e.g. questions, paragraphs, etc.)
@@
 Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
-This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.
+This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}
 
 \subsection{Discussion}
-
-As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object?
+\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
+As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object \cs{instance?}?
 How much variation is there, for specific instances?
-What factors affect this variation?
-How does that impact modeling in L\&V?
 To answer these sorts of questions, we need naming data from many subjects for the same instances. 
-This is the motivation for our dataset, ManyNames, an augmentation of \vg.
+And, what factors affect observed naming variations (e.g.,\ the category or salience of other objects)? How does that impact the modeling of natural language in L\&V? 
+Additional, dense annotations of images would be beneficial for these kinds of analyses.  
+These are the motivations for our dataset, ManyNames, and for building it on top of \vg.
 

### 2019-11-29 analysis/load_results.py
merge MN + VERIF for basic eval

@@ -1,4 +1,4 @@
-from collections import Counter
+from collections import Counter, defaultdict
 import glob
 import json
 import os
@@ -11,6 +11,39 @@ import numpy as np
 import pandas as pd
 #from spellchecker import SpellChecker
 #from nltk.stem.wordnet import WordNetLemmatizer
+
+def load_verified_results(datafile_csv="../proc_data_phase0/spellchecking/all_responses_round0-3_cleaned.csv",
+                          veriffile_csv="../many_names_collection/verification_phase0/1_crowdsourced/results/merged_1-2-3-4-5-6-7-8/name_annotations_ANON.csv",
+                          min_adequacy=1,
+                          clustered=False):
+    """
+    Adds a column to the MN dataframe with response sets for only verified (mean adequacy>=min_adequacy) names. 
+    (TODO: make more efficient)
+    Args:
+        clustered (bool)    Loads response set with all "adequate" names, irrespective of the clustering
+    """
+    mn_df = load_cleaned_results(datafile_csv)    
+    verif_df = pd.read_csv(veriffile_csv, sep=",")
+    groups = verif_df[["image","object","name","adequacy"]].groupby(by=["image","name"])
+    names_per_imgid = defaultdict(list)
+    for gr in groups:
+        imgid,objname = gr[0]
+        adequacy = gr[1]["adequacy"].mean()
+        if adequacy <= min_adequacy:
+            names_per_imgid[imgid].append(objname)
+    
+    verified = [None]*len(mn_df)
+    for row in mn_df.iterrows():
+        imgid = row[1]["vg_img_id"]
+        idx = row[0]
+        verified_responses = Counter(dict([(nm,cnt) for (nm,cnt) in row[1]["spellchecked"].most_common() if nm in names_per_imgid[imgid]]))
+        # assumption: img not in verif_df ==> take all responses with cnt > 1, because these are highly frequent <-> valid [@MW: double-check that this is what has been done]
+        if len(verified_responses) == 0:
+            verified_responses = Counter(dict([(nm,cnt) for (nm,cnt) in row[1]["spellchecked"].most_common() if cnt>1]))
+        verified[idx] = verified_responses
+        
+    mn_df["verified"] = verified
+    return mn_df
 
 def load_resultsdata_csv(datafile_csv):
     if os.path.isdir(datafile_csv):

### 2019-11-29 papers/LREC2020/lrec2020naming.tex
adressed Carina's comments in abstract

@@
 We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
-Our dataset, ManyNames, provides 36 name annotations for each of 25K images\cs{objects} selected from VisualGenome.
-We highlight the challenges involved and provide a preliminary analysis of the ManyNames data that, on the one hand, shows high consistency in naming, and on the other, suggests that the main source of variation analyzed to date (taxonomic variation, as in \word{chihuahua} vs.\ \word{dog}) may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
-% , contrary to expectation, hierarchical variation is not the main source of 
-% Massive data collections for applications in language \& vision are nowadays available.
-In principle, these could constitute valuable resources also for research in computational linguistics (CL).
-However, in practice, very few studies have tested linguistic hypotheses using these large-scale datasets.
-In this paper, we illustrate the challenges of using this type of corpora for CL research, by focusing on a case study, namely naming of objects in real-world images.
-Our analysis of existing resources in language \& vision reveals that available datasets do not generally provide the right type and consistent quality of object naming data,  for being able to conduct a linguistically motivated study of this phenomenon.
-We contribute a new dataset on top of Visual Genome that  \sz{...
-continue}
+Our dataset, ManyNames, provides 36 name annotations for each of 25K objects in images selected from VisualGenome.
+We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average.
+At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like taxonomic variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
+% may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
  \\ \newline \Keywords{object naming, language and vision, computer vision} }

### 2019-11-29 papers/LREC2020/data-collection.tex

@@
 
-We take data from \vgenome~\cite{krishna2016visualgenome}, which
+We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
 contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
 all linked to WordNet synsets \cite{fellbaum1998wordnet}.
-\vgenome (VG) suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
+\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
 As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
@@
 
-From the set of synsets that match or subsume the concepts in the McRae norms, we kept those with a high number of \vg object instances of different names.
+First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and have a high number of \vg object instances of different names.\cs{prev.
+sentence this is still a bit fluffy}
 For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
@@
 This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
-Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.
+Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains.
 
@@
 %We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
-After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vgenome name.
+After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
 This yielded $25,596$ images (we discarded $5,497$).

### 2019-11-29 papers/LREC2020/intro.tex
adressed Carina's comments in Sec 1 and 2

@@
 Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
-Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily \cs{necessarily???
-\ra inherently?
-naturally?} results in linguistic variation.
+Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- naturally results in linguistic variation.
 For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
@@
 We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
-As a starting point, we compare three popular datasets in L\&V: \refcoco \cs{CITE}, a collection of referring expressions, \flickr \cs{CITE}, a collection of captions\cs{no, Flickr30K is a collection of captions, F Entities \ra of region-to-phrase linkings for image captions}, and \vgenome \cs{CITE -- at least VisualGenome should be cited}, which features extensive region-level annotations.
+As a starting point, we compare three popular datasets in L\&V: \refcoco \cite{Yu2016}, a collection of referring expressions, \flickr \cite{plummer2015flickr30kentities}, which provides region-to-phrase linkings for Flickr 30K captions \cite{young:2014}, and \vgenome \cite{krishna2016visualgenome}, which features extensive region-level annotations.
 We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or linguistic analysis.
@@
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \cs{explain basic-level, and if only with a reference or in a footnote} \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic (i.e.,\ hierarchical) relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explananation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic (i.e.,\ hierarchical) relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
 

### 2019-11-29 papers/LREC2020/survey.tex
adressed Carina's comments in Sec 1 and 2

@@
 Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
-%The latter provides five captions for each of  $300k$~images, spanning $80$~of the COCO categories.  
-%However, the COCO region-level (object) annotations are not linked to the captions.
 a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 

### 2019-11-29 papers/LREC2020/survey.tex
small changes

@@
 
-Both datasets use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco}, 
+Both datasets  \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco},
 a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
@@
 
-We expect this dataset to be good to examine the effect of distractors on naming choices in a referential setting, because images contain distractors.
-\cs{what does this mean, maybe give example?, e.g., from above with dog and dalmatian or so; otherwise the issue with the following part may not be understood}
+We expect this dataset to be good to examine the effect of context on naming choices in a referential setting, because the images contain complex scenes with other objects of more or less similar categories, i.e.\ so-called distractors \cite{krahmer:2012}.
 Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
@@
 
-\gbt{@Sina, pls check that I got this right:}
 One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.

### 2019-11-29 papers/LREC2020/analysis.tex
LREC2020: adds comments Sect.5-6

@@
 
-As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous dataset: 35.3 on average, compared to 1-7.
+As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous datasets: 35.3 on average, compared to 1-7.
 It also contains the most variability, since objects have on average 5.7 names (compared to 1-1.9).
-Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low agreement.
-ManyNames is in principle suitable to study how much inter-subject naming variation there is, and what factors influence such variation.
-However, data analysis shows that object identification is still an issue in our data: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low name agreement.
+ManyNames 
+%in in principle suitable to study 
+shows high potential use for studying the extent of inter-subject naming variation, and what factors influence such variation.
+Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
 Typically, workers named an adjacent object or one supported by the target object (such as \word{toy/book} instead of \word{bed} in Fig.~\ref{fig:ex-high-low-agreement}, image K), or a part of the target object.
-While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the bounding box, as in the \word{bed/sleeping bag} case of in Fig.~\ref{fig:ex-high-low-agreement} (image L).
+While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the bounding box, as in the \word{bed/sleeping bag} case in Fig.~\ref{fig:ex-high-low-agreement} (image L).
 Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
@@
 \label{subsec:counts}
-
+\cs{(Unless I have overseen it:) It would be good to introduce/explain what a response set is, i.e.
+the set of names + counts---the number of annotators having entered each of these names---and that threshold t is on the counts in the response set, etc.
+(and referring to Figure~5)}
 Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$ to account for possible noise in the crowdsourced data.
-Without any frequency thresholding~\mbox{($t$=1)}, the proportion of instances that have a single name annotated is very small, below 10\%, and there is a long tail of datapoints with many names, up to 19.
-With a reasonable (based on data inspection) threshold of $t$=2, a bit over 20\% of the objects have one name, almost 50\% up to 3 names, and 100\% up to 8 names.
-The average number of names is 2.9, and the most frequent name accounts on average for 75\% of the responses for a given object (Table~\ref{tab:agree}, and see below).
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$\cs{what is t actually?
+e.g., 'thresholds on the number of annotators entering an individual name (?)'} to account for possible noise in the crowdsourced data.
+Without any frequency thresholding~\mbox{($t$=1 \cs{maybe add something like 'i.e.
+the name was entered by one annotator'})}, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
+With a reasonable (based on data inspection) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
+The average number of names is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
 Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.
@@
 Our dataset can be expected to yield a more robust estimate for so-called entry-point names \cite{jolicoeur1984pictures}, that is, the name that most naturally comes to mind for a given object.
-The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of 0.55), which can be expected when using real images.
+The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of\ $0.55$), which can be expected when using real images.
 
 If we check agreement by domain, two domains stand out: the \domain{animals\_plants} domain, which is often discussed in the literature and where we find almost perfect agreement\ (\mbox{$H=0.2$}), and the \domain{people} domain with a particularly low agreement.
-Across domains, however, we find a large standard deviation for both \%top and $H$, of around 20\% for all domains except \domain{people}.
+Across domains, however, we find a large standard deviation for both \%top and $H$, of around\ $20\%$ for all domains except \domain{people}.
 This indicates that agreement varies quite a bit across instances, with factors that cannot be attributed to domain only.
@@
 
-Previous work on object naming has assumed that variation is mostly taxonomical (see Section~\ref{sec:rel-work}).
+Previous work on object naming has assumed that variation is mostly taxonomic\cs{hierarchical, to stream-line use of terms here?} (see Section~\ref{sec:rel-work}).
 This parameter does not seem to explain the variation in ManyNames. 
@@
 Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of specificity.
+\cs{I'd prefer to use the term abstraction here.}
 Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.

### 2019-11-29 papers/LREC2020/conclusion.tex
LREC2020: adds comments Sect.5-6

@@
 Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
-Our data suggests that this is not always the case and provides empirical data to for instance asses whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
+Our data suggests that this is not always the case and provides empirical data to, for instance, assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
 % (as in the case where they label objects as the background, like \word{grass} for \word{dog}).
@@
 The ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
-Our data provides a first step towards enabling model evaluation on naming variants of an instance, checking for instance to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet}) or not (\textsl{dog, hat, grass}).
+Our data provides a first step towards enabling model evaluation on naming variants of an instance, checking, e.g.,\ to what extent the top N predicted names are valid alternatives (\word{dog, animal, pet}) or not (\word{dog, hat, grass}).
 However, to fully enable this sort of analysis, a further annotation step is needed, to account for the referential uncertainty of bounding boxes and annotation noise.

### 2019-11-29 papers/LREC2020/background.tex

@@
 \subsection{Object Naming as a Linguistic Phenomenon}
+\label{subsec:rosch}
 
@@
 
-Seminal work on objects\cs{only use object, not concept, otherwise we would unnecessarily need to explain it} by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity called the ``entry-level'' \cite{jolicoeur1984pictures}.
+Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}.
 This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
-\cs{Rosch uses the term 'level of abstraction'}
 However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).
@@
 An important experimental paradigm in work on human vision and categorization is picture naming, where subjects have to say or write down the first name that comes to mind when looking at a picture of (typically) a line drawing depicting a prototypical instance of a category \cite{snodgrass,rossion2004revisiting}, see Figure\ \ref{fig:cake}.
-Subjects reach very high agreement\cs{what does agreement mean?
-\ra e.g., their is a clear tendency towards a certain name across all speakers?} in this task \cite{rossion2004revisiting}, and the resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
+Subjects reach very high agreement in this task \cite{rossion2004revisiting}, i.e. for a given object, there is a clear tendency towards a certain name across all speakers.
+The resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
 Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
@@
 
-In Computer Vision, object recognition is typically modeled as a classification task where objects need to be localized and categorized according to a given labeling scheme, which can comprise thousands of different categories, in \cs{?
-by?with?} state-of-the-art systems \cite{googlenet,ILSVRC15}.
+In Computer Vision, object recognition is typically modeled as a classification task where state-of-the-art systems localize and categorize objects according to a given labeling scheme which can comprise thousands of different categories  \cite{googlenet,ILSVRC15}.
 Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
@@
 While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions.
-The overview in Section \ref{sec:survey}\cs{why is there a dot behind the section number?} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
+The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
 

### 2019-11-29 papers/LREC2020/intro.tex
intro revised

--- 2019-11-28 papers/LREC2020/intro.tex
@@
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
-Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
+Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers naturally talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
+Data collections in L\&V are typically set up as free annotation tasks,  where subjects are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue), which naturally results in linguistic variation.
 For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
 
-As compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
-For instance, so-called picture naming norms used in Psycholinguistics typically record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
-Consequently, a reliable assessment of inter-annotator agreement, speaker preferences and a deeper linguistic analysis of the observed variation is mostly out of scope with available data collections in  L\&V.
-At the same time, these datasets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories, compared to the idealized drawings used in picture naming norms, as shown in Figure \ref{fig:cake}.
+Compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
+For instance, so-called picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
+At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
+A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
 
-In this paper, we take a first step towards building a dataset with object naming data for real-world images.
-We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
-As a starting point, we compare three popular datasets in L\&V: \refcoco, a collection of referring expressions, \flickr, a collection of captions, and \vgenome, which features extensive region-level annotations.
-We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.
+In this paper, we present ManyNames, a dataset with substantial amounts of object names per object for real-world images.
+We start by surveying existing resources in L\&V that provide object names: \refcoco \cite{Yu2016}, a collection of referring expressions, \flickr \cite{plummer2015flickr30kentities}, which provides region-to-phrase linkings for Flickr 30K captions \cite{young:2014}, and \vgenome \cite{krishna2016visualgenome}, which features extensive region-level annotations.
+We highlight their potential contributions to the study of object naming, and also argue that the low number of annotations per item prevents reliable assessment or linguistic analysis of instance-specific preferences and naming variation.
 
@@
 The number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V.
-Moreover, our images show objects in complex visual contexts,
-unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
+%Moreover, our images show objects in complex visual contexts,
+%unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and %unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explananation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
 

### 2019-11-29 papers/LREC2020/analysis.tex
rel work revised; 2 comments by carina remaining

@@
 
-Previous work on object naming has assumed that variation is mostly taxonomic\cs{hierarchical, to stream-line use of terms here?} (see Section~\ref{sec:rel-work}).
+Previous work on object naming has assumed that variation is mostly hierarchical (see Section~\ref{sec:rel-work}).
 This parameter does not seem to explain the variation in ManyNames. 
@@
 As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of specificity.
-\cs{I'd prefer to use the term abstraction here.}
+Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction. 
 Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.

### 2019-11-29 papers/LREC2020/background.tex
rel work revised; 2 comments by carina remaining

@@
 The resulting naming norms are useful for studying various cognitive processes \cite{humphreys1988cascade}.
-Our task is inspired by picture naming, but uses real-world images with objects highlighted in them.
+Our task is inspired by picture naming, but uses real-world images showing objects in context.
 
@@
 
-Our new collection, ManyNames, presented in Section \ref{sec:data} focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V.
+Our new collection, ManyNames, focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V.
 This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

### 2019-11-29 papers/LREC2020/intro.tex
rel work revised; 2 comments by carina remaining

@@
 We start by surveying existing resources in L\&V that provide object names: \refcoco \cite{Yu2016}, a collection of referring expressions, \flickr \cite{plummer2015flickr30kentities}, which provides region-to-phrase linkings for Flickr 30K captions \cite{young:2014}, and \vgenome \cite{krishna2016visualgenome}, which features extensive region-level annotations.
-We highlight their potential contributions to the study of object naming, and also argue that the low number of annotations per item prevents reliable assessment or linguistic analysis of instance-specific preferences and naming variation.
+We highlight their potential contributions to the study of object naming, and also argue that the low number of annotations per item prevents reliable assessment or linguistic analysis of object-specific preferences and naming variation.
 

### 2019-11-29 papers/LREC2020/lrec2020naming.tex
intro revised
rel work revised; 2 comments by carina remaining

@@
 We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average.
-At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like taxonomic variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
+At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
 % may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
@@
 
-\cs{maybe streamline use of (i),(ii),... and (1),(2),...}
+% gbt decisions to streamline:
+% use "hierarchical" instead of "taxonomic", throughout
+% use (i) (ii) (iii), ... in inline lists
+
 \section{Introduction}
@@
 
- \section{Acknowledgements}
+%\section{Acknowledgements}
 

### 2019-11-29 papers/LREC2020/survey.tex
rel work revised; 2 comments by carina remaining

@@
-\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
-
+%\cs{If space allows, I would also put an example image+annotation for RefCOCO and Flickr30kE}
+%\gbt{Space doesn't seem to allow :)}
 We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
@@
 Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
-As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual instances.
+As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects.
 This motivates our data collection. %, in which we collect 36 names per object.
@@
 
-Both datasets  \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco},
+Both \refcoco and \refcocop \cite{Yu2016} use the \referit\cite{Kazemzadeh2014} game for collecting referring expressions (RE) for natural objects in real-world images, and are built on top of MS COCO \cite{mscoco},
 a dataset of images of natural scenes of $91$~common object categories (e.g.,~\cat{dog, pizza, chair}). 
@@
 Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
-The matcher must click on the object he thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which prompts the players to avoid the mere object category as RE, and (ii) in \refcocop the players must not use location words, urging them to refer to the appearance of objects.
+The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
+REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
  % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
@@
 We expect this dataset to be good to examine the effect of context on naming choices in a referential setting, because the images contain complex scenes with other objects of more or less similar categories, i.e.\ so-called distractors \cite{krahmer:2012}.
-Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming variation.
+Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming preferences and variation.
 However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
-While in \refcoco, the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
+Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
 Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
@@
 
-This dataset has three main differences with respect to \refcoco/+: (1) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (2) the images and the production of entity mentions were not subject to any constraints; (3) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}).
+This dataset has three main differences with respect to \refcoco/+: (i) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (ii) the images and the production of entity mentions were not subject to any constraints; (iii) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}).
 %\gbt{Any idea what kind of categories are covered in \flickr?}
@@
 The number of annotations per object, $2.3$\ annotations, is comparable to \refcoco.
+This dataset is suitable to analyze object naming in descriptions, for a quite large set of categories (although, again, not enough annotations are available to analyze image-specific naming data).
 
@@
 One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
-Another is the fact that it potentially provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
-This should make it easier to identify factors intervening in naming choices.
+Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.
 However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
@@
 \cs{@Sina I changed some stuff here, maybe you prefer the old version...}
-As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess instance-specific naming behavior: To what extent do different people choose the same name for an object \cs{instance?}?
-How much variation is there, for specific instances?
-To answer these sorts of questions, we need naming data from many subjects for the same instances. 
-And, what factors affect observed naming variations (e.g.,\ the category or salience of other objects)? How does that impact the modeling of natural language in L\&V? 
-Additional, dense annotations of images would be beneficial for these kinds of analyses.  
-These are the motivations for our dataset, ManyNames, and for building it on top of \vg.
+As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess object-specific naming behavior: To what extent do different people choose the same name for a specific object?
+How much variation is there?
+To answer these sorts of questions, we need naming data from many subjects for the same objects. 
+Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
+These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
 

### 2019-11-29 papers/LREC2020/survey.tex
data collection checked

@@
 \subsection{Visual Genome}
+\label{sec:vg-survey}
 
@@
 
-One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
+One of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
 Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
@@
 How much variation is there?
-To answer these sorts of questions, we need naming data from many subjects for the same objects. 
-Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
-These are the motivations for our dataset, ManyNames, and for building it on top of \vg, as discussed next.
+To answer these sorts of questions, we need naming data from many subjects for the same objects; this is what we collect in ManyNames.
 

### 2019-11-29 papers/LREC2020/analysis.tex
checked until section 5.1 inclusive

@@
 %in in principle suitable to study 
-shows high potential use for studying the extent of inter-subject naming variation, and what factors influence such variation.
+shows high potential use for studying the degree of inter-subject naming agreement, and what factors influence variation.
 Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
@@
 \label{subsec:counts}
-\cs{(Unless I have overseen it:) It would be good to introduce/explain what a response set is, i.e.
-the set of names + counts---the number of annotators having entered each of these names---and that threshold t is on the counts in the response set, etc.
-(and referring to Figure~5)}
+
+We analyze the response sets obtained per object, that is, the set of names and their frequency (number of annotators entering a particular name).
 Our analysis of naming variation shows that, on the one hand, we have a fair bit of consistency in the names chosen for objects, and, on the other, also consistent variation.
-Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$\cs{what is t actually?
-e.g., 'thresholds on the number of annotators entering an individual name (?)'} to account for possible noise in the crowdsourced data.
-Without any frequency thresholding~\mbox{($t$=1 \cs{maybe add something like 'i.e.
-the name was entered by one annotator'})}, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
-With a reasonable (based on data inspection) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
-The average number of names is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
+Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
+Without any frequency thresholding~\mbox{($t$=1}, that is, allowing names entered by only one annotator)}, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
+With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
+This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which includes names that have at least frequency 2.
+The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
 Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.

### 2019-11-29 papers/LREC2020/background.tex
more discussion in sec 3

@@
 However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).
+
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in their choice of the level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
+While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
 %Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
 For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
+The effect of such distractor objects on the production of referring expressions has been looked at a lot in the language generation community \cite{krahmer:2012}, though not specifically for object naming.
+We believe that our new dataset provides an interesting resource for tackling this question.
 %, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.
-The purely taxonomic view has been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+
+The purely taxonomic view on naming has also been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
 This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
@@
     \toprule
-    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
+    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
     \midrule

### 2019-11-29 papers/LREC2020/data-collection.tex
more discussion in sec 3

@@
 
-We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
+\sz{the next paragraph is quite redundant, isn't it?}
+We take data from VG \cite{krishna2016visualgenome}, which
 contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,

### 2019-11-29 papers/LREC2020/intro.tex
more discussion in sec 3

@@
 At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
-A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V, along the lines of e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
 
@@
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explananation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explanation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
 

### 2019-11-29 papers/LREC2020/survey.tex
more discussion in sec 3

--- 2019-11-29 papers/LREC2020/survey.tex
@@
 We identified three previously existing resources that can be of use for analysis and modeling of object naming: RefCOCO (and a variant, RefCOCO+), Flickr30k Entities, and Visual Genome. %
-%\footnote{Other resources, such as \gbt{imagenet, openimages, see the other datasets cited in the openimages dataset}, provide object categories, rather than names.}
-% footnote not necessary! this is explained in the background section
 Table~\ref{tab:compare} summarizes their main characteristics and compares them to our dataset (last two columns; see Section~\ref{sec:data}).
-As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects.
-This motivates our data collection. %, in which we collect 36 names per object.
-Since these datasets can, however, be useful to examine other aspects of object naming, we summarize their characteristics below.
+As the table shows, previous datasets provide between one and three annotations per object, which, we believe, is not enough to assess naming behavior for individual objects and which
+motivates our data collection. %, in which we collect 36 names per object.
+In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable below for a large-scale, in-depth study targeted at object naming.
 
@@
 
-We expect this dataset to be good to examine the effect of context on naming choices in a referential setting, because the images contain complex scenes with other objects of more or less similar categories, i.e.\ so-called distractors \cite{krahmer:2012}.
-Moreover, multiple annotations ($2.84$\ on average) allow for some minimal analysis of naming preferences and variation.
-However, note that not all objects of an image are annotated with REs and corresponding categories, so it may be difficult to analyze the effect of distractors with automatic processing.
+The statistics in Table \ref{tab:compare} suggest that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object).
+However, the small number of annotations per object would not allow for a reliable assessment of speaker agreement.
+
+RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
+A controlled analysis of the effect of context on choice in object naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories.
+Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
 Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
 Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
-To sum up, we would recommend \refcoco to study the effect of distractors on object naming in a restricted set of categories.
+To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming in particular.
 
@@
 One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
-Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+Another is the fact that it, in principle, provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
 This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.
+
 However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
 Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
-This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze contextual factors for naming.\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}
+This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
+The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this problem.
+Thus, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, this cannot be established based on the given data.
+We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).
+
+Table \ref{tab:compare} also shows the statistics for the subset of objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7).
+However, interestingly, the portion of objects that have different names associated with them is still extremely small.
+Note that, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).
+
+%\cs{The explanation of intervening factors in object naming in the background may be a bit more detailed, such as to really understand the drawbacks of the existing datasets with respect to distractors.}
 
@@
 \cs{@Sina I changed some stuff here, maybe you prefer the old version...}
-As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to assess object-specific naming behavior: To what extent do different people choose the same name for a specific object?
+As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to systematically assess how variable object naming really is.
+The RefCOCO data suggest that many objects  object-specific naming behavior: To what extent do different people choose the same name for a specific object?
 How much variation is there?

### 2019-11-29 papers/LREC2020/analysis.tex

@@
 Figure \ref{fig:ntypes} shows the cumulative histograms for type counts, i.e.\ how many objects have at least $n$\ names, with different frequency thresholds~$t$.
-Without any frequency thresholding~\mbox{($t$=1}, that is, allowing names entered by only one annotator)}, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
+Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
 With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.

### 2019-11-29 papers/LREC2020/data-collection.tex

--- 2019-11-29 papers/LREC2020/data-collection.tex
@@
 
-We take data from \vgenome~(VG, \newcite{krishna2016visualgenome}), which
-contains a dense region-based labeling of $108$K~images with, inter alia, object names, attributes and relationships,
-all linked to WordNet synsets \cite{fellbaum1998wordnet}.
+We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
 \vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
-As common in Computer Vision, objects are localized as bounding boxes, as in Figure~\ref{fig:cake}.% 
+Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which affords analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
+% The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).
+Note that, as common in Computer Vision, objects in \vg images are localized as bounding boxes, as shown in Figure~\ref{fig:cake} (left).% 
 \footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}
@@
 
-First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and have a high number of \vg object instances of different names.\cs{prev.
-sentence this is still a bit fluffy}
-For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
+First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and cover different names in \vg.
+%which \vg objects get diverse names.
+For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
 %\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
 
-We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
-\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
+We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them.
+We refer to the names obtained as \textit{seeds} ($450$\ in total).
+%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
 We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}).
@@
 Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains.
+\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}
 

### 2019-11-29 papers/LREC2020/survey.tex

@@
 motivates our data collection. %, in which we collect 36 names per object.
-In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable below for a large-scale, in-depth study targeted at object naming.
+In the following, we will look at their characteristics in more detail and work out requirements for a dataset that is suitable for a large-scale study of object naming.
 
@@
 
-One of the main advantages of \vg are its size, with 3.8 million objects as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
-Another is the fact that it, in principle, provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+One of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
+Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
 This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.
@@
 This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
-The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this problem.
-Thus, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, this cannot be established based on the given data.
+For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
+The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
 We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).
 
-Table \ref{tab:compare} also shows the statistics for the subset of objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7).
+Table \ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). 
+We think that this might be an effect of our category selection procedure explained in Section \ref{sec:data}.
 However, interestingly, the portion of objects that have different names associated with them is still extremely small.
-Note that, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).
+Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).
 
@@
 \subsection{Discussion}
-\cs{@Sina I changed some stuff here, maybe you prefer the old version...}
-As the discussion above showed, while some existing resources can be used to shed light on factors affecting naming choices, they do not provide enough data to systematically assess how variable object naming really is.
-The RefCOCO data suggest that many objects  object-specific naming behavior: To what extent do different people choose the same name for a specific object?
-How much variation is there?
-To answer these sorts of questions, we need naming data from many subjects for the same objects. 
+
+While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is.
+The RefCOCO data (and to some extent the Flickr30k entities data) suggests that for most objects there is more than none available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all.
+The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
+This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
 Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.

### 2019-11-29 papers/LREC2020/background.tex
a bit of shortening to fit in 8 pages

@@
 
-The purely taxonomic view on naming has also been criticized in more recent work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
 This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
-We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the main parameter that accounts for variation in our data.
+We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the most frequent source of variation in our data.
 
@@
 
-In Computer Vision, object recognition is typically modeled as a classification task where state-of-the-art systems localize and categorize objects according to a given labeling scheme which can comprise thousands of different categories  \cite{googlenet,ILSVRC15}.
+In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems localize and classify objects into thousands of different categories  \cite{googlenet,ILSVRC15}.
 Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
@@
 
-In contrast to work on object recognition, work in L\&V typically collects and uses data sets where annotators produce free and natural utterances for a given image. 
+Previous work in L\&V has collected and used data sets where annotators produced free and natural utterances for a given image. 
 Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}.
@@
 
-Our new collection, ManyNames, focuses on object names in isolation and is, therefore, substantially more controlled than typical data sets that are currently in use in L\&V.
+Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V data sets.
 This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

### 2019-11-29 papers/LREC2020/conclusion.tex
a bit of shortening to fit in 8 pages

@@
 Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
-Our data suggests that this is not always the case and provides empirical data to, for instance, assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
+Our data suggests that this is not always the case and can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
 % (as in the case where they label objects as the background, like \word{grass} for \word{dog}).

### 2019-11-29 papers/LREC2020/survey.tex
a bit of shortening to fit in 8 pages

@@
 The REs were collected via crowdsourcing in a two-player reference game designed to obtain REs uniquely referring to the target object. 
-Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object in the image. 
+Specifically, a director and a matcher are presented with an image, and the director produces a RE for an outlined target object. 
 The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
@@
 
-The statistics in Table \ref{tab:compare} suggest that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object).
-However, the small number of annotations per object would not allow for a reliable assessment of speaker agreement.
+Table \ref{tab:compare} shows that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object).
+However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement.
 
 RefCOCO has been used to model and examine the effect of context on referring expression generation in general \cite{Yu2016}, though this work did not look at object names specifically. 
-A controlled analysis of the effect of context on choice in object naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories.
+A controlled analysis of the effect of context on choice in naming, as for instance in \cite{graf2016animal}, would require substantial further data annotation as not all objects of an image are annotated with REs and corresponding categories.
 Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
 Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
-Finally, the main drawback of this dataset is that the set of categories included is quite small ($80$~COCO categories).
-To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming in particular.
+Finally, the set of categories in MSCOCO included is quite small ($80$~COCO categories).
+To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming at a large scale.
 
@@
 While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is.
-The RefCOCO data (and to some extent the Flickr30k entities data) suggests that for most objects there is more than none available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all.
+The RefCOCO data (and to some extent the Flickr30k data) suggests that for most objects there is more than one available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all.
 The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).

### 2019-11-30 papers/LREC2020/conclusion.tex
lrec submission revised until conclusion; 3 lines overspill

@@
 For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
-Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
-Our data suggests that this is not always the case and can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
-% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).
+Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.
 
@@
 
-Our current data clearly supports the prediction in theoretical research on object naming and categorization that there will in general be a preferred name for a given visually presented object.
-It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches; (c) there is high variability in agreement across instances within the same domain.
+With respect to naming variation, our current data clearly supports the prediction in theoretical research on object naming that there will in general be a preferred (entry-level) name for a given visually presented object.
+It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
 The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.

### 2019-11-30 papers/LREC2020/conclusion.tex
no more spill over

@@
 
-With respect to naming variation, our current data clearly supports the prediction in theoretical research on object naming that there will in general be a preferred (entry-level) name for a given visually presented object.
-It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
+With respect to naming variation, our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
+It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
 The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation.

### 2019-11-30 analysis/gemmas-analysis.py
Notebook for analysis of verification data; for the moment focusing on entry-level

@@ -2,58 +2,93 @@
 
 # created gbt Sun Feb 24 2019
 
-import pandas as pd
-import numpy as np
 import os
-#from collections import Counter
-#from utils_analysis import *
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+from ast import literal_eval
+from collections import Counter
+
+# spellchecked_min2: why this restriction? Did we really not check names with freq=1?
+
+df=pd.read_csv('../proc_data_phase0/verification/all_responses_round0-3_verified.csv', sep="\t")
+#df=pd.read_csv('kk.csv', sep="\t")
+df=df.drop(['responses_r0','opt-outs','top_response_domain_r0','responses_domains_r0',
+            'sample_type','all_responses','clean','canon',
+            'responses_domains_r1', 'responses_r1', 'top_response_domain_r1',
+       'responses_domains_r2', 'responses_r2', 'top_response_domain_r2',
+       'responses_domains_r3', 'responses_r3', 'top_response_domain_r3'], axis=1)
+#df=df.head(1)
+#print(df)
+print(df.columns)
+
+adequacies=[] # number of adequate names (total)
+tot_names=0; non_ad=0 # total n of names; n of non-adequate names (see threshold below)
+list_n_ad_names=[] # number of adequate names per canonical object
+list_entry_names=[] # entry names for each canonical object (cluster 0)
+list_freqs_entry_name=[] # entry names for each canonical object (cluster 0)
+no_entry_lev=0
+for row in df.itertuples():
+    name_freqs=eval(row.spellchecked_min2)
+    print(name_freqs)
+    # find entry-level name; this should be done for the canonical object,
+    # but I can't recover the info from the verified column (name data in a dictionary),
+    # so I use the one from all data and check if the entry level name form those data is in cluster 0
+    # there are only 700 imgs where the most frequent name is not in cluster 0; TODO: check them, and mend this
+    entry_name,entry_freq=name_freqs.most_common(1)[0] # returns tuple, e.g. ('man',11)
+    d = literal_eval(row.verified) # dictionary with verification data
+    n_ad_names_img=0; freqs_canon_names=1; entry_name_in_cluster0=False
+    for name in d.keys(): # each name for this object
+        tot_names+=1
[…]

### 2019-11-30 papers/LREC2020/analysis.tex
a bit of shortening to fit in 8 pages

@@
 
-\begin{table*}
+\begin{table}
 \centering
-%\footnotesize
+\small
 \begin{tabular}{lccccc}
@@
 \label{tab:agree}
-\end{table*}
+\end{table}
 
@@
 
-Previous work on object naming has assumed that variation is mostly hierarchical (see Section~\ref{sec:rel-work}).
+Previous work on object naming has assumed that variation is mostly along a taxonomic axis, and in particular hierarchical (see Section~\ref{sec:rel-work}).
 This parameter does not seem to explain the variation in ManyNames. 
@@
 As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
-Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction. 
-Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
+Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
+Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 
@@
 In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
-\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{toast/dessert/breakfast}, image C).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers (\textit{bed/bench}, \textit{sandwich/hotdog}, images J and D).
-\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{sandwich/basket}, image B).
+\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{toast/dessert}, image C).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\textit{bed/bench}, images J).
+\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{burger/basket}, image B).
 \textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe/dress}, image not shown).

### 2019-11-30 papers/LREC2020/data-collection.tex

@@
 Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \domain{home}).
-Instead, we defined a set of synsets ($52$\ in total; listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.
+Instead, we defined a set of 52 synsets (listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.
 
@@
 %which \vg objects get diverse names.
-For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
+For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
 %\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
@@
 Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains. 
-\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}
+%\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}
 

### 2019-11-30 papers/LREC2020/intro.tex

@@
 
-Compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
-For instance, so-called picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
+For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
 Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
 At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
-A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V, along the lines of e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures, as e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
 

### 2019-12-02 proc_data_phase0/verification/insert_verification_column.py
bug fixes (properly remove fillers; don't delete index objectid)

@@ -14,13 +14,14 @@ os.makedirs('../proc_data_phase0/verified/', exist_ok=True)
 manynames = load_results.load_cleaned_results(many_names_path, index_col='vg_img_id')
 manynames['spellchecked_min2'] = manynames['spellchecked'].apply(lambda x: Counter({k: x[k] for k in x if x[k] > 1}))
 
-verifications = pd.read_csv(verification_data_path, converters={'name_cluster-nofillers': eval, 'same_object': eval})
+verifications = pd.read_csv(verification_data_path, converters={'name_cluster-nofillers': eval, 'same_object-nofillers': eval})
 del verifications['batch']
 del verifications['source']
 del verifications['hitid']
 del verifications['assignmentid']
 del verifications['workerid']
 del verifications['name_cluster']
+del verifications['same_object']
 
 # Remove all manipulated control items
 # ad hoc fix for weird bug: elizabethville is not in fact a control item
@@ -28,7 +29,7 @@ verifications = verifications.loc[(verifications['name'] == 'elizabethville') |
                                   verifications['control_type'].isna() |
                                   (verifications['control_type'] == 'vg_majority') |
                                   (verifications['control_type'].apply(lambda x: isinstance(x, str) and x.startswith('syn')))]
-verifications.rename(columns={'name_cluster-nofillers': 'name_cluster'}, inplace=True)
+verifications.rename(columns={'name_cluster-nofillers': 'name_cluster', 'same_object-nofillers': 'same_object'}, inplace=True)
 
 
 print("ManyNames:", len(manynames))
@@ -90,5 +91,5 @@ for img, row in tqdm(manynames.iterrows(), total=len(manynames)):
             manynames.at[img, 'verified'][name]['cluster_id'] = clusters_sorted.index(manynames.at[img, 'verified'][name]['cluster'])
             manynames.at[img, 'verified'][name]['cluster_weight'] = cluster_weights[manynames.at[img, 'verified'][name]['cluster']]
 
-manynames.to_csv(out_path, index=False, sep="\t")
+manynames.to_csv(out_path, sep="\t")
 print("New ManyNames csv with verification column saved to",out_path)

### 2019-12-02 papers/ACL2020/manynames.tex
bit more analysis

@@
 
+brief summary of lrec paper, shortcoming, what we added
+
 \subsection{Verification of Annotations}
@@
 
+@mw
+
 \subsection{Analysis}
 \label{sect:mn_analysis}
+
 \paragraph{Of ManyNames:} 
@@
 \begin{itemize}
-	\item Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)
-	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs. 1 vs. 2 vs. 3). (i.e.,\ entry-level names cannot be derived from a few annotators)
-	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz}
+	\item Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level) \gbt{But, what's an object class in our data?
+We can't really use collection synsets, can we?
+Those are not really object classes?}
+	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs.
+1 vs.
+2 vs.
+3).
+(i.e.,\ entry-level names cannot be derived from a few annotators) \gbt{My guess is that it will be pretty constant the moment you have 9 annotators, as in round 0.
+Plan: report percentage of overlap with VG name (72\%); if you want, we can estimate something based on the annotated data, but this would be more like sampling from all annotations (randomly sample 1, 2, 3, ...
+names and see how things change.)}
+	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz} \gbt{According to my data, there are 415 entry-level names (=entry-level names for canonical object; could extend definition to all objects if need be).
+Are your 442 names the most frequent names for some image?
+Else, we could do the experiments with the entry-level names as the vocabulary (but it's probably too late now).}
 	\item ...
@@
 \end{itemize}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-03 papers/ACL2020/acl2020_main.tex
bit more analysis
ACL main

@@
 \label{sec:experiments}
-%\input{experiments}
-\iffalse
-\cs{under construction}
-\begin{itemize}
-	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
-	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
-	\item ... 
-	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
-	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
-	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
-	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
-	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data.
-\end{itemize}
-\fi
-
-We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
-Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
-Can object detection models, trained on arbitrary names, account for human object naming?
-\begin{itemize}
-	\item Do they predict the entry-level name?
-	\item Are valid name alternatives among the top-N predictions?
-	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
-	-- naming an alternative object (maybe more salient)\\
-	-- predicting a semantically related name
-	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
-	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
-	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
-	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
-\end{itemize}
-
-\subsection{Predicting Entry-Level Names}
-\label{sect:exp_entry}
-Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?
-
-Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
-		Model--Vocab	 
-		&  GTtrain &  =VG & =MN & $\in$MN  & KL & MRR & HL 
-		&  =VG & =MN & $\in$MN  & KL & MRR & HL\\ 
-		\midrule
-		FRCNN--VG2500 & VG \\
-		FRCNN--VG1600 & VG \\
-		FRCNN--MN442 & VG \\
-		\midrule \midrule
-		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
-		Features--Vocab & GTtrain  \\
-		\midrule 
-		FRCNN--VG1600--XX1600 & MN \\
-		FRCNN--VG1600--MN442 &  MN \\
-		ResNet101--VG1600 & VG \\
-		ResNet101--VG1600 & MN \\
-		ResNet101--MN442 & VG \\
-		ResNet101--MN442 & MN \\
-		\bottomrule
-	\end{tabular}
-	\caption{Target vocabulary in test data: MN442.
-Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
-GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
-MRR is mean reciprocal rank; HL is Hamming loss.\label{tab:entrylevels}.
-}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l@{~}|rrrr}
-		\toprule
-		... \\
-		\midrule
-		Domain	 & ... \\ 
-		\midrule
-		All           \\
-		home           \\
-		food           \\
-		buildings      \\
-		vehicles       \\
-		animals\_plants \\
-		clothing       \\
-		people         \\
-		\bottomrule
-	\end{tabular}
-	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
-\end{table*}
-
-\subsection{Humans vs. Models: Which Mistakes do they Make?}
-\label{sect:exp_analysis}
-
-\paragraph{Categorisation of Errors}
-see Figure\ ref{fig:mistakes}
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.\ plane vs. airplane
-	\item Semantically related\\
-	e.g.\  motorcycle vs. scooter
-\end{enumerate}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
-
-	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
-\end{figure}
-
-\subsection{Generalization Ability: OpenImages}
-\label{sect:exp_openimages}
-Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
-
-Models compared: FRCNN--VG1600 vs. FRCNN--MN442 vs. ResNet101--XX (best Vanilla).
+\input{experiments}
 

### 2019-12-03 papers/ACL2020/experiments.tex
[ACL2020] adds experiments.tex

% experiments.tex

\iffalse
\cs{under construction}
\begin{itemize}
	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
	\item ... 
	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data. 
\end{itemize}
\fi

We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
Can object detection models, trained on arbitrary names, account for human object naming?
\begin{itemize}
	\item Do they predict the entry-level name?
	\item Are valid name alternatives among the top-N predictions?
	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
	-- naming an alternative object (maybe more salient)\\
	-- predicting a semantically related name
	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)? 
	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
\end{itemize}

\subsection{Experimental Setup}
\label{sect:exp_setup}

\paragraph{Data}

\paragraph{Models}

\paragraph{Measures}

\subsection{[TBC] Predicting Entry-Level Names}
\label{sect:exp_entry}
Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?

Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
		\toprule
		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
		Model--Vocab	 
		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
		\midrule
		FRCNN--VG2500 & VG \\
		FRCNN--VG1600 & VG & \\
		FRCNN--MN442 & VG &   \\
		\midrule \midrule
		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
		Features--Vocab & GTtrain  \\
		\midrule 
		FRCNN--VG1600--VGMN & MN &  \\
		& MN-12ep  &           \\ 
		FRCNN--VG1600--MN442 &  MN \\
		\midrule
		ResNet101--VGMN\_4ep  &   VG  \\
		ResNet101--VGMN\_8ep & VG &  \\
		ResNet101--VGMN & MN \\
		ResNet101--MN442 & VG \\
		ResNet101--MN442 & MN &\\
		\bottomrule
	\end{tabular}
	\caption{Target vocabulary in test data: MN442. Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary). GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}. MRR is mean reciprocal rank; J is Jaccard score.\label{tab:entrylevels}. }
\end{table*}

\subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
\label{sect:exp_analysis}

\paragraph{Categorization of Errors}
see Figure\ ref{fig:mistakes}
\begin{enumerate}
	\item Clear mistake \\
	e.g.,\ rice vs. bread
	\item Alternative name\\
	e.g.,\ building vs. house
	\item Alternative object \cs{(other cluster from verif data)}
	\item Synonym\\
	e.g.,\ plane vs. airplane
	\item Semantically related\\
	e.g.,\  motorcycle vs. scooter
\end{enumerate}

\begin{figure}
	\centering
	\includegraphics[scale=.2]{images/2323938.jpg}
	\includegraphics[scale=.2]{images/2322259.jpg}
	\includegraphics[scale=.2]{images/2371657.jpg}

	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
\end{figure}

\subsection{[TBC] Generalization Ability: OpenImages}
\label{sect:exp_openimages}
Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\

Models compared: FRCNN--VG1600 vs. FRCNN--MN442 vs. ResNet101--XX (best Vanilla).

### 2019-12-03 papers/ACL2020/experiments.tex
[ACL2020] adds tables w. confusing results :)

@@
 Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.
-
 \begin{table*}[t]
@@
 		\midrule
+		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
 		FRCNN--VG2500 & VG \\
-		FRCNN--VG1600 & VG & \\
-		FRCNN--MN442 & VG &   \\
+		FRCNN--VG1600 & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
 		\midrule \midrule
@@
 		\midrule 
-		FRCNN--VG1600--VGMN & MN &  \\
-		& MN-12ep  &           \\ 
+		FRCNN--VG1600--VGMN & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
 		FRCNN--VG1600--MN442 &  MN \\
 		\midrule
-		ResNet101--VGMN\_4ep  &   VG  \\
-		ResNet101--VGMN\_8ep & VG &  \\
-		ResNet101--VGMN & MN \\
-		ResNet101--MN442 & VG \\
-		ResNet101--MN442 & MN &\\
+		ResNet101--VGMN & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
+
+		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
+		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
+		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
+		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
 		\bottomrule
@@
 GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
-MRR is mean reciprocal rank; J is Jaccard score.\label{tab:entrylevels}.
+MRR is mean reciprocal rank; J is Jaccard score.
+Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:entrylevels}.
 }
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l@{~}|rrrr}
+		\toprule
+		... \\
+		\midrule
+		Domain	 & ... \\ 
+		\midrule
+		All           \\
+		home           \\
+		food           \\
+		buildings      \\
+		vehicles       \\
+		animals\_plants \\
+		clothing       \\
+		people         \\
+		\bottomrule
+	\end{tabular}
+	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
 \end{table*}
@@
 
+\subsection{Results}
+\paragraph{Overview}
+Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}
+
+\paragraph{Correct predictions}
+Table\ \ref{tab:exp_details_correct}: \cs{Gives detailed results to the categories of "correct name" (but not hit): same cluster, WordNet synonym, WordNet hypernym/hyponym}\\
+To look into in detail (example images): 
+\begin{itemize}
+	\item Compare FRCNN vs.
+FRCNN-finetuned (row block 1 vs.
+row block 2) with respect to the synonym categories (i.e., predicted name is in a synonym/synonyms\_cluster-relation to the target object) vs.
+same\_cluster (i.e., predicted name is in response set).
+\end{itemize}
+
+\paragraph{Wrong predictions}
+Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
+		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
+	\toprule
+	Model--Vocab	& GTtrain  
+	&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
+	\midrule
+	FRCNN--VG1600 & VG           &         0.75 &                  0.14 &                    0.11 &         0.54 &                  0.30 &                    0.16 \\
+	RCNN--MN442 & VG &         0.71 &                  0.13 &                    0.15 &         0.48 &                  0.28 &                    0.24 \\
+	\midrule \midrule
+	FRCNN--VG1600--VGMN & MN &         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+	\midrule
+	ResNet101--MN442 & MN & 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
+	ResNet101--VG1600 & MN &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+	ResNet101--VG1600 & VG &         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+	ResNet101--MN442 & VG &         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+	\bottomrule
+\end{tabular}
+\caption{Break-down of the results: Categorization of the predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
+standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
+\label{tab:exp_overview_results}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
+		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. \\
+		& 	&  cluster &  & cluster & & & cluster 
+			& cluster  &  & cluster & & & cluster \\
+		\midrule
+		FRCNN--VG1600 & VG             &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		RCNN--MN442 & VG &                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		\midrule \midrule
+		FRCNN--VG1600--VGMN & MN &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		\midrule
+		ResNet101--VGMN & MN &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101--MN442 & MN & 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101--VGMN & VG &                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101--MN442 & VG &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		\bottomrule
+	\end{tabular}
+
+	\caption{Break-down of the results for the \textit{correct} name predictions.
+\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
+\textit{hyponym\_cl}: $\hat{n}$ is a hyponym of any of the valid names (cluster).
+\textit{Synonym} and \textit{synonym\_cl} are analogous.
+\label{tab:exp_details_correct}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
+		\toprule
+		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
+		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model--Vocab & GTtrain  
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
+		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
+		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
+
+	\midrule
+	FRCNN--VG1600 & VG     &                 0.06 
+		&            0.02 &                 0.0 &                  0.16 &           0.06 &           0.49 &             0.20 &                 0.03 &            0.05 &                 0.0 &                  0.16 &           0.13 &           0.50 &             0.13 \\
+	FRCNN--MN442 & VG       &                 0.06 
+		&            0.01 &                 0.0 &                  0.15 &           0.06 &           0.60 &             0.13 &                 0.02 &            0.02 &                 0.0 &                  0.13 &           0.11 &           0.60 &             0.11 \\
+	\midrule \midrule
+	FRCNN--VG1600--VGMN & MN &                 0.14 
+		&            0.01 &                 0.0 &                  0.12 &           0.05 &           0.50 &             0.17 &                 0.11 &            0.03 &                 0.0 &                  0.16 &           0.11 &           0.50 &             0.11 \\
+	\midrule
+		ResNet101--VGMN & MN		&                 0.11 &             0.0 &                 0.0 &                  0.12 &           0.01 &           0.64 &             0.11 &                 0.03 &             0.0 &                 0.0 &                  0.12 &           0.05 &           0.69 &             0.10 \\
+	ResNet101--MN442 & MN &                 0.09 
+		&             0.0 &                 0.0 &                  0.13 &           0.02 &           0.63 &             0.13 &                 0.05 &             0.0 &                 0.0 &                  0.15 &           0.07 &           0.62 &             0.12 \\
+	ResNet101--VGMN & VG &                 0.10 
+			&             0.0 &                 0.0 &                  0.06 &           0.02 
+			&           0.69 &             0.12 
+		&  0.04 
+			&             0.0 &                 0.0 &                  0.03 &           0.06 
+			&           0.67 &             0.20 \\ 
+	ResNet101--MN442 & VG &                 0.08 &             0.0 &                 0.0 &                  0.07 &           0.03 &           0.69 &             0.13 &                 0.01 &             0.0 &                 0.0 &                  0.06 &           0.08 &           0.62 &             0.23 \\
+	\bottomrule
+\end{tabular}
+\caption{Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
+\end{table*}
+
 \subsection{[TBC] Generalization Ability: OpenImages}

### 2019-12-03 verification_phase0/merge_and_clean_csv.py
fix weird elizabethville bug; add same_object-nofillers column

@@ -27,8 +27,8 @@ else:
 
 if write_csv:
 
-    name_annotations_paths = [(i, '1_crowdsourced/results/{}/name_annotations.csv'.format(i)) for i in BATCHES]
-    assignments_paths = [(i, '1_crowdsourced/results/{}/per_assignment.csv'.format(i)) for i in BATCHES]
+    name_annotations_paths = [(i, '1_crowdsourced/results/{}/name_annotations_ANON.csv'.format(i)) for i in BATCHES]
+    assignments_paths = [(i, '1_crowdsourced/results/{}/per_assignment_ANON.csv'.format(i)) for i in BATCHES]
 
     print("Merging dataframes...")
 
@@ -45,18 +45,24 @@ if write_csv:
 
     print('Merged into name_annotations of {} rows.'.format(len(name_annotations)))
 
+    # Weird bug fix: elizabethville is not a filler
+    name_annotations.at[name_annotations['name'] == 'elizabethville','control_type'] = np.nan
+
     # Create "no-filler" variants of same_object and name_cluster:
     print("Creating columns without fillers")
     fillers = {}
     for i, row in tqdm(name_annotations.iterrows()):
+        key = (row['image'], row['object'])
+        if key not in fillers:
+            fillers[key] = []
         if isinstance(row['control_type'], str) and row['control_type'] != 'vg_majority' and not row['control_type'].startswith('syn'):
-            key = (row['image'], row['object'])
-            if key not in fillers:
-                fillers[key] = []
             fillers[key].append(row['name'])
     name_annotations['name_cluster-nofillers'] = name_annotations['name_cluster'].copy()
     for i, row in tqdm(name_annotations.iterrows()):
         name_annotations.at[i,'name_cluster-nofillers'] = [n for n in row['name_cluster-nofillers'] if n not in fillers[(row['image'], row['object'])]]
+    name_annotations['same_object-nofillers'] = name_annotations['same_object'].copy()
+    for i, row in tqdm(name_annotations.iterrows()):
+        name_annotations.at[i,'same_object-nofillers'] = {n: row['same_object-nofillers'][n] for n in row['same_object-nofillers'] if n not in fillers[(row['image'], row['object'])]}
 
 
     assignments_dfs = []
@@ -92,8 +98,8 @@ if write_csv:
     name_annotations_anon = name_annotations.copy()
     assignments_anon = assignments.copy()
[…]

### 2019-12-03 verification_phase0/merge_and_clean_csv.py
Revert part of commit a3166c6

@@ -27,8 +27,8 @@ else:
 
 if write_csv:
 
-    name_annotations_paths = [(i, '1_crowdsourced/results/{}/name_annotations_ANON.csv'.format(i)) for i in BATCHES]
-    assignments_paths = [(i, '1_crowdsourced/results/{}/per_assignment_ANON.csv'.format(i)) for i in BATCHES]
+    name_annotations_paths = [(i, '1_crowdsourced/results/{}/name_annotations.csv'.format(i)) for i in BATCHES]
+    assignments_paths = [(i, '1_crowdsourced/results/{}/per_assignment.csv'.format(i)) for i in BATCHES]
 
     print("Merging dataframes...")
 
@@ -98,8 +98,8 @@ if write_csv:
     name_annotations_anon = name_annotations.copy()
     assignments_anon = assignments.copy()
     for i, workerid in enumerate(name_annotations_anon['workerid'].unique()):
-        name_annotations_anon.replace(to_replace={'workerid': {workerid: 'Worker{}'.format(i)}}, inplace=True)
-        assignments_anon.replace(to_replace={'workerid': {workerid: 'Worker{}'.format(i)}}, inplace=True)
+        name_annotations_anon.replace(to_replace={'workerid': {workerid: 'worker{}'.format(i)}}, inplace=True)
+        assignments_anon.replace(to_replace={'workerid': {workerid: 'worker{}'.format(i)}}, inplace=True)
 
     with open(os.path.join(out_path, 'name_annotations_ANON.csv'), 'w+') as outfile:
         name_annotations_anon.to_csv(outfile, index=False)

### 2019-12-04 papers/ACL2020/experiments.tex
[ACL2020] fixes hyper-hypo bug in experiments.tex
[ACL2020] experiments.tex

@@
 	\midrule
-	FRCNN--VG1600 & VG     &                 0.06 
-		&            0.02 &                 0.0 &                  0.16 &           0.06 &           0.49 &             0.20 &                 0.03 &            0.05 &                 0.0 &                  0.16 &           0.13 &           0.50 &             0.13 \\
-	FRCNN--MN442 & VG       &                 0.06 
-		&            0.01 &                 0.0 &                  0.15 &           0.06 &           0.60 &             0.13 &                 0.02 &            0.02 &                 0.0 &                  0.13 &           0.11 &           0.60 &             0.11 \\
+	FRCNN--VG1600 & VG     &                 6 
+		&            2 & 0 &                   16 &           6 &           49 &             20 &                 3 &            5 & 0 &                   16 &           13 &           50 &             13 \\
+	FRCNN--MN442 & VG       &                 6 
+		&            1 & 0 &                   15 &           6 &           60 &             13 &                 2 &            2 & 0 &                   13 &           11 &           60 &             11 \\
 	\midrule \midrule
-	FRCNN--VG1600--VGMN & MN &                 0.14 
-		&            0.01 &                 0.0 &                  0.12 &           0.05 &           0.50 &             0.17 &                 0.11 &            0.03 &                 0.0 &                  0.16 &           0.11 &           0.50 &             0.11 \\
+	FRCNN--VG1600--VGMN & MN &                 14 
+		&            1 & 0 &                   12 &           5 &           50 &             17 &                 11 &            3 & 0 &                   16 &           11 &           50 &             11 \\
 	\midrule
-		ResNet101--VGMN & MN		&                 0.11 &             0.0 &                 0.0 &                  0.12 &           0.01 &           0.64 &             0.11 &                 0.03 &             0.0 &                 0.0 &                  0.12 &           0.05 &           0.69 &             0.10 \\
-	ResNet101--MN442 & MN &                 0.09 
-		&             0.0 &                 0.0 &                  0.13 &           0.02 &           0.63 &             0.13 &                 0.05 &             0.0 &                 0.0 &                  0.15 &           0.07 &           0.62 &             0.12 \\
-	ResNet101--VGMN & VG &                 0.10 
-			&             0.0 &                 0.0 &                  0.06 &           0.02 
-			&           0.69 &             0.12 
-		&  0.04 
-			&             0.0 &                 0.0 &                  0.03 &           0.06 
-			&           0.67 &             0.20 \\ 
-	ResNet101--MN442 & VG &                 0.08 &             0.0 &                 0.0 &                  0.07 &           0.03 &           0.69 &             0.13 &                 0.01 &             0.0 &                 0.0 &                  0.06 &           0.08 &           0.62 &             0.23 \\
+		ResNet101--VGMN & MN		&                 11 & 0 &  0 &                   12 &           1 &           64 &             11 &                 3 & 0 &  0 &                   12 &           5 &           69 &             10 \\
+	ResNet101--MN442 & MN &                 9 
+		& 0 &  0 &                   13 &           2 &           63 &             13 &                 5 & 0 &  0 &                   15 &           7 &           62 &             12 \\
+	ResNet101--VGMN & VG &                 10 
+			& 0 &  0 &                   6 &           2 
+			&           69 &             12 
+		&  4 
+			& 0 &  0 &                   3 &           6 
+			&           67 &             20 \\ 
+	ResNet101--MN442 & VG &                 8 & 0 &  0 &                   7 &           3 &           69 &             13 &                 1 & 0 &  0 &                   6 &           8 &           62 &             23 \\
 	\bottomrule
 \end{tabular}
-\caption{Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
+\caption{Results in \%. Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
 \end{table*}

### 2019-12-04 papers/ACL2020/manynames.tex
[ACL2020] adds comment to gbt's comments in manynames.tex

@@
 names and see how things change.)}
+	\cs{We saw in the pilot that it does change in relation to the number of responses.
+I think it would be helpful for the whole story if we could show quantitatively that we need many annotations per instance to get a reliable entry-level name (and that this may depend on the domain; that the entry-level is different from the VG name we have already calculated).
+I would not use the verified data for this, and each round could correspond to a sample, i.e., we draw 9 vs.
+18 vs.
+17 vs.
+36 samples.}
 	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz} \gbt{According to my data, there are 415 entry-level names (=entry-level names for canonical object; could extend definition to all objects if need be).

### 2019-12-04 proc_data_phase0/verification/insert_verification_column.py
maintain old way of clustering as well

@@ -82,21 +82,21 @@ def cluster_from_similarity_matrix(similarities):
     # 3. threshold of majority (>.5)
 
 
-if True:    # new clustering
-    scores_per_name['same_object'] = scores_per_name['same_object'].apply(lambda x: {key: sum(x[key])/len(x[key]) for key in x})
-    for (img, name), row in scores_per_name.iterrows():
-        scores_per_name.at[(img, name), 'same_object'] = {name: row['same_object']}
-    scores_per_image = scores_per_name.reset_index().groupby('image').agg({'same_object': lambda x: {key: d[key] for d in x for key in d}})
-    for img, row in scores_per_image.iterrows():
-        scores_per_image.at[img,'same_object'] = cluster_from_similarity_matrix(row['same_object'])
-        # TODO Rename this col, also below.
+# Old way:
+scores_per_name['same_object_majority'] = scores_per_name['same_object'].apply(lambda x: {k: Counter(x[k]).most_common(1)[0][0] for k in x})
+scores_per_name['name_cluster_majority'] = scores_per_name['same_object_majority'].apply(lambda x: tuple(sorted(k for k in x if x[k] == 1)))
 
-    print("\nScores_per_image:", len(scores_per_image))
-    print(scores_per_image[:10].to_string())
+# New way:
+scores_per_name['same_object'] = scores_per_name['same_object'].apply(lambda x: {key: sum(x[key])/len(x[key]) for key in x})
+for (img, name), row in scores_per_name.iterrows():
+    scores_per_name.at[(img, name), 'same_object'] = {name: row['same_object']}
+scores_per_image = scores_per_name.reset_index().groupby('image').agg({'same_object': lambda x: {key: d[key] for d in x for key in d}})
+for img, row in scores_per_image.iterrows():
+    scores_per_image.at[img,'same_object'] = cluster_from_similarity_matrix(row['same_object'])
+    # TODO Rename this col, also below.
 
-else:   # old, majority based 'clustering'
-    scores_per_name['same_object_majority'] = scores_per_name['same_object'].apply(lambda x: {k: Counter(x[k]).most_common(1)[0][0] for k in x})
-    scores_per_name['name_cluster_majority'] = scores_per_name['same_object_majority'].apply(lambda x: tuple(sorted(k for k in x if x[k] == 1)))
+print("\nScores_per_image:", len(scores_per_image))
+print(scores_per_image[:10].to_string())
 
[…]

### 2019-12-04 proc_data_phase0/verification/insert_verification_column.py
add 'can_be_same_object' also for single-name images

@@ -109,6 +109,7 @@ for img, row in tqdm(manynames.iterrows(), total=len(manynames)):
         for name in names_for_img: # (there's only one though)
             manynames.at[img, 'verified'][name] = {'cluster': [name],
                                                'adequacy': 1.0,
+                                               'can_be_same_object': [name],
                                                'inadequacy_type': None,
                                                 'cluster_id': 0,
                                                 'cluster_weight': 1.0,

### 2019-12-04 papers/ACL2020/experiments.tex
[ACL2020] Updates analysis results in experiments.tex

@@
 	\midrule
-	FRCNN--VG1600 & VG           &         0.75 &                  0.14 &                    0.11 &         0.54 &                  0.30 &                    0.16 \\
-	RCNN--MN442 & VG &         0.71 &                  0.13 &                    0.15 &         0.48 &                  0.28 &                    0.24 \\
+	FRCNN--VG1600 & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
+	FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
 	\midrule \midrule
-	FRCNN--VG1600--VGMN & MN &         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+	FRCNN--VG1600--VGMN & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+	 &         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
 	\midrule
-	ResNet101--MN442 & MN & 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-	ResNet101--VG1600 & MN &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-	ResNet101--VG1600 & VG &         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-	ResNet101--MN442 & VG &         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+	ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
+	 &         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
+	ResNet101--VGMN & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+	 &         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
+	ResNet101--VGMN & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+	 &         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
+	ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+	 &         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
 	\bottomrule
 \end{tabular}
-\caption{Break-down of the results: Categorization of the predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
+\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
 standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
@@
 		\toprule
-		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. &  same &  syn. &  syn. &  hyper. &  hypo. &  hypo. \\
+		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
 		& 	&  cluster &  & cluster & & & cluster 
@@
 		\midrule
-		FRCNN--VG1600 & VG             &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		RCNN--MN442 & VG &                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		FRCNN--VG1600 & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		 &                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
+		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		 &                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
 		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		FRCNN--VG1600--VGMN & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		 &                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
 		\midrule
-		ResNet101--VGMN & MN &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		ResNet101--MN442 & MN & 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		ResNet101--VGMN & VG &                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		ResNet101--MN442 & VG &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101--VGMN & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		 &                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
+		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		  &                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
+		ResNet101--VGMN & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		 &                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
+		ResNet101--MN442 & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
 		\bottomrule
@@
 	\caption{Break-down of the results for the \textit{correct} name predictions.
+Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
 \textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hyponym\_cl}: $\hat{n}$ is a hyponym of any of the valid names (cluster).
+\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
 \textit{Synonym} and \textit{synonym\_cl} are analogous.
@@
 	\midrule
-	FRCNN--VG1600 & VG     &                 6 
-		&            2 & 0 &                   16 &           6 &           49 &             20 &                 3 &            5 & 0 &                   16 &           13 &           50 &             13 \\
-	FRCNN--MN442 & VG       &                 6 
-		&            1 & 0 &                   15 &           6 &           60 &             13 &                 2 &            2 & 0 &                   13 &           11 &           60 &             11 \\
+	FRCNN--VG1600 & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
+	FRCNN--MN442 & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
 	\midrule \midrule
-	FRCNN--VG1600--VGMN & MN &                 14 
-		&            1 & 0 &                   12 &           5 &           50 &             17 &                 11 &            3 & 0 &                   16 &           11 &           50 &             11 \\
+	FRCNN--VG1600--VGMN & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
 	\midrule
-		ResNet101--VGMN & MN		&                 11 & 0 &  0 &                   12 &           1 &           64 &             11 &                 3 & 0 &  0 &                   12 &           5 &           69 &             10 \\
-	ResNet101--MN442 & MN &                 9 
-		& 0 &  0 &                   13 &           2 &           63 &             13 &                 5 & 0 &  0 &                   15 &           7 &           62 &             12 \\
-	ResNet101--VGMN & VG &                 10 
-			& 0 &  0 &                   6 &           2 
-			&           69 &             12 
-		&  4 
-			& 0 &  0 &                   3 &           6 
-			&           67 &             20 \\ 
-	ResNet101--MN442 & VG &                 8 & 0 &  0 &                   7 &           3 &           69 &             13 &                 1 & 0 &  0 &                   6 &           8 &           62 &             23 \\
+	ResNet101--VGMN & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
+	ResNet101--MN442 & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
+	ResNet101--VGMN & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
+	ResNet101--MN442 & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
 	\bottomrule
 \end{tabular}
-\caption{Results in \%. Break-down of the results for the \textit{wrong} name predictions.  \label{tab:exp_details_wrong}}
+\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
 \end{table*}

### 2019-12-04 papers/ACL2020/acl2020_main.tex
add verification image to appendix

@@
 
-\section{ManyNames: Entry-Level Names and their Alternatives}
+\section{ManyNames: A Source for Entry-Level Names}
 \label{sec:manynames}
@@
 
+\begin{figure*}[t]
+	\centering
+	\includegraphics[width=\textwidth]{images/verification-interface.pdf}
+	\caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
+	\label{fig:verification-interface}
+\end{figure*}
+
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-04 papers/ACL2020/manynames.tex
add rough and too long description of verification gathering

@@
 
-@mw
+\mw{Below can be shortened no doubt; but could also be moved to appendix. Plz. let me know what you consider the most appropriate (I'm an ACL noobie).}
+
+Although the initial data gathering phase involved some very basic quality control (detecting repeated names, empty text fields, typos), we had no rigorous way of ascertaining that our participants were providing adequate names for the intended object.
+Given our high number of annotators in phase 1 we decided to simply discard names that were entered by only one annotator.
+Moreover, for images where all 36 annotators entered the same name we decided to take this name to be adequate. 
+That still leaves 19427 images, with on average 4 names each, to be properly verified, which we did as follows.
+
+We conducted a second round of annotation where we asked people whether each name for a given image was adequate and, if not, what type of inadequacy it was.
+Moreover, we asked them to indicate which names were likely intended for the same real-world object.
+The task interface is shown in figure~\ref{fig:verification-interface} in the appendix.
+Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate rage faces.
+We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
+When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
+We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.
+
+Because the quality of the data we gather in this phase will be essential for gaining insight into our data from phase one, as well as for evaluating computational object naming models (section~\ref{sec:experiments}), we set up a rigorous quality control protocol.
+Every task included between 10\% and 20\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
+Participants would get a warning if, upon submitting their results, their accuracy on these items was below 90\%, and the advice to not do any more tasks of this type if it was below 80\%.
+After every round we blocked annotators with low (<90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.
+
+We implemented our task on Amazon Mechanical Turk (\url{https://mturk.com}).
+We relied on 255 mostly recurring workers, who did a total of 9491 published tasks.
+Each task would present the worker with 6 or 7 images, for a total of between 20 and 30 names.
+We offered a reward of \$0.50 with an additional bonus of \$0.15 if all control items were answered correctly as extra incentive (which happened about half the time).
+Our approach was valued by the workers for the interesting task, natural interface and good reward.
+
+\mw{Maybe the following should go in 3.3 analysis? I think it fits here though.}
+We reached high inter-annotator agreement: adequacy judgments (encoded on a scale from 0 to 2) have a standard deviation of 0.19, with the proportion of annotators agreeing on ``adequate'' being 88\%; the proportion of annotators agreeing on inadequacy type (the 4 options) is 86\%, and this agreement is 94\% on the judgments of whether two names were intended for the same object.
+Bearing in mind that the latter often required our participants to do some kind of mind-reading -- which object could someone who entered an inadequate name plausibly have in mind?
+-- this level is agreement is very high.
+
+\mw{Probably the following should go to 3.3 analysis}
+For our analysis below we aggregate our judgments of adequacy by taking the mean, and judgments of inadequacy type by taking the majority (also counting ``none'' if there was no inadequacy).
+As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
+For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
+This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
+However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
+For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
+A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
+\mw{But this is not as bad as it sounds!
+It's often quite plausible, e.g., that food names the pizza, not the topping!}
+This way, our method may slightly underestimate the number of names per object.
+(The alternative -- soft clustering, where each name could potentially be in multiple clusters -- risks overestimating the number of named objects in an image.)
+
+\mw{I realize the foregoing is quite cryptical... Sorry no more time to work on this today!}
 
@@
 \cs{@gbt @mw}
+
 \begin{itemize}

### 2019-12-05 papers/ACL2020/experiments.tex
visualization of change in predictions

@@
 \paragraph{Wrong predictions}
+
+\begin{figure}[t]
+\includegraphics[scale=.6]{images/FRCNN_change_matrix.jpg}
+\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
+\end{figure}
+
 Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}

### 2019-12-05 papers/ACL2020/experiments.tex
more visualization

@@
 
-\begin{figure}[t]
-\includegraphics[scale=.6]{images/FRCNN_change_matrix.jpg}
+\begin{figure*}[t]
+\includegraphics[scale=.5]{images/FRCNN-1600-442_change_matrix.jpg}
+\includegraphics[scale=.5]{images/FRCNN_change_matrix.jpg}
+\includegraphics[scale=.5]{images/FRCNN-ResNet_change_matrix.jpg}
+\includegraphics[scale=.5]{images/FRCNN-ResNet-VG_change_matrix.jpg}
+
 \caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
-\end{figure}
+\end{figure*}
 

### 2019-12-05 papers/ACL2020/experiments.tex
matrices with order error categories

--- 2019-12-05 papers/ACL2020/experiments.tex
@@
 
-\begin{figure}[t]
-\includegraphics[scale=.6]{images/FRCNN_change_matrix.jpg}
+\begin{figure*}[t]
+\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
+\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
+\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
+\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
+
 \caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
-\end{figure}
+\end{figure*}
 

### 2019-12-05 papers/ACL2020/experiments.tex

@@
 
-	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
+	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:matrices}}
 \end{figure}
@@
 Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}
+
+\paragraph{How do predictions change?} Figure \ref{fig:matrices} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
+For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
+Observations:
+\begin{itemize}
+\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
+\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
+Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
+(top right matrix)
+\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
+This is less the case when ResNet is finetuned on VG annotations.
+\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
+\end{itemize}
 

### 2019-12-05 papers/ACL2020/experiments.tex
new table: results for high and low agreement entry level names

@@
 	\small
+\begin{tabular}{lrrr||rrr}
+\toprule
+&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
+\midrule
+       FRCNN--VG1600\_VG &      0.95 &          0.02 &            0.03 &     0.64 &         0.24 &           0.12 \\
+        FRCNN--MN442\_VG &      0.90 &          0.02 &            0.09 &     0.61 &         0.24 &           0.15 \\
+         \midrule \midrule
+ FRCNN--VG1600--VGMN\_MN &      0.95 &          0.01 &            0.04 &     0.73 &         0.16 &           0.11 \\
+ \midrule 
+     ResNet101--VGMN\_VG &      0.88 &          0.02 &            0.10 &     0.49 &         0.24 &           0.28 \\
+     ResNet101--VGMN\_MN &      0.90 &          0.02 &            0.09 &     0.57 &         0.19 &           0.24 \\
+    ResNet101--MN442\_MN &      0.90 &          0.01 &            0.09 &     0.58 &         0.20 &           0.22 \\
+\bottomrule
+\end{tabular}
+\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} for objects with a high agreement entry-level name and less agreement entry-level names.
+\label{tab:errors_agreement}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
 	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}

### 2019-12-05 papers/ACL2020/experiments.tex

--- 2019-12-05 papers/ACL2020/experiments.tex
@@
 	\small
+\begin{tabular}{lrrr||rrr}
+\toprule
+&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
+\midrule
+       FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
+        FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
+        		\midrule \midrule
+ FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
+ 		\midrule 
+     ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
+     ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
+    ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
+\bottomrule
+
+\end{tabular}
+\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:errors_agreement}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
 	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}

### 2019-12-05 papers/ACL2020/manynames.tex

@@
 We can't really use collection synsets, can we?
-Those are not really object classes?}
+Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''.
+Matthijs is on it.}
 	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs.
@@
 3).
-(i.e.,\ entry-level names cannot be derived from a few annotators) \gbt{My guess is that it will be pretty constant the moment you have 9 annotators, as in round 0.
-Plan: report percentage of overlap with VG name (72\%); if you want, we can estimate something based on the annotated data, but this would be more like sampling from all annotations (randomly sample 1, 2, 3, ...
-names and see how things change.)}
-	\cs{We saw in the pilot that it does change in relation to the number of responses.
-I think it would be helpful for the whole story if we could show quantitatively that we need many annotations per instance to get a reliable entry-level name (and that this may depend on the domain; that the entry-level is different from the VG name we have already calculated).
-I would not use the verified data for this, and each round could correspond to a sample, i.e., we draw 9 vs.
-18 vs.
-17 vs.
-36 samples.}
+(i.e.,\ entry-level names cannot be derived from a few annotators).
+\gbt{UPDATE:}
+          \begin{itemize}
+          \item The average change in most frequent name across rounds is 20\% (SD 2.4\%) -- i.e.
+even having 9 names only assures you to get the entry-level name for 80\% of the objects on average.
+\gbt{The data would be more compelling if we did proper sampling (samples of 1, 2, 3, ...
+names).
+Matthijs is on it.
+}
+          \end{itemize}
 	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz} \gbt{According to my data, there are 415 entry-level names (=entry-level names for canonical object; could extend definition to all objects if need be).

### 2019-12-05 papers/ACL2020/acl2020_main.tex
small paragraph on faster rcnn models

--- 2019-12-03 papers/ACL2020/acl2020_main.tex
@@
 \newcommand{\mn}{ManyNames\xspace}
+\newcommand{\vg}{VisualGenome\xspace}
 
@@
 
-\appendix
+%\appendix
+%
+%\section{Appendices}
+%\label{sec:appendix}
+%Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
+%Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
+%Upon acceptance, the appendices come after the references, as shown here.
+%
+%\paragraph{\LaTeX-specific details:}
+%Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
+%
+%
+%\section{Supplemental Material}
+%\label{sec:supplemental}
+%Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
+%Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
 
-\section{Appendices}
-\label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
+\bibliographystyle{acl_natbib}
+\bibliography{naming}
+\end{document}
 
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-\end{document}
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-05 papers/ACL2020/experiments.tex
small paragraph on faster rcnn models

@@
 \paragraph{Models}
+
+We test two object detection models that are trained with a different vocabulary:
+
+\begin{itemize}
+\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
+The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
+
+\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
+We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
+\end{itemize}
+
+We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
+
+\begin{itemize}
+\item ...
+\end{itemize}
 

### 2019-12-05 papers/ACL2020/introduction.tex
[ACL2020] first rough draft of introduction

\cs{need to make clear the diff btw objects meaning the concept and meaning an instance}

Real-world objects, being members of many categories, can be called by many names (e.g.,\ an apple can be called \name{apple, fruit, food} etc.). 
In \langvis research (\lv), the choice of a particular name for an object is a pervasive task---it underlies virtually all tasks which model how speakers use language to refer to objects in the world, such as image description, visual question answering, etc. 
%
\lv methods are generally based on object detection or image classification models (or the visual features extracted from them) which were pre-trained towards predicting the single correct label of objects. The set of labels are often determined rather arbitrarily---it may contain very specific (e.g.,\ \name{goblet, gyromitra}) as well as "basic-level" labels (e.g., \name{bus}) (cf. the inventory of the ILSVRC challenges; \citealt{ILSVRC15}).

This approach has its justification in that models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ shape--pointed vs. slightly pointed). 
It is, however, different from predicting the natural name of an object, 
because, as has been found in numerous studies in psychology, humans have a preference towards a particular name (\textit{entry-level name}, e.g.,\ \name{apple}) when naturally calling an object  \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}. 
Entry-level names have hereby usually been considered to be an attribute of concrete \textit{concepts} (e.g.,\ penguin, duck), where the choice of a concept's entry-level name depends on factors such as its typicality with respect to its basic-level category (bird). \cs{Need to check Jolicoeur and their experiments} 
Crucially, though, as our analysis also shows (ManyNames analysis), human object naming is \textit{instance}-dependent---contextual visual features (see also \citet{graf2016animal}) may humans have choose different names for object instances of the same concrete concept, and have them even disagree in their choice for the same instance \cs{real example here with duck, bird}.

Despite its relevance in \lv, the challenge of instance-based naming variation has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modelling natural object naming (they only provide very few names). 
Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialised methods implementing the taxonomic view (?)\cite{Ordonez:2016}. \cs{check paper}

In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and address the problem of automatically predicting those. %, i.e.,\ the name that humans naturally prefer to call an object.  
Specifically, and in contrast to previous works, we 
(i) take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image. 
(ii) examine in how far standard models in computer vision, namely object detection or image classification models, do already learn entry-level names by being trained on images labelled with rather \textit{arbitrary} object names. XXX
For this purpose, we use \mn, a new dataset of real-world images, built on top of \vg, which was  annotated with a large number\ $(36)$ of object names by means of a crowdsourcing study.

Our contributions are: 
(i) We present our extension of the \mn dataset that augments all collected object names with verification information, which allows an in-depth analysis of naming models on the task of object naming. 
(ii) Theoretical:
(a) We show that entry-level names should be derived on the instance-level as opposed to the XXX level \cs{(TO SHOW: entry-level names are different for the same "class" @Sina) (contrast to psychological studies)}
(b) We need many name annotations to derive the entry-level name (contrast to few annotations in L+V and computer vision; \cs{TO SHOW: entry-level name of an instance varies depending on the number of annotations/instance)}
(iii) Practical:
(a) Object detectors trained on "arbitrary" natural object names do learn entry-level names to some extend (as expected: they learn the shared features leading to entry-level \cs{-- can we show that mistakes are rather class-based? i.e., tendency towards a certain name for each class?)}
(b) To predict entry-level names without annotating a huge amount of training examples, it is possible to fine-tune (iii) on \mn. We show that \cs{(say something about mistakes not made anymore). }

### 2019-12-05 proc_data_phase0/verification/insert_verification_column.py
add commented out pie chart code

@@ -6,6 +6,7 @@ from tqdm import tqdm
 import numpy as np
 import random
 from sklearn import cluster
+from matplotlib import pyplot as plt
 
 from itertools import chain, combinations
 
@@ -44,6 +45,12 @@ print(manynames[:10].to_string())
 
 print("\nVerifications:", len(verifications))
 print(verifications[:10].to_string())
+
+## Pie chart of error distribution :)
+# verifications['inadequacy_type_level'] = verifications['inadequacy_type'].apply(str) + verifications['adequacy'].apply(str)
+# verifications['inadequacy_type_level'].value_counts().plot.pie()
+# plt.show()
+# quit()
 
 # verifications['matrix'] = verifications['same_object'].copy()
 # for i, row in verifications.iterrows():

### 2019-12-05 papers/ACL2020/acl2020_main.tex

@@
 % To streamline frequently used terms:
+\newcommand{\langvis}{language\ \&\ vision\xspace}
+\newcommand{\lv}{L\&V\xspace}
 \newcommand{\mn}{ManyNames\xspace}
@@
 
-\title{Something with Objects and Names}
+\newcommand{\cat}[1]{\textsc{#1}}
+\newcommand{\name}[1]{\textsl{#1}}
+
+\title{How to Name a Real-World Object, and how not}
 
@@
 \label{sec:intro}
-%\input{introduction}
-
-\begin{itemize}
-	\item Real-world objects, being members of many categories, can be called by many names.
-Nonetheless, humans have a preferred name which they use to call an object (CITE) (\textsl{entry-level name}).
-	\item ...
-	\item ...
-	\item ...
-	\item We adopt an empirical view on the notion of entry-level name, and define it  as the most frequently given name by humans who were asked to name an object depicted in an image. 
-	\item ...
-	\item ...
-	\item This paper:
-	\item We address the problem of (entry-level) object naming, and use the \mn dataset that provides many name annotations per object to obtain entry-level names and their alternatives for each object instance.
-	\item Contributions are XXX:
-	\item[(1)] We obtain verified name responses for each object in \mn, along with name sets of originally wrongly identified objects. 
-	\item We provide an analysis of naming variation: Agreement, number of alternatives, ...
-	\item[(2)] ...
-\end{itemize}
+\input{introduction}
 

### 2019-12-06 papers/ACL2020/introduction.tex
[ACL2020] introduction draft v0.2

@@
 
-Real-world objects, being members of many categories, can be called by many names (e.g.,\ an apple can be called \name{apple, fruit, food} etc.). 
-In \langvis research (\lv), the choice of a particular name for an object is a pervasive task---it underlies virtually all tasks which model how speakers use language to refer to objects in the world, such as image description, visual question answering, etc.
+Real-world objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
+In \langvis research (\lv), the choice of a particular name for an object is a pervasive task---it underlies virtually all tasks which model how speakers use language to refer to objects in the world, such as image description, visual question answering, referring expression generation, etc.
 %
 \lv methods are generally based on object detection or image classification models (or the visual features extracted from them) which were pre-trained towards predicting the single correct label of objects.
-The set of labels are often determined rather arbitrarily---it may contain very specific (e.g.,\ \name{goblet, gyromitra}) as well as "basic-level" labels (e.g., \name{bus}) (cf.
-the inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+The set of labels are often determined rather arbitrarily---it may contain very specific (e.g.,\ \name{goblet, gyromitra}) as well as "basic-level" labels (e.g., \name{bus}; cf.
+the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
 
@@
 It is, however, different from predicting the natural name of an object, 
-because, as has been found in numerous studies in psychology, humans have a preference towards a particular name (\textit{entry-level name}, e.g.,\ \name{apple}) when naturally calling an object  \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
+because, as has been found in numerous studies in psychology, humans have a preference towards a particular name (\textit{entry-level name}, e.g.,\ \name{duck}) when naturally calling an object  \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
 Entry-level names have hereby usually been considered to be an attribute of concrete \textit{concepts} (e.g.,\ penguin, duck), where the choice of a concept's entry-level name depends on factors such as its typicality with respect to its basic-level category (bird).
 \cs{Need to check Jolicoeur and their experiments}
-Crucially, though, as our analysis also shows (ManyNames analysis), human object naming is \textit{instance}-dependent---contextual visual features (see also \citet{graf2016animal}) may humans have choose different names for object instances of the same concrete concept, and have them even disagree in their choice for the same instance \cs{real example here with duck, bird}.
+Crucially, though, as we will empirically show, human object naming is \textit{instance}-dependent---contextual visual features (see also \citealt{graf2016animal}) may humans have prefer different names for object instances of the same concrete concept, and have them even disagree in their choice for the same instance \cs{insert image example here with duck, bird}.
 
 Despite its relevance in \lv, the challenge of instance-based naming variation has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modelling natural object naming (they only provide very few names).
-Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialised methods implementing the taxonomic view (?)\cite{Ordonez:2016}.
+Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialized methods implementing the taxonomic view (?)\cite{Ordonez:2016}.
 \cs{check paper}
 
-In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and address the problem of automatically predicting those.
+In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and systematic insights into  the problem of retraining or fine-tuning object detection models (and features in transfer learning) such that they capture a natural vocabulary and linguistic preferences in naming.
 %, i.e.,\ the name that humans naturally prefer to call an object.
@@
 (i) take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
-(ii) examine in how far standard models in computer vision, namely object detection or image classification models, do already learn entry-level names by being trained on images labelled with rather \textit{arbitrary} object names.
-XXX
-For this purpose, we use \mn, a new dataset of real-world images, built on top of \vg, which was  annotated with a large number\ $(36)$ of object names by means of a crowdsourcing study.
+(ii) We examine in how far standard models in computer vision, namely object detection and image classification models, do learn entry-level naming by being trained on images labeled with rather \textit{arbitrary} (as opposed to entry-level) object names.
+\cs{add sth based on results - how to fine-tune or whether it's possible to fine-tune; how readily available they are to be used for transfer learning, the standard method in \lv}
+
+We use \mn, a new dataset of real-world images, built on top of \vg, which provides an excellent resource for our study, since it was  annotated with a large number\ $(36)$ of object names by means of a crowdsourcing study.
 

### 2019-12-06 papers/ACL2020/introduction.tex
[ACL2020] +Gemma's comments: introduction draft v0.3

@@
 
-Real-world objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
-In \langvis research (\lv), the choice of a particular name for an object is a pervasive task---it underlies virtually all tasks which model how speakers use language to refer to objects in the world, such as image description, visual question answering, referring expression generation, etc.
+Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
+In \langvis research (\lv), the choice of a particular name for an object is a ubiquitous problem---it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering, referring expression generation, etc.
 %
-\lv methods are generally based on object detection or image classification models (or the visual features extracted from them) which were pre-trained towards predicting the single correct label of objects.
-The set of labels are often determined rather arbitrarily---it may contain very specific (e.g.,\ \name{goblet, gyromitra}) as well as "basic-level" labels (e.g., \name{bus}; cf.
-the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+\lv methods are generally based on object detection or image classification models (or the visual features extracted from them) that were pre-trained towards predicting the single correct label of objects.
+The set of labels are often determined rather arbitrarily---it may contain very specific (e.g.,\ \name{goblet, gyromitra}) as well as "basic-level" labels (e.g., \name{bus}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
 
-This approach has its justification in that models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ shape--pointed vs.
+This pre-training strategy has its justification in that computer vision models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp--pointed vs.
 slightly pointed).
@@
 
-Despite its relevance in \lv, the challenge of instance-based naming variation has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modelling natural object naming (they only provide very few names).
+Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modelling natural object naming (they only provide very few names).
 Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialized methods implementing the taxonomic view (?)\cite{Ordonez:2016}.
@@
 (i) take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
-(ii) We examine in how far standard models in computer vision, namely object detection and image classification models, do learn entry-level naming by being trained on images labeled with rather \textit{arbitrary} (as opposed to entry-level) object names.
+(ii) We examine in how far standard models in computer vision, namely object detection and image classification models, do learn entry-level naming by being trained on images labeled with rather \textit{arbitrary}\cs{choose better term} (as opposed to entry-level) object names.
 \cs{add sth based on results - how to fine-tune or whether it's possible to fine-tune; how readily available they are to be used for transfer learning, the standard method in \lv}
@@
 (ii) Theoretical:
-(a) We show that entry-level names should be derived on the instance-level as opposed to the XXX level \cs{(TO SHOW: entry-level names are different for the same "class" @Sina) (contrast to psychological studies)}
+(a) We show that entry-level names should be derived on the instance-level as opposed to the XXX level \cs{(TO SHOW: entry-level names are different for the same "class" @Sina or @Matthijs?) (contrast to psychological studies)}
 (b) We need many name annotations to derive the entry-level name (contrast to few annotations in L+V and computer vision; \cs{TO SHOW: entry-level name of an instance varies depending on the number of annotations/instance)}
-(iii) Practical:
-(a) Object detectors trained on "arbitrary" natural object names do learn entry-level names to some extend (as expected: they learn the shared features leading to entry-level \cs{-- can we show that mistakes are rather class-based?
+(iii) Technical:
+(a) Object detectors trained on "arbitrary"\cs{choose better term} natural object names do learn entry-level names to some extend (as expected: they learn the shared features leading to entry-level \cs{-- can we show that mistakes are rather class-based?
 i.e., tendency towards a certain name for each class?)}

### 2019-12-06 papers/ACL2020/related.tex
[ACL2020] adds tex for related work

[Sectioning to be revised]

As we outline in the following, our work on natural object naming is of relevance to research in psychology, \langvis and computer vision.

\paragraph{(Entry-Level) Object Names}

cognitive science/psychology:\\
- levels of specificity\\
- basic-level vs. entry-level\\ 
- object naming studies

Language + Vision:\\
Ordonez et al., Zarriess \& Schlangen, ... \\
- Our work: empirical notion of entry-level

\paragraph{}
In psychology and cognitive science, the study of (entry-level) naming is well-established (CITE). 
Studies have usually used prototypical line drawings of members of different \textit{basic-level} categories (e.g., a duck, a robin, a penguin, etc. are all members of \cat{birds}) 
\cite{jolicoeur1984pictures}, and examined the influence of an object's typicality with respect to its category on the natural choice of its name: highly typical objects (e.g.,\ a robin) have been found to be preferably named by their basic-level category (\name{bird}), while for atypical members a subordinate category (e.g.,\ \name{penguin}) is preferred. 
As such, entry-level names have been considered being an attribute of concrete \textit{concepts} (e.g.,\ penguin). \cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}
% prototypical visual features common to all its instances (e.g.,\ apples are round, pears are ... (CHECK)).

\paragraph{Visual Object Recognition in Computer Vision}
- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

### 2019-12-06 papers/ACL2020/acl2020_main.tex
[ACL2020] adds tex for related work

@@
 \label{sec:related}
-%\input{related}
-
-[Sectioning to be revised]
-
-\paragraph{(Entry-Level) Object Names}
-Cognitive Science/psycholinguistics:\\
-- levels of specificity\\
-- basic-level vs. entry-level\\
-- object naming studies
-Language + Vision:\\
-Ordonez et al., Zarriess \& Schlangen, ... \\
-- Our work: empirical notion of entry-level
-
-\paragraph{Visual Object Recognition in Computer Vision}
-- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
-- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
-- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?
+\input{related}
 

### 2019-12-06 papers/ACL2020/acl2020_main.tex
add crowdsource task screenshot back in

@@
 %
-%\section{Appendices}
-%\label{sec:appendix}
-%Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-%Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-%Upon acceptance, the appendices come after the references, as shown here.
-%
-%\paragraph{\LaTeX-specific details:}
-%Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-%
-%
-%\section{Supplemental Material}
-%\label{sec:supplemental}
-%Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-%Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
+\section{Appendices}
+\label{sec:appendix}
+Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
+Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
+Upon acceptance, the appendices come after the references, as shown here.
+
+\paragraph{\LaTeX-specific details:}
+Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
+
+\section{Supplemental Material}
+\label{sec:supplemental}
+Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
+Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=\textwidth]{images/verification-interface.pdf}
+  \caption{A screenshot of our verification task interface. Up to ten names could be shown for an image in this way (the number of available colors in the second task would increase accordingly).}
+  \label{fig:verification-interface}
+\end{figure*}
 

### 2019-12-06 papers/ACL2020/manynames.tex
add commented out verification interface figure back; Carina why u remove?
tweaks mainly to section 3.2

@@
 The task interface is shown in figure~\ref{fig:verification-interface} in the appendix.
-Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate rage faces.
+Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate emotes.
 We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
@@
 
-Because the quality of the data we gather in this phase will be essential for gaining insight into our data from phase one, as well as for evaluating computational object naming models (section~\ref{sec:experiments}), we set up a rigorous quality control protocol.
-Every task included between 10\% and 20\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
-Participants would get a warning if, upon submitting their results, their accuracy on these items was below 90\%, and the advice to not do any more tasks of this type if it was below 80\%.
-After every round we blocked annotators with low (<90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.
+Because the quality of the data we gather in this phase will be essential for gaining insight into the ManyNames dataset, as well as for evaluating computational models (section~\ref{sec:experiments}), we conducted rigorous quality control.
+Every task included around 15\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
+When trying to submit their results, participants would get a warning if their accuracy on these items was below 90\%, and the advice to stop doing these tasks if it was below 80\%, with the option to double-check their responses.
+They would get a bonus of \$0.15 if all control items were answered correctly (happened about half the time).
+After every round we blocked annotators with low ($<$90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.
 
-We implemented our task on Amazon Mechanical Turk (\url{https://mturk.com}).
-We relied on 255 mostly recurring workers, who did a total of 9491 published tasks.
-Each task would present the worker with 6 or 7 images, for a total of between 20 and 30 names.
-We offered a reward of \$0.50 with an additional bonus of \$0.15 if all control items were answered correctly as extra incentive (which happened about half the time).
-Our approach was valued by the workers for the interesting task, natural interface and good reward.
+We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}). 
+Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{|ll|ll|}
+		\hline
+		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
+		Images: & 19427 &
+			Annotators: & 255 \\
+		Img-name pairs: & 69356 &
+			Annotators/task: & $\geq$ 3 \\
+		Tasks: & 3052 &
+			Adeq. mean: & \hspace{-3em}.80 (std .093)\\
+		Images/task: & 6-7 &			
+			Agreement (adeq.) & 88\% \\ 
+		Names/task: & 20-30 &
+			Agr. (inadeq. type): & 86\% \\
+		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
+			Agr. (same-obj): & 94\% \\
+		\hline
+	\end{tabular}
+	\caption{Verification task overview.}
+	\label{tab:verification-numbers}
+\end{table}
+Average name adequacy, encoded on a scale $[0,1]$, is 0.80 with small standard deviation (0.093). 
+Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
+This level is agreement is high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
+Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
+\begin{figure}[t]
+	\centering
+	\hspace*{.2\columnwidth}\includegraphics[width=.7\columnwidth]{images/verification_piechart.pdf}
+	\caption{Verification results (counting individual annotations). Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
+	\label{fig:verification-piechart}
+\end{figure}
 
-\mw{Maybe the following should go in 3.3 analysis? I think it fits here though.}
-We reached high inter-annotator agreement: adequacy judgments (encoded on a scale from 0 to 2) have a standard deviation of 0.19, with the proportion of annotators agreeing on ``adequate'' being 88\%; the proportion of annotators agreeing on inadequacy type (the 4 options) is 86\%, and this agreement is 94\% on the judgments of whether two names were intended for the same object.
-Bearing in mind that the latter often required our participants to do some kind of mind-reading -- which object could someone who entered an inadequate name plausibly have in mind?
--- this level is agreement is very high.
-
-\mw{Probably the following should go to 3.3 analysis}
-For our analysis below we aggregate our judgments of adequacy by taking the mean, and judgments of inadequacy type by taking the majority (also counting ``none'' if there was no inadequacy).
-As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
-For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
-This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
-For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
-A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
-\mw{But this is not as bad as it sounds!
-It's often quite plausible, e.g., that food names the pizza, not the topping!}
-This way, our method may slightly underestimate the number of names per object.
-(The alternative -- soft clustering, where each name could potentially be in multiple clusters -- risks overestimating the number of named objects in an image.)
-
-\mw{I realize the foregoing is quite cryptical... Sorry no more time to work on this today!}
+% We relied on 255 mostly recurring workers, who did a total of 9491 published tasks.
+% Each task would present the worker with 6 or 7 images, for a total of between 20 and 30 names.
+% We offered a reward of \$0.50 with an additional bonus of \$0.15 if all control items were % answered correctly as extra incentive (which happened about half the time).
+% Our approach was valued by the workers for the interesting task, natural interface and good reward.
 
@@
 \paragraph{Of Verification Annotations}
+
+We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
+As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
+For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
+This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
+However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
+For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
+A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
+\mw{But this is not as bad as it sounds!
+It's often quite plausible, e.g., that food names the pizza, not the topping!}
+This way, our method may slightly underestimate the number of names per object.
+The alternative -- soft clustering, where each name could potentially be in multiple clusters -- would risk overestimating the number of names per object, as well as the number of named objects in an image.
+
+\mw{I realize the foregoing is quite cryptical... Sorry no more time to work on this today!}
+
 \cs{@gbt @mw}

### 2019-12-06 analysis/analysis_verification_matthijs.py
add analysis file used by matthijs

@@ -1,0 +1,136 @@
+# global variables
+ADEQUACY_THRESHOLD = 0.5
+CANONICAL_THRESHOLD = 0.5
+NUM_SAMPLES_FOR_STABILITY = 5
+
+import os
+import sys
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+from ast import literal_eval
+from collections import Counter
+import itertools
+from tqdm import tqdm
+
+from analysis import load_results
+
+import random
+random.seed(12345)
+
+pd.set_option('display.max_colwidth', 180)
+pd.set_option('expand_frame_repr', False)
+
+
+#csvfile='../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
+#csvfile='kk.csv'
+csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
+df = load_results.load_cleaned_results(csvfile)
+
+# df = pd.read_csv(csvfile,
+#     converters={'responses_r0': eval, 'responses_r1': eval, 'responses_r2': eval, 'responses_r3': eval, 'verified': eval},
+#     sep="\t")
+# df['spellchecked_min2'] = df['spellchecked_min2'].apply(eval)
+
+
+total_objects=len(df)
+print("Total objects: ", total_objects)
+print(df.columns)
+
+
+
+if True:
+    print("WARNING: LOOKING ONLY AT PART OF THE DATA FOR DEBUGGING")
+    df = df[:500]
+
+
+# get necessary data from csv file
+adequacies=[] # number of adequate names (total)
+tot_names=0; tot_ad=0 # total n of names; n of -adequate names (see threshold above)
+list_n_ad_names=[] # number of adequate names per canonical object
+list_entry_names=[] # entry names for each canonical object (cluster 0)
+list_freqs_entry_name=[] # entry names for each canonical object (cluster 0)
+no_entry_lev=0
+for row in df.itertuples():
+    name_freqs=row.spellchecked_min2
+    #print(name_freqs)
+    # find entry-level name; this should be done for the canonical object,
+    # but I can't recover the info from the verified column (name data in a dictionary),
+    # so I use the one from all data and check if the entry level name form those data is in cluster 0
+    # there are only 700 imgs where the most frequent name is not in cluster 0; TODO: check these cases; mend this
+    entry_name,entry_freq=name_freqs.most_common(1)[0] # returns tuple, e.g. ('man',11) # problem: what if there's a tie of most common names? (happens, but rarely)
[…]

### 2019-12-06 papers/ACL2020/manynames.tex
basic analysis for entry-level names in sec 3.3

@@
 
-\paragraph{Of ManyNames:} 
 \cs{+ @sz?}\\
@@
 \cs{Results aimed to show that we need \underline{multiple} annotations per object \underline{instance} to get the entry-level name}
-\begin{itemize}
-	\item Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level) \gbt{But, what's an object class in our data?
+
+\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?} In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.
+
+\paragraph{Entry-level Names in ManyNames:} As shown in Table \ref{tab:stat-entry-level}, ManyNames provides a large vocabulary of names (7970) for 25K objects.
+Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on.
+The vocabulary of entry-level names is drastically smaller and contains only 442 types.
+This small set, however, covers at least 50\% of the objects in VisualGenome, i.e.
+almost 2M objects in VisualGenome are mentioned in a region descriptions with one of these 442 entry-level names.
+
+\begin{figure}
+	\centering
+	\small
+	\begin{tabular}{p{3cm}p{3cm}}
+%VisualGenome+ManyNames & \cite{snodgrass}\\
+\centering
+\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
+\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
+ bird\ (27),  duck\ (8) & duck (33), bird (3)\\
+\end{tabular}
+
+	\caption{Different naming preferences for different instances of the same class (duck)\label{fig:duck}}
+\end{figure}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{p{5cm}l}
+		\toprule		
+\# objects in MN & 25,315\\
+total vocab  &  7,970\\
+entry-level vocab & 442\\
+\# objects with entry-level name in VG & $\sim$ 2M (50\%)\\
+\midrule
+av. agreement all names & 34.9\%\\
+av. agreement entry-level names & 75.2\%\\
+av. agreement entry-level cluster & 42.3\%\\
+\midrule
+av. adequacy all names & 0.81\\
+av. adequacy entry-level names & 0.97 \\
+av. adequacy entry-level cluster & 0.94 \\
+\bottomrule	
+	\end{tabular}
+	\caption{Basic statistics for entry-level names in MN}
+	\label{tab:stat-entry-level}
+\end{table}
+
+\paragraph{Entry-level Names are Instance-Dependent:} In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name.
+The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names).
+Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \textit{duck} is named \textit{bird} by most annotators.
+We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g.
+\textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).
+\sz{does this solve this?
+Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)} \gbt{But, what's an object class in our data?
 We can't really use collection synsets, can we?
@@
 Matthijs is on it.}
+
+\begin{itemize}
 	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs.
@@
           \end{itemize}
-	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz} \gbt{According to my data, there are 415 entry-level names (=entry-level names for canonical object; could extend definition to all objects if need be).
-Are your 442 names the most frequent names for some image?
-Else, we could do the experiments with the entry-level names as the vocabulary (but it's probably too late now).}
-	\item ...
+
 \end{itemize}

### 2019-12-06 papers/ACL2020/related.tex

@@
-[Sectioning to be revised]
-
 As we outline in the following, our work on natural object naming is of relevance to research in psychology, \langvis and computer vision.
@@
 
-cognitive science/psychology:\\
-- levels of specificity\\
-- basic-level vs. entry-level\\ 
-- object naming studies
+%cognitive science/psychology:\\
+%- levels of specificity\\
+%- basic-level vs. entry-level\\ 
+%- object naming studies
+%
+%Language + Vision:\\
+%Ordonez et al., Zarriess \& Schlangen, ... \\
+%- Our work: empirical notion of entry-level
 
-Language + Vision:\\
-Ordonez et al., Zarriess \& Schlangen, ... \\
-- Our work: empirical notion of entry-level
+In psychology and cognitive science, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}.
+The typicality of the object with respect to this basic-level category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level category (\name{bird}), while for atypical objects  (e.g.,\ \name{penguin}) the more specific name corresponds to the entry-level category.
+This strictly taxonomic view suggests that entry-level names generally hold for all instances a category (e.g.,\ penguin). 
+\newcite{Ordonez:2016} take up this view and learn to transfer an object's category detected by an object recognition system to its natural name, using external resources like corpus statistics. 
+In contrast, our work exploits actual naming data for instances of real-world objects and tests object naming model on ManyNames, a corpus with robust name annotations from many different speakers.
+This dataset is comparable to picture naming data, though we focus on real-world objects in images instead of prototypical line drawings as in e.g.\ \cite{rossion2004revisiting}, 
+ \newcite{zarriess-schlangen:2017} learn a naming model from names produced in referring expressions to real-world objects, but they do not have access to name annotations from (many) different speakers and adopt very simply evaluation measures (like accuracy).
+ This work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
+ \sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}
 
-\paragraph{}
-In psychology and cognitive science, the study of (entry-level) naming is well-established (CITE). 
-Studies have usually used prototypical line drawings of members of different \textit{basic-level} categories (e.g., a duck, a robin, a penguin, etc. are all members of \cat{birds}) 
-\cite{jolicoeur1984pictures}, and examined the influence of an object's typicality with respect to its category on the natural choice of its name: highly typical objects (e.g.,\ a robin) have been found to be preferably named by their basic-level category (\name{bird}), while for atypical members a subordinate category (e.g.,\ \name{penguin}) is preferred.
-As such, entry-level names have been considered being an attribute of concrete \textit{concepts} (e.g.,\ penguin).
+%members of different \textit{basic-level} categories (e.g., a duck, a robin, a penguin, etc. are all members of \cat{birds}) 
+% \newcite{rohde2012communicating} and \newcite{graf2016animal} investigate naming in context and find that the specificity of a name is dependent on the taxonomic relatedness of other objects in context.
+
  \cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}

### 2019-12-06 papers/ACL2020/introduction.tex
[ACL2020] moves bird-duck example to intro

@@
-\cs{need to make clear the diff btw objects meaning the concept and meaning an instance}
+\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
 
@@
 \cs{Need to check Jolicoeur and their experiments}
-Crucially, though, as we will empirically show, human object naming is \textit{instance}-dependent---contextual visual features (see also \citealt{graf2016animal}) may humans have prefer different names for object instances of the same concrete concept, and have them even disagree in their choice for the same instance \cs{insert image example here with duck, bird}.
+Crucially, though, as we will empirically show, human object naming is \textit{instance}-dependent---contextual visual features may humans have prefer different names for object instances of the same concrete concept, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+For example, Figure~\ref{fig:duck} shows two instances of the concept duck, and when people were asked to name the highlighted object, most ($27$) people called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance.
 
-Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modelling natural object naming (they only provide very few names).
+Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modeling natural object naming (they only provide very few names).
 Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialized methods implementing the taxonomic view (?)\cite{Ordonez:2016}.
 \cs{check paper}
+%
+\begin{figure}
+	\centering
+	\small
+	\begin{tabular}{p{3cm}p{3cm}}
+		%VisualGenome+ManyNames & \cite{snodgrass}\\
+		\centering
+		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
+		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
+		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
+	\end{tabular}
 
-In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and systematic insights into  the problem of retraining or fine-tuning object detection models (and features in transfer learning) such that they capture a natural vocabulary and linguistic preferences in naming.
+	\caption{Different naming preferences for different instances of the same concept (duck)\label{fig:duck}}
+\end{figure}
+%
+In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and to give systematic insights into the problem of retraining or fine-tuning object detection models (and features in transfer learning) such that they capture a natural vocabulary and account for linguistic preferences in naming.
 %, i.e.,\ the name that humans naturally prefer to call an object.
@@
 (i) take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
-(ii) We examine in how far standard models in computer vision, namely object detection and image classification models, do learn entry-level naming by being trained on images labeled with rather \textit{arbitrary}\cs{choose better term} (as opposed to entry-level) object names.
+(ii) We examine in how far standard models in computer vision, namely object detection and image classification models, do learn entry-level naming by being trained on images labeled with rather \textit{\arbitrary} (as opposed to entry-level) object names.
 \cs{add sth based on results - how to fine-tune or whether it's possible to fine-tune; how readily available they are to be used for transfer learning, the standard method in \lv}
@@
 (iii) Technical:
-(a) Object detectors trained on "arbitrary"\cs{choose better term} natural object names do learn entry-level names to some extend (as expected: they learn the shared features leading to entry-level \cs{-- can we show that mistakes are rather class-based?
+(a) Object detectors trained on "\arbitrary" natural object names do learn entry-level names to some extend (as expected: they learn the shared features leading to entry-level \cs{-- can we show that mistakes are rather class-based?
 i.e., tendency towards a certain name for each class?)}

### 2019-12-06 papers/ACL2020/manynames.tex
a little additional note in sec3
[ACL2020] moves bird-duck example to intro

@@
 
-\begin{figure}
-	\centering
-	\small
-	\begin{tabular}{p{3cm}p{3cm}}
-%VisualGenome+ManyNames & \cite{snodgrass}\\
-\centering
-\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
-\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
- bird\ (27),  duck\ (8) & duck (33), bird (3)\\
-\end{tabular}
-
-	\caption{Different naming preferences for different instances of the same class (duck)\label{fig:duck}}
-\end{figure}
-
 \begin{table}[t]
@@
 
+\sz{somewhere we should mention these tendencies on adequacy and agreement for (non-)entry-level names shown in Table \ref{tab:stat-entry-level}}
+
 \paragraph{Of Verification Annotations}

### 2019-12-06 papers/ACL2020/acl2020_main.tex
[ACL2020] main
[ACL2020] moves bird-duck example to intro
[ACL2020] starts filling in experiments.tex

@@
 
-\title{How to Name a Real-World Object, and how not}
+% Terms that need to be replaced throughout the paper by more appropriate ones:
+\newcommand{\arbitrary}{arbitrary$_{SIC}$\xspace}
+
+\title{How to Name a Real-World Object, and how not to}
 
@@
 \label{sec:appendix}
+\iffalse
 Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
@@
 Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
+\fi
 
@@
 \label{sec:supplemental}
+\iffalse
 Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
 Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
+\fi
 

### 2019-12-06 papers/ACL2020/experiments.tex
[ACL2020] starts filling in experiments.tex

@@
 % experiments.tex
+
+\cs{todo: discuss differences between domains}
+
+Our goal is to experimentally obtain insights into the usefulness of computer vision object labeling models, that are commonly used for \lv methods, to account for natural human object naming. 
+Specifically, our research questions are
+\begin{enumerate}
+	\item Do object detection models, despite being trained on \arbitrary  
+	names, account for human object naming?\cs{repetitive}
+	\item Can image features, that were pre-trained using object detection or image classification model, be fine-tuned on \mn towards this naming task through simple transfer learning?
+Figure~\ref{fig:exp_confusions} \\
+	\cs{move to models: -- can we learn entry-level names by fine-tuning object detection models on \mn?\\
+		-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?}
+\end{enumerate}
+TO BE COVERED BY THE SUBSECTIONS BELOW:
+\begin{enumerate}
+	\item Do models prefer the entry-level name of an object over an \cs{arbitrary$\rightarrow$?} name? Table~\ref{tab:exp_VGvsMN}
+	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
+	\item What phenomena of human behavior on the object naming task of \mn do the models mirror?
+That is, which model mistakes or confusions are due to the artificial setup of the task itself, and less a failure of the model?
+(Recall that \mn serves as a \textit{proxy} for natural human object naming, since annotators were asked to name a highlighted object in an image isolated from its situative context; Section~\ref{sec:manynames}) Table~\ref{tab:exp_details_wrong} (and \ref{tab:exp_errors_agreement},  \ref{tab:exp_alternatives})
+
+	%That is, do they make similar mistakes (wrong object--maybe more salient?, related name, e.g.,~co-hyponyms)?
+	\item \cs{Not examined at the moment -- MRR and Jaccard may be re-added for this: Are valid name alternatives among the top-N predictions?}
+	%\item do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
+\end{enumerate}
+We use the \mn dataset in two ways, as analytical testbed, and for fine-tuning pre-trained image features towards entry-level name prediction.
+
+\subsection{Experimental Setup}
+\label{sect:exp_setup}
+
+\paragraph{Data}
+
+\paragraph{Models}
+We test two object detection models that are trained with a different vocabulary:
+
+\begin{itemize}
+	\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
+The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
+
+	\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
+We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
+\end{itemize}
+
+We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
+
+\begin{itemize}
+	\item ...
+\end{itemize}
+
+\paragraph{Measures}
+
+\subsection{Results}
+\label{sect:exp_results}
+
+\paragraph{Entry-Level Name Prediction}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{l@{~}|@{~}c@{~}|@{~}r@{~}r@{~}|@{~}r@{~}r@{~}}
+		\toprule
+		&  & \multicolumn{2}{c}{All} 
+		& \multicolumn{2}{c}{VG$\neq$MN}\\
+		&  & \multicolumn{2}{c}{($1072$)} 
+		& \multicolumn{2}{c}{($223$)}\\	
+		Model--Vocab	 
+		&  GTtrain &  =VG & =MN 
+		&  =VG & =MN \\ 
+		\midrule
+		FRCNN--MN442 & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
+		FRCNN--VG1600 & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
+		\midrule \midrule
+		\multicolumn{6}{c}{Classifiers: Fine-tuning pre-trained features on MN}\\
+		Features--Vocab &   \\
+		\midrule 
+		FRCNN--VG1600--VGMN & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
+		\midrule
+		ResNet101--VGMN & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
+
+		ResNet101--MN442 & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
+		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
+		ResNet101--MN442 & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
+		\bottomrule
+	\end{tabular}
+	\caption{Target vocabulary in test data: MN442.
+Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
+GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
+Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:exp_VGvsMN}.
+}
+\end{table}
+
+\paragraph{Alternative Name Prediction}
+\begin{figure}
+	\centering
+	\includegraphics[scale=.2]{images/2323938.jpg}
+	\includegraphics[scale=.2]{images/2322259.jpg}
+	\includegraphics[scale=.2]{images/2371657.jpg}
+
+	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
+\end{figure}
+
+\cs{TODO::}
+Categorization of "errors" (see Figure~\ref{fig:mistakes}):
+\begin{enumerate}
+	\item Clear mistake \\
+	e.g.,\ rice vs. bread
+	\item Alternative name\\
+	e.g.,\ building vs. house
+	\item Alternative object \cs{(other cluster from verif data)}
+	\item Synonym\\
+	e.g.,\ plane vs. airplane
+	\item Semantically related\\
+	e.g.,\  motorcycle vs. scooter
+\end{enumerate}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
+		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model--Vocab	& GTtrain  
+		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
+		\midrule
+		FRCNN--VG1600 & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
+		FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
+		\midrule \midrule
+		FRCNN--VG1600--VGMN & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
+		\midrule
+		ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
+		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
+		ResNet101--VGMN & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
+		ResNet101--VGMN & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
+		ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
+standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
+\label{tab:exp_overview_results}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{lrrr||rrr}
+		\toprule
+		&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+		model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
+		\midrule
+		FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
+		FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
+		\midrule \midrule
+		FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
+		\midrule 
+		ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
+		ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
+		ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
+		\bottomrule
+
+	\end{tabular}
+	\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
+		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
+		& 	&  cluster &  & cluster & & & cluster 
+		& cluster  &  & cluster & & & cluster \\
+		\midrule
+		FRCNN--VG1600 & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
+		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
+		\midrule \midrule
+		FRCNN--VG1600--VGMN & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
+		\midrule
+		ResNet101--VGMN & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
+		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
+		ResNet101--VGMN & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
+		ResNet101--MN442 & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
+		\bottomrule
+	\end{tabular}
+
+	\caption{Break-down of the results for the \textit{correct} name predictions.
+Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
+\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
+\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
+\textit{Synonym} and \textit{synonym\_cl} are analogous.
+\label{tab:exp_alternatives}}
+\end{table*}
+
+\paragraph{Incorrect Predictions}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
+		\toprule
+		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
+		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model--Vocab & GTtrain  
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
+		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
+		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
+
+		\midrule
+		FRCNN--VG1600 & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
+		FRCNN--MN442 & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
+		\midrule \midrule
+		FRCNN--VG1600--VGMN & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
+		\midrule
+		ResNet101--VGMN & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
+		ResNet101--MN442 & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
+		ResNet101--VGMN & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
+		ResNet101--MN442 & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
+\end{table*}
+
+\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
+For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
+Observations:
+\begin{itemize}
+	\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
+	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
+Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
+(top right matrix)
+	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
+This is less the case when ResNet is finetuned on VG annotations.
+	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
+\end{itemize}
+
+\begin{figure*}[t]
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
+
+	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
+\end{figure*}
+
+\subsection{Discussion}
+\label{sect:exp_discussion}
 
@@
 
+\iffalse
 We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
@@
 \end{tabular}
-\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:errors_agreement}}
+\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
 \end{table*}
@@
 
+\fi
+
 \subsection{[TBC] Generalization Ability: OpenImages}

### 2019-12-06 papers/ACL2020/experiments.tex
[ACL2020] more in experiments.tex

@@
 \paragraph{Models}
-We test two object detection models that are trained with a different vocabulary:
+We test two object detection models which both use the Faster R-CNN architecture \cite{fasterrcnn2015}, and were initialized with features that were pre-trained on $1K$~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
+They were both trained on \vg, but, essentially, differ in their target vocabulary. 
+FRCNN--VG1600\footnote{We used the code and model of \citeauthor{anderson2018updown}'s \shortcite{anderson2018updown} bottom-up attention model, available at  \url{github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} \cite{anderson2018updown} uses a vocabulary of $1600$~object classes \cs{add how it was derived}.
+For FRCNN--MN442, we pre-process the \vg data as in \citeauthor{anderson2018updown} \cs{right, @Sina?}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:?}).
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
 
-\begin{itemize}
-	\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
-
-	\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
-We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
-\end{itemize}
-
-We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
-
-\begin{itemize}
-	\item ...
-\end{itemize}
+Using transfer learning, we further test a range of Vanilla object classification models consisting of multi-layer neural networks.  
+To predict the entry-level name of a target object, they are fed image features extracted for the target's bounding box, and apply softmax at the output layer that corresponds to the vocabulary of target names.
+The models differ in the pre-trained image features used for feature extraction, in the training signal, and, similarly to the FRCNN models above, in the vocabulary that we use for training them: 
+Regarding the features, we either use the FRCNN--VG1600 model above (i.e.,~the features were pre-trained on \vg), or use the ResNet-101 model that was used to initialize the FRCNN models above. 
+Note that ResNet's $1K$~object classes capture subordinate categories of ImageNet leaf nodes (e.g.,~Siberian husky, American black bear). 
+Vocab + signal:
 

### 2019-12-06 papers/ACL2020/introduction.tex
[ACL2020] starts filling in experiments.tex
[ACL2020] more in experiments.tex

@@
 \cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
+\cs{need to discuss problematic of standard evaluation procedure of CV models}
 
@@
 Despite its relevance in \lv, the challenge of instance-based natural naming has been overseen, and most \lv datasets not necessarily provide enough information to make progress on the problem of modeling natural object naming (they only provide very few names).
-Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted (i) taxonomic view (?) and (ii) developed specialized methods implementing the taxonomic view (?)\cite{Ordonez:2016}.
-\cs{check paper}
+Research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted the view that (i) entry-level names arise on the conceptual level, and (ii) developed specialized methods \cite{Ordonez:2016}.
+%To our knowledge, work that gives systematic insights into the ability of standard object recognition models to account for natural object naming, and in how far simple \cs{straightfoward?} re-training or transfer learning can increase this ability, is lacking.
 %

### 2019-12-07 analysis/analysis_verification_matthijs.py
finish analysis first version (based on shuffling names list).

@@ -1,7 +1,11 @@
 # global variables
-ADEQUACY_THRESHOLD = 0.5
-CANONICAL_THRESHOLD = 0.5
-NUM_SAMPLES_FOR_STABILITY = 5
+ADEQUACY_THRESHOLD = .5   # adequacy of entry name (and, in one condition, alternative names) should be at least...
+CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
+NUM_SAMPLES_FOR_STABILITY = 30
+
+SUBSAMPLE = False       # for debugging
+
+SUBSETS_TO_PLOT = ['all names', 'canonical object names']
 
 import os
 import sys
@@ -13,124 +17,138 @@ from collections import Counter
 import itertools
 from tqdm import tqdm
 
+import seaborn as sns
+
 from analysis import load_results
 
 import random
+import statistics
 random.seed(12345)
+np.random.seed(129387)
 
 pd.set_option('display.max_colwidth', 180)
 pd.set_option('expand_frame_repr', False)
 
+sns.set(font_scale=1.2)
 
-#csvfile='../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
-#csvfile='kk.csv'
-csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
-df = load_results.load_cleaned_results(csvfile)
+auxfile = 'aux/stability_samples_{}_{}_{}_{}'.format(ADEQUACY_THRESHOLD, CANONICAL_THRESHOLD, NUM_SAMPLES_FOR_STABILITY, SUBSAMPLE)
+os.makedirs('aux', exist_ok=True)
 
-# df = pd.read_csv(csvfile,
-#     converters={'responses_r0': eval, 'responses_r1': eval, 'responses_r2': eval, 'responses_r3': eval, 'verified': eval},
-#     sep="\t")
-# df['spellchecked_min2'] = df['spellchecked_min2'].apply(eval)
+recompute = not os.path.exists(auxfile) or input("Overwrite existing auxiliary file (recompute the sampling)? y/N").lower().startswith("y")
 
+settings = ['all names', 'adequate names', 'canonical object names', 'adequate canonical names']
 
-total_objects=len(df)
-print("Total objects: ", total_objects)
-print(df.columns)
+if recompute:
 
+    csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
[…]

### 2019-12-07 analysis/analysis_verification_matthijs.py
added code for analytic approach instead; messy but works.

@@ -3,7 +3,7 @@ ADEQUACY_THRESHOLD = .5   # adequacy of entry name (and, in one condition, alter
 CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
 NUM_SAMPLES_FOR_STABILITY = 30
 
-SUBSAMPLE = False       # for debugging
+SUBSAMPLE = 1000       # for debugging
 
 SUBSETS_TO_PLOT = ['all names', 'canonical object names']
 
@@ -16,6 +16,10 @@ from ast import literal_eval
 from collections import Counter
 import itertools
 from tqdm import tqdm
+
+from functools import reduce
+from operator import mul
+from math import factorial as fac, floor
 
 import seaborn as sns
 
@@ -34,121 +38,208 @@ sns.set(font_scale=1.2)
 auxfile = 'aux/stability_samples_{}_{}_{}_{}'.format(ADEQUACY_THRESHOLD, CANONICAL_THRESHOLD, NUM_SAMPLES_FOR_STABILITY, SUBSAMPLE)
 os.makedirs('aux', exist_ok=True)
 
-recompute = not os.path.exists(auxfile) or input("Overwrite existing auxiliary file (recompute the sampling)? y/N").lower().startswith("y")
+settings = ['all_names', 'entry_cluster_names']
 
-settings = ['all names', 'adequate names', 'canonical object names', 'adequate canonical names']
+#
+def majorities(n_elements, total_sum):
+    candidates = [[n] for n in range(total_sum + 1, 0, -1)]
+    solutions = []
+    while len(candidates) > 0:
+        c = candidates.pop(0)
+        if len(c) >= n_elements:
+            if sum(c) == total_sum:
+                solutions.append(c)
+        else:
+            for o in range(min(total_sum-sum(c), c[0]-1), -1, -1):
+                candidates.append(c + [o])
+    return solutions
 
-if recompute:
+# probability of majority
+def prob_majority(probs, n_names):
+    probs = [p/sum(probs) for p in probs]   # normalize
+    prob = 0.0
+    for counts in majorities(len(probs), n_names):
+        prob += reduce(mul, [prob**count for prob,count in zip(probs,counts)], 1) * fac(n_names) / reduce(mul, [fac(count) for count in counts], 1)
+    return prob
+
+def n_names_for_prob_majority(probs, threshold=.9, max_n_names=38, increment=2):
+    # time-saving shortcut: if prob[0] and prob[1] aren't so different, then even with 36 names only .85 can be reached.
[…]

### 2019-12-07 papers/ACL2020/manynames.tex
[ACL2020] more in experiments
on paragraph "Identifying entry-level names requires many annotators"

@@
 \end{figure}
+\mw{Possibly a pie-chart counting actual names and their aggregated (+thresholded) scores would be more informative than the current pie-chart, which counts original (i.e., non-aggregated) verification annotations.}
+
+We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
+As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
+For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
+This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
+However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
+For this, we need to compute clusters of names (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
+A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
+It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
+But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships (which could be gotten from, e.g., WordNet) -- rather, we care about (and asked our annotators) which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top.
+Moreover, although (hard) clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.
 
@@
 
-\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?} In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.
+\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?}
+\mw{I'd definitely put this in the introduction, and leave only a reminder here.}
+In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.
+\mw{We could also consider defining entry-level name as `the most frequent adequate name'?
+Or perhaps as `the most frequent name \emph{if it is adequate}, none otherwise'?
+Depending on what makes the narrative easier.}
+
+\mw{Also make sure to define the notion of `entry-level object', or `canonical object' perhaps? i.e., the object/cluster of the entry-level name.}
 
@@
 \textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).
+
 \sz{does this solve this?
@@
 
-\begin{itemize}
-	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs.
-1 vs.
-2 vs.
-3).
-(i.e.,\ entry-level names cannot be derived from a few annotators).
-\gbt{UPDATE:}
-          \begin{itemize}
-          \item The average change in most frequent name across rounds is 20\% (SD 2.4\%) -- i.e.
-even having 9 names only assures you to get the entry-level name for 80\% of the objects on average.
-\gbt{The data would be more compelling if we did proper sampling (samples of 1, 2, 3, ...
-names).
-Matthijs is on it.
-}
-          \end{itemize}
-
-\end{itemize}
-
 \sz{somewhere we should mention these tendencies on adequacy and agreement for (non-)entry-level names shown in Table \ref{tab:stat-entry-level}}
 
+\paragraph{Identifying entry-level names requires many annotators}
+ManyNames was collected in four rounds of 9 annotators each.
+On average, the most frequent names differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
+Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
+\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading.
+I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look.
+But I think the following is better:}
+\begin{figure}[t]
+	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
+	\caption{\mw{plot to be improved, rerun on all data, properly framed, captioned, lines becoming horizontal}}
+	\label{fig:entry-level-name-stability}
+\end{figure}
+For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the most frequent name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
+The blue line shows that, even after gathering 10 names, the entry-level name has been identified with 95\% confidence for only 69\% of objects.
+Gathering 20 names increases this to 82\%.
+The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
+by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
+Both lines level level out after gathering 23-25 names, reflecting that for 12\%-15\% of objects even gathering more than 25 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
+\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I lack a proper overview to be able to tell.}
+
+%%%%%% BY SAMPLING, FOR GEMMA:
+% For each object that has an adequate entry-level name (adequacy $<.5$ according to our Verification results), we randomly sampled (including duplicates) a list of 36 names using the proportions in ManyNames as sampling probabilities, and computed the lowest number of collected names (i.e., the lowest index in the list) after which the entry-level name would reliably remain the most frequent one.
+% We did this 30 times for each object.
+% The blue line in the figure shows that, after collecting 10 names, the entry-level name is reliably identified for on average around 85\% of objects; collecting 20 names increases this to 90\%.\footnote{
+%	But even when gathering 36 names, for around 6\% of objects this can still result in a different entry-level name.
+This reflects the existence of objects with no clear entry-level name, e.g., where two (almost) equally frequent names are both candidates.
+%	\mw{Can we quantify this?}
+%}
+%The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
+%by discarding names for other objects, the entry-level name for the intended object can be identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
+%\begin{figure}[t]
+%	\includegraphics[width=\columnwidth]{images/stability-all-05-05-spellchecked.png}
+%	\caption{}
+%	\label{fig:entry-level-name-stability}
+%\end{figure}
+
 \paragraph{Of Verification Annotations}
-
-We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
-As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
-For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
-This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
-For this, we need to compute clusters of names  (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
-A disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
-\mw{But this is not as bad as it sounds!
-It's often quite plausible, e.g., that food names the pizza, not the topping!}
-This way, our method may slightly underestimate the number of names per object.
-The alternative -- soft clustering, where each name could potentially be in multiple clusters -- would risk overestimating the number of names per object, as well as the number of named objects in an image.
-
-\mw{I realize the foregoing is quite cryptical... Sorry no more time to work on this today!}
 

### 2019-12-07 papers/ACL2020/experiments.tex

--- 2019-12-06 papers/ACL2020/experiments.tex
@@
 	names, account for human object naming?\cs{repetitive}
-	\item Can image features, that were pre-trained using object detection or image classification model, be fine-tuned on \mn towards this naming task through simple transfer learning?
+	\item Can we apply simple transfer learning on \mn to train classifiers towards this naming task by utilizing pre-trained object detection or image classification model as feature extractors?
 Figure~\ref{fig:exp_confusions} \\
@@
 \begin{enumerate}
-	\item Do models prefer the entry-level name of an object over an \cs{arbitrary$\rightarrow$?} name? Table~\ref{tab:exp_VGvsMN}
+	\item Do models prefer the entry-level name of an object over an \arbitrary name? Table~\ref{tab:exp_VGvsMN}
 	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
@@
 
-\paragraph{Data}
+\paragraph{Models}
+We test two object detection models which both use the Faster R-CNN architecture \cite{fasterrcnn2015}, and were initialized with features that were pre-trained on $1$K~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
+They were both trained on \vg, but, essentially, differ in their target vocabulary. 
+FRCNN$_{\text{VG1600}}$\footnote{We used the code and model of \citeauthor{anderson2018updown}'s \shortcite{anderson2018updown} bottom-up attention model, available at  \url{github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} \cite{anderson2018updown} uses a vocabulary of $1600$~object classes \cs{add how it was derived}.
+For FRCNN$_{\text{MN442}}$, we pre-process the \vg data as in \citeauthor{anderson2018updown} \cs{right, @Sina?}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
 
-\paragraph{Models}
-We test two object detection models that are trained with a different vocabulary:
+\cs{start to be moved to an appropriate place}
+While we consider \mn's size ($25$K instances) to be excellent for evaluation and analysis purposes, it is too small to serve as data for training object detection models from scratch, which require the learning of millions of parameters.
+It may, however, serve as training data for transfer learning. 
+\cs{end to be moved to an appropriate place}
+We assess the possibility to explicitly obtain entry-level naming models through transfer learning, by training a Vanilla object classifier on \mn using the FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN--VG442, so we only use the former model.} model as feature extractor.
+For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} 
+\cs{todo: details to architecture and training}
+To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
+The target vocabulary (VGMN, henceforth) comprises the overlap of VG1600 and the \mn names (\cs{$XX$} in total).
 
-\begin{itemize}
-	\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
-
-	\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
-We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
-\end{itemize}
-
-We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
-
-\begin{itemize}
-	\item ...
-\end{itemize}
-
-\paragraph{Measures}
-
-\subsection{Results}
-\label{sect:exp_results}
-
-\paragraph{Entry-Level Name Prediction}
+We furthermore assess the drop in effectiveness of such a Vanilla  classifier when we do not use FRCNN (trained on \vg) as feature extractor, but instead it's initialization model, i.e.,~ResNet-101. 
+\cs{Next sentence relevant here?
+Or just as detail in related work?:: (Note that ResNet's $1$K~object classes capture subordinate categories of ImageNet leaf nodes; e.g.,~Siberian husky, American black bear.)}
+As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
+\cs{Maybe the next sentences are better just in the results section, when discussing the table::} Finally, we compare against two further classifiers which are trained on the \vg labels. 
+Note that all four models are optimized on the $25$K~objects in \mn.
 
@@
 	\small
-	\begin{tabular}{l@{~}|@{~}c@{~}|@{~}r@{~}r@{~}|@{~}r@{~}r@{~}}
+	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc|cc@{~}}
 		\toprule
@@
 		& \multicolumn{2}{c}{($223$)}\\	
-		Model--Vocab	 
-		&  GTtrain &  =VG & =MN 
-		&  =VG & =MN \\ 
+		Model$_{\text{Vocab}}$ 
+		&  GTtrain &  VG & MN 
+		&  VG & MN \\ 
 		\midrule
-		FRCNN--MN442 & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
-		FRCNN--VG1600 & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
+		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
+		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
 		\midrule \midrule
-		\multicolumn{6}{c}{Classifiers: Fine-tuning pre-trained features on MN}\\
-		Features--Vocab &   \\
+		\multicolumn{6}{c}{Classifiers: Transfer learning on MN}\\
+		Features$_{\text{Vocab}}$ &   \\
 		\midrule 
-		FRCNN--VG1600--VGMN & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
 		\midrule
-		ResNet101--VGMN & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
+		ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
 
-		ResNet101--MN442 & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
-		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
-		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
-		ResNet101--MN442 & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
+		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
+		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
+		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
 		\bottomrule
 	\end{tabular}
-	\caption{Target vocabulary in test data: MN442.
-Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
-GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
-Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:exp_VGvsMN}.
-}
+	\caption{Model accuracy (in \%) on the \mn test objects.
+Vocab denotes the dataset used to induce the target vocabulary for training (the numbers give the size of the vocabulary).
+GTtrain gives the dataset that provides the ground truth labels during training, and VG and MN for testing \label{tab:exp_VGvsMN}.}
 \end{table}
+
+\paragraph{Data}
+\cs{todo after Section~\ref{sect:mn_overview} has been written.}
+\begin{itemize}
+	\item Test data: overlap of \mn and \vg test data (CITE)
+	\item Target vocabulary of test data: overlap of MN442 and VG (\cs{XX} names)
+	\item Source of label: \mn, but we compare against \vg
+\end{itemize}
+
+%\paragraph{Measures}
+
+\subsection{Results: Entry-Level Name Prediction}
+\label{sect:exp_results}
+%\paragraph{Entry-Level Name Prediction}
+Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
+We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN).
+\begin{itemize}
+	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
+	This shows that they do learn entry-level naming to some extent, despite being trained on VG, i.e.,~\arbitrary ground truth labels.
+	\cs{I would not comment on diff.
+btw.
+the two FRCNNs, it's small compared to their diffs to the classifiers, and may be also due to the diff.
+implementations, and VG1600 being trained additionally on attributes.}
+	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
+	\item \cs{?What to keep here:} The classifiers using ResNet features are the least effective, but come close to the FRCNN object detectors on entry-level naming (columns MN, GTtrain MN), or even better  (columns VG, GTtrain VG) despite being trained on a fraction of FRCNN's training size using a simple Vanilla classifier in contrast to a fully-fledged CNN architecture.
+	This confirms what we observed on the FRCNN results: and follow the pattern of learning entry-level naming  
+	\item Models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than \arbitrary name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
+\cs{overfitting?}
+	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
+\end{itemize}
+
+\subsection{Quantitative Analysis}
+\label{sect:exp_analysis}
 
@@
 	\small
-	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
 		\toprule
@@
 		\toprule
-		Model--Vocab	& GTtrain  
+		Model$_{\text{Vocab}}$	& GTtrain  
 		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
 		\midrule
-		FRCNN--VG1600 & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-		FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
+		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
+		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
 		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
 		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
 		\midrule
-		ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
+		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
 		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-		ResNet101--VGMN & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
 		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-		ResNet101--VGMN & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
 		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-		ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
 		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
@@
 	\small
-	\begin{tabular}{lrrr||rrr}
+	\begin{tabular}{l|c|rrr||rrr}
 		\toprule
-		&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
-		model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
+		& &  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+		Model$_{\text{Vocab}}$ &  GTtrain & hit &  correct &  incorrect &  hit &  correct &  incorrect \\
 		\midrule
-		FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
-		FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
+		FRCNN$_{\text{VG1600}}$ & VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
+		FRCNN$_{\text{MN442}}$ & VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
 		\midrule \midrule
-		FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
 		\midrule 
-		ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-		ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
-		ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
+		ResNet101$_{\text{VGMN}}$ & VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
+		ResNet101$_{\text{VGMN}}$ & MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
+		ResNet101$_{\text{MN442}}$ & MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
 		\bottomrule
@@
 	\small
-	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
+	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
 		\toprule
@@
 		\toprule
-		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
+		Model$_{\text{Vocab}}$ &  GTtrain & same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
 		& 	&  cluster &  & cluster & & & cluster 
@@
 		\midrule
-		FRCNN--VG1600 & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
 		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		FRCNN$_{\text{MN442}}$ & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
 		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
 		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
 		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
 		\midrule
-		ResNet101--VGMN & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
 		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{MN442}}$ & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
 		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101--VGMN & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
 		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101--MN442 & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
 		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
@@
 	\small
-	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
+	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
 		\toprule
@@
 		\toprule
-		Model--Vocab & GTtrain  
+		Model$_{\text{Vocab}}$ & GTtrain  
 		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
@@
 		\midrule
-		FRCNN--VG1600 & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-		FRCNN--MN442 & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
+		FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
+		FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
 		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
 		\midrule
-		ResNet101--VGMN & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-		ResNet101--MN442 & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-		ResNet101--VGMN & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-		ResNet101--MN442 & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
+		ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
+		ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
+		ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
+		ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
 		\bottomrule
@@
 \begin{itemize}
-\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
+\item FRCNN$_{\text{VG1600}}$: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
 The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
@@
 		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
-		Model--Vocab	 
+		Model$_{\text{Vocab}}$	 
 		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
@@
 		FRCNN--VG2500 & VG \\
-		FRCNN--VG1600 & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
+		FRCNN$_{\text{VG1600}}$ & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
 		\midrule \midrule
 		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
-		Features--Vocab & GTtrain  \\
+		Features$_{\text{Vocab}}$ & GTtrain  \\
 		\midrule 
-		FRCNN--VG1600--VGMN & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
-		FRCNN--VG1600--MN442 &  MN \\
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
+		FRCNN$_{\text{VG1600}}$--MN442 &  MN \\
 		\midrule
-		ResNet101--VGMN & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
+		ResNet101$_{\text{VGMN}}$ & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
 
 		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
-		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
-		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
+		ResNet101$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
+		ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
 		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
@@
 	\toprule
-	Model--Vocab	& GTtrain  
+	Model$_{\text{Vocab}}$	& GTtrain  
 	&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
 	\midrule
-	FRCNN--VG1600 & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
+	FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
 	FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
 	\midrule \midrule
-	FRCNN--VG1600--VGMN & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
 	 &         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
@@
 	 &         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-	ResNet101--VGMN & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+	ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
 	 &         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-	ResNet101--VGMN & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+	ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
 	 &         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
@@
 \midrule
-       FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
+       FRCNN$_{\text{VG1600}}$\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
         FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
         		\midrule \midrule
- FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
+ FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
  		\midrule 
-     ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-     ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
+     ResNet101$_{\text{VGMN}}$\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
+     ResNet101$_{\text{VGMN}}$\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
     ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
@@
 		\midrule
-		FRCNN--VG1600 & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
 		 &                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
@@
 		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
 		 &                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
 		\midrule
-		ResNet101--VGMN & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
 		 &                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
@@
 		  &                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101--VGMN & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
 		 &                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101--MN442 & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
 		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
@@
 	\midrule
-	FRCNN--VG1600 & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-	FRCNN--MN442 & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
+	FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
+	FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
 	\midrule \midrule
-	FRCNN--VG1600--VGMN & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
+	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
 	\midrule
-	ResNet101--VGMN & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-	ResNet101--MN442 & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-	ResNet101--VGMN & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-	ResNet101--MN442 & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
+	ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
+	ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
+	ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
+	ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
 	\bottomrule
@@
 
-Models compared: FRCNN--VG1600 vs. FRCNN--MN442 vs. ResNet101--XX (best Vanilla).
+Models compared: FRCNN$_{\text{VG1600}}$ vs. FRCNN$_{\text{MN442}}$ vs. ResNet101--XX (best Vanilla).

### 2019-12-07 papers/ACL2020/related.tex

@@
 
-\paragraph{(Entry-Level) Object Names}
+\paragraph{(Entry-Level) Object Naming}
 
@@
 - Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
-- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image)\\
+- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image).
+It predicts the class of the most salient object in an image.
+\\
 - Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

### 2019-12-07 papers/ACL2020/manynames.tex
improve stability plot

@@
 	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
-	\caption{\mw{plot to be improved, rerun on all data, properly framed, captioned, lines becoming horizontal}}
+	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
 	\label{fig:entry-level-name-stability}
@@
 	\item For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering).
+	\item Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. 
 \end{itemize}

### 2019-12-07 papers/ACL2020/manynames.tex
update section below plot

@@
 For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the most frequent name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
-The blue line shows that, even after gathering 10 names, the entry-level name has been identified with 95\% confidence for only 69\% of objects.
-Gathering 20 names increases this to 82\%.
+The blue line shows that, even after gathering 10 names, the entry-level name has been confidently identified for only 68\% of objects.
+Gathering 20 names increases this to 78\%.
 The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level level out after gathering 23-25 names, reflecting that for 12\%-15\% of objects even gathering more than 25 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
+Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
 \mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I lack a proper overview to be able to tell.}

### 2019-12-07 papers/ACL2020/manynames.tex
clarify stability remark

@@
 \end{figure}
-For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the most frequent name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
+For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
 The blue line shows that, even after gathering 10 names, the entry-level name has been confidently identified for only 68\% of objects.
@@
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
-\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I lack a proper overview to be able to tell.}
+Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
+\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper.
+I think the difference between sample majority name and population majority name could be useful?
+I lack a proper overview to be able to tell.}
 

### 2019-12-07 papers/ACL2020/manynames.tex
final attempt at clarification; good night!

@@
 Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
-\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper.
-I think the difference between sample majority name and population majority name could be useful?
-I lack a proper overview to be able to tell.}
+\mw{@cs, @sz, @gbt: A closely related (but different) question this immediately brings to mind (of a critical reviewer?) is: how sure are we, for a given object, given the particular names we gathered, that the most frequent name in our sample (what we \emph{call} the entry-level name) is indeed the most frequent name in the population (what actually \emph{is} the entry-level name, right?)?
+Should we address this question earlier?
+I think the stats will look very similar (though they're not the same): that for 15-20\% of objects we really aren't sure.}
 

### 2019-12-07 papers/ACL2020/manynames.tex
[ACL2020] comment@MW

@@
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
+Both lines level level out well below 100\%, reflecting that for 15\%-20\% \cs{Can you compute that individually for each domain?} of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
 \mw{@cs, @sz, @gbt: A closely related (but different) question this immediately brings to mind (of a critical reviewer?) is: how sure are we, for a given object, given the particular names we gathered, that the most frequent name in our sample (what we \emph{call} the entry-level name) is indeed the most frequent name in the population (what actually \emph{is} the entry-level name, right?)?

### 2019-12-07 papers/ACL2020/manynames.tex
ahem.

--- 2019-12-07 papers/ACL2020/manynames.tex
@@
 For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
-The blue line shows that, even after gathering 10 names, the entry-level name has been confidently identified for only 68\% of objects.
+The blue line shows that, even after gathering 10 names, the majority name is this likely to be the entry-level name for only 68\% of objects (put differently: for the remaining 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
 Gathering 20 names increases this to 78\%.
@@
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
+Both lines level level out well below 100\%, reflecting that for 15\%-20\% \cs{Can you compute that individually for each domain?} of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
 \mw{@cs, @sz, @gbt: A closely related (but different) question this immediately brings to mind (of a critical reviewer?) is: how sure are we, for a given object, given the particular names we gathered, that the most frequent name in our sample (what we \emph{call} the entry-level name) is indeed the most frequent name in the population (what actually \emph{is} the entry-level name, right?)?

### 2019-12-08 papers/ACL2020/analysis.tex
restructures section 4 into 4 (modeling), 5 (analysis); redoes explanation of models

--- 2019-12-06 papers/ACL2020/experiments.tex
@@
-% experiments.tex
-
-\cs{todo: discuss differences between domains}
-
-Our goal is to experimentally obtain insights into the usefulness of computer vision object labeling models, that are commonly used for \lv methods, to account for natural human object naming. 
-Specifically, our research questions are
-\begin{enumerate}
-	\item Do object detection models, despite being trained on \arbitrary  
-	names, account for human object naming?\cs{repetitive}
-	\item Can image features, that were pre-trained using object detection or image classification model, be fine-tuned on \mn towards this naming task through simple transfer learning?
-Figure~\ref{fig:exp_confusions} \\
-	\cs{move to models: -- can we learn entry-level names by fine-tuning object detection models on \mn?\\
-		-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?}
-\end{enumerate}
-TO BE COVERED BY THE SUBSECTIONS BELOW:
-\begin{enumerate}
-	\item Do models prefer the entry-level name of an object over an \cs{arbitrary$\rightarrow$?} name? Table~\ref{tab:exp_VGvsMN}
-	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
-	\item What phenomena of human behavior on the object naming task of \mn do the models mirror?
-That is, which model mistakes or confusions are due to the artificial setup of the task itself, and less a failure of the model?
-(Recall that \mn serves as a \textit{proxy} for natural human object naming, since annotators were asked to name a highlighted object in an image isolated from its situative context; Section~\ref{sec:manynames}) Table~\ref{tab:exp_details_wrong} (and \ref{tab:exp_errors_agreement},  \ref{tab:exp_alternatives})
-
-	%That is, do they make similar mistakes (wrong object--maybe more salient?, related name, e.g.,~co-hyponyms)?
-	\item \cs{Not examined at the moment -- MRR and Jaccard may be re-added for this: Are valid name alternatives among the top-N predictions?}
-	%\item do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
-\end{enumerate}
-We use the \mn dataset in two ways, as analytical testbed, and for fine-tuning pre-trained image features towards entry-level name prediction.
-
-\subsection{Experimental Setup}
-\label{sect:exp_setup}
-
-\paragraph{Data}
-
-\paragraph{Models}
-We test two object detection models that are trained with a different vocabulary:
-
-\begin{itemize}
-	\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
-
-	\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
-We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
-\end{itemize}
-
-We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
-
-\begin{itemize}
-	\item ...
-\end{itemize}
-
-\paragraph{Measures}
-
-\subsection{Results}
-\label{sect:exp_results}
-
-\paragraph{Entry-Level Name Prediction}
-
-\begin{table}[t]
-	\centering
-	\small
-	\begin{tabular}{l@{~}|@{~}c@{~}|@{~}r@{~}r@{~}|@{~}r@{~}r@{~}}
-		\toprule
-		&  & \multicolumn{2}{c}{All} 
-		& \multicolumn{2}{c}{VG$\neq$MN}\\
-		&  & \multicolumn{2}{c}{($1072$)} 
-		& \multicolumn{2}{c}{($223$)}\\	
-		Model--Vocab	 
-		&  GTtrain &  =VG & =MN 
-		&  =VG & =MN \\ 
-		\midrule
-		FRCNN--MN442 & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
-		FRCNN--VG1600 & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
-		\midrule \midrule
-		\multicolumn{6}{c}{Classifiers: Fine-tuning pre-trained features on MN}\\
-		Features--Vocab &   \\
-		\midrule 
-		FRCNN--VG1600--VGMN & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
-		\midrule
-		ResNet101--VGMN & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
-
-		ResNet101--MN442 & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
-		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
-		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
-		ResNet101--MN442 & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Target vocabulary in test data: MN442.
-Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
-GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
-Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:exp_VGvsMN}.
-}
-\end{table}
-
-\paragraph{Alternative Name Prediction}
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
-
-	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
-\end{figure}
-
-\cs{TODO::}
-Categorization of "errors" (see Figure~\ref{fig:mistakes}):
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.,\ plane vs. airplane
-	\item Semantically related\\
-	e.g.,\  motorcycle vs. scooter
-\end{enumerate}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model--Vocab	& GTtrain  
-		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
-		\midrule
-		FRCNN--VG1600 & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-		FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
-		\midrule
-		ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-		ResNet101--VGMN & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-		ResNet101--VGMN & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-		ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{lrrr||rrr}
-		\toprule
-		&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
-		model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
-		\midrule
-		FRCNN--VG1600\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
-		FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
-		\midrule \midrule
-		FRCNN--VG1600--VGMN\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
-		\midrule 
-		ResNet101--VGMN\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-		ResNet101--VGMN\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
-		ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
-		\bottomrule
-
-	\end{tabular}
-	\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
-		& 	&  cluster &  & cluster & & & cluster 
-		& cluster  &  & cluster & & & cluster \\
-		\midrule
-		FRCNN--VG1600 & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
-		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
-		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
-		\midrule
-		ResNet101--VGMN & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101--VGMN & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101--MN442 & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
-		\bottomrule
-	\end{tabular}
-
-	\caption{Break-down of the results for the \textit{correct} name predictions.
-Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
-\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
-\textit{Synonym} and \textit{synonym\_cl} are analogous.
-\label{tab:exp_alternatives}}
-\end{table*}
-
-\paragraph{Incorrect Predictions}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
-		\toprule
-		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
-		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model--Vocab & GTtrain  
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
-		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
-		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
-
-		\midrule
-		FRCNN--VG1600 & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-		FRCNN--MN442 & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
-		\midrule \midrule
-		FRCNN--VG1600--VGMN & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
-		\midrule
-		ResNet101--VGMN & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-		ResNet101--MN442 & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-		ResNet101--VGMN & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-		ResNet101--MN442 & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
-\end{table*}
-
-\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
-For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
-Observations:
-\begin{itemize}
-	\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
-	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
-Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
-(top right matrix)
-	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
-This is less the case when ResNet is finetuned on VG annotations.
-	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
-\end{itemize}
-
-\begin{figure*}[t]
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
-
-	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
-\end{figure*}
-
-\subsection{Discussion}
-\label{sect:exp_discussion}
-
-\iffalse
-\cs{under construction}
-\begin{itemize}
-	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
-	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
-	\item ... 
-	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
-	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
-	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
-	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
-	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data.
-\end{itemize}
-\fi
-
-\iffalse
-We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
-Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
-Can object detection models, trained on arbitrary names, account for human object naming?
-\begin{itemize}
-	\item Do they predict the entry-level name?
-	\item Are valid name alternatives among the top-N predictions?
-	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
-	-- naming an alternative object (maybe more salient)\\
-	-- predicting a semantically related name
-	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
-	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
-	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
-	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
-\end{itemize}
-
-\subsection{Experimental Setup}
-\label{sect:exp_setup}
-
-\paragraph{Data}
-
-\paragraph{Models}
-
-We test two object detection models that are trained with a different vocabulary:
-
-\begin{itemize}
-\item FRCNN--VG1600: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
-
-\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
-We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
-\end{itemize}
-
-We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
-
-\begin{itemize}
-\item ...
-\end{itemize}
-
-\paragraph{Measures}
-
-\subsection{[TBC] Predicting Entry-Level Names}
-\label{sect:exp_entry}
-Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?
-
-Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
-		Model--Vocab	 
-		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
-		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
-		\midrule
-		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
-		FRCNN--VG2500 & VG \\
-		FRCNN--VG1600 & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
-		\midrule \midrule
-		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
-		Features--Vocab & GTtrain  \\
-		\midrule 
-		FRCNN--VG1600--VGMN & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
-		FRCNN--VG1600--MN442 &  MN \\
-		\midrule
-		ResNet101--VGMN & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
-
-		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
-		ResNet101--VGMN\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
-		ResNet101--VGMN\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
-		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Target vocabulary in test data: MN442.
-Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
-GTtrain denotes the dataset from which the ground truth labels are obtained during \textit{training}.
-MRR is mean reciprocal rank; J is Jaccard score.
-Note that we considered all name responses in MN, including those with $\text{count}(name)<2$\label{tab:entrylevels}.
-}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l@{~}|rrrr}
-		\toprule
-		... \\
-		\midrule
-		Domain	 & ... \\ 
-		\midrule
-		All           \\
-		home           \\
-		food           \\
-		buildings      \\
-		vehicles       \\
-		animals\_plants \\
-		clothing       \\
-		people         \\
-		\bottomrule
-	\end{tabular}
-	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
-\end{table*}
-
 \subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
@@
 
-\fi
-
-\subsection{[TBC] Generalization Ability: OpenImages}
-\label{sect:exp_openimages}
-Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
-
-Models compared: FRCNN--VG1600 vs. FRCNN--MN442 vs. ResNet101--XX (best Vanilla).
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-08 papers/ACL2020/experiments.tex
adds supp-mat.tex file
restructures section 4 into 4 (modeling), 5 (analysis); redoes explanation of models

@@
 \cs{todo: discuss differences between domains}
+\gbt{Not sure we'll have space :) }
 
-Our goal is to experimentally obtain insights into the usefulness of computer vision object labeling models, that are commonly used for \lv methods, to account for natural human object naming. 
-Specifically, our research questions are
-\begin{enumerate}
-	\item Do object detection models, despite being trained on \arbitrary  
-	names, account for human object naming?\cs{repetitive}
-	\item Can we apply simple transfer learning on \mn to train classifiers towards this naming task by utilizing pre-trained object detection or image classification model as feature extractors?
+We use \mn to gain insight into the extent to which current models account for object naming.
+We do so in three ways: By analyzing the behavior of existing models on entry-level names, by assessing the consequences of fine-tuning models with entry-level name data, and by analyzing the predictions of the models, comparing them to human naming behavior as attested in \mn.
+The latter will be done in Section~\ref{sec:analysis}; here we focus on modeling experiments.
+\gbt{Maybe this needs to go in the intro or somewhere else. It's important to stress that the modeling experiments are on entry-level only, and the analysis takes into account the other names.}
+
+The modeling experiments adopt the standard single-label object classification approach of Computer Vision, and we will compare prediction of the original \vg name with the entry-level name.
+We leave modeling experiments that take into account other possible names of objects for future work.
+
+% Our goal is to experimentally obtain insights into the usefulness of computer vision object labeling models, that are commonly used for \lv methods, to account for natural human object naming. 
+% Specifically, our research questions are
+% \begin{enumerate}
+% 	\item Do object detection models, despite being trained on \arbitrary  
+% 	names, account for human object naming?\cs{repetitive}
+% 	\item Can we apply simple transfer learning on \mn to train classifiers towards this naming task by utilizing pre-trained object detection or image classification model as feature extractors?
 Figure~\ref{fig:exp_confusions} \\
-	\cs{move to models: -- can we learn entry-level names by fine-tuning object detection models on \mn?\\
-		-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?}
-\end{enumerate}
-TO BE COVERED BY THE SUBSECTIONS BELOW:
-\begin{enumerate}
-	\item Do models prefer the entry-level name of an object over an \arbitrary name? Table~\ref{tab:exp_VGvsMN}
-	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
-	\item What phenomena of human behavior on the object naming task of \mn do the models mirror?
+% 	\cs{move to models: -- can we learn entry-level names by fine-tuning object detection models on \mn?\\
+% 		-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?}
+% \end{enumerate}
+% TO BE COVERED BY THE SUBSECTIONS BELOW:
+% \begin{enumerate}
+% 	\item Do models prefer the entry-level name of an object over an \arbitrary name? Table~\ref{tab:exp_VGvsMN}
+% 	\item In cases of failure, do they predict alternative, but less preferred  names instead? Tables~\ref{tab:exp_overview_results}, \ref{tab:exp_alternatives}
+% 	\item What phenomena of human behavior on the object naming task of \mn do the models mirror?
 That is, which model mistakes or confusions are due to the artificial setup of the task itself, and less a failure of the model?
 (Recall that \mn serves as a \textit{proxy} for natural human object naming, since annotators were asked to name a highlighted object in an image isolated from its situative context; Section~\ref{sec:manynames}) Table~\ref{tab:exp_details_wrong} (and \ref{tab:exp_errors_agreement},  \ref{tab:exp_alternatives})
-
-	%That is, do they make similar mistakes (wrong object--maybe more salient?, related name, e.g.,~co-hyponyms)?
-	\item \cs{Not examined at the moment -- MRR and Jaccard may be re-added for this: Are valid name alternatives among the top-N predictions?}
+% \item \cs{Not examined at the moment -- MRR and Jaccard may be re-added for this: Are valid name alternatives among the top-N predictions?}
 %\item do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
-\end{enumerate}
-We use the \mn dataset in two ways, as analytical testbed, and for fine-tuning pre-trained image features towards entry-level name prediction.
+%\end{enumerate}
 
@@
 
+\paragraph{Data}
+\gbt{I moved this here cause I think it will be useful to define the different vocabularies here and then be able to simply refer to them later.
+Btw, consider using `MN-Entry' instead of `MN442'?
+but maybe having the number in the name is useful to be able to compare.}
+\cs{todo after Section~\ref{sect:mn_overview} has been written.}
+\begin{itemize}
+	\item Test data: overlap of \mn and \vg test data (CITE)
+	\item Target vocabulary of test data: overlap of MN442 and VG (\cs{XX} names)
+	\item Source of label: \mn, but we compare against \vg
+\end{itemize}
+
 \paragraph{Models}
-We test two object detection models which both use the Faster R-CNN architecture \cite{fasterrcnn2015}, and were initialized with features that were pre-trained on $1$K~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
-They were both trained on \vg, but, essentially, differ in their target vocabulary. 
-FRCNN$_{\text{VG1600}}$\footnote{We used the code and model of \citeauthor{anderson2018updown}'s \shortcite{anderson2018updown} bottom-up attention model, available at  \url{github.com/peteanderson80/bottom-up-attention}.
-The model is trained with an additional output over attributes, but we only use the object class prediction layer.} \cite{anderson2018updown} uses a vocabulary of $1600$~object classes \cs{add how it was derived}.
-For FRCNN$_{\text{MN442}}$, we pre-process the \vg data as in \citeauthor{anderson2018updown} \cs{right, @Sina?}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
 
-\cs{start to be moved to an appropriate place}
-While we consider \mn's size ($25$K instances) to be excellent for evaluation and analysis purposes, it is too small to serve as data for training object detection models from scratch, which require the learning of millions of parameters.
-It may, however, serve as training data for transfer learning. 
-\cs{end to be moved to an appropriate place}
-We assess the possibility to explicitly obtain entry-level naming models through transfer learning, by training a Vanilla object classifier on \mn using the FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN--VG442, so we only use the former model.} model as feature extractor.
-For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} 
-\cs{todo: details to architecture and training}
-To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
-The target vocabulary (VGMN, henceforth) comprises the overlap of VG1600 and the \mn names (\cs{$XX$} in total).
+We test 1) an existing object detection and classification model trained on \vg (FRCNN$_{\text{VG1600}}$); 2) the same model, re-trained on the smaller vocabulary of entry-level names, MN442 (FRCNN$_{\text{MN442}}$); 3) an object classification model trained on FRCNN$_{\text{VG1600}}$ features, that is, a version of FRCNN$_{\text{VG1600}}$ fine-tuned on \mn data (FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ \gbt{find better name?}); 4) object classification models trained directly on object detection features (given by ResNet 101; \cite{}), rather than object classification features.
 
-We furthermore assess the drop in effectiveness of such a Vanilla  classifier when we do not use FRCNN (trained on \vg) as feature extractor, but instead it's initialization model, i.e.,~ResNet-101. 
+FRCNN$_{\text{VG1600}}$ is the bottom-up attention model of \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown},\footnote{Available at \url{https://github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.}
+trained to do object classification with a vocabulary of $1600$ VG names as class labels. \cs{add how the vocabulary was derived}.
+The model is based on the object detection \gbt{detection, or classification?} method Faster R-CNN \cite{fasterrcnn2015}. 
+The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.
+To train FRCNN$_{\text{MN442}}$, we follow the same methodology as in \citeauthor{anderson2018updown} \cs{right, @Sina?} but restrict the object classes to the $442$~entry-level names found in \mn; accordingly, we train on fewer images.
+\gbt{Right?
+Only those that have an entry-level name?
+TODO: add how many imgs for FRCNN$_{\text{VG1600}}$ and FRCNN$_{\text{MN442}}$.}
+\gbt{Also, Do we also use the additional attribute loss?}
+\footnote{For training, we use a PyTorch reimplementation of Faster R-CNN, \url{github.com/jwyang/faster-rcnn.pytorch}.}
+FRCNN$_{\text{MN442}}$ serves us to test the hypothesis that training only on entry-level names may improve generalization and hence performance.
+
+The two former models are trained on \vg, which has almost 4 million labeled objects.
+\mn is too small to train object detection models on it from scratch, which require learning millions of parameters.
+On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly --probably unrealistic.
+Therefore, we investigate the possibility of obtaining entry-level data via transfer learning, fine-tuning existing models with \mn data.
+We do so with the standard methodology \gbt{in L\&V?} of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).
+
+We experiment with two kinds of input.
+First, the features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}.
+We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).
+For comparison, we consider a much less informed kind of input, namely the features from an object detection model, ResNet-101 \cite{+++}, which are the ones that FRCNN$_{\text{VG1600}}$ use as initialization features.
+\gbt{Previous sentence to be improved}
+Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
+
 \cs{Next sentence relevant here?
 Or just as detail in related work?:: (Note that ResNet's $1$K~object classes capture subordinate categories of ImageNet leaf nodes; e.g.,~Siberian husky, American black bear.)}
+
+\gbt{begin not integrated}
 As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
@@
 Note that all four models are optimized on the $25$K~objects in \mn. 
+\gbt{end not integrated}
+
+\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and also the explanation and doesn't add much information.
+I'd put the most relevant (at most two, maybe even only one) in the main paper and leave the rest for the supplementary material.
+TBD}
+
+\cs{todo: details to architecture and training of the vanilla classifiers.}
+\gbt{I leave this here unchanged:} For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} 
+To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
+The target vocabulary (VGMN, henceforth) comprises the overlap of VG1600 and the \mn names (\cs{$XX$} in total). \gbt{All \mn names? or only MN422? To be clarified above under paragraph `Data'.}
 
@@
 \end{table}
-
-\paragraph{Data}
-\cs{todo after Section~\ref{sect:mn_overview} has been written.}
-\begin{itemize}
-	\item Test data: overlap of \mn and \vg test data (CITE)
-	\item Target vocabulary of test data: overlap of MN442 and VG (\cs{XX} names)
-	\item Source of label: \mn, but we compare against \vg
-\end{itemize}
 
@@
 
-\iffalse
+%\iffalse
 \cs{under construction}
@@
 \end{itemize}
-\fi
+%\fi
 
@@
 \end{itemize}
+\fi
 
-\subsection{Experimental Setup}
-\label{sect:exp_setup}
-
-\paragraph{Data}
-
-\paragraph{Models}
-
-We test two object detection models that are trained with a different vocabulary:
-
-\begin{itemize}
-\item FRCNN$_{\text{VG1600}}$: we used the code and model of the bottom-up attention model (\textit{Bottom-up} henceforth)  \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown} \footnote{\url{https://github.com/peteanderson80/bottom-up-attention}} The model is based on the object detection method Faster R-CNN \cite{fasterrcnn2015}.
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.\footnote{Bottom-up is trained with an additional output over attributes, but we only use the object class prediction layer.}
-
-\item FRCNN--MN442: we retrain Faster R-CNN \cite{fasterrcnn2015} on a smaller vocab.
-We use \citeauthor{anderson2018updown}'s to preprocess the data set, but restrict the object classes to the 442 entry-level names found in ManyNames.
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{https://github.com/jwyang/faster-rcnn.pytorch}} and initialized it with a pretrained ResNet-101 provided in this implementation.\footnote{ResNet-101 was pretrained with Caffe.}
-\end{itemize}
-
-We test a range of object classification models via transfer learning, that are finetuned with different vocabulary/training data:
-
-\begin{itemize}
-\item ...
-\end{itemize}
-
-\paragraph{Measures}
-
+\iffalse
 \subsection{[TBC] Predicting Entry-Level Names}
@@
 
-\subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
-\label{sect:exp_analysis}
+% \subsection{[TBC] Generalization Ability: OpenImages}
+% \label{sect:exp_openimages}
+% Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
 
-\paragraph{Categorization of Errors}
-see Figure\ ref{fig:mistakes}
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.,\ plane vs. airplane
-	\item Semantically related\\
-	e.g.,\  motorcycle vs. scooter
-\end{enumerate}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
-
-	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:matrices}}
-\end{figure}
-
-\subsection{Results}
-\paragraph{Overview}
-Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}
-
-\paragraph{How do predictions change?} Figure \ref{fig:matrices} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
-For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
-Observations:
-\begin{itemize}
-\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
-\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
-Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
-(top right matrix)
-\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
-This is less the case when ResNet is finetuned on VG annotations.
-\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
-\end{itemize}
-
-\paragraph{Correct predictions}
-Table\ \ref{tab:exp_details_correct}: \cs{Gives detailed results to the categories of "correct name" (but not hit): same cluster, WordNet synonym, WordNet hypernym/hyponym}\\
-To look into in detail (example images): 
-\begin{itemize}
-	\item Compare FRCNN vs.
-FRCNN-finetuned (row block 1 vs.
-row block 2) with respect to the synonym categories (i.e., predicted name is in a synonym/synonyms\_cluster-relation to the target object) vs.
-same\_cluster (i.e., predicted name is in response set).
-\end{itemize}
-
-\paragraph{Wrong predictions}
-
-\begin{figure*}[t]
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
-
-\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
-\end{figure*}
-
-Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-	\toprule
-	Model$_{\text{Vocab}}$	& GTtrain  
-	&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
-	\midrule
-	FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-	FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-	\midrule \midrule
-	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-	 &         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
-	\midrule
-	ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-	 &         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-	ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-	 &         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-	ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-	 &         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-	ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-	 &         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
-	\bottomrule
-\end{tabular}
-\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
-\end{table*}
-
-\begin{table*}[t]
-\centering
-	\small
-\begin{tabular}{lrrr||rrr}
-\toprule
-&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
-                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
-\midrule
-       FRCNN$_{\text{VG1600}}$\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
-        FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
-        		\midrule \midrule
- FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
- 		\midrule 
-     ResNet101$_{\text{VGMN}}$\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-     ResNet101$_{\text{VGMN}}$\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
-    ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
-\bottomrule
-
-\end{tabular}
-\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
-		& 	&  cluster &  & cluster & & & cluster 
-			& cluster  &  & cluster & & & cluster \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		 &                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		 &                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
-		 &                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		 &                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		  &                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		 &                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
-		\bottomrule
-	\end{tabular}
-
-	\caption{Break-down of the results for the \textit{correct} name predictions.
-Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
-\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
-\textit{Synonym} and \textit{synonym\_cl} are analogous.
-\label{tab:exp_details_correct}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
-		\toprule
-		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
-		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ & GTtrain  
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
-		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
-		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
-
-	\midrule
-	FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-	FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
-	\midrule \midrule
-	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
-	\midrule
-	ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-	ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-	ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-	ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
-	\bottomrule
-\end{tabular}
-\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
-\end{table*}
-
+% Models compared: FRCNN$_{\text{VG1600}}$ vs. FRCNN$_{\text{MN442}}$ vs. ResNet101--XX (best Vanilla).
 \fi
 
-\subsection{[TBC] Generalization Ability: OpenImages}
-\label{sect:exp_openimages}
-Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
-
-Models compared: FRCNN$_{\text{VG1600}}$ vs. FRCNN$_{\text{MN442}}$ vs. ResNet101--XX (best Vanilla).
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-08 papers/ACL2020/analysis.tex
deletes redundant tables

@@
+\gbt{To do: better structure content into subsections. Decide which results to report. Adapt text.}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
+		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model$_{\text{Vocab}}$	& GTtrain  
+		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
+		\midrule
+		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
+		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
+		\midrule \midrule
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
+		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
+		\midrule
+		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
+		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
+		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
+		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
+		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
+		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
+		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
+		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
+standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
+\label{tab:exp_overview_results}}
+\end{table*}
+
+\paragraph{Alternative Name Prediction}
+\begin{figure}
+	\centering
+	\includegraphics[scale=.2]{images/2323938.jpg}
+	\includegraphics[scale=.2]{images/2322259.jpg}
+	\includegraphics[scale=.2]{images/2371657.jpg}
+
+	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes} \gbt{Will we have space for the figure?
+(Maybe we should \textit{make} space?) Also, shouldn't we put examples from the most successful model instead?}}
+\end{figure}
+
+\cs{TODO::}
+Categorization of "errors" (see Figure~\ref{fig:mistakes}):
+\begin{enumerate}
+	\item Clear mistake \\
+	e.g.,\ rice vs. bread
+	\item Alternative name\\
+	e.g.,\ building vs. house
+	\item Alternative object \cs{(other cluster from verif data)}
+	\item Synonym\\
+	e.g.,\ plane vs. airplane
+	\item Semantically related\\
+	e.g.,\  motorcycle vs. scooter
+\end{enumerate}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
+		\toprule
+		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
+		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model$_{\text{Vocab}}$ &  GTtrain & same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
+		& 	&  cluster &  & cluster & & & cluster 
+		& cluster  &  & cluster & & & cluster \\
+		\midrule
+		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
+		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
+		FRCNN$_{\text{MN442}}$ & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
+		\midrule \midrule
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
+		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
+		\midrule
+		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
+		ResNet101$_{\text{MN442}}$ & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
+		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
+		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
+		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
+		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
+		\bottomrule
+	\end{tabular}
+
+	\caption{Break-down of the results for the \textit{correct} name predictions.
+Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
+\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
+\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
+\textit{Synonym} and \textit{synonym\_cl} are analogous.
+\label{tab:exp_alternatives}}
+\end{table*}
+
+\paragraph{Incorrect Predictions}
+
+\begin{table*}[t]
+	\centering
+	\small
+	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
+		\toprule
+		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
+		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
+		\toprule
+		Model$_{\text{Vocab}}$ & GTtrain  
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
+		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
+		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
+		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
+
+		\midrule
+		FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
+		FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
+		\midrule \midrule
+		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
+		\midrule
+		ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
+		ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
+		ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
+		ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
+\end{table*}
+
+\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
+For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
+Observations:
+\begin{itemize}
+	\item Retraining faster-rcnn on fewer, entry-level names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round.
+(top left matrix)
+	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
+Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
+(top right matrix)
+	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
+This is less the case when ResNet is finetuned on VG annotations.
+	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
+\end{itemize}
+
+\begin{figure*}[t]
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
+	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
+
+	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
+\end{figure*}
+
 \subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
@@
 \subsection{Results}
+
 \paragraph{Overview}
@@
 \paragraph{Wrong predictions}
-
-\begin{figure*}[t]
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
-\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
-
-\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned)}
-\end{figure*}
 
@@
 
-\begin{table*}[t]
-\centering
-	\small
-\begin{tabular}{lrrr||rrr}
-\toprule
-&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
-                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
-\midrule
-       FRCNN$_{\text{VG1600}}$\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
-        FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
-        		\midrule \midrule
- FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
- 		\midrule 
-     ResNet101$_{\text{VGMN}}$\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-     ResNet101$_{\text{VGMN}}$\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
-    ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
-\bottomrule
-
-\end{tabular}
-\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{llr@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		& &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
-		& 	&  cluster &  & cluster & & & cluster 
-			& cluster  &  & cluster & & & cluster \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		 &                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN--MN442 & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		 &                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
-		 &                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		 &                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101--MN442 & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		  &                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		 &                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
-		\bottomrule
-	\end{tabular}
-
-	\caption{Break-down of the results for the \textit{correct} name predictions.
-Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
-\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
-\textit{Synonym} and \textit{synonym\_cl} are analogous.
-\label{tab:exp_details_correct}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{ll|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
-		\toprule
-		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
-		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ & GTtrain  
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
-		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
-		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
-
-	\midrule
-	FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-	FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
-	\midrule \midrule
-	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
-	\midrule
-	ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-	ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-	ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-	ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
-	\bottomrule
-\end{tabular}
-\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
-\end{table*}
-
 %%% Local Variables:

### 2019-12-08 papers/ACL2020/experiments.tex
deletes redundant tables

@@
 \gbt{Not sure we'll have space :) }
+
+\gbt{Note: I've rewritten this intro, the previous version with the plan of what is to be covered is commented out in the tex file}
 
@@
 
-\gbt{begin not integrated}
+\gbt{BEGIN not integrated in the text yet}
 As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
@@
 Note that all four models are optimized on the $25$K~objects in \mn. 
-\gbt{end not integrated}
+\gbt{END not integrated}
 
-\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and also the explanation and doesn't add much information.
+\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and doesn't add much information.
 I'd put the most relevant (at most two, maybe even only one) in the main paper and leave the rest for the supplementary material.
@@
 
-\subsection{Results: Entry-Level Name Prediction}
+\subsection{Results}
 \label{sect:exp_results}
-%\paragraph{Entry-Level Name Prediction}
+
+\gbt{To do: streamline to make consistent with motivations + expectations laid out in the previous subsection.}
+
 Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
-We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN).
+We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN) \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}.
 \begin{itemize}
-	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
+	\item The FRCNN models \gbt{all models, actually} are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
 	This shows that they do learn entry-level naming to some extent, despite being trained on VG, i.e.,~\arbitrary ground truth labels.
@@
 \end{itemize}
-
-\subsection{Quantitative Analysis}
-\label{sect:exp_analysis}
-
-\paragraph{Alternative Name Prediction}
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
-
-	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes}}
-\end{figure}
-
-\cs{TODO::}
-Categorization of "errors" (see Figure~\ref{fig:mistakes}):
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.,\ plane vs. airplane
-	\item Semantically related\\
-	e.g.,\  motorcycle vs. scooter
-\end{enumerate}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$	& GTtrain  
-		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
-		\midrule
-		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|rrr||rrr}
-		\toprule
-		& &  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
-		Model$_{\text{Vocab}}$ &  GTtrain & hit &  correct &  incorrect &  hit &  correct &  incorrect \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
-		FRCNN$_{\text{MN442}}$ & VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
-		\midrule 
-		ResNet101$_{\text{VGMN}}$ & VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
-		ResNet101$_{\text{VGMN}}$ & MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
-		ResNet101$_{\text{MN442}}$ & MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
-		\bottomrule
-
-	\end{tabular}
-	\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ &  GTtrain & same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
-		& 	&  cluster &  & cluster & & & cluster 
-		& cluster  &  & cluster & & & cluster \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN$_{\text{MN442}}$ & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
-		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
-		\bottomrule
-	\end{tabular}
-
-	\caption{Break-down of the results for the \textit{correct} name predictions.
-Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
-\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
-\textit{Synonym} and \textit{synonym\_cl} are analogous.
-\label{tab:exp_alternatives}}
-\end{table*}
-
-\paragraph{Incorrect Predictions}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
-		\toprule
-		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
-		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ & GTtrain  
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
-		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
-		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
-
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-		FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-		ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-		ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-		ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
-\end{table*}
-
-\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
-For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
-Observations:
-\begin{itemize}
-	\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
-	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
-Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
-(top right matrix)
-	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
-This is less the case when ResNet is finetuned on VG annotations.
-	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
-\end{itemize}
-
-\begin{figure*}[t]
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
-
-	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
-\end{figure*}
 
@@
 	\item Are valid name alternatives among the top-N predictions?
-	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
+x	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
 	-- naming an alternative object (maybe more salient)\\
@@
 \iffalse
-\subsection{[TBC] Predicting Entry-Level Names}
-\label{sect:exp_entry}
-Question: Can object detection models trained on a set of "arbitrarily" chosen object names account for entry-level object names?
+OLD TABLE WITH MORE MEASURES
 
-Note that the source dataset for defining the vocabulary (\textsl{Vocab}, i.e.,\ the overall set of considered names, i.e., the softmax layer's dimensions), and the source dataset which provides the ground truth names for the individual objects (\textsl{GTtrain}) may differ.
 \begin{table*}[t]

### 2019-12-08 papers/ACL2020/supplementary.tex
[ACL2020] adds supplementary.tex

--- 2019-12-06 papers/ACL2020/acl2020_main.tex
@@
 % Terms that need to be replaced throughout the paper by more appropriate ones:
-\newcommand{\arbitrary}{arbitrary$_{SIC}$\xspace}
+\newcommand{\arbitrary}{arbitrary$\rightarrow$?\xspace}
 
-\title{How to Name a Real-World Object, and how not to}
+\title{Supplementary Material}
 
@@
 \begin{document}
-\maketitle
-\begin{abstract}
 
-\end{abstract}
-
-\section{Introduction}
-\label{sec:intro}
-\input{introduction}
-
-\section{Related Work}
-\label{sec:related}
-\input{related}
-
-\section{ManyNames: A Source for Entry-Level Names}
-\label{sec:manynames}
-\input{manynames}
-
-\section{Experiments}
-\label{sec:experiments}
-\input{experiments}
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-%\bibliography{BLA}
-%\bibliographystyle{acl_natbib}
-
-%\appendix
-%
-\section{Appendices}
-\label{sec:appendix}
-\iffalse
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-\fi
-
-\section{Supplemental Material}
-\label{sec:supplemental}
-\iffalse
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-\fi
-
+\section{Verification Procedure with AMT}
+\label{sec:verif}
 \begin{figure*}[t]
@@
 
+\cs{The text is is just copied from the main, it needs to be adapted here.}
+We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
+When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
+We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.
+
 \bibliographystyle{acl_natbib}
@@
 \end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: "acl2020_main"
-%%% End:

### 2019-12-08 papers/ACL2020/manynames.tex
[ACL2020] CS is done with editing Section 3.2

@@
-\cs{@gbt @mw}
+\cs{In the remainder of this paper, we will use object and object instance interchangeably.}
 \subsection{Overview of ManyNames}
@@
 
+\begin{itemize}
+	\item For each object: a response set comprising all entered names (spellchecked) and their respective counts, i.e., the number of annotators which enter the respective name.
+	\item Problems: referential uncertainty: object other than target object was  identified as named
+\end{itemize}
+
 \subsection{Verification of Annotations}
 \label{sect:mn_verification}
+\cs{START TODO at the end}
+Goal: Verification of entered object names necessary to exclude incorrect names (wrong object was named) required. \\
+Collected: adequacy judgements from 0-2; source/type of inadequacy; CLUSTERS: for each entry-level name (or any other name in the response set), all its valid alternatives.
+\cs{END TODO }
 
-\mw{Below can be shortened no doubt; but could also be moved to appendix. Plz. let me know what you consider the most appropriate (I'm an ACL noobie).}
+We used Amazon Mechanical Turk\footnote{(\url{https://mturk.com})} (AMT) to verify all the \mn naming data (response sets), with two exceptions: We consider response sets with ~$100$\%~agreement (i.e.,~all annotators gave the same name for an object) as correct, so do not require verification, and all names with a count of~$1$ as unreliable, so we directly discarded those from the sets.
+We collected verifications for the remaining $19,427$~objects, with on average $4$ names each, as follows: 
+For each object, we presented $3$~annotators with its image, with the object highlighted by its bounding box, and a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
+They were asked to judge the ``adequacy''\footnote{We defined that \textit{a name is   ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.} of each name on a 3-point scale (with $0$=``perfectly adequate'', $1$=``there may be a (slight) inadequacy'', and $2$=``totally inadequate'').
+In the case they did not choose ``adequate", they had to specify the type of inadequacy (``linguistic mistake", ``named object not tightly in bounding box",  ``named object mistaken for something it's not", and ``something else").
+\cs{maybe in ManyNames we need exampled for all those, when the need for verification is explained.}
 
+In addition to judging name adequacy, we asked the annotators to cluster the list of names (through coloring), such that each group (color) would comprise the names they thought to be likely intended (by the \mn annotators entering the name) for the \textit{same} real-world object.
+
+\iffalse
 Although the initial data gathering phase involved some very basic quality control (detecting repeated names, empty text fields, typos), we had no rigorous way of ascertaining that our participants were providing adequate names for the intended object.
-Given our high number of annotators in phase 1 we decided to simply discard names that were entered by only one annotator.
-Moreover, for images where all 36 annotators entered the same name we decided to take this name to be adequate. 
-That still leaves 19427 images, with on average 4 names each, to be properly verified, which we did as follows.
+\fi
 
-We conducted a second round of annotation where we asked people whether each name for a given image was adequate and, if not, what type of inadequacy it was.
-Moreover, we asked them to indicate which names were likely intended for the same real-world object.
-The task interface is shown in figure~\ref{fig:verification-interface} in the appendix.
-Adequacy was rated on a 3-point scale from ``perfectly adequate'' to ``there may be a (slight) inadequacy'' to ``totally inadequate'', represented by appropriate emotes.
-We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
-When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
-We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.
+Since the quality of the data we gather in this phase will be essential for gaining insight into the \mn dataset, as well as for evaluating computational models (Section~\ref{sec:experiments}), we conducted rigorous quality control (see the supplementary material for details).
 
-Because the quality of the data we gather in this phase will be essential for gaining insight into the ManyNames dataset, as well as for evaluating computational models (section~\ref{sec:experiments}), we conducted rigorous quality control.
-Every task included around 15\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
-When trying to submit their results, participants would get a warning if their accuracy on these items was below 90\%, and the advice to stop doing these tasks if it was below 80\%, with the option to double-check their responses.
-They would get a bonus of \$0.15 if all control items were answered correctly (happened about half the time).
-After every round we blocked annotators with low ($<$90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.
+%We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}).
 
-We implemented this verification task on Amazon Mechanical Turk (\url{https://mturk.com}). 
-Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
-\begin{table}[t]
-	\centering
-	\small
-	\begin{tabular}{|ll|ll|}
-		\hline
-		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
-		Images: & 19427 &
-			Annotators: & 255 \\
-		Img-name pairs: & 69356 &
-			Annotators/task: & $\geq$ 3 \\
-		Tasks: & 3052 &
-			Adeq. mean: & \hspace{-3em}.80 (std .093)\\
-		Images/task: & 6-7 &			
-			Agreement (adeq.) & 88\% \\ 
-		Names/task: & 20-30 &
-			Agr. (inadeq. type): & 86\% \\
-		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
-			Agr. (same-obj): & 94\% \\
-		\hline
-	\end{tabular}
-	\caption{Verification task overview.}
-	\label{tab:verification-numbers}
-\end{table}
-Average name adequacy, encoded on a scale $[0,1]$, is 0.80 with small standard deviation (0.093). 
-Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
-This level is agreement is high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
-Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
+\paragraph{Postprocessing and Basic Statistics}
+\cs{Table moved to suppl.}
 \begin{figure}[t]
@@
 \mw{Possibly a pie-chart counting actual names and their aggregated (+thresholded) scores would be more informative than the current pie-chart, which counts original (i.e., non-aggregated) verification annotations.}
+\cs{If you have time for it, @MW, could you add this in addition?}
+%
+Overall, $255$~annotators a total of $69,356$~obj--name pairs.
+We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
+Average name adequacy on this scale of $[0,1]$ is 0.80 (\mbox{std=$0.093$}). \cs{@MW: check that this is the right place here.}
+Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
+We consider this level of agreement as high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
+Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
 
-We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
-As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.
-For evaluating computational object naming models, we want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
-This we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
-For this, we need to compute clusters of names (the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
+As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.\cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it?
+In this case, it would be "aggregating name cluster", no?!
+So what you did for the first aggregation (modeling) was a pair-wise aggregation?}
+For analysing computational object naming models, we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 
+%want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
+This we compute, by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
+
+For analysing object naming on the verified \mn data (Section~\ref{sect:mn_analysis}), e.g.~assess the mean number of names per object, however, 
+%However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
+%For this, 
+we need \cs{@MW please check if that's correct}  to compute hard clusters
+%clusters of names
+(the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
 A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
 It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
-But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships (which could be gotten from, e.g., WordNet) -- rather, we care about (and asked our annotators) which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top.
-Moreover, although (hard) clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.
+But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships--- %(which could be gotten from, e.g., WordNet) -- 
+rather, we care about %(and asked our annotators) 
+which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top. 
+Moreover, although hard clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.
 

### 2019-12-08 papers/ACL2020/analysis.tex

@@
 \label{tab:exp_overview_results}}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+	\small
+\begin{tabular}{lrrr||rrr}
+\toprule
+&  \multicolumn{3}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+                  model &  hit &  correct &  incorrect &  hit &  correct &  incorrect \\
+\midrule
+       FRCNN$_{\text{VG1600}}$\_VG &      94.8 &           1.8 &             3.4 &     63.6 &         24.5 &           12.0 \\
+        FRCNN--MN442\_VG &      89.6 &           1.6 &             8.8 &     60.7 &         23.9 &           15.4 \\
+        		\midrule \midrule
+ FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$\_MN &      94.5 &           1.3 &             4.2 &     72.9 &         16.5 &           10.6 \\
+ 		\midrule 
+     ResNet101$_{\text{VGMN}}$\_VG &      88.3 &           1.8 &             9.9 &     48.5 &         23.6 &           27.8 \\
+     ResNet101$_{\text{VGMN}}$\_MN &      89.6 &           1.6 &             8.8 &     57.0 &         19.4 &           23.6 \\
+    ResNet101--MN442\_MN &      90.1 &           1.3 &             8.6 &     58.2 &         19.5 &           22.3 \\
+\bottomrule
+
+\end{tabular}
+\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
 \end{table*}

### 2019-12-08 papers/ACL2020/introduction.tex
pass at the intro

@@
 \cs{need to discuss problematic of standard evaluation procedure of CV models}
+
+When people talk, they choose particular names for objects, such as \textit{bird} or \textit{duck} for the images in Figure~\ref{fig:duck}.
+The task of \textbf{object naming} has been studied in Psycholinguistics~\cite{refs}, \gbt{Which term do you prefer, Psycholing, or CogSci?
+I don't care.
+Use same term throughout.} but has not received much attention in Computational Linguistics; we seek to remedy this situation by providing data and modeling results on this phenomenon, and in particular on \textbf{entry-level names}, defined in psycholinguistic research as the preferred name for an object~\cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}: For the left object in the figure, according to our data, the entry-level name is \textit{bird}, and for the right object it is instead \textit{duck}.
+%We seek to shed light into how people naturally name objects in real images, and in
+
+Our contributions are two-fold.
+First, we provide data on object naming with real images on a large scale.
+We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+Second, we provide an extensive analysis of the performance of object classification models on the task of predicting the entry-level names in our dataset.
+
+\begin{figure}[htb]
+	\centering
+	\small
+	\begin{tabular}{p{3cm}p{3cm}}
+		\centering
+		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
+		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
+		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
+	\end{tabular}
+
+	\caption{Different naming preferences for different instances of the same category \textsc{duck} in \mn.\label{fig:duck}}
+\end{figure}
+As for the former, note that Psycholinguistic research on entry-level names has focused on categories, as opposed to instances:
+When a subcategory is atypical, such as penguins not being very typical birds, this affects their entry-level name (it is common to call a sparrow, but not a penguin, \textit{bird}).
+Accordingly, datasets used for object naming in Psycholinguistics use idealized drawings that correspond more to categories than to instances~\cite{+++++}.
+However, when they speak, humans in general name specific \textit{instances} of objects ---actually, object instances in particular situations and points of view.
+Our data contain object instances, corresponding more closely to the kind of visual objects that humans typically encounter, and so can potentially shed light on the instance-level factors that affect naming.
+%Indeed, Psycholinguistic research has typically ignored
+% The example shows two instances of the category \textsc{duck}, and when people were asked to name the highlighted object, most ($27$) people called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance.
+%It seems plausible that there are instance-specific factors affecting naming behavior in general.
+%, and entry-level names in particular, and our data suggest that this is the case
+% gbt: maybe put back a "crucially" somewhere: "Crucially, though, as we will empirically show, human object naming is \textit{instance}-dependent: It depends on the characteristics "
+In particular, we validate the notion of entry-level name at the instance level:
+For almost 90\% of the 25K objects analyzed, humans showed a preference for a given name (frequency of that name $>50\%$ of the valid responses).
+
+As for the second contribution, \gbt{to be expanded; proposed structure follows; probably here only a summary and a fuller explanation later?}
+% allows for an in-depth analysis of naming data as well as of naming models on the task of object naming.
+\begin{itemize}
+\item resources developed in CV and \lv can be useful to study object naming. 
+\item However, they provide only one (or a few) name per object \ra no guarantee that it is the entry-level name.
+(We provide more, to have a robust estimate of entry-level names (as well as data on other possible names).
+\gbt{actually, maybe move this to the previous part?
+\ra differences with Psycholing, with CV resources})
+\item object naming has often been conflated with object classification in CV. \gbt{Discuss differences; mention the swan - whatever name it has in wordnet example of ordonez et al?}
+\item a big problem with this approach is that it follows a single-label evaluation.
+With our data, we show that often model responses are adequate even if they do not correspond to the entry-level name.
+\item we also show that object classification models ``spontaneously'' learn to provide entry-level names for objects
+\item and that it is possible to use \mn to successfully fine-tune existing object detection and classification models to predict entry-level names for objects.
+\end{itemize}
+
+\gbt{Below is the old text. I factored out the entry-level aspects in the previous paragraph. It should be removed from this second part.}
 
@@
 %
-\begin{figure}
-	\centering
-	\small
-	\begin{tabular}{p{3cm}p{3cm}}
-		%VisualGenome+ManyNames & \cite{snodgrass}\\
-		\centering
-		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
-		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
-		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
-	\end{tabular}
 
-	\caption{Different naming preferences for different instances of the same concept (duck)\label{fig:duck}}
-\end{figure}
-%
 In this paper, we seek an understanding of the notion of entry-level names of instances of real-world objects in images, and to give systematic insights into the problem of retraining or fine-tuning object detection models (and features in transfer learning) such that they capture a natural vocabulary and account for linguistic preferences in naming.
@@
 (b) To predict entry-level names without annotating a huge amount of training examples, it is possible to fine-tune (iii) on \mn. We show that \cs{(say something about mistakes not made anymore). }
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-08 papers/ACL2020/supplementary.tex

@@
 \cs{The text is is just copied from the main, it needs to be adapted here.}
+\paragraph{Annotation Procedure}
 We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
@@
 
+\paragraph{Quality Control}
+Every task included around 15\% automatically generated quality control items of various kinds (names for objects in a different image, names for other objects in the same image, WordNet synonyms of given names, inserted typos, and more).
+When trying to submit their results, participants would get a warning if their accuracy on these items was below 90\%, and the advice to stop doing these tasks if it was below 80\%, with the option to double-check their responses.
+They would get a bonus of \$0.15 if all control items were answered correctly (happened about half the time).
+After every round we blocked annotators with low ($<$90\%) average accuracy, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of our data.
+
+\paragraph{Basic Statistics}
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{|ll|ll|}
+		\hline
+		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
+		Images: & 19,427 &
+		Annotators: & 255 \\
+		Img-name pairs: & 69,356 &
+		Annotators/task: & $\geq$ 3 \\
+		Tasks: & 3,052 &
+		Adeq. mean: & \hspace{-3em}.80 (std .093)\\
+		Images/task: & 6-7 &			
+		Agreement (adeq.) & 88\% \\ 
+		Names/task: & 20-30 &
+		Agr. (inadeq. type): & 86\% \\
+		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
+		Agr. (same-obj): & 94\% \\
+		\hline
+	\end{tabular}
+	\caption{Verification task overview. 
+		\label{tab:verification-numbers}}
+\end{table}
+Basic numbers and results are reported in Table~\ref{tab:verification-numbers}.
 \bibliographystyle{acl_natbib}

### 2019-12-08 papers/ACL2020/manynames.tex
[ACL2020] CS is done with Sect.3.3

@@
 \label{sect:mn_analysis}
-
-\cs{+ @sz?}\\
 \cs{Here goes what has not been discussed in LREC paper, because it focusses on entry-level names. }
@@
 
-\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?}
+\paragraph{Definition of \textit{Entry-level Name}} \sz{has this been mentioned before?}
 \mw{I'd definitely put this in the introduction, and leave only a reminder here.}
-In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.
+\cs{Remove me at the end, to make sure definition is in intro.}
+As we explained in Section~\ref{sec:intro}, we define \textit{entry-level name} for an object as the name that 
+%In the following, we consider a name annotated for an object as an entry-level name if it 
+corresponds to the most frequent name given a set of name annotations for the object.
 \mw{We could also consider defining entry-level name as `the most frequent adequate name'?
@@
 \mw{Also make sure to define the notion of `entry-level object', or `canonical object' perhaps? i.e., the object/cluster of the entry-level name.}
-
-\paragraph{Entry-level Names in ManyNames:} As shown in Table \ref{tab:stat-entry-level}, ManyNames provides a large vocabulary of names (7970) for 25K objects.
-Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on.
-The vocabulary of entry-level names is drastically smaller and contains only 442 types.
-This small set, however, covers at least 50\% of the objects in VisualGenome, i.e.
-almost 2M objects in VisualGenome are mentioned in a region descriptions with one of these 442 entry-level names.
 
@@
 	\end{tabular}
-	\caption{Basic statistics for entry-level names in MN}
+	\caption{Basic statistics for entry-level names in MN. Av. agreement denotes the proportion of annotators that annotated a certain name for an object. }
 	\label{tab:stat-entry-level}
@@
 
-\paragraph{Entry-level Names are Instance-Dependent:} In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name.
+\paragraph{Entry-level Names in ManyNames:} As shown in Table \ref{tab:stat-entry-level}, ManyNames provides a large vocabulary of names (7970) for 25K objects.
+Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on.
+The vocabulary of entry-level names is drastically smaller and contains only 442 types.
+This small set, however, covers at least 50\% of the objects in \vg, i.e.
+almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
+
+\paragraph{Entry-level Names are Instance-Dependent:} 
+\cs{Make consistent with what is (was) in the intro wrt formulation:}
+In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name.
 The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names).
-Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \textit{duck} is named \textit{bird} by most annotators.
+Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
 We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g.
-\textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).
+\name{boy-player}, \textit{sandwich-food}, \name{building-church}, ...).
 
+\iffalse
 \sz{does this solve this?
@@
 Matthijs is on it.}
+\fi
 
+TODO: 
 \sz{somewhere we should mention these tendencies on adequacy and agreement for (non-)entry-level names shown in Table \ref{tab:stat-entry-level}}
@@
 \paragraph{Identifying entry-level names requires many annotators}
+\iffalse
 ManyNames was collected in four rounds of 9 annotators each.
-On average, the most frequent names differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
+On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
 Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
@@
 But I think the following is better:}
+\fi
 \begin{figure}[t]
@@
 \end{figure}
-For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
-The blue line shows that, even after gathering 10 names, the majority name is this likely to be the entry-level name for only 68\% of objects (put differently: for the remaining 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
+For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability.
+% (a reasonable confidence requirement).
+The blue line shows that, even after gathering 10 names, the majority name is  likely to be the entry-level name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
 Gathering 20 names increases this to 78\%.
-The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
+The red line shows the same tendency but by taking only names from the cluster of the entry-level name into account (as identified by our hard clustering in \ref{sect:mn_verification}): 
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level level out well below 100\%, reflecting that for 15\%-20\% \cs{Can you compute that individually for each domain?} of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
+Both lines level out well below 100\%, reflecting that for 15\%-20\% \cs{If time permits, can you compute that individually for each domain, and mention what/if something stands out?} of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
+\cs{@mw: see discussion on slack wrt following comments - can you add what was agreed upon there?}
 \mw{@cs, @sz, @gbt: A closely related (but different) question this immediately brings to mind (of a critical reviewer?) is: how sure are we, for a given object, given the particular names we gathered, that the most frequent name in our sample (what we \emph{call} the entry-level name) is indeed the most frequent name in the population (what actually \emph{is} the entry-level name, right?)?
@@
 
-\paragraph{Of Verification Annotations}
-
-\cs{@gbt @mw}
-
+\paragraph{TODOS (if possible)}
 \begin{itemize}
-	\item ...
-	\item ...
-	\item For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering).
-	\item Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. 
+	\item For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering). (for Sect 4)
+	\item Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. ()for Sect 4)
 \end{itemize}
 
-%%% Local Variables:
 %%% mode: latex

### 2019-12-08 analysis/analysis_verification_matthijs.py
refractoring

@@ -1,18 +1,7 @@
-# global variables
-ADEQUACY_THRESHOLD = .5   # adequacy of entry name (and, in one condition, alternative names) should be at least...
-CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
-NUM_SAMPLES_FOR_STABILITY = 30
-
-SUBSAMPLE = 1000       # for debugging
-
-SUBSETS_TO_PLOT = ['all names', 'canonical object names']
-
 import os
-import sys
 import pandas as pd
 import matplotlib.pyplot as plt
 import numpy as np
-from ast import literal_eval
 from collections import Counter
 import itertools
 from tqdm import tqdm
@@ -27,18 +16,221 @@ from analysis import load_results
 
 import random
 import statistics
+
 random.seed(12345)
 np.random.seed(129387)
-
 pd.set_option('display.max_colwidth', 180)
 pd.set_option('expand_frame_repr', False)
-
 sns.set(font_scale=1.2)
 
-auxfile = 'aux/stability_samples_{}_{}_{}_{}'.format(ADEQUACY_THRESHOLD, CANONICAL_THRESHOLD, NUM_SAMPLES_FOR_STABILITY, SUBSAMPLE)
-os.makedirs('aux', exist_ok=True)
 
-settings = ['all_names', 'entry_cluster_names']
+ADEQUACY_THRESHOLD = .5   # adequacy of entry name (and, in one condition, alternative names) should be at least...
+CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
+NUM_SAMPLES_FOR_STABILITY = 30
+SUBSAMPLE = False       # for debugging
+
+def analytic(auxfile):
+
+    settings = ['all_names', 'entry_cluster_names']
+
+    recompute = not os.path.exists(auxfile) or input("Overwrite existing auxiliary file (recompute the sampling)? y/N").lower().startswith("y")
+
+    if recompute:
+
+        csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
+        df = load_results.load_cleaned_results(csvfile)
+
+        if SUBSAMPLE:
+            print("WARNING: LOOKING ONLY AT PART OF THE DATA FOR DEBUGGING")
+            df = df.sample(n=SUBSAMPLE)
+
+        df['probabilities_all_names'] = df['spellchecked'].apply(lambda x: sorted([x[n] / 36 for n in x], reverse=True))
[…]

### 2019-12-08 papers/ACL2020/analysis.tex
new TABLE, with human-like errors

@@
-\gbt{To do: better structure content into subsections. Decide which results to report. Adapt text.}
+The previous Section \ref{}
 
@@
 	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+\begin{tabular}{ll|rrrr|rrrr|rrrr}
 \toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$	& GTtrain  
-		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
+&  & \multicolumn{4}{c||}{All objects} & \multicolumn{4}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
+               model &  GT &  hit &  valid &  err$_{hum}$ &  err &  hit &  valid &   err$_{hum}$ &   err &  hit &  valid &  err$_{hum}$ &  err \\
 \midrule
-		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
-		\midrule
-		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
+       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.3 &         7.5 &    4.5 &      94.8 &           0.5 &              2.1 &             2.6 &     63.6 &         20.4 &            10.5 &            5.5 \\
+        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.4 &         8.1 &    7.4 &      89.6 &           0.8 &              3.4 &             6.2 &     60.7 &         20.5 &            10.8 &            8.0 \\
+ FRCNN$_{\text{VG1600VGMN}}$ &  MN & 80.7 &      8.8 &         7.4 &    3.2 &      94.5 &           0.0 &              4.2 &             1.3 &     72.9 &         13.7 &             9.2 &            4.2 \\
+     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.4 &        15.8 &   10.0 &      88.3 &           0.5 &              5.7 &             5.5 &     48.5 &         17.5 &            21.4 &           12.5 \\
+     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.2 &        13.9 &    8.1 &      89.6 &           0.5 &              4.9 &             4.9 &     57.0 &         14.1 &            19.0 &            9.9 \\
+    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.3 &        13.5 &    7.5 &      90.1 &           0.5 &              4.4 &             4.9 &     58.2 &         14.3 &            18.7 &            8.9 \\
+    ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.6 &        14.8 &    9.8 &      88.6 &           0.8 &              4.4 &             6.2 &     49.9 &         17.6 &            20.7 &           11.8 \\
 \bottomrule
 \end{tabular}
-	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
+
+\caption{New table} \label{tab:humanlike}
 \end{table*}

### 2019-12-08 papers/ACL2020/analysis.tex
reducing Section 5 to 2 tables

--- 2019-12-08 papers/ACL2020/analysis.tex
@@
-\gbt{To do: better structure content into subsections. Decide which results to report. Adapt text.}
+The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
+This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.
+In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behaviour.
 
@@
 	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
+\begin{tabular}{ll||rr|rrr}
 \toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$	& GTtrain  
-		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
+&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
+                         model &  gt &  hit &  valid &  human-like &  related &  off \\
 \midrule
-		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
+       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
+        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
         \midrule
-		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
+ FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
+         \midrule
+     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
+     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
+    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
+    ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
 \bottomrule
 \end{tabular}
-	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
+
+\caption{Model results for different categories of errors} \label{tab:humanlike}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+	\small
+\begin{tabular}{ll|rrr|rrr}
+\toprule
+&  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
+                         model &  gt &  hit &  valid &  incorrect &  hit &  valid &  incorrect \\
+\midrule
+       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &      0.8 &      4.4 &   63.6 &     21.0 &     15.5 \\
+        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &      0.8 &      9.6 &   60.7 &     20.8 &     18.5 \\
+                \midrule
+ FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &      0.0 &      5.5 &   72.9 &     14.0 &     13.1 \\
+         \midrule
+     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &      0.5 &     11.2 &   48.5 &     17.8 &     33.7 \\
+     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &      0.5 &      9.9 &   57.0 &     15.2 &     27.8 \\
+    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &      0.5 &      9.4 &   58.2 &     15.2 &     26.7 \\
+    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &      0.8 &     10.6 &   49.9 &     18.1 &     32.1 \\
+\bottomrule
+\end{tabular}
+\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
 \end{table*}
@@
 
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ &  GTtrain & same &  syn. &  syn. &  hyper. &  hypo. &  hyper. &  same &  syn. &  syn. &  hyper. &  hypo. &  hyper. \\
-		& 	&  cluster &  & cluster & & & cluster 
-		& cluster  &  & cluster & & & cluster \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     %        &                  0.95 &              0.0 &                0.01 &              0.01 &             0.03 &                 0.0 &                  0.96 &              0.0 &                 0.0 &              0.01 &             0.03 &                 0.0 \\
-		&                  94.6 &              0.0 &                 0.7 &               3.4 &              1.3 &                  0.0 &                  95.5 &              0.0 &                 0.0 &               3.0 &              1.5 &                  0.0 \\
-		FRCNN$_{\text{MN442}}$ & VG %&                   0.97 &             0.01 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  93.3 &              1.3 &                 2.0 &               1.3 &              2.0 &                  0.0 &                  93.8 &              0.0 &                 3.1 &               1.6 &              1.6 &                  0.0 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 &                   1.0 &              0.0 &                 0.0 &               0.0 &              0.0 &                 0.0 \\
-		&                  94.9 &              0.0 &                 0.0 &               2.0 &              3.0 &                  0.0 &                  96.2 &              0.0 &                 0.0 &               1.9 &              1.9 &                  0.0 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN %&                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  83.9 &              0.0 &                 2.7 &               6.2 &              5.4 &                  1.8 &                  92.6 &              0.0 &                 1.9 &               1.9 &              3.7 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & MN %& 0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  86.4 &              0.0 &                 2.7 &               5.5 &              3.6 &                  1.8 &                  92.3 &              0.0 &                 1.9 &               1.9 &              3.8 &                  0.0 \\
-		ResNet101$_{\text{VGMN}}$ & VG %&                   0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 \\
-		&                  87.4 &              0.0 &                 2.2 &               1.5 &              8.1 &                  0.7 &                  92.5 &              0.0 &                 1.5 &               1.5 &              4.5 &                  0.0 \\
-		ResNet101$_{\text{MN442}}$ & VG% &                  0.98 &              0.0 &                0.02 &               0.0 &              0.0 &                 0.0 &                  0.97 &              0.0 &                0.03 &               0.0 &              0.0 &                 0.0 \\
-		&                  88.9 &              0.0 &                 2.2 &               2.2 &              5.9 &                  0.7 &                  92.5 &              0.0 &                 3.0 &               1.5 &              3.0 &                  0.0 \\
-		\bottomrule
-	\end{tabular}
-
-	\caption{Break-down of the results for the \textit{correct} name predictions.
-Proportions (in \%) of the \textit{correct} categories to all correctly classified instances.
-\textit{hyponym}: $\hat{n}$ is a hyponym of the entry-level name.
-\textit{hypernym\_cl}: $\hat{n}$ is a hypernym of any of the valid names (cluster).
-\textit{Synonym} and \textit{synonym\_cl} are analogous.
-\label{tab:exp_alternatives}}
-\end{table*}
-
-\paragraph{Incorrect Predictions}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}||r@{~}|r@{~}r@{~}r@{~}r@{~}|r@{~}r@{~}}
-		\toprule
-		&& \multicolumn{7}{c}{All Test Images ($\#$)} 
-		& \multicolumn{7}{c}{VG$\neq$MN Images ($\#$)}\\
-		\toprule
-		Model$_{\text{Vocab}}$ & GTtrain  
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low 
-		&  co- &  \multicolumn{4}{c}{other object}  &  error &  low \\
-		& & hypo. & (vis. &  ling. &  box &  other)   & & count 
-		&  hypo. & (vis. &  ling. &  box &  other) &   & count     \\
-
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG     &                 13.2 &             1.7 &                 0.0 &                  17.4 &            6.6 &           39.7 &             21.5 &                  5.7 &             5.7 &                 0.0 &                  17.1 &           14.3 &           42.9 &             14.3 \\
-		FRCNN$_{\text{MN442}}$ & VG       &                 15.5 &             0.6 &                 0.0 &                  15.5 &            6.2 &           49.1 &             13.0 &                  5.9 &             2.0 &                 0.0 &                  13.7 &           11.8 &           54.9 &             11.8 \\
-		\midrule \midrule
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &                 30.6 &             0.9 &                 0.0 &                  13.0 &            5.6 &           32.4 &             17.6 &                 16.7 &             2.8 &                 0.0 &                  16.7 &           11.1 &           41.7 &             11.1 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN	&                 34.1 &             0.0 &                 0.0 &                  13.0 &            1.3 &           39.5 &             12.1 &                 19.6 &             0.0 &                 0.0 &                  12.5 &            5.4 &           51.8 &             10.7 \\
-		ResNet101$_{\text{MN442}}$ & MN  &                 33.0 &             0.0 &                 0.0 &                  14.0 &            1.9 &           37.7 &             13.5 &                 21.1 &             0.0 &                 0.0 &                  15.8 &            7.0 &           43.9 &             12.3 \\
-		ResNet101$_{\text{VGMN}}$ & VG  &                 37.6 &             0.0 &                 0.0 &                   6.1 &            2.3 &           41.1 &             12.9 &                 24.4 &             0.0 &                 0.0 &                   3.5 &            5.8 &           45.3 &             20.9 \\
-		ResNet101$_{\text{MN442}}$ & VG &                 34.0 &             0.0 &                 0.0 &                   7.5 &            2.8 &           41.9 &             13.8 &                 22.6 &             0.0 &                 0.0 &                   6.0 &            8.3 &           39.3 &             23.8 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the results for the \textit{wrong} name predictions. Proportions (in \%) of the corresponding categories to all wrongly classified instances.  \label{tab:exp_details_wrong}}
-\end{table*}
-
 \paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
@@
 \end{itemize}
-
-\begin{figure*}[t]
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--MN442_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_FRCNN--VG1600--VGMN_MN.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--VGMN_VG.jpg}
-	\includegraphics[scale=.5]{images/matrix_FRCNN--VG1600_VG_ResNet101--MN442_MN.jpg}
-
-	\caption{Confusion-matrix-style visualization showing error categories of predictions that changed from object detection with FRCNN-VG1600 to naming with FRCNN-VG1600-VGMN (finetuned) \label{fig:exp_confusions}}
-\end{figure*}
 
@@
 
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|l|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
-		\toprule
-		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
-		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
-	\toprule
-	Model$_{\text{Vocab}}$	& GTtrain  
-	&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
-	\midrule
-	FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
-	FRCNN--MN442 & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
-	\midrule \midrule
-	FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
-	 &         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
-	\midrule
-	ResNet101--MN442 & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
-	 &         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
-	ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
-	 &         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
-	ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
-	 &         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
-	ResNet101--MN442 & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
-	 &         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
-	\bottomrule
-\end{tabular}
-\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf.
-standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake).
-\label{tab:exp_overview_results}}
-\end{table*}
-
 %%% Local Variables:

### 2019-12-08 papers/ACL2020/analysis.tex
some text in Section 5

@@
 In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behaviour.
+
+\paragraph{Error Categories} We categorize model predictions into the following types (also see Figure~\ref{fig:mistakes} for examples):
+
+\begin{itemize}
+\item Correct-hit: the entry-level name 
+\item Correct-valid: a name from the set of valid alternatives, a synonym or a hypernym (\textit{house/building})
+\item: Incorrect-human-like: a name produced by annotators, but not a valid alternative of the entry-level name  (\textit{chair/cat})
+\item Incorrect-related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+\item Incorrect-off: a non-sensical name (none of the above)
+\end{itemize}
+
+\subsection{How human-like are model predictions and errors?}
+
+Table \ref{tab:humanlike} shows the breakdown of the model results for the error categories explained above.
+An important general trend is that the proportion of human-like error seems to be surprisingly constant across all models.
+\sz{why??}
+Both object detection models essentially achieve the same portion of valid predictions.
+Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the models makes more nonsensical errors, which might be an effect of the reduction in training data.
+Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
+This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit by the finetuned classification model.
+All ResNet models produce a lot of errors in the ``related'' category, which suggests that they tend to confuse similar names that are, however, not valid.
 
@@
      ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
+         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
      ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
     ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
-    ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
 \bottomrule
@@
 
-\paragraph{Alternative Name Prediction}
 \begin{figure}
@@
 
-\cs{TODO::}
-Categorization of "errors" (see Figure~\ref{fig:mistakes}):
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.,\ plane vs. airplane
-	\item Semantically related\\
-	e.g.,\  motorcycle vs. scooter
-\end{enumerate}
+\subsection{How do predictions correlate with human agreement?}
 
-\paragraph{Human Object Naming through Transfer-Learning} Figure \ref{fig:exp_confusions} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
-For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
-Observations:
-\begin{itemize}
-	\item Retraining faster-rcnn on fewer, entry-level names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round.
-(top left matrix)
-	\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
-Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
-(top right matrix)
-	\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
-This is less the case when ResNet is finetuned on VG annotations.
-	\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
-\end{itemize}
+An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
+This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans \sz{is it okay to claim this?}.
+In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
+Here, we find a very clear pattern for all models, namely that the portion of hits is generally high when human agreement is also high.
+Note that this even holds for the ResNet-based classifiers that generally achieve less accuracy.
+When agreement is lower, all models produce less hits and more valid alternatives. 
+This indicates that there is indeed a certain similarity between what is difficult for humans and models.
+Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. \sz{why???}
 
-\subsection{[TBC] Humans vs. Models: Which Mistakes do they Make?}
-\label{sect:exp_analysis}
-
-\paragraph{Categorization of Errors}
-see Figure\ ref{fig:mistakes}
-\begin{enumerate}
-	\item Clear mistake \\
-	e.g.,\ rice vs. bread
-	\item Alternative name\\
-	e.g.,\ building vs. house
-	\item Alternative object \cs{(other cluster from verif data)}
-	\item Synonym\\
-	e.g.,\ plane vs. airplane
-	\item Semantically related\\
-	e.g.,\  motorcycle vs. scooter
-\end{enumerate}
-
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
-
-	\caption{resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:matrices}}
-\end{figure}
-
-\subsection{Results}
-
-\paragraph{Overview}
-Table\ \ref{tab:exp_overview_results}: \cs{Shows the overview and what MN adds without going into detail: Standard evaluation -- hit; We can additionally distinguish between correct (name alternative, see caption of Table) and clear mistake.}
-
-\paragraph{How do predictions change?} Figure \ref{fig:matrices} visualizes the change in predictions for  some of our retrained and finetuned models with respect to the object detection baseline (bottom-up-1600).
-For each object, where the new model predicts a different name than the baseline model, we look at the hit-error categories of the original and new predicted name.
-Observations:
-\begin{itemize}
-\item Retraining faster-rcnn on less names does not lead to better calibration of entry-level names: more original hits change to same-cluster predictions than the other way round. (top left matrix)
-\item Finetuning the original faster-rcnn on many names recalibrates many decision from same-cluster names to the correct hit.
-Interestingly, also clear errors are calibrated to perfect hits, whereas hardly any error is changed to same-cluster or related.
-(top right matrix)
-\item A similar tendency can be found for the ResNet models: finetuning ResNet on MN changes many predictions from same-cluster to hits.
-This is less the case when ResNet is finetuned on VG annotations.
-\item Interestingly, both ResNet models change hits into related names (hypernyms, hyponyms, cp-hyponyms) -- why does this happen?
-\end{itemize}
-
-\paragraph{Correct predictions}
-Table\ \ref{tab:exp_details_correct}: \cs{Gives detailed results to the categories of "correct name" (but not hit): same cluster, WordNet synonym, WordNet hypernym/hyponym}\\
-To look into in detail (example images): 
-\begin{itemize}
-	\item Compare FRCNN vs.
-FRCNN-finetuned (row block 1 vs.
-row block 2) with respect to the synonym categories (i.e., predicted name is in a synonym/synonyms\_cluster-relation to the target object) vs.
-same\_cluster (i.e., predicted name is in response set).
-\end{itemize}
-
-\paragraph{Wrong predictions}
-
-Table\ \ref{tab:exp_details_wrong}: \cs{Gives detailed results to the categories of predicted name\ $\hat{n}$ is incorrect: WordNet co-hyponyms,  other object (inadequacy types: visual, linguistic, bounding box, other (types other+None), $\text{count}(\hat{n})<2$, error (just wrong+unkn(not found in WordNet))}
+%\cs{TODO::}
+%Categorization of "errors" ():
+%\begin{enumerate}
+%	\item Clear mistake \\
+%	e.g.,\ rice vs. bread
+%	\item Alternative name\\
+%	e.g.,\ building vs. house
+%	\item Alternative object \cs{(other cluster from verif data)}
+%	\item Synonym\\
+%	e.g.,\ plane vs. airplane
+%	\item Semantically related\\
+%	e.g.,\  motorcycle vs. scooter
+%\end{enumerate}
 

### 2019-12-08 analysis/analysis_verification_matthijs.py
tweak stability plot; allow plot per domain (cat), also add some provisional stats code

@@ -8,7 +8,7 @@ from tqdm import tqdm
 
 from functools import reduce
 from operator import mul
-from math import factorial as fac, floor
+from math import factorial as fac
 
 import seaborn as sns
 
@@ -28,6 +28,41 @@ ADEQUACY_THRESHOLD = .5   # adequacy of entry name (and, in one condition, alter
 CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
 NUM_SAMPLES_FOR_STABILITY = 30
 SUBSAMPLE = False       # for debugging
+
+def basic_stats():
+
+    csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
+    df = load_results.load_cleaned_results(csvfile)
+
+    errors = []
+    for i, row in tqdm(df.iterrows(), total=len(df)):
+        for n in row['verified']:
+            errors.append([row['cat'],
+                           n,
+                           row['spellchecked_min2'][n],
+                           row['verified'][n]['adequacy'],
+                           row['verified'][n]['inadequacy_type'],
+                           int(round(row['verified'][n]['adequacy']))
+                           ])
+
+    errors = pd.DataFrame(errors, columns=['cat', 'name', 'count', 'adequacy', 'inadequacy_type', 'adequacy_bin'])
+    errors['inadequacy_type_level'] = errors['inadequacy_type'].apply(str) + errors['adequacy_bin'].apply(str)
+
+    counts = errors['inadequacy_type_level'].value_counts()
+
+    # counts = counts[['None1', 'None0', 'bounding box1', 'bounding box0', 'visual1', 'visual0', 'linguistic1', 'linguistic0', 'other1', 'other0']]
+
+    print(counts)
+    print(counts / counts.sum())
+
+    counts.plot.pie()
+    plt.show()
+
+    quit()
+
+    pass
+
+
 
 def analytic(auxfile):
 
@@ -57,20 +92,37 @@ def analytic(auxfile):
 
     df = pd.read_csv(auxfile)
 
+    # for i, row in df.iterrows():
+    #     domains = {}
+    #     for r in range(4):
+    #         domains.update(eval(row['responses_domains_r{}'.format(r)]))
+    #     entry_name = eval(row['spellchecked_min2']).most_common(1)[0][0]
+    #     if entry_name in domains:
+    #         df.at[i, 'domain'] = domains[entry_name]
+    #     else:
[…]

### 2019-12-09 papers/ACL2020/introduction.tex
[ACL2020] introduction.tex v3

@@
-\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
-\cs{need to discuss problematic of standard evaluation procedure of CV models}
+\cs{need to make clear the diff btw objects meaning the class and meaning an instance}
 
-When people talk, they choose particular names for objects, such as \textit{bird} or \textit{duck} for the images in Figure~\ref{fig:duck}.
-The task of \textbf{object naming} has been studied in Psycholinguistics~\cite{refs}, \gbt{Which term do you prefer, Psycholing, or CogSci?
-I don't care.
-Use same term throughout.} but has not received much attention in Computational Linguistics; we seek to remedy this situation by providing data and modeling results on this phenomenon, and in particular on \textbf{entry-level names}, defined in psycholinguistic research as the preferred name for an object~\cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}: For the left object in the figure, according to our data, the entry-level name is \textit{bird}, and for the right object it is instead \textit{duck}.
-%We seek to shed light into how people naturally name objects in real images, and in
+Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
+The task of \textbf{object naming} has been studied in psycholinguistics~\cite{refs}, but has not received much attention in \langvis (\lv) and computational linguistics (CL) research. 
+We seek to remedy this situation by providing data and systematic modeling insights on the  phenomenon of naming real-world objects, and in particular on \textbf{entry-level names}, the name people  prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, right image).
 
-Our contributions are two-fold.
-First, we provide data on object naming with real images on a large scale.
-We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
-Second, we provide an extensive analysis of the performance of object classification models on the task of predicting the entry-level names in our dataset.
-
-\begin{figure}[htb]
+In \lv, the choice of a particular name for an object is a ubiquitous problem---it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering, referring expression generation, etc.
+\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single correct label of objects.
+The labels seem often to be unintuitive from a human perspective---they may be "basic-level" (e.g., \name{bus}), but also very specific labels (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+This pre-training strategy on such labels has its justification in that computer vision models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp--pointed vs.
+slightly pointed).
+Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label. 
+In contrast, the goal of \lv naming models is to predict the natural name of an object, i.e.,~the name humans would choose for the object instance in the given visual situation and points of view. 
+Moreover, as psycholinguistic studies found, humans have a preference towards a particular name, defined as the \textit{entry-level name} (e.g.,\ \name{duck}) when naturally calling an object  \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
+Note, though, that this research has focused on \categories\footnote{When a sub-ordinate level \category is atypical, such as penguins not being very typical birds, this affects their entry-level name (it is common to call a sparrow, but not a penguin, \name{bird}).}, as opposed to instances \lv is encompassed with, for which humans may prefer different names for instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+For example, Figure~\ref{fig:duck} shows two instances of a duck, and when people were asked to name the highlighted object, most people ($27$) called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance.
+Hence, the single-ground truth view of CV models %, which was generally adopted by \lv models, 
+is inconclusive for assessing the effectiveness of \lv human entry-level naming models.
+\begin{figure}[t]
 	\centering
@@
 \end{figure}
+In this paper, addressing the task of \textit{instance-based entry-level object naming}, we put forward a more nuanced evaluation scheme, that goes beyond judging model effectiveness on predicting the entry-level name, and analyses models also in terms of the degree of ``mistakes" it makes (e.g.,~the prediction may be a less preferred name as opposed to a true error).
+
+Our contributions towards the task of instance-based entry-level naming in \lv and CL research are two-fold:  
+First, we provide data on object naming with real images on a large scale. 
+We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
+We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{krishna2016visualgenome}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+
+Second, we introduce the verified \mn dataset as evaluation data, and provide an extensive analysis of the ability of object detection and classification models to account for entry-level object naming in our dataset.
+We show that object classification models ``spontaneously'' learn to provide entry-level names for objects, and that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and classification models to train entry-level name classifiers.
+
+\iffalse
+%However, when they speak, humans in general name specific \textit{instances} of objects---actually, instances in particular situations and points of view, which may humans have prefer different names for instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+
+%Accordingly, datasets used for object naming in Psycholinguistics use idealized drawings that correspond more to categories than to instances~\cite{+++++}.
+%
+%
+
+Despite its relevance in \lv and CL, the challenge of instance-based natural naming has been overseen. 
+\lv research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted the \category-based concept of entry-level names \cite{Ordonez:2016}. 
+Furthermore, existing datasets lack necessary information to make progress in \lv and CL research on this phenomenon. 
+\cs{TODO@CS: EVALUATION ISSUE GOES HERE.}
+\begin{itemize}
+	\item resources developed in CV and \lv can be useful to study object naming. 
+	\item However, they provide only one (or a few) name per object \ra no guarantee that it is the entry-level name.
+(We provide more, to have a robust estimate of entry-level names (as well as data on other possible names).
+\gbt{actually, maybe move this to the previous part?
+\ra differences with Psycholing, with CV resources})
+	\item object naming has often been conflated with object classification in CV. \gbt{Discuss differences; mention the swan - whatever name it has in wordnet example of ordonez et al?}
+	\item a big problem with this approach is that it follows a single-label evaluation.
+With our data, we show that often model responses are adequate even if they do not correspond to the entry-level name.
+	\item we also show that object classification models ``spontaneously'' learn to provide entry-level names for objects
+	\item and that it is possible to use \mn to successfully fine-tune existing object detection and classification models to predict entry-level names for objects.
+\end{itemize}
+
+This paper seeks to spur \lv and CL research on the problem of \textit{instance-based entry-level object naming}.
+
+Our contributions are two-fold:  
+First, we provide data on object naming with real images on a large scale. 
+We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
+We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+
+\cs{I'll continue from here.}
+Second, we introduce the verified \mn dataset as evaluation data that allows XXX.
+We provide an extensive analysis of the ability of object detection and classification models on the task of predicting the entry-level names in our dataset.
+
+When people talk, they choose particular names for objects, such as \textit{bird} or \textit{duck} for the images in Figure~\ref{fig:duck}.
+The task of \textbf{object naming} has been studied in Psycholinguistics~\cite{refs}, \gbt{Which term do you prefer, Psycholing, or CogSci?
+I don't care.
+Use same term throughout.} but has not received much attention in Computational Linguistics; we seek to remedy this situation by providing data and modeling results on this phenomenon, and in particular on \textbf{entry-level names}, defined in psycholinguistic research as the preferred name for an object~\cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}: For the left object in the figure, according to our data, the entry-level name is \textit{bird}, and for the right object it is instead \textit{duck}.
+%We seek to shed light into how people naturally name objects in real images, and in
+
+Our contributions are two-fold.
+First, we provide data on object naming with real images on a large scale.
+We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+Our data contain object instances, corresponding more closely to the kind of visual objects that humans typically encounter, and so can potentially shed light on the instance-level factors that affect naming.
+
+Second, we provide an extensive analysis of the performance of object classification models on the task of predicting the entry-level names in our dataset.
+
 As for the former, note that Psycholinguistic research on entry-level names has focused on categories, as opposed to instances:
@@
 
+\fi
 %%% Local Variables:

### 2019-12-09 papers/ACL2020/related.tex
[ACL2020] related - typos

@@
-As we outline in the following, our work on natural object naming is of relevance to research in psychology, \langvis and computer vision.
+As we outline in the following, our work on natural object naming brings together  research in psycholinguistics, \langvis and computer vision.
 
@@
 %- Our work: empirical notion of entry-level
-
-In psychology and cognitive science, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}.
-The typicality of the object with respect to this basic-level category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level category (\name{bird}), while for atypical objects  (e.g.,\ \name{penguin}) the more specific name corresponds to the entry-level category.
-This strictly taxonomic view suggests that entry-level names generally hold for all instances a category (e.g.,\ penguin). 
-\newcite{Ordonez:2016} take up this view and learn to transfer an object's category detected by an object recognition system to its natural name, using external resources like corpus statistics. 
-In contrast, our work exploits actual naming data for instances of real-world objects and tests object naming model on ManyNames, a corpus with robust name annotations from many different speakers.
-This dataset is comparable to picture naming data, though we focus on real-world objects in images instead of prototypical line drawings as in e.g.\ \cite{rossion2004revisiting}, 
- \newcite{zarriess-schlangen:2017} learn a naming model from names produced in referring expressions to real-world objects, but they do not have access to name annotations from (many) different speakers and adopt very simply evaluation measures (like accuracy).
- This work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
+\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
+In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
+The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while for atypical objects  (e.g.,\ \name{penguin}) the more specific name corresponds to the entry-level category.
+This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin). 
+\newcite{Ordonez:2016} take up this view and learn to transfer an object's \category detected by an object recognition system to its natural name, using external resources like corpus statistics. 
+In contrast, our work exploits actual naming data for instances of real-world objects and tests object naming models on ManyNames, a corpus with robust name annotations from many different speakers.
+This dataset is comparable to picture naming data, though we focus on real-world objects in images instead of prototypical line drawings as in, e.g.,~\newcite{rossion2004revisiting}.  
+ \newcite{zarriess-schlangen:2017} learn a naming model from names produced in referring expressions to real-world objects, but they do not have access to name annotations from (many) different speakers and adopt very simple evaluation measures (like accuracy).
+Our present work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
  \sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}
@@
 \paragraph{Visual Object Recognition in Computer Vision}
-- Object detection, using pre-trained features representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
+- Object detection, using pre-trained feature representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
 - Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image).

### 2019-12-09 papers/ACL2020/analysis.tex
example figure for annotations, verification, predictions

@@
 
+\begin{figure}
+	\centering
+	\footnotesize
+	\begin{tabular}{p{3.7cm}p{3.7cm}}
+	\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
+	\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
+	\\
+	Entry-level: rug (21) &  animal (9)\\
+	\midrule
+	Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
+	Error-box: chair (5, 0.5), floor (3, 0.5) & \\
+	Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
+	\midrule
+	FRCNN$_{\text{VG1600}}$: floor & animal\\
+	FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
+	\end{tabular}
+	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
+\end{figure}
+
 \subsection{How do predictions correlate with human agreement?}

### 2019-12-09 papers/ACL2020/analysis.tex
[ACL2020] analysis

--- 2019-12-08 papers/ACL2020/analysis.tex
@@
 The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
-This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.
-In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behaviour.
+This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.\cs{XX}
+In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behavior.
 
@@
 \item Correct-hit: the entry-level name 
-\item Correct-valid: a name from the set of valid alternatives, a synonym or a hypernym (\textit{house/building})
-\item: Incorrect-human-like: a name produced by annotators, but not a valid alternative of the entry-level name  (\textit{chair/cat})
+\item Correct-valid: a name from the set of valid alternatives, a synonym or a hypernym (\name{house/building}) \cs{set of alternatives:: task1: all, task2: only adequacy$>$0.5}
+\item Incorrect-human-like: a name produced by annotators, but not a valid alternative of the entry-level name  (\name{chair/cat}) \cs{task1: other object; low count; task2: alternatives adequ $<$ 0.5 (other object, low count)}
 \item Incorrect-related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
@@
 \end{itemize}
+\cs{WordNet}
 
-\subsection{How human-like are model predictions and errors?}
+\subsection{How Human-Like are Model Predictions and Errors?}
 
@@
 Both object detection models essentially achieve the same portion of valid predictions.
-Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the models makes more nonsensical errors, which might be an effect of the reduction in training data.
+Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column off), which might be an effect of the reduction in training data.
 Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
-This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit by the finetuned classification model.
-All ResNet models produce a lot of errors in the ``related'' category, which suggests that they tend to confuse similar names that are, however, not valid.
+This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
+The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse semantically similar names to a valid name, that are, however, not valid.
 
@@
 An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
-This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans \sz{is it okay to claim this?}.
+This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.
+\sz{is it okay to claim this?}.\cs{how about the way it is now?}
 In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.

### 2019-12-09 papers/ACL2020/analysis.tex
[ACL2020] analysis: Table which subsumes Tasks1+2

@@
 \caption{Model results for different categories of errors} \label{tab:humanlike}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+\begin{tabular}{ll||c|cccc|c}
+	\toprule
+	  &  & Hit & \multicolumn{4}{c|}{Human-like} & Off \\
+	Model &  GT &  & SameObject &  OtherObject &  Low Count &  Related &   \\
+	\midrule
+	FRCNN--VG1600&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
+	FRCNN--MN442&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
+	\midrule
+	FRCNN--VG1600--VGMN&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
+	\midrule
+	ResNet101--VGMN&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
+	ResNet101--MN442&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
+	ResNet101--VGMN&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
+	ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\
+
+	\bottomrule
+\end{tabular}
 \end{table*}

### 2019-12-09 papers/ACL2020/manynames.tex
push sec3 (still ongoing)

@@
 	\item For each object: a response set comprising all entered names (spellchecked) and their respective counts, i.e., the number of annotators which enter the respective name.
-	\item Problems: referential uncertainty: object other than target object was  identified as named
+	\item Problems \mw{I already had a go writing a 'bridge' paragraph containing this; see below.}: referential uncertainty: object other than target object was  identified as named
+	\item \cs{Mention how agreement on \mn is computed (anticipating that we'll be taking a closer look at this in 3.3 when the verification is in place).}
 \end{itemize}
 
-\subsection{Verification of Annotations}
+\mw{Sina wrote this in 3.3; I think it should go here in 3.1., in order for 3.3 to more clearly show the added value of verification:}
+ManyNames provides a large vocabulary of names (7970) for 25K objects.
+Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on. 
+The vocabulary of entry-level names -- defined for each object as the most frequent name given -- is drastically smaller and contains only 442 types. 
+This small set, however, covers at least 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
+
+Manual inspection of the \mn data revealed that annotators occasionally named an object different from the one highlighted by the bounding box (e.g., the name \emph{helmet} when the bounding box highlights an entire motorcyclist), or the right object but with an incorrect name (e.g., ``horse'' for a cow), and sometimes the bounding box may have been unclear.
+Although these errors are interesting human data in their own right, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology used for \mn, where there is a financial incentive to complete the task as quickly as possible.
+As such they pose a challenge for our research goal, which is to see whether the object-naming ability of computational models resembles those of actual language users.
+
+\subsection{Collecting verification of ManyNames}
 \label{sect:mn_verification}
-\cs{START TODO at the end}
-Goal: Verification of entered object names necessary to exclude incorrect names (wrong object was named) required. \\
-Collected: adequacy judgements from 0-2; source/type of inadequacy; CLUSTERS: for each entry-level name (or any other name in the response set), all its valid alternatives.
-\cs{END TODO }
 
-We used Amazon Mechanical Turk\footnote{(\url{https://mturk.com})} (AMT) to verify all the \mn naming data (response sets), with two exceptions: We consider response sets with ~$100$\%~agreement (i.e.,~all annotators gave the same name for an object) as correct, so do not require verification, and all names with a count of~$1$ as unreliable, so we directly discarded those from the sets.
-We collected verifications for the remaining $19,427$~objects, with on average $4$ names each, as follows: 
+To overcome the aforementioned challenge we collected a new layer of verification annotations on top of \mn.
+We recruited annotators from Amazon Mechanical Turk\footnote{
+	\url{https://mturk.com}
+} (AMT) to categorize the object-name pairs from \mn into various categories (e.g., adequate vs.\ different types of errors), explained below.
+Since this is a multiple-choice task (unlike the generation task through which \mn was gathered) we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).
+
+We verified all the \mn naming data (response sets), with two exceptions: 
+We consider response sets with ~$100$\%~agreement (i.e.,~all annotators gave the same name for an object) as correct, so do not require verification, and all names with a count of~$1$ as unreliable, so we directly discarded those from the sets.
+We collected verifications for the remaining $19,427$~objects, with on average $4$ names each, which we did as follows:
+
 For each object, we presented $3$~annotators with its image, with the object highlighted by its bounding box, and a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
-They were asked to judge the ``adequacy''\footnote{We defined that \textit{a name is   ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.} of each name on a 3-point scale (with $0$=``perfectly adequate'', $1$=``there may be a (slight) inadequacy'', and $2$=``totally inadequate'').
-In the case they did not choose ``adequate", they had to specify the type of inadequacy (``linguistic mistake", ``named object not tightly in bounding box",  ``named object mistaken for something it's not", and ``something else").
-\cs{maybe in ManyNames we need exampled for all those, when the need for verification is explained.}
+They were asked to judge the ``adequacy''\footnote{
+	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
+} of each name on a 3-point scale (represented pictorially): ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
+Whenever they did not select ``adequate'', they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else'' (represented pictorially).
+In addition to judging name adequacy, we asked the annotators which names they thought were likely intended (by the original    quit()
+ \mn annotators) to name the \textit{same} real-world object, 
+through an intuitive coloring task where they would assign the same color to names intended for the same object (again, see Figure~\cs{1}).
+Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
 
-In addition to judging name adequacy, we asked the annotators to cluster the list of names (through coloring), such that each group (color) would comprise the names they thought to be likely intended (by the \mn annotators entering the name) for the \textit{same} real-world object.
-
-\iffalse
-Although the initial data gathering phase involved some very basic quality control (detecting repeated names, empty text fields, typos), we had no rigorous way of ascertaining that our participants were providing adequate names for the intended object.
-\fi
-
-Since the quality of the data we gather in this phase will be essential for gaining insight into the \mn dataset, as well as for evaluating computational models (Section~\ref{sec:experiments}), we conducted rigorous quality control (see the supplementary material for details).
+\mw{I think the following is nice, but strictly redundant, so candidate for deletion if need be:}
+Summing up, we provide new verification of \mn, in the form of: name adequacy judgments, type of inadequacy (linguistic, bounding box, named object misinterpreted, other), and information about which names were likely intended for the same object.
+In relation to our research goal, in section~\ref{sec:analysis} these results will allow us to quantify, for instance, whether the name generated by a given model, if it is not the entry-level name, is at least a name that could reasonably be for the same object as the entry-level name, and whether it is adequate.
 
@@
 
-\paragraph{Postprocessing and Basic Statistics}
-\cs{Table moved to suppl.}
+\paragraph{Judgment aggregation}
+Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
+We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority (counting ``none'' for annotators saying there is no inadequacy). 
+Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
+Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
+We consider this level of agreement as high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
+Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our individual annotators reported (a), as well as the aggregated (mean/majority) judgments (b).
 \begin{figure}[t]
 	\centering
-	\hspace*{.2\columnwidth}\includegraphics[width=.7\columnwidth]{images/verification_piechart.pdf}
-	\caption{Verification results (counting individual annotations). Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
+	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
+	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
+	\caption{Verification results: a.
+counting individual annotations; b.
+counting image-name pairs with their aggregated scores.
+Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
 	\label{fig:verification-piechart}
 \end{figure}
-\mw{Possibly a pie-chart counting actual names and their aggregated (+thresholded) scores would be more informative than the current pie-chart, which counts original (i.e., non-aggregated) verification annotations.}
-\cs{If you have time for it, @MW, could you add this in addition?}
-%
-Overall, $255$~annotators a total of $69,356$~obj--name pairs.
-We aggregate our name adequacy judgments (representing adequate as 1, slightly inadequate as 0.5 and totally inadequate as 0) by taking the mean, and inadequacy type judgments by taking the majority (also counting ``none'' if there was no inadequacy).
-Average name adequacy on this scale of $[0,1]$ is 0.80 (\mbox{std=$0.093$}). \cs{@MW: check that this is the right place here.}
-Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
-We consider this level of agreement as high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
-Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our annotators reported.
 
-As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes.\cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it?
+As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes: \sameobject and \cluster.
+% \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it?
 In this case, it would be "aggregating name cluster", no?!
-So what you did for the first aggregation (modeling) was a pair-wise aggregation?}
-For analysing computational object naming models, we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names. 
-%want to know primarily whether a name generated by a model could have been intended to name the same object as the entry-level name (i.e., the most frequent name).
-This we compute, by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-
-For analysing object naming on the verified \mn data (Section~\ref{sect:mn_analysis}), e.g.~assess the mean number of names per object, however, 
+So what you did for the first aggregation (modeling) was a pair-wise aggregation?} \mw{I don't understand this...}
+First, for analysing computational object naming models (Section~\ref{sec:analysis}), 
+% we want to have all valid name alternatives to the entry-level name (or a target name in general), i.e.,~a soft clustering of names.
+	% <- Carina's reformulation, but not strictly true and not clear to me.
+we want to know primarily whether the name generated by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name (i.e., the most frequent name).
+This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
+Second, for a better understanding of the verified \mn data itself (Section~\ref{sect:mn_analysis}) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering).
 %However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
 %For this, 
-we need \cs{@MW please check if that's correct}  to compute hard clusters
-%clusters of names
-(the pairwise majority rule does not result in a proper clustering): as distance between names we use the proportion of annotators saying they do not name the same object, and we perform agglomerative, complete-linkage clustering with a threshold of .5 (i.e., all pairs of names in a cluster must name the same object according to a majority of annotators).
+% we need \cs{@MW please check if that's correct} \mw{No it isn't} to compute hard clusters
+We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).
+\mw{The following is candidate for removal/shortening if we need to save space.}
 A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
@@
 \label{sect:mn_analysis}
-\cs{Here goes what has not been discussed in LREC paper, because it focusses on entry-level names. }
-\cs{Results aimed to show that we need \underline{multiple} annotations per object \underline{instance} to get the entry-level name}
 
-\paragraph{Definition of \textit{Entry-level Name}} \sz{has this been mentioned before?}
-\mw{I'd definitely put this in the introduction, and leave only a reminder here.}
-\cs{Remove me at the end, to make sure definition is in intro.}
-As we explained in Section~\ref{sec:intro}, we define \textit{entry-level name} for an object as the name that 
-%In the following, we consider a name annotated for an object as an entry-level name if it 
-corresponds to the most frequent name given a set of name annotations for the object.
-\mw{We could also consider defining entry-level name as `the most frequent adequate name'?
-Or perhaps as `the most frequent name \emph{if it is adequate}, none otherwise'?
-Depending on what makes the narrative easier.}
-
-\mw{Also make sure to define the notion of `entry-level object', or `canonical object' perhaps? i.e., the object/cluster of the entry-level name.}
-
+The verification we conducted is necessary for our main research aim -- to evaluate computational object naming models -- but they also enable a deeper understanding of the \mn data.
+Table~\ref{tab:stat-entry-level} provides a bird's eye overview.
 \begin{table}[t]
@@
 		\toprule		
-		\# objects in MN & 25,315\\
-		total vocab  &  7,970\\
-		entry-level vocab & 442\\
-		\# objects with entry-level name in VG & $\sim$ 2M (50\%)\\
+		objects in MN & 25,315\\
+		total vocabulary &  7,970\\
+		entry-level vocabulary & 442\\
+		objects in VG with name in entry-level vocab & $\sim$ 2M (50\%)\\
 		\midrule
@@
 	\end{tabular}
-	\caption{Basic statistics for entry-level names in MN. Av. agreement denotes the proportion of annotators that annotated a certain name for an object. }
+	\caption{Basic statistics for entry-level names in \mn.
+Av.agreement denotes the proportion of annotators (out of 36) that annotated a given name for an object, averaged over all names of a relevant subset.}
 	\label{tab:stat-entry-level}
 \end{table}
+\mw{Add more info to the table, e.g., 1. cluster size.
+2. For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering). (for Sect 4)
+. 3. Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. (for Sect 4)}
 
-\paragraph{Entry-level Names in ManyNames:} As shown in Table \ref{tab:stat-entry-level}, ManyNames provides a large vocabulary of names (7970) for 25K objects.
-Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on.
-The vocabulary of entry-level names is drastically smaller and contains only 442 types.
-This small set, however, covers at least 50\% of the objects in \vg, i.e.
-almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
+\cs{Make consistent with what is (was) in the intro wrt formulation:}
+Let us focus on our two main reasons for using \mn to evaluate computational models, i.e., a dataset where actual contextualized instances are named (not prototypes or classes), and where every instance is named by many annotators.
+Regarding the first, we can show that different instances of the same class can differ in entry-level name.
 
-\paragraph{Entry-level Names are Instance-Dependent:} 
-\cs{Make consistent with what is (was) in the intro wrt formulation:}
+\mw{Old stuff here, currently redoing but Carina was too impatient so I had to push:}
 In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name.
@@
 
-\iffalse
-\sz{does this solve this?
-Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)} \gbt{But, what's an object class in our data?
-We can't really use collection synsets, can we?
-Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''.
-Matthijs is on it.}
-\fi
-
-TODO: 
-\sz{somewhere we should mention these tendencies on adequacy and agreement for (non-)entry-level names shown in Table \ref{tab:stat-entry-level}}
-
-\paragraph{Identifying entry-level names requires many annotators}
-\iffalse
-ManyNames was collected in four rounds of 9 annotators each.
-On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
-Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
-\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading.
+%ManyNames was collected in four rounds of 9 annotators each.
+%On average, the entry-level name differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
+%Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
+%\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading.
 I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look.
 But I think the following is better:}
-\fi
+Regarding our second reason, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
 \begin{figure}[t]
-	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
+	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
 	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
@@
 \end{figure}
-For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability.
-% (a reasonable confidence requirement).
-The blue line shows that, even after gathering 10 names, the majority name is  likely to be the entry-level name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
+For each object we estimated, on the basis of its \mn response set, how many names should have been gathered for the entry-level name (as defined on the basis of 36 names) to be the majority name among them with 95\% probability.
+The blue line shows that, even after gathering 10 names, the entry-level name is sufficiently likely to be the majority name for only 68\% of objects (i.e.,~for 32\% of objects, there's a greater than 5\% chance of getting a different majority name).
 Gathering 20 names increases this to 78\%.
-The red line shows the same tendency but by taking only names from the cluster of the entry-level name into account (as identified by our hard clustering in \ref{sect:mn_verification}): 
-by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
-Both lines level out well below 100\%, reflecting that for 15\%-20\% \cs{If time permits, can you compute that individually for each domain, and mention what/if something stands out?} of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
-\cs{@mw: see discussion on slack wrt following comments - can you add what was agreed upon there?}
-\mw{@cs, @sz, @gbt: A closely related (but different) question this immediately brings to mind (of a critical reviewer?) is: how sure are we, for a given object, given the particular names we gathered, that the most frequent name in our sample (what we \emph{call} the entry-level name) is indeed the most frequent name in the population (what actually \emph{is} the entry-level name, right?)?
-Should we address this question earlier?
-I think the stats will look very similar (though they're not the same): that for 15-20\% of objects we really aren't sure.}
+Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
+the red line is computed by taking only names from the \cluster of the entry-level name into account:
+by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
+(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
+
+Note that both lines in Figure~\ref{fig:entry-level-name-stability} stay well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
+Turning this around: for around 15\%-20\% of objects, we aren't sure that the \emph{sample} entry-level name we derive from \mn -- what we simply called the entry-level name -- in fact corresponds to the \emph{population} entry-level name.
+In these cases gathering more annotations (i.e., more than 36) could help, but it is also possible that some instances do not have a single, clear entry-level name within a mixed population, or even for a given individual.
+Either way, this indeterminacy is not expected to affect our model comparison, hence we will continue to use all entry-level names, as defined in Section~\ref{sec:intro} as the majority name in \mn.
+
+\cs{If time permits, can you compute Figure~\ref{fig:entry-level-name-stability} individually for each domain, and mention what/if something stands out?} \mw{I did this for the `cat' column, see slack, but you probably meant something different by `domain'.
+Anyway, there are pretty big differences between domains yes...}
 
@@
 
-\paragraph{TODOS (if possible)}
-\begin{itemize}
-	\item For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering). (for Sect 4)
-	\item Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. ()for Sect 4)
-\end{itemize}
-
 %%% mode: latex

### 2019-12-09 papers/ACL2020/acl2020_main.tex
[ACL2020] more in experiments
adds supp-mat.tex file
restructures section 4 into 4 (modeling), 5 (analysis); redoes explanation of models
pass at the intro
[ACL2020] CS is done with Sect.3.3
[ACL2020] introduction.tex v3
add \cluster and \sameobject commands
abstract

--- 2019-12-06 papers/ACL2020/acl2020_main.tex
@@
 \newcommand{\vg}{VisualGenome\xspace}
+\newcommand{\ra}{$\rightarrow$}
+\newcommand{\sameobject}{SameObject\xspace}
+\newcommand{\cluster}{Cluster\xspace}
 
@@
 
-\title{How to Name a Real-World Object, and how not}
+% Terms that need to be replaced throughout the paper by more appropriate ones:
+\newcommand{\arbitrary}{arbitrary$\rightarrow$?\xspace}
+\newcommand{\categories}{classes\xspace}
+\newcommand{\category}{class\xspace}
+
+\title{From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects}
 
@@
 \begin{abstract}
-
+Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
+Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object, i.e.,~the name most humans would choose.  
+Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
+We show that object classification models ``spontaneously'' learn good entry-level names and that they can be further finetuned via transfer learning. 
+\sz{A short sentence on human-like errors?}
 \end{abstract}
@@
 \label{sec:manynames}
+\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
 \input{manynames}
 
-\section{Experiments}
+\section{Predicting Entry-Level Names}
 \label{sec:experiments}
 \input{experiments}
+
+\section{Analysis of Model Naming Behavior}
+\label{sec:analysis}
+\input{analysis}
 
@@
 %
-%\section{Appendices}
-%\label{sec:appendix}
-%Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-%Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-%Upon acceptance, the appendices come after the references, as shown here.
-%
-%\paragraph{\LaTeX-specific details:}
-%Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
-%
-%
-%\section{Supplemental Material}
-%\label{sec:supplemental}
-%Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-%Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
+% \section{Appendices}\newcommand{sameobject}
+% \label{sec:appendix}
+% \iffalse
+% Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
+% Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
+% Upon acceptance, the appendices come after the references, as shown here.
+
+% \paragraph{\LaTeX-specific details:}
+% Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
+% \fi
+
+% \section{Supplemental Material}
+% \label{sec:supplemental}
+% \iffalse
+% Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
+% Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
+% \fi
 

### 2019-12-09 papers/ACL2020/acl2020_main.tex
update Table 4 in Sec 5

@@
 Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
-Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object, i.e.,~the name most humans would choose.  
+Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose.  
 Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.

### 2019-12-09 papers/ACL2020/analysis.tex
update Table 4 in Sec 5

@@
 &  & \multicolumn{3}{c|}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$0.9}\\
-                         model &  gt &  hit &  valid &  incorrect &  hit &  valid &  incorrect \\
+                         model &  GT &  hit &  human-like &  off &  hit &  human-like &  off \\
 \midrule
-       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &      0.8 &      4.4 &   63.6 &     21.0 &     15.5 \\
-        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &      0.8 &      9.6 &   60.7 &     20.8 &     18.5 \\
+       FRCNN$_{\text{VG1600}}$ &  VG &   94.8 &           2.6 &      2.6 &   63.6 &          30.9 &      5.5 \\
+        FRCNN$_{\text{MN442}}$ &  VG &   89.6 &           4.2 &      6.2 &   60.7 &          31.3 &      8.0 \\
         \midrule
- FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &      0.0 &      5.5 &   72.9 &     14.0 &     13.1 \\
+ FRCNN$_{\text{VG1600--VGMN}}$ &  MN &   94.5 &           4.2 &      1.3 &   72.9 &          22.7 &      4.4 \\
  \midrule
-     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &      0.5 &     11.2 &   48.5 &     17.8 &     33.7 \\
-     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &      0.5 &      9.9 &   57.0 &     15.2 &     27.8 \\
-    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &      0.5 &      9.4 &   58.2 &     15.2 &     26.7 \\
-    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &      0.8 &     10.6 &   49.9 &     18.1 &     32.1 \\
+     ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
+     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
+    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
+    ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
 \bottomrule
 \end{tabular}
-\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} \label{tab:exp_errors_agreement}}
+\caption{Break-down of the results (in \%) according to the agreement level of the MN name: Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit}, \textit{human-like} error (less preferred name, synonym, hypernym/hyponym), or \textit{off} \label{tab:exp_errors_agreement}}
 \end{table*}

### 2019-12-09 papers/ACL2020/manynames.tex
changes in sec 3.1

@@
-\cs{In the remainder of this paper, we will use object and object instance interchangeably.}
+In this Section, we discuss why ManyNames is an interesting resource for our purpose of studying entry-level naming and why we needed to extend it with more thoroughly verified annotations. 
+In the remainder of this paper, we will use object and object instance interchangeably.
+
 \subsection{Overview of ManyNames}
@@
 
-brief summary of lrec paper, shortcoming, what we added
+ManyNames\footnote{The dataset will be made available upon publication.} builds upon object annotations in \vg and provides up to 36 name annotations in parallel for 25K objects, see e.g.\ Figure \ref{fig:duck}.
+Given the substantial amount of annotation tokens per object, we are able to (i) identify entry-level names as the most frequent name given to each object, and (ii) compute agreement for each name, as the proportion of annotators that opted for a given name.
 
-\begin{itemize}
-	\item For each object: a response set comprising all entered names (spellchecked) and their respective counts, i.e., the number of annotators which enter the respective name.
-	\item Problems \mw{I already had a go writing a 'bridge' paragraph containing this; see below.}: referential uncertainty: object other than target object was  identified as named
-	\item \cs{Mention how agreement on \mn is computed (anticipating that we'll be taking a closer look at this in 3.3 when the verification is in place).}
-\end{itemize}
-
-\mw{Sina wrote this in 3.3; I think it should go here in 3.1., in order for 3.3 to more clearly show the added value of verification:}
 ManyNames provides a large vocabulary of names (7970) for 25K objects.
 Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on. 
-The vocabulary of entry-level names -- defined for each object as the most frequent name given -- is drastically smaller and contains only 442 types. 
-This small set, however, covers at least 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
+Interestingly, the vocabulary of entry-level names is drastically smaller and contains only 442 types. 
+This small set covers at least 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
 
-Manual inspection of the \mn data revealed that annotators occasionally named an object different from the one highlighted by the bounding box (e.g., the name \emph{helmet} when the bounding box highlights an entire motorcyclist), or the right object but with an incorrect name (e.g., ``horse'' for a cow), and sometimes the bounding box may have been unclear.
-Although these errors are interesting human data in their own right, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology used for \mn, where there is a financial incentive to complete the task as quickly as possible.
+Manual inspection of the \mn data, however, revealed a range of annotation problems: annotators occasionally named an object different from the one highlighted by the bounding box (e.g., the name \emph{helmet} when the bounding box highlights an entire motorcyclist), or the right object but with an incorrect name (e.g., ``horse'' for a cow), and sometimes the bounding box may have been unclear.
+See Figure \ref{fig:rug} for examples.
+Although these errors are interesting human data in their own right, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
+%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
 As such they pose a challenge for our research goal, which is to see whether the object-naming ability of computational models resembles those of actual language users.

### 2019-12-09 papers/ACL2020/manynames.tex
Redo paragraph in 3.3 about entry-names being instance-based, with more convincing stats, to emphasize that it's nice to have verified data.

--- 2019-12-09 papers/ACL2020/manynames.tex
@@
 
-\cs{Make consistent with what is (was) in the intro wrt formulation:}
-Let us focus on our two main reasons for using \mn to evaluate computational models, i.e., a dataset where actual contextualized instances are named (not prototypes or classes), and where every instance is named by many annotators.
-Regarding the first, we can show that different instances of the same class can differ in entry-level name.
+Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
+\cs{Make formulation consistent with what is (was) in the intro:}
+Regarding feature (i), recall that the traditional, taxonomic view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
+Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
+To quantify this point, let us concentrate on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a very strict requirement which only 281 of the 422 entry-level names of \mn meet.
+These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (SD: .34).
+Now, some of this is due to errors of the type we have sought to identify, but the verified results support the same conclusion: 
+even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, but skewed with about half over 80\%).
 
-\mw{Old stuff here, currently redoing but Carina was too impatient so I had to push:}
-In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name.
-The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names).
-Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
+%provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names).
 We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g.
@@
 But I think the following is better:}
-Regarding our second reason, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
+Regarding our second reason, feature (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
 \begin{figure}[t]

### 2019-12-09 analysis/analysis_verification_matthijs.py
more ugly quick stats code, now for quantifying instance-based entry names

@@ -29,11 +29,88 @@ CANONICAL_THRESHOLD = .5   # weight of canonical cluster should be at least ...
 NUM_SAMPLES_FOR_STABILITY = 30
 SUBSAMPLE = False       # for debugging
 
+VERIFIED = False
+
 def basic_stats():
 
     csvfile = '../proc_data_phase0/verification/all_responses_round0-3_verified.csv'
     df = load_results.load_cleaned_results(csvfile)
 
+    df['entry_name'] = df['spellchecked_min2'].apply(lambda x: x.most_common(1)[0][0])
+    for i, row in df.iterrows():
+        df.at[i,'entry_name_verified'] = row['entry_name'] if row['verified'][row['entry_name']]['adequacy'] > ADEQUACY_THRESHOLD else np.nan
+
+    if VERIFIED:   # restrict to verified cases
+        df = df.loc[~(df['entry_name_verified'].isna())]
+        df['entry_name'] = df['entry_name_verified']
+
+    all_entry_names_statuses = {n: [] for n in df['entry_name'].unique()}
+
+    same_cluster = []
+
+    count_pairs = 0
+    for i, row in df.iterrows():
+        n0 = row['entry_name']
+        # if clear winner:
+        most_common = row['spellchecked_min2'].most_common()
+        if len(most_common) == 1 or .5*most_common[0][1] > most_common[1][1]:
+            all_entry_names_statuses[n0].append(True)
+            for n1 in row['spellchecked_min2']:
+                if VERIFIED:
+                    if n1 in all_entry_names_statuses and n1 != n0 and row['verified'][n1]['adequacy'] > ADEQUACY_THRESHOLD and row['verified'][n0]['cluster'] == row['verified'][n1]['cluster']:
+                        count_pairs += 1
+                        all_entry_names_statuses[n1].append(False)
+                        same_cluster.append(True)
+                    elif n1 in all_entry_names_statuses and n1 != n0 and row['verified'][n1]['adequacy'] > ADEQUACY_THRESHOLD:
+                        same_cluster.append(False)
+
+                else:
+                    if n1 in all_entry_names_statuses and n1 != n0 and .5*row['spellchecked_min2'][n0] > row['spellchecked_min2'][n1]:
+                        count_pairs += 1
+                        all_entry_names_statuses[n1].append(False)
+
+    all_entry_names_proportions = {}
+    for n in all_entry_names_statuses:
[…]

### 2019-12-09 papers/ACL2020/analysis.tex
changes in sec 3.1
[ACL2020] analysis

--- 2019-12-09 papers/ACL2020/analysis.tex
@@
 
+\iffalse
 \begin{table*}[t]
@@
 \end{table*}
+\fi
 
@@
 	ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
-
 	\bottomrule
 \end{tabular}
+\caption{Model results for different categories of errors. \label{tab:humanlike}}
 \end{table*}
+
+\begin{table*}[t]
+	\centering
+	\small
+\begin{tabular}{ll|c@{~}c@{~}c@{~}c}
+	\toprule
+	{Model} &  GT & visual &  linguistic &  box &  other \\
+	\midrule
+	FRCNN--VG1600 & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
+	FRCNN--MN442 & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
+	\midrule
+	FRCNN--VG1600--VGMN & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
+	\midrule
+	ResNet101--VGMN & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
+	ResNet101--MN442 & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
+	ResNet101--VGMN & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
+	ResNet101--MN442 & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
+	\bottomrule
+\end{tabular}
+\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
+\end{table*}
+
+\paragraph{Why May Models Predict Inadequate Names?}
+In Table~\ref{tab:exp_inadequacy} we focus on the predicted names that are in \mn for the corresponding objects, but judged as inadequate (i.e.,~adequacy score$<0.5$). 
+Most of the inadequate object name predictions are related to an inaccurate bounding box. 
+The overall best FRCNN$_{\text{VG1600--VGMN}}$ model has the smallest proportion of box errors, and hence, the least \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
+\cs{remove next couple of sentences? it's very assumptive}
+This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
+And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
+
+None of the models predicted an inadequate name that was a linguistic, or any other error. 
+The results show that the models make similar mistakes to humans (problems in identifying or recognizing the target object) when being faced with data that was collected with a task setup that approximates human behavior, such as \mn.
+It HERAUSLOCKEN also, though, the limitations of using annotated datasets such as \mn as approximation for human behavior on object naming )or related tasks), and the importance in defining and implementing annotation tasks for data collection.
 

### 2019-12-09 papers/ACL2020/analysis.tex

@@
 	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
+	\label{fig:rug}
 \end{figure}

### 2019-12-09 papers/ACL2020/analysis.tex

@@
-The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
-This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.\cs{XX}
-In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behavior.
-
-\paragraph{Error Categories} We categorize model predictions into the following types (also see Figure~\ref{fig:mistakes} for examples):
-
-\begin{itemize}
-\item Correct-hit: the entry-level name 
-\item Correct-valid: a name from the set of valid alternatives, a synonym or a hypernym (\name{house/building}) \cs{set of alternatives:: task1: all, task2: only adequacy$>$0.5}
-\item Incorrect-human-like: a name produced by annotators, but not a valid alternative of the entry-level name  (\name{chair/cat}) \cs{task1: other object; low count; task2: alternatives adequ $<$ 0.5 (other object, low count)}
-\item Incorrect-related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
-\item Incorrect-off: a non-sensical name (none of the above)
-\end{itemize}
-\cs{WordNet}
-
-\subsection{How Human-Like are Model Predictions and Errors?}
-
-Table \ref{tab:humanlike} shows the breakdown of the model results for the error categories explained above.
-An important general trend is that the proportion of human-like error seems to be surprisingly constant across all models.
-\sz{why??}
-Both object detection models essentially achieve the same portion of valid predictions.
-Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column off), which might be an effect of the reduction in training data.
-Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
-This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
-The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse semantically similar names to a valid name, that are, however, not valid.
-
-\iffalse
-\begin{table*}[t]
+\begin{figure}
 	\centering
-	\small
-\begin{tabular}{ll||rr|rrr}
-\toprule
-&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
-                         model &  gt &  hit &  valid &  human-like &  related &  off \\
+	\footnotesize
+	\begin{tabular}{p{3.7cm}p{3.7cm}}
+		\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
+		\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
+		\\
+		Entry-level: rug (21) &  animal (9)\\
 		\midrule
-       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
-        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
+		Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
+		Error-box: chair (5, 0.5), floor (3, 0.5) & \\
+		Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
 		\midrule
- FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
-         \midrule
-     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
-         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
-     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
-    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
-\bottomrule
+		FRCNN$_{\text{VG1600}}$: floor & animal\\
+		FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
 	\end{tabular}
-
-\caption{Model results for different categories of errors} \label{tab:humanlike}
-\end{table*}
-\fi
+	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
+	\label{fig:mistakes}
+\end{figure}
 
@@
 
+The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
+This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.\cs{XX}
+In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behavior.
+
+\paragraph{Error Categories} We categorize model predictions into the following types (also see Figure~\ref{fig:mistakes} for examples):\\
+Hit: the entry-level name\\
+Off: a non-sensical name (none of the others). \\
+Human-like mishits:
+\begin{itemize}
+\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
+\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name  
+\item LowCount: a name produced by only one annotator
+\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+\item Incorrect-off: a non-sensical name (none of the above)
+\end{itemize}
+We use WordNet for determining whether two names are semantically related   \newcite{fellbaum1998wordnet}.
+
+\subsection{How Human-Like are Model Predictions and Errors?}
+
+Table \ref{tab:humanlike} shows the breakdown of the model results for the error categories explained above.
+An important general trend is that the proportion of human-like error seems to be surprisingly constant across all models.
+\sz{why??}
+Both object detection models essentially achieve the same portion of valid predictions.
+Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column off), which might be an effect of the reduction in training data.
+Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
+This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
+The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse semantically similar names to a valid name, that are, however, not valid.
+
+\iffalse
+\begin{table*}[t]
+\centering
+	\small
+\begin{tabular}{ll||rr|rrr}
+\toprule
+&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
+                         model &  gt &  hit &  valid &  human-like &  related &  off \\
+\midrule
+       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
+        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
+        \midrule
+ FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
+         \midrule
+     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
+         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
+     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
+    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
+\bottomrule
+\end{tabular}
+
+\caption{Model results for different categories of errors} \label{tab:humanlike}
+\end{table*}
+\fi
+
 \paragraph{Why May Models Predict Inadequate Names?}
@@
 The overall best FRCNN$_{\text{VG1600--VGMN}}$ model has the smallest proportion of box errors, and hence, the least \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
+\iffalse
 \cs{remove next couple of sentences? it's very assumptive}
@@
 And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
+\fi
 
 None of the models predicted an inadequate name that was a linguistic, or any other error. 
-The results show that the models make similar mistakes to humans (problems in identifying or recognizing the target object) when being faced with data that was collected with a task setup that approximates human behavior, such as \mn.
-It HERAUSLOCKEN also, though, the limitations of using annotated datasets such as \mn as approximation for human behavior on object naming )or related tasks), and the importance in defining and implementing annotation tasks for data collection.
+The results show that the models make similar mistakes to humans (problems in identifying or recognizing the target object) when being faced with data that was collected with a task setup that approximates human behavior, such as \mn, and the limitations in defining and implementing annotation tasks for data collection of this sort.
 
@@
 
+\iffalse
 \begin{figure}
@@
 \end{figure}
-
-\begin{figure}
-	\centering
-	\footnotesize
-	\begin{tabular}{p{3.7cm}p{3.7cm}}
-	\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
-	\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
-	\\
-	Entry-level: rug (21) &  animal (9)\\
-	\midrule
-	Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
-	Error-box: chair (5, 0.5), floor (3, 0.5) & \\
-	Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
-	\midrule
-	FRCNN$_{\text{VG1600}}$: floor & animal\\
-	FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
-	\end{tabular}
-	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
-	\label{fig:rug}
-\end{figure}
+\fi
 

### 2019-12-09 papers/ACL2020/experiments.tex

@@
 
-We test 1) an existing object detection and classification model trained on \vg (FRCNN$_{\text{VG1600}}$); 2) the same model, re-trained on the smaller vocabulary of entry-level names, MN442 (FRCNN$_{\text{MN442}}$); 3) an object classification model trained on FRCNN$_{\text{VG1600}}$ features, that is, a version of FRCNN$_{\text{VG1600}}$ fine-tuned on \mn data (FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ \gbt{find better name?}); 4) object classification models trained directly on object detection features (given by ResNet 101; \cite{}), rather than object classification features.
+We test two object detection models trained on objects and names from the original \vg data, using the Faster R-CNN architecture \cite{fasterrcnn2015} which is initialized with features that were pre-trained on $1$K~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
+We use and retrain these two models with different target vocabularies:
 
-FRCNN$_{\text{VG1600}}$ is the bottom-up attention model of \citeauthor{anderson2018updown}'s \citeyear{anderson2018updown},\footnote{Available at \url{https://github.com/peteanderson80/bottom-up-attention}.
-The model is trained with an additional output over attributes, but we only use the object class prediction layer.}
-trained to do object classification with a vocabulary of $1600$ VG names as class labels. \cs{add how the vocabulary was derived}.
-The model is based on the object detection \gbt{detection, or classification?} method Faster R-CNN \cite{fasterrcnn2015}. 
-The authors initialized it with ResNet-101 \cite{he2016deep} features (pretrained on ImageNet) to then train it on \vg.
-To train FRCNN$_{\text{MN442}}$, we follow the same methodology as in \citeauthor{anderson2018updown} \cs{right, @Sina?} but restrict the object classes to the $442$~entry-level names found in \mn; accordingly, we train on fewer images.
-\gbt{Right?
-Only those that have an entry-level name?
-TODO: add how many imgs for FRCNN$_{\text{VG1600}}$ and FRCNN$_{\text{MN442}}$.}
-\gbt{Also, Do we also use the additional attribute loss?}
-\footnote{For training, we use a PyTorch reimplementation of Faster R-CNN, \url{github.com/jwyang/faster-rcnn.pytorch}.}
-FRCNN$_{\text{MN442}}$ serves us to test the hypothesis that training only on entry-level names may improve generalization and hence performance.
+\begin{small}
+\begin{itemize}
+\item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set 1600 object names in \vg.
+This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
+ \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
+\end{itemize}
+\end{small}
 
@@
 \mn is too small to train object detection models on it from scratch, which require learning millions of parameters.
-On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly --probably unrealistic.
+On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly and probably unrealistic.
 Therefore, we investigate the possibility of obtaining entry-level data via transfer learning, fine-tuning existing models with \mn data.
-We do so with the standard methodology \gbt{in L\&V?} of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).
+We do so with the standard methodology of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).
 
-We experiment with two kinds of input.
-First, the features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}.
+We experiment with two kinds of (transferred) input features, different training vocabularies and ground-truth names for instances, similar to the detection models above.
+This yields the following 5 transfer-learning-based naming models:
+
+\begin{small}
+\begin{itemize}
+\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}.
 We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).
-For comparison, we consider a much less informed kind of input, namely the features from an object detection model, ResNet-101 \cite{+++}, which are the ones that FRCNN$_{\text{VG1600}}$ use as initialization features.
-\gbt{Previous sentence to be improved}
+For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
+\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
 Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
+The model uses the VGMN vocabulary.
+The model is optimized on VG and MN ground truth names respectively.
+ \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
+\end{itemize}
+\end{small}
 
-\cs{Next sentence relevant here?
-Or just as detail in related work?:: (Note that ResNet's $1$K~object classes capture subordinate categories of ImageNet leaf nodes; e.g.,~Siberian husky, American black bear.)}
-
-\gbt{BEGIN not integrated in the text yet}
-As with the FRCNN models above, we compare models which differ in  their target vocabulary, i.e.,~VGMN or MN442. 
-\cs{Maybe the next sentences are better just in the results section, when discussing the table::} Finally, we compare against two further classifiers which are trained on the \vg labels. 
-Note that all four models are optimized on the $25$K~objects in \mn. 
-\gbt{END not integrated}
-
-\gbt{IMPORTANT: I would not include all four ResNet models in the main paper; it takes a lot of space in all the result tables and doesn't add much information.
-I'd put the most relevant (at most two, maybe even only one) in the main paper and leave the rest for the supplementary material.
-TBD}
-
-\cs{todo: details to architecture and training of the vanilla classifiers.}
-\gbt{I leave this here unchanged:} For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} 
+Note that all five models are optimized on the $25$K~objects in \mn. 
 To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
-The target vocabulary (VGMN, henceforth) comprises the overlap of VG1600 and the \mn names (\cs{$XX$} in total). \gbt{All \mn names? or only MN422? To be clarified above under paragraph `Data'.}
 

### 2019-12-09 papers/ACL2020/related.tex

@@
 %- Our work: empirical notion of entry-level
-\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
+%\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
 In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
@@
 Our present work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
- \sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}
+ %\sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}
 
@@
 
-\paragraph{Visual Object Recognition in Computer Vision}
-- Object detection, using pre-trained feature representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
-- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image).
+\paragraph{Visual Object Recognition} is a major focus of research in Computer Vision, with object classification being a core task in this area. 
+Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}).
+These neural object classifiers have proven extremely useful in a large range of transfer learning scenarios.
+They are commonly used as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
+For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
+We will use a pretrained ResNet, Faster-RCNN and Bottom-up as models in our work too, extending and testing them for entry-level object naming.
+
+%Current recognition benchmarks use labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically implement a single ground-truth label approach.
+%- Object detection, using pre-trained feature representations (see next point) (localize object and predict its \textit{label}; trained with, e.g.\ more coarse-grained ImageNet labels or VG names)\\
+%- Pre-trained feature representations, trained on image classification with 1000 ImageNet fine-grained labels (predict \textit{label} for most salient object in image).
 It predicts the class of the most salient object in an image.
 \\
-- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?
+%- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?

### 2019-12-09 papers/ACL2020/experiments.tex
[ACL2020] experiments results description

@@
 
+\iffalse
 \begin{table}[t]
@@
 \end{table}
+\fi
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc@{~}}
+		\toprule
+		&  & \multicolumn{2}{c}{GTtest} \\
+		Model$_{\text{Vocab}}$ &  GTtrain &  VG & MN  \\ 
+		\midrule
+		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
+		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
+		\midrule \midrule
+		\multicolumn{4}{c}{Classifiers: Transfer learning on MN}\\
+		Features$_{\text{Vocab}}$ &   \\
+		\midrule 
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
+		\midrule
+		ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\
+
+		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6  \\
+		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9  \\
+		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
+		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7   \\
+		\bottomrule
+	\end{tabular}
+	\caption{Model accuracy (in \%) on the \mn test objects.
+Vocab denotes the dataset used to induce the target vocabulary for training (the numbers are vocabulary size).
+GTtrain gives the dataset providing the ground truth labels for training, and GTtest for testing \label{tab:exp_VGvsMN}.}
+\end{table}
 
@@
 \label{sect:exp_results}
-
 \gbt{To do: streamline to make consistent with motivations + expectations laid out in the previous subsection.}
@@
 Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
-We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the \arbitrary VG name (columns VG), and furthermore report results on the test instances where the two names differ (block VG$\neq$MN) \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}.
+We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the VG name (columns VG). 
+%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.
+
+% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
+%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
+%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
+% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
+\cs{Left as items for the sake of a better overview for now}
 \begin{itemize}
-	\item The FRCNN models \gbt{all models, actually} are better on predicting the entry-level name (columns MN) than the \arbitrary VG name (columns VG). 
-	This shows that they do learn entry-level naming to some extent, despite being trained on VG, i.e.,~\arbitrary ground truth labels.
-	\cs{I would not comment on diff.
-btw.
-the two FRCNNs, it's small compared to their diffs to the classifiers, and may be also due to the diff.
-implementations, and VG1600 being trained additionally on attributes.}
+	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the VG name (columns VG), despite being trained on VG.  
+	Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
+	The results therefore indicate that the FRCNN models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
 	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
-	\item \cs{?What to keep here:} The classifiers using ResNet features are the least effective, but come close to the FRCNN object detectors on entry-level naming (columns MN, GTtrain MN), or even better  (columns VG, GTtrain VG) despite being trained on a fraction of FRCNN's training size using a simple Vanilla classifier in contrast to a fully-fledged CNN architecture.
-	This confirms what we observed on the FRCNN results: and follow the pattern of learning entry-level naming  
-	\item Models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than \arbitrary name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
-\cs{overfitting?}
+	\item The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
+	This confirms what we observed on the FRCNN results. 
+	\item In sum, we find that models learn entry-level naming when being trained on ``\arbitrary'' naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
 	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.

### 2019-12-09 papers/ACL2020/acl2020_main.tex
[ACL2020] note in main on what to add
changes in abstract

@@
 Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
-Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose.  
-Based on large-scale, thouroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
-We show that object classification models ``spontaneously'' learn good entry-level names and that they can be further finetuned via transfer learning. 
-\sz{A short sentence on human-like errors?}
+Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by a single annotator.
+Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
+We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
+on predicting entry-level than \arbitrary names, despite being trained on  \arbitrary names.
+We further fine-tune these models via transfer learning and systematically vary their training vocabulary.
+\sz{something ...}
 \end{abstract}
@@
 \label{sec:manynames}
-\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
+%\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
 \input{manynames}

### 2019-12-09 papers/ACL2020/experiments.tex

@@
 \paragraph{Data}
-\gbt{I moved this here cause I think it will be useful to define the different vocabularies here and then be able to simply refer to them later.
-Btw, consider using `MN-Entry' instead of `MN442'?
-but maybe having the number in the name is useful to be able to compare.}
-\cs{todo after Section~\ref{sect:mn_overview} has been written.}
-\begin{itemize}
-	\item Test data: overlap of \mn and \vg test data (CITE)
-	\item Target vocabulary of test data: overlap of MN442 and VG (\cs{XX} names)
-	\item Source of label: \mn, but we compare against \vg
-\end{itemize}
+We split \mn into training ($21K$~objects) and test data ($1,072$). 
+The test data corresponds to the overlap of \mn (MN) and the VG (VG) test split used by  \newcite{anderson2018updown}. 
+The target vocabulary of the test data is MN442. %the overlap of MN442 and VG ($355$ names). 
+For training using transfer learning, we train on the ground truth labels provided by \mn, but compare to training on \vg labels.
 

### 2019-12-09 papers/ACL2020/experiments.tex
smoothed sec4, including discussion

@@
 
-\cs{todo: discuss differences between domains}
-\gbt{Not sure we'll have space :) }
-
-\gbt{Note: I've rewritten this intro, the previous version with the plan of what is to be covered is commented out in the tex file}
-
-We use \mn to gain insight into the extent to which current models account for object naming.
-We do so in three ways: By analyzing the behavior of existing models on entry-level names, by assessing the consequences of fine-tuning models with entry-level name data, and by analyzing the predictions of the models, comparing them to human naming behavior as attested in \mn.
-The latter will be done in Section~\ref{sec:analysis}; here we focus on modeling experiments.
-\gbt{Maybe this needs to go in the intro or somewhere else. It's important to stress that the modeling experiments are on entry-level only, and the analysis takes into account the other names.}
-
-The modeling experiments adopt the standard single-label object classification approach of Computer Vision, and we will compare prediction of the original \vg name with the entry-level name.
-We leave modeling experiments that take into account other possible names of objects for future work.
+Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
+Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
+The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
+Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
+% found in the verification data in Section \ref{sec:verification}.
+%We leave modeling experiments that take into account other possible names of objects for future work.
 
@@
 
-\begin{small}
 \begin{itemize}
@@
 \end{itemize}
-\end{small}
 
@@
 \label{sect:exp_results}
-\gbt{To do: streamline to make consistent with motivations + expectations laid out in the previous subsection.}
 
@@
 % \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
-\cs{Left as items for the sake of a better overview for now}
-\begin{itemize}
-	\item The FRCNN models are better on predicting the entry-level name (columns MN) than the VG name (columns VG), despite being trained on VG.  
+%\cs{Left as items for the sake of a better overview for now}
+
+A pervasive trend in these results is that all models perform better 
+at predicting the entry-level name (columns MN) than the VG name (columns VG), regardless of which vocab and which ground-truth they are trained on.  
 Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
-	The results therefore indicate that the FRCNN models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
-	\item The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
-	\item The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
+The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
+
+ The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
+The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
 This confirms what we observed on the FRCNN results.
-	\item In sum, we find that models learn entry-level naming when being trained on ``\arbitrary'' naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
-	\item Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
-\end{itemize}
+In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
+Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
 
@@
 
-%\iffalse
+To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
+As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon, which involves a lot of variation when names are freely annotated, but also a lot of agreement.
+Hence, it is a striking result that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
+However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
+The next Section elaborates on this point and proposes a more fair assessment of naming quality achieved by the different models.
+
+\iffalse
 \cs{under construction}
@@
 \end{itemize}
-%\fi
+\fi
 

### 2019-12-09 papers/ACL2020/introduction.tex
increase coherence of sections 1-2-3; shortening still required

--- 2019-12-08 papers/ACL2020/introduction.tex
@@
-\cs{need to make clear the diff btw objects meaning the concept/class and meaning an instance}
-\cs{need to discuss problematic of standard evaluation procedure of CV models}
+Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
+The task of \emph{object naming} -- generating not just a formally correct but also an appropriate, \emph{natural} name for an object -- is distinct from the closely related tasks of object detection and image classification (see below).
+It has been studied in psycholinguistics~\cite{refs} \mw{Refs!}, but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
+We address the following question:\\
+\fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
+In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
+We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
+A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
+
+In \lv, the choice of a particular name for an object is a ubiquitous problem -- it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
+\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
+The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+Pre-training on such labels has its justification in that computer vision models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
+slightly pointed).
+But it raises the issue of whether these models could be used for more human-like object naming.
+% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.
+
+% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
+Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
+However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
+Humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+For example, in Figure~\ref{fig:duck}, for the two instances of a duck (from \vg, with names from \mn), most people (27 out of 36) called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance.
+\begin{figure}[t]
+	\centering
+	\small
+	\begin{tabular}{p{3cm}p{3cm}}
+		\centering
+		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
+		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
+		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
+	\end{tabular}
+	\caption{Different naming preferences for different instances of the same \category \name{duck} in \mn.\label{fig:duck}}
+\end{figure}
+Hence, both the single-ground-truth view of CV models and the category-level approach predominant in Psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
+The \mn dataset was designed to help mend this gap: it consists of names entered by 36 annotators in parallel, for 25K objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
+However, the name annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.
+
+Our main contributions in this paper are (i) to run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models for their ability at the task of \emph{instance-based, entry-level object naming}.
+More precisely, \mn enables us to define the entry-level as follows:\\
+\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to \mn}}\\\\
+We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understnad the kinds of mistakes each model makes (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
+We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
+\mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}
+
+%% END OF FILE %%
+
+%Our contributions towards the task of instance-based entry-level naming in \lv and CL research are two-fold:  
+%First, we provide data on object naming with real images on a large scale. 
+%We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
+%We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{krishna2016visualgenome}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+%
+%Second, we introduce the verified \mn dataset as evaluation data, and provide an extensive analysis of the ability of object detection and classification models to account for entry-level object naming in our dataset.
+
+\iffalse
+%However, when they speak, humans in general name specific \textit{instances} of objects---actually, instances in particular situations and points of view, which may humans have prefer different names for instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+
+%Accordingly, datasets used for object naming in Psycholinguistics use idealized drawings that correspond more to categories than to instances~\cite{+++++}.
+%
+%
+
+Despite its relevance in \lv and CL, the challenge of instance-based natural naming has been overseen. 
+\lv research that particularly focuses on the prediction of entry-level names is scarce, and existing work has adopted the \category-based concept of entry-level names \cite{Ordonez:2016}. 
+Furthermore, existing datasets lack necessary information to make progress in \lv and CL research on this phenomenon. 
+\cs{TODO@CS: EVALUATION ISSUE GOES HERE.}
+\begin{itemize}
+	\item resources developed in CV and \lv can be useful to study object naming. 
+	\item However, they provide only one (or a few) name per object \ra no guarantee that it is the entry-level name.
+(We provide more, to have a robust estimate of entry-level names (as well as data on other possible names).
+\gbt{actually, maybe move this to the previous part?
+\ra differences with Psycholing, with CV resources})
+	\item object naming has often been conflated with object classification in CV. \gbt{Discuss differences; mention the swan - whatever name it has in wordnet example of ordonez et al?}
+	\item a big problem with this approach is that it follows a single-label evaluation.
+With our data, we show that often model responses are adequate even if they do not correspond to the entry-level name.
+	\item we also show that object classification models ``spontaneously'' learn to provide entry-level names for objects
+	\item and that it is possible to use \mn to successfully fine-tune existing object detection and classification models to predict entry-level names for objects.
+\end{itemize}
+
+This paper seeks to spur \lv and CL research on the problem of \textit{instance-based entry-level object naming}.
+
+Our contributions are two-fold:  
+First, we provide data on object naming with real images on a large scale. 
+We take on an empirical notion of entry-level names, and define it on the instance-level, i.e., the name that humans prefer to use when calling a particular object in a real-world image.   
+We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+
+\cs{I'll continue from here.}
+Second, we introduce the verified \mn dataset as evaluation data that allows XXX.
+We provide an extensive analysis of the ability of object detection and classification models on the task of predicting the entry-level names in our dataset.
 
@@
 We extend \mn (under submission), a dataset that provides 36 names for each of 25K objects from \vg~\cite{+++}, with information on adequacy and reference of all collected names, which affords rich analysis possibilities.
+Our data contain object instances, corresponding more closely to the kind of visual objects that humans typically encounter, and so can potentially shed light on the instance-level factors that affect naming.
+
 Second, we provide an extensive analysis of the performance of object classification models on the task of predicting the entry-level names in our dataset.
 
-\begin{figure}[htb]
-	\centering
-	\small
-	\begin{tabular}{p{3cm}p{3cm}}
-		\centering
-		\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
-		\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
-		bird\ (27),  duck\ (8) & duck (33), bird (3)\\
-	\end{tabular}
-
-	\caption{Different naming preferences for different instances of the same category \textsc{duck} in \mn.\label{fig:duck}}
-\end{figure}
 As for the former, note that Psycholinguistic research on entry-level names has focused on categories, as opposed to instances:

### 2019-12-09 papers/ACL2020/manynames.tex
increase coherence of sections 1-2-3; shortening still required

--- 2019-12-09 papers/ACL2020/manynames.tex
@@
-\cs{In the remainder of this paper, we will use object and object instance interchangeably.}
-\subsection{Overview of ManyNames}
-\label{sect:mn_overview}
-
-brief summary of lrec paper, shortcoming, what we added
-
-\begin{itemize}
-	\item For each object: a response set comprising all entered names (spellchecked) and their respective counts, i.e., the number of annotators which enter the respective name.
-	\item Problems \mw{I already had a go writing a 'bridge' paragraph containing this; see below.}: referential uncertainty: object other than target object was  identified as named
-	\item \cs{Mention how agreement on \mn is computed (anticipating that we'll be taking a closer look at this in 3.3 when the verification is in place).}
-\end{itemize}
-
-\mw{Sina wrote this in 3.3; I think it should go here in 3.1., in order for 3.3 to more clearly show the added value of verification:}
-ManyNames provides a large vocabulary of names (7970) for 25K objects.
-Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on. 
-The vocabulary of entry-level names -- defined for each object as the most frequent name given -- is drastically smaller and contains only 442 types. 
-This small set, however, covers at least 50\% of the objects in \vg, i.e. almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
-
-Manual inspection of the \mn data revealed that annotators occasionally named an object different from the one highlighted by the bounding box (e.g., the name \emph{helmet} when the bounding box highlights an entire motorcyclist), or the right object but with an incorrect name (e.g., ``horse'' for a cow), and sometimes the bounding box may have been unclear.
-Although these errors are interesting human data in their own right, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology used for \mn, where there is a financial incentive to complete the task as quickly as possible.
-As such they pose a challenge for our research goal, which is to see whether the object-naming ability of computational models resembles those of actual language users.
-
-\subsection{Collecting verification of ManyNames}
+\paragraph{Collection procedure}
 \label{sect:mn_verification}
 
-To overcome the aforementioned challenge we collected a new layer of verification annotations on top of \mn.
 We recruited annotators from Amazon Mechanical Turk\footnote{
@@
 
-\mw{I think the following is nice, but strictly redundant, so candidate for deletion if need be:}
-Summing up, we provide new verification of \mn, in the form of: name adequacy judgments, type of inadequacy (linguistic, bounding box, named object misinterpreted, other), and information about which names were likely intended for the same object.
+%\mw{I think the following is nice, but strictly redundant, so candidate for deletion if need be:}
+%Summing up, we provide new verification of \mn, in the form of: name adequacy judgments, type of inadequacy (linguistic, bounding box, named object misinterpreted, other), and information about which names were likely intended for the same object.
 In relation to our research goal, in section~\ref{sec:analysis} these results will allow us to quantify, for instance, whether the name generated by a given model, if it is not the entry-level name, is at least a name that could reasonably be for the same object as the entry-level name, and whether it is adequate.
@@
 Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
-Inter-annotator agreement is high also by other measures: the proportion of annotators agreeing on ``adequate'' is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
-We consider this level of agreement as high given the complexity of the task (e.g., pictures sometimes unclear), especially bearing in mind that we essentially asked our participants to do some kind of mind-reading (i.e., which object could someone who entered an inadequate name plausibly have had in mind?).
-Figure~\ref{fig:verification-piechart} shows the proportion of `adequate' judgments and the types of inadequacies our individual annotators reported (a), as well as the aggregated (mean/majority) judgments (b).
+The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
+This is high given the complexity of the task, essentially mind-reading what the original \mn annotators may have meant, plus the fact that pictures and bounding boxes are sometimes unclear.
+Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types (individual judgments and aggregated).
 \begin{figure}[t]
@@
 Second, for a better understanding of the verified \mn data itself (Section~\ref{sect:mn_analysis}) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering).
-%However, we are also interested in more general statistics, e.g., the mean number of names per object, and the relative frequencies of names for a given object.
-%For this, 
-% we need \cs{@MW please check if that's correct} \mw{No it isn't} to compute hard clusters
-We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).
-\mw{The following is candidate for removal/shortening if we need to save space.}
-A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
-It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
-But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships--- %(which could be gotten from, e.g., WordNet) -- 
-rather, we care about %(and asked our annotators) 
-which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top. 
-Moreover, although hard clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image, both of which would be more harmful to our aims.
+We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
+	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis).
+The alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters), would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.
+}
+
+%A possible disadvantage of this (hard) clustering method is that every name can only be in one cluster, i.e., name only one object.
+%It entails for instance that \emph{food} cannot be clustered both with \emph{pizza} and with the \emph{cheese} on top, even though both are definitely instances of food.
+%But this is not as problematic as it may seem, because we do not care primarily about such taxonomic relationships--- %(which could be gotten from, e.g., WordNet) -- 
+%rather, we care about which single object a person who entered \emph{food} was likely intending to name: presumably the pizza as a whole rather than the cheese on top. 
+%Moreover, although hard clustering may occasionally lead us to \emph{under}estimate the number of names for an object, the alternative, \emph{soft} clustering (where each name could potentially be in multiple clusters) would risk \emph{over}estimating the number of names per object, as well as the number of named objects in an image.
 
@@
 
-\subsection{Analysis}
+\paragraph{Analysis}
 \label{sect:mn_analysis}
@@
 \end{table}
-\mw{Add more info to the table, e.g., 1. cluster size.
-2. For the instances where VG!=topMN: Percentage of instances where the VG name is among the responses of an \textit{alternative object} (as given by clustering). (for Sect 4)
-. 3. Comparison of VG and MN, demonstrating that MN is a more reliable source for entry-level names. (for Sect 4)}
+Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
 
-Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
-\cs{Make formulation consistent with what is (was) in the intro:}
-Regarding feature (i), recall that the traditional, taxonomic view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
+Regarding feature (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
 Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
@@
 	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
-	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
+	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal).}
 	\label{fig:entry-level-name-stability}
@@
 Either way, this indeterminacy is not expected to affect our model comparison, hence we will continue to use all entry-level names, as defined in Section~\ref{sec:intro} as the majority name in \mn.
-
-\cs{If time permits, can you compute Figure~\ref{fig:entry-level-name-stability} individually for each domain, and mention what/if something stands out?} \mw{I did this for the `cat' column, see slack, but you probably meant something different by `domain'.
-Anyway, there are pretty big differences between domains yes...}
 

### 2019-12-09 papers/ACL2020/related.tex
increase coherence of sections 1-2-3; shortening still required

@@
-As we outline in the following, our work on natural object naming brings together  research in psycholinguistics, \langvis and computer vision.
-
-\paragraph{(Entry-Level) Object Naming}
-
+%\paragraph{(Entry-Level) Object Naming}
 %cognitive science/psychology:\\
@@
 %\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
+Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision.
 In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}.
-The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while for atypical objects  (e.g.,\ \name{penguin}) the more specific name corresponds to the entry-level category.
-This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin). 
-\newcite{Ordonez:2016} take up this view and learn to transfer an object's \category detected by an object recognition system to its natural name, using external resources like corpus statistics. 
-In contrast, our work exploits actual naming data for instances of real-world objects and tests object naming models on ManyNames, a corpus with robust name annotations from many different speakers.
-This dataset is comparable to picture naming data, though we focus on real-world objects in images instead of prototypical line drawings as in, e.g.,~\newcite{rossion2004revisiting}.  
- \newcite{zarriess-schlangen:2017} learn a naming model from names produced in referring expressions to real-world objects, but they do not have access to name annotations from (many) different speakers and adopt very simple evaluation measures (like accuracy).
-Our present work explores and adopts more nuanced evaluation metrics and aims to model robust speaker preferences with respect to natural naming.
+The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific category.
+%% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
+\newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
+By contrast, we rely on the \mn dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.
+
+Our approach is closer in this regard to \newcite{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions to real-world objects.
+However, they do not have access to name annotations from (many) different annotators, and they rely on simple evaluation measures (like accuracy) whereas the additional annotations we collect enable more fine-grained evaluation.
+The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\newcite{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.
+
  %\sz{maybe we should not mention the Graf paper here ... we do not look at objects in context}
@@
 
-\paragraph{Visual Object Recognition} is a major focus of research in Computer Vision, with object classification being a core task in this area. 
+In Computer Vision a major focus is visual object recognition, with object classification being a core task in this area. 
 Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}).
@@
 For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
-We will use a pretrained ResNet, Faster-RCNN and Bottom-up as models in our work too, extending and testing them for entry-level object naming.
+We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.
+
+\paragraph{The ManyNames dataset}
+As mentioned we will rely heavily on the \mn dataset (Anonymous, under review), which builds upon object annotations in \vg.
+\mn provides up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
+The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as in Section~\ref{sec:intro} as the most frequent name for an object instance.\footnote{
+	The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.
+almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
+}
+Moreover, the fact that these objects are diverse and visually situated in real-world scenes aligns with our view (see Section~\ref{sec:intro}) that entry-level name should be characterized at an instance-level, not at the class-level (cf.\ Section~\ref{sec:manynames}.
+However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
+Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
+%used for \mn, where there is a financial incentive to complete the task as quickly as possible.
+As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
+To overcome these we collected a new layer of verification annotations on top of \mn, as follows.
 

### 2019-12-09 papers/ACL2020/analysis.tex
[ACL2020] analysis: Sect 5.1

@@
 	\small
-	\begin{tabular}{ll||c|cccc|c}
+	\begin{tabular}{l|@{~}c|@{~}c@{~}|c@{~}c@{~}c@{~}c@{~}|c}
 		\toprule
-		&  & Hit & \multicolumn{4}{c|}{Human-like} & Off \\
-		Model &  GT &  & SameObject &  OtherObject &  Low Count &  Related &   \\
+		&  & Hit & \multicolumn{4}{c@{~}|}{Human-like} & Off \\
+		Model &  GT &  & SameObj. &  OtherObj. &  LowCount &  Related &   \\
 		\midrule
-		FRCNN--VG1600&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
-		FRCNN--MN442&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
+		FRCNN$_{\text{VG1600}}$&VG &         74.8 &                13.7 &                  2.9 &              2.4 &              1.7 &          4.5 \\
+		FRCNN$_{\text{MN442}}$&VG &         71.1 &                13.6 &                  3.4 &              2.0 &              2.6 &          7.4 \\
 		\midrule
-		FRCNN--VG1600--VGMN&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
+		FRCNN$_{\text{VG1600--VGMN}}$&MN &         80.7 &                 9.0 &                  2.0 &              1.8 &              3.4 &          3.3 \\
 		\midrule
-		ResNet101--VGMN&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
-		ResNet101--MN442&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
-		ResNet101--VGMN&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
-		ResNet101--MN442&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
+		ResNet101$_{\text{VGMN}}$&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
+		ResNet101$_{\text{MN442}}$&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
+		ResNet101$_{\text{VGMN}}$&VG &         62.8 &                11.6 &                  2.1 &              3.2 &             10.3 &         10.1 \\
+		ResNet101$_{\text{MN442}}$&VG &         63.8 &                11.9 &                  2.4 &              3.3 &              8.8 &          9.9 \\
 		\bottomrule
@@
 
-\begin{table*}[t]
+\begin{table}[t]
 	\centering
 	\small
-	\begin{tabular}{ll|c@{~}c@{~}c@{~}c}
+	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
 		\toprule
@@
 		\midrule
-		FRCNN--VG1600 & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
-		FRCNN--MN442 & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
+		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
+		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
 		\midrule
-		FRCNN--VG1600--VGMN & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
+		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
 		\midrule
-		ResNet101--VGMN & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
-		ResNet101--MN442 & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
-		ResNet101--VGMN & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
-		ResNet101--MN442 & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
+		ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
+		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
+		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
+		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
 		\bottomrule
@@
 	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
-\end{table*}
+\end{table}
 
 The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
-This way of evaluating object naming is unsatisfactory: the ManyNames data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names might be adequate too.\cs{XX}
+This way of evaluating object naming is unsatisfactory: the \mn data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names maybe being adequate too.
 In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behavior.
+\cs{do we?}
 
-\paragraph{Error Categories} We categorize model predictions into the following types (also see Figure~\ref{fig:mistakes} for examples):\\
-Hit: the entry-level name\\
-Off: a non-sensical name (none of the others). \\
-Human-like mishits:
+\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples):\\
+Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
 \begin{itemize}
@@
 \item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
-\item Incorrect-off: a non-sensical name (none of the above)
 \end{itemize}
-We use WordNet for determining whether two names are semantically related   \newcite{fellbaum1998wordnet}.
+
+We use WordNet \cite{fellbaum1998wordnet} for determining whether two names are semantically related.
 
@@
 \sz{why??}
-Both object detection models essentially achieve the same portion of valid predictions.
-Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column off), which might be an effect of the reduction in training data.
+Both object detection models essentially achieve the same portion of human-like mishits.
+Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
 Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
@@
 \paragraph{Why May Models Predict Inadequate Names?}
-In Table~\ref{tab:exp_inadequacy} we focus on the predicted names that are in \mn for the corresponding objects, but judged as inadequate (i.e.,~adequacy score$<0.5$). 
+In Table~\ref{tab:exp_inadequacy} we focus on the predicted names that are in \mn, but judged as inadequate (i.e.,~adequacy score$<0.5$). 
 Most of the inadequate object name predictions are related to an inaccurate bounding box. 
-The overall best FRCNN$_{\text{VG1600--VGMN}}$ model has the smallest proportion of box errors, and hence, the least \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
+The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, and hence, the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
 \iffalse
@@
 \fi
-
+%
 None of the models predicted an inadequate name that was a linguistic, or any other error. 
-The results show that the models make similar mistakes to humans (problems in identifying or recognizing the target object) when being faced with data that was collected with a task setup that approximates human behavior, such as \mn, and the limitations in defining and implementing annotation tasks for data collection of this sort.
+Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
+That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs.
 

### 2019-12-09 papers/ACL2020/manynames.tex
shortening -0.5 page

@@
 	\url{https://mturk.com}
-} (AMT) to categorize the object-name pairs from \mn into various categories (e.g., adequate vs.\ different types of errors), explained below.
-Since this is a multiple-choice task (unlike the generation task through which \mn was gathered) we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).
-
-We verified all the \mn naming data (response sets), with two exceptions: 
-We consider response sets with ~$100$\%~agreement (i.e.,~all annotators gave the same name for an object) as correct, so do not require verification, and all names with a count of~$1$ as unreliable, so we directly discarded those from the sets.
-We collected verifications for the remaining $19,427$~objects, with on average $4$ names each, which we did as follows:
-
-For each object, we presented $3$~annotators with its image, with the object highlighted by its bounding box, and a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
+} (AMT) to categorize the object-name pairs from \mn.
+Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).
+We ran all the \mn naming data (response sets) through our verification, with two exceptions: 
+response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are simply treated as correct, and all names with a count of~$1$ are considered unreliable.
+The remaining $19,427$~objects, with on average $4$ names each, were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
 They were asked to judge the ``adequacy''\footnote{
 	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
-} of each name on a 3-point scale (represented pictorially): ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
-Whenever they did not select ``adequate'', they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else'' (represented pictorially).
-In addition to judging name adequacy, we asked the annotators which names they thought were likely intended (by the original    quit()
- \mn annotators) to name the \textit{same} real-world object, 
-through an intuitive coloring task where they would assign the same color to names intended for the same object (again, see Figure~\cs{1}).
-Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
+} of each name on a 3-point scale: ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
+If they did not select ``adequate'' they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
+Lastly, annotators were asked to judge which names were likely intended for the same object, through an intuitive interface where they would assign the same color to names intended for the same object.
+%% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
+Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
 
@@
 \paragraph{Judgment aggregation}
-Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
-We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority (counting ``none'' for annotators saying there is no inadequacy). 
+We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority.
+%% SHORTENING %%  (counting ``none'' for annotators saying there is no inadequacy). 
 Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
 The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
-This is high given the complexity of the task, essentially mind-reading what the original \mn annotators may have meant, plus the fact that pictures and bounding boxes are sometimes unclear.
-Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types (individual judgments and aggregated).
+This is high given the complexity of the task
+%% SHORTENING %% , essentially mind-reading what the original \mn annotators may have meant, 
+and the fact that pictures and bounding boxes are sometimes unclear.
+Figure~\ref{fig:verification-piechart} shows the proportion of adequate names and inadequacy types.
 \begin{figure}[t]
@@
 
-As for the judgments of whether two names were intended for the same object, we use two different types of aggregations, for different purposes: \sameobject and \cluster.
+We aggregate the judgments of whether two names were intended for the same object in two ways, for different purposes: \sameobject and \cluster.
 % \cs{This pair-wise view is only because of the need for aggregating the clustering of 3 annotators into one, isn't it?
@@
 This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-Second, for a better understanding of the verified \mn data itself (Section~\ref{sect:mn_analysis}) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering).
+Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering).
 We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
@@
 \end{table}
-Let us focus on our two main reasons for wanting to use \mn to evaluate computational models, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
+We will focus on the two main reasons why we want to test computational models on \mn, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
 
-Regarding feature (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
-Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure~\ref{fig:duck} where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
-To quantify this point, let us concentrate on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a very strict requirement which only 281 of the 422 entry-level names of \mn meet.
-These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (SD: .34).
-Now, some of this is due to errors of the type we have sought to identify, but the verified results support the same conclusion: 
-even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, but skewed with about half over 80\%).
+Regarding (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
+Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances (as illustrated in Figure~\ref{fig:duck}). 
+%% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
+We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a strict requirement which only 281 of the 422 entry-level names of \mn meet.
+These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
+%% SHORTENING %%  (SD: .34).
+Importantly, the verified results support the same conclusion: 
+even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, skewed with about half over 80\%).
 
@@
 \begin{figure}[t]
-	\includegraphics[width=.9\columnwidth]{images/stability_analytic.png}
-	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal).}
+	\centering
+	\includegraphics[width=.7\columnwidth]{images/stability_analytic.png}
+	\caption{\% of objects for which the entry-level name can be confidently identified after gathering N names.}
 	\label{fig:entry-level-name-stability}
@@
 by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
-(An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
+%% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
 
 Note that both lines in Figure~\ref{fig:entry-level-name-stability} stay well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
-Turning this around: for around 15\%-20\% of objects, we aren't sure that the \emph{sample} entry-level name we derive from \mn -- what we simply called the entry-level name -- in fact corresponds to the \emph{population} entry-level name.
-In these cases gathering more annotations (i.e., more than 36) could help, but it is also possible that some instances do not have a single, clear entry-level name within a mixed population, or even for a given individual.
-Either way, this indeterminacy is not expected to affect our model comparison, hence we will continue to use all entry-level names, as defined in Section~\ref{sec:intro} as the majority name in \mn.
+Turning this around: for 15\%-20\% of objects we aren't sure that the \emph{sample} entry-level name we derive from \mn -- what we simply defined as the entry-level name -- in fact corresponds to the \emph{population} entry-level name.
+This indeterminacy is not expected to affect our model comparison, but in principle gathering more annotations (i.e., more than 36) could help for these cases -- although it is also possible that some instances do not have a single, clear entry-level name within a mixed population, or even for a given individual.
 

### 2019-12-09 papers/ACL2020/analysis.tex
[ACL2020] analysis: Sect 5.2

@@
 		&  & Hit & \multicolumn{4}{c@{~}|}{Human-like} & Off \\
-		Model &  GT &  & SameObj. &  OtherObj. &  LowCount &  Related &   \\
+		Model & GT  &  & SameObject &  OtherObject &  LowCount &  Related &   \\
 		\midrule
@@
 
-\begin{table}[t]
-	\centering
-	\small
-	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
-		\toprule
-		{Model} &  GT & visual &  linguistic &  box &  other \\
-		\midrule
-		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
-		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
-		\midrule
-		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
-		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
-		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
-		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
-\end{table}
-
 The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
@@
 Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
+\begin{tabularx}{.49\textwidth}{lX}
+	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
+	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
+	LowCount: & a name produced by one annotator\\
+	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+\end{tabularx}
+\iffalse
 \begin{itemize}
@@
 \end{itemize}
+\fi
 
@@
 
-\paragraph{Why May Models Predict Inadequate Names?}
-In Table~\ref{tab:exp_inadequacy} we focus on the predicted names that are in \mn, but judged as inadequate (i.e.,~adequacy score$<0.5$). 
-Most of the inadequate object name predictions are related to an inaccurate bounding box. 
-The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, and hence, the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
-\iffalse
-\cs{remove next couple of sentences? it's very assumptive}
-This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
-And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
-\fi
-%
-None of the models predicted an inadequate name that was a linguistic, or any other error. 
-Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
-That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs.
-
 \begin{table*}[t]
@@
 \end{table*}
-
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{l|l|c@{~}c@{~}c@{~}c}
+		\toprule
+		{Model} &  GT & visual &  linguistic &  box &  other \\
+		\midrule
+		FRCNN$_{\text{VG1600}}$ & VG &             4.3 &                 0.0 &                  95.7 &            0.0 \\
+		FRCNN$_{\text{MN442}}$ & VG &             3.4 &                 0.0 &                  96.6 &            0.0 \\
+		\midrule
+		FRCNN$_{\text{VG1600--VGMN}}$ & MN &             6.7 &                 0.0 &                  93.3 &            0.0 \\
+		\midrule
+		ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
+		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\
+		ResNet101$_{\text{VGMN}}$ & VG &             5.6 &                 0.0 &                  94.4 &            0.0 \\
+		ResNet101$_{\text{MN442}}$ & VG &             4.8 &                 0.0 &                  95.2 &            0.0 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Break-down of the instances (in \%) for which the models predicted an \textit{inadequate} name according to the type of inadequacy.  \label{tab:exp_inadequacy}}
+\end{table}
 \iffalse
@@
 \fi 
-
-\subsection{How do predictions correlate with human agreement?}
-
+\subsection{How do Predictions Correlate with Human Agreement?}
 An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
 This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.
-\sz{is it okay to claim this?}.\cs{how about the way it is now?}
+
 In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
@@
 This indicates that there is indeed a certain similarity between what is difficult for humans and models.
-Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. \sz{why???}
+Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. \sz{why???}\\
+
+In Table~\ref{tab:exp_inadequacy} we focus on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score\mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}.
+Most of the inadequate name predictions are related to an inaccurate bounding box. 
+The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, and hence, the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
+This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
+\iffalse
+\cs{remove next couple of sentences? it's very assumptive}
+This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
+And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
+\fi
+%
+None of the models predicted an inadequate name that was a linguistic, or any other error. 
+Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
+That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs.
 

### 2019-12-09 papers/ACL2020/introduction.tex

@@
 In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
-We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
+%% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
 A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
@@
 However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
-Humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
-For example, in Figure~\ref{fig:duck}, for the two instances of a duck (from \vg, with names from \mn), most people (27 out of 36) called the instance on the left \name{bird}, while \name{duck} was strongly preferred for the right instance.
+Yet humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right. 
 \begin{figure}[t]
@@
 We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
-\mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}
+%% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}
 

### 2019-12-09 papers/ACL2020/related.tex

@@
 %\cs{Necessary to say something about class vs. category? Otherwise I would just always use class to make things easier.}
-Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision.
+%% SHORTENING %%Our work on natural object naming connects research in psycholinguistics, \langvis and computer vision. 
 In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
@@
 
-\cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}
+%% SHORTENING %% \cs{Need to check Jolicoeur and their experiments; say sth about shared visual features}
 % prototypical visual features common to all its instances (e.g.,\ apples are round, pears are ... (CHECK)).
 
-In Computer Vision a major focus is visual object recognition, with object classification being a core task in this area. 
+In Computer Vision a major focus is visual object recognition, with object classification being a core task. 
 Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}).
-These neural object classifiers have proven extremely useful in a large range of transfer learning scenarios. 
-They are commonly used as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
-For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetunes Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
+These neural object classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
+as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
+For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
 We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.
@@
 \paragraph{The ManyNames dataset}
-As mentioned we will rely heavily on the \mn dataset (Anonymous, under review), which builds upon object annotations in \vg.
-\mn provides up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
-The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as in Section~\ref{sec:intro} as the most frequent name for an object instance.\footnote{
-	The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.
+The \mn dataset (Anonymous, under review) which builds upon object annotations in \vg, providing up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
+The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
+Its vocabulary of all names has 7970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
+	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.
 almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
-}
-Moreover, the fact that these objects are diverse and visually situated in real-world scenes aligns with our view (see Section~\ref{sec:intro}) that entry-level name should be characterized at an instance-level, not at the class-level (cf.\ Section~\ref{sec:manynames}.
+The fact that these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level name should be characterized at an instance-level, not at the class-level.
 However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] Sect4+5: ResNetVGMN removed from tables

@@
 		\midrule
-		ResNet101$_{\text{VGMN}}$&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
+		%ResNet101$_{\text{VGMN}}$&MN &         68.7 &                 9.9 &                  3.0 &              2.5 &              7.7 &          8.2 \\
 		ResNet101$_{\text{MN442}}$&MN &         69.7 &                 9.9 &                  3.2 &              2.7 &              7.0 &          7.6 \\	
@@
          \midrule
+         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
+         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
      	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
          ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
-     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
-    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
+
 \bottomrule
@@
  \midrule
+ %ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
+ ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
      ResNet101$_{\text{VGMN}}$ &  VG &   88.3 &           6.2 &      5.5 &   48.5 &          38.8 &     12.7 \\
-     ResNet101$_{\text{VGMN}}$ &  MN &   89.6 &           5.5 &      4.9 &   57.0 &          32.9 &     10.1 \\
-    ResNet101$_{\text{MN442}}$ &  MN &   90.1 &           4.9 &      4.9 &   58.2 &          32.8 &      9.0 \\
     ResNet101$_{\text{MN442}}$ &  VG &   88.6 &           5.2 &      6.2 &   49.9 &          38.2 &     12.0 \\
@@
 		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
+		%ResNet101$_{\text{VGMN}}$ & MN &             3.1 &                 0.0 &                  96.9 &            0.0 \\
 		ResNet101$_{\text{MN442}}$ & MN &             3.0 &                 0.0 &                  97.0 &            0.0 \\

### 2019-12-10 papers/ACL2020/analysis.tex
some tweaks in sec5

--- 2019-12-09 papers/ACL2020/analysis.tex
@@
 The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
-This way of evaluating object naming is unsatisfactory: the \mn data, and also our verification data, clearly shows that human annotators often agree on a certain entry-level name with other names maybe being adequate too.
-In the following, we show how our verification data can be used to gain more detailed insights into the way different naming models calibrate their decisions and reflect human-like naming behavior.
-\cs{do we?}
+This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
+In the following, we use our verification data to assess the severity of errors in different naming models.
 
@@
 
-Table \ref{tab:humanlike} shows the breakdown of the model results for the error categories explained above.
-An important general trend is that the proportion of human-like error seems to be surprisingly constant across all models.
-\sz{why??}
+Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. Here, the proportion of human-like error is suprisingly constant across all models.
 Both object detection models essentially achieve the same portion of human-like mishits.
@@
 \subsection{How do Predictions Correlate with Human Agreement?}
-An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
-This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.
+%An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
+%This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.
 
 In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
-Here, we find a very clear pattern for all models, namely that the portion of hits is generally high when human agreement is also high.
+Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
 Note that this even holds for the ResNet-based classifiers that generally achieve less accuracy.
@@
 This indicates that there is indeed a certain similarity between what is difficult for humans and models.
-Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. \sz{why???}\\
+%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\
 
@@
 Most of the inadequate name predictions are related to an inaccurate bounding box. 
-The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, and hence, the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
-This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
+The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, but the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
+An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$  predicts a more specific \textit{cow} for an object that most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
+This illustrates an extremely tricky case of entry-level name: the model essentially has to guess that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.
+
+%This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
 \iffalse
@@
 %
-None of the models predicted an inadequate name that was a linguistic, or any other error. 
+None of the models predicted an inadequate name that was a linguistic, or any other error \sz{what??? no errors no more :-)}. 
 Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
 That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs.
+\sz{this sounds a bit ...
+convoluted}
 

### 2019-12-10 papers/ACL2020/acl2020_main.tex
shortening -0.5 page
[ACL2020] main

@@
 \usepackage{multirow}
+\usepackage{tabularx}
 \usepackage{times}
@@
 Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
-Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by a single annotator.
+Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators.
 Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
 We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
-on predicting entry-level than \arbitrary names, despite being trained on  \arbitrary names.
-We further fine-tune these models via transfer learning and systematically vary their training vocabulary.
+on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
+Our analyses also reveal the limitations of modeling human naming behavior with proxy data of the true situation in which the phenomenon occurs.  
+%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
 \sz{something ...}
@@
 
-\section{ManyNames: A Source for Entry-Level Names}
+\section{Adequacy and Errors in ManyNames}
 \label{sec:manynames}

### 2019-12-10 papers/ACL2020/analysis.tex
some tweaks in sec4
some tiny tweaks in sec5

@@
 	\end{tabular}
-	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
+	\caption{Name (no. of annotations, adequacy rating), verification and predictions for two objects}
 	\label{fig:mistakes}
@@
 
-We use WordNet \cite{fellbaum1998wordnet} for determining whether two names are semantically related.
+Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}.
 
-\subsection{How Human-Like are Model Predictions and Errors?}
+\paragraph{How Human-Like are Model Predictions and Errors?}
 
-Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. Here, the proportion of human-like error is suprisingly constant across all models.
+Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
 Both object detection models essentially achieve the same portion of human-like mishits.
@@
 \fi 
-\subsection{How do Predictions Correlate with Human Agreement?}
+\paragraph{Do Predictions Deteriorate with Agreement?}
 %An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.

### 2019-12-10 papers/ACL2020/supplementary.tex
finish(ish) supplementary material

--- 2019-12-08 papers/ACL2020/supplementary.tex
@@
 \label{sec:verif}
+As summarized in the main paper, we recruited annotators from Amazon Mechanical Turk\footnote{
+	\url{https://mturk.com}
+} (AMT) to categorize the object-name pairs from the \mn dataset.
+Here we detail the task interface, our population of annotators, the quality control measures we took, and the approval/rejection policy and rewards.
+Basic numbers and results are summarized in Table~\ref{tab:verification-numbers}.
+
+\paragraph{Task interface and instructions}
+The task interface is shown in Figure~\ref{fig:verification-interface}.
+We provided (and clarified by means of explanation and visual examples, not show in the image) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
+The buttons in the interface all contained suitable pictorial representations to facilitate learning the task.
+We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons and some of the highlighted terms in the task headings.
+The hover text of the coloring/clustering task contained a visual example of a completed color grid.
+Feedback from annotators suggested that the task interface was intuitive, and they generally enjoyed doing our tasks.
 \begin{figure*}[t]
@@
 
-\cs{The text is is just copied from the main, it needs to be adapted here.}
-We provided (and clarified by means of explanation and visual examples) the following definition: \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
-When the participant selected slightly or totally inadequate, four additional icons would appear to indicate the type of inadequacy: ``linguistic mistake'', ``named object not tightly in bounding box'', ``named object mistaken for something it's not'', and ``something else''.
-We provided detailed instructions and examples at the top, as well as informative hover texts on all the buttons.
+\paragraph{Annotators}
+We used AMT's system of qualifications to set the following entry requirements: at least 1000 tasks completed with over 98\% approval rate, and physical location in country with English as a common language (UK, Ireland, USA, New Zealand, Australia), as a proxy for linguistic background.
+We published our tasks in eight batches of a few hundred each, with one or two days in between batches.
+In every batch we set a limit, using the UniqueTurker script\footnote{\url{https://uniqueturker.myleott.com/}}, to 50 tasks per annotator, which ensured a diversity of annotators (hence more informative inter-annotator agreement scores), enabled us to accumulate a larger crowd of typically recurring annotators -- ultimately 255 annotators in total -- and prevented unreliable annotators from doing too many of our tasks before we had the ability to block them (based on our quality control, see below) by assigning a blocking qualification to them, which we did in between batches.
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{|ll|ll|}
+		\hline
+		\multicolumn{2}{|c|}{\textbf{Task setup:}} & \multicolumn{2}{c|}{\textbf{Results:}} \\ \hline
+		Images: & 19,427 &
+		Annotators: & 255 \\
+		Img-name pairs: & 69,356 &
+		Annotators/task: & $\geq$ 3 \\
+		Tasks: & 3,052 &
+		Adeq. mean: & \hspace{-3em}.80 (std .093)\\
+		Images/task: & 6-7 &			
+		Agreement (adeq.) & 88\% \\ 
+		Names/task: & 20-30 &
+		Agr. (inadeq. type): & 86\% \\
+		\multicolumn{2}{|l|}{Task reward: \ \$.50 (+.15)} & 
+		Agr. (same-obj): & 94\% \\
+		\hline
+	\end{tabular}
+	\caption{Verification task overview. 
+		\label{tab:verification-numbers}}
+\end{table}
 
-\bibliographystyle{acl_natbib}
-\bibliography{naming}
+\paragraph{Quality Control}
+Every task (comprising 20-30 names) contained around 15\% automatically generated quality control items of various kinds, based on several simple automatic rules that are \emph{mostly} true:
+\begin{itemize}
+	\item If the \mn entry-level name is equivalent to the original \vg name, assume it is an adequate name.
+	\item Duplicate one of the \mn names for the object (with a strong bias for selecting the entry-level name), randomly insert a plausible-looking typo, assume it counts as a ``linguistic error''.
+	\item Insert a \vg name for a different object in the same image, with a sufficiently different bounding box, and assume it is a ``bounding box error''.
+	\item Insert a random \mn name from the full vocabulary of \mn names, that is not among the \mn names for the present image, and assume this will qualify as an ''other error''.
+	\item Take any two names among the \mn-names for the object that are synonyms according to WordNet, and assume that they should get the same adequacy rating and inadequacy type.
+\end{itemize}
+Moreover, we checked for consistency between the adequacy/inadequacy type categorization task and the subsequent coloring/clustering task in various ways, e.g., if one name is judged adequate and the other a ``bounding box error'', then they should be assigned different colors.
+None of these rules were exceptionless, but put together they gave a pretty clear picture.
+After ignoring the quality controls that no annotator did in the way intended (assuming those must be exceptions to our rules), about half of our tasks scored a 100\% accurate on the quality controls.
+We would award those annotators a bonus (see below).
+We used our quality control items for providing direct feedback to our annotators: when trying to submit their results, participants would get a warning if their accuracy on the quality control items was below 90\%, and the advice to stop doing these tasks if it was below 80\%, with the option to double-check their responses.
+This was meant to encourage them to pay attention, and to discourage them from doing too many of our tasks if they would continue to get warnings.
+We did not prevent them from submitting however, and we made sure they understood that getting the warning would not mean automatic rejection.
+
+\paragraph{Approval/rejection, compensation and bonus}
+Upon task approval, annotators were awarded \$0.50.
+Annotators who scored 100\% accuracy on our quality controls (ignoring ones that no annotator did correctly) received a bonus of \$0.15, as we announced in the instructions for extra incentive.
+After every round we blocked annotators with average accuracy below 90\%, removed their results from the dataset and republished the relevant tasks to ensure consistent coverage of the \mn data.
+Approval/rejection was decided on a much lower threshold of 70\% accuracy, and with various mechanisms in place for more leniency, e.g., the first task below this threshold would be approved nonetheless; and any task below this threshold would be approved if the annotator's average accuracy was above 90\%.
+We rejected less than 2\% of the tasks.
+
+%\bibliographystyle{acl_natbib}
+%\bibliography{naming}
 \end{document}

### 2019-12-10 papers/ACL2020/manynames.tex
[ACL2020] Sect1-3

@@
-\paragraph{Collection procedure}
+\paragraph{Collection Procedure}
 \label{sect:mn_verification}
@@
 } (AMT) to categorize the object-name pairs from \mn.
-Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of our new layer of annotations (see the supplementary material for details).
-We ran all the \mn naming data (response sets) through our verification, with two exceptions: 
-response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are simply treated as correct, and all names with a count of~$1$ are considered unreliable.
-The remaining $19,427$~objects, with on average $4$ names each, were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
+Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
+We ran all the \mn data (response sets) through our verification, with two exceptions: 
+response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
+The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
 They were asked to judge the ``adequacy''\footnote{
@@
 If they did not select ``adequate'' they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
-Lastly, annotators were asked to judge which names were likely intended for the same object, through an intuitive interface where they would assign the same color to names intended for the same object.
+Lastly, annotators were asked to judge which names were likely intended for the same object, through an interface where they would assign the same color to names for the same object.
 %% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
@@
 
-\paragraph{Judgment aggregation}
+\paragraph{Judgment Aggregation}
 We aggregate our name adequacy judgments by taking the mean, and inadequacy type judgments by taking the majority.
@@
 	% <- Carina's reformulation, but not strictly true and not clear to me.
-we want to know primarily whether the name generated by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name (i.e., the most frequent name).
+we want to know primarily whether the name predicted by a model, if it isn't the entry-level name, was at least intended for the same object as the entry-level name.
 This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
@@
 
-The verification we conducted is necessary for our main research aim -- to evaluate computational object naming models -- but they also enable a deeper understanding of the \mn data.
-Table~\ref{tab:stat-entry-level} provides a bird's eye overview.
+The verification we conducted is necessary for our main research aim---to evaluate  object naming models---but they also enable a deeper understanding of the \mn data.
+Table~\ref{tab:stat-entry-level} provides an overview.
 \begin{table}[t]
@@
 \end{table}
-We will focus on the two main reasons why we want to test computational models on \mn, i.e., a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
+We will focus on the two main reasons for testing models on \mn: a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
 
-Regarding (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all instances of a class have the same entry-level name.
-Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances (as illustrated in Figure~\ref{fig:duck}). 
+Regarding (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all its instances have the same entry-level name. 
+Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
 %% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
-We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name -- a strict requirement which only 281 of the 422 entry-level names of \mn meet.
-These names, which are a clear winner at least once, are still on average a clear winner only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
+We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 422 entry-level names of \mn meet.
+These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
 %% SHORTENING %%  (SD: .34).
 Importantly, the verified results support the same conclusion: 
-even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (SD: .35, skewed with about half over 80\%).
+even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
 
@@
 But I think the following is better:}
-Regarding our second reason, feature (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
+Regarding our second reason (ii) mentioned above, Figure~\ref{fig:entry-level-name-stability} shows that gathering many annotations is necessary for reliably identifying entry-level names.
 \begin{figure}[t]
@@
 the red line is computed by taking only names from the \cluster of the entry-level name into account:
-by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
+by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily---but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
 %% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)
 
-Note that both lines in Figure~\ref{fig:entry-level-name-stability} stay well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the entry-level name to come out as majority with 95\% probability: differences in frequencies between the contenders are simply too small.
-Turning this around: for 15\%-20\% of objects we aren't sure that the \emph{sample} entry-level name we derive from \mn -- what we simply defined as the entry-level name -- in fact corresponds to the \emph{population} entry-level name.
-This indeterminacy is not expected to affect our model comparison, but in principle gathering more annotations (i.e., more than 36) could help for these cases -- although it is also possible that some instances do not have a single, clear entry-level name within a mixed population, or even for a given individual.
+Note that both lines in Figure~\ref{fig:entry-level-name-stability} stay well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the entry-level name to come out as majority (95\% probability): differences in frequencies between the contenders are simply too small.
+That is, for 15\%-20\% of objects we aren't sure that the \emph{sample} entry-level name we derive from \mn---what we defined as the entry-level name---in fact corresponds to the \emph{population} entry-level name.
+This is not expected to affect our model comparison, but in principle gathering even more annotations could help for these cases---although it is also possible that some instances do not have a single, clear entry-level name within a mixed population, or even for a given individual.
 

### 2019-12-10 papers/ACL2020/related.tex
[ACL2020] Sect1-3

@@
 In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
-The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific category.
+The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific \category.
 %% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
 \newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
-By contrast, we rely on the \mn dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.
+By contrast, we rely on the ManyNames dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.
 
@@
 In Computer Vision a major focus is visual object recognition, with object classification being a core task. 
-Neural object classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1000 fine-grained classes \cite{googlenet,he2016deep}).
-These neural object classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
-as pretrained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
-For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pretrained ResNet classification and finetuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
-We will use pretrained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.
+Neural image classification systems are trained to label the most salient object in an image and often use the ImageNet \cite{imagenet_cvpr09} benchmark that labels images/objects with 1,000 fine-grained classes \cite{googlenet,he2016deep}.
+These neural classifiers have proven extremely useful %% SHORTENING %%in a large range of transfer learning scenarios. They are commonly used 
+as pre-trained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
+For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
+We will use pre-trained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.
 
 \paragraph{The ManyNames dataset}
-The \mn dataset (Anonymous, under review) which builds upon object annotations in \vg, providing up to 36 name annotations in parallel for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
+The \mn dataset (MN, Anonymous, under review) which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
 The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
-Its vocabulary of all names has 7970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
+Its vocabulary of all names has 7,970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
 	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.
 almost 2M objects in \vg are mentioned in region descriptions with one of these 442 entry-level names.
-The fact that these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level name should be characterized at an instance-level, not at the class-level.
+That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
 However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.

### 2019-12-10 papers/ACL2020/experiments.tex
[ACL2020] Sect4+5: ResNetVGMN removed from tables

@@
 		\midrule
-		ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\
+		%ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6   \\
 
@@
 
-Table \ref{tab:exp_VGvsMN} shows the accuracy of all models on the \mn test data. 
+Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
 We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the VG name (columns VG). 
@@
 
-A pervasive trend in these results is that all models perform better 
+A pervasive trend is that all models perform better 
 at predicting the entry-level name (columns MN) than the VG name (columns VG), regardless of which vocab and which ground-truth they are trained on.  
@@
 
- The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$, the Vanilla classifier that uses  FRCNN$_\text{VG1600}$ features and is trained on the \mn training data. 
+ The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn). 
 The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
@@
 
-To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
-As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon, which involves a lot of variation when names are freely annotated, but also a lot of agreement.
+%To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
+As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, despite a fair amount of agreement between humans,
 Hence, it is a striking result that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
 However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
-The next Section elaborates on this point and proposes a more fair assessment of naming quality achieved by the different models.
+The next Section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.
 

### 2019-12-10 papers/ACL2020/acl2020_main.tex
a get-it-done-conclusion

@@
 \label{sec:conclusions}
+In this paper, we have investigated instance-level entry-level naming of objects in images.
+To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
+as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
+For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
+We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then finetune via transfer learning to entry-level names. 
+In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
+We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
+%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
+%Future work will need to address these challenges.
 

### 2019-12-10 papers/ACL2020/introduction.tex

@@
 Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
-The task of \emph{object naming} -- generating not just a formally correct but also an appropriate, \emph{natural} name for an object -- is distinct from the closely related tasks of object detection and image classification (see below).
-It has been studied in psycholinguistics~\cite{refs} \mw{Refs!}, but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
+The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
+It has been studied in psycholinguistics~(e.g.,~\citet{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
 We address the following question:\\
 \fbox{\parbox{\columnwidth}{\textbf{Q:} Can standard object detection/image classification models (be fine-tuned to) exhibit human-like object naming behavior?}}\\\\
-In particular, we test several models for their ability to generate \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{duck} in Figure~\ref{fig:duck}, right image).
+In particular, we test several models for their ability to predict \emph{entry-level names}, i.e., the names people prefer when calling a specific object (e.g.,~\name{bird} in Figure~\ref{fig:duck}, left image).
 %% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
-A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (\mn, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
-
-In \lv, the choice of a particular name for an object is a ubiquitous problem -- it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
-\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
-The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
-Pre-training on such labels has its justification in that computer vision models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
-slightly pointed).
-But it raises the issue of whether these models could be used for more human-like object naming.
-% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.
-
-% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
-Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
-However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
-Yet humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
-For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right. 
+A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
 \begin{figure}[t]
@@
 \end{figure}
-Hence, both the single-ground-truth view of CV models and the category-level approach predominant in Psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
-The \mn dataset was designed to help mend this gap: it consists of names entered by 36 annotators in parallel, for 25K objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
-However, the name annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.
+
+In \lv, the choice of a particular name for an object is a ubiquitous problem---it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
+\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
+The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+Pre-training on such labels has its justification in that CV models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
+slightly pointed).
+But it raises the issue of whether these models could be directly used for more human-like object naming.
+% Accordingly, these CV models are assessed by their ability to predict a single, in cases very specific, ground-truth label.
+
+% By contrast, the goal of \lv object naming models is to predict the `natural' name of an object, i.e.,~the name a human could choose for the object instance.
+Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
+However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
+Yet humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right.
+
+Hence, both the single-ground-truth view of CV models and the category-level approach predominant in psycholinguistics are insufficient for assessing the effectiveness of \lv models for human-like, entry-level object naming.
+The ManyNames (MN) dataset was designed to help mend this gap: it consists of names entered by 36~annotators in parallel, for 25K~objects in naturalistic images from \vg~\cite{krishna2016visualgenome}.
+However, the annotations of \mn have not been verified to filter out incorrect names or names for the wrong object, a problem that is in some sense the opposite of that posed by the single-ground-truth approach.
 
@@
 More precisely, \mn enables us to define the entry-level as follows:\\
-\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to \mn}}\\\\
-We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understnad the kinds of mistakes each model makes (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
+\fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
+We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
 We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] main

--- 2019-12-10 papers/ACL2020/acl2020_main.tex
@@
 on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
-Our analyses also reveal the limitations of modeling human naming behavior with proxy data of the true situation in which the phenomenon occurs.  
+Our analyses also demonstrate the challenges of collecting data of language phenomena that is a proxy for real-world situations in which the phenomenon under occurs.  
 %and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}

### 2019-12-10 papers/ACL2020/manynames.tex
[ACL2020] small things

@@
 response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
-The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~\cs{1}) in the supplementary material).
+The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~1 in the supplementary material).
 They were asked to judge the ``adequacy''\footnote{

### 2019-12-10 papers/ACL2020/related.tex
[ACL2020] small things

@@
 
-\paragraph{The ManyNames dataset}
+\paragraph{The ManyNames Dataset}
 The \mn dataset (MN, Anonymous, under review) which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.

### 2019-12-10 papers/ACL2020/supplementary.tex
[ACL2020] small things

@@
 
-\paragraph{Task interface and instructions}
+\paragraph{Task interface and Instructions}
 The task interface is shown in Figure~\ref{fig:verification-interface}.
@@
 
-\paragraph{Approval/rejection, compensation and bonus}
+\paragraph{Approval/Rejection, Compensation and Bonus}
 Upon task approval, annotators were awarded \$0.50.

### 2019-12-10 papers/ACL2020/introduction.tex

@@
 	\end{tabular}
-	\caption{Different naming preferences for different instances of the same \category \name{duck} in \mn.\label{fig:duck}}
+	\caption{Different naming preferences (frequencies) for instances of the same \category \name{duck} in \mn.\label{fig:duck}}
 \end{figure}
@@
 The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
-Pre-training on such labels has its justification in that CV models can learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
+Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
 slightly pointed).
@@
 However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
-Yet humans may prefer different names for different instances of the same \category, and have them even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
-For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right.
+But humans may prefer different names for instances of the same \category (e.g., Figure~\ref{fig:duck}), and even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
+%% SHORTENING %% For example, in Figure~\ref{fig:duck} most people (27 out of 36) called the duck on the left \name{bird}, while \name{duck} was strongly preferred for the duck on the right.
 
@@
 
-Our main contributions in this paper are (i) to run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models for their ability at the task of \emph{instance-based, entry-level object naming}.
-More precisely, \mn enables us to define the entry-level as follows:\\
+Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}.
+More precisely, \mn enables us to define entry-level name as follows:\\
 \fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
 We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
-We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that it is possible to apply transfer learning on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
+We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
 %% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

### 2019-12-10 papers/ACL2020/manynames.tex
more space saving

@@
 } (AMT) to categorize the object-name pairs from \mn.
-Since this is a multiple-choice task we were able to conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
+Since this is multiple-choice we could conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
 We ran all the \mn data (response sets) through our verification, with two exceptions: 
 response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
-The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (see Figure~1 in the supplementary material).
+The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (Figure~1 in supplementary material).
 They were asked to judge the ``adequacy''\footnote{
 	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
-} of each name on a 3-point scale: ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (we will encode these below as 1.0, 0.5 and 0.0, respectively).
-If they did not select ``adequate'' they had to specify the type of inadequacy, choosing between ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
-Lastly, annotators were asked to judge which names were likely intended for the same object, through an interface where they would assign the same color to names for the same object.
+} of each name among ``perfectly adequate'', ``there may be a (slight) inadequacy'' and ``totally inadequate'' (encoded below as 1.0, 0.5 and 0.0, respectively).
+If they did not select ``adequate'' they had to specify the type of inadequacy from ``linguistic mistake'', ``named object not tightly in bounding box",  ``named object mistaken for something it's not'', and ``something else''.
+Lastly, annotators had to judge which names were likely intended for the same object, through an interface where they would assign the same color to names intended for the same object.
 %% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
-Overall, $255$~participants annotated a total of $69,356$~object-name pairs, with three participants per pair.
+Overall, $255$~participants annotated $69,356$~object-name pairs, with three participants per pair.
 
@@
 This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, and for that we need to compute actual \emph{clusters} of names (the pairwise majority rule does not result in a proper clustering).
-We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (i.e., this means that all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
+Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, and for that we need to do clustering (the pairwise majority rule does not result in a proper clustering).
+We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (hence all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
 	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis).
@@
 \end{table}
-We will focus on the two main reasons for testing models on \mn: a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
+We focus on our two main reasons for testing models on \mn: a dataset where (i) actual contextualized instances are named (not prototypes or classes), and (ii) every instance is named by many annotators.
 
-Regarding (i), recall that a traditional view of object naming regards entry-level names as determinable based on the object's class, meaning that all its instances have the same entry-level name. 
-Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
+Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
+We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
 %% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
@@
 Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
-the red line is computed by taking only names from the \cluster of the entry-level name into account:
-by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily---but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
+the red line is computed by taking only names from the \cluster of the entry-level name into account.
+
+by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
 %% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

### 2019-12-10 papers/ACL2020/related.tex
more space saving

--- 2019-12-10 papers/ACL2020/related.tex
@@
 In psycholinguistics, studies of picture naming have found that humans identify objects at a preferred level of abstraction, the so-called basic-level \cite{rosch1976basic,jolicoeur1984pictures}. 
-The typicality of the object with respect to this basic-level \category is important for determining the preferred name, i.e.\ the entry-level name: highly typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific \category.
+The typicality of the object with respect to this basic-level is important for determining the preferred name, i.e.\ the entry-level name: typical objects (e.g.,\ a robin) are simply named by their basic-level \category (\name{bird}), while atypical objects (e.g.,\ \name{penguin}) are preferably named by the more specific \category.
 %% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
-\newcite{Ordonez:2016} take up this view and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
-By contrast, we rely on the ManyNames dataset (more details below) to directly test as well as fine-tune object recognition (and image classification) systems, and without presupposing a taxonomical relationship between the possible names for an object.
+\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
+By contrast, we use \mn (details below) to directly test and fine-tune object recognition (and image classification) systems, without presupposing a taxonomical relationship between the possible names for an object.
 

### 2019-12-10 papers/ACL2020/experiments.tex

@@
 
-Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
+Given the entry-level naming data from \mn which extends the \arbitrary naming data from VisualGenome (\vg), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
 Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.

### 2019-12-10 papers/ACL2020/analysis.tex
WOOOHOOO 8 pages

@@
 	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
+	\end{tabularx}
+\begin{tabularx}{.49\textwidth}{lX}
 	LowCount: & a name produced by one annotator\\

### 2019-12-10 papers/ACL2020/experiments.tex

@@
 %To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
-As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, despite a fair amount of agreement between humans,
-Hence, it is a striking result that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
+As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
+Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
 However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] small things

@@
 \newcommand{\mn}{ManyNames\xspace}
+\newcommand{\mnshort}{MN\xspace}
 \newcommand{\vg}{VisualGenome\xspace}
@@
 % Terms that need to be replaced throughout the paper by more appropriate ones:
-\newcommand{\arbitrary}{arbitrary$\rightarrow$?\xspace}
+\newcommand{\arbitrary}{arbitrary\xspace}
 \newcommand{\categories}{classes\xspace}
@@
 as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
-For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
-We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then finetune via transfer learning to entry-level names. 
+For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
+We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
 In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] small things

--- 2019-12-10 papers/ACL2020/analysis.tex
@@
 %
-None of the models predicted an inadequate name that was a linguistic, or any other error \sz{what??? no errors no more :-)}. 
+None of the models predicted an inadequate name that was a linguistic, or any other error. 
 Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
-That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on the \mn data reveals the problem of modeling a phenomenon of human behavior---object naming in our case---by leveraging data that only approximates the real-world situation in which the phenomenon occurs.
-\sz{this sounds a bit ...
-convoluted}
+That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on MN illustrates the challenges involved in collecting object names from image data to model natural object naming, and the relevance of thorough verification and quality control as we did in our work.
 

### 2019-12-10 papers/ACL2020/experiments.tex
[ACL2020] small things

--- 2019-12-10 papers/ACL2020/experiments.tex
@@
 
-Given the entry-level naming data from ManyNames which extends the \arbitrary naming data from \vg, we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
+Given the entry-level naming data from \mn which extends the \arbitrary naming data from VisualGenome (VG), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
 Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
@@
 We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).
-For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.\cs{add size} The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
+For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.
+The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
 \item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
@@
 \fi
+%\paragraph{Measures}
+
+\subsection{Results}
+\label{sect:exp_results}
+
+Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
+We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the VG name (columns VG). 
+%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.
+
+% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
+%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
+%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
+% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
+%\cs{Left as items for the sake of a better overview for now}
 \begin{table}[t]
@@
 GTtrain gives the dataset providing the ground truth labels for training, and GTtest for testing \label{tab:exp_VGvsMN}.}
+	\vspace{0ex}
 \end{table}
-
-%\paragraph{Measures}
-
-\subsection{Results}
-\label{sect:exp_results}
-
-Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
-We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the VG name (columns VG). 
-%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.
-
-% and furthermore report results on the test instances where the two names differ (block VG$\neq$MN). 
-%Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
-%We therefore consider an object's VG name less likely to represent the entry-level name than its MN name. 
-% \gbt{add motivation for the latter, and make sure we address this when we discuss results; else, remove.}. 
-%\cs{Left as items for the sake of a better overview for now}
 

### 2019-12-10 papers/ACL2020/introduction.tex

@@
 
-In \lv, the choice of a particular name for an object is a ubiquitous problem---it underlies virtually all tasks that model how speakers use language to refer to objects in the world, such as image description, visual question answering and referring expression generation.
-\lv methods are generally based on object detection or image classification models from computer vision (CV) research (or the visual features extracted from them) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
-The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (e.g., \name{bus}) while others seem overly specific (e.g.,\ \name{goblet, gyromitra}; cf.\ the label inventory of the ILSVRC challenges; \citealt{ILSVRC15}).
+In \lv, object naming underlies virtually all tasks that model how speakers refer to objects in the world, such as image description or visual question answering.
+\lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
+The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
 Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] abstract
minor tweaks here and there

@@
 on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
-Our analyses also demonstrate the challenges of collecting data of language phenomena that is a proxy for real-world situations in which the phenomenon under occurs.  
+%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
 %and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
-\sz{something ...}
 \end{abstract}
@@
 To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
-as opposed to previous works that mostly adopted a strictly taxonomic view of naming.
+as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
 For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?

### 2019-12-10 papers/ACL2020/analysis.tex
minor tweaks here and there

--- 2019-12-10 papers/ACL2020/analysis.tex
@@
 
-\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples):\\
-Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
+\paragraph{Error Categories} We categorize model predictions into several types (see also Figure~\ref{fig:mistakes} for examples).
+Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:
 \begin{tabularx}{.49\textwidth}{lX}
-	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
-	OtherObject & a name produced by annotators, but not an alternative of the entry-level name \\
-	LowCount: & a name produced by one annotator\\
-	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+	\textbf{\sameobject:} & alternative name for the same object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
+	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
 	\end{tabularx}
-\iffalse
-\begin{itemize}
-	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
-	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
-	\item LowCount: a name produced by only one annotator
-	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
-\end{itemize}
-\fi
-
+\begin{tabularx}{.49\textwidth}{lX}
+	\textbf{LowCount:} & name produced by 1 annotator\\
+	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+\end{tabularx}
 Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}. 
+%\iffalse
+%\begin{itemize}
+%	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
+%	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
+%	\item LowCount: a name produced by only one annotator
+%	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+%\end{itemize}
+%\fi
 
@@
 Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
-Both object detection models essentially achieve the same portion of human-like mishits.
+Both object detection models achieve essentially the same portion of human-like mishits.
 Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
-Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but less valid predictions, and also less nonsensical errors as compared to FRCNN$_{\text{VG1600}}$.
+Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but fewer valid predictions, and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
 This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
-The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse semantically similar names to a valid name, that are, however, not valid.
+The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.
 
-\iffalse
-\begin{table*}[t]
-\centering
-	\small
-\begin{tabular}{ll||rr|rrr}
-\toprule
-&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
-                         model &  gt &  hit &  valid &  human-like &  related &  off \\
-\midrule
-       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
-        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
-        \midrule
- FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
-         \midrule
-         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
-         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
-     	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
-         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
-
-\bottomrule
-\end{tabular}
-
-\caption{Model results for different categories of errors} \label{tab:humanlike}
-\end{table*}
-\fi
+%\iffalse
+%\begin{table*}[t]
+%\centering
+%	\small
+%\begin{tabular}{ll||rr|rrr}
+%\toprule
+%&  & \multicolumn{2}{c|}{Correct} & \multicolumn{3}{c}{Incorrect}\\
+%                         model &  gt &  hit &  valid &  human-like &  related &  off \\
+%\midrule
+%       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.7 &         5.3 &      1.7 &    4.5 \\
+%        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.6 &         5.3 &      2.6 &    7.4 \\
+%        \midrule
+% FRCNN$_{\text{VG1600--VGMN}}$ &  MN & 80.7 &      9.0 &         3.7 &      3.4 &    3.3 \\
+%         \midrule
+%         %ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.9 &         5.5 &      7.7 &    8.2 \\
+%         ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.9 &         5.9 &      7.0 &    7.6 \\
+%     	ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.6 &         5.2 &     10.3 &   10.1 \\
+%         ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.9 &         5.7 &      8.8 &    9.9 \\
+%     
+%\bottomrule
+%\end{tabular}
+%
+%\caption{Model results for different categories of errors} \label{tab:humanlike}
+%\end{table*}
+%\fi
 
@@
 \end{table}
-\iffalse
-\begin{figure}
-	\centering
-	\includegraphics[scale=.2]{images/2323938.jpg}
-	\includegraphics[scale=.2]{images/2322259.jpg}
-	\includegraphics[scale=.2]{images/2371657.jpg}
+%\iffalse
+%\begin{figure}
+%	\centering
+%	\includegraphics[scale=.2]{images/2323938.jpg}
+%	\includegraphics[scale=.2]{images/2322259.jpg}
+%	\includegraphics[scale=.2]{images/2371657.jpg}
+%	
+%	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes} \gbt{Will we have space for the figure?
+(Maybe we should \textit{make} space?) Also, shouldn't we put examples from the most successful model instead?}}
+%\end{figure}
+%\fi
 
-	\caption{TODO: examples resnet mistakes (trained on vg\_manynames, tested on manynames-442)\label{fig:mistakes} \gbt{Will we have space for the figure?
-(Maybe we should \textit{make} space?) Also, shouldn't we put examples from the most successful model instead?}}
-\end{figure}
-\fi 
-\paragraph{Do Predictions Deteriorate with Agreement?}
+\paragraph{Low Human Agreement, Worse Predictions?}
 %An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
@@
 
-In Table \ref{tab:exp_errors_agreement}, we show the break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
+Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
 Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
-Note that this even holds for the ResNet-based classifiers that generally achieve less accuracy.
-When agreement is lower, all models produce less hits and more valid alternatives. 
-This indicates that there is indeed a certain similarity between what is difficult for humans and models.
+Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
+When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
 %Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\
 
-In Table~\ref{tab:exp_inadequacy} we focus on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score\mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}.
-Most of the inadequate name predictions are related to an inaccurate bounding box. 
-The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of box errors, but the highest \textit{visual} (i.e.,~the object is difficult to interpret) inadequate name predictions.
-An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$  predicts a more specific \textit{cow} for an object that most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
-This illustrates an extremely tricky case of entry-level name: the model essentially has to guess that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.
+Table~\ref{tab:exp_inadequacy} focuses on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score \mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}).
+Most of the inadequate name predictions are due to the model naming an object that does not properly fit the bounding box. 
+The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of these bounding box errors, but the highest proportion of \textit{visual} errors (i.e.,~named object misinterpreted for something it's not).
+An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$ predicts the more specific name \textit{cow} for an object that is not strictly speaker a cow and which most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
+This illustrates a tricky case of entry-level name: the model needs to `understand' that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.
 
 %This might be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names . 
-\iffalse
-\cs{remove next couple of sentences? it's very assumptive}
-This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
-And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
-\fi
+%\iffalse
+%\cs{remove next couple of sentences? it's very assumptive}
+%This may be due to it using features pre-trained towards object detection (i.e.,~localization), but then being optimized towards \mn entry-level names. 
+%And the ResNet101-based models, which use features that were pre-trained towards image classification (i.e.,~categorizing the salient object in an image (region)), make slightly more visual errors when being optimized on \vg ground truth labels than their \mn ground truth counterparts.
+%\fi
 %
-None of the models predicted an inadequate name that was a linguistic, or any other error. 
-Recall that all predictions we are analysing here were in the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
+None of the models predicted an inadequate name classified as a ``linguistic error'' or as ``other error''.
+Recall that all predictions we are analyzing here concerned the \mn data, i.e.,~at least two people gave the predicted, but inadequate name for the object. 
 That the models make similar mistakes to humans (problems in identifying or recognizing the target object) on MN illustrates the challenges involved in collecting object names from image data to model natural object naming, and the relevance of thorough verification and quality control as we did in our work.

### 2019-12-10 papers/ACL2020/manynames.tex
intro
minor tweaks here and there

@@
 %% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
-We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 422 entry-level names of \mn meet.
+We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 442 entry-level names of \mn meet.
 These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
@@
 Our verification results let us see that most of the remaining indeterminacy occurs within the entry-level name's \cluster:
-the red line is computed by taking only names from the \cluster of the entry-level name into account.
-
-by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily -- but not by much, since names for the wrong object tend not to compete for `most frequent' anyway.
+the red line is computed by taking only names from the \cluster of the entry-level name into account, showing that, by discarding names for other objects, the entry-level name for the intended object can be confidently identified more easily (but not by much, since names for the wrong object tend not to be frequent anyway).
 %% SHORTENING %% (An analogous plot for the subset of all adequate names essentially coincided with the red line, reflecting that most adequate names were intended for the same object as the entry-level name.)

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] ...

--- 2019-12-10 papers/ACL2020/analysis.tex
@@
 
-\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples):\\
-Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:
-\begin{tabularx}{.49\textwidth}{lX}
+\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples): 
+Besides \textit{Hit}, the entry-level name, and \textit{Off}, a non-sensical name (none of the others), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
+
+\begin{tabularx}{.46\textwidth}{@{~}lX}
 	\sameobject: & an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
@@
 	LowCount: & a name produced by one annotator\\
-	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
+	Related:& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\\
 \end{tabularx}

### 2019-12-10 papers/ACL2020/analysis.tex

--- 2019-12-10 papers/ACL2020/analysis.tex
@@
 \paragraph{Error Categories} We categorize model predictions into several types (see also Figure~\ref{fig:mistakes} for examples).
-Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:
-\begin{tabularx}{.49\textwidth}{lX}
+Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
+
+\begin{tabularx}{.46\textwidth}{@{~}lX}
 	\textbf{\sameobject:} & alternative name for the same object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
 	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
+	\textbf{LowCount:} & name produced by 1 annotator\\
+	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\\
 \end{tabularx}
-\begin{tabularx}{.49\textwidth}{lX}
-	\textbf{LowCount:} & name produced by 1 annotator\\
-	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
-\end{tabularx}
+
 Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}. 

### 2019-12-10 papers/ACL2020/experiments.tex

@@
 
-Given the entry-level naming data from \mn which extends the \arbitrary naming data from VisualGenome (VG), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
-Moreover, we are able to systematically vary the vocabulary these models are tasked to learn during training, i.e.\ a standard object naming vocab compiled from a frequency list as in \cite{anderson2018updown} or a carefully selected set of entry-level names, aggregated from the ManyNames data.
-The modeling experiments will assess these various modeling decisions for the task of entry-level naming, but using accuracy as a standard evaluation metric,
-Section~\ref{sec:analysis} will analyse these results with respect to more detailed error types.
+Given the entry-level naming data from \mn, which extends the more \arbitrary naming data from VisualGenome (VG), we now have a variety of possibilities to train, re-train or fine-tune existing object detection or classification models, to capture natural naming.
+Moreover, we can systematically vary the vocabulary for these models during training: a standard object naming vocabulary compiled from a frequency list as in \cite{anderson2018updown}, or a set of entry-level names as aggregated from the ManyNames data.
+Our experiments will assess these various modeling decisions for the task of entry-level naming, in the current section by using accuracy as a standard evaluation metric.
+Section~\ref{sec:analysis} will analyze the results with respect to the different types of errors identified by our verification data.
 % found in the verification data in Section \ref{sec:verification}.
@@
 \paragraph{Data}
-We split \mn into training ($21K$~objects) and test data ($1,072$). 
-The test data corresponds to the overlap of \mn (MN) and the VG (VG) test split used by  \newcite{anderson2018updown}. 
-The target vocabulary of the test data is MN442. %the overlap of MN442 and VG ($355$ names). 
-For training using transfer learning, we train on the ground truth labels provided by \mn, but compare to training on \vg labels.
+We split \mn into training ($21K$~objects) and test data ($1,072$), where the test data corresponds to the overlap of \mn (MN) and the \vg (VG) test split used by  \newcite{anderson2018updown}. 
+The target vocabulary of the test data is MN442: the 442 entry-level names we derived from \mn. %the overlap of MN442 and VG ($355$ names). 
+For transfer learning we train models on the ground truth entry-level names provided by \mn, and compare this to training on \vg labels.
 
 \paragraph{Models}
-
-We test two object detection models trained on objects and names from the original \vg data, using the Faster R-CNN architecture \cite{fasterrcnn2015} which is initialized with features that were pre-trained on $1$K~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
+We test two object detection models trained on objects and names from the original \vg data, using the Faster R-CNN architecture \cite{fasterrcnn2015}, initialized with features that were pre-trained on $1$K~ImageNet classes with the ResNet-101 classification model \cite{he2016deep}.
 We use and retrain these two models with different target vocabularies:
@@
 \item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
-The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set 1600 object names in \vg.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of 1600 object names in \vg.
 This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
@@
 The two former models are trained on \vg, which has almost 4 million labeled objects.
-\mn is too small to train object detection models on it from scratch, which require learning millions of parameters.
+\mn is too small to train object detection models on it from scratch, which requires learning millions of parameters.
 On the other hand, obtaining enough naming data to be able to estimate entry-level names for larger datasets is very costly and probably unrealistic.
-Therefore, we investigate the possibility of obtaining entry-level data via transfer learning, fine-tuning existing models with \mn data.
+Therefore, we investigate the possibility of obtaining effective entry-level naming models via transfer learning, fine-tuning existing models with \mn data.
 We do so with the standard methodology of taking the last hidden layer of existing Computer Vision models as input, and train object classification models to predict entry-level names (MN442).
@@
 This yields the following 5 transfer-learning-based naming models:
-
 \begin{itemize}
-\item FRCNN$_{\text{VG1600}}$-VGMN:  This models extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.}.
+\item FRCNN$_{\text{VG1600}}$-VGMN:
+	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
+	As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.
+}.
 We expect these to be very good features for our task, as they have been obtained with the same task (object classification) and dataset (\vg).
 For each object (i.e.,~bounding box) in \mn, we extract its activation features from FRCNN's last hidden layer before the output layer.
-The model uses the VGMN vocabulary (overlap of ManyNames and VG vocab).
-\item ResNet-VGMN: For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{+++}.
+The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
+  \item ResNet-VGMN: 
+For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{imagenet_cvpr09}.
 Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
@@
 The model is optimized on VG and MN ground truth names respectively.
- \item  ResNet-MN442:  The same model as before, but trained with a vocab of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
+ \item  ResNet-MN442:
+ The same model as before, but trained with a vocabulary of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
 \end{itemize}
-
-Note that all five models are optimized on the $25$K~objects in \mn. 
+Note that these five models are optimized on the $25$K~objects in \mn. 
 To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
 
-\iffalse
-\begin{table}[t]
-	\centering
-	\small
-	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc|cc@{~}}
-		\toprule
-		&  & \multicolumn{2}{c}{All} 
-		& \multicolumn{2}{c}{VG$\neq$MN}\\
-		&  & \multicolumn{2}{c}{($1072$)} 
-		& \multicolumn{2}{c}{($223$)}\\	
-		Model$_{\text{Vocab}}$ 
-		&  GTtrain &  VG & MN 
-		&  VG & MN \\ 
-		\midrule
-		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
-		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
-		\midrule \midrule
-		\multicolumn{6}{c}{Classifiers: Transfer learning on MN}\\
-		Features$_{\text{Vocab}}$ &   \\
-		\midrule 
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
-		\midrule
-		ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
-
-		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
-		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
-		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
-		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
-		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
-		\bottomrule
-	\end{tabular}
-	\caption{Model accuracy (in \%) on the \mn test objects.
+%\iffalse
+%\begin{table}[t]
+%	\centering
+%	\small
+%	\begin{tabular}{@{~}l@{~}|@{~}c@{~}|cc|cc@{~}}
+%		\toprule
+%		&  & \multicolumn{2}{c}{All} 
+%		& \multicolumn{2}{c}{VG$\neq$MN}\\
+%		&  & \multicolumn{2}{c}{($1072$)} 
+%		& \multicolumn{2}{c}{($223$)}\\	
+%		Model$_{\text{Vocab}}$ 
+%		&  GTtrain &  VG & MN 
+%		&  VG & MN \\ 
+%		\midrule
+%		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2 &   20.0 &      48.4  \\
+%		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 &    19.1 &      52.9  \\
+%		\midrule \midrule
+%		\multicolumn{6}{c}{Classifiers: Transfer learning on MN}\\
+%		Features$_{\text{Vocab}}$ &   \\
+%		\midrule 
+%		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6 &    13.8 &      60.4  \\ 
+%		\midrule
+%		ResNet$_{\text{VGMN}}$ & MN  & 60.9 &  68.6 &  13.8 & 50.2  \\
+%		
+%		ResNet$_{\text{MN442}}$ & MN &            61.7 &              69.6 &                        13.8 &              50.7 \\
+%		ResNet$_{\text{VGMN}}$  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+%		%ResNet$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &              28.4 &              31.1  \\
+%		%ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &          34.2 &              28.0 \\
+%		ResNet$_{\text{MN442}}$ & VG  &            63.7 &              63.7 &                  30.7 &              31.1  \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{Model accuracy (in \%) on the \mn test objects.
 Vocab denotes the dataset used to induce the target vocabulary for training (the numbers give the size of the vocabulary).
 GTtrain gives the dataset that provides the ground truth labels during training, and VG and MN for testing \label{tab:exp_VGvsMN}.}
-\end{table}
-\fi
+%\end{table}
+%\fi
 %\paragraph{Measures}
@@
 %To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
-As Section \ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
+As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
 Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
@@
 
-\iffalse
-\cs{under construction}
-\begin{itemize}
-	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
-	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
-	\item ... 
-	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
-	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
-	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
-	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
-	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data.
-\end{itemize}
-\fi
+%\iffalse
+%\cs{under construction}
+%\begin{itemize}
+%	\item Object detection models in CV have different goal than L+V object recognition models (see related work--former is on labels, latter on predicting natural language). 
+%	However, the former, pre-trained towards labels, are the backbone / used as feature extractors for the latter.
+%	\item ... 
+%	\item As we explained, there is a high variation of object names, and objects may be named by multiple alternative names (\cs{vocab size MN vs. vocab size VG for same object set}). 
+%	Yet, humans usually have a clearly preferred name for individual object instances (and the set of those is relatively small)--humans agree on a particular name for an instance (entry-level name).
+%	\item Hence, to model human object naming, datasets with many/dozens of annotations for the same instance are required. 
+%	\item We argue that such datasets are more reliable in that they provide empirically derived preferred names (entry-level names), and richer--the provide valid name alternatives. 
+%	\item But since their elicitation is expensive and time-consuming, it is not realistic to create training datasets of dozens of object names for pre-training features with CV models, which need a huge amount of training data.
+%\end{itemize}
+%\fi
 
-\iffalse
-We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
-Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
-Can object detection models, trained on arbitrary names, account for human object naming?
-\begin{itemize}
-	\item Do they predict the entry-level name?
-	\item Are valid name alternatives among the top-N predictions?
-x	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
-	-- naming an alternative object (maybe more salient)\\
-	-- predicting a semantically related name
-	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
-	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
-	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
-	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
-\end{itemize}
-\fi
+%\iffalse
+%We propose to use datasets of object names for evaluating models on the task of object naming (depending on results: also valuable for comparing object detection/image classification models).
+%Specifically, we analyse object detection [and classification] models on the task of human object naming, using the \mn dataset as test data:\\
+%Can object detection models, trained on arbitrary names, account for human object naming?
+%\begin{itemize}
+%	\item Do they predict the entry-level name?
+%	\item Are valid name alternatives among the top-N predictions?
+%x	\item Do models make similar mistakes as humans when being faced with the task of naming highlighted objects in images [i.e.,\ the artificial setup of object naming for data annotation]?\\
+%	-- naming an alternative object (maybe more salient)\\
+%	-- predicting a semantically related name
+%	%do we get different evaluation results when testing existing object classification models on preferred responses from name distributions, as compared to naming responses collected from 1-3 workers (e.g., VisualGenome)?
+%	\item Can we use \mn as fine-tuning dataset? (Here: only Vanilla model)\\
+%	-- can we learn entry-level names by fine-tuning object detection models on \mn?\\
+%	-- Can we directly learn entry-level names by fine-tuning image classification models on \mn, i.e.,\ the pre-trained features to initialize object detection models?
+%\end{itemize}
+%\fi
 
-\iffalse
-OLD TABLE WITH MORE MEASURES
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
-		\toprule
-		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
-		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
-		Model$_{\text{Vocab}}$	 
-		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
-		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
-		\midrule
-		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
-		FRCNN--VG2500 & VG \\
-		FRCNN$_{\text{VG1600}}$ & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
-		\midrule \midrule
-		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
-		Features$_{\text{Vocab}}$ & GTtrain  \\
-		\midrule 
-		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
-		FRCNN$_{\text{VG1600}}$--MN442 &  MN \\
-		\midrule
-		ResNet101$_{\text{VGMN}}$ & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
-
-		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
-		ResNet101$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
-		ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
-		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
-		\bottomrule
-	\end{tabular}
-	\caption{Target vocabulary in test data: MN442.
+%\iffalse
+%OLD TABLE WITH MORE MEASURES
+%
+%\begin{table*}[t]
+%	\centering
+%	\small
+%	\begin{tabular}{l|c|r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r|@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}r@{~}}
+%		\toprule
+%		&   & \multicolumn{6}{c}{All Test Images ($\#$)} 
+%		& \multicolumn{6}{c}{VG$\neq$MN Images ($\#$)}\\	
+%		Model$_{\text{Vocab}}$	 
+%		&  GTtrain &  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR 
+%		&  =VG & =MN & $\in$MN  & KL & J & MRR & AvgMRR\\ 
+%		\midrule
+%		FRCNN--MN442 & VG &            65.4 &              71.2 &                85.6 &         1.0 &             69.8 &          0.8 &             0.7 &            20.0 &              48.4 &                78.7 &         1.4 &             60.4 &          0.7 &             0.5 \\
+%		FRCNN--VG2500 & VG \\
+%		FRCNN$_{\text{VG1600}}$ & VG &            67.3 &              74.5 &                89.2 &         0.6 &             74.3 &          0.8 &             0.7 &            19.1 &              52.9 &                86.2 &         0.8 &             69.4 &          0.7 &             0.6 \\
+%		\midrule \midrule
+%		& \multicolumn{12}{c}{Classifiers: Fine-tuning pre-trained image features on \mn}\\
+%		Features$_{\text{Vocab}}$ & GTtrain  \\
+%		\midrule 
+%		FRCNN$_{\text{VG1600}}$$_{\text{VGMN}}$ & MN &            70.8 &              80.6 &                90.1 &         4.7 &             62.0 &          0.8 &             0.6 &            13.8 &              60.4 &                85.8 &         4.6 &             47.3 &          0.7 &             0.5 \\
+%		FRCNN$_{\text{VG1600}}$--MN442 &  MN \\
+%		\midrule
+%		ResNet101$_{\text{VGMN}}$ & MN  &            60.9 &              68.6 &                77.9 &         4.9 &             56.4 &          0.8 &             0.6 &            13.8 &              50.2 &                73.3 &         4.7 &             42.9 &          0.6 &             0.4 \\
+%		
+%		ResNet101--MN442 & MN &            61.7 &              69.6 &                78.9 &         4.9 &             57.4 &          0.8 &             0.6 &            13.8 &              50.7 &                73.8 &         4.6 &             45.1 &          0.6 &             0.5 \\
+%		ResNet101$_{\text{VGMN}}$\_4ep  &   VG &  62.4 &              62.9 &                75.0 &         5.0 &             53.7 &          0.7 &             0.6 &            28.4 &              31.1 &                64.9 &         4.8 &             39.1 &          0.4 &             0.4 \\
+%		ResNet101$_{\text{VGMN}}$\_8ep & VG &            63.9 &              62.6 &                75.6 &         5.0 &             53.9 &          0.7 &             0.6 &            34.2 &              28.0 &                66.2 &         4.9 &             39.7 &          0.4 &             0.4 \\
+%		ResNet101--MN442 & VG  &            63.7 &              63.7 &                76.6 &         5.0 &             55.4 &          0.7 &             0.6 &            30.7 &              31.1 &                67.1 &         4.8 &             41.0 &          0.4 &             0.4 \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{Target vocabulary in test data: MN442.
 Vocab denotes the dataset from which the target vocabulary for training was induced (the numbers give the size of the vocabulary).
@@
 }
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\small
-	\begin{tabular}{l@{~}|rrrr}
-		\toprule
-		... \\
-		\midrule
-		Domain	 & ... \\ 
-		\midrule
-		All           \\
-		home           \\
-		food           \\
-		buildings      \\
-		vehicles       \\
-		animals\_plants \\
-		clothing       \\
-		people         \\
-		\bottomrule
-	\end{tabular}
-	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
-\end{table*}
-
-% \subsection{[TBC] Generalization Ability: OpenImages}
-% \label{sect:exp_openimages}
-% Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
-
-% Models compared: FRCNN$_{\text{VG1600}}$ vs. FRCNN$_{\text{MN442}}$ vs. ResNet101--XX (best Vanilla).
-\fi
+%\end{table*}
+%
+%
+%\begin{table*}[t]
+%	\centering
+%	\small
+%	\begin{tabular}{l@{~}|rrrr}
+%		\toprule
+%		... \\
+%		\midrule
+%		Domain	 & ... \\ 
+%		\midrule
+%		All           \\
+%		home           \\
+%		food           \\
+%		buildings      \\
+%		vehicles       \\
+%		animals\_plants \\
+%		clothing       \\
+%		people         \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{RESULTS FOR SELECTED MODELS \label{tab:domains_bestmodel}}
+%\end{table*}
+%
+%% \subsection{[TBC] Generalization Ability: OpenImages}
+%% \label{sect:exp_openimages}
+%% Question: Can models trained towards \mn generalize to other, related datasets? Here: OpenImages. \cs{[Increase coverage with zero-shot learning?]}\
+%
+%% Models compared: FRCNN$_{\text{VG1600}}$ vs. FRCNN$_{\text{MN442}}$ vs. ResNet101--XX (best Vanilla).
+%\fi
 

### 2019-12-10 papers/ACL2020/analysis.tex
[ACL2020] fixes in exps.

@@
 
-Table~\ref{tab:exp_inadequacy} focuses on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score \mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}).
+Table~\ref{tab:exp_inadequacy} focuses on the predicted \mn names that were judged as inadequate (i.e.,~adequacy score~\mbox{$<0.5$}) and their inadequacy types (see Section~\ref{sect:mn_analysis}).
 Most of the inadequate name predictions are due to the model naming an object that does not properly fit the bounding box. 
-The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of these bounding box errors, but the highest proportion of \textit{visual} errors (i.e.,~named object misinterpreted for something it's not).
-An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$ predicts the more specific name \textit{cow} for an object that is not strictly speaker a cow and which most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
+The overall best model FRCNN$_{\text{VG1600--VGMN}}$ has the smallest proportion of these bounding box errors, and the highest proportion of \textit{visual} errors (i.e.,~named object misinterpreted for something it's not).
+An example for this is shown in Figure \ref{fig:mistakes} (right): FRCNN$_{\text{VG1600--VGMN}}$ predicts the more specific name \textit{cow} for an object that is not strictly speaking a cow and which most humans and FRCNN$_{\text{VG1600}}$ named \textit{animal}.
 This illustrates a tricky case of entry-level name: the model needs to `understand' that humans will have difficulties naming that object with a specific or basic-level name and opt instead for an unusually general name.

### 2019-12-10 papers/ACL2020/experiments.tex
[ACL2020] fixes in exps.

@@
 \begin{itemize}
-\item FRCNN$_{\text{VG1600}}$-VGMN:
+\item FRCNN$_{\text{VG1600--VGMN}}$:
 	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
@@
   \item ResNet-VGMN: 
-For comparison, we consider a much less informed input, namely the features from the ResNet-101 object detection  pretrained on ImageNet \cite{imagenet_cvpr09}.
+For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}.
 Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
@@
 \end{itemize}
-Note that these five models are optimized on the $25$K~objects in \mn. 
+Note that these five models are optimized on the $21$K~objects in \mn. 
 To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
@@
 Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
-We compare model effectiveness on predicting the entry-level name (columns MN) against predicting the VG name (columns VG). 
+We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name (column VG). 
 %We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.
@@
 A pervasive trend is that all models perform better 
-at predicting the entry-level name (columns MN) than the VG name (columns VG), regardless of which vocab and which ground-truth they are trained on.  
+at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on.  
 Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
@@
  The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn). 
-The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (columns MN, GTtrain MN) is decently low.
+The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low.
 This confirms what we observed on the FRCNN results.
@@
 However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
-The next Section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.
+The next section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.
 

### 2019-12-10 papers/ACL2020/acl2020_main.tex
[ACL2020] ...
small things, + a new final sentence in abstract on error analysis

@@
 
-%\usepackage{microtype}
+\usepackage{microtype}
 
@@
 
+\iffalse
 \newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
@@
 \newcommand{\mw}[1]{\textcolor{orange!60!black}{\emph{//mw: #1//}}}
-
+\fi
 % To streamline frequently used terms:
@@
 
-\title{From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects}
+\title{From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects}
 
@@
 on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
+Our detailed error analysis reveals that models generally make more mistakes when human agreement is also low, with inadequate predictions due to bounding box issues being a major source of errors.
 %Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.

### 2019-12-10 papers/ACL2020/analysis.tex
small things, + a new final sentence in abstract on error analysis

@@
 
-Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. The proportion of human-like error is suprisingly constant across all models.
+Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. 
+The proportion of the human-like errors that related inadequate alternatives is surprisingly constant across all models.
 Both object detection models achieve essentially the same portion of human-like mishits.
 Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
-Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits but fewer valid predictions, and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
+Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
+However, it also predicts fewer valid alternatives (SameObject).
 This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.

### 2019-12-10 papers/ACL2020/experiments.tex
small things, + a new final sentence in abstract on error analysis

@@
 	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
-	As our experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former model.
+	As experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former.
 }.

### 2019-12-10 papers/ACL2020/manynames.tex
small things, + a new final sentence in abstract on error analysis

@@
 Importantly, the verified results support the same conclusion: 
-even restricting attention to cases where the name is adequate and names the right object, they are still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
+even restricting attention to cases where the name is adequate and names the right object, they is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
 

### 2019-12-10 papers/ACL2020/related.tex
small things, + a new final sentence in abstract on error analysis

@@
 %% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
-\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to its natural name, guided by external resources like corpus statistics.
+\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to a name, guided by external resources like corpus statistics.
 By contrast, we use \mn (details below) to directly test and fine-tune object recognition (and image classification) systems, without presupposing a taxonomical relationship between the possible names for an object.

### 2019-12-10 papers/ACL2020/acl2020_main.tex
enthusiastic sentence at the end of the conclusions :-)
small fixes intro

@@
 on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
-Our detailed error analysis reveals that models generally make more mistakes when human agreement is also low, with inadequate predictions due to bounding box issues being a major source of errors.
+Our detailed error analysis reveals that models generally make more mistakes when human agreement is low, with inadequate predictions due to bounding box issues being a major source of errors.
 %Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
@@
 We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling).
+
+More generally, we believe that the verified object naming data as well as our modeling approach affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as the prototypicality of the instance itself, or the effect of the visual context.
+
 %Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).

### 2019-12-10 papers/ACL2020/introduction.tex
small fixes intro

@@
-Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal} etc.). 
+Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal}, etc.). 
 The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
-It has been studied in psycholinguistics~(e.g.,~\citet{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
+It has been studied in psycholinguistics~(e.g.,~\citealt{Rosch1978}), but has received comparatively little attention in \langvis (\lv) and computational linguistics (CL) research.
 We address the following question:\\
@@
 %% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
-A secondary contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe and make available with this paper.
+A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe here.%
+\footnote{Data and code for this paper will be made available upon publication.}
 \begin{figure}[t]
@@
 \lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
-The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
+The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others are much more specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
 Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
@@
 Psycholinguistic studies have found that humans have a preference towards a particular name, defined as the \textit{entry-level name}, when naturally naming an object \cite{rosch1976basic,Rosch1978,jolicoeur1984pictures}.
-However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \newcite{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
+However, this research has traditionally focused on \categories and/or their prototypical/schematic depictions (e.g., \citealt{rossion2004revisiting}), as opposed to the situated instances in naturalistic images with which \lv is mostly concerned.
 But humans may prefer different names for instances of the same \category (e.g., Figure~\ref{fig:duck}), and even disagree in their choice for the same instance (see also \citealt{graf2016animal}).
@@
 Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}.
-More precisely, \mn enables us to define entry-level name as follows:\\
+More precisely we define entry-level name as follows:\\
+%, \mn enables us to define entry-level name as follows:\\
 \fbox{\parbox{\columnwidth}{\textbf{Entry-level name:} the most common name given to an object instance according to ManyNames}}\\\\
 We evaluate the effectiveness of different models on predicting these entry-level names, and our additional verification annotations enable us to understand the kinds of mistakes the models make (e.g.,~a `wrong' prediction may be a less preferred name as opposed to a true error).
-We show that generic object classification models on their own (ResNet, Faster-RCNN and Bottom-up) already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
+We show that generic object classification models on their own already learn to provide entry-level names for objects, but also that they can transfer-learn on \mn, successfully using pre-trained features from object detection and image classification models to train entry-level naming models.
 %% SHORTENING %% \mw{Remark about the kinds of human errors, just as in the abstract, or some other more interesting teaser?}

### 2019-12-10 papers/ACL2020/related.tex
small fixes section 2

@@
 %% This strictly taxonomic view suggests that entry-level names generally hold for all instances of a \category (e.g.,\ penguin).   \mw{Not true!!}
-\newcite{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to a name, guided by external resources like corpus statistics.
-By contrast, we use \mn (details below) to directly test and fine-tune object recognition (and image classification) systems, without presupposing a taxonomical relationship between the possible names for an object.
+\citet{Ordonez:2016} adopt this and train a model to map an object's \category detected by an object recognition system to a name, guided by external resources like corpus statistics.
+By contrast, we use \mn (details below) to directly test and fine-tune object recognition and image classification systems, without presupposing a taxonomical relationship between the possible names for an object.
 
-Our approach is closer in this regard to \newcite{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions to real-world objects.
-However, they do not have access to name annotations from (many) different annotators, and they rely on simple evaluation measures (like accuracy) whereas the additional annotations we collect enable more fine-grained evaluation.
-The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\newcite{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.
+Our approach is closer in this regard to \citet{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions for real-world objects.
+However, they do not have access to name annotations from (many) different annotators, whereas the additional annotations we collect enable more fine-grained evaluation.
+The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\citealt{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.
 
@@
 %members of different \textit{basic-level} categories (e.g., a duck, a robin, a penguin, etc. are all members of \cat{birds}) 
-% \newcite{rohde2012communicating} and \newcite{graf2016animal} investigate naming in context and find that the specificity of a name is dependent on the taxonomic relatedness of other objects in context.
+% \citet{rohde2012communicating} and \citet{graf2016animal} investigate naming in context and find that the specificity of a name is dependent on the taxonomic relatedness of other objects in context.
 
@@
 as pre-trained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
-For instance, a commonly used object detector in \lv is \citep{anderson2018updown}'s so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
-We will use pre-trained ResNet, Faster-RCNN and Bottom-up as models in this paper, extending and testing them for entry-level object naming.
+For instance, a commonly used object detector in \lv is \citet{anderson2018updown}'s so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
+We will use pre-trained ResNet and Faster-RCNN as models in this paper, extending and testing them for entry-level object naming.
 
 \paragraph{The ManyNames Dataset}
-The \mn dataset (MN, Anonymous, under review) which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
+The \mn dataset (MN, Anonymous, under review), which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
 The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
-Its vocabulary of all names has 7,970 types; restricted to entry-level names it has 442 types (still covering over 50\% of the objects in \vg).
+Its total vocabulary of names has 7,970 types; restricted to entry-level names, it has 442 types (still covering over 50\% of the object instances in \vg).
 	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.
@@
 That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
-However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name.
+However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name (see Figure.
 Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
@@
 %- Our work: can object detectors account for natural human object naming with respect to predicting the entry-level name?
+
+%%% Local Variables:
+%%% mode: plain-tex
+%%% TeX-master: "acl2020_main"
+%%% End:

### 2019-12-10 papers/ACL2020/analysis.tex
in the middle of sect 4

@@
-\begin{figure}
-	\centering
-	\footnotesize
-	\begin{tabular}{p{3.7cm}p{3.7cm}}
-		\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
-		\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
-		\\
-		Entry-level: rug (21) &  animal (9)\\
-		\midrule
-		Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
-		Error-box: chair (5, 0.5), floor (3, 0.5) & \\
-		Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
-		\midrule
-		FRCNN$_{\text{VG1600}}$: floor & animal\\
-		FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
-	\end{tabular}
-	\caption{Name (no. of annotations, adequacy rating), verification and predictions for two objects}
-	\label{fig:mistakes}
-\end{figure}
-
 \begin{table*}[t]

### 2019-12-10 papers/ACL2020/experiments.tex
in the middle of sect 4

@@
 \begin{itemize}
-\item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
+\item FRCNN$_{\text{VG1600}}$: This is \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
 The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of 1600 object names in \vg.
@@
  \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
-For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
+For training, we use a PyTorch reimplementation of Faster. R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
 \end{itemize}
@@
 
-We experiment with two kinds of (transferred) input features, different training vocabularies and ground-truth names for instances, similar to the detection models above.
-This yields the following 5 transfer-learning-based naming models:
+We experiment with two kinds of input features, as well as different training vocabularies and ground-truth names for instances, similar to the detection models above.
+This yields the following 4 transfer-learning-based naming models:
 \begin{itemize}
@@
 Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
-The model uses the VGMN vocabulary.
-The model is optimized on VG and MN ground truth names respectively.
- \item  ResNet-MN442:
- The same model as before, but trained with a vocabulary of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
+ResNet-VGMN uses the VGMN vocabulary; we trained two models, optimized on VG and MN ground truth names, respectively, but report only the one optized on VG (the other one yielded similar output).
+ \item  ResNet-MN442 (two models):
+ The same model as ResNet-VGMN, but trained with a vocabulary of 442 entry-level names; we optimized for on VG or MN ground truth names respectively.
 \end{itemize}
-Note that these five models are optimized on the $21$K~objects in \mn. 
+Note that these four models are optimized on the $21$K~objects in \mn. 
 To predict the entry-level name of a target object~$o$, the classifier, a multi-layer neural network, is fed the object's features, and applies softmax activation to the output layer that corresponds to the target vocabulary.
@@
 
-Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
-We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name (column VG). 
+Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data.
+%\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its counterpart.}. 
+We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name . 
 %We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.

### 2019-12-10 papers/ACL2020/manynames.tex
in the middle of sect 4

@@
+\begin{figure}
+	\centering
+	\footnotesize
+	\begin{tabular}{p{3.7cm}p{3.7cm}}
+		\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
+		\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
+		\\
+		Entry-level: rug (21) &  animal (9)\\
+		\midrule
+		Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
+		Error-box: chair (5, 0.5), floor (3, 0.5) & \\
+		Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
+		\midrule
+		FRCNN$_{\text{VG1600}}$: floor & animal\\
+		FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
+	\end{tabular}
+	\caption{Name (no. of annotations, adequacy rating), verification and predictions for two objects}
+	\label{fig:mistakes}
+\end{figure}
+
 \paragraph{Collection Procedure}
@@
 } (AMT) to categorize the object-name pairs from \mn.
-Since this is multiple-choice we could conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
+Since the task was multiple-choice we could conduct rigorous quality control, ensuring the reliability of these annotations (see the supplementary material for details).
 We ran all the \mn data (response sets) through our verification, with two exceptions: 
 response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
-The remaining $19,427$~objects (on average $4$ names each), were presented to $3$~annotators each (i.e., an image with the object highlighted by its bounding box), with a list of all its names to be verified (Figure~1 in supplementary material).
-They were asked to judge the ``adequacy''\footnote{
+Each of the remaining $19,427$ images, with the target object highlighted with a bounding box, were presented to $3$~annotators, with a list of all its names to be verified (Figure~1 in supplementary material; on average $4$ names per object).
+They were asked to judge the adequacy\footnote{
 	In the task we provided the definition that \textit{a name is ``adequate'' if there is an object in the image, whose visible parts are tightly circumscribed by the red bounding box, that one could reasonably call by that name}.
@@
 %% SHORTENING %% Note that this is independent of name adequacy: ``cow'' can be adequate and ``horse'' inadequate, yet both could be intended as naming the same object (i.e., a cow that one annotator misinterpreted to be a horse).
-Overall, $255$~participants annotated $69,356$~object-name pairs, with three participants per pair.
+Overall, $255$~participants annotated $69,356$~object-name pairs (each pair receiving 3 annotations).
 
@@
 Regarding (i), recall that a traditional view of object naming regards all instances of a class to have the same entry-level name.
+This predicts that we will find a stable ordering of entry-level names. 
 We observe instead that many pairs of entry-level names do not have a fixed preference ordering across instances (e.g.,~Figure~\ref{fig:duck}). 
 %% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
-We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name---a strict requirement which only 281 of the 442 entry-level names of \mn meet.
+We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name (covering 281 of the 442 entry-level names of \mn).
 These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
@@
 Importantly, the verified results support the same conclusion: 
-even restricting attention to cases where the name is adequate and names the right object, they is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
+even restricting attention to cases where the name is adequate and names the right object, there is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
 
@@
 
-%%% mode: latex
+%%% Local Variables:
+%%% mode: plain-tex
 %%% TeX-master: "acl2020_main"

### 2019-12-10 papers/ACL2020/related.tex
in the middle of sect 4

@@
 That these objects are diverse and visually situated in real-world scenes aligns with our view that entry-level names should be characterized at an instance-level, not at the class-level.
-However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name (see Figure.
+However, our manual inspection of the \mn data revealed a range of annotation problems, e.g., annotators occasionally named an object different from the one highlighted by the bounding box, or the right object but with an incorrect name (see Figure~\ref{fig:mistakes}, {\it error-box} and {\it error-visual}).
 Although these errors are interesting human data, many of them would not occur in actual language use but are artifacts of the crowdsourcing methodology that uses simple graphical boxes to point workers to the annotation target.
 %used for \mn, where there is a financial incentive to complete the task as quickly as possible.
-As such they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
-To overcome these we collected a new layer of verification annotations on top of \mn, as follows.
+As such, they pose challenges for our research goal, which is to see whether the object-naming ability of computational models resembles that of actual language users.
+To overcome these, we collected a new layer of verification annotations on top of \mn, as follows.
 

### 2019-12-10 papers/ACL2020/experiments.tex
pass over sect 4 finished

@@
 		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
-		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
+		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      {\bf 74.5} \\
 		\midrule \midrule
@@
 		\midrule 
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    {\bf 70.8} &      {\bf 80.6}  \\ 
 		\midrule
@@
 at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on. 
-Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
-The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
+Note that the VG names were derived on the basis of 1-2 annotations per object, which, as shown in Section~\ref{sect:mn_analysis}, is not enough to robustly estimate entry-level names.
+%even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
+The results therefore indicate that, even when not trained to do so (FRCNN$_{\text{VG1600}}$), models tend to predict entry-level names.
+This is likely because entry-level names better reflect generalizations across objects.
+% the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
 
- The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn). 
-The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low.
-This confirms what we observed on the FRCNN results.
-In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
-Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
+The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the transfer learning classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn).
+Fine-tuning on entry-level names also helps in the original task of predicting VG names, as FRCNN$_\text{VG1600}$$_\text{-VGMN}$ also improves in the VG evaluation (70.8\% accuracy, vs.\ \ 67.3\% without fine-tuning).
+As expected, the classifiers using ResNet features obtain the worst results, but are still remarkably effective considering that they were trained on a fraction of FRCNN's training size using a simple transfer learning classifier.
+%, in contrast to the fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low. 
+%This confirms what we observed on the FRCNN results.
+
+In sum, we find that models learn entry-level naming even when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and that they benefit from transfer learning with entry-level names.
+Instead, restricting the training vocabulary to entry-level names is not effective (all MN422 models are worse or comparable to VGMN/VG1600 models).
+% Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
 
@@
 %To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
-As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
-Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
+As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which exhibits a fair amount of agreement and also variation and potential errors.
+Hence, it is striking that even models that are trained on \arbitrary names capture entry-level naming to a good extent.
 However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
-The next section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.
+The next section elaborates on this and proposes a fairer assessment of naming quality.
 

### 2019-12-10 papers/ACL2020/analysis.tex
pass over sect 5

@@
 
-The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
+The previous section looked at the performance of the different naming models using a standard single-label evaluation scheme.
+%vanilla evaluation methods like accuracy.
 This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
@@
 
-\paragraph{Error Categories} We categorize model predictions into several types (see also Figure~\ref{fig:mistakes} for examples).
-Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
+\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples).
+Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a wrong name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
 
 \begin{tabularx}{.46\textwidth}{@{~}lX}
-	\textbf{\sameobject:} & alternative name for the same object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
+	\textbf{\sameobject:} & alternative name for the same object, estimated from \mn and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
+%(see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
 	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
 	\textbf{LowCount:} & name produced by 1 annotator\\
-	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\\
+	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt}; also estimated from WordNet)\\
 \end{tabularx}
 
-Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}. 
+%Semantically related names are determined with WordNet 
 %\iffalse
@@
 This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
-The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.
+The proportion of instances for which the ResNet models predict a `related' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.
 
@@
 
-\paragraph{Low Human Agreement, Worse Predictions?}
+\paragraph{Low Human Agreement, Worse Predictions}
 %An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
@@
 
-Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name.
+Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (viz.\ less) than 90\% of the annotators opted for the entry-level name.
 Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.

### 2019-12-10 papers/ACL2020/acl2020_main.tex
and conclusions

@@
 In this paper, we have investigated instance-level entry-level naming of objects in images.
-To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
-as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
+To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale.
+% but thorougly verified empirical basis, 
+%as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
 For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?

### 2020-01-10 papers/ACL2020/analysis.tex
merges changes by CS and GBT--not submitted version

@@
 
-The previous section looked at the performance of the different naming models using a standard single-label evaluation scheme.
+The previous section looked at the effectiveness of the different naming models using a standard single-label evaluation scheme.
 %vanilla evaluation methods like accuracy.
@@
 \paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples).
-Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a wrong name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
+Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name)
+%wrong name), % [CS] we did not do an exhaustive collection of object names, so the name may still be correct, but just very rare for the instance
+ we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}
 
-\begin{tabularx}{.46\textwidth}{@{~}lX}
-	\textbf{\sameobject:} & alternative name for the same object, estimated from \mn and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
+\begin{tabularx}{.47\textwidth}{@{~}lX}
+	\textbf{\sameobject:} & alternative name for the same object, as estimated from its valid \mn names (see Section~\ref{sect:mn_verification}), or a WordNet synonym or hypernym of the valid MN names (\name{house/building}; \citealt{fellbaum1998wordnet})\\
+	%and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
 %(see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
@@
 	\textbf{LowCount:} & name produced by 1 annotator\\
-	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt}; also estimated from WordNet)\\
+	\textbf{Related:}& a WordNet hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\
 \end{tabularx}
@@
 
-Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (viz.\ less) than 90\% of the annotators opted for the entry-level name.
+Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (vs.\ less) than~$90\%$ of the annotators opted for the entry-level name.
 Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.

### 2020-01-10 papers/ACL2020/introduction.tex
merges changes by CS and GBT--not submitted version

@@
-Objects, being members of many categories, can be called by many names (e.g.,\ a duck can be called \name{duck, bird, animal}, etc.). 
+Objects, being members of many \categories, can be called by many names (e.g.,~a duck can be called \name{duck, bird, animal}, etc.). 
 The task of \emph{object naming}---generating not just a formally correct but also an appropriate, \emph{natural} name for an object---is distinct from the closely related tasks of object detection and image classification (see below).
@@
 %% SHORTENING %% We wish to find out, for instance, whether different types of models or training regimes will tend towards different kinds of human-like errors in this regard.
-A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data of which we also describe here.%
+A second contribution of this paper is instrumental: for a proper evaluation we must first augment an existing human object naming dataset (ManyNames, Anonymous, under review) with extensive quality control, the resulting data which we also describe here.%
 \footnote{Data and code for this paper will be made available upon publication.}
@@
 \lv methods are generally based on object detection or image classification models from computer vision (CV) that were pre-trained towards predicting the single label of each object that is deemed correct by the dataset.
-The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others are much more specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
+The labels used often seem unintuitive from a human perspective, e.g., some are very basic, natural names (\name{bus}) while others seem overly specific (\name{goblet, gyromitra}), cf.\ the label inventory of the ILSVRC challenges \cite{ILSVRC15}.
 Pre-training on such labels can enable CV models to learn rich, discriminative visual feature representations which capture fine-grained differences in object appearances (e.g.,\ sharp-pointed vs.
@@
 Our main contributions are to (i) run the \mn data through a rigorous annotation round to quantify both the adequacy of its names and the types of errors they contain, in order to (ii) test and compare object detection and image classification models at the task of \emph{instance-based, entry-level object naming}.
-More precisely we define entry-level name as follows:\\
+%More precisely w
+We define entry-level name as follows:\\
 %, \mn enables us to define entry-level name as follows:\\

### 2020-01-10 papers/ACL2020/manynames.tex
merges changes by CS and GBT--not submitted version

@@
 response sets with $100$\%~agreement (i.e.,~all annotators gave the same name for an object) are treated as correct, and all names with a count of~$1$ considered unreliable.
-Each of the remaining $19,427$ images, with the target object highlighted with a bounding box, were presented to $3$~annotators, with a list of all its names to be verified (Figure~1 in supplementary material; on average $4$ names per object).
+Each of the remaining $19,427$~images, with the target object highlighted with a bounding box, were presented to $3$~annotators, with a list of all its names to be verified (Figure~1 in supplementary material; on average $4$~names per object).
 They were asked to judge the adequacy\footnote{
@@
 %% SHORTENING %%  (counting ``none'' for annotators saying there is no inadequacy). 
-Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is 0.80 (\mbox{std=$0.093$}).
-The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is 86\%, and agreeing on whether two names were intended for the same object is 94\%.
+Average name adequacy, on the scale from totally inadequate (0) to adequate (1), is~$0.80$ (\mbox{std=$0.093$}).
+The proportion of annotators agreeing on adequacy ratings is 88\%, agreeing on inadequacy type is~$86\%$, and agreeing on whether two names were intended for the same object is~$94\%$.
 This is high given the complexity of the task
@@
 This \textbf{\sameobject} measure we compute by a simple majority rule: true if name1 and name2 were judged to be for the same object by a majority of annotators, and false otherwise.
-Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, and for that we need to do clustering (the pairwise majority rule does not result in a proper clustering).
-We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of .5, using as distance between two names the proportion of annotators saying they do not name the same object (hence all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
+Second, for a better understanding of the verified \mn data itself (analysis below) we want to be able, e.g., to assess the mean number of names per object, which requires clustering (the pairwise majority rule does not result in a proper clustering).
+We compute the \textbf{\cluster} of a name by agglomerative, complete-linkage clustering with a distance threshold of~$.5$, using as distance between two names the proportion of annotators saying they do not name the same object (hence all pairs of names in a cluster must name the same object according to a majority of annotators).\footnote{
 	The `hard' clustering we use may occasionally lead us to \emph{under}estimate the number of names for an object (this is also why we will use \sameobject and not \cluster in model analysis).
@@
 %% SHORTENING %% where the rather non-prototypical instance of a \name{duck} is named \name{bird} by most annotators.
-We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name (covering 281 of the 442 entry-level names of \mn).
-These names, which are a clear winner at least once, are so still on average only in 46\% of cases where there is a clear winner at all (meaning in the other 54\% of cases they are a clear loser).
+We quantify this by focusing on cases in \mn where there is a `clear winner', namely, objects where the entry-level name is at least twice as frequent in the response set as the next most frequent name (covering $281$~of the $442$~entry-level names of \mn).
+These names, which are a clear winner at least once, are so still on average only in $46\%$~of cases where there is a clear winner at all (meaning in the other $54\%$~of cases they are a clear loser).
 %% SHORTENING %%  (SD: .34).
 Importantly, the verified results support the same conclusion: 
-even restricting attention to cases where the name is adequate and names the right object, there is still a clear winner only in 66\% of cases where there is one (std\mbox{$=.35$}, skewed with about half over 80\%).
+even restricting attention to cases where the name is adequate and names the right object, there is still a clear winner only in $66\%$~of cases where there is one (std\mbox{$=.35$}, skewed with about half over $80\%$).
 

### 2020-02-05 papers/ACL2020/experiments_merged.tex

--- 2019-12-10 papers/ACL2020/experiments.tex
@@
 \paragraph{Data}
-We split \mn into training ($21K$~objects) and test data ($1,072$), where the test data corresponds to the overlap of \mn (MN) and the \vg (VG) test split used by  \newcite{anderson2018updown}. 
-The target vocabulary of the test data is MN442: the 442 entry-level names we derived from \mn. %the overlap of MN442 and VG ($355$ names). 
-For transfer learning we train models on the ground truth entry-level names provided by \mn, and compare this to training on \vg labels.
+We split \mn into training ($21$K objects) and test data ($1,072$), where the test data corresponds to the overlap of \mn (MN) and the \vg (VG) test split used by  \newcite{anderson2018updown}. 
+The target vocabulary of the test data is MN442: the $442$~entry-level names we derived from \mnshort. %the overlap of MN442 and VG ($355$ names). 
+For transfer learning we train models on the ground truth entry-level names provided by \mnshort, and compare this to training on \vgshort labels.
 
@@
 \begin{itemize}
-\item FRCNN$_{\text{VG1600}}$: We use \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
-The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of 1600 object names in \vg.
-This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
- \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
+\item FRCNN$_{\text{VG1600}}$: We use \citeauthor{anderson2018updown}'s  \shortcite{anderson2018updown} model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of $1600$~object names in \vgshort.
+This set was obtained by first taking the $2500$~most frequent names in \vgshort and then (manually) filtering certain names.
+ \item  FRCNN$_{\text{MN442}}$: We pre-process the \vgshort data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
 For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
@@
 
-The two former models are trained on \vg, which has almost 4 million labeled objects.
+The two former models are trained on \vg, which has almost $4$~million labeled objects.
 \mn is too small to train object detection models on it from scratch, which requires learning millions of parameters.
@@
 
-We experiment with two kinds of (transferred) input features, different training vocabularies and ground-truth names for instances, similar to the detection models above.
-This yields the following 5 transfer-learning-based naming models:
+We experiment with two kinds of (transferred) input features, different training vocabularies (similar to the detection models above), as well as ground-truth names with which the  instances are annotated (provided by either \mnshort or \vgshort).
+This yields the following $5$~transfer-learning-based naming models:
 \begin{itemize}
 \item FRCNN$_{\text{VG1600--VGMN}}$:
-	This model extracts features from the object classification model FRCNN$_{\text{VG1600}}$\footnote{
+	This model extracts features from the object detection model FRCNN$_{\text{VG1600}}$\footnote{
 	As experimental results will show, FRCNN$_{\text{VG1600}}$ is more effective than FRCNN$_{\text{MN442}}$, so we only use the former.
@@
 The model uses the VGMN vocabulary (overlap of the full ManyNames vocabulary with VG).
-  \item ResNet-VGMN: 
+  \item ResNet$_{\text{VGMN}}$: 
 For comparison, we consider a much less informed input, namely the features from the ResNet-101 image classification model, that was used to initialize the FRCNN models above, and pretrained on ImageNet \cite{imagenet_cvpr09}.
 Results should of course be worse, and our aim is to assess the feasibility of using such generic object representations to obtain entry-level names.
-The model uses the VGMN vocabulary.
-The model is optimized on VG and MN ground truth names respectively.
- \item  ResNet-MN442:
- The same model as before, but trained with a vocabulary of 442 entry-level names. The model is optimized on VG and MN ground truth names respectively.
+ResNet$_{\text{VGMN}}$ uses the VGMN vocabulary.
+It is optimized on VG or MN ground truth names respectively.
+ \item  ResNet$_{\text{MN442}}$:
+ A variant of ResNet$_{\text{VGMN}}$, that is trained with a vocabulary of $442$~entry-level names. It is optimized on VG or MN ground truth names respectively.
 \end{itemize}
@@
 Table \ref{tab:exp_VGvsMN} shows the accuracy of the models on the \mn test data\footnote{ResNet$_{\text{VGMN}}$ with MN is comparable to its couterpart.}. 
-We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name (column VG). 
+We compare model effectiveness on predicting the entry-level name (column MN) against predicting the VG name. 
 %We therefore consider an object's VG name less likely to represent the entry-level name than its MN name.
@@
 %\cs{Left as items for the sake of a better overview for now}
+
 \begin{table}[t]
@@
 		FRCNN$_{\text{MN442}}$ & VG &  65.4 &      71.2   \\
-		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      74.5 \\
+		FRCNN$_{\text{VG1600}}$ & VG &    67.3 &      \textbf{74.5} \\
 		\midrule \midrule
@@
 		\midrule 
-		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    70.8 &      80.6  \\ 
+		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN &    \textbf{70.8} &      \textbf{80.6}  \\ 
 		\midrule
@@
 A pervasive trend is that all models perform better 
-at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they are trained on.  
-Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively.
-The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, with an accuracy of up to~$74.5$\%.
+at predicting the entry-level name (MN) than the VG name (VG), regardless of which vocabulary (Vocab) and which ground-truth (GTtrain) they were trained on.  
+Note that the VG names were derived on the basis of a few annotations per object only, and, as shown in Section~\ref{sect:mn_analysis}, is not enough to robustly estimate entry-level names. 
+%, even ``just'' $10$ or $20$ names sufficiently likely yield an entry-level name for only $68\%$ or $78\%$ instances, respectively. 
+%The results therefore indicate that, even when not trained to do so (FRCNN$_{\text{VG1600}}$), models tend to predict entry-level names.
+The results therefore indicate that the even the FRCNN detection models do learn entry-level naming, despite not trained being to do so, with an accuracy of up to~$74.5$\%.
 
- The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on the \mn). 
-The classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low.
-This confirms what we observed on the FRCNN results.
-In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and benefit from being trained on entry-levels using transfer learning.
+ The overall best model is FRCNN$_\text{VG1600}$$_\text{-VGMN}$ (the Vanilla classifier with FRCNN$_\text{VG1600}$ features, trained on  \mn). 
+ Transfer-learning on entry-level names also helps in the original task of predicting VG names---FRCNN$_\text{VG1600}$$_\text{-VGMN}$ also improves in the VG evaluation ($70.8\%$~accuracy, vs.~$67.3\%$).
+ % [CS] we need to do stat. significance tests
+ %
+As expected, the classifiers using ResNet features are the least effective, but considering that they were trained on a fraction of FRCNN's training size using a simple Vanilla classifier, in contrast to a fully-fledged CNN architecture of the FRCNN object detectors, the drop in effectiveness on entry-level naming (column MN, GTtrain MN) is decently low.
+%This confirms what we observed on the FRCNN results. 
+%
+In sum, we find that models learn entry-level naming when being trained on \arbitrary naming data, obtaining better results on entry-level prediction than VG name prediction for the same instances, and that they benefit from being trained on entry-levels using transfer learning.
 Comparing the target vocabulary, MN442 and VG1600/VGMN, we see that the restriction on a smaller, but empirically derived vocabulary of entry-level names only, is not beneficial, with all MN442 models being worse or comparable to VGMN/VG100.
@@
 %To date, little research has been done on how to finetune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, for purposes of \lv.
-As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which involves a lot of variation and potential errors, besides a fair amount of agreement.
+As Section~\ref{sec:manynames} showed, object naming is a linguistically complex phenomenon which exhibits a fair amount of agreement and also variation and potential errors. 
 Hence, it is striking that even models that are trained on (a lot of) \arbitrary names capture entry-level naming to a good extent.
 However, our results also suggest that current \textit{evaluation} methods might not be very reliable when applied on \arbitrary names, probably punishing models for `errors' that actually constitute plausible alternatives.
-The next section elaborates on this and proposes a more fair assessment of naming quality achieved by the different models.
+The next section elaborates on this and proposes a fairer assessment of naming quality.
 

### 2020-02-05 papers/ACL2020/related.tex

@@
 Our approach is closer in this regard to \citet{zarriess-schlangen:2017}, who train an object naming model from names produced in referring expressions for real-world objects.
-However, they do not have access to name annotations from (many) different annotators, whereas the additional annotations we collect enable more fine-grained evaluation.
+However, they do not have access to name annotations from (many) different annotators, and rely on simple evaluation measures, whereas the additional annotations we collect enable more fine-grained evaluation.
 The \mn dataset on which we rely is akin in spirit to older picture naming datasets (e.g.,~\citealt{rossion2004revisiting}) but focuses on naturalistic images of real-world objects instead of prototypical line drawings.
@@
 as pre-trained feature extractors in object detection systems that localize objects and predict their labels \cite{fasterrcnn2015}.
-For instance, a commonly used object detector in \lv is \citet{anderson2018updown}'s so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
+For instance, a commonly used object detector in \lv is \citeauthor{anderson2018updown}'s~(\citeyear{anderson2018updown}) so-called bottom-up model, which is based on a pre-trained ResNet classifier and fine-tuned Faster-RCNN \cite{fasterrcnn2015} for object detection and classification on \vg.
 We will use pre-trained ResNet and Faster-RCNN as models in this paper, extending and testing them for entry-level object naming.
@@
 \paragraph{The ManyNames Dataset}
-The \mn dataset (MN, Anonymous, under review), which builds upon object annotations in VisualGenome (VG), provides up to 36 name annotations for 25K objects in images, see e.g.\ Figure \ref{fig:duck}.
-The large number of name annotations per object in \mn gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
-Its total vocabulary of names has 7,970 types; restricted to entry-level names, it has 442 types (still covering over 50\% of the object instances in \vg).
+The \mn dataset (MN, Anonymous, under review), which builds upon object annotations in VisualGenome (VG), provides up to $36$~name annotations for $25$K objects in images, see e.g.\ Figure \ref{fig:duck}.
+The large number of name annotations per object in \mnshort gives us a way to reliably derive entry-level names, defined as the most frequent name for an object instance.
+Its total vocabulary of names has $7,970$~types; restricted to entry-level names, it has $442$~types (still covering over $50\%$~of the  instances in \vgshort).
 	%% SHORTENING %%The vocabulary of all entry-level names in \mn contains 442 types (the vocabulary of all names is 7970), covering more than 50\% of the objects in \vg, i.e.

### 2020-02-05 papers/TACL2020/tacl_objectnaming.tex

% File tacl2018v2.tex
% Sep 20, 2018

% The English content of this file was modified from various *ACL instructions
% by Lillian Lee and Kristina Toutanova
%
% LaTeXery is mostly all adapted from acl2018.sty.

\documentclass[11pt,a4paper]{article}
\usepackage{times,latexsym}
\usepackage{url}
\usepackage[T1]{fontenc}

%% Package options:
%% Short version: "hyperref" and "submission" are the defaults.
%% More verbose version:
%% Most compact command to produce a submission version with hyperref enabled
%%    \usepackage[]{tacl2018v2}
%% Most compact command to produce a "camera-ready" version
%%    \usepackage[acceptedWithA]{tacl2018v2}
%% Most compact command to produce a double-spaced copy-editor's version
%%    \usepackage[acceptedWithA,copyedit]{tacl2018v2}
%
%% If you need to disable hyperref in any of the above settings (see Section
%% "LaTeX files") in the TACL instructions), add ",nohyperref" in the square
%% brackets. (The comma is a delimiter in case there are multiple options specified.)

\usepackage[]{tacl2018v2}

%%%% Material in this block is specific to generating TACL instructions
\usepackage{xspace,mfirstuc,tabulary}
\newcommand{\dateOfLastUpdate}{Sept. 20, 2018}
\newcommand{\styleFileVersion}{tacl2018v2}

\newcommand{\ex}[1]{{\sf #1}}

\newif\iftaclinstructions
\taclinstructionsfalse % AUTHORS: do NOT set this to true
\iftaclinstructions
\renewcommand{\confidential}{}
\renewcommand{\anonsubtext}{(No author info supplied here, for consistency with
TACL-submission anonymization requirements)}
\newcommand{\instr}
\fi

%
\iftaclpubformat % this "if" is set by the choice of options
\newcommand{\taclpaper}{final version\xspace}
\newcommand{\taclpapers}{final versions\xspace}
\newcommand{\Taclpaper}{Final version\xspace}
\newcommand{\Taclpapers}{Final versions\xspace}
\newcommand{\TaclPapers}{Final Versions\xspace}
\else
\newcommand{\taclpaper}{submission\xspace}
\newcommand{\taclpapers}{{\taclpaper}s\xspace}
\newcommand{\Taclpaper}{Submission\xspace}
\newcommand{\Taclpapers}{{\Taclpaper}s\xspace}
\newcommand{\TaclPapers}{Submissions\xspace}
\fi

%%%% End TACL-instructions-specific macro block
%%%%

%%%% Start personalised macro block
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tabularx}

\newcommand{\mvec}[1]{$\mathbf{#1}$\xspace}
\newcommand{\name}[1]{\textsl{#1}\xspace}
\renewcommand{\vec}[1]{\mathbf{#1}\xspace}

\newcommand{\cs}[1]{\begin{color}{blue}CS: #1\end{color}\xspace}
\newcommand{\tbd}[1]{\begin{color}{red}TBD: #1\end{color}\xspace}
%%%% End personalised macro block

\title{}

% Author information does not appear in the pdf unless the "acceptedWithA" option is given
% See tacl2018v2.sty for other ways to format author information
\author{
 Template Affiliation/Address Line 1 \\
 Template Affiliation/Address Line 2 \\
 Template Affiliation/Address Line 2 \\
  {\sf template.email@sampledomain.com} \\
}

\date{}

\begin{document}
\maketitle
\begin{abstract}

\begin{itemize}
	\item We address the task of human object naming: given an object that is depicted in an image, produce the name for it. 
	\item While people, when being asked to name an object, tend to agree on a specific name in many cases, there is also variation (REF). The choice of a name for an individual object can thus be considered to underlie some probability distribution over possible names, representing naming preferences. 
	%Individual objects can thus be associated with naming preferences instead of a unique name. 
	\cs{How could we examine in how far/under which conditions the difference in rankings between two objects is not by chance? randomised test?}
	\item Variation can be effected by several factors, such as the appearance of the object itself, or its situated context (both have been studied in psychological research, REF). 
	\item Our goal is to understand the factors which play a role in preferring one name over valid name alternatives for individual objects. 
	\item We formulate the task of object naming as the prediction of  object name preferences, and present XXX model. 
	\item We examine the factors: 
	\item Our results show that XXX.

\end{itemize}

\end{abstract}

\section{Introduction}
\label{sec:introduction}

\cs{How to formulate it? As label distribution learning or as preference learning? (See related work)}

\section{Related Work}
\label{sec:related}

\subsection{Referring Expression Comprehension/Generation}
\cs{relevant for choosing comparison models / models to build upon; urls see tex source}\\
Current SOTA on RefCOCO+/g, in descending order of accuracy:\\

\paragraph{Transformer}
\noindent
Su et al. (2019): VL-BERT: PRE-TRAINING OF GENERIC VISUAL-LINGUISTIC REPRESENTATIONS\\
\cs{Work in progress, results only on RefCOCO+: } compared to VilBERT (below), no seprate vis and lang transformers in early parts of the model, but attention over both modalities from early on; no pre-training on visual-language relation prediction. FRCNN parameters updated during training. \url{arxiv.org/pdf/1908.08530.pdf}\\

\paragraph{Gated Graph ConvNet}
\noindent
Yang et al. (CVPR 2019): Cross-Modal Relationship Inference for Grounding Referring Expressions\\
%\url{openaccess.thecvf.com/content_CVPR_2019/papers/Yang_Cross-Modal_Relationship_Inference_for_Grounding_Referring_Expressions_CVPR_2019_paper.pdf}\\

\paragraph{Transformers}
\noindent
Lu et al. (NIPS 2019): ViLBERT: Pretraining Task-Agnostic Visio-linguistic Representations for Vision-and-Language Tasks\\
In "modelling task", VilBERT is pre-trained to minimise the KL divergence between its input---masked softmax prediction obtained from FRCNN---and its output---reconstruction of the input. In the "multi-modal alignment" task, the model is pre-trained to determine whether image and text match, based on a joint hidden representation (element-wise product of hidden vectors).\\
 \url{arxiv.org/pdf/1908.02265.pdf}\\
 Follow-up: 12-in-1 [...] (work in progress):\\
\url{arxiv.org/pdf/1912.02315.pdf}\\

\noindent
Liu et al. (CVPR 2019): Improving Referring Expression Grounding
with Cross-modal Attention-guided Erasing\\
%\url{openaccess.thecvf.com/content_CVPR_2019/papers/Liu_Improving_Referring_Expression_Grounding_With_Cross-Modal_Attention-Guided_Erasing_CVPR_2019_paper.pdf}\\

\noindent
Wang et al. (CVPR 2019): Neighbourhood Watch: Referring Expression Comprehension via
Language-guided Graph Attention Networks\\
%\url{openaccess.thecvf.com/content_CVPR_2019/papers/Wang_Neighbourhood_Watch_Referring_Expression_Comprehension_via_Language-Guided_Graph_Attention_Networks_CVPR_2019_paper.pdf}\\

\subsection{Object Recognition}
\newcite{kang2019decoupling}: long-tailed recognition

\subsection{Multi-Label Learning / Multi-Target Learning}
Sorower (2010)

\noindent
Xu et al. (2019)\\
\url{ieeexplore.ieee.org/abstract/document/8892612}\\

\noindent
ML:\\
\textbf{Label distribution learning (DLD; Geng, 2016)}\\ \url{ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=7439855}\\
Single-label approach in object recognition, where the object is assigned the most frequently assigned label, underlies the wrong assumption that the relative frequency of the label expresses the \textit{probability} of it being the correct label. Instead, all annotations may be correct, such that the relative frequency of a label~$l$ in fact expresses the \textit{degree of preference} of~$l$ over the other labels.   \\

\noindent
NLP:\\
Zhou et al. (2016) Emotion Distribution Learning from Texts\\
\url{www.aclweb.org/anthology/D16-1061.pdf}\\

\noindent
Visual Emotion Classification: \\
%LDL: related to object naming in that different names can be true for an object (intensity of emotion == degree of preference for name), and naming underlies diverse social and cultural background \\
Yang et al. (2017): tasks of emotion classification and distribution prediction  \url{www.ijcai.org/Proceedings/2017/0456.pdf}\\
-- softmax for classification, and additionally KL loss\\

\noindent
\textbf{Preference Learning}\\
-- Graded Multilabel Classification: The Ordinal Case\\
\url{www.kde.cs.uni-kassel.de/wp-content/uploads/conf/lwa10/papers/kdml18.pdf}   \\
\noindent
-- Label Ranking by Learning Pairwise Preferences\\
\url{www.ke.tu-darmstadt.de/~juffi/publications/aij-08.pdf}\\

\noindent
Object recognition: \\
-- Gao et al. (2017)\\ \url{ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=7890384}\\

\noindent
NLP:\\
-- Fuernkranz et al. (2008) \url{link.springer.com/content/pdf/10.1007/s10994-008-5064-8.pdf}\\
-- (Patent)
\url{patents.google.com/patent/US20190251446A1/en}\\

\section{MODELNAME for Human Object Naming}
\label{sec:method}

\subsection{Architecture}
\label{ssec:model_architecture}
\tbd{START}
\cs{NOTE START}
A graph-based model (as shortly talked about in the last object naming meeting) would make sense if the task was refexp generation/interpretation, where there exists a mutual dependence between the objects and their respective refexps, and the refexp itself encodes relational information between the objects (e.g., \textsl{Y beside X})---the nodes would be the different objects, and the edges would be used to exchange information which effects the determination of a \textit{unique} linguistic reference (generation) for each of them.\\
So, I am favouring a transformer-based NN architecture, without a graph-structure, with self-attention (target object and the input information), and cross-attention (between different objects).
\cs{NOTE END}

\textbf{\cs{I'll add content to the actual architecture tomorrow. But feel free to comment on everything that is here by now / add things to the document.}}

\paragraph{Features (/Input)}
Let $\mathcal{X} = \mathbb{R}^q$ denote the input space, and $\mathcal{N} = \{n_1, n2, \dots, n_N\}$ denote the complete set of names. 
Given a training set $\mathcal{M} = \{({ x_1},R_1), ({ x_2},R_2),\dots,({ x_n},R_n)\}$ of tuples target object representations and name responses. \\
Input ${x_i}$ for target object $o_i$ comprises one or more of the following information:
\begin{description}
	\item[Visual:] $\mathbf{v_i}$, $\mathbf{v_1}, \dots, \mathbf{v_k}$; $\mathbf{s_i}$, $\mathbf{s_1}, \dots, \mathbf{s_k}$; $\mathbf{v_g}$
	\begin{itemize}
		\item Target object representation:\\
		-- image features $\mathbf{v_i}$ of bounding box $\mathbf{b_i}$ of $o_i$ \cs{see below for image features}\\
		-- spatial location features $\mathbf{s_i}$: 5-d vector with normalised top left and bottom right location and relative size (standard features for grounding tasks, such as refexp comprehension, visual semantic role labeling)
		\item Context representation:\\
		-- image features $\mathbf{v_1}, \dots, \mathbf{v_k}$ of other objects $o_1, \dots, o_k; i \notin \{1, \dots, k\}$\\
		option: only objects whose boxes $\mathbf{b_1}, \dots, \mathbf{b_k}$ overlap with box $\mathbf{b_i}$ (e.g., food domain); or no restriction on objects (e.g., racket in image (a), Table~\ref{tab:player_statue})\\
		-- spatial location features of other objects $\mathbf{s_1}, \dots, \mathbf{s_k}$\\
		-- AND/OR: "global" image features, encoding whole image $\mathbf{v_g}$
		%\item Target + context representation:\\
		%-- spatial location features: (standard features for grounding tasks, such as refexp comprehension, visual semantic role labeling)
	\end{itemize}
	\item[Language:] None, $\vec{l_i}$, $\vec{l_1}, \dots, \vec{l_k}$; $\vec{l^g_i}$,  $\vec{l^g_1}, \dots, \vec{l^g_k}$
	\begin{itemize}
		\item Target object:\\
		(A) for ranking loss objective:\\
		-- embedding(s) $\vec{l_i}$ of candidate name(s)\\
		-- length of name, in letters\\
		(B) for KL divergence objective:\\
		-- None \\
		-- embedding $\vec{l^g_i}$ of VG name \cs{does this make sense!?}
		\item Context objs. \mbox{$o_1, \dots, o_k; i \notin \{1, \dots, k\}$}\\
		-- None \\
		-- embeddings $\vec{l_1}, \dots, \vec{l_k}$ of MN names\\
		-- embeddings $\vec{l^g_1}, \dots, \vec{l^g_k}$ of VG names \cs{does this make sense!?}\\
	\end{itemize}
\end{description}

\paragraph{Data}
Image features $\mathbf{v}$
\begin{itemize}
	\item Faster-RCNN, pre-trained on ImageNet?
	\item Faster-RCNN, pre-trained on VG? (Bottom-Up)
	\item ResNet-101? (lower layers, not before softmax output (!))
\end{itemize}
\tbd{END}

\noindent
\tbd{START}
\subsection{Training}
\label{ssec:model_training}
\begin{itemize}
	\item Pre-train on, e.g., VG
	\item Fine-tune on ManyNames 
	%\item [Apply GAN -- generator does not receive visual input.]
	\item View it as Label Distribution Learning, or more generally Preference Order Learning? In the former, the degree of preference (i.e., the actual value) is important, in the latter it's only the ranking of labels according to preference. 
\end{itemize}
\textbf{Ranking loss (max-margin loss)} or \textbf{Label-Ranking Loss} (multiple labels per instance; takes into account the ranking of all labels\footnote{\url{scikit-learn.org/stable/modules/model_evaluation.html}})\\
\cs{Arguments for ranking loss: 
\begin{itemize}
	\item during training, the target name for an instance could be sampled according to its response distribution, thus implicitly learning the distribution / ranking; also, we cannot assume the response distribution to be correct, but it is rather an estimate of the true distribution
	\item we can use the same model for pre-training and fine-tuning: sample highly unlikely negative names from vocabulary
	\item \textbf{for fine-tuning on MN, for the "difficult" cases, we could get negative names for free from the verification data (low adequacy score or wrong cluster)}
	\item using a sigmoid or tanh activation function which feeds the loss function, we could set the margin such that it mirrors the order of preference (higher margin for highly preferred names, lower for less preferred names (is that numerically stable?!))
	\item experimentally successful
	\item fits the view on naming is a matter of preference over multiple names
\end{itemize}
}

\textbf{Normalized Discounted Cumulative Gain}\\
Ranking metric, where only gt labels are considered for computing the loss\footnote{\url{https://scikit-learn.org/stable/modules/model_evaluation.html}}.\\

\textbf{Kullback-Leibler divergence loss (KL loss)}\\

\subsection{Testing}
\begin{itemize}
	\item For ranking objective: compute score for each word in the vocabulary, produce a probability distribution by applying softmax / normalising
	\item For KL divergence objective using a softmax output layer: take directly  output
\end{itemize}
\tbd{END}

\section{Experiments}
\label{sec:experiments}

\paragraph{Questions}
\begin{itemize}
	\item How do we learn these  name preferences?\\
	 (Model itself, TBD) How do we incorporate rankings of names into the training procedure? Is the ManyNames data big enough to do that?
	\item Do contextual features (which ones?) influence the ranking? (refs: \citealp{murphy1989categorizing})\\
	Can we formulate a ``multimodal analogy task''?
	\begin{itemize}
		\item Are specific context objects determinative of the name (e.g., skies+person -> skier; salad;)?
		\item Is there a dependence on the event/situation and the object name on the model effectiveness?  (e.g., TBD)\\
		additional task on action recognition (see also \newcite{Rosch1978} and "basic-level" objects: the most general classes which have common motor sequences)
	\end{itemize}
	\item Appearance of object: prototypicality? lexical factors (familiarity, length)?
\end{itemize}

\paragraph{Minor Questions (for analysis)}
\begin{itemize}
	\item For which domains does context play a more important role?
	\item When entry-level name diverges from object classes' entry-level name (e.g., duck vs. bird), is that due to
	- context?
	- prototypicality (i.e., object itself)?
\end{itemize}

\subsection{Tasks}
\label{ssec:exp_task}

\begin{table*}[t]
\begin{tabularx}{\textwidth}{XXX}
\multicolumn{1}{c}{\textbf{parrot}} 
& \multicolumn{1}{c}{\textbf{bird?}} 
&\multicolumn{1}{c}{\textbf{bird}} \\
\includegraphics[width=0.6\columnwidth]{images/2371393_739660_seed_ambiguous.png}
& \includegraphics[width=0.6\columnwidth]{images/2356387_820983_singleton_obj.png}
& \includegraphics[width=0.6\columnwidth]{images/2341058_944671_singleton_obj.png}
\\
(a) 'parrot': 18, 'bird': 12
% {'bird': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy_type': None, 'cluster_id': 0, 'cluster_weight': 1.0}, 'parrot': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy_type': None, 'cluster_id': 0, 'cluster_weight': 1.0}}
& (b) 'bird': 22, 'parrot': 14
%{'parrot': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'bird': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}}
& (c) 'bird': 27, 'parrot': 9	
%{'parrot': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'bird': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}}
\\
%%%
\includegraphics[width=0.6\columnwidth]{images/2349587_2162340_seed_ambiguous.png}
& \includegraphics[width=0.6\columnwidth]{images/2332379_2755215_supercat_unique.png}
& \includegraphics[width=0.6\columnwidth]{images/2348089_2328048_seed_ambiguous.png}
\\
(d) 'parrot': 20, 'bird': 14
%	{'parrot': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'bird': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}}
& (e) 'bird': 16, 'parrot': 7, 'toy': 4, 'stuffed animal': 3, 'plushier': 2
%{'toy': {'cluster': ('bird', 'parrot', 'plushier', 'stuffed animal', 'toy'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'bird': {'cluster': ('bird', 'parrot', 'plushier', 'stuffed animal', 'toy'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'stuffed animal': {'cluster': ('bird', 'parrot', 'plushier', 'stuffed animal', 'toy'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'plushier': {'cluster': ('bird', 'parrot', 'plushier', 'stuffed animal', 'toy'), 'adequacy': 0.5, 'inadequacy\_type': 'linguistic', 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'parrot': {'cluster': ('bird', 'parrot', 'plushier', 'stuffed animal', 'toy'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}}
& (f) 'bird': 30, 'parrot': 5
%{'parrot': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}, 'bird': {'cluster': ('bird', 'parrot'), 'adequacy': 1.0, 'inadequacy\_type': None, 'cluster\_id': 0, 'cluster\_weight': 1.0}}
\end{tabularx}
\caption{\label{tab:parrot} Parrot vs. bird}
\end{table*}

\begin{table*}[t]
	\begin{tabularx}{\textwidth}{XXX}
		\multicolumn{1}{c}{\textbf{woman / tennis player}} 
		& \multicolumn{1}{c}{\textbf{horse / statue}} 
		&\multicolumn{1}{c}{\textbf{statue / bird}} \\
		\includegraphics[width=0.6\columnwidth]{images/2384231_692300_singleton_obj.png}
		& \includegraphics[width=0.6\columnwidth]{images/2374110_2599202_singleton_obj.png}
		& \includegraphics[width=0.6\columnwidth]{images/2387975_676194_seed_ambiguous.png}
		\\
		(a) 'woman': 17, 'tennis player': 11, 'athlete': 3, 'player': 3, 'person': 2
		& 'horse': 30, 'statue': 5
		& 'statue': 19, 'bird': 8
		\\
		%%%
		\includegraphics[width=0.6\columnwidth]{images/2321096_1048648_singleton_obj.png}
		& \includegraphics[width=0.6\columnwidth]{images/2362660_2481248_supercat_unique.png}
		& \includegraphics[width=0.6\columnwidth]{images/2332099_3492153_singleton_obj.png}\\
		'tennis player': 14, 'woman': 6, 'player': 4, 'shoe': 3, 't-shirt': 2
		& 'statue': 33
		& 'bird': 26, 'swan': 2, 'statue': 2
		\\

	\end{tabularx}
	\caption{\label{tab:player_statue} }
\end{table*}

\tbd{START (minor)}
\cs{Focus on Task 1("full task"), subtasks can be addressed later.}\\
Let $\mathcal{X} = \mathbb{R}^q$ denote the input space, and $\mathcal{N} = \{n_1, n2, \dots, n_N\}$ denote the complete set of names. 
Given a training set $\mathcal{M} = \{({\bf x_1},R_1), ({\bf x_2},R_2),\dots,({\bf x_n},R_n)\}$ of tuples of objects and name responses. 
\begin{enumerate}
	\item As a first step towards Task 2 below, we address the task of agreement prediction \cs{better name for this needed}, i.e.,~$R_i \in \mathbb{N}$ is simply the cardinality of the response set (types) of instance~$\mathbf{x}_i$.\\
	$\Rightarrow$ Factor out the linguistic factors involved in the choice of a name, and analyse the effectiveness of the model on the level of instances/classes/domains, and the influence of the factors under examination (input features). Especially interesting: cases such as object~(e) (visual appearance of instance; Table~\ref{tab:parrot}), and object~(a) (domain; Table~\ref{tab:player_statue}). \\
	$\Rightarrow$ Compare model effectiveness on this task with that on the full task, and analyse with respect to input factors and instances/classes/domains.
	\item Predicting  name preferences (full task)	
	\cs{How do we evaluate this? (see also training losses above) Suggestions:}
	\begin{enumerate}
		\item \textbf{Probability distribution}\\
		Interpret $R_i$ as name response distribution for instance $\mathbf{x}_i$, i.e., the task is to learn a conditional probability mass function $p(y|\mathbf{x};\theta)$ from $\mathcal{M}$, where ${\bf x} \in \mathcal{X}$, $y \in \mathcal{N}$.  $\theta$ are the parameters generating the a distribution that approximates $R_i$ for an instance $\mathbf{x}_i$.
		\item Alternatives: \\
		-- \textbf{Preference Learning}\\
		Interpret $R_i$ as a ranking of name responses, i.e., the actual scores are not considered. 
		E.g.,~woman $>$ tennis player $>$ athlete/player $>$ person (image (a) in Table~\ref{tab:player_statue}) \cs{??possible problem: (near-)ties are not considered}\\
		-- Average reciprocal rank?\\
		-- ... ?
	\end{enumerate}
	\item Subtask 1: Entry-level only\\
	Generation: Given an object, predict its top-responded name (e.g.,~\name{parrot} for images on the left, Table~\ref{tab:parrot}).
	\item Subtask 2: Determine representative of a given name: Which of these two objects is more of an X?\\	
	Interpretation: Given two objects and a name, (o1,o2,nj), determine which object is more likely to be meant. For instance, for (img(a), img(f), \name{parrot}), it would be img(a), and img(f) for nj=\name{bird} (Table~\ref{tab:parrot}).\\
	Related to: prototypicality\\
	-- Task setup:
	Each item consists of two objects and a name nj, (o1,o2,nj), with nj being valid for both, o1 and o2, but the entry-level name for only one of the two objects. 
	%-- Evaluation for Task (i): Is the predicted object’s entry-level name == nj?
	%
	\item \cs{NEW Subtask 3: "Taboo"-game: Given some object names $o_1, \dots, o_k$, predict another alternative name $o_j$ (Assuming $o_1, \dots, o_k$ is in descending order of preference, target could be sampled such that $1<j<k$).  Extra tricky subset: $k=1$}
\end{enumerate}
\tbd{END (minor)}

\subsection{Experimental Setup}
\label{ssec:exp_setup}

\subsection{Results}
\label{ssec:exp_results}

\section{Conclusions}
\label{sec:conclusions}

\section{Notes}
\begin{itemize}
	\item Hypothesis: Naming variation is higher in domains for which humans naturally have "close-to-expert" knowledge, e.g., food, people.\\
	\newcite{tanaka1991object}: \textit{``The main findings were that in the domain of expertise (a) subordinate-level categories were as differentiated as the basic-level categories, (b) subordinate-level names were used as frequently as basic-level names for identifying objects, and(c) subordinate-level categorizations were as fast as basic-level categorizations. [...]\\
		one might hypothesize a downward shift in the basic level or the creation of a
		second more specific basic level in a classification hierarchy as a function
		of expertise. ''}
\end{itemize}

\section{Appendices} 
\label{sec:appendix}
Appendices, if any, directly follow the text and the
references.  Recall that {\em appendices count
towards the page limit.}

\bibliography{naming}
\bibliographystyle{acl_natbib}

\end{document}

### 2020-02-05 papers/TACL2020/tacl_objectnaming.tex
some bla on building blocks of model

@@
 \cs{How to formulate it? As label distribution learning or as preference learning? (See related work)}
-
+\cs{To discuss: issue due to task being conflated with object identification}
 \section{Related Work}
@@
 %\url{openaccess.thecvf.com/content_CVPR_2019/papers/Liu_Improving_Referring_Expression_Grounding_With_Cross-Modal_Attention-Guided_Erasing_CVPR_2019_paper.pdf}\\
+Operates on a language-guided visual relation graph, whose creation is based on  n-order relationships between objects contained in refexps, i.e., a crucial part of the approach is not relevant for addressing object naming.
 
@@
 
-\textbf{\cs{I'll add content to the actual architecture tomorrow. But feel free to comment on everything that is here by now / add things to the document.}}
+\textbf{\cs{Below are some baselines and building blocks for a model which we could discuss and extend, to come to an agreement as to which building blocks and features we want to use.
+Feel free to comment on everything that is here by now / add things to the document.}}
+
+\begin{itemize}
+	\item Simple model 1 (see ACL2020): MLP with softmax at output layer, input is  image feature $\mathbf{v_i}$ of the target object, output is prob distribution
+	\item Simple model 2: MLP with ranking loss, input are $\mathbf{v_i}$ and a true name $\vec{l_i}$, and a set $\vec{L^k_i}$ of $k$ "negative" name embeddings for the target, output similarity score for pair $(v,l)$; score of correct pair, i.e., $MLP(\mathbf{v_i}$, $\vec{l_i})$, is to be larger than score of incorrect pairs by a margin.\footnote{see comments on ranking loss for possible definitions of "negative" and "margin"}
+	\item Simple model 3: same as 2, but with spatial location feature $\mathbf{s_i}$ (see below) as additional input; embed $\mathbf{s_i}$ in hidden space, then combine (e.g., element-wise multiplication) with hidden repr of $\mathbf{v_i}$
+\end{itemize}
+
+\noindent
+Now we assume an input of target object and context objects reprs, $\mathbf{v_i}$, $\mathbf{v_1}, \dots, \mathbf{v_k}$; $\mathbf{s_i}$, $\mathbf{s_1}, \dots, \mathbf{s_k}$; $\mathbf{v_g}$, and positive and negative name embeddings $\vec{l_i}$, $\vec{L^k_i}$\\
+The following are not necessarily in order (i.e., one could come before/after the other) 
+\begin{itemize}
+	\item compute object representation using $\mathbf{v_i}$ and $\mathbf{s_i}$ (context accordingly)
+	\item compute cross-modal reprs fusing name and object repr$^*$
+	\item produce context repr using attention between visual context objects and target object repr $\Rightarrow$ context repr is based on the objects relevant for the target object (e.g., racket in Table~\ref{tab:player_statue})
+	\item ...
+	\item some magic happens and a score for each pair is output (ranking criterion)
+\end{itemize}
+
+\noindent
+$^*$Questions:\\
+\cs{would it make sense to use some kind of a gating mechanism, that, conditioned on the name, produces a visual object repr that contains only information relevant for the name?}
 
@@
 		-- image features $\mathbf{v_i}$ of bounding box $\mathbf{b_i}$ of $o_i$ \cs{see below for image features}\\
-		-- spatial location features $\mathbf{s_i}$: 5-d vector with normalised top left and bottom right location and relative size (standard features for grounding tasks, such as refexp comprehension, visual semantic role labeling)
+		-- spatial location features $\mathbf{s_i}$: 5-d vector with normalised top left and bottom right location and relative size; or alternatively  vectors with normalised coordinates of the center, the width, height and size (standard features for grounding tasks, such as refexp comprehension, visual semantic role labeling)
 		\item Context representation:\\
@@
 		%-- spatial location features: (standard features for grounding tasks, such as refexp comprehension, visual semantic role labeling)
+		\item Relationship between target and context:\\
+		-- 3-d vector of relative distance, relative angle, IoU (intersection-over-union) \cs{this explicit calculation of the visual relations could be an argument for graph-based methods}
+		(Yang et al., inter alia)\\
 	\end{itemize}
@@
 		-- None \\
-		-- embeddings $\vec{l_1}, \dots, \vec{l_k}$ of MN names\\
+		%-- embeddings $\vec{l_1}, \dots, \vec{l_k}$ of MN names\\
 		-- embeddings $\vec{l^g_1}, \dots, \vec{l^g_k}$ of VG names \cs{does this make sense!?}\\
@@
 In the former, the degree of preference (i.e., the actual value) is important, in the latter it's only the ranking of labels according to preference.
+	\item Auxiliary task on prototypicality prediction? (estimated from, e.g., ImageNet)
 \end{itemize}

### 2020-02-17 papers/ACL2020/review_responses.txt
adds reviews + responses

==================== ANSWER GENERAL ====================
We thank all the reviewers for their reviews and comments!
==================== ====================

==================== Review #1 ====================

What is this paper about, what contributions does it make, what are the main strengths and weaknesses?
Authors define the notion of 'entry-level names' which are the most frequent tag given to an object - or simply put, is the majority annotation in the human labeling tasks. 
The main contribution of the work is the new set of crowd-sourced annotations, and the introduction of the notion of entry-level names. There is high inter-annotator agreement among annotators in defining 'adequacy' of a provided label The proposed method is simply to reduce vocabulary and fine-tune a pre-existing model. The examples which authors provide, for example, the duck in figure 1 -- make it seem that many of the cases where entry level name is significantly different are more 'difficult' examples for a typical object detection model. Some discussion in the paper about such aspect would have been great.
Strengths:

The proposed system could be of significant use in bots and agents build to interact with humans which might find use of entry-level names more relatable - though no experiments are conducted to ascertain any impact in downstream applications.

Detailed error analysis is conducted.

Weaknesses:

Comparisons to other methods: Did authors consider using a standard taxonomy to reduce the 'complex labels' to simpler ones? For example, some taxonomies might readily mark ducks to be a 'type-of' bird.

Missing statistics on how frequent are the 'most frequent' labels which are ultimately considered as the entry level names.

Not much is discussed about the set of annotators selected such as their education level and native language. Such attributes of annotators can have an impact on what are the most frequent labels of an object.

Reasons to accept
A new annotation resource on entry-level names.
Reasons to reject
Incomplete details and limited analysis of the collected dataset. Not clear if the the notion of 'entry-level names' is robust across most user groups.
Overall Recommendation:	2.5

Questions for the Authors(s)
Questions:
It wasn't clear how much of the annotations are part of the dataset, and what part is collected as part of this paper.

Annotation collection: are all of 442 names provided as part of annotation task? how is the set of 442 names decided ?

L.317 - How are the same object instances known ? Is this part of the dataset ?

Some more statistics on the most frequent label being chosen as the entry level name -- what is the mininum percentage count of an entry-level name among all the labels of the corresponding object (e.g. left image in figure 1: 'bird' is more frequent with 27/35 fraction of all counts for that object. What is the avergae count ?

==================== ANSWER ====================
Q in Weaknesses: First, our goal is to predict the name of a particular object which humans would naturally use to name it. Mapping labels to "simpler ones" by means of a taxonomy contradicts this goal.

Q1: The set of names per object are part of the original ManyNames dataset (described in Related Work). All other annotations, i.e., the verifications including the name adequacy, were collected as part of this submission (described in Section 3 and the supplementary material).

Q2+Q3: The annotation task for the original ManyNames dataset was to "enter the first name that comes to mind" for an individual target object shown in an image and  marked by a bounding box. Hence, same object instances are part of the dataset, and each of them had up to 36 names annotated (Q3).  
(Q2:) These collected names were then verified with additional annotations (Section 3). The set of 442 names was directly derived from the annotations: we collected the most frequent name of each object instance (i.e., it's entry-level name), which amounts to an overall set of 442 names across the 25k object instances.

Q4: On average, the proportion of the entry-level name to all its names of an object is 75.2% (std=21.9%).
==================== ====================

==================== Review #2 ====================
What is this paper about, what contributions does it make, what are the main strengths and weaknesses?
Summary: The paper aims to predict for an image the entry-level name (natural name of an object that most people would use). The authors do this by building a image classification dataset where the labels are "entry-level" names on top of the ManyNames dataset. The authors present experiments to compares classification performance of pretrained computer vision models and shows that the models perform better at predicting entry-level names vs names from Visual Genome (VG).
Contributions:

Clean up the annotation of the ManyNames dataset so that 1) incorrect names are removed and 2) entry-level names can be extracted
Show standard object classifiers can learn good entry-level names and perform better on entry-level names
Show that models make more mistakes when human agreement is low
Strengths:

What name people choose to use to refer to an object is an interesting and important question
There is careful data collection and good error analysis
Weaknesses:

No insight into what makes a name a "entry-level" names
This is a paper that studies image classifier performance and provides little insight on the language aspect of the problem.
The conclusions are not surprising as the entry-level classification task (with 442 labels) should be easier than the visual-genome classification task (with many more names).
Reasons to accept
The dataset of "entry-level" names for objects in images could be of interest to the ACL commmunity
Reasons to reject
This paper is really more of a vision paper than one that is suited for ACL community.
The study of the classifier performance is not that interesting as it is basically an image classification problem
Overall Recommendation:	2
Missing References
Categorizing Concepts With Basic Level for Vision-to-Language Hanzhang Wang, Hanli Wang, Kaisheng Xu CVPR 2018

==================== ANSWER ====================
Thank you for the references we did miss to include.
==================== ====================

==================== Review #3 ====================
What is this paper about, what contributions does it make, what are the main strengths and weaknesses?
Existing object detection and image classification models achieved good performance on computer vision benchmarks. However, this system still has a gap to how human learn to call a object.
This paper presents a new task, object naming to bridge the gap between machine and human. The contributions of this paper are as follows.

(1) test and compare object detection and image classification models (ResNet, Faster-RCNN) at a new task of instance-based, entry-level object naming, i.e., the names people prefer when calling a specific object

(2) introduce a dataset called ManyNames with extensive quality control quantify both the adequacy of its names and the types of errors they contain.

(3) further shows that generic computer vision models not only contain the ability to provide entry-level names for objects but also can transfer-learn on ManyNames, to train entry-level naming models.

Reasons to accept
introduce both a new task object naming and a object naming data.
Reasons to reject
No exciting new technical idea provided.
Overall Recommendation:	3.5
Questions for the Authors(s)
L502: what is the last hidden layer before the output layer in FRCNN. Did the author talk about the resent backbone or the detection head?
Any reason not to use Facebook's maskrcnn benchmark? I guess it's that Anderson et al. already provided the model trained on VisualGenome?

Can we use and test the detector trained on COCO?

==================== ANSWER ====================

Q1+2: It's the last layer before the softmax layer over the object classes (i.e., the mean-pooled convolutional feature for the target bounding box).
Q3: We used Anderson et al.'s model for it being pre-trained on VisualGenome (and for being used (e.g., VilBERT, Lu et al. 2019) or compared to in other works in Language+Vision).  
==================== ====================

### 2020-02-17 papers/ACL2020/review_responses.txt
adds reviews + responses

@@
 ==================== ANSWER GENERAL ====================
-We thank all the reviewers for their reviews and comments!
+We are grateful to the reviewers for their time and comments!
 ==================== ====================
@@
 Thank you for the references we did miss to include.
+
+Generating/understanding the name humans would choose to name a particular object instance underlies a range of tasks in Language+Vision, and we therefore consider it relevant for the ACL community, of which Language+Vision has become an established subdiscipline.
 ==================== ====================

### 2020-02-17 papers/ACL2020/review_responses.txt

@@
 ==================== ANSWER ====================
-Q in Weaknesses: First, our goal is to predict the name of a particular object which humans would naturally use to name it.
-Mapping labels to "simpler ones" by means of a taxonomy contradicts this goal.
+Thanks for your questions which will help us improve the clarity of our paper.
 
-Q1: The set of names per object are part of the original ManyNames dataset (described in Related Work).
+Re weaknesses:
+  - First, our goal is to predict the name of a particular object which humans would naturally use to name it. Mapping labels to "simpler ones" by means of a taxonomy contradicts this goal.
+  - Please note that there is an entire section about the analysis/statistics of the dataset.
+The proportion of the entry-level name to all its names of an object is given in Table 1.
+(it is 75.2% (std=21.9%))
+
+Re questions:
+ - Q1: The set of names per object are part of the original ManyNames dataset (described in Related Work).
 All other annotations, i.e., the verifications including the name adequacy, were collected as part of this submission (described in Section 3 and the supplementary material).
-
-Q2+Q3: The annotation task for the original ManyNames dataset was to "enter the first name that comes to mind" for an individual target object shown in an image and  marked by a bounding box.
+- Q2+3: The annotation task for the original ManyNames dataset was to "enter the first name that comes to mind" for an individual target object shown in an image and  marked by a bounding box.
 Hence, same object instances are part of the dataset, and each of them had up to 36 names annotated (Q3).
-(Q2:) These collected names were then verified with additional annotations (Section 3).
+- Q4: These collected names were then verified with additional annotations (Section 3).
 The set of 442 names was directly derived from the annotations: we collected the most frequent name of each object instance (i.e., it's entry-level name), which amounts to an overall set of 442 names across the 25k object instances.
 
-Q4: On average, the proportion of the entry-level name to all its names of an object is 75.2% (std=21.9%).
 ==================== ====================
@@
 ==================== ANSWER ====================
-Thank you for the references we did miss to include.
+
+Thanks a lot for the remarks on linguistic analysis and additional references.
+
+We agree that it would be really interesting to establish what linguistic factors make a name an "entry-level" name.
+We see the experiments in this paper as a first step towards adressing this complex question and we believe that CV models are an obvious starting point to approach the task of object naming.
+In that sense, we believe that our results are not unsurprising as even CV models trained on object classes fair well at entry-level naming.
+Please note that the target vocabulary when tested on VisualGenome (VG) names and ManyNames is the same!
+So the plus in performance is not due to the number of labels, but to the properties of the data.
 
@@
 
+Thanks a lot for you comments. Indeed the paper does not contribute a new model, but we see its main contribution in the careful analysis of human and system annotation errors in a new task.
+
 Q1+2: It's the last layer before the softmax layer over the object classes (i.e., the mean-pooled convolutional feature for the target bounding box).

### 2020-02-17 papers/ACL2020/acl2020_main.tex
title

--- 2019-12-10 papers/ACL2020/acl2020_main.tex
@@
 \newcommand{\vg}{VisualGenome\xspace}
+\newcommand{\vgshort}{VG\xspace}
 \newcommand{\ra}{$\rightarrow$}
@@
 
-\title{From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects}
+\title{From Classification to Naming:\\ Modeling Entry-Level Names for Objects in Images}
 
@@
 \label{sec:experiments}
-\input{experiments}
+\input{experiments_merged}
 
@@
 In this paper, we have investigated instance-level entry-level naming of objects in images.
-To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
-as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
-For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
+To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale, thoroughly verified empirical basis, as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
+For models in \lv, the complexity of human naming data we observed brings up an important question: how should naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
 We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 

### 2020-02-17 papers/ACL2020/experiments_archive.tex

--- 2019-12-10 papers/ACL2020/experiments.tex
@@
 \begin{itemize}
-\item FRCNN$_{\text{VG1600}}$: This is \citep{anderson2018updown}'s model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
-The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized for a set of 1600 object names in \vg.
+\item FRCNN$_{\text{VG1600}}$: This is \citeauthor{anderson2018updown}'s~(\citeyear{anderson2018updown}) model\footnote{We used the code and model available at  \url{github.com/peteanderson80/bottom-up-attention}.
+The model is trained with an additional output over attributes, but we only use the object class prediction layer.} that is optimized on a set of 1600 object names in \vg.
 This set was obtained by first taking the 2500 most frequent names in \vg and then (manually) filtering certain names.
  \item  FRCNN$_{\text{MN442}}$: we pre-process the \vg data as in \citeauthor{anderson2018updown}, but restrict the object classes to the $442$~entry-level names found in \mn (Section~\ref{sect:mn_analysis}).
-For training, we use a PyTorch reimplementation of Faster. R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
+For training, we use a PyTorch reimplementation of Faster R-CNN\footnote{\url{github.com/jwyang/faster-rcnn.pytorch}}
 \end{itemize}

### 2020-02-20 analysis/wordnet_analysis_verified.py
print vg obj name, not synset

@@ -171,6 +171,7 @@ if __name__ == '__main__':
     total_relation_types = Counter()
     for i, row in verified_data.iterrows():
         relations = [(name, synset_word_relation(row['synset'], name, name_to_synset)) for name in row['names_to_be_counted'] if name != row['vg_obj_name']]
+        relations = [(t[0], (t[1][0], t[1][1], row['vg_obj_name'])) for t in relations]
         relations_types = [relation[1][0] for relation in relations]
         relations_tokens = list(chain(*[[relation[1][0] for _ in range(row['spellchecked'][relation[0]])] for relation in relations]))
 
@@ -182,9 +183,9 @@ if __name__ == '__main__':
         total_relation_tokens.update(relations_tokens)
         total_relation_types.update(relations_types)
 
-    ## Print examples of no-relation:
-    # rel_not_covereds = Counter(rel_not_covereds).most_common(9999)
-    # print('\n'.join([str(x[0]) + ' ' + str(x[1]) for x in rel_not_covereds]))
+    # Print examples of no-relation:
+    rel_not_covereds = Counter(rel_not_covereds).most_common(9999)
+    print('\n'.join([str(x[0]) + ' ' + str(x[1]) for x in rel_not_covereds]))
 
 
     print()

### 2020-02-25 papers/LREC2020/analysis.tex
adds TODOS (in reviews.txt) and small fixes

@@
 Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
-Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps reduced uncertainty.
+Note that pointing gestures in natural communication are as referentially uncertain as bounding boxes, if not more; however, typically those gestures are grounded in a specific discourse context, which helps to reduce uncertainty.
 In future work, we plan to filter out these cases.

### 2020-02-25 papers/LREC2020/background.tex
adds TODOS (in reviews.txt) and small fixes

@@
 For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
-The effect of such distractor objects on the production of referring expressions has been looked at a lot in the language generation community \cite{krahmer:2012}, though not specifically for object naming.
+The effect of such distractor objects on the production of referring expressions has been widely examined in the language generation community \cite{krahmer:2012}, though not specifically for object naming.
 We believe that our new dataset provides an interesting resource for tackling this question.
@@
 Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
-The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology where automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
+The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
 Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
@@
     \midrule
-    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
-    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
+    \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
+    naming vocab size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
     av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\

### 2020-02-25 papers/LREC2020/conclusion.tex
adds TODOS (in reviews.txt) and small fixes

@@
 Our data provides a first step towards enabling model evaluation on naming variants of an instance, checking, e.g.,\ to what extent the top N predicted names are valid alternatives (\word{dog, animal, pet}) or not (\word{dog, hat, grass}).
-However, to fully enable this sort of analysis, a further annotation step is needed, to account for the referential uncertainty of bounding boxes and annotation noise.
+However, to fully enable this kind of analysis, a further annotation step is needed, to account for the referential uncertainty of bounding boxes and annotation noise.
 We plan to take this step in future work, which will also enable more robust conclusions with respect to naming variation.

### 2020-02-25 papers/LREC2020/data-collection.tex
adds TODOS (in reviews.txt) and small fixes

@@
 \vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
-Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which affords analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
+Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which allows for analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
 % The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).

### 2020-02-25 papers/LREC2020/intro.tex
adds TODOS (in reviews.txt) and small fixes

@@
 At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
-A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures, as e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
 
@@
 To address this shortcoming, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vgenome.%
-\footnote{The dataset will be available upon publication.}
+\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
 The number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V.

### 2020-02-25 papers/LREC2020/survey.tex
adds TODOS (in reviews.txt) and small fixes

@@
 
-One of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
+Some of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
 Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
@@
 %This is a figure with a caption.}}
-\includegraphics[scale=0.4]{figures/vulture.png} 
+\includegraphics[scale=0.32]{figures/vulture.png} 
 \begin{tabular}{lp{6cm}}

### 2020-02-28 papers/LREC2020/intro.tex
Gemma's to-do done :)

--- 2019-11-30 papers/LREC2020/intro.tex
@@
-Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers naturally talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
-Data collections in L\&V are typically set up as free annotation tasks,  where subjects are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue), which naturally results in linguistic variation.
-For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
+% SUBMITTED VERSION:
+% Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers naturally talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
+% Data collections in L\&V are typically set up as free annotation tasks,  where subjects are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue), which naturally results in linguistic variation.
+% For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.
 
-Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
-For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
-Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
-At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
-A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures, as e.g.\ \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}.
+% GBT revision (I've re-organized the material into paragraphs differently and gone more directly to object names):
+A central issue in Language \& Vision (L\&V) is how speakers refer to objects. 
+This is most prominent for referring expression generation and interpretation [REFS], but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue [REFS].
+One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} `cake', `food', `bread', or `dessert', a.o.
+This aspect of reference has been understudied in Computational Linguistics and L\&V; as a consequence, it is not clear to what extent current L\&V models capture human naming behavior.
+% the factors affecting the choice of a name are far from clear, as is the potential of current L\&V models to successfully model naming data.
 
-In this paper, we present ManyNames, a dataset with substantial amounts of object names per object for real-world images.
-We start by surveying existing resources in L\&V that provide object names: \refcoco \cite{Yu2016}, a collection of referring expressions, \flickr \cite{plummer2015flickr30kentities}, which provides region-to-phrase linkings for Flickr 30K captions \cite{young:2014}, and \vgenome \cite{krishna2016visualgenome}, which features extensive region-level annotations.
+% SUBMITTED VERSION:
+% In this paper, we present ManyNames, a dataset with substantial amounts of object names per object for real-world images.
+% We start by surveying existing resources in L\&V that provide object names: \refcoco \cite{Yu2016}, a collection of referring expressions, \flickr \cite{plummer2015flickr30kentities}, which provides region-to-phrase linkings for Flickr 30K captions \cite{young:2014}, and \vgenome \cite{krishna2016visualgenome}, which features extensive region-level annotations.
 We highlight their potential contributions to the study of object naming, and also argue that the low number of annotations per item prevents reliable assessment or linguistic analysis of object-specific preferences and naming variation.
+% GBT revision:
+In this paper, we present a new dataset, ManyNames, to enable research on both analysis and modeling of human naming behavior. 
+We start by surveying existing existing resources in L\&V that provide object names,
+assessing their potential to contribute to the study of object naming.
+While these resources can be exploited for this area of inquiry to some extent (as detailed in the survey), we argue that the low number of annotations per item prevents reliable assessment of naming preferences, on the one hand, and variation, on the other, which is what we are interested in.
+This motivates the development of ManyNames, as well as our design choices for it.
+
+% SUBMITTED VERSION:
+% Compared to experimental work on perception and language grounding, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
+% For instance, picture naming norms used in Psycholinguistics record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+% Consequently, a reliable assessment of inter-annotator agreement, speaker preferences, and a deeper linguistic analysis of the observed variation is mostly not possible with available data collections in  L\&V.
+% At the same time, these datasets have much potential for research on these topics, as they provide more realistic images of real-world objects and scenes than the idealized drawings used in picture naming norms (see Figure \ref{fig:cake}), as well as a wider coverage of object categories.
+% A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+ManyNames v.1, the version presented in this paper, contains 36 crowd-sourced names for 25K instances from \vgenome \cite{krishna2016visualgenome}.%
+\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
+It is inspired in naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
+ManyNorms is much larger and uses real images of objects in complex visual contexts, in contrast to idealized drawings (Figure \ref{fig:cake}, right), which makes it suitable for research in L\&V.
+%Moreover, our images show objects in complex visual contexts,
+%unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and %unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
+% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
+% Naming norms in Psycholinguistics are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right).
+% \gbt{TODO: add footnote with the naming norms that have real images?}
+% ManyNames is much larger and, crucially, is based on real images and 
+Names are sometimes used as object labels in Computer Vision, in large datasets with real-world images; however, compared to experimental work on perception and language grounding, recent data collections in L\&V capture a rather limited amount of data; for instance, captioning or referring expression data sets typically provide 2-5 annotations per object \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+\gbt{Is the latter redundant?}
 
@@
 
-To address this shortcoming, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vgenome.%
-\footnote{The dataset will be available upon publication.}
-The number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V.
-%Moreover, our images show objects in complex visual contexts,
-%unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and %unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
+% NEW -- I thought we needed to include this discussion, too.
+Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
+However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion [REFS], we believe there is value in modeling object names on their own.
+Questions that need addressing regarding this topic are 1) what factors drive the choice of a name, 2) how much variation in naming do we find and what factors drive this variation (object category?
+individual properties of the object?
+context?), 3) what aspects of naming pose difficulties for models in L\&V.
+ManyNames enables research on these questions; here, for reasons of scope and space, we will provide only preliminary results on the amount and type of variation we find in the data. 
+ManyNames can also potentially inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the so-called basic-level name \textit{cake}, see Section \ref{subsec:rosch} for further explanation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \textit{cake}, corresponding to the so-called basic-level category, see Section \ref{subsec:rosch} for further explanation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
 

### 2020-03-04 papers/LREC2020/intro.tex
LREC paper: polish intro, adding refs; a few questions remain

@@
 A central issue in Language \& Vision (L\&V) is how speakers refer to objects. 
-This is most prominent for referring expression generation and interpretation [REFS], but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue [REFS].
-One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} `cake', `food', `bread', or `dessert', a.o.
+This is most prominent for referring expression generation and interpretation~\cite{Kazemzadeh2014,mao15,Yu2016}, but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue \cite{fangetal:2015,devlin:imcaqui,das2017visual,vries2017guesswhat}.
+One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} `cake', `food', or `dessert', a.o.
 This aspect of reference has been understudied in Computational Linguistics and L\&V; as a consequence, it is not clear to what extent current L\&V models capture human naming behavior.
@@
 We highlight their potential contributions to the study of object naming, and also argue that the low number of annotations per item prevents reliable assessment or linguistic analysis of object-specific preferences and naming variation.
+
 % GBT revision:
-In this paper, we present a new dataset, ManyNames, to enable research on both analysis and modeling of human naming behavior. 
-We start by surveying existing existing resources in L\&V that provide object names,
+In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
+We start by surveying existing resources in L\&V that provide object names,
 assessing their potential to contribute to the study of object naming.
-While these resources can be exploited for this area of inquiry to some extent (as detailed in the survey), we argue that the low number of annotations per item prevents reliable assessment of naming preferences, on the one hand, and variation, on the other, which is what we are interested in.
+While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey}), we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
 This motivates the development of ManyNames, as well as our design choices for it.
@@
 \footnote{Available at \url{https://github.com/amore-upf/manynames}.}
-It is inspired in naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
-ManyNorms is much larger and uses real images of objects in complex visual contexts, in contrast to idealized drawings (Figure \ref{fig:cake}, right), which makes it suitable for research in L\&V.
-%Moreover, our images show objects in complex visual contexts,
+It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
+\gbt{Is it ``picture naming norms'', or ``naming norms''?}
+% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
+Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right); ManyNames is much larger and uses real images of objects in complex visual contexts, which makes it suitable for research in L\&V.
+\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
+
+% From Andreas Mädebach:
+
+% the most comprehensive naming norms (I am aware of) are these:
+
+% ***MultiPic***
+% - https://www.bcbl.eu/databases/multipic
+% - 750 colored line drawings, normed across different languages (incl. English)
+% - available data includes also the non-dominant names per image
+
+% ***BOSS***
+% - https://sites.google.com/site/bosstimuli/
+% - 1468 foto objects, normed in English
+% - available data includes only dominant names per image
+
+% ***IPNP***
+% - https://crl.ucsd.edu/experiments/ipnp/
+% - 520 black-white drawings, normed across different languages (incl. English)
+% - available data includes only dominant names per image
+
+% I expect that all three of these databases will cover most of the "high-agreement" names in the manyNames data set (when I have access to these data I can check that).
+MultiPic (non-dominant names also available) and BOSS (photos) seem to be the most interesting to me for comparisons with the manyNames data.
+
+% There exist many more norm data sets for different languages and for special purposes (morphologically complex names, manipulable objects, depicting actions, naming by children, etc.).
+Many of these data sets use line drawings (often partially based on the original Snodgrass & Vanderwart set), but there also some with photos which might be interesting in addition to the BOSS database (e.g., https://doi.org/10.1371/journal.pone.0037527).
+
+% Moreover, our images show objects in complex visual contexts,
 %unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and %unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).
-% Naming norms record naming responses for dozens or hundreds of speakers for the same object.
-% Naming norms in Psycholinguistics are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right).
-% \gbt{TODO: add footnote with the naming norms that have real images?}
-% ManyNames is much larger and, crucially, is based on real images and 
-Names are sometimes used as object labels in Computer Vision, in large datasets with real-world images; however, compared to experimental work on perception and language grounding, recent data collections in L\&V capture a rather limited amount of data; for instance, captioning or referring expression data sets typically provide 2-5 annotations per object \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
-\gbt{Is the latter redundant?}
+% Names are sometimes used as object labels in Computer Vision, in large datasets with real-world images; however, compared to experimental work on perception and language grounding, recent data collections in L\&V capture a rather limited amount of data; for instance, captioning or referring expression data sets typically provide 2-5 annotations per object \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
+% \gbt{Removing the latter cause I find it redundant}
 
@@
 Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
-However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion [REFS], we believe there is value in modeling object names on their own.
-Questions that need addressing regarding this topic are 1) what factors drive the choice of a name, 2) how much variation in naming do we find and what factors drive this variation (object category?
+However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, we believe there is value in modeling object names on their own.
+Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category?
 individual properties of the object?
-context?), 3) what aspects of naming pose difficulties for models in L\&V.
-ManyNames enables research on these questions; here, for reasons of scope and space, we will provide only preliminary results on the amount and type of variation we find in the data. 
-ManyNames can also potentially inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}, 2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
+% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \textit{cake}, corresponding to the so-called basic-level category, see Section \ref{subsec:rosch} for further explanation) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \textit{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
 

### 2020-03-11 papers/LREC2020/intro.tex
comments to intro

@@
 assessing their potential to contribute to the study of object naming.
-While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey}), we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
+While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
 This motivates the development of ManyNames, as well as our design choices for it.
@@
 % A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
-ManyNames v.1, the version presented in this paper, contains 36 crowd-sourced names for 25K instances from \vgenome \cite{krishna2016visualgenome}.%
+ManyNames v.1, the version\cs{would remove "the version"} presented in this paper, contains 36 crowd-sourced names for 25K object instances from \vgenome \cite{krishna2016visualgenome}.%
 \footnote{Available at \url{https://github.com/amore-upf/manynames}.}
 It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
-\gbt{Is it ``picture naming norms'', or ``naming norms''?}
+%\gbt{Is it ``picture naming norms'', or ``naming norms''?}
 % Naming norms record naming responses for dozens or hundreds of speakers for the same object.
-Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right); ManyNames is much larger and uses real images of objects in complex visual contexts, which makes it suitable for research in L\&V.
+Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real images of objects in complex visual contexts, which makes it suitable for research in L\&V.
 \gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
+\cs{see the addition in ref to Figure}
 

### 2020-03-12 papers/LREC2020/background.tex
LREC paper, small change in table 1
LREC paper: polish intro, adding refs; a few questions remain
small changes here and there.

@@
 
-The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
+The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left'').\cs{rephrase}
 Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.
@@
 Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}.
-This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
-However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).
+This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \word{bird}, \word{car}), as opposed to more generic (super-ordinate,\ e.g., \word{animal}, \word{vehicle}) or more specific categories (sub-ordinate,\ e.g., \word{sparrow}, \word{convertible}).
+However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \word{penguin} and not \word{bird}; \newcite{jolicoeur1984pictures}).
 
 %This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
-While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
+While the traditional notion of entry-level categories suggests that objects tend to be named by a \textit{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
 %Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
-For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers.
+For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \word{rottweiler}, \word{beagle}) is potentially preferred by speakers.
 The effect of such distractor objects on the production of referring expressions has been widely examined in the language generation community \cite{krahmer:2012}, though not specifically for object naming.
@@
 
-The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
-This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
+The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lives are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}.
+This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.,~\word{meat, vegetable}) or script-based (e.g.,~\word{breakfast, snack}).
 We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the most frequent source of variation in our data.
@@
 
-In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems localize and classify objects into thousands of different categories  \cite{googlenet,ILSVRC15}.
+In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems identify objects by classifying them into thousands of different categories  \cite{googlenet,ILSVRC15}.
 Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
 The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
-Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
+Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}.\cs{double-check latter}
 Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
@@
 \subsection{Object Naming in L\&V} 
+Previous work in L\&V has collected and used datasets where annotators produced free and natural utterances for a given image. 
+These datasets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}.
+While object names occur in all of these datasets, they are not necessarily marked up and linked to the corresponding image regions.
+The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names of objects to their regions is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
 
-Previous work in L\&V has collected and used data sets where annotators produced free and natural utterances for a given image. 
-Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}.
-While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions.
-The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.
-
-Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V data sets.
-This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.
+Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V datasets.
+This controlled collection procedure allowed us to elicit many names for the same object from different annotators, resulting in a dataset that is amenable to  studying systematically and on a large scale the core phenomena of object naming, viz.
+naming variation and preferences.\cs{rephrase}
 
@@
     \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
-    naming vocab size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
+    name vocabulary size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
     av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
-    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
-    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
+    ratio of objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
+    av. name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
     \bottomrule
   \end{tabular}
-  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
+  \caption{Overview statistics for different datasets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
 \end{table*}

### 2020-03-12 papers/LREC2020/conclusion.tex
small changes here and there.

@@
 
-For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
-Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.
+For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object recognition and naming.
+Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.
 
@@
 
-With respect to naming variation, our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
+%With respect to naming variation, our
+Our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
 It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.

### 2020-03-12 papers/LREC2020/data-collection.tex
small changes here and there.

--- 2019-11-30 papers/LREC2020/data-collection.tex
@@
 
+\iffalse
 \begin{table*}[htp]
@@
 \end{table*}
+\fi
+
+\begin{figure*}[htp]
+	\centering
+	\includegraphics[height=.8\columnwidth]{figures/distr_imgs-per-domain_VG.png}
+	\caption{Overview of the number of images and names per domain in ManyNames.}
+	\label{fig:overview_dataset1}
+\end{figure*}
 
@@
 
-We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
+We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,~the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
 \vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
-Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which affords analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
+Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which allows for analysis possibilities that we will exploit in Section~\ref{sec:analysis}.
 % The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).
@@
 We selected images from seven domains: \domain{animals\_plants}, \domain{buildings}, \domain{clothing}, \domain{food}, \domain{home}, \domain{people}, \domain{vehicles}. 
-They are all based on McRae et al.'s  \cite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
+They are all based on McRae et al.'s~\shortcite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
 % We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\domain{animals}, \domain{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
@@
 
-Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \domain{home}).
-Instead, we defined a set of 52 synsets (listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.
+Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \word{dog} and \word{cow} are both mammals, but \word{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.,~\domain{home}).
+Instead, we defined a set of $52$~synsets (listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.
 
@@
 %which \vg objects get diverse names.
-For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
+For example, \vg instances subsumed by McRae's \word{dog} were named \word{dog, beagle, greyhound, bulldog}, etc., while McRae's \word{duck}, \word{goose}, or \word{gull} did not have name variants in \vg, so we kept \word{dog} and \word{bird} (which subsumes \word{duck}, \word{goose}, or \word{gull}) as collection synsets.
 %\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}
@@
 We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them.
-We refer to the names obtained as \textit{seeds} ($450$\ in total).
+We refer to the names obtained as \textit{seeds} ($450$~in total).
 %\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
-We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}).
+We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\word{pink bird}).
 We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
@@
 % \paragraph{Sampling of instances}
-Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds.
-This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
-Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains. 
+Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$~instances for seeds with up to $800$~objects, and up to $1$K~instances for larger seeds.
+This yielded a dataset of $31,093$~instances, which was further pruned during annotation, as explained next.
+Table~\ref{tab:overview_dataset1} shows the top $5$~\vg names in each of the domains. 
 %\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}
@@
 In initial pilot studies, we found object identification via bounding boxes to be problematic.
-In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
+In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (e.g.,~for a box around a jacket, the man wearing it).
 We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning images with unclear boxes or occluded objects via an initial collection round in which we allowed workers to mark such cases.
-Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which 9 workers annotated each image.
+Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which $9$~workers annotated each image.
 
 %We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
-After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
-This yielded $25,596$ images (we discarded $5,497$).
-We then did 3 more collection rounds, obtaining a total of 36 images per object.
+After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were chosen by manually inspecting the remaining and discarded instances, respectively, depending on different threshold values): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most~$17$\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
+This yielded $25,596$~images (we discarded~$5,497$).
+We then did ~3~more collection rounds, obtaining a total of $36$~annotations per object.
 Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
 We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
-Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
+Overall $841$~workers\footnote{Participation was restricted to residents of the UK, USA, Canada, New Zealand, and Australia.} took part in the data elicitation, with a median of  $261$~instances \mbox{($\textrm{range}=[9,17K]$)} per worker.
 

### 2020-03-12 papers/LREC2020/lrec2020naming.tex
small changes here and there.

@@
 We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average.
-At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
+At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed at length in the theoretical literature, and other less well studied phenomena like cross-classification\cs{Should we keep this term?
+(@GBT cf.
+discussion with A.
+Maedebach)} (\word{cake} vs.\ \word{dessert}).
 % may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
@@
 
-\section{Object Names in Existing L\&V resources}
+\section{Object Names in Existing L\&V Resources}
 \label{sec:survey}
@@
 
-%\section{Acknowledgements}
-
+\section{Acknowledgments}
+We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
+ This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
+ % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
+ This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
+ \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
 % Place all acknowledgements (including those concerning research grants and

### 2020-03-12 papers/LREC2020/survey.tex
small changes here and there.

@@
 
-Table \ref{tab:compare} shows that the multiple annotations ($2.84$\ on average) actually contain a considerable amount of variation in naming (almost 2 different names on average per object).
-However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement.
+Table~\ref{tab:compare} shows that the multiple annotations ($2.8$~on average) actually contain a considerable amount of variation in naming (almost~$2$ different names on average per object). 
+%However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement. 
+However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement. \cs{double-check formulation}
 
@@
 Hence, so-called distractor objects  \cite{krahmer:2012} and their names cannot be analyzed systematically.
-Also, while in \refcoco the elicited names can assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
-Finally, the set of categories in MSCOCO included is quite small ($80$~COCO categories).
+Also, while in \refcoco the elicited names can be assumed to be natural, it is unclear how the additional constraints in \refcocop impact on the naturalness of object naming.
+Finally, the underlying set of MS COCO categories is quite small ($80$~categories).
 To sum up, \refcoco is suitable for generally modeling referring expressions in context for a restricted set of categories, but less appropriate for analyzing object naming at a large scale.
@@
 % We estimate this distance as the minimal path length of all synsets of a word  to the root node.
-% Table \ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
+% Table~\ref{tab:specnames} shows the estimated levels of specificity for object names in the \refcoco data set.
 % We observe distances to the root between 2 and 17, meaning that there is a much more fine-grained distinction of levels than the three-way classification adopted in \cite{graf2016animal}.
@@
 
-This dataset has three main differences with respect to \refcoco/+: (i) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (ii) the images and the production of entity mentions were not subject to any constraints; (iii) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table\ \ref{tab:compare}).
+This dataset has three main differences with respect to \refcoco/+: (i) the entity mentions were obtained via an image description task (captioning), as opposed to a referential task; (ii) the images and the production of entity mentions were not subject to any constraints; (iii) a much wider range of categories are covered (cf.\ the number of objects and the vocabulary size in Table~\ref{tab:compare}).
 %\gbt{Any idea what kind of categories are covered in \flickr?}
@@
 The data collection followed a complex procedure, involving many different rounds of annotation.
-The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure \ref{fig:bird}).
+The first round of the procedure, and the basic backbone for the further rounds, is a collection of region-based descriptions: workers were asked to describe regions in the image and draw boxes around the corresponding area in the image (for examples, see Figure~\ref{fig:bird}).
 
@@
 
-Some of the main advantages of \vg are its size, with 3.8 million objects ($108$K images) as opposed to 50K and 243K for the other two datasets, and its category coverage, with a vocabulary of object names of 105K compared to 5K/10K.
-Another is the fact that it in principle provides exhaustive annotations of objects in the image, often with several region descriptions and possibly object names per object.
+Some of the main advantages of \vg are its size, with $3.8$~million objects ($108$K images) as opposed to $50$K and $243$K for the other two datasets, and its category coverage, with a vocabulary of object names of $105$K compared to $5$K/$10$K.
+Another plus is the fact that it in principle provides exhaustive annotations of objects in an image, often with several region descriptions and possibly object names per object.
 This should make it easier to identify factors intervening in naming choices, and to model contextual aspects that may affect them, than in the case of \refcoco.
 
-However, there is a crucial pitfall: As Figure \ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
+However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
 Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird.
-This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
-For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
-The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
-We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).
+%This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
+%For instance, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
+Finally, even though there is a different name (\word{vulture}) for \word{bird} in Figure~\ref{fig:bird}, the annotation suggests that \word{bird} is the only available name. 
+Hence, the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
+The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($5$\%) seem to be an effect of this partial linking problem.
+We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.,~truly overlapping objects).
 
-Table \ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of annotations per object (7). 
-We think that this might be an effect of our category selection procedure explained in Section \ref{sec:data}.
+Table~\ref{tab:compare} also shows the statistics for the subset of those VG objects that we selected for ManyNames and, here, we find a considerably higher average of $7$~annotations per object. 
+We think that this might be an effect of our category selection procedure explained in Section~\ref{sec:data}.
 However, interestingly, the portion of objects that have different names associated with them is still extremely small.
-Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names (70\%).
+Note that in contrast, even though RefCOCO has much less annotations per object, there are many objects with different names ($70$\%).
 
@@
 The VG data, to the contrary, seems to indicate that the vast majority of objects should only be associated with a single name, but it is difficult to estimate to what extent this finding results from problems with annotation (partial linking).
-This shows that to be able to analyze object naming in more detail, we simply need naming data from many subjects for the same objects. 
+This shows that to be able to analyze object naming in more detail, it is crucial to have naming data from many subjects for the same objects. 
 Also, dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.

### 2020-03-12 papers/LREC2020/survey.tex
lrec camera ready, correcting 2 small issues identified by Carina

--- 2020-02-25 papers/LREC2020/survey.tex
@@
 For instance, even though there is a different name (\textit{vulture}) for \textit{bird} object in Figure \ref{fig:bird}, the annotation suggests that \textit{bird} is the only available name. 
-The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (5\%) seem to be an effect of this partial linking problem.
+The relatively low number of annotations per objects in VisualGenome (1.7 on average) shown in Table \ref{tab:compare} and the very small number of objects that have more than one name associated with it (2\%) seem to be an effect of this partial linking problem.
 We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.\ truly overlapping objects).

### 2020-03-12 papers/LREC2020/survey.tex
solve conflict with Sina

--- 2020-03-12 papers/LREC2020/survey.tex
@@
 Hence, the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
-The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($5$\%) seem to be an effect of this partial linking problem.
+The relatively low number of $1.7$~annotations per objects on average in VG (Table~\ref{tab:compare}) and the very small number of objects that have more than one name associated with it ($2$\%) seem to be an effect of this partial linking problem.
 We experimented with filtering and merging bounding boxes based on overlap, but this would introduce substantial noise into the data (e.g.,~truly overlapping objects).

### 2020-03-12 papers/LREC2020/lrec2020naming.tex
updates acklowledgements

@@
 We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
- This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
+ This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154) and by the Catalan government~(SGR 2017 1575).
  % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
  This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
- \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
+ %\hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
+ \begin{flushright}
+ 	\vspace{-2ex}
+ 	\includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
+ \end{flushright}
+
 % Place all acknowledgements (including those concerning research grants and

### 2020-03-12 papers/LREC2020/survey.tex
merge

--- 2020-03-12 papers/LREC2020/survey.tex
@@
 2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
-2385747 & small white beak of \textbf{bird}\\
+%2385747 & small white beak of \textbf{bird}\\
 2681429 & a semi \textbf{long beak}\\  

### 2020-03-12 papers/LREC2020/analysis.tex

@@
 
-As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous datasets: 35.3 on average, compared to 1-7.
-It also contains the most variability, since objects have on average 5.7 names (compared to 1-1.9).
+As shown in Table~\ref{tab:compare} above, ManyNames gathers many more names per object than previous datasets: $35.3$~on average, compared to~$1-7$.
+It also contains the most variability, since objects have on average $5.7$~names (compared to~\mbox{$1-1.9$}).
 Figure~\ref{fig:ex-high-low-agreement} shows some example datapoints of ManyNames with high and low name agreement.
@@
 shows high potential use for studying the degree of inter-subject naming agreement, and what factors influence variation.
-Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same bounding box.
+Data analysis shows that object identification remains an issue in our data, though: Despite our care in filtering out objects that are occluded or have unclear bounding boxes (see\ Section~\ref{sec:data}), we still find many examples where annotators identified different objects for the same box.
 Typically, workers named an adjacent object or one supported by the target object (such as \word{toy/book} instead of \word{bed} in Fig.~\ref{fig:ex-high-low-agreement}, image K), or a part of the target object.
-While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the bounding box, as in the \word{bed/sleeping bag} case in Fig.~\ref{fig:ex-high-low-agreement} (image L).
+While some of these cases are arguably annotation errors, in many cases it is not possible to distinguish which object is being indicated by the  box, as in the \word{bed/sleeping bag} case in Fig.~\ref{fig:ex-high-low-agreement} (image L).
 Referential uncertainty of this kind is a roadblock for the use of L\&V resources to study naming variation.
@@
 
-\subsection{Naming variation and agreement}
+\subsection{Naming Variation and Agreement}
 \label{subsec:counts}
@@
 With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
-This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which includes names that have at least frequency 2.
+This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
 The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
-Thus, in our data objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, and at the same time there is variation.
+Hence, in our data, objects tend to have a preferred name, as expected from work in Psychology \cite{rosch1976basic,jolicoeur1984pictures}, but at the same time there is variation.
 
@@
 % & \multicolumn{5}{c}{Instance-level agreement} \\
-  domain &    N &         \%top (std) &          H (std) & t=VG &   \%VG \\
+  Domain &    N &         \%top (std) &          H (std) & t=VG &   \%VG \\
   \midrule
@@
 \vspace{-0.3cm}
-\caption{Agreement in object naming, with a frequency threshold of 2.}
+\caption{Agreement in object naming, with a frequency threshold of~$2$.}
 % Domain `an\_pl' is animal\_plants.}
@@
 
-To further assess agreement on the object names, we check the following measures, computed with $t=2$, with results in Table~\ref{tab:agree}:
+To further assess agreement on the object names, we check the following measures, computed with \mbox{$t$=$2$}, with results in Table~\ref{tab:agree}:
 \begin{itemize}
-\item \textbf{N}: the average number of types in the response set of ManyNames.
+\item \textbf{N}: the average number of types in the response set. %of ManyNames.
 \item \textbf{\% top}: the average relative frequency of the most frequent response (shown in percent).
-\item \textbf{$H$}: the $H$ agreement measure from \cite{snodgrass}, where 0 is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
-where $k$\ denotes the number of name types and $p_i$\ is the proportion of name type\ $i$ in the responses. 
+\item $\mathbf{H}$: the $H$ agreement measure from \cite{snodgrass}, where $0$~is perfect agreement: \mbox{$H = \sum_{i=1}^k p_i~log_2\frac{1}{p_i}$}, 
+where $k$~denotes the number of name types and $p_i$~is the proportion of type~$i$ in the responses. 
 \item \textbf{t=VG}: the percentage of items where the top response in ManyNames is the \vg name.
@@
 
-Apart from the trends mentioned above, it is remarkable that only in 73\% of the cases the most frequent response coincides with the \vg name, and the \vg name accounts for 63\% of the responses on average.
+Apart from the trends mentioned above, it is remarkable that only in $73$\%~of the cases the most frequent response coincides with the \vg name, and the \vg name accounts for $63$\%~of the responses on average.
 Our dataset can be expected to yield a more robust estimate for so-called entry-point names \cite{jolicoeur1984pictures}, that is, the name that most naturally comes to mind for a given object.
-The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of\ $0.55$), which can be expected when using real images.
+The $H$ measures indicate a fair amount of agreement, a bit lower than in picture norming studies on artificial idealized images (e.g.\ \newcite{snodgrass} report an average $H$ of~$0.55$), which can be expected when using real images.
 
@@
 This indicates that agreement varies quite a bit across instances, with factors that cannot be attributed to domain only.
-The qualitative examples in Figure \ref{fig:ex-high-low-agreement} illustrate this, showing visual instances with very high or low agreement.
+The qualitative examples in Figure \ref{fig:ex-high-low-agreement} illustrate this, showing instances with very high or low agreement.
 These suggest that instances which are more prototypical of a category trigger higher agreement, although further research is necessary to examine the relevant factors.
@@
 
-\subsection{Sources of variation}
+\subsection{Sources of Variation}
 \label{subsec:sources}
@@
 To obtain these data, we exploited the synset annotation in the \vg names, and added automatic linking for the additional ManyNames names, with a simple first-sense heuristic.%
-\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of 10; the other relations are straightforward.
-The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).}
+\footnote{To detect hypernyms, we use the hypernym closure of the synset with a depth of $10$; the other relations are straightforward.
+The coverage of WordNet for our name data is satisfactory ($90$\%\ of the name types, accounting for $97$\%\ of the tokens).}
 As shown in the table, in the vast majority of cases, no hierarchical relation between the name and the synset can be retrieved from WordNet.
@@
 In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
-\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \textit{toast/dessert}, image C).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\textit{bed/bench}, images J).
-\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\textit{burger/basket}, image B).
-\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\textit{robe/dress}, image not shown).
+\textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \word{toast/dessert}, image C).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, images J).
+\textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\word{burger/basket}, image B).
+\textbf{Issues with WordNet}: due to WordNet's fine-grained hierarchy, it is difficult to retrieve certain loose synonyms or hypernyms (\word{robe/dress}, image not shown).
 %As it is non-trivial to separate these phenomena, we leave a quantitative analysis for future work.
 %
+\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
 \begin{table}[t]
@@
 % At the same time, compared to annotation and modeling frameworks in Computer Vision that frame the problem as an object labeling task, our data shows a much lower agreement than what should be expected if object names were indeed entirely canonical,
-See e.g.\ the ResNet which achieves a top-1 error rate of 25\% on ILSVRC 2015.
+See e.g.\ the ResNet which achieves a top-1 error rate of $25$\% on ILSVRC 2015.
 \gbt{It is not clear to me what this means: what kind of data is this?

### 2020-03-12 papers/LREC2020/intro.tex

@@
 This is most prominent for referring expression generation and interpretation~\cite{Kazemzadeh2014,mao15,Yu2016}, but it also pervades virtually any other L\&V task, such as caption generation or visual dialogue \cite{fangetal:2015,devlin:imcaqui,das2017visual,vries2017guesswhat}.
-One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} `cake', `food', or `dessert', a.o.
+One of the central components of referring expressions are \textit{object names}; for instance, speakers may name the left object in Figure \ref{fig:cake} \word{cake}, \word{food}, or \word{dessert}, a.o.
 This aspect of reference has been understudied in Computational Linguistics and L\&V; as a consequence, it is not clear to what extent current L\&V models capture human naming behavior.
@@
 % Naming norms record naming responses for dozens or hundreds of speakers for the same object.
-Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure \ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real images of objects in complex visual contexts, which makes it suitable for research in L\&V.
-\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
-\cs{see the addition in ref to Figure}
+Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure~\ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
+%\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
+%\cs{see the addition in ref to Figure}
 
@@
 Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
-However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, we believe there is value in modeling object names on their own.
+However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, \cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too} we believe there is value in modeling object names on their own.
 Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category?
@@
 
-The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \textit{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \textit{dessert} highlights a different facet of the object.
+The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \word{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \word{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \word{dessert} highlights a different facet of the object.
 

### 2020-03-12 papers/LREC2020/data-collection.tex
shortens Gemma's new intro

@@
 
-\begin{figure*}[htp]
+\begin{figure}[htp]
 	\centering
-	\includegraphics[height=.8\columnwidth]{figures/distr_imgs-per-domain_VG.png}
-	\caption{Overview of the number of images and names per domain in ManyNames.}
+	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VG.png}
+	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
 	\label{fig:overview_dataset1}
-\end{figure*}
+\end{figure}
 

### 2020-03-12 papers/LREC2020/intro.tex
shortens Gemma's new intro

@@
 
+% NEW -- I thought we needed to include this discussion, too.
+%Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
+%However, in 
+In the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion, for which systems are required  to integrate and reason over the visual scene and context objects in which an object is presented, %\cite{Kazemzadeh2014,mao15,Yu2016},
+%\cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too}
+we believe there is value in modeling object names on their own. 
+Specifically, questions that need addressing regarding object naming are (1)~how much naming variation is attested and what factors drive the choice of a name (object category?
+individual properties of the object?
+context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}; (2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+%\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
+% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
+
 % GBT revision:
 In this paper, we present a new dataset, ManyNames, to provide richer possibilities for both analysis and modeling of human naming behavior. 
-We start by surveying existing resources in L\&V that provide object names,
-assessing their potential to contribute to the study of object naming.
-While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
-This motivates the development of ManyNames, as well as our design choices for it.
+%We start by surveying existing resources in L\&V that provide object names, assessing their potential to contribute to the study of object naming.
+%While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
+Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
+We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
+%This motivates the development of ManyNames, as well as our design choices for it.
 
@@
 % A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
-ManyNames v.1, the version\cs{would remove "the version"} presented in this paper, contains 36 crowd-sourced names for 25K object instances from \vgenome \cite{krishna2016visualgenome}.%
+ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
 \footnote{Available at \url{https://github.com/amore-upf/manynames}.}
@@
 % Naming norms record naming responses for dozens or hundreds of speakers for the same object.
-Picture naming norms are typically small (500-1000 images) and use idealized drawings (Figure~\ref{fig:cake}, right; \cs{but see, e.g.,~\cite{brodeur2014bank} for exceptions}); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
+Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
 %\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
@@
 
-% NEW -- I thought we needed to include this discussion, too.
-Object names are rarely used in isolation; typically they are embedded in more complex referring expressions, which are themselves embedded in sentences that are part of discourses or dialogues.
-However, in the same way that it has proven useful to model referring expressions in visual scenes in an isolated fashion \cite{Kazemzadeh2014,mao15,Yu2016}, \cs{test models on reasoning abilities over whole scene; we observe instance-based variation, triggered by concrete appearance of object and its context, hence, analogous reasoning is required for naming, too} we believe there is value in modeling object names on their own.
-Questions that need addressing regarding object naming are 1)~how much variation in naming is attested and what factors drive the choice of a name (object category?
-individual properties of the object?
-context?); see e.g.\ Rohde et al.~\shortcite{rohde2012communicating} and Graf et al.~\shortcite{graf2016animal}, 2)~how to make L\&V models more human-like with respect to naming, improving the design of L\&V architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
-\gbt{I looked at the bst file but I don't know how to make the year appear without parentheses inside the parenthesis.}
-% ManyNames can inform both theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal} and on the design of L\&V models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
 Here, for reasons of scope and space, we provide preliminary results on the amount and type of variation we find in the data.
-
+%
 The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the name \word{cake}, corresponding to the so-called basic-level category, see Section~\ref{sec:rel-work}) and also rich variation (the remaining annotators prefer other options like \word{food, dessert, bread}) that is not restricted to taxonomic relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}: while \word{food} is in a taxonomic relation to \word{cake} (it is a hypernym), \word{dessert} highlights a different facet of the object.

### 2020-03-12 papers/LREC2020/survey.tex
shortens Gemma's new intro

@@
 
-However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fifth object IDs in the figure actually correspond to the same object.
-Moreover, the regions for the beak of the object (third and fourth object IDs) overlap with those of the bird. 
+However, there is a crucial pitfall: As Figure~\ref{fig:bird} shows, there is only a partial linking of objects that are mentioned across different region descriptions; for instance, the first, second, and fourth object ID in the figure actually correspond to the same object.
+Moreover, the region for the beak of the object (third object IDs) overlaps with those of the bird. 
 %This means that the identity of objects cannot be established based on the annotation, which severely limits the usefulness of the data to analyze naming.
@@
 %This is a figure with a caption.}}
-\includegraphics[scale=0.32]{figures/vulture.png} 
+\includegraphics[scale=0.25]{figures/vulture.png} 
 \begin{tabular}{lp{6cm}}

### 2020-03-12 papers/LREC2020/data-collection.tex
adds logos

@@
 	\centering
-	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VG.png}
+	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VGMN.png}
 	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
@@
 This yielded a dataset of $31,093$~instances, which was further pruned during annotation, as explained next.
-Table~\ref{tab:overview_dataset1} shows the top $5$~\vg names in each of the domains. 
+Figure~\ref{fig:overview_dataset1} shows the distribution of images and names in ManyNames per domain. 
 %\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}

### 2020-03-13 papers/LREC2020/conclusion.tex
some comments (5 or 6) in LREC paper

@@
 
-For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object recognition and naming.
-Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.
+For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous \sz{does the data presented here really do this?}, which can affect model performance on object recognition and naming.
+Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.\sz{well, this paper does not contain the verification data right=}
 

### 2020-03-13 papers/LREC2020/data-collection.tex
updates distr plot; updates lrec style file
some comments (5 or 6) in LREC paper

@@
 
-\begin{figure}[htp]
+\begin{figure*}[htp]
 	\centering
-	\includegraphics[width=1\columnwidth]{figures/distr_imgs-per-domain_VGMN.png}
-	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
+	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN.png}
+	\caption{Cumulative histograms of the number of images and \sz{original VG?} names per domain in ManyNames.}
 	\label{fig:overview_dataset1}
-\end{figure}
+\end{figure*}
 
@@
   \centering
-  \includegraphics[width=1.5\columnwidth]{figures/round1+_p1.png}
+  \includegraphics[width=1\columnwidth]{figures/round1+_p1.png}
   \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}

### 2020-03-13 papers/LREC2020/intro.tex
some comments (5 or 6) in LREC paper

@@
 Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
-We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
+We chose a creation methodology for ManyNames to \sz{sounds slightly weird, a methodology that ... ???}overcome these shortcomings in particular.
 %This motivates the development of ManyNames, as well as our design choices for it.
@@
 \footnote{Available at \url{https://github.com/amore-upf/manynames}.}
-It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
+It is inspired in \sz{by?} picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
 %\gbt{Is it ``picture naming norms'', or ``naming norms''?}

### 2020-03-13 papers/LREC2020/lrec2020naming.tex
some comments (5 or 6) in LREC paper

--- 2020-03-12 papers/LREC2020/lrec2020naming.tex
@@
 
-\section{Object Names in Existing L\&V Resources}
+\section{Object Names in Existing L\&V resources}
 \label{sec:survey}
@@
 
-\section{Acknowledgments}
-We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
- This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
- % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
- This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
- \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
+%\section{Acknowledgements}
+
 % Place all acknowledgements (including those concerning research grants and

### 2020-03-13 papers/LREC2020/survey.tex
adds logos
updates distr plot; updates lrec style file
some comments (5 or 6) in LREC paper

--- 2020-03-12 papers/LREC2020/survey.tex
@@
 The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
+REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use certain \sz{only left and right were forbidden, east and west are allowed ;-)} location words, urging them to refer to the appearance of objects.
  % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?

### 2020-03-13 papers/LREC2020/lrec2020naming.tex
Revert "some comments (5 or 6) in LREC paper"
This reverts commit 227533ee2d519b2c6544ce13e566a156d256805e.

--- 2020-03-12 papers/LREC2020/lrec2020naming.tex
@@
 We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average.
-At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed at length in the theoretical literature, and other less well studied phenomena like cross-classification\cs{Should we keep this term?
-(@GBT cf.
-discussion with A.
-Maedebach)} (\word{cake} vs.\ \word{dessert}).
+At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed at length in the theoretical literature, and other less well studied phenomena like cross-classification
+%\cs{Should we keep this term? (@GBT cf. discussion with A. Maedebach)} 
+(\word{cake} vs.\ \word{dessert}).
 % may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}

### 2020-03-13 papers/LREC2020/analysis.tex
move img
small mods

@@
 \begin{figure}
+\vspace{-4ex}
 \includegraphics[width=\columnwidth]{figures/types_instances.png}
@@
 Even factoring in the noise introduced by referential uncertainty, it is clear that a good portion of our data cannot be explained by variation in the level of abstraction of the chosen name. 
-Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
+Among the names that do have a taxonomic relation to the synset, hypernyms are the most frequent, meaning that our annotators often chose a more general name than the \vg annotators.
 %%In this section, we take a closer look at the lexical variation we observe in our data set. 
@@
 
-In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}.
+In a qualitative analysis, we found the following types of variation in the data, illustrated with examples in Figure~\ref{fig:ex-high-low-agreement}: 
 \textbf{Cross-classification}: a substantial group are names conceptualizing alternative aspects of the same object (e.g. \word{toast/dessert}, image C).
-\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, images J).
+\textbf{Conceptual disagreement}: as we did not filter objects for prototypicality, our data mirrors a certain amount of disagreement between speakers as to what an object is (\word{bed/bench}, image J).
 \textbf{Metonymy}: we find examples reminiscent of metonymy discussed in the linguistic literature \cite{pustejovsky1991generative} where logically related parts of an object stand in as its name (\word{burger/basket}, image B).
@@
 %
-\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
+%\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
+Our analysis 
 \begin{table}[t]

### 2020-03-13 papers/LREC2020/intro.tex
small mods

--- 2020-03-12 papers/LREC2020/intro.tex
@@
 %While these resources can be exploited for this area of inquiry to some extent (as detailed in Section~\ref{sec:survey})\cs{how remove dot?}, we argue that the low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
-Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}\cs{how remove dot?}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
-We chose a creation methodology for ManyNames to overcome these shortcomings in particular.
+Existing resources in L\&V that provide object names can be exploited for this area of inquiry to a limited extent only, as we will detail in Section~\ref{sec:survey}, because their low number of annotations per item prevents reliable assessment of \textbf{naming preferences}, on the one hand, and \textbf{variation}, on the other.
+We chose a creation methodology for ManyNames that overcome these shortcomings in particular.
 %This motivates the development of ManyNames, as well as our design choices for it.
@@
 % A more systematic understanding of the factors influencing the choice of object names could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures (e.g.,~Lazaridou et al.~\shortcite{lazaridou-dinu-baroni:2015:ACL-IJCNLP}; Ordonez et al.,~\shortcite{Ordonez:2016}; Zhao et al.,~\shortcite{zhao2017open}).
-ManyNames~v.1 contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}.%
-\footnote{Available at \url{https://github.com/amore-upf/manynames}.}
-It is inspired in picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
+ManyNames~v.1\footnote{Available at \url{https://github.com/amore-upf/manynames}.} contains $36$ crowd-sourced names for $25$K object instances from \vgenome \cite{krishna2016visualgenome}. 
+It is inspired by picture naming norms as developed in Psycholinguistics~\cite{snodgrass,rossion2004revisiting}, which is the field that has devoted the most attention to object naming to date.
 %\gbt{Is it ``picture naming norms'', or ``naming norms''?}
 % Naming norms record naming responses for dozens or hundreds of speakers for the same object.
-Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~\cite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
+Picture naming norms are typically small ($500$-$1$K~images) and use idealized drawings (Figure~\ref{fig:cake}, right; but see, e.g.,~Brodeur et al.,~\shortcite{brodeur2014bank} for exceptions); ManyNames is much larger and uses real-world images of objects in complex visual contexts, which makes it suitable for research in L\&V.
 %\gbt{should we add footnote citing the naming norms that have real images? (See commented-out tex; \cite{brodeur2014bank} is the ref for the BOSS database.)}
@@
 \centering
-\includegraphics[scale=0.15]{figures/2390077_1254219_supercat_unique.png} &
+\includegraphics[scale=0.14]{figures/2390077_1254219_supercat_unique.png} &
 \includegraphics[scale=0.4]{figures/snodgrass_vanderwart_cake_042.png}\\

### 2020-03-13 papers/LREC2020/survey.tex
small mods

--- 2020-03-12 papers/LREC2020/survey.tex
@@
 The matcher must click on the object she thinks the RE refers to. % (For more details on the datasets see \cite{Yu2016}). 
-REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use location words, urging them to refer to the appearance of objects.
+REs in \refcoco/+ were collected under the constraints that (i) all images contain at least two objects of the same category (80 COCO categories), which results in longer and more complex REs than just the object name, and (ii) in \refcocop the players cannot use certain location words, urging them to refer to the appearance of objects.
  % \gbt{How come the naming vocabulary size is so large if RefCOCO contains only 80 categories?
@@
 %However, the small number of annotations per object does not allow for a reliable assessment of speaker agreement. 
-However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement. \cs{double-check formulation}
+However, the small number of annotations per object does not allow to reliably infer object-specific naming preferences or assess speaker agreement.
 
@@
 %This is a figure with a caption.}}
-\includegraphics[scale=0.25]{figures/vulture.png} 
-\begin{tabular}{lp{6cm}}
+\includegraphics[scale=0.2]{figures/vulture.png} 
+\begin{tabular}{lp{6.2cm}}
 object id & linked region descriptions\\

### 2020-03-13 papers/LREC2020/analysis.tex
solves a couple of issues and makes fit again

@@
 Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
-With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
-This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
+With a reasonable threshold of $t$=2 (based on data inspection; names entered by one annotator only have the most noise, which is to be expected), a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
+This threshold is used in Fig.~\ref{fig:ex-high-low-agreement}, showing names that have at least frequency 2.
 The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
@@
 \begin{itemize}
+  \setlength\itemsep{-0.5pt}
 \item \textbf{N}: the average number of types in the response set. %of ManyNames.

### 2020-03-13 papers/LREC2020/data-collection.tex
fixes errors in Fig 3
solves a couple of issues and makes fit again

@@
 % Number of collection nodes (synsets):    52 \\
-
-\begin{table*}[htp]
-	\small
-	\centering
-	\begin{tabular}{lp{14cm}}
-			\toprule
-			Domain & \multicolumn{1}{c}{Collection synsets}\\
-			\midrule			
-			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
-			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
-			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
-                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
-			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
-                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
-			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
-                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
-			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
-			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
-			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
-			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
-			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
-                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
-			\bottomrule
-		\end{tabular}
-		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
-                  \label{tab:overview_dataset2}}
-	\end{table*}
 
@@
 	\centering
-	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN.png}
-	\caption{Cumulative histograms of the number of images and \sz{original VG?} names per domain in ManyNames.}
+	\includegraphics[scale=.8]{figures/distr_imgs-per-domain_VGMN_v2.png}
+% WAS:	\caption{Cumulative histograms of the number of images and names per domain in ManyNames.}
+% But it's not really a cumulative histogram
+	\caption{Number of images per domain ManyNames. Colors are the original VG names; all high-frequency names are shown, as well as a few lower-frequency names.}
 	\label{fig:overview_dataset1}
-\end{figure*}
-
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=1.5\columnwidth]{figures/round0_cropped.png}
-  \caption{Instructions for AMT annotators for the first round (whole instructions showed more examples, see Figure~\ref{fig:instructions2}).}
-  \label{fig:instructions1}
 \end{figure*}
@@
 
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1.5\columnwidth]{figures/round0_cropped.png}
+  \caption{Instructions for AMT annotators for the first round (whole instructions showed more examples, see Figure~\ref{fig:instructions2}).}
+  \label{fig:instructions1}
+\end{figure*}
+
+\begin{figure*}[htp]
+  \centering
+  \includegraphics[width=1\columnwidth]{figures/round1+_p1.png}
+  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
+  \label{fig:instructions2}
+\end{figure*}
+
 \subsection{Elicitation Procedure}
@@
 
-\begin{figure*}[htp]
-  \centering
-  \includegraphics[width=1\columnwidth]{figures/round1+_p1.png}
-  \caption{Instructions for AMT annotators for rounds~$2$ to~$4$.}% They were accompanied by the FAQ in Figure~\ref{fig:faq}}
-  \label{fig:instructions2}
-\end{figure*}
-
 % \begin{figure*}[htp]

### 2020-03-13 papers/LREC2020/analysis.tex
Adds Gemma's corrections

--- 2020-03-13 papers/LREC2020/analysis.tex
@@
 Without any frequency thresholding~\mbox{$t$=1}, that is, allowing names entered by only one annotator, the proportion of instances that have a single name annotated is very small, below\ $10\%$, and there is a long tail of datapoints with many names, up to 19.
-With a reasonable (based on data inspection; names entered by one annotator only have the most noise, which is to be expected) threshold of $t$=2, a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
-This threshold is the one illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
+With a reasonable threshold of~$t$=$2$ (based on data inspection; names entered by one annotator only have the most noise, which is to be expected), a bit over $20\%$\ of the objects have one name, almost $50\%$\ up to $3$\ names, and $100\%$\ up to $8$\ names.
+This threshold is illustrated in Fig.~\ref{fig:ex-high-low-agreement}, which shows names that have at least frequency 2.
 The average number of names with this threshold is\ $2.9$, and the most frequent name accounts on average for $75\%$\ of the responses for a given object (Table~\ref{tab:agree}, and see below).
@@
 %\cs{TO ADD: What does ManyNames provide, that WordNet can't: out-of-vocabulary words; we observe instance-based variation, WordNet is class-based: valid (co-)hyponyms, different most preferred name depending on instance, variations which are not due to taxonomic relations}
-Our analysis 
 \begin{table}[t]

### 2020-03-17 papers/LREC2020/conclusion.tex

--- 2020-03-12 papers/LREC2020/conclusion.tex
@@
 With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.
+%
+These findings also show WordNet's limitations in its use for  visual object naming \cite[a.o.]{Ordonez:2016}: while, for a particular object, synonyms and hypernyms may be retrieved as name alternatives, hierarchically unrelated alternatives cannot, nor does WordNet provide information on object-specific naming preferences.
 

### 2020-03-17 papers/LREC2020/data-collection.tex
Adds Gemma's corrections

@@
 % But it's not really a cumulative histogram
-	\caption{Number of images per domain ManyNames. Colors are the original VG names; all high-frequency names are shown, as well as a few lower-frequency names.}
+	\caption{Number of images and top responses (most frequent name per image), per domain. All high-frequency names are shown, as well as a few lower-frequency names.}
 	\label{fig:overview_dataset1}

### 2020-03-20 papers/ACL2020/revision/manynames.tex

\begin{itemize}
\item brief intro to manynames and the verification procedure 
\item limit the analysis to aspects that are clearly and strictly related to the goals of the paper: 1)~quality of the verification data itself (inter-annotator agreement), 2)~show that most objects do in fact have a ``natural name'' (such that it makes sense to do single-label classification with those), 3)~show that we need for many annotations to establish ``natural name''. TBD: also show the distribution of human errors in the original ManyNames v.1 data?
\end{itemize}

% \begin{figure}[t]
% 	\centering
% 	\includegraphics[width=\columnwidth]{images/verification_piechart_double.pdf}\\
% 	\hspace*{\fill}a.\hspace*{\fill}\hspace*{\fill}b.\hspace*{\fill}\hspace*{\fill}
% 	\caption{Verification results: a. counting individual annotations; b. counting image-name pairs with their aggregated scores. Lighter shade within a hue indicates slight/possible error of that type; darker shade severe error.}
% 	\label{fig:verification-piechart}
% \end{figure}

%%% Local Variables:
%%% mode: plain-tex
%%% TeX-master: "acl2020_main"
%%% End:

### 2020-03-20 papers/LREC2020/survey.tex

@@
 
+\begin{figure}
+\begin{center}
+%\fbox{\parbox{6cm}{
+%This is a figure with a caption.}}
+\includegraphics[scale=0.2]{figures/vulture.png} 
+\small
+\begin{tabular}{lp{6.2cm}}
+object id & linked region descriptions\\
+\hline
+3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
+2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
+%2385747 & small white beak of \textbf{bird}\\
+2681429 & a semi \textbf{long beak}\\  
+2346210 & a black and gray \textbf{vulture}\\
+ \end{tabular}
+\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
+\label{fig:bird}
+\end{center}
+\end{figure}
+
+\begin{table*}[htbp]
+	\small
+	\centering
+	\begin{tabular}{lp{14cm}}
+			\toprule
+			Domain & \multicolumn{1}{c}{Collection synsets}\\
+			\midrule			
+			animals\_plants & ungulate$_1$ (2037), horse$_1$ (833), feline$_1$ (763), dog$_1$ (688)
+			bird$_1$ (389), flower$_1$ (44), rodent$_1$ (27), insect$_1$ (12), fish$_1$ (11)\\
+			buildings      &  house$_1$ (364), bridge$_1$ (297), shelter$_1$ (169), restaurant$_1$ (58),
+                                         outbuilding$_1$ (31), hotel$_1$ (19), housing$_1$ (17), place\_of\_worship$_1$ (12)     \\
+			clothing       &  shirt$_1$ (968), overgarment$_1$ (786), dress$_1$ (199), headdress$_1$ (135),
+                                         neckwear$_1$ (65), robe$_1$ (27), glove$_2$ (7), footwear$_1$ (5)    \\
+			food           &  dish$_2$ (812), baked\_goods$_1$ (770), foodstuff$_2$ (280), vegetable$_1$ (48),
+                                         edible\_fruit$_1$ (42), beverage$_1$ (23)   \\
+			home           &  furnishing$_2$ (5,355), vessel$_3$ (525), kitchen\_utensil$_1$ (132), crockery$_1$ (92),
+			cutlery$_2$ (82), tool$_1$ (72), lamp$_1$ (34)    \\
+			people         & woman$_1$ (1768), man$_1$ (1167), male\_child$_1$ (853), athlete$_1$ (396),
+			 child$_1$ (333), creator$_2$ (11), professional$_1$ (5)    \\
+			vehicles       &  aircraft$_1$ (1208), train$_1$ (957), car$_1$ (727), motorcycle$_1$ (564),
+                                         truck$_1$ (559), boat$_1$ (499), ship$_1$ (38)    \\
+			\bottomrule
+		\end{tabular}
+		\caption{Overview of the ManyNames dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses).
+                  \label{tab:overview_dataset2}}
+	\end{table*}
+
 \vgenome (VG, \newcite{krishna2016visualgenome}) is one of the most densely and richly annotated resources currently available in L\&V; here, we focus on aspects immediately relevant to object naming.
@@
 
-While some existing resources do provide naming data for objects in context, they do not provide \textit{enough} data to systematically assess how variable or stable object naming really is.
+While some existing resources do provide naming data for objects in context, they do not provide enough data to systematically assess how variable or stable object naming really is.
 The RefCOCO data (and to some extent the Flickr30k data) suggests that for most objects there is more than one available name, but it is unclear which name most speakers would prefer or whether there is such a preferred name at all.
@@
 
-\begin{figure}
-\begin{center}
-%\fbox{\parbox{6cm}{
-%This is a figure with a caption.}}
-\includegraphics[scale=0.2]{figures/vulture.png} 
-\begin{tabular}{lp{6.2cm}}
-object id & linked region descriptions\\
-\hline
-3595788 & the \textbf{bird} is black in color, nose of the \textbf{bird}, a \textbf{bird} relaxing in stand, small white beak of \textbf{bird}, large black talon of \textbf{bird}, a \textbf{bird} on a green pole, a green bar under \textbf{bird}, black \textbf{bird} on green rail, small black eye of \textbf{bird}\\
-2286017 & large black \textbf{vulture} on fence, a vulture on bar\\
-%2385747 & small white beak of \textbf{bird}\\
-2681429 & a semi \textbf{long beak}\\  
-2346210 & a black and gray \textbf{vulture}\\
- \end{tabular}
-\caption{Bounding boxes, names and region descriptions for an object in VisualGenome}
-\label{fig:bird}
-\end{center}
-\end{figure}
-
 %%% Local Variables:

### 2020-03-30 papers/ACL2020/revision/introduction.tex

\begin{itemize}
\item We're interested in modeling human naming behavior [motivate]
\item names are sometimes used as labels for object classification in CV
\item usually: single-label evaluation scheme
  \begin{enumerate}
  \item if a single-label evaluation scheme is used, the target name should be the one that is most naturally used for the object. [Here we need a bit of background saying that it has been shown in Psycholing that people tend to agree in the name they give to objects.] To estimate this ``natural name'' (need better term), we need a reasonable sample.
  \item however, a single-label evaluation scheme assumes object names are unique (cf.\ evaluation; any other response is counted as incorrect). But alternative names are in fact possible.
  \end{enumerate}
\item (thanks to ManyNames,) we train models on the task of providing natural names; existing models, fine-tuned models 
\item and we analyze the consequences of evaluating them on a single-label scheme vs.\ one that allows for naming variants
\item (TBD: and we compare their errors/behavior to the human errors/behavior)
\end{itemize}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl2020_main"
%%% End:

### 2020-03-30 papers/LREC2020/background.tex
lrec camera ready, correcting 2 small issues identified by Carina

@@
 
-The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left'').\cs{rephrase}
+The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left''). 
 Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.
@@
 The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
-Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}.\cs{double-check latter}
+Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
 Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
@@
 This controlled collection procedure allowed us to elicit many names for the same object from different annotators, resulting in a dataset that is amenable to  studying systematically and on a large scale the core phenomena of object naming, viz.
-naming variation and preferences.\cs{rephrase}
+naming variation and preferences.
 
@@
     av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
-    ratio of objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
-    av. name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
+    ratio of objects with \# types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
+    av. \# name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
     \bottomrule
